### 2022-11-03 Motivations and Related Work.tex
first commit with some preliminary work

\documentclass[11pt,a4paper]{article}
\usepackage[a4paper, total={6.5in, 10in}]{geometry}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{complexity} %% already defined: \NP \APX \SAT \MaxSAT \FPT ...
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{comment}
%\usepackage{mathabx}
\usepackage{mathrsfs}
\usepackage{blindtext, rotating} %turn environments
\usepackage{diagbox} %slashbox in tabular environment
\usepackage{multicol} %\begin{multicols}{3}[ta del ni v kolonah]
%\usepackage{enumitem}
\usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
\usepackage{enumerate}
\usepackage{wrapfig} %wrap the text around the picture
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{caption} %for subfigure - join multiple figures and add captions
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{multirow} %join two rows in a table
\usepackage{todonotes}
\newcommand{\todogr}[2][]{\todo[color=cyan!10!green!100!,#1]{#2}} %special color todo note
\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
\setlength{\marginparwidth}{3.7cm} %setting the length of todonote

\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{patterns}
\usetikzlibrary{fadings}
\tikzstyle{vert2}=[circle,inner sep=1.5,fill=white,draw,minimum size=.2cm]
\tikzstyle{vert3}=[inner sep=1.5,fill=white,draw=black,minimum size=.2cm]
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Environments
\newenvironment{remark}{\itshape Remark:}{\par}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%listings je paket za vnašanje programske kode
\usepackage{listings}
\renewcommand{\lstlistingname}{Koda}

\usepackage{xcolor}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	language=Python,
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=10pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=4
}

\lstset{basicstyle=\large,style=mystyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Hyperref
\usepackage[pdfusetitle]{hyperref}

\definecolor{myBlue}{rgb}{0.25, 0.0, 1.0}
\hypersetup{
	pdfauthor=  {Nina Klobas},
	colorlinks = true,
	linkcolor=myBlue,
	citecolor=green!50!black,
	urlcolor=green!50!black,
	bookmarksopen=true,
	bookmarksnumbered,
	bookmarksopenlevel=2,
	bookmarksdepth=3
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Cref (nameinLink = whole name is a link)
\usepackage[capitalise,nameinlink, noabbrev]{cleveref}
\usepackage{authblk} % customize author and affiliation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% My macros
\newcommand{\ie}{i.\,e.,\ }
\newcommand{\st}{s.\,t.,\ }
\newcommand{\etal}{et.\,al.\ }
\newcommand{\appsymb}{$\star$}

\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\QQ}{\mathbb{Q}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
\usepackage{tabularx}
\newcommand{\problemdef}[3]{
	\begin{center}
		\begin{minipage}{0.95\textwidth}
			\noindent
			#1
			\vspace{5pt}\\
			\setlength{\tabcolsep}{3pt}
			\begin{tabularx}{\textwidth}{@{}lX@{}}
				\textbf{Input:}& #2 \\
				\textbf{Output:}& #3
			\end{tabularx}
		\end{minipage}
	\end{center}
}

%\newcommand{\Walks}{\textsc{Temporally Disjoint Walks}}

%\graphicspath{{../fig/}} %%%%%definiramo pot do mape s slikami

\title{Graph Realization -- literature}
\author{}
\begin{document}

\section{Motivation}
\begin{enumerate}
	\item \hyperlink
{http://dagstuhl.sunsite.rwth-aachen.de/volltexte/2022/16811/pdf/LIPIcs-MFCS-2022-13.pdf}
{Graph Realization of Distance Sets - Amotz Bar-Noy, David Peleg, Mor Perry, Dror Rawitz}

``
Network realization problems are fundamental graph-algorithmic questions in which one is asked to construct a network conforming to some predefined requirements.
Given a specification (or information profile) that consists of constraints on some network parameters, such as the vertex degrees, distances, or connectivity, one is required to construct a network conforming to the given specification, i.e., satisfying the requirements, or to determine that no such network exists. The motivation for network realization problems stems from both “exploratory” contexts where one attempts to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering contexts related to network design.
''

\item
\hyperlink{https://arxiv.org/pdf/1912.13287.pdf}{Efficiently Realizing Interval Sequences - Amotz Bar-Noy, Keerti Choudhary, David Peleg, Dror Rawitz}

``
The Graph Realization problem for a property P deals with the following existential question: Does there
exist a graph that satisfies the property P? Its fundamental importance is apparent, ranging from better
theoretical understanding, to network design questions (such as constructing networks with certain desirable
connectivity properties). Some very basic, yet challenging, properties that have been considered in past are
degree sequences [9, 18, 20], eccentricites [6, 24], connectivity and flow [16, 12, 10, 11].
''

\item 
\hyperlink{https://arxiv.org/pdf/1912.13286.pdf}{Graph Realizations: Maximum and Minimum Degree in Vertex
	Neighborhoods - Amotz Bar-Noy, Keerti Choudhary, David Peleg, Dror Rawitz}

``
The motivation underlying the current paper is
rooted in the observation that realization questions of a similar nature pose themselves naturally in a large
variety of other application contexts, where given some type of information profile specifying the desired
vertex properties (be it concerning degrees, distances, centrality, or any other property of significance), it
can be asked whether there exists a graph conforming to the specified profile. Broadly speaking, this type
of investigation may arise, and find potential applications, both in scientific contexts, where the information
profile reflects measurement results obtained from some natural network of unknown structure, and the goal
is to obtain a model that may explain these measurements, and in engineering contexts, where the informa-
tion profile represents a specification with some desired properties, and the goal is to find an implementation
in the form of a network conforming to that specification.

This basic observation motivates a vast research direction, which was little studied over the last five
decades. In this paper we make a step towards a systematic study of one specific type of information
profiles, concerning neighborhood degree profiles. Such profiles are of theoretical interest in context of
social networks (where degrees often reflect influence and centrality, and consequently neighboring degrees
reflect “closeness to power”).
''

\item 
\hyperlink{https://sci-hub.ru/https://link.springer.com/chapter/10.1007/978-3-030-79987-8_5}
{Relaxed and Approximate Graph Realizations Amotz Bar-Noy, Toni Bohnlein, David Peleg, Mor Perry, Dror Rawitz}\footnote{Page 22 of 605 (page 3)}

``
Network realization problems are fundamental questions pertaining to the ability
to construct a network conforming to pre-defined requirements. Given a specifica-
tion (or information profile) detailing constraints on some network parameters,
such as the vertex degrees, distances or connectivity, it is required to construct
a network abiding by the specified profile, i.e., satisfying the requirements, or to
determine that no such network exists.

Realization problems may arise in two general types of contexts. In scientific
contexts, the information profile may consist of the outcomes of some measure-
ments obtained from observing some real world network (e.g., social networks
and information networks) whose full structure is unknown. In such a setting, our
goal is to construct a model that may possibly explain the empirical observations.
Many of the studies in the field of phylogenetics and evolutionary trees (see, e.g.,
[16,23,41,42,51,63,68,84,88]) as well as in the field of discrete tomography and
microscopic image reconstruction (see, e.g., [3–5,11,15,46,47,52,64,77]) belong
to this class.

A second, engineering-related context where realization problems come up is
network design. Here, the profile may be defined based on a specification dic-
tated by the future users of the network, and the goal is to construct a network
that obeys the specification. For example, the profile may specify the required
connectivity, flow capacities, or distances between vertex pairs in the network. In
particular, network realization techniques may be useful in the area of software
defined networks (SDN). For example, in service chain placement, the specifi-
cation can define a directed acyclic graph (DAG) of virtual network functions
(VNF), and the realization must determine the placement of one of the paths of
the DAG in the physical network [38,39,72].
'''

\item 
\hyperlink{https://sci-hub.ru/https://link.springer.com/chapter/10.1007/978-3-030-79987-8_5}{Composed Degree-Distance Realizations of Graphs - Amotz Bar-Noy, David Peleg, Mor Perry, Dror Rawitz}\footnote{Page 80 of 605 (page 63)}

```
Network realization problems require, given a speciﬁcation $\Pi$
for some network parameter (such as degrees, distances or connectivity),
to construct a network $G$ conforming to $\Pi$, or to determine that no such
network exists. In this paper we study composed proﬁle realization, where
the given instance consists of two or more proﬁle speciﬁcations that need
to be realized simultaneously. To gain some understanding of the problem, we focus on two classical proﬁle types, namely, degrees and distances,
which were (separately) studied extensively in the past.
'''
\end{enumerate}

\section{Related work}
\begin{enumerate}

\item \hyperlink{https://arxiv.org/pdf/2002.05376.pdf}
{DISTRIBUTED GRAPH REALIZATIONS - John Augustine, Keerti Choudhary, Avi Cohen, David Peleg, Sumathi Sivasubramaniam, Suman Sourav}

\textbf{Motivation/development:}
``
Over the last two decades, peer-to-peer (P2P) networks have developed as a versatile and effective platform for cooperative distributed computations. Research on P2P has lead to ideas that have become crucial in a variety of contexts,
ranging from fully decentralized applications like blockchain networks to more controlled contexts like Akamai’s
network services [33]. Overlay construction is an important P2P component, involving the formation of new links
– so called overlay links – that comprise an overlay network tailored to benefit P2P applications. In the typical scenario, starting from some basic network state, the nodes in a P2P network must interact with each other in a fully
decentralized manner and form an overlay network to be used for specific purposes.

The constructed overlay network G is often required to possess certain desirable properties. A common requirement
is that G be of bounded degree, so that the overhead for network formation and maintenance at each node is bounded.
Additionally, one can envision a variety of other desired properties that the overlay G should possess, like bounded
diameter, well-connectedness, flow guarantees, tolerance to both benign and malicious failures, and so on.

Note, however, that such overlay constructions can be viewed as (distributed) graph realization problems. This natural
connection makes it plausible that ideas from graph realization theory may lend interesting new techniques allowing
us to build better overlay networks. Conversely, the endeavor to build useful overlay networks is expected to pose new
theoretical challenges that are likely to enrich graph realization theory. We hope that our work will initiate this new
synergy between these two areas that, to the best of our knowledge, has not been formally explored in the past.

Towards the goal of formulating and studying distributed graph realization problems, we employ the node capacitated
clique (NCC) model [4] that captures several key aspects of P2P networks. In this model, we have n nodes V with
unique identifiers called IDs. Any node u can send messages of bounded size to any other node v provided u knows
v’s ID; we can think of v’s ID as its IP address. In this sense, the NCC model is somewhat similar to the congested
clique (CC) model [23, 25]. However, in the interest of being useful in the P2P context, NCC limits each node to send
and receive a bounded number of messages, which, interestingly, makes NCC quite distinct from CC.
''

\textbf{Problem Statements}:

``
We say that an overlay graph $G = (V, E)$ is constructed if, for every $e = (u, v) \in E$, at
least one of the endpoints is aware of the ID of the other and also aware that $e \in E$. We say that the overlay graph
is explicit if, for every edge in the graph, both endpoints are aware of the edge. Otherwise, the overlay is said to be
implicit. In this paper, we focus on distributed realization problems in which, from a given initial knowledge graph
and some other required input parameters, we are to construct an overlay graph that satisfies certain requirements. We
study both explicit and implicit versions of the following two realization problems.

\emph{Degree Realization:} Each node $v_i$ in the distributed network knows its required degree $d(v_i) = d_i$. The goal is to
construct a realizing graph (if one exists). Formally, our input is a vector $D = (d_1, d_2, \dots, d_n)$ such that each $d_i$
is only known to the corresponding node $v_i$. The required output is an overlay graph in which every $v_i$ has degree
$d_i$ if $D$ is realizable; otherwise, at least one node outputs Unrealizable. We also explore degree realization in the
non-preassigned setting. In this case, each node $v_i$ is given a degree $d_i$, but the required output is an overlay graph
whose degree sequence is only required to be a permutation of $D$.

\emph{Connectivity Threshold Realization:} The local edge connectivity of two nodes $u$ and $v$, denoted $Conn_G(u, v)$, captures the minimum number of edge disjoint paths required between the nodes $u$ and $v$¸. In the connectivity realization
problem, each node $v$ in the distributed network is provided with a vector specifying the required minimum local edge
connectivity (denoted by $\sigma (u, v)$) to every other node $u$. The goal is then to compute an overlay graph $G$ with as few
edges as possible so that any two nodes $u, v \in G$ satisfy the edge-connectivity relation $Conn_G(u, v) \geq \sigma (u, v)$.
For this problem, we primarily focus on an approximate solution. In particular, we ensure that the number of edges in
the overlay network is larger by at most twice that of the optimal realization.
''
\end{enumerate}

\end{document}

### 2022-11-03 RealizingTemporalGraphs.tex
first commit with some preliminary work

\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}

\usepackage{fullpage}

\usepackage{amsmath}
\let\proof\relax
\let\endproof\relax

\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{wrapfig} %wrap the text around the picture

\usepackage{thmtools} 
\usepackage{thm-restate}

\usepackage{caption} %for subfigure - join multiple figures and add captions
\usepackage{subcaption}
\usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
\usepackage{mathtools} % write text [under]{over} arrow $\xrightarrow[\text{world}]{\text{hello}}$

\usepackage{graphicx}
\graphicspath{{Figures/}}

%\usepackage{enumitem} %enumerate 
\usepackage{enumerate}
\usepackage{todonotes}
\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
\setlength{\marginparwidth}{3.7cm} %setting the length of todonote

\newtheorem{theorem}{Theorem}
\newtheorem{observation}{Observation}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[definition]{Example}
\usepackage{comment}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

%font encoding
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\usepackage{hyperref}

\usepackage[capitalise,nameinlink, noabbrev]{cleveref}
\crefname{claim}{Claim}{Claims}

\usepackage{authblk}

%\usepackage{natbib}

\newcommand{\ie}{i.\,e.,\ }
\newcommand{\st}{s.\,t.,\ }
\newcommand{\NP}{\textrm{NP}}
\newcommand{\APX}{\textrm{APX}}
\newcommand{\FPT}{\textrm{FPT}}
\newcommand{\XP}{\textrm{XP}}

\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\QQ}{\mathbb{Q}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
\usepackage{tabularx}
\newcommand{\problemdef}[3]{
	\begin{center}
		\begin{minipage}{0.95\textwidth}
			\noindent
			#1
			\vspace{5pt}\\
			\setlength{\tabcolsep}{3pt}
			\begin{tabularx}{\textwidth}{@{}lX@{}}
				\textbf{Input:}& #2 \\
				\textbf{Question:}& #3
			\end{tabularx}
		\end{minipage}
	\end{center}
}

\title{Realizing Temporal Graphs}
\author{Nina Klobas, George B. Mertzios, Hendrik Molter, Paul G. Spirakis}

\bibliographystyle{abbrv}
\begin{document}
	\maketitle

\section{Preliminaries}

\begin{definition}
	Let $P = ((e_1, \lambda_1), (e_2,\lambda_2), \dots , (e_k, \lambda_k))$ be a temporal path from $u$ to $v$, then the duration of $P$, denoted as $d(P)$ is $\lambda(e_k) - \lambda(e_1) + 1$.
\end{definition}

We denote with $d(u,v)$ the duration of the \emph{fastest} temporal path from $u$ to $v$.

\problemdef{\textsc{Exact Realization $(\Delta, k)$}}
{A matrix $D$ of exact durations of fastest temporal paths among each pair of vertices, and a period $\Delta$.}
{Does there exist a labeling $\lambda$ of the underlying graph $G$ of $D$, such that every edge receives exactly one label and $d(v_i,v_j) = D_{i,j}$, for any pair of vertices $v_i, v_j \in V(G)$.}

\problemdef{\textsc{Upper-bounded Realization $(\Delta, k)$}}
{A matrix $D$ of exact durations of fastest temporal paths among each pair of vertices, and a period $\Delta$.}
{Does there exist a labeling $\lambda$ of the underlying graph $G$ of $D$, such that every edge receives exactly one label and $d(v_i,v_j) \leq D_{i,j}$, for any pair of vertices $v_i, v_j \in V(G)$.}

\section{Results}

\begin{theorem}
	\textsc{Exact Realization $(\Delta, k)$} can be solved in polynomial time on paths, cycles, trees and stars.
\end{theorem}

\begin{proof}[Idea:]
	Starting from a fixed vertex we can fix the temporal path to all/some other vertices in the graph. This allows us to determine the value of labels on edges, with respect to each other.
	We then fix one label as $1$ and all other labels follow.
	Produced labeling is unique, up to $\Delta$ (\ie we get $\Delta$ ``equivalent'' labelings).

	Exact proof TBD.
\end{proof}

\begin{theorem}
	\textsc{Exact Realization $(\Delta, k)$} is \NP-hard on general graphs.
\end{theorem}

\begin{proof}
	Reduction from 3-SAT.

	Idea for gadgets, see ``Whiteboards/2022-11-03-Hendrik-Nina-Paul.pdf'', details TBD.
\end{proof}

%\bibliography{bibliography}	
\end{document}

### 2022-11-10 RealizingTemporalGraphs.tex
Updates from Overleaf

@@
 \crefname{claim}{Claim}{Claims}
+\crefname{observation}{Observation}{Observations}
 
@@
 
-\problemdef{\textsc{Exact Realization $(\Delta, k)$}}
-{A matrix $D$ of exact durations of fastest temporal paths among each pair of vertices, and a period $\Delta$.}
+\problemdef{\textsc{Exact Realization $(\Delta)$}}
+{A matrix $D$ of exact durations of fastest strict temporal paths among each pair of vertices, and a period $\Delta$.}
 {Does there exist a labeling $\lambda$ of the underlying graph $G$ of $D$, such that every edge receives exactly one label and $d(v_i,v_j) = D_{i,j}$, for any pair of vertices $v_i, v_j \in V(G)$.}
 
-\problemdef{\textsc{Upper-bounded Realization $(\Delta, k)$}}
-{A matrix $D$ of exact durations of fastest temporal paths among each pair of vertices, and a period $\Delta$.}
+\problemdef{\textsc{Upper-bounded Realization $(\Delta)$}}
+{A matrix $D$ of exact durations of fastest strict temporal paths among each pair of vertices, and a period $\Delta$.}
 {Does there exist a labeling $\lambda$ of the underlying graph $G$ of $D$, such that every edge receives exactly one label and $d(v_i,v_j) \leq D_{i,j}$, for any pair of vertices $v_i, v_j \in V(G)$.}
 
-\section{Results}
+%\section{Results}
+
+\section{
+\texorpdfstring{\textsc{Exact Realization $(\Delta)$} is in $P$}
+{Exact Realization (Delta) is in P}
+}
+
+	Let $G$ be the underlying graph of matrix $D$ and let $v$ be an arbitrary vertex in $G$, we want to determine the labeling $\lambda: E(G) \rightarrow [\Delta]$, that assigns exactly one label to each edge in $G$ and satisfies the distances from $D$.
+	To do so we observe some properties of the problem.
+
+	Let $v \in V$ be an arbitrary vertex in $V(G)$ and let $u \in V \setminus \{v\}$ be a vertex, that is at distance at least $2$ from $v$, in the underlying graph $G$.
+	Let $\mathcal{P}_{u}^v$ be a set of all $P_3$ paths on $3$ vertices in $G$, of form $(v_1, v_2, u)$, where $v_1, v_2 \in V(G)$, \st $v_1 v_2, v_2 u \in E(G)$ and $d(v,v_1) < d(v,v_2) < d(v,u)$. 
+	Intuitively, we can imagine the set $\mathcal{P}_{u}^v$ as the set of all incoming temporal $P_3$ paths to the vertex $u$, with respect to starting from the vertex $v$.
+
+	Let $P = (v_1,v_2,u)$ be an arbitrary path from $\mathcal{P}_u^v$, denote with $\lambda_1, \lambda_2$ the labels of edges $(v_1,v_2)$ and $(v_2, u)$, respectively.
+	By the definition of $\mathcal{P}_u^v$ it follows that $v_1, v_2$ are reached by $v$ faster than $u$ is reached by $v$, therefore we get the following inequality:
+	\begin{equation}\label{eq:ineq-uv-onePath}
+	    \lambda_2 \geq_\Delta \lambda_1 + d(v,u)-d(u,v_2) \pmod \Delta
+	\end{equation}
+	We repeat the above procedure for every path $P \in \mathcal{P}$ and collect all the inequalities to a set $S_u^v$.
+	Similarly we proceed for every pair of vertices $u$ and $v$.
+	At the end we get the collection of sets, each containing inequalities of the form \cref{eq:ineq-uv-onePath}.
+
+	\begin{claim}
+	\label{claim:exact-setsOfInequalities}
+	For the labeling $\lambda$ of $G$, that fulfills the fastest temporal paths conditions from $D$, the following two conditions have to hold. 
+	\begin{enumerate}
+	    \item $\lambda$ has to satisfy all the inequalities of sets $S_u^v$.
+	    \item At least one inequality in each set $S_u^v$ has to be an equality.
+	\end{enumerate}
+	\end{claim}
+    Intuitively, we know that we reach the vertex $u$ starting from $v$, only through paths in $\mathcal{P}_u^v$. 
+    An arbitrary path $P \in \mathcal{P}_u^v$ is either a part of the fastest path from $v$ to $u$, which means that the path arrives to $u$ at the time equal to $d(v,u)$,
+    or it is not a part of the fastest path, which means it arrives to $u$ at some time greater than $d(v,u)$.
+    This is how the inequalities from $S_u^v$ are constructed.
+Since the fastest path from $v$ to $u$ has to be of duration $d(v,u)$, at least one of the inequalities from $S_u^v$ has to be an equality.
+
+    Let $e_1=uv$ and $e_2=vz$ be two incident edges with $e_1 \cap e_2 = v$.
+    We denote with $\tau_v^{uz}$ the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo $\Delta$.
+    More specifically:
+    \begin{equation}\label{eq:def-VertexWaitingTime}
+       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+    \end{equation}
+    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal paths waits at vertex $v$ when first taking the edge $e_1=uv$ and then the edge $e_2 = vz$.
+
+    \begin{observation}
+    For any two consecutive edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, the value $\tau_v^{zu} = \Delta - \tau_v^{uz}$.
+    \end{observation}
+
+    \begin{proof}
+        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
+        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz}$.
+    \end{proof}
+
+    \begin{observation} \label{obs:exact-CyclesSum}
+    Let $C = (v_1, v_2, \dots, v_k)$ be a cycle in $G$.
+    Then 
+    \begin{equation*}
+        \sum_{i = 1}^k \tau_{v_i}^{v_{i-1}v_{i+1}} \equiv  0 \pmod \Delta,
+    \end{equation*}
+    where the indices of vertices $v_i$ are taken modulo $k$ (\ie $v_{-1}=v_{k-1}, v_0 = v_k, v_1 = v_{k+1}, \dots$).
+    \end{observation}
+
+    \begin{proof}
+        Using \cref{eq:def-VertexWaitingTime} and the fact that the indices of vertices $v_i$ are taken modulo $k$, we get the following:
+        \begin{align*}
+            &\sum_{i = 1}^k \tau_{v_i}^{v_{i-1}v_{i+1}}  \equiv  \sum_{i = 1}^k  (\lambda(v_i v_{i+1} - \lambda (v_{i-1} v_i) \pmod \Delta \equiv \\
+            &\lambda(v_1 v_2) - \lambda(v_{k}v_1) + \lambda(v_2 v_3) - \lambda(v_2 v_1) + \dots + \lambda(v_k v_1) - \lambda(v_{k-1}v_k) \pmod \Delta.
+        \end{align*}
+
+    \end{proof}
 
 \begin{theorem}
-	\textsc{Exact Realization $(\Delta, k)$} can be solved in polynomial time on paths, cycles, trees and stars.
+	\textsc{Exact Realization $(\Delta)$} can be solved in polynomial time on paths, cycles, trees and stars.
 \end{theorem}
@@
 \begin{proof}[Idea:]
-	Starting from a fixed vertex we can fix the temporal path to all/some other vertices in the graph. This allows us to determine the value of labels on edges, with respect to each other.
-	We then fix one label as $1$ and all other labels follow.
-	Produced labeling is unique, up to $\Delta$ (\ie we get $\Delta$ ``equivalent'' labelings).
+    For a labeling $\lambda$ we know that it has to satisfy \cref{claim:exact-setsOfInequalities}.
+    There are at most $n^2$ different sets $S_u^v$, each containing at most $n^2$ inequalities. 
+    Therefore we have $O(n^4)$ inequalities to satisfy with at least of $n^2$ of them being equalities (one for each set $S_u^v$.
 
-	Exact proof TBD.
+    Besides that we can also use the fact from \cref{obs:exact-CyclesSum}, which produces some extra restrictions on all inequalities.
+    We believe we can create some ``base of cycles'' over $G$ that would help us use \cref{obs:exact-CyclesSum} efficiently.
 \end{proof}
 
+\section{Hardness of Exact Realization}
+
+\todo[inline]{HM: For the following hardness I assume that we only consider strict temporal paths. (NK: Yes you are right, all paths are strict, sorry forgot to specify). \\
+Furthermore, I can currently only make it work if we do not have periods ($\Delta=\infty$). I am not sure the idea also works if we have periods.}
+
 \begin{theorem}
-	\textsc{Exact Realization $(\Delta, k)$} is \NP-hard on general graphs.
+	\textsc{Exact Realization $(\infty)$} is \NP-hard.
 \end{theorem}
@@
 \begin{proof}
-	Reduction from 3-SAT.
+	We present a polynomial-time reduction from the NP-hard problem 3-SAT~\cite{Karp1972Reducibility}.
+Here, we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
+We construct an instance of \textsc{Exact Realization $(\infty)$} as follows.
 
-	Idea for gadgets, see ``Whiteboards/2022-11-03-Hendrik-Nina-Paul.pdf'', details TBD.
+ We start by describing the vertex set of the underlying graph $G$.
+\begin{itemize}
+\item For each variable $x$ in $\phi$, we create three variable vertices $x, x^T, x^F$.
+\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
+\item We add one additional super vertex $v$.
+\end{itemize}
+Next, we describe the edge set of $G$.
+\begin{itemize}
+\item For each variable $x$ in $\phi$ we add the following five edges:
+
+$\{x, x^T\}, \{x, x^F\}, \{x^T, x^F\}, \{x^T, v\}, \{x^F,v\}$.
+\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges
+
+$\{x^T,y^T\},\{x^T,y^F\}, \{x^F,y^T\},\{x^F,y^F\}$.
+\item For each clause $c$ in $\phi$ we add one edge for each literal.
+Let $x$ appear in $c$.
+If $X$ appears non-negated in $c$ we add edge $\{c,x^T\}$.
+If $x$ appears negated in $c$ we add edge $\{c, x^F\}$.
+\end{itemize}
+This finishes the construction of $G$.
+
+Now we specify the distances between all vertex pairs. Naturally, the distance between all pairs of adjacent vertices is one.
+\begin{itemize}
+    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
+
+    %$d(x_1,x_2)=2$. 
+    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following distances:
+
+    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
+    \item For each variable $x$ in $\phi$ we specify the following distances to the super vertex $v$:
+
+    $d(x,v)=2$. %, $d(x_2,v)=3$.
+
+    \item For each clause $c$ in $\phi$ we specify the following distances to the super vertex $v$:
+
+    $d(c,v)=2$
+    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distances:
+
+    $d(c,x)=2$.
+
+    If $x$ appears non-negated in $c$ we specify the following distances:
+
+    $d(c,x_F)=2$.
+
+    If $x$ appears negated in $c$ we specify the following distances:
+
+    $d(c,x_T)=2$.
+    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
+
+    $d(c,x^T)=d(c,x^F)=2$.
+\end{itemize}
+All distances between non-adjacent vertex pairs that are not defined above are set to $\infty$.
+
+This finishes the construction of the \textsc{Exact Realization $(\infty)$} which can clearly be done in polynomial time.
+In the remainder we show that it is a yes-instance if and only if $\phi$ is satisfiable.
+
+$(\Rightarrow)$: Assume the constructed \textsc{Exact Realization $(\infty)$} is a yes-instance.
+Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path between from $u$ to $w$ has exactly duration $d(u,w)$.
+In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
+
+We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$, then we set $x$ to \texttt{true}, otherwise we set $x$ to \texttt{false}.
+
+To show that this yields a satisfying assignment, we need to show some following properties of $\lambda$.
+First, observe that adding some integer $t$ to all time labels does not change the duration of any temporal path.
+Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$, then there is a shortest path from $u$ to $w$ in $G$ such that $\lambda$ puts consecutive time labels on the edges of that shortest path.
+
+Assume that for some variable $x$ we have that $\lambda(\{x,x^T\})=t$ and $\lambda(\{x,x^F\})=t'$.
+We can deduce that $\lambda(\{x^T,v\})=t+1$ or $\lambda(\{x^F,v\})=t'+1$ (or both), otherwise we have that $d(x,v)>2$.
+In particular, this means that if $\lambda(\{x,x^F\})=\lambda(\{x^F,v\})$, then we set $x$ to \texttt{false}, since in this case $\lambda(\{x,x^T\})\neq\lambda(\{x^T,v\})$.
+
+%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
+Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
+
+Now assume for contradiction that the described assignment is not satisfying.
+Then there exists a clause $c$ that is not satisfied.
+Recall that we require $d(c,v)=2$.
+Hence, we must have a temporal path consisting of two edges from $c$ to $v$ such that the two edges have consecutive labels.
+By construction of $G$ there are three candidates for such a path, one for each literal of $c$.
+Assume w.l.o.g.\ that $x$ appears in $c$ non-negated (the case of negated is symmetrical) and the temporal path realizing $d(c,v)=2$ goes through vertex $x^T$.
+Then we have that $\lambda(\{c,x^T\})=\lambda(\{x^T,v\})-1$.
+Furthermore, since $d(c,x)=2$ we also have that $\lambda(\{c,x^T\})=\lambda(\{x,x^T\})-1$.
+It follows that $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$.
+However, this implies that $x$ is set to \texttt{true} in the satisfying assignment and the clause $c$ is satisfied, a contradiction.
+
+%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
+Then we have that $\{c,x^T\}\in E(G)$.
+Assume that $\lambda(\{c,x^T\})=t$.
+Recall that we have specified $d(c,x_2)=2$.
+Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
+
+$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
+
+We construct a labelling $\lambda$ as follows.
+\begin{itemize}
+    \item All edges incident with a clause vertex $c$ obtain label one.
+    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
+    \item If variable $x$ is set to \texttt{true}, we set $\lambda(\{x^F,v\})=3$.
+    \item If variable $x$ is set to \texttt{false}, we set $\lambda(\{x^T,v\})=3$.
+    \item We set the labels of all other edges to two.
+\end{itemize}
+
+Next, we verify that all distances are realized.
+\begin{itemize}
+    \item For each variable $x$ in $\phi$ we have $d(x,v)=2$:
+
+    If $x$ is set to \texttt{true}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(\{x,x^F\})=2$ and $\lambda(\{x^F,v\})=3$.
+If $x$ is set to \texttt{false}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(\{x,x^T\})=2$ and $\lambda(\{x^T,v\})=3$.
+
+    \item For each clause $c$ in $\phi$ we have that $d(c,v)=2$:
+
+    Since we have a satisfying assignment there is a variable $x$ appearing in $c$ that is set to a truth-value that satisfies $c$.
+If $x$ appears non-negated in $c$ (and hence is set to \texttt{true}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x^T,v\})=2$.
+If $x$ appears negated in $c$ (and hence is set to \texttt{false}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x^F,v\})=2$.
+    \item Let $x$ be a variable that appears in clause $c$.
+    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_F)=2$:
+
+    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x,x^T\})=\lambda(\{x^T,x^F\})=2$.
+
+    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_T)=2$:
+
+    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x,x^F\})=\lambda(\{x^T,x^F\})=2$.
+    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we have $d(c,x^T)=d(c,x^F)=2$:
+
+    Let $y$ be a variable that appears non-negated in $c$ (the case where $y$ appears negated is symmetrical).
+Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(\{c,y^T\})=1$ and $\lambda(\{y^T,x^T\})=\lambda(\{y^T,x^F\})=2$.
+\end{itemize}
+Lastly, we show that all non-adjacent vertex pairs $u,w$ with $d(u,w)=\infty$ are not temporally connected in $(G,\lambda)$.
+\todo[inline]{HM: this part is unfinished}
+\begin{itemize}
+\item For all pairs of clause vertices $c,c'$ we have $d(c,c')=\infty$:
+
+Since all edges incident with clause vertices have label one and clause vertices are pairwise non-adjacent, there cannot be a temporal path from one clause vertex to another.
+\item For all variable vertices $x$ and clause vertices $c$ we have $d(x,c)=\infty$:
+
+Since all edges incident with variable vertices have label two and all edges incident with clause vertices have label one, there cannot be a temporal path from a variable vertex to a clause vertex.
+\item For all pairs of variable vertices $x,y$ we have $d(x,y)=\infty$:
+
+Since all edges incident with variable vertices have label two and variable vertices are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
+\item $d(x,y^T)=d(x,y^F)=d(y^T,x)=d(y^F,x)=\infty$
+\item $d(v,x)=d(v,c)=\infty$
+\end{itemize}
 \end{proof}
 
-%\bibliography{bibliography}	
+\bibliography{bibliography}	
 \end{document}

### 2022-11-14 RealizingTemporalGraphs.tex
Monday 14th November

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
+%% One label per edge, period Delta, exact realization
+\newcommand{\deltaExactLong}{\textsc{Simple $\Delta$-periodic Exact Temporal Graph Realization}}
+\newcommand{\deltaExact}{\textsc{Simple $\Delta$-TGR}}
+
+%% k labels per edge, period Delta, exact realization
+\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
+\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
+
+%% One label per edge, period Delta, upper-bounded realization
+\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
+%\newcommand{\deltaUpperBound}{}
+
+%% k labels per edge, period Delta, lower-bound realization
+\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
+
 \title{Realizing Temporal Graphs}
@@
 
-\begin{definition}
-	Let $P = ((e_1, \lambda_1), (e_2,\lambda_2), \dots , (e_k, \lambda_k))$ be a temporal path from $u$ to $v$, then the duration of $P$, denoted as $d(P)$ is $\lambda(e_k) - \lambda(e_1) + 1$.
+Let $G=(V,E)$ and $k,\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ be an edge-labeling function that assigns to every edge of $G$ exactly $k$ different labels from $\{1,\ldots,\Delta\}$.
+Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,\lambda_{\Delta})$, where for every edge $e\in E$ we have $\lambda_{\Delta}(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$.
+In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. If $k=1$, we call $\lambda$ a \emph{simple $\Delta$-periodic labeling} of $G$.
+
+\begin{definition}[temporal path]
+Let $(G,\lambda)$ be a temporal graph.
+A \emph{temporal path} $P$ from $u=u_0$ to $v=u_k$ in $(G,\lambda)$ is a sequence $(u_0 u_1,t_1),(u_1 u_2,t_2),\ldots,(u_{k-1} u_k,t_k)$, where $(u_0,u_1,\ldots,u_k)$ is a path in the underlying static graph $G$, $t_i\in \lambda(u_{i-1}u_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$.
+The \emph{duration} of this temporal path $P$ from $u$ to $v$ is $d(P)=t_k - t_1 + 1$.
+A \emph{fastest} temporal path $P$ from $u$ to $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest possible duration.
+The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
 \end{definition}
 
-We denote with $d(u,v)$ the duration of the \emph{fastest} temporal path from $u$ to $v$.
+\problemdef{\deltaExactLong\ (\deltaExact)}
+{An $n \times n$ matrix $D$.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a simple $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
 
-\problemdef{\textsc{Exact Realization $(\Delta)$}}
-{A matrix $D$ of exact durations of fastest strict temporal paths among each pair of vertices, and a period $\Delta$.}
-{Does there exist a labeling $\lambda$ of the underlying graph $G$ of $D$, such that every edge receives exactly one label and $d(v_i,v_j) = D_{i,j}$, for any pair of vertices $v_i, v_j \in V(G)$.}
+\problemdef{\kDeltaExactLong\ (\kDeltaExact)}
+{An $n \times n$ matrix $D$ of positive integers.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
 
-\problemdef{\textsc{Upper-bounded Realization $(\Delta)$}}
-{A matrix $D$ of exact durations of fastest strict temporal paths among each pair of vertices, and a period $\Delta$.}
-{Does there exist a labeling $\lambda$ of the underlying graph $G$ of $D$, such that every edge receives exactly one label and $d(v_i,v_j) \leq D_{i,j}$, for any pair of vertices $v_i, v_j \in V(G)$.}
+\problemdef{\kDeltaUpperBoundLong}
+{An $n \times n$ matrix $D$ of positive integers.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{i,j}$.}
+
+\problemdef{\kDeltaLowerBoundLong}
+{An $n \times n$ matrix $D$ of positive integers.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at least} $D_{i,j}$.}
+
+Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$ that we are looking for in the above problems. 
+For simplicity of the presentation (and with a slight abuse of notation), we may refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
+$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we might put as indices of the matrix $D$ the corresponding vertices of $G$ instead of their numbering.
+
+\begin{definition}[$D$-increasing temporal path]
+Let $(G,\lambda,\Delta)$ be a $\Delta$-periodic temporal graph on $n$ vertices, and let $D$ be an $n\times n $ matrix of positive integers. 
+Let $P$ be a temporal path from $u_0$ to $u_k$ on the vertices $u_0,u_1,\ldots,u_k$, and let $P^\textsc{ST}=(u_0,u_1,\ldots,u_k)$ be the underlying \emph{static} path in $G$.
+Then $P$ is \emph{$D$-increasing} in $G$ if $0=D_{u_0,u_0}<D_{u_0,u_1}<D_{u_0,u_2}<\ldots,D_{u_0,u_k}$.
+\end{definition}
+
+\begin{observation}
+Let $D$ be \textsc{YES}-instance of \textsc{$(k,\Delta)$-TGR}, and let 
+$(G,\lambda,\Delta)$ be a certificate for $D$, where $\lambda:E\rightarrow \{1,2,\ldots,\Delta\}^k$ a $\Delta$-periodic labeling of $G$.
+Then, for every pair $u,v$ of vertices of $G$, every fastest temporal path from $u$ to $v$ is $D$-increasing.
+\end{observation}
 
@@
 \section{
-\texorpdfstring{\textsc{Exact Realization $(\Delta)$} is in $P$}
-{Exact Realization (Delta) is in P}
-}
+\texorpdfstring{\deltaExact\ is polynomial-time solvable}
+{\textsc{Simple Delta-TGR} is polynomial-time solvable}
+}\
+
+$G$ can be deduced easily from $D$.
 
@@
 	To do so we observe some properties of the problem.
+
+\subsection*{Inequalities}
 
@@
 	\begin{equation}\label{eq:ineq-uv-onePath}
-	    \lambda_2 \geq_\Delta \lambda_1 + d(v,u)-d(u,v_2) \pmod \Delta
+	    \lambda_2 \geq_\Delta \lambda_1 + d(v,u)-d(v,v_2) \pmod \Delta
 	\end{equation}
+ \todo[inline]{GM: WHY??? THIS IS WRONG}
 	We repeat the above procedure for every path $P \in \mathcal{P}$ and collect all the inequalities to a set $S_u^v$.
@@
 
-	\begin{claim}
+	\begin{lemma}
 	\label{claim:exact-setsOfInequalities}
-	For the labeling $\lambda$ of $G$, that fulfills the fastest temporal paths conditions from $D$, the following two conditions have to hold. 
+    Let $D$ be \textsc{YES}-instance of \textsc{Simple $\Delta$-TGR}, and let 
+$(G,\lambda,\Delta)$ be a certificate for $D$, where $\lambda:E\rightarrow \{1,2,\ldots,\Delta\}$ a simple periodic labeling of $G$. Then, for every pair $u,v$ of non-adjacent vertices:
 	\begin{enumerate}
-	    \item $\lambda$ has to satisfy all the inequalities of sets $S_u^v$.
-	    \item At least one inequality in each set $S_u^v$ has to be an equality.
+	    \item \label{itemize:Claim-exact-AtLeastOneEquality-1} $\lambda$ satisfies all the inequalities of the set $S_u^v$, and 
+	    \item \label{itemize:Claim-exact-AtLeastOneEquality} at least one of the inequalities of $S_u^v$ is an equality.
 	\end{enumerate}
-	\end{claim}
-    Intuitively, we know that we reach the vertex $u$ starting from $v$, only through paths in $\mathcal{P}_u^v$. 
+	\end{lemma}
+
+    \begin{proof}
+    By the definition of $\mathcal{P}_u^v$, every fastest temporal path from $v$ to $u$ must reach $u$ using one of the $P_3$ paths of $\mathcal{P}_u^v$.
+    Let $P$ be an arbitrary temporal path from $v$ to $u$. 
     An arbitrary path $P \in \mathcal{P}_u^v$ is either a part of the fastest path from $v$ to $u$, which means that the path arrives to $u$ at the time equal to $d(v,u)$,
@@
     This is how the inequalities from $S_u^v$ are constructed. 
+    \todo{GM: WHY? WRONG} 
     Since the fastest path from $v$ to $u$ has to be of duration $d(v,u)$, at least one of the inequalities from $S_u^v$ has to be an equality.    
+    \end{proof}
 
+    \paragraph{Manipulation of inequalities modulo $\Delta$.}
+    Suppose we have a path $P$ on three vertices, of form $(v_1, v_2, u)$,
+    and suppose $d(v,v_1) < d(v,v_2) < d(v,u)$ for some $v \in V \setminus P$, with $d(v,v_2) = a, d(v,u)=b$. 
+    Let us denote with $\lambda_1 = \lambda(v_1 v_2), \lambda_2 = \lambda(v_2 u)$ and $k = b-a$, where $1 \leq k \leq \Delta$ as all edge labels have values from $1$ to $\Delta$.
+    Then by \cref{eq:ineq-uv-onePath} we know that 
+    \begin{equation}\label{eq:inequalities-properties-example}
+        \lambda_2 \geq_\Delta \lambda_1 + k \pmod \Delta.
+    \end{equation}
+    Note that if $\lambda_2 = \lambda_1$, the duration of temporal path $(P, \lambda) = ((v_1v_2, \lambda_1), (v_2u, \lambda_2))$ is exactly $\Delta+1$,
+    therefore $\lambda_1 = \lambda_2$ satisfies \cref{eq:inequalities-properties-example}.
+    We can rewrite \cref{eq:inequalities-properties-example} as
+    \begin{equation*}
+        \lambda_2 \in 
+        \{
+        \lambda_1 + k, \lambda_1 + (k + 1), \dots , \lambda_1 + (\Delta - 1), \lambda_1 + \Delta 
+        \} \pmod \Delta.
+    \end{equation*}
+    Suppose now we have the following two inequalities
+    \begin{align*}
+        & \lambda_2 \geq_\Delta \lambda_1 + k \pmod \Delta, \\
+        & \lambda_2 \geq_\Delta \lambda_1 + k' \pmod \Delta,
+    \end{align*}
+    for some $k' > k$, then the set of all possible solutions satisfying both equations is the following
+        \begin{equation*}
+        \lambda_2 \in 
+        \{
+        \lambda_1 + k', \lambda_1 + (k' + 1), \dots , \lambda_1 + (\Delta - 1), \lambda_1 + \Delta 
+        \} \pmod \Delta.
+    \end{equation*}
+
+    Observe now that without the condition~\ref{itemize:Claim-exact-AtLeastOneEquality} of \cref{claim:exact-setsOfInequalities}, all inequalities of condition~\ref{itemize:Claim-exact-AtLeastOneEquality-1} can be satisfied by setting the label of every edge of the graph to be the same.
+
+    \subsection*{Cycles}
+    \begin{definition}[Travel delays]
     Let $e_1=uv$ and $e_2=vz$ be two incident edges with $e_1 \cap e_2 = v$.
-    We denote with $\tau_v^{uz}$ the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo $\Delta$.
+    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
     More specifically:
@@
     Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal paths waits at vertex $v$ when first taking the edge $e_1=uv$ and then the edge $e_2 = vz$.
+    \end{definition}
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking the edge $e_1=uv$ and then the edge $e_2 = vz$.
 
     \begin{observation}
-    For any two consecutive edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, the value $\tau_v^{zu} = \Delta - \tau_v^{uz}$.
+    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
     \end{observation}
@@
         By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz}$.
+        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{proof}
+
+    \begin{observation} \label{obs:exact-VertexSum}
+    Let $v$ be a vertex of $G$, and let $N(v)=\{u_1, u_2, \ldots, u_k\}$, Then 
+    \begin{equation*}
+        \sum_{i = 1}^k \tau_{v}^{u_{i}v_{i+1}} \equiv  0 \pmod \Delta,
+    \end{equation*}
+    where the indices of vertices $u_i$ are taken modulo $k$.
+    \end{observation}
+
+    \begin{proof}
+        tbd
     \end{proof}
@@
         \begin{align*}
-            &\sum_{i = 1}^k \tau_{v_i}^{v_{i-1}v_{i+1}}  \equiv  \sum_{i = 1}^k  (\lambda(v_i v_{i+1} - \lambda (v_{i-1} v_i) \pmod \Delta \equiv \\
+            &\sum_{i = 1}^k \tau_{v_i}^{v_{i-1}v_{i+1}}  \equiv  
+            \sum_{i = 1}^k  ( \lambda(v_i v_{i+1}) - \lambda (v_{i-1} v_i) ) \pmod \Delta \equiv \\
             &\lambda(v_1 v_2) - \lambda(v_{k}v_1) + \lambda(v_2 v_3) - \lambda(v_2 v_1) + \dots + \lambda(v_k v_1) - \lambda(v_{k-1}v_k) \pmod \Delta.
         \end{align*}
+    \end{proof}
 
+    \begin{claim}
+    Labelling $\lambda$ is a solution for the \textsc{Exact Realization $(\Delta)$} if and only if
+    for every cycle $C$ of $(G,\lambda)$ it holds that the sum of the travel delays along $C$ is $0$ modulo $\Delta$.
+    \end{claim}
+
+    \begin{proof}
+        TBD
     \end{proof}
@@
 \end{proof}
+
+\subsection{
+\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}
+is polynomial-time solvable on trees, paths and cycles}
+
+Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
+By the definition, each vertex is on distance $0$ from itself. This corresponds with all diagonal entries of $D$ being $0$.
+Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v{i-1}$ and $v_{i+1}$,
+therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
+This results in the upper and lower diagonal of $D$ having all $1$'s, with $D_{1,n} = D_{n,1} = 1$.
+The matrix $D$ is of the following form
+\begin{equation*}
+  D = 
+  \begin{bmatrix}
+    0 & 1 &  &  &  & 1\\
+    1 & 0 & 1 &  &  & \\
+    & 1 & 0 & 1 & & \\
+    & & \ddots & \ddots & \ddots &   \\
+    &   & &1 &  0 & 1\\ 
+    1 &  &  &  &1 &  0 
+  \end{bmatrix},
+\end{equation*}
+where the empty entries consists of positive integers different than $1$.
+
+Let $v_i$ be an arbitrary vertex in $C_n$.
+Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
+and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
+Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
+and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
+Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
+
+\begin{claim} \label{claim:poly-delta-cycle-monotonicity}
+    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
+    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
+    using the same, positive side  (resp.~negative), side of the cycle,
+    where the indices are taken modulo $n$.
+\end{claim}
+\begin{proof}
+    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
+    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
+    for which $D_{i,k} \neq d^+(i,k)$.
+    Then $d^-(i,k)$ passes through the vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
+    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
+    So 
+    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
+        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
+    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to the vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
+    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
+    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
+    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
+This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
+    In the above construction vertex $v_k$ is visited twice.
+By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
+Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
+    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
+\end{proof}
+
+Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the duration of fastest temporal paths from $v_i$ to any other vertex $v_j \in C_n$.
+Using \cref{claim:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
+and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
+Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
+Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
+$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
+Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
+Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
+Let us denote these two values as $m_i^1$ and $m_i^2$.
+The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has a $1$ at entries $i-1, i+1$,
+the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
+and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
+where indices are taken modulo $n$.
+
+\begin{theorem}
+    \deltaExact\ can be solved in polynomial time on cycles.
+\end{theorem}
 
@@
 Assume that for some variable $x$ we have that $\lambda(\{x,x^T\})=t$ and $\lambda(\{x,x^F\})=t'$. 
-We can deduce that $\lambda(\{x^T,v\})=t+1$ or $\lambda(\{x^F,v\})=t'+1$ (or both), otherwise we have that $d(x,v)>2$.
+We can deduce that $\lambda(\{x^T,v\})=t+1$ or $\lambda(\{x^F,v\})=t'+1$, otherwise we have that $d(x,v)>2$.
+Note that, if both $\lambda(\{x^T,v\})=t+1$ and $\lambda(\{x^F,v\})=t'+1$, then
+
 In particular, this means that if $\lambda(\{x,x^F\})=\lambda(\{x^F,v\})$, then we set $x$ to \texttt{false}, since in this case $\lambda(\{x,x^T\})\neq\lambda(\{x^T,v\})$.
@@
 Lastly, we show that all non-adjacent vertex pairs $u,w$ with $d(u,w)=\infty$ are not temporally connected in $(G,\lambda)$.
-\todo[inline]{HM: this part is unfinished}
 \begin{itemize}
@@
 
-Since all edges incident with variable vertices have label two and all edges incident with clause vertices have label one, there cannot be a temporal path from a variable vertex to a clause vertex.
+Since all edges incident with variable vertices $x$ have label two and all edges incident with clause vertices $c$ have label one, there cannot be a temporal path from a variable vertex $x$ to a clause vertex $c$.
 \item For all pairs of variable vertices $x,y$ we have $d(x,y)=\infty$:
 
-Since all edges incident with variable vertices have label two and variable vertices are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
-\item $d(x,y^T)=d(x,y^F)=d(y^T,x)=d(y^F,x)=\infty$
-\item $d(v,x)=d(v,c)=\infty$
+Since all edges incident with variable vertices $x$ have label two and variable vertices $x$ are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
+\item For all pairs of variable vertices $x,y$ we have $d(y^T,x)=d(y^F,x)=\infty$:
+
+Since all edges incident with variable vertices $x$ have label two and all edges incident with variable vertices $y^T, y^F$ have labels two or three and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from a variable vertex $y^T$ or $y^F$ to variable vertex $x$.
+\item For all pairs of variable vertices $x,y$ we have $d(x,y^T)=d(x,y^F)=\infty$:
+
+Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
+Furthermore, $v$ has distance two from $x$ in the unlabelled graph $G$.
+Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
+Hence, there is no temporal path from $x$ to $y^T, y^F$ using an edge with label three.
+Since all edges incident with $x$ have label two and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from variable vertex $x$ to variable vertex $y^T$ or $y^F$.
+\item For all variable vertices $x$ and clause vertices $c$ we have $d(v,x)=d(v,c)=\infty$:
+
+All edges incident with $v$ have labels two or three.
+All edges incident with $x$ have label two and all edges incident with $c$ have label one.
+We immediately have that there is no temporal path from $v$ to $c$.
+Furthermore, since $x$ and $v$ are non-adjacent, we also have that there is no temporal path from $v$ to $x$.
 \end{itemize}

### 2022-11-29 RealizingTemporalGraphs.tex
Tuesday 29th November - Overleaf changes

@@
 
+\section{Ideas}
+\begin{itemize}
+    \item Symmetric distance matrix $D$: polytime?
+    \item Use $|D|_\infty$ (maximum value in $D$) + max degree $\Delta$ as parameter $\rightarrow$ should give FPT
+    \item FPT with feedback edge number
+    \item use as parameter $\max_{i,j} |D_{i,j}-D_{j,i}|$
+    \item approximation (additive or multiplicative), maybe with graph as input
+\end{itemize}
+
 \section{Preliminaries}
@@
 \problemdef{\kDeltaUpperBoundLong}
-{An $n \times n$ matrix $D$ of positive integers.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
 for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{i,j}$.}
@@
 \problemdef{\kDeltaLowerBoundLong}
-{An $n \times n$ matrix $D$ of positive integers.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
+{Does there exist a graph $G=(V,E)$ on the vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
 for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at least} $D_{i,j}$.}
+\todo[inline]{NOT TEMPORALLY INTERESTING: the difficulty is to find a static graph with equal labels}
+
+\todo[inline]{The matrix $D$ is m x m, and capturing the distances from an edge e to an edge f (zoom 14 Nov 22, GH).}
+\todo[inline]{Check if the reduction works for the UPPER BOUNDED version (seems to work)}
+\todo[inline]{how to extend the poly algorithms of cycles? Easy candidate: FES, FVS, series-parallel graphs, or tw=2 graphs}
+\todo[inline]{FVS, $c$-factor approximation, hardness of approximation for $c<1.5$}
 
@@
 \section{
-\texorpdfstring{\deltaExact\ is polynomial-time solvable}
+\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}}
+
+In this section we study the hardness of \deltaExact. We first start with defining certain notions, that will be of use when solving the problem.
+
+\todo[inline]{NK:Following definition and observation are copied from the previous section (need to delete from one part).}
+
+    \begin{definition}[Travel delays]
+    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact.
+    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+    More specifically:
+    \begin{equation}\label{eq:def-VertexWaitingTime}
+       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+    \end{equation}
+    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    \end{definition}
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking the edge $e_1=uv$ and then the edge $e_2 = vz$.
+
+    \begin{observation}\label{obs:travel-delays-both-directions}
+    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact.
+    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{observation}
+
+    \begin{proof}
+        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
+        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{proof}
+
+\begin{claim} \label{claim:unique-fastest-path-allDelays}
+    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact,
+    and let $P=P_{1,k}$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+    Let us denote with $P_{1,i}$ the sub-path of temporal path $P_{1,k}$, that starts at $v_1$ and finishes at $v_i$.
+    Suppose that $P_{1,i}$ is also the fastest temporal path from $u=v_1$ to any other vertex $v_i$ in $P$.
+    Then we can determine travel delays on $P$ using the following equation
+    \begin{equation}\label{eq:trav-delays-paths}
+        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
+    \end{equation}
+    for all $i \in \{2,3, \dots, k-1\}$.
+\end{claim}
+
+\begin{proof}
+    Let $P$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
+    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
+    \begin{align*}
+        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
+        & = 
+        \left(\lambda(v_{i}v_{i+1} - \lambda(v_1v_2) + 1\right) -  
+        \left(\lambda(v_{i-1}v_{i} - \lambda(v_1v_2) + 1\right) \\
+        & = \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}),
+        \end{align*}
+    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
+\end{proof}
+
+\subsection{
+\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}
+is polynomial-time solvable on trees and paths}
+
+Let $D$ be a matrix from \deltaExact, when the underlying graph $G$ of $D$ is a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
+Consequently, it follows that the temporal paths $P_{i,j}$ from $v_i$ to $v_j$ and $P_{j,i}$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
+and therefore are the fastest.
+Then $D$ is of the following form:
+\begin{equation*}
+    D_{i,j} =
+    \begin{cases}
+    0 & \text{if $i = j$}, \\
+    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
+    d(P_{i,j}) & \text{else}
+    \end{cases},
+\end{equation*}
+where $d(P_{i,j})$ is the duration of the (unique) temporal path $P_{i,j}$ from $v_i$ to $v_j$.
+
+\begin{observation}\label{obs:travel-delays-in-trees}
+    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
+    Since there is a unique temporal path $P_{i,j}$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j}) = D_{i,j}$. 
+    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $P_{i,j}$.
+    Now using \cref{claim:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
+\end{observation}
+
+\begin{theorem}
+    \deltaExact\ can be solved in polynomial time on trees.
+\end{theorem}
+
+\begin{proof}
+    Let $D$ be an input matrix for problem \deltaExact of dimension $n \times n$.
+    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
+    This can be done in polynomial time as we need to read through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
+At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
+    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
+    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
+
+    From now on we can assume that we know that the underlying graph $G$ is a tree and we know how it looks like.
+    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
+
+    For a vertex $v_i$ we check which vertex $v_j \in G$ is furthest away from it, \ie for which vertex $v_j$ the entry $D_{i,j}$ is maximum.
+    We now take the unique (fastest) temporal path $P_{i,j}$ and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+    We save those values in a matrix $T$ and mark vertices of the path  $P_{i,j}$ as visited.
+    Matrix $T$ stores at the position $(i,i-1,i+1)$ the value corresponding to the travel delay at vertex $v_i$ when traveling from $v_{i-1}$ to $v_{i}$, \ie $\tau_{v_i}^{v_{i-1}, v_i}$, whenever $v_{i-1}v_i, v_iv_{i+1} \in E(G)$.
+All other values of $T$ are set to \textsc{Null}.
+    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
+    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
+    When we have exhausted the $i$-th row of $D$, corresponding to the vertex $v_i$,
+    we continue and repeat the procedure for all other vertices.
+    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
+    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices $v_i$ in the tree, of degree at least $2$.
+    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
+    \begin{claim}\label{claim:matrixT-travelDelays-tree}
+        Matrix $T$ consists of travel delays of all vertices of degree at least $2$ in $G$.
+    \end{claim}
+    \begin{proof}[Proof of \cref{claim:matrixT-travelDelays-tree}]
+        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
+        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
+        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
+        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
+        When our algorithm was inspecting the row of $D$ corresponding to the vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
+        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
+        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
+        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
+    \end{proof}
+
+    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
+    We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
+    Knowing the label of the edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+    Note, w.l.o.g we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
+Therefore all together the whole algorithm is performed in polynomial time.
+\end{proof}
+
+\subsection{
+\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}
+is polynomial-time solvable on cycles}
+
+Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
+By the definition, each vertex is on distance $0$ from itself. This corresponds with all diagonal entries of $D$ being $0$.
+Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
+therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
+This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
+The matrix $D$ is of the following form
+\begin{equation*}
+  D = 
+  \begin{bmatrix}
+    0 & 1 &  &  &  & 1\\
+    1 & 0 & 1 &  &  & \\
+    & 1 & 0 & 1 & & \\
+    & & \ddots & \ddots & \ddots &   \\
+    &   & &1 &  0 & 1\\ 
+    1 &  &  &  &1 &  0 
+  \end{bmatrix},
+\end{equation*}
+where the empty entries consists of positive integers different than $1$.
+
+Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
+If it is not of correct for, our algorithm stops and returns the negative answer.
+From now on, we will assume, that the input matrix is of correct form.
+
+Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
+Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
+and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
+Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
+and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
+Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
+
+\begin{claim} \label{claim:poly-delta-cycle-monotonicity}
+    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
+    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
+    using the same, positive (resp.~negative) side of the cycle,
+    where the indices are taken modulo $n$.
+\end{claim}
+\begin{proof}
+    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
+    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
+    for which $D_{i,k} \neq d^+(i,k)$.
+    Then $d^-(i,k)$ passes through the vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
+    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
+    So 
+    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
+        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
+    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to the vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
+    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
+    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
+    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
+This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
+    In the above construction vertex $v_k$ is visited twice.
+By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
+Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
+    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
+\end{proof}
+
+Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
+Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the fastest temporal path from $v_i$ to $v_j$, using the positive (resp.~negative) side of the cycle, 
+\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
+Then by \cref{claim:poly-delta-cycle-monotonicity} and \cref{claim:unique-fastest-path-allDelays},
+we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
+
+Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
+Using \cref{claim:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
+and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
+Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
+Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
+$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
+Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
+Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
+Let us denote these two values as $m_i^1$ and $m_i^2$.
+The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
+the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
+and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
+where indices are taken modulo $n$.
+
+Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
+To determine these two sets we do the following.
+We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
+We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
+for which it has to hold that
+$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
+$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
+Note, it can also happen that $m_i^1 = m_i^2$. 
+Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
+the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
+By \cref{claim:poly-delta-cycle-monotonicity} and \cref{claim:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
+which we store in a list $T$ of length $n$,
+where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
+Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
+We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
+Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
+
+To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
+
+\begin{claim}
+List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
+\end{claim}
+\begin{proof}
+    Throughout the proof we
+    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
+    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
+    where indices are taken modulo $n$.
+
+    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
+    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
+    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
+    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum distance from every vertex $v_j \in C_n \setminus \{v_i\}$.
+    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
+    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
+    Since $v_i$ has to be on the maximum duration from both of them 
+    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
+    we know that 
+    \begin{align}\label{eq:cycle-travel-delays-all}
+        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
+        & d^-(i-1,i+1) < d^+(i-1,i+1).
+    \end{align}
+    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
+
+    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1} = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
+    W.l.o.g. we can suppose that $a \geq a'$.
+    Therefore, using the definition for the duration of temporal paths, we get that
+    $d^+(i+1,i-1) = (k \delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
+    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
+    $(k \delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
+    $b - b' < a - a'$.
+    Now again using the definition of the duration, we get
+    $d^+(i-1,i+1)= (k\delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \delta + a - a + 1$.
+    Again by the definition, $d^-(i-1,i+1) = (k' \delta + b') -b + 1$, for some non-negative integer $k'$.
+    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
+    $(k' \delta + b') -b + 1 < \delta + a - a + 1$.
+    Which is equivalent to  $(k' \delta + b') -b < \delta + a' - a $.
+This can hold only when $k' = 1$, in that case we get $ \delta + b' -b < \delta + a' - a $ which is equivalent to $b' -b < a' - a$.
+    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
+
+    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
+\end{proof}
+
+All of the above observations imply the following result.
+\begin{theorem}
+    \deltaExact\ can be solved in polynomial time on cycles.
+\end{theorem}
+
+\begin{proof}
+As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
+Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
+We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
+Knowing the label of the edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+Note, w.l.o.g we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+\end{proof}
+
+\section{Hardness of Exact Realization}
+
+\todo[inline]{HM: For the following hardness I assume that we only consider strict temporal paths. (NK: Yes you are right, all paths are strict, sorry forgot to specify). \\
+Furthermore, I can currently only make it work if we do not have periods ($\Delta=\infty$). I am not sure the idea also works if we have periods.}
+
+\begin{theorem}
+	\textsc{Exact Realization $(\infty)$} is \NP-hard.
+\end{theorem}
+
+\begin{proof}
+	We present a polynomial-time reduction from the NP-hard problem 3-SAT~\cite{Karp1972Reducibility}.
+Here, we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
+We construct an instance of \textsc{Exact Realization $(\infty)$} as follows.
+
+ We start by describing the vertex set of the underlying graph $G$.
+\begin{itemize}
+\item For each variable $x$ in $\phi$, we create three variable vertices $x, x^T, x^F$.
+\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
+\item We add one additional super vertex $v$.
+\end{itemize}
+Next, we describe the edge set of $G$.
+\begin{itemize}
+\item For each variable $x$ in $\phi$ we add the following five edges:
+
+$\{x, x^T\}, \{x, x^F\}, \{x^T, x^F\}, \{x^T, v\}, \{x^F,v\}$.
+\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges
+
+$\{x^T,y^T\},\{x^T,y^F\}, \{x^F,y^T\},\{x^F,y^F\}$.
+\item For each clause $c$ in $\phi$ we add one edge for each literal.
+Let $x$ appear in $c$.
+If $X$ appears non-negated in $c$ we add edge $\{c,x^T\}$.
+If $x$ appears negated in $c$ we add edge $\{c, x^F\}$.
+\end{itemize}
+This finishes the construction of $G$.
+
+Now we specify the distances between all vertex pairs. Naturally, the distance between all pairs of adjacent vertices is one.
+\begin{itemize}
+    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
+
+    %$d(x_1,x_2)=2$. 
+    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following distances:
+
+    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
+    \item For each variable $x$ in $\phi$ we specify the following distances to the super vertex $v$:
+
+    $d(x,v)=2$. %, $d(x_2,v)=3$.
+
+    \item For each clause $c$ in $\phi$ we specify the following distances to the super vertex $v$:
+
+    $d(c,v)=2$
+    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distances:
+
+    $d(c,x)=2$.
+
+    If $x$ appears non-negated in $c$ we specify the following distances:
+
+    $d(c,x_F)=2$.
+
+    If $x$ appears negated in $c$ we specify the following distances:
+
+    $d(c,x_T)=2$.
+    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
+
+    $d(c,x^T)=d(c,x^F)=2$.
+\end{itemize}
+All distances between non-adjacent vertex pairs that are not defined above are set to $\infty$.
+
+This finishes the construction of the \textsc{Exact Realization $(\infty)$} which can clearly be done in polynomial time.
+In the remainder we show that it is a yes-instance if and only if $\phi$ is satisfiable.
+
+$(\Rightarrow)$: Assume the constructed \textsc{Exact Realization $(\infty)$} is a yes-instance.
+Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path between from $u$ to $w$ has exactly duration $d(u,w)$.
+In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
+
+We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$, then we set $x$ to \texttt{true}, otherwise we set $x$ to \texttt{false}.
+
+To show that this yields a satisfying assignment, we need to show some following properties of $\lambda$.
+First, observe that adding some integer $t$ to all time labels does not change the duration of any temporal path.
+Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$, then there is a shortest path from $u$ to $w$ in $G$ such that $\lambda$ puts consecutive time labels on the edges of that shortest path.
+
+Let $\lambda(\{x,x^T\})=t$ and $\lambda(\{x,x^F\})=t'$, for an arbitrary variable $x$. 
+If both $\lambda(\{x^T,v\})\neq t+1$ and $\lambda(\{x^F,v\})\neq t'+1$, then $d(x,v)>2$, which is a contradiction. 
+Thus, for every variable $x$, we have that $\lambda(\{x^T,v\})= t+1$ or $\lambda(\{x^F,v\})= t'+1$ (or both). 
+In particular, this means that if $\lambda(\{x,x^F\})=\lambda(\{x^F,v\})$, then we set $x$ to \texttt{false}, since in this case $\lambda(\{x,x^T\})\neq\lambda(\{x^T,v\})$.
+
+%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
+Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
+
+Now assume for contradiction that the described assignment is not satisfying.
+Then there exists a clause $c$ that is not satisfied.
+Recall that we require $d(c,v)=2$.
+Hence, we must have a temporal path consisting of two edges from $c$ to $v$ such that the two edges have consecutive labels.
+By construction of $G$ there are three candidates for such a path, one for each literal of $c$.
+Assume w.l.o.g\ that $x$ appears in $c$ non-negated (the case of a negated appearance of $x$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x^T$. 
+Then we have that $\lambda(\{c,x^T\})=\lambda(\{x^T,v\})-1$.
+Furthermore, since $d(c,x)=2$ we also have that $\lambda(\{c,x^T\})=\lambda(\{x,x^T\})-1$.
+It follows that $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$.
+However, this implies that $x$ is set to \texttt{true} in the satisfying assignment and thus the clause $c$ is satisfied, a contradiction.
+
+%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
+Then we have that $\{c,x^T\}\in E(G)$.
+Assume that $\lambda(\{c,x^T\})=t$.
+Recall that we have specified $d(c,x_2)=2$.
+Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
+
+$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
+
+We construct a labelling $\lambda$ as follows.
+\begin{itemize}
+    \item All edges incident with a clause vertex $c$ obtain label one.
+    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
+    \item If variable $x$ is set to \texttt{true}, we set $\lambda(\{x^F,v\})=3$.
+    \item If variable $x$ is set to \texttt{false}, we set $\lambda(\{x^T,v\})=3$.
+    \item We set the labels of all other edges to two.
+\end{itemize}
+
+Next, we verify that all distances are realized.
+\begin{itemize}
+    \item For each variable $x$ in $\phi$ we have $d(x,v)=2$:
+
+    If $x$ is set to \texttt{true}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(\{x,x^F\})=2$ and $\lambda(\{x^F,v\})=3$.
+If $x$ is set to \texttt{false}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(\{x,x^T\})=2$ and $\lambda(\{x^T,v\})=3$.
+
+    \item For each clause $c$ in $\phi$ we have that $d(c,v)=2$:
+
+    Since we have a satisfying assignment there is a variable $x$ appearing in $c$ that is set to a truth-value that satisfies $c$.
+If $x$ appears non-negated in $c$ (and hence is set to \texttt{true}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x^T,v\})=2$.
+If $x$ appears negated in $c$ (and hence is set to \texttt{false}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x^F,v\})=2$.
+    \item Let $x$ be a variable that appears in clause $c$.
+    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_F)=2$:
+
+    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x,x^T\})=\lambda(\{x^T,x^F\})=2$.
+
+    If $x$ appears negated in $c$ we have $d(c,x)=d(c,x_T)=2$:
+
+    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x,x^F\})=\lambda(\{x^T,x^F\})=2$.
+    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we have $d(c,x^T)=d(c,x^F)=2$:
+
+    Let $y$ be a variable that appears non-negated in $c$ (the case where $y$ appears negated is symmetrical).
+Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(\{c,y^T\})=1$ and $\lambda(\{y^T,x^T\})=\lambda(\{y^T,x^F\})=2$.
+\end{itemize}
+Lastly, we show that all non-adjacent vertex pairs $u,w$ with $d(u,w)=\infty$ are not temporally connected in $(G,\lambda)$.
+\begin{itemize}
+\item For all pairs of clause vertices $c,c'$ we have $d(c,c')=\infty$: 
+\todo[inline]{New matrix entries D for period Delta: d(c,c')=Delta+1 (using three edges, with labels L, L+1, L).}
+
+Since all edges incident with clause vertices have label one and clause vertices are pairwise non-adjacent, there cannot be a temporal path from one clause vertex to another.
+\item For all variable vertices $x$ and clause vertices $c$ we have $d(x,c)=\infty$:
+\todo[inline]{New matrix entries D for period Delta: if x appears (negated or not) in c, then d(x,c)=Delta (using two edges, with label L+1, L).
+Otherwise D(x,c)=2Delta (using three edges, with labels L, L, L-1).}
+
+Since all edges incident with variable vertices $x$ have label two and all edges incident with clause vertices $c$ have label one, there cannot be a temporal path from a variable vertex $x$ to a clause vertex $c$.
+\item For all pairs of variable vertices $x,y$ we have $d(x,y)=\infty$:
+\todo[inline]{New matrix entries D for period Delta: d(x,y)=2Delta+1 (using three edges, each with the same label).}
+
+Since all edges incident with variable vertices $x$ have label two and variable vertices $x$ are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
+\item For all pairs of variable vertices $x,y$ we have $d(y^T,x)=d(y^F,x)=\infty$:
+\todo[inline]{New matrix entries D for period Delta: $d(y^T,x)=d(y^F,x)=Delta+1$ (using two edges, with equal labels).}
+
+Since all edges incident with variable vertices $x$ have label two and all edges incident with variable vertices $y^T, y^F$ have labels two or three and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from a variable vertex $y^T$ or $y^F$ to variable vertex $x$.
+\item For all pairs of variable vertices $x,y$ we have $d(x,y^T)=d(x,y^F)=\infty$:
+\todo[inline]{New matrix entries D for period Delta: $d(x,y^T)=d(x,y^F)=Delta+1$ (using two edges, with equal labels).}
+
+Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
+Furthermore, $v$ has distance two from $x$ in the unlabelled graph $G$.
+Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
+Hence, there is no temporal path from $x$ to $y^T, y^F$ using an edge with label three.
+Since all edges incident with $x$ have label two and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from variable vertex $x$ to variable vertex $y^T$ or $y^F$.
+\item For all variable vertices $x$ and clause vertices $c$ we have $d(v,x)=d(v,c)=\infty$:
+\todo[inline]{New matrix entries D for period Delta: d(v,x)=Delta (using two edges, with labels L+1,L). 
+New matrix entries D for period Delta: d(v,c)=Delta (using two edges, with labels L,L-1).}
+
+All edges incident with $v$ have labels two or three.
+All edges incident with $x$ have label two and all edges incident with $c$ have label one.
+We immediately have that there is no temporal path from $v$ to $c$.
+Furthermore, since $x$ and $v$ are non-adjacent, we also have that there is no temporal path from $v$ to $x$.
+\end{itemize}
+\end{proof}
+
+\bibliography{bibliography}
+
+\clearpage
+
+\appendix
+
+\section{
+\texorpdfstring{\deltaExact\ is (NOT) polynomial-time solvable}
 {\textsc{Simple Delta-TGR} is polynomial-time solvable}
@@
     More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
+    \begin{equation}\label{eq:def-VertexWaitingTimes}
        \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
@@
     \begin{observation} \label{obs:exact-VertexSum}
-    Let $v$ be a vertex of $G$, and let $N(v)=\{u_1, u_2, \ldots, u_k\}$, Then 
+    Let $v$ be a vertex of $G$, and let $N(v)=\{u_1, u_2, \ldots, u_k\}$. Then 
     \begin{equation*}
@@
     \begin{proof}
-        Using \cref{eq:def-VertexWaitingTime} and the fact that the indices of vertices $v_i$ are taken modulo $k$, we get the following:
+        Using \cref{eq:def-VertexWaitingTimes} and the fact that the indices of vertices $v_i$ are taken modulo $k$, we get the following:
         \begin{align*}
@@
 
-\subsection{
-\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}
-is polynomial-time solvable on trees, paths and cycles}
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation*}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation*}
-where the empty entries consists of positive integers different than $1$.
-
-Let $v_i$ be an arbitrary vertex in $C_n$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{claim} \label{claim:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive side  (resp.~negative), side of the cycle,
-    where the indices are taken modulo $n$.
-\end{claim}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through the vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to the vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the duration of fastest temporal paths from $v_i$ to any other vertex $v_j \in C_n$.
-Using \cref{claim:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has a $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\section{Hardness of Exact Realization}
-
-\todo[inline]{HM: For the following hardness I assume that we only consider strict temporal paths. (NK: Yes you are right, all paths are strict, sorry forgot to specify). \\
-Furthermore, I can currently only make it work if we do not have periods ($\Delta=\infty$). I am not sure the idea also works if we have periods.}
-
-\begin{theorem}
-	\textsc{Exact Realization $(\infty)$} is \NP-hard.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem 3-SAT~\cite{Karp1972Reducibility}.
-Here, we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
-We construct an instance of \textsc{Exact Realization $(\infty)$} as follows.
-
- We start by describing the vertex set of the underlying graph $G$.
-\begin{itemize}
-\item For each variable $x$ in $\phi$, we create three variable vertices $x, x^T, x^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x$ in $\phi$ we add the following five edges:
-
-$\{x, x^T\}, \{x, x^F\}, \{x^T, x^F\}, \{x^T, v\}, \{x^F,v\}$.
-\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges
-
-$\{x^T,y^T\},\{x^T,y^F\}, \{x^F,y^T\},\{x^F,y^F\}$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal.
-Let $x$ appear in $c$.
-If $X$ appears non-negated in $c$ we add edge $\{c,x^T\}$.
-If $x$ appears negated in $c$ we add edge $\{c, x^F\}$.
-\end{itemize}
-This finishes the construction of $G$.
-
-Now we specify the distances between all vertex pairs. Naturally, the distance between all pairs of adjacent vertices is one.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following distances:
-
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x$ in $\phi$ we specify the following distances to the super vertex $v$:
-
-    $d(x,v)=2$. %, $d(x_2,v)=3$.
-
-    \item For each clause $c$ in $\phi$ we specify the following distances to the super vertex $v$:
-
-    $d(c,v)=2$
-    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distances:
-
-    $d(c,x)=2$.
-
-    If $x$ appears non-negated in $c$ we specify the following distances:
-
-    $d(c,x_F)=2$.
-
-    If $x$ appears negated in $c$ we specify the following distances:
-
-    $d(c,x_T)=2$.
-    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
-
-    $d(c,x^T)=d(c,x^F)=2$.
-\end{itemize}
-All distances between non-adjacent vertex pairs that are not defined above are set to $\infty$.
-
-This finishes the construction of the \textsc{Exact Realization $(\infty)$} which can clearly be done in polynomial time.
-In the remainder we show that it is a yes-instance if and only if $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed \textsc{Exact Realization $(\infty)$} is a yes-instance.
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path between from $u$ to $w$ has exactly duration $d(u,w)$.
-In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$, then we set $x$ to \texttt{true}, otherwise we set $x$ to \texttt{false}.
-
-To show that this yields a satisfying assignment, we need to show some following properties of $\lambda$.
-First, observe that adding some integer $t$ to all time labels does not change the duration of any temporal path.
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$, then there is a shortest path from $u$ to $w$ in $G$ such that $\lambda$ puts consecutive time labels on the edges of that shortest path.
-
-Assume that for some variable $x$ we have that $\lambda(\{x,x^T\})=t$ and $\lambda(\{x,x^F\})=t'$. 
-We can deduce that $\lambda(\{x^T,v\})=t+1$ or $\lambda(\{x^F,v\})=t'+1$, otherwise we have that $d(x,v)>2$.
-Note that, if both $\lambda(\{x^T,v\})=t+1$ and $\lambda(\{x^F,v\})=t'+1$, then
-
-In particular, this means that if $\lambda(\{x,x^F\})=\lambda(\{x^F,v\})$, then we set $x$ to \texttt{false}, since in this case $\lambda(\{x,x^T\})\neq\lambda(\{x^T,v\})$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for contradiction that the described assignment is not satisfying.
-Then there exists a clause $c$ that is not satisfied.
-Recall that we require $d(c,v)=2$.
-Hence, we must have a temporal path consisting of two edges from $c$ to $v$ such that the two edges have consecutive labels.
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$.
-Assume w.l.o.g.\ that $x$ appears in $c$ non-negated (the case of negated is symmetrical) and the temporal path realizing $d(c,v)=2$ goes through vertex $x^T$.
-Then we have that $\lambda(\{c,x^T\})=\lambda(\{x^T,v\})-1$.
-Furthermore, since $d(c,x)=2$ we also have that $\lambda(\{c,x^T\})=\lambda(\{x,x^T\})-1$.
-It follows that $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$.
-However, this implies that $x$ is set to \texttt{true} in the satisfying assignment and the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labelling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x$ is set to \texttt{true}, we set $\lambda(\{x^F,v\})=3$.
-    \item If variable $x$ is set to \texttt{false}, we set $\lambda(\{x^T,v\})=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-
-Next, we verify that all distances are realized.
-\begin{itemize}
-    \item For each variable $x$ in $\phi$ we have $d(x,v)=2$:
-
-    If $x$ is set to \texttt{true}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(\{x,x^F\})=2$ and $\lambda(\{x^F,v\})=3$.
-If $x$ is set to \texttt{false}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(\{x,x^T\})=2$ and $\lambda(\{x^T,v\})=3$.
-
-    \item For each clause $c$ in $\phi$ we have that $d(c,v)=2$:
-
-    Since we have a satisfying assignment there is a variable $x$ appearing in $c$ that is set to a truth-value that satisfies $c$.
-If $x$ appears non-negated in $c$ (and hence is set to \texttt{true}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x^T,v\})=2$.
-If $x$ appears negated in $c$ (and hence is set to \texttt{false}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x^F,v\})=2$.
-    \item Let $x$ be a variable that appears in clause $c$.
-    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_F)=2$:
-
-    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x,x^T\})=\lambda(\{x^T,x^F\})=2$.
-
-    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_T)=2$:
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x,x^F\})=\lambda(\{x^T,x^F\})=2$.
-    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we have $d(c,x^T)=d(c,x^F)=2$:
-
-    Let $y$ be a variable that appears non-negated in $c$ (the case where $y$ appears negated is symmetrical).
-Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(\{c,y^T\})=1$ and $\lambda(\{y^T,x^T\})=\lambda(\{y^T,x^F\})=2$.
-\end{itemize}
-Lastly, we show that all non-adjacent vertex pairs $u,w$ with $d(u,w)=\infty$ are not temporally connected in $(G,\lambda)$.
-\begin{itemize}
-\item For all pairs of clause vertices $c,c'$ we have $d(c,c')=\infty$:
-
-Since all edges incident with clause vertices have label one and clause vertices are pairwise non-adjacent, there cannot be a temporal path from one clause vertex to another.
-\item For all variable vertices $x$ and clause vertices $c$ we have $d(x,c)=\infty$:
-
-Since all edges incident with variable vertices $x$ have label two and all edges incident with clause vertices $c$ have label one, there cannot be a temporal path from a variable vertex $x$ to a clause vertex $c$.
-\item For all pairs of variable vertices $x,y$ we have $d(x,y)=\infty$:
-
-Since all edges incident with variable vertices $x$ have label two and variable vertices $x$ are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
-\item For all pairs of variable vertices $x,y$ we have $d(y^T,x)=d(y^F,x)=\infty$:
-
-Since all edges incident with variable vertices $x$ have label two and all edges incident with variable vertices $y^T, y^F$ have labels two or three and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from a variable vertex $y^T$ or $y^F$ to variable vertex $x$.
-\item For all pairs of variable vertices $x,y$ we have $d(x,y^T)=d(x,y^F)=\infty$:
-
-Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
-Furthermore, $v$ has distance two from $x$ in the unlabelled graph $G$.
-Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
-Hence, there is no temporal path from $x$ to $y^T, y^F$ using an edge with label three.
-Since all edges incident with $x$ have label two and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from variable vertex $x$ to variable vertex $y^T$ or $y^F$.
-\item For all variable vertices $x$ and clause vertices $c$ we have $d(v,x)=d(v,c)=\infty$:
-
-All edges incident with $v$ have labels two or three.
-All edges incident with $x$ have label two and all edges incident with $c$ have label one.
-We immediately have that there is no temporal path from $v$ to $c$.
-Furthermore, since $x$ and $v$ are non-adjacent, we also have that there is no temporal path from $v$ to $x$.
-\end{itemize}
-\end{proof}
-
-\bibliography{bibliography}	
 \end{document}

### 2022-11-30 RealizingTemporalGraphs.tex
Wednesday 30th November

@@
 
+\section{FPT and W[1]-hardness of exact realization}
+In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
+The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
+Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
+
+\begin{theorem}
+    \deltaExactLong\ is FPT parameterized by the feedback edge number.
+\end{theorem}
+
+Let $D$ be an instance of \deltaExact, with $G$ being its underlying graph.
+We solve the problem using the following steps.
+\begin{enumerate}
+    \item Create $G'$ and $D'$ from $G$ and $D$ respectively, by removing all degree $1$ vertices from $G$ and $D$.
+    \item Compute a minimum feedback edge set $F$ in $G'$.
+    \item Determine $O(k)$ vertices of interest $U$ of $G'$, where $k = |F|$.
+    \item Find the (partial) labelling of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
+    \item Fill in the labeling for whole $G'$.
+    \item Fill in the labeling for $G$, respecting $D$.
+\end{enumerate}
+
 \bibliography{bibliography}

### 2022-12-04 RealizingTemporalGraphs.tex
Sunday 4th December

@@
 
+Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
+Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
+In their work Wo et.~al. \cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
+$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
+From this result, we can deduce the following. 
+\begin{lemma} \label{lemma:calculatingD}
+Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
+Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
+and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
+To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
+To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
+\end{lemma}
+
+Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
+$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
+Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
+Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
+
 %\section{Results}
@@
 
-\begin{theorem}
+\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
     \deltaExact\ can be solved in polynomial time on trees.
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:FPTwrtFES}
     \deltaExactLong\ is FPT parameterized by the feedback edge number.
@@
 
-Let $D$ be an instance of \deltaExact, with $G$ being its underlying graph.
-We solve the problem using the following steps.
+Before we start with the proof we fix the following notation. 
+Let $D$ be the input matrix of \deltaExact\ \ie
+the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
+Let $F$ be a minimum feedback edge set of $G$ and let $k$ be the feedback edge number of $G$.
+
+We now introduce an algorithm that determines the labeling of $G$, satisfying $D$, that runs in $f(k) \cdot \text{poly}(n)$ time.
+Our algorithm performs the following steps.
 \begin{enumerate}
     \item Create $G'$ and $D'$ from $G$ and $D$ respectively, by removing all degree $1$ vertices from $G$ and $D$.
-    \item Compute a minimum feedback edge set $F$ in $G'$.
-    \item Determine $O(k)$ vertices of interest $U$ of $G'$, where $k = |F|$.
-    \item Find the (partial) labelling of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
-    \item Fill in the labeling for whole $G'$.
-    \item Fill in the labeling for $G$, respecting $D$.
+    \item Compute a minimum feedback edge set $F$ in $G'$ (note $F$ is also a minimum feedback edge set of $G$).
+    \item Determine vertices of interest $U$ of the graph $G'$.
+    \item Find the (partial) labelling $\lambda$ of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
+    \item Extend the partial labelling $\lambda$ to the labeling of the whole $G'$, respecting $D'$.
+    \item Extend the labelling $\lambda$ of $G'$ to the labeling of $G$, respecting $D$.
 \end{enumerate}
+For each of the steps we now argue its correctness and time complexity.
+
+\paragraph{Step 1.}
+In the first step of the algorithm we create an instance $D'$, with the underlying graph $G'$, from $D$ and $G$, by simply removing all the vertices of degree one from $G$ and their corresponding rows and columns from the matrix $D$.
+This step is executed in $O(n+m)$ time.
+Since we determine the labels of edges in $G \setminus G'$ in the last step, the the whole solution is not affected by performing this step.
+
+\paragraph{Step 2.}
+To find a minimum feedback edge set $F$ of $G'$ we find a spanning tree $T$ of $G'$ and get $F = E(G) \setminus E(T)$. 
+Clearly we perform this step in linear time.
+
+\paragraph{Step 3.}
+Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
+Let $V_1 \subset V(G')$ be the set of leaves in $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to some edges in $F$, and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$.
+Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
+and $|V_3| \leq |V_1|$ by the properties of trees.
+We denote with $U = V_1 \cup V_2 \cup V_3$ the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
+Clearly we perform this step in linear time.
+
+\paragraph{Step 4}
+In this step we want to determine the labeling of fastest temporal paths among all vertices in $U$.
+For a pair $u,v$ of vertices in $U$, there are $2^{O(k)}$ possible paths in $G'$ between them, where each one could be the fastest temporal path from $u$ to $v$ and $v$ to $u$.
+Therefore we get $2^{O(k)}$ partial (different) labelings of $G'$.
+\todo{NK: How??}
+This is true for any pair of vertices in $U$. 
+We then try to join the labelings of different pairs of vertices and end up with $(2^{O(k)})^{k^2} = 2^{O(k^3)}$ different labelings.
+Some of them we can reject immediately, namely if two different labellings label the same edge with the different label.
+At the end we end up with $22^{O(k^3)}$ partial labelings $\lambda$ of $G'$, where $(G',\lambda)$ has labels on all fastest paths among any pair of vertices in $U$,  and the duration of the fastest temporal path from $u$, to $v$, where $u,v \in U$ satisfies the value $D_{u,v}$.
+\todo[inline]{Missing details.}
+
+\paragraph{Step 5.}
+In the partially labeled temporal graph $(G',\lambda)$ the durations of the fastest temporal paths among vertices in $U$ satisfy the conditions of $D'$,
+but there are still some labels without labels.
+Let $e=(uv)$ be one such edge.
+\todo[inline]{TBD}
+
+\paragraph{Step 6.}
+Let $\lambda$ be the labelling of $G'$, that satisfies $D'$.
+Let $s \in V(G) \setminus V(G')$, be a vertex of degree one, that was removed from $G$ in Step 1,
+and let $u$ be its neighbor in $G$.
+First, we can easily assume that $|N_{G'}(u)|\geq 1$, if this is not true, then either $G$ is a star or $G'$ is disconnected and therefore also $G$ is disconnected, where $u$ is in a part of $G$ that forms a star.
+We can solve the problem for stars in polynomial time (see \cref{thm:deltaExact-PolyTimeTrees}).
+
+To determine the correct label of edge $su$ we do the following.
+We find the vertex $v_i \in N_{G'}(u)$ that is the closest to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
+We claim, that the path $P=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $(G, \lambda'')$.
+Suppose that is not true, then there exists a faster path $P^*$ from $s$ to $v_i$, that goes through $u$ (as this is the only neighbor of $s$), through some other vertex $v_j \in N_{G'}(u) \setminus \{v_i \}$, and through some other path $P'$ in $G$, before it finishes it $v_i$, where $P'$ is at least an edge (from $v_j$ to $v_i$).
+Therefore $P^* = (s,u,v_j,P',v_i)$, where $d(P^*) \leq d(P)$, now since $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$, the first part of path $P^*$ from $s$ to $v_j$ takes at least $D_{s,v_i}$ time,
+since $v_i \neq v_j$, we need at least one more time-step (one more edge) to traverse from $v_i$ to reach $v_j$, so $d(P^) \geq D_{s,v_i} + 1$, and so $P^*$ cannot be faster than $P$.
+Since $P=(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of the edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
+
+We repeat the above procedure for all degree one vertices in $G$, that we removed in Step 1, and we end up with the labeling $\lambda$ of the whole graph.
+Now we have to make sure that all the new labels satisfy $D$, to do this we calculate the matrix $D'$ of fastest temporal paths among all pairs of vertices in $(G, \lambda)$ and compare the results with $D$, if any values differ, we stop and return a \textit{NO} answer, if $D = D'$ we return the labeling $\lambda$.
+
+To calculate $\lambda (s,v_i)$ we need $O(|N_{G'}(u)|) = O(n)$ time, therefore to calculate all labels of edges incident to vertices of degree one in $G$, we need $O(n^2)$ time, calculating $D'$ takes $O(n^3\log n)$ time (see \cref{lemma:calculatingD}), therefore the whole step is performed in polynomial time.
 

### 2023-01-09 RealizingTemporalGraphs.tex

@@
 In this section we study the hardness of \deltaExact. We first start with defining certain notions, that will be of use when solving the problem.
-
-\todo[inline]{NK:Following definition and observation are copied from the previous section (need to delete from one part).}
 
@@
 
-We construct a labelling $\lambda$ as follows.
+We construct a labeling $\lambda$ as follows.
 \begin{itemize}
@@
 Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
-Furthermore, $v$ has distance two from $x$ in the unlabelled graph $G$.
+Furthermore, $v$ has distance two from $x$ in the unlabeled graph $G$.
 Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
@@
     \item Create $G'$ and $D'$ from $G$ and $D$ respectively, by removing all degree $1$ vertices from $G$ and $D$.
-    \item Compute a minimum feedback edge set $F$ in $G'$ (note $F$ is also a minimum feedback edge set of $G$).
+    \item Compute a minimum feedback edge set $F$ in $G'$ (note, $F$ is also a minimum feedback edge set of $G$).
     \item Determine vertices of interest $U$ of the graph $G'$.
-    \item Find the (partial) labelling $\lambda$ of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
-    \item Extend the partial labelling $\lambda$ to the labeling of the whole $G'$, respecting $D'$.
-    \item Extend the labelling $\lambda$ of $G'$ to the labeling of $G$, respecting $D$.
+    \item \label{enum:FPT-labelingVerticesOfInterest} Guess the (partial) labeling $\lambda$ of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
+    \item \label{enum:FPT-labelingraphNoLeafs} Extend the partial labeling $\lambda$ to the labeling of the whole $G'$, respecting $D'$.
+    \item \label{enum:FPT-labelingWholeGraph} Extend the labeling $\lambda$ of $G'$ to the labeling of $G$, respecting $D$.
 \end{enumerate}
+It is important to point out, that in step~\ref{enum:FPT-labelingVerticesOfInterest}, our algorithm does not build a labeling satisfying conditions in this step,
+and then tries to extend it in steps~\ref{enum:FPT-labelingraphNoLeafs} and \ref{enum:FPT-labelingWholeGraph},
+but it
+builds an integer linear program (ILP) problem with $O(k)$ variables,
+with restrictions satisfying condition from steps~\ref{enum:FPT-labelingVerticesOfInterest}--\ref{enum:FPT-labelingWholeGraph}.
 For each of the steps we now argue its correctness and time complexity.
 
-\paragraph{Step 1.}
+\subsection{Steps 1 -- 3 of the FPT algorithm}
 In the first step of the algorithm we create an instance $D'$, with the underlying graph $G'$, from $D$ and $G$, by simply removing all the vertices of degree one from $G$ and their corresponding rows and columns from the matrix $D$.
 This step is executed in $O(n+m)$ time.
-Since we determine the labels of edges in $G \setminus G'$ in the last step, the the whole solution is not affected by performing this step.
+Since we determine the labels of edges in $G \setminus G'$ in the last step, the whole solution is not affected by performing this step.
 
-\paragraph{Step 2.}
-To find a minimum feedback edge set $F$ of $G'$ we find a spanning tree $T$ of $G'$ and get $F = E(G) \setminus E(T)$. 
-Clearly we perform this step in linear time.
+In the second step,
+we determine a minimum feedback edge set $F$ of $G'$ by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
+We can perform this step in linear time.
 
-\paragraph{Step 3.}
+In the third step we determine the set $U$ of \emph{vertices of interest}.
 Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
 Let $V_1 \subset V(G')$ be the set of leaves in $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to some edges in $F$, and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$.
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
+Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ are incident to at least one edge in $F$,
 and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with $U = V_1 \cup V_2 \cup V_3$ the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
-Clearly we perform this step in linear time.
+We denote with $U = V_1 \cup V_2 \cup V_3$ the set of vertices of interest. It follows that $|U| \leq 4k$.
+We can determine vertices of $U$ in linear time.
 
-\paragraph{Step 4}
-In this step we want to determine the labeling of fastest temporal paths among all vertices in $U$.
-For a pair $u,v$ of vertices in $U$, there are $2^{O(k)}$ possible paths in $G'$ between them, where each one could be the fastest temporal path from $u$ to $v$ and $v$ to $u$.
-Therefore we get $2^{O(k)}$ partial (different) labelings of $G'$.
-\todo{NK: How??}
-This is true for any pair of vertices in $U$. 
-We then try to join the labelings of different pairs of vertices and end up with $(2^{O(k)})^{k^2} = 2^{O(k^3)}$ different labelings.
-Some of them we can reject immediately, namely if two different labellings label the same edge with the different label.
-At the end we end up with $22^{O(k^3)}$ partial labelings $\lambda$ of $G'$, where $(G',\lambda)$ has labels on all fastest paths among any pair of vertices in $U$,  and the duration of the fastest temporal path from $u$, to $v$, where $u,v \in U$ satisfies the value $D_{u,v}$.
-\todo[inline]{Missing details.}
+\subsection{Step 4 of the FPT algorithm}
+In this step we want to guess the structure of the fastest paths among all pairs of vertices of $U$. %and then determine their labeling.
+For a pair $u,v$ of vertices in $U$, there are $2^{O(k)}$\todo{NK: why?
+\\ Isn't $k!$} possible paths in $G'$ between them, where each one could be the fastest temporal path from $u$ to $v$ and $v$ to $u$.
 
-\paragraph{Step 5.}
+We claim that knowing the structure of the fastest temporal path among two vertices, determines the labeling of such path, up to the label of the first edge.
+To prove this we use the following observation, that follows from the definition of the duration of the fastest temporal path.
+\begin{observation}\label{obs:FirstLabelAndDuration}
+    Let $P$ be the fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
+    Then knowing the label of the first (last) edge and the duration of $P$, one can uniquely determine the label of the last (first) edge of $P$.
+\end{observation}
+This is true as, by the definition the duration of $P$ is calculated as the difference of labels of last and first edge plus $1$,
+where the label of last edge is considered with some delta periods,
+\ie $d(P) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$.
+Therefore $d(P) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
+We can now state and prove the following claim.
+\begin{claim}
+    Suppose $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, is a $u,v$ path in $G'$, which is also the underlying path of the fastest temporal path from $u$ to $v$.
+    One can determine the labelling $\lambda$ of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
+    such that the labelling $\lambda$ respects $D'$.
+\end{claim}
+\begin{proof}
+Let $P$ be the fastest temporal path from $u$ to $v$.
+We have the following two options:
+\begin{enumerate}
+\item no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset $,
+\item there are at least $3$ vertices of interest in $P$.
+\end{enumerate}
+
+In the first case we get that all other vertices in $P$ are reached from $u$ using a (sub)path of $P$.
+To prove this suppose for the contradiction, that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$.
+Since only $u$ and $v$ are the vertices of interest, it follows that all other vertices on $P$ are of degree $2$. 
+Then, the only way to reach $v_i$ from $v$, that differs from $P$, would be to go from $v$ to $u$ using a differnt path $P_2$,
+and then go from $u$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
+But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 + (u,v_i) > d(P) > d(P_i)$.
+
+Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
+therefore we can label each edge using the \cref{obs:FirstLabelAndDuration},
+where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
+we set the first label of $P$ to be a constant $c_{uv}$.
+This gives us a condition on the label of each edge of $P$, that depends on the value $c_{u,v}$.
+
+Let us now prove the correctness of the second case.
+We denote with $v_i \in U$ a vertex of interest in $P \setminus \{u,v\}$.
+There are two options, either $v_i$ is reached from $u$ using the subpath $P_i = (u, v_2, v_3, \dots, v_i)$ of $P$,
+or there exists a fastest temporal path $P' = (u, w_2, w_3, \dots, w_{p'} = v_i)$, for which $P \cap P' = \{u, v_i\}$.
+If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling the same as in previous case.
+So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD}
+\end{proof}
+
+Therefore, knowing the structure of the exact temporal path $P$ from $u$ to $v$, labeling the path equals to creating a variable $c_{u,v} \in [\Delta]$ that represents the label of the first edge of $P$,
+and $O(len(P))$ constraints, that uniquely determine the labels of all other edges of $P$.
+This holds for all pairs of vertices in $U$, therefore
+knowing the structure of fastest temporal paths among all pairs of vertices in $U$ creates $k^2$ variables of form $c_{u,v}$.
+
+There are $(2^{O(k)})^{k^2} = 2^{O(k^3)}$ different possible fastest temporal paths among all pairs of vertices in $U$. 
+Therefore we have to build $2^{O(k^3)}$ different ILP problems.
+
+\subsection{Step 5 of the FPT algorithm}
 In the partially labeled temporal graph $(G',\lambda)$ the durations of the fastest temporal paths among vertices in $U$ satisfy the conditions of $D'$,
@@
 
-\paragraph{Step 6.}
-Let $\lambda$ be the labelling of $G'$, that satisfies $D'$.
+\subsection{Step 6 of the FPT algorithm}
+\todo[inline]{This section is wrong, we keep this here as we will use some of the ideas.}
+Let $\lambda$ be the labeling of $G'$, that satisfies $D'$.
 Let $s \in V(G) \setminus V(G')$, be a vertex of degree one, that was removed from $G$ in Step 1,
@@
     \begin{claim}
-    Labelling $\lambda$ is a solution for the \textsc{Exact Realization $(\Delta)$} if and only if
+    labeling $\lambda$ is a solution for the \textsc{Exact Realization $(\Delta)$} if and only if
     for every cycle $C$ of $(G,\lambda)$ it holds that the sum of the travel delays along $C$ is $0$ modulo $\Delta$.

### 2023-01-09 RealizingTemporalGraphs.tex

@@
 Let $P$ be a temporal path from $u_0$ to $u_k$ on the vertices $u_0,u_1,\ldots,u_k$, and let $P^\textsc{ST}=(u_0,u_1,\ldots,u_k)$ be the underlying \emph{static} path in $G$.
-Then $P$ is \emph{$D$-increasing} in $G$ if $0=D_{u_0,u_0}<D_{u_0,u_1}<D_{u_0,u_2}<\ldots,D_{u_0,u_k}$.
+Then $P$ is \emph{$D$-increasing} in $G$ if $0=D_{u_0,u_0}<D_{u_0,u_1}<D_{u_0,u_2}< \ldots < D_{u_0,u_k}$.
 \end{definition}
@@
 \begin{observation}
-Let $D$ be \textsc{YES}-instance of \textsc{$(k,\Delta)$-TGR}, and let 
-$(G,\lambda,\Delta)$ be a certificate for $D$, where $\lambda:E\rightarrow \{1,2,\ldots,\Delta\}^k$ a $\Delta$-periodic labeling of $G$.
+Let $D$ be a \textsc{YES}-instance of \textsc{$(k,\Delta)$-TGR}, and let 
+$(G,\lambda,\Delta)$ be a certificate for $D$, where $\lambda:E\rightarrow \{1,2,\ldots,\Delta\}^k$ is a $\Delta$-periodic labeling of $G$.
 Then, for every pair $u,v$ of vertices of $G$, every fastest temporal path from $u$ to $v$ is $D$-increasing.
@@
         \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & = 
-        \left(\lambda(v_{i}v_{i+1} - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i} - \lambda(v_1v_2) + 1\right) \\
-        & = \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}),
+        & \equiv 
+        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
+        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
+        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
         \end{align*}
@@
     Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to read through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
+    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
 At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
@@
 
-    From now on we can assume that we know that the underlying graph $G$ is a tree and we know how it looks like.
+    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know how it looks like.
     For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
 
-    For a vertex $v_i$ we check which vertex $v_j \in G$ is furthest away from it, \ie for which vertex $v_j$ the entry $D_{i,j}$ is maximum.
-    We now take the unique (fastest) temporal path $P_{i,j}$ and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$ and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(i,i-1,i+1)$ the value corresponding to the travel delay at vertex $v_i$ when traveling from $v_{i-1}$ to $v_{i}$, \ie $\tau_{v_i}^{v_{i-1}, v_i}$, whenever $v_{i-1}v_i, v_iv_{i+1} \in E(G)$.
+    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
+    We now take the unique path $P_{i,j}$ in $G$, which has to also be the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
+    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$.
 All other values of $T$ are set to \textsc{Null}.
@@
     We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$, corresponding to the vertex $v_i$,
+    When we have exhausted the $i$-th row of $D$,
+    \ie vertex $v_i$ now reaches every vertex of $G$,
     we continue and repeat the procedure for all other vertices.
     If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices $v_i$ in the tree, of degree at least $2$.
+    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
     The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
@@
     Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of the edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+    We start by fixing a label of one arbitrary edge as $a$, where $a \in [\Delta]$.
+    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
     More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
@@
     It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore all together the whole algorithm is performed in polynomial time.
+Therefore, all together the whole algorithm is performed in polynomial time.
 \end{proof}
@@
 but it
-builds an integer linear program (ILP) problem with $O(k)$ variables,
+builds (many different instances of) integer linear program (ILP) problem with $O(k)$ variables,
 with restrictions satisfying condition from steps~\ref{enum:FPT-labelingVerticesOfInterest}--\ref{enum:FPT-labelingWholeGraph}.
+At the end we solve the ILP problem on all instances and if there is a positive solution, it gives rise to the desired labeling $\lambda$ of $G$.
 For each of the steps we now argue its correctness and time complexity.

### 2023-01-12 RealizingTemporalGraphs.tex
Changes, Thursday 12th of January

@@
 
-\begin{definition}[temporal path]
+\begin{definition}[temporal path] \label{def:temporalPath+Duration}
 Let $(G,\lambda)$ be a temporal graph.
@@
     \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking the edge $e_1=uv$ and then the edge $e_2 = vz$.
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
 
@@
         Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to the vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
+        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
         At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
@@
 The matrix $D$ is of the following form
-\begin{equation*}
+\begin{equation} \label{eq:D-matrixForCycles}
   D = 
@@
   \end{bmatrix},
-\end{equation*}
+\end{equation}
 where the empty entries consists of positive integers different than $1$.
@@
 Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct for, our algorithm stops and returns the negative answer.
-From now on, we will assume, that the input matrix is of correct form.
+If it is not of correct form, our algorithm stops and returns the negative answer.
+From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
 
@@
     for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through the vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
+    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
     first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
@@
         d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to the vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
+    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
     (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
@@
 We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of the edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
 More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
@@
 \begin{enumerate}
+    \item Preprocessing on graph $G$. Determine the set $E$ of feedback edges and the set $U$ of vertices of interest, where $|E|, |U| \in O(k)$.
+    \item Guess the fastest temporal paths among vertices in $U$, for each guess create an ILP with variables corresponding to fastest temporal paths.
+    All in total create $f(k)$ partial ILP instances, each with $f(k)$ variables
+    \item For each partial ILP instance I:
+    \begin{enumerate}
+        \item create $f(k)$ final instances $I_I$,
+        \item check if $I_I$ has a solution.
+    \end{enumerate}
+\end{enumerate}
+\begin{comment}
+\begin{enumerate}
     \item Create $G'$ and $D'$ from $G$ and $D$ respectively, by removing all degree $1$ vertices from $G$ and $D$.
@@
 \end{enumerate}
+
 It is important to point out, that in step~\ref{enum:FPT-labelingVerticesOfInterest}, our algorithm does not build a labeling satisfying conditions in this step,
@@
 For each of the steps we now argue its correctness and time complexity.
-
-\subsection{Steps 1 -- 3 of the FPT algorithm}
+\end{comment}
+
+\subsection{Step 1 of the FPT algorithm}
 In the first step of the algorithm we create an instance $D'$, with the underlying graph $G'$, from $D$ and $G$, by simply removing all the vertices of degree one from $G$ and their corresponding rows and columns from the matrix $D$.
-This step is executed in $O(n+m)$ time.
-Since we determine the labels of edges in $G \setminus G'$ in the last step, the whole solution is not affected by performing this step.
-
-In the second step,
-we determine a minimum feedback edge set $F$ of $G'$ by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-We can perform this step in linear time.
-
-In the third step we determine the set $U$ of \emph{vertices of interest}.
+This part is executed in $O(n+m)$ time.
+
+Then we determine a minimum feedback edge set $F$ of $G'$ by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
+Lastly, we determine the set $U$ of \emph{vertices of interest}.
 Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
@@
 We denote with $U = V_1 \cup V_2 \cup V_3$ the set of vertices of interest. It follows that $|U| \leq 4k$.
-We can determine vertices of $U$ in linear time.
-
-\subsection{Step 4 of the FPT algorithm}
-In this step we want to guess the structure of the fastest paths among all pairs of vertices of $U$. %and then determine their labeling.
-For a pair $u,v$ of vertices in $U$, there are $2^{O(k)}$\todo{NK: why?
-\\ Isn't $k!$} possible paths in $G'$ between them, where each one could be the fastest temporal path from $u$ to $v$ and $v$ to $u$.
-
-We claim that knowing the structure of the fastest temporal path among two vertices, determines the labeling of such path, up to the label of the first edge.
-To prove this we use the following observation, that follows from the definition of the duration of the fastest temporal path.
+We determine $F$ and $U$ in linear time.
+
+\subsection{Step 2 of the FPT algorithm}
+In this step we want to guess the structure of fastest paths (underlying paths) among all pairs of vertices of $U$. %and then determine their labeling.
+For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
+Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$.
+Repeating this for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of fastest temporal paths among all vertices.
+
+Each partial ILP instance is connected to one list of specific fastest temporal paths among the vertices from $U$.
+From now on, for every par of vertices $u,v \in U$ we assume that we know exactly what is the underlying path of a fastest temporal path from $u$ to $v$.
+We describe now how to build a specific partial ILP instance from a specific list of fastest temporal paths.
+While building the ILP instances we exploit the following property greatly, that is why we state it as a separate observation.
+
 \begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then knowing the label of the first (last) edge and the duration of $P$, one can uniquely determine the label of the last (first) edge of $P$.
+    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
+    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P)$ of $P$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
+    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
 \end{observation}
-This is true as, by the definition the duration of $P$ is calculated as the difference of labels of last and first edge plus $1$,
+The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}. Since the duration of $P$ is calculated as the difference of labels of last and first edge plus $1$,
 where the label of last edge is considered with some delta periods,
-\ie $d(P) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$.
+\ie $d(P) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
 Therefore $d(P) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-We can now state and prove the following claim.
+
+In the following we prove that knowing the structure (the exact underlying path) of a fastest temporal path $P$, among two vertices of interest $u,v \in U$,
+results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ (with the exception of some constant number of edges), up to the label of the first edge.
+
 \begin{claim}
-    Suppose $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, is a $u,v$ path in $G'$, which is also the underlying path of the fastest temporal path from $u$ to $v$.
-    One can determine the labelling $\lambda$ of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
-    such that the labelling $\lambda$ respects $D'$.
+    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
+    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
+    Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
+    We can determine the labeling $\lambda$ of every edge in $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
+    such that the labeling $\lambda$ respects $D'$.
 \end{claim}
-\begin{proof}
-Let $P$ be the fastest temporal path from $u$ to $v$.
-We have the following two options:
-\begin{enumerate}
-\item no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset $,
-\item there are at least $3$ vertices of interest in $P$.
-\end{enumerate}
-
-In the first case we get that all other vertices in $P$ are reached from $u$ using a (sub)path of $P$.
-To prove this suppose for the contradiction, that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$.
-Since only $u$ and $v$ are the vertices of interest, it follows that all other vertices on $P$ are of degree $2$. 
-Then, the only way to reach $v_i$ from $v$, that differs from $P$, would be to go from $v$ to $u$ using a differnt path $P_2$,
-and then go from $u$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 + (u,v_i) > d(P) > d(P_i)$.
+
+\begin{proof}
+In this case we get that all other vertices in $P$ are reached from $u$ using a (sub)path of $P$.
+To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$.
+Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
+Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
+and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
+But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 + (v,v_{p-1}, \dots, v_i) > d(P) > d(P_i)$.
 
 Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using the \cref{obs:FirstLabelAndDuration},
+therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
 where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
 we set the first label of $P$ to be a constant $c_{uv}$.
-This gives us a condition on the label of each edge of $P$, that depends on the value $c_{u,v}$.
-
-Let us now prove the correctness of the second case.
+This gives us a unique label for each edge of $P$, that depends on the value $c_{u,v}$.
+\end{proof}
+
+\begin{claim}
+    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
+    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
+    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
+    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
+    such that the labeling $\lambda$ respects $D'$.
+    Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
+\end{claim}
+
+\begin{proof}
 We denote with $v_i \in U$ a vertex of interest in $P \setminus \{u,v\}$.
@@
 If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling the same as in previous case.
-So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD}
-\end{proof}
-
-Therefore, knowing the structure of the exact temporal path $P$ from $u$ to $v$, labeling the path equals to creating a variable $c_{u,v} \in [\Delta]$ that represents the label of the first edge of $P$,
-and $O(len(P))$ constraints, that uniquely determine the labels of all other edges of $P$.
-This holds for all pairs of vertices in $U$, therefore
-knowing the structure of fastest temporal paths among all pairs of vertices in $U$ creates $k^2$ variables of form $c_{u,v}$.
-
-There are $(2^{O(k)})^{k^2} = 2^{O(k^3)}$ different possible fastest temporal paths among all pairs of vertices in $U$. 
-Therefore we have to build $2^{O(k^3)}$ different ILP problems.
-
-\subsection{Step 5 of the FPT algorithm}
-In the partially labeled temporal graph $(G',\lambda)$ the durations of the fastest temporal paths among vertices in $U$ satisfy the conditions of $D'$,
-but there are still some labels without labels.
-Let $e=(uv)$ be one such edge.
-\todo[inline]{TBD}
+So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD - George prooved it}
+\end{proof}
+
+We use the above results in the following way.
+For all vertices of interest $u \in U$ and $v \in U \setminus \{v\}$, we know the underlying path $P_{u,v}$ of a fastest temporal path from $u$ to $v$. 
+We create a variable $c_{u,v}^{e_1} \in [\Delta]$ that corresponds to the label of the first edge of $P_{u,v}$ in $(G', \lambda')$ and potentially at most $\ell_{u,v}$ variables $c_{u,v}^{e_w} \in [\Delta]$ corresponding to
+labels of edges $e_w \in P_{u,v}$ that are incident to a vertex of interest $w$, for which the underlying path $P_{u,w}$ of a fastest temporal path from $u$ to $w$ intersects $P_{u,v}$ only in vertices $u$ and $w$.
+Labels on all other edges of $P_{u,v}$ are determined exactly, in relation to the constant $c_{u,v}^{e_1}$.
+Repeating this procedure for all $u,v \in U$ creates at most $|U|^3 = O(k^3)$ new variables.
+
+\todo[inline]{Write example for variables and constrains this part produces.}
+
+\subsection{Step 3 of the FPT algorithm}
+
+After finishing the second step of the FPT algorithm, labels on all edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined up to the label of the first edge.
+There may still be some edges in the graph, that are unlabeled. Note that these edges are exactly the ones that are not a part of any fastest temporal path.
+Let us first observe some properties of such edges.
+
+\todo[inline]{Fix the following proof, add more details/definitions to the introduction.}
+\begin{claim}
+    Unlabeled edges form disjoint paths in $G'$, where each path $P$ starts and ends in some vertex of interest, 
+    \ie for every unlabeled path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+\end{claim}
+
+\begin{proof}
+    We prove this claim in two steps.
+    First, all inner vertices of $P$, \ie vertices $v_i \in P \setminus \{u,v\}$ are of degree exactly $2$.
+They are of degree at least $2$ since they are on a path $P$ and are incident to two unlabeled edges in  $P$.
+    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter (sub)paths.
+
+    Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
+As $u$ is the starting vertex of the unlabeled path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
+    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among some vertices of interest and $u$ would be an inner vertex on that path.
+    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one unlabeled edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
+\end{proof}
+
+\begin{claim}
+    Among any pair of vertices of interest $u,v \in U$ there can be at most one unlabeled path $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+\end{claim}
+\begin{proof}
+    Suppose for the contradiction that there are two unlabeled paths among $u,v \in U$.
+    Denote them with $P$ and $P'$. 
+    Then $C = P \cup P'$ form a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
+   Since $C$ is a cycle, at least one of it's edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
+   both endpoints of $e$ have to be in $U$.
+   So $P$ and $P'$ cannot be both fully unlabeled.
+\end{proof}
+
+From the above it follows that there are at most $f(k)$ (namely $O(|U|^2$) unlabeled paths in $G'$ after algorithm finishes step 2.
+Now we want to extend the labeling from Step 2 to all unlabeled paths.
+To do this we want to relate the labeling of an unlabeled path to some fully labeled (\ie fastest temporal) path.
+Let us first observe some properties.
+
+Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an unlabeled path in $G'$, between vertices of interest $u,v \in U$,
+let $P$ be the underlying path of a fastest temporal path from $u',v' \in U$.
+Let $P$ be such path that there exists a vertex $x \in P \setminus \{u,v\}$ of degree two (\ie $x\notin U$).
+
+Since $x$ is an inner vertex of $P$ and is of degree two, then we know the labels of its two edges incident to it.
+Denote with $\ell_x$ the edge incident to $x$ that is closer to $u'$ on the path $P$, and with $r_x$ the edge that is closer to $v'$ on $P$.
+Let $y$ be an inner vertex on the path $Q$.
+Similarly, denote with $\ell_y$ the edge incident to $y$ that is closer to $u$ on the path $Q$, and with $r_y$ the edge that is closer to $v$ on $Q$.
+Observe the following. 
+To reach $y$ from $x$ there are $4$ different options, at the start path uses either edge $\ell_y$ or $r_y$, 
+and at the end path must use either $\ell_x$ or $y_x$.
+Since this is true for any path (hence any temporal path), it holds also for the fastest temporal pathfrom $x$ to $y$.
+
+\begin{claim}\label{claim:FPT-unlabeldPaths-01}
+    Suppose that the fastest temporal path from $x$ to $y$ uses at the beginning edge $\ell_x$.
+    We now claim that if the fastest temporal path from $x$ to $y$ uses edge $\ell_y$ (resp.~$r_y$) as the last edge,
+    then the fastest temporal path from $x$ to any other vertex of $Q$, that is closer to $u$ (resp.~$v$) 
+    uses the same edge $\ell_y$ (resp.~$r_y$) as the last edge and $\ell_x$ as the first edge.
+    Similarly holds if the first edge of the fastest temporal path is $r_x$.
+\end{claim}
+\begin{proof}
+    Suppose that $y, y'$ are two vertices of $Q$, where the distance from $u$ to $y'$, in $Q$, is shorter than the distance from $u$ to $y$.
+    Suppose also that the fastest temporal path from $x$ to $y$ uses the edges $\ell_x$ and $\ell_y$, and passes through $y'$. Denote this path as $P_{x,y}$.
+    Denote with $P_{x,y}^{y'}$ the subpath of the temporal path $P_{x,y}$ from $x$ to $y'$
+    Now observe the following possibilities. %
+    \\
+    First, suppose that a fastest temporal path from $x$ to $y'$ uses the edges $\ell_x$ and $r_y$, denote it with $P_{x,y'}^1$.
+    Then the duration of $d(P_{x,y}^{y'}) \geq  d(P_{x,y'}^1)$.
+    But since $P_{x,y'}^1$ passes through vertex $y$, the duration from $x$ to $y$ on $P_{x,y'}^1$ is strictly smaller than $d(P_{x,y'}^1)$, and conversely 
+    $d(P_{x,y})$ is strictly greater than $d(P_{x,y}^{y'})$,
+    therefore at vertex $y$ we get that 
+    $d(P_{x,y})$ is strictly bigger than the duration of the subpath of $P_{x,y'}^1$ from $x$ to $y$, which is not possible. %
+    \\
+    Second, suppose that a fastest temporal path from $x$ to $y'$ uses the edges $r_x$ and $\ell_y$, denote it with $P_{x,y'}^2$.
+    Therefore $d(P_{x,y'}^2) \leq d(P_{x,y}^{y'})$.
+    To get the duration of the initial $P_{x,y}$ we can split the problem into calculating the duration from $x$ to $y'$ and the duration from $y'$ to $y$, plus the waiting time at vertex $y'$.
+    Since there is a unique path from $u$ to $y'$ and then to $y$, the waiting time at $y'$ and the duration of the path from $y'$ to $y$ is independent of the choice of path from $x$ to $y'$. 
+    Therefore, from the fact that $P_{x,y}$ is a fastest temporal path from $x$ to $y$ we get that $d(P_{x,y'}^2) \geq d(P_{x,y}^{y'})$.
+    All together we conclude that $d(P_{x,y}^{y'})$ is a fastest temporal path from $x$ to $y'$.%
+    \\
+    Third, suppose that a fastest temporal path from $x$ to $y'$ uses the edges $r_x$ and $r_y$, denote it with $P_{x,y'}^3$.
+    Then the subpath of $P_{x,y'}^3$ from $x$ to $y$ would be strictly faster than $P_{x,y}$, which is not possible.
+\end{proof}
+%
+Using the results from above we can now prove the following.
+\begin{lemma}
+    Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an unlabeled path in $G'$, between vertices of interest $u,v \in U$,
+    let $P$ be the underlying path of a fastest temporal path from $u',v' \in U$.
+    Let $P$ be such path that there exists a vertex $x \in P \setminus \{u,v\}$ of degree two (\ie $x \notin U$).
+    Then we can precisely determine the labels on every edge of $Q$, but one, up to the label $c_{u'v'}$ of the first edge of path $P$.
+\end{lemma}
+\begin{proof}
+    %To prove this we use \cref{claim:FPT-unlabeldPaths-01} and \cref{obs:FirstLabelAndDuration}.
+    Let us denote with $y$ the vertex of $Q$, for which the duration from $x$ to $y$ is the biggest, among vertices of $Q$,
+    more precisely $x$ is a vertex corresponding to $max_{v_i \in Q} D_{x,v_i}$.
+    Denote 
+    with $\ell_x$ the edge incident to $x$ that is closer to $u'$ on path $P$, and with $r_x$ the edge that is closer to $v'$ on $P$.
+    Similarly, denote with $\ell_y$ the edge incident to $y$ that is closer to $u$ on the path $Q$, and with $r_y$ the edge that is closer to $v$ on $Q$.
+    Suppose that the fastest temporal path $P$ from $x$ to $y$ uses first edge $\ell_x$ and then edge $\ell_y$.
+    Then it follows from \cref{claim:FPT-unlabeldPaths-01} that all fastest temporal paths from $x$ to vertices between $u$ and $y$ use as a first edge $\ell_x$ and go through vertex $u$. 
+    Now using \cref{obs:FirstLabelAndDuration} it follows that we can determine labels on all edges between $u$ and $y$.
+
+    Denote now with $y'$ the neighbor of $y$ in $Q$, that is closer to $v$ than $u$. 
+    We know that we reach $y'$ starting from $x$ the fastest, when the path passes through vertex $v$.
+    There are two options how the fastest temporal path from $x$ to $y'$ departs from $x$. Either it first uses edge $\ell_x$ or edge $r_x$. 
+    Once we know which of these two options happens, we can determine all the labels on edges between $v$ and $y'$.
+
+    In total we have uniquely determined labels of all edges of $Q$, with respect to the labeling of edges in $P$ (\ie with respect to the label of the first edge on $P$), with the exception of edge $yy'$.
+\end{proof}
+
+\subsubsection*{Step 3(a) of the FPT algorithm}
 
@@
 To determine the correct label of edge $su$ we do the following.
-We find the vertex $v_i \in N_{G'}(u)$ that is the closest to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
+We find vertex $v_i \in N_{G'}(u)$ that is the closest to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
 We claim, that the path $P=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $(G, \lambda'')$.
@@
 since $v_i \neq v_j$, we need at least one more time-step (one more edge) to traverse from $v_i$ to reach $v_j$, so $d(P^) \geq D_{s,v_i} + 1$, and so $P^*$ cannot be faster than $P$.
-Since $P=(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of the edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
+Since $P=(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
 
@@
 	Let $\mathcal{P}_{u}^v$ be a set of all $P_3$ paths on $3$ vertices in $G$, of form $(v_1, v_2, u)$, where $v_1, v_2 \in V(G)$, \st $v_1 v_2, v_2 u \in E(G)$ and $d(v,v_1) < d(v,v_2) < d(v,u)$. 
-	Intuitively, we can imagine the set $\mathcal{P}_{u}^v$ as the set of all incoming temporal $P_3$ paths to the vertex $u$, with respect to starting from the vertex $v$.
+	Intuitively, we can imagine the set $\mathcal{P}_{u}^v$ as the set of all incoming temporal $P_3$ paths to vertex $u$, with respect to starting from vertex $v$.
 

### 2023-01-13 RealizingTemporalGraphs.tex
FPT algorithm proof first draft. Need to still add inside George's proof + introduce the definition of line segments.

@@
 In the following we prove that knowing the structure (the exact underlying path) of a fastest temporal path $P$, among two vertices of interest $u,v \in U$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ (with the exception of some constant number of edges), up to the label of the first edge.
+results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ (with the exception of some constant number of edges), with respect to the label of the first edge.
 
@@
 
-After finishing the second step of the FPT algorithm, labels on all edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined up to the label of the first edge.
+After finishing the second step of the FPT algorithm labels on all edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge.
 There may still be some edges in the graph, that are unlabeled. Note that these edges are exactly the ones that are not a part of any fastest temporal path.
@@
 
-From the above it follows that there are at most $f(k)$ (namely $O(|U|^2$) unlabeled paths in $G'$ after algorithm finishes step 2.
+From the above it follows that there are at most $f(k)$ (namely $O(|U|^2$) unlabeled paths in $G'$ after algorithm finishes Step 2.
 Now we want to extend the labeling from Step 2 to all unlabeled paths.
-To do this we want to relate the labeling of an unlabeled path to some fully labeled (\ie fastest temporal) path.
+To do this we want to relate the labeling of an unlabeled path to some labeled (\ie fastest temporal) path.
 Let us first observe some properties.
@@
 and at the end path must use either $\ell_x$ or $y_x$.
-Since this is true for any path (hence any temporal path), it holds also for the fastest temporal pathfrom $x$ to $y$.
+Since this is true for any path (hence any temporal path), it holds also for the fastest temporal path from $x$ to $y$.
 
@@
 Using the results from above we can now prove the following.
-\begin{lemma}
+\begin{lemma}\label{lem:FPT-DetermineLabelsOnUnlabeledNonFastestPaths}
     Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an unlabeled path in $G'$, between vertices of interest $u,v \in U$,
@@
     Let $P$ be such path that there exists a vertex $x \in P \setminus \{u,v\}$ of degree two (\ie $x \notin U$).
-    Then we can precisely determine the labels on every edge of $Q$, but one, up to the label $c_{u'v'}$ of the first edge of path $P$.
+    Then we can precisely determine the labels on every edge of $Q$, but one, with respect to the label $c_{u'v'}$ of the first edge of path $P$.
 \end{lemma}
@@
 
+Up to now we have determined the labels (the constraints for labels) of edges of $G'$. We will now extend the labeling to the initial graph $G$. 
+Recall, $G'$ was created from $G$ by iteratively removing all vertices of degree $1$ from $G$.
+
+Let $s \in V(G) \setminus V(G')$ be a vertex of degree one that was removed from $G$ at the beginning,
+and let $u$ be its neighbor in $G$.
+First, we can easily assume that $|N_{G'}(u)|\geq 1$.
+If this is not true then either $G$ is a star or $G'$ is disconnected and therefore also $G$ is disconnected, where $u$ is in a part of $G$ that forms a star.iteratively
+We can solve the problem for stars in polynomial time (see \cref{thm:deltaExact-PolyTimeTrees}).
+
+To determine the correct label of edge $su$ we use the following properties.
+\begin{claim}
+Let $v_i \in N_{G'}(u)$ be the closest vertex to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
+Then the path $P=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $G$.
+\end{claim}
+\begin{proof}
+Suppose that this is not true.
+Then there exists a faster path $P^*$ from $s$ to $v_i$, that goes through $u$ (as this is the only neighbor of $s$), through some other vertex $v_j \in N_{G'}(u) \setminus \{v_i \}$, 
+and through some other path $P'$ in $G$, before it finishes in $v_i$, where $P'$ is at least an edge (from $v_j$ to $v_i$). 
+Therefore $P^* = (s,u,v_j,P',v_i)$, where $d(P^*) \leq d(P)$.
+Now since $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$ the first part of path $P^*$ from $s$ to $v_j$ takes at least $D_{s,v_i}$ time.
+Since $v_i \neq v_j$ we need at least one more time-step (one more edge) to traverse from $v_i$ to reach $v_j$. 
+So $d(P^) \geq D_{s,v_i} + 1$, and so $P^*$ cannot be faster than $P$.
+\end{proof}
+
+Since $P=(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
+We repeat the above procedure for all degree one vertices in $G$, that we removed in Step 1, and we end up with the labeling $\lambda$ of the whole graph.
+
+\begin{comment}
+Now we have to make sure that all the new labels satisfy $D$, to do this we calculate the matrix $D'$ of fastest temporal paths among all pairs of vertices in $(G, \lambda)$ and compare the results with $D$, if any values differ, we stop and return a \textsc{No} answer, if $D = D'$ we return the labeling $\lambda$.
+
+To calculate $\lambda (s,v_i)$ we need $O(|N_{G'}(u)|) = O(n)$ time, therefore to calculate all labels of edges incident to vertices of degree one in $G$, we need $O(n^2)$ time, calculating $D'$ takes $O(n^3\log n)$ time (see \cref{lemma:calculatingD}), therefore the whole step is performed in polynomial time.
+\end{comment}
+%
+%
 \subsubsection*{Step 3(a) of the FPT algorithm}
-
-\subsection{Step 6 of the FPT algorithm}
-\todo[inline]{This section is wrong, we keep this here as we will use some of the ideas.}
-Let $\lambda$ be the labeling of $G'$, that satisfies $D'$.
-Let $s \in V(G) \setminus V(G')$, be a vertex of degree one, that was removed from $G$ in Step 1,
-and let $u$ be its neighbor in $G$.
-First, we can easily assume that $|N_{G'}(u)|\geq 1$, if this is not true, then either $G$ is a star or $G'$ is disconnected and therefore also $G$ is disconnected, where $u$ is in a part of $G$ that forms a star.
-We can solve the problem for stars in polynomial time (see \cref{thm:deltaExact-PolyTimeTrees}).
-
-To determine the correct label of edge $su$ we do the following.
-We find vertex $v_i \in N_{G'}(u)$ that is the closest to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
-We claim, that the path $P=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $(G, \lambda'')$.
-Suppose that is not true, then there exists a faster path $P^*$ from $s$ to $v_i$, that goes through $u$ (as this is the only neighbor of $s$), through some other vertex $v_j \in N_{G'}(u) \setminus \{v_i \}$, and through some other path $P'$ in $G$, before it finishes it $v_i$, where $P'$ is at least an edge (from $v_j$ to $v_i$).
-Therefore $P^* = (s,u,v_j,P',v_i)$, where $d(P^*) \leq d(P)$, now since $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$, the first part of path $P^*$ from $s$ to $v_j$ takes at least $D_{s,v_i}$ time,
-since $v_i \neq v_j$, we need at least one more time-step (one more edge) to traverse from $v_i$ to reach $v_j$, so $d(P^) \geq D_{s,v_i} + 1$, and so $P^*$ cannot be faster than $P$.
-Since $P=(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
-
-We repeat the above procedure for all degree one vertices in $G$, that we removed in Step 1, and we end up with the labeling $\lambda$ of the whole graph.
-Now we have to make sure that all the new labels satisfy $D$, to do this we calculate the matrix $D'$ of fastest temporal paths among all pairs of vertices in $(G, \lambda)$ and compare the results with $D$, if any values differ, we stop and return a \textit{NO} answer, if $D = D'$ we return the labeling $\lambda$.
-
-To calculate $\lambda (s,v_i)$ we need $O(|N_{G'}(u)|) = O(n)$ time, therefore to calculate all labels of edges incident to vertices of degree one in $G$, we need $O(n^2)$ time, calculating $D'$ takes $O(n^3\log n)$ time (see \cref{lemma:calculatingD}), therefore the whole step is performed in polynomial time.
+Using all of the above results we proceed in the following way.
+For a partial ILP instance $I$ we 
+select an inner vertex $x$ of every fastest temporal path among vertices of interest $u'$ and $v'$,
+and for every unlabeled path among vertices of interest $u$ and $v$ we find such $y$ and $y_1, y_2$ from this path, that $y$ is furthest away from $x$ and $y_1, y_2$ are its neighbors.
+We then enumerate $4$ possible ways that a fastest temporal path starts from $x$ and reaches $y$, 
+and then $2$ additional ways, how a fastest temporal path starts from $x$ to $y_1$ (resp.~$y_2$).
+For each of the possibilities we then precisely determine labels of the unlabeled path, up to the constant of the fastest $u',v'$ temporal path.
+
+Since there are at most $|U|^2$ fastest temporal paths among vertices of interest, we create at most $4|U|^2$ extra instances for each unlabeled path.
+Therefore one partial ILP instance $I$ is further extended into $O(|U|^3)=f(k)$ \todo{$O(2^k)$} final ILP instances $I_I$.
+
+\subsubsection*{Step 3(b) of the FPT algorithm}
+Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
+In the case when the input instance as a solution, algorithm also provids us with one.
+
+One final ILP instance $I_I$, that was built by our algorithm, has $f(k)$ variables. 
+Therefore one $I_I$ can be solved in FPT time with respect to $k$.
+
+We have build $f(k)$ different final ILP instances.
+If none of the instances is a \textsc{Yes} instance, then we conclude that there is no labeling $\lambda$ of $G$, that would satisfy the distances of the matrix $D$,
+and therefore $D$ is a \textsc{No} instance of \deltaExact.
+If there is a final ILP instance $I_I$, that is a \textsc{Yes} instance, then we take a solution $S$, provided by the algorithm from \cite{Lenstra1983Integer}, and determine the corresponding labeling $\lambda$ of $G$.
+Note, the minimum number of solutions of $I_I$ is at least $\delta$, since the graph is periodic and adding the same constant to every edge in the graph, dose not change the duration of any temporal path in $(G, \lambda)$.
 

### 2023-01-13 RealizingTemporalGraphs.tex
Final version _ 02 :)

@@
 \subsection{Step 1 of the FPT algorithm}
-In the first step of the algorithm we create an instance $D'$, with the underlying graph $G'$, from $D$ and $G$, by simply removing all the vertices of degree one from $G$ and their corresponding rows and columns from the matrix $D$.
+In the first step of the algorithm we create an instance $D'$, with the underlying graph $G'$, from $D$ and $G$, by iteratively removing vertices of degree one from $G$ and their corresponding rows and columns from the matrix $D$.
 This part is executed in $O(n+m)$ time.
@@
 
-Let $s \in V(G) \setminus V(G')$ be a vertex of degree one that was removed from $G$ at the beginning,
-and let $u$ be its neighbor in $G$.
-First, we can easily assume that $|N_{G'}(u)|\geq 1$.
-If this is not true then either $G$ is a star or $G'$ is disconnected and therefore also $G$ is disconnected, where $u$ is in a part of $G$ that forms a star.iteratively
-We can solve the problem for stars in polynomial time (see \cref{thm:deltaExact-PolyTimeTrees}).
-
-To determine the correct label of edge $su$ we use the following properties.
+Note that vertices from $V(G) \setminus V(G')$ form disjoint paths in $G$. 
+Each such path is incident to exactly one vertex from $G'$.
+
+Let $P' = (v_1, v_2, \dots, v_p=s)$ be a path in $G$ on vertices from $V(G) \setminus V(G')$  (\ie path on vertices that were removed from $G$)
+and let $u$ be a neighbor of $s$ in $G$,
+therefore $P=(v_1, v_2, \dots, v_p=s, u)$ is an induced path in $G$.
+First observe that $|N_{G'}(u)|\geq 1$, if not also $u$ would be removed from $G$ and $G$ would be a tree, for which we can solve the problem in polynomial time (see~\cref{thm:deltaExact-PolyTimeTrees}).
+
+To determine the correct label of all edges of $P$ we use the following property.
 \begin{claim}
+Let $P = (v_1, v_2, \dots, v_p=s)$ be a path in $G$ on vertices from $V(G) \setminus V(G')$
+and let $u$ be a neighbor of $s$ in $G$.
 Let $v_i \in N_{G'}(u)$ be the closest vertex to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
-Then the path $P=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $G$.
+Then the path $P^*=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $G$.
 \end{claim}
@@
 Suppose that this is not true.
-Then there exists a faster path $P^*$ from $s$ to $v_i$, that goes through $u$ (as this is the only neighbor of $s$), through some other vertex $v_j \in N_{G'}(u) \setminus \{v_i \}$, 
+Then there exists a faster path $P^*_2$ from $s$ to $v_i$, that goes through $u$ (as this is the only neighbor of $s$), through some other vertex $v_j \in N_{G'}(u) \setminus \{v_i \}$, 
 and through some other path $P'$ in $G$, before it finishes in $v_i$, where $P'$ is at least an edge (from $v_j$ to $v_i$). 
-Therefore $P^* = (s,u,v_j,P',v_i)$, where $d(P^*) \leq d(P)$.
-Now since $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$ the first part of path $P^*$ from $s$ to $v_j$ takes at least $D_{s,v_i}$ time.
+Therefore $P^*_2= (s,u,v_j,P',v_i)$, where $d(P^*_2) \leq d(P^*)$.
+Now since $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$ the first part of path $P^*_2$ from $s$ to $v_j$ takes at least $D_{s,v_i}$ time.
 Since $v_i \neq v_j$ we need at least one more time-step (one more edge) to traverse from $v_i$ to reach $v_j$. 
-So $d(P^) \geq D_{s,v_i} + 1$, and so $P^*$ cannot be faster than $P$.
-\end{proof}
-
-Since $P=(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
-We repeat the above procedure for all degree one vertices in $G$, that we removed in Step 1, and we end up with the labeling $\lambda$ of the whole graph.
+So $d(P^*) \geq D_{s,v_i} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
+\end{proof}
+
+Because $(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
+Since $P$ is a path, the fastest temporal path from all vertices of $P$ to $u$ is the temporal path along $P$, therefore using \cref{obs:FirstLabelAndDuration} and the value of the edge $su$, we can determine labels of all edges in $P$.
+
+We repeat the above procedure for paths in $G$ that we removed in Step 1, and we end up with the labeling $\lambda$ of the whole graph.
 

### 2023-01-17 RealizingTemporalGraphs.tex
Changes 17th january

@@
 Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
-Furthermore, $v$ has distance two from $x$ in the unlabeled graph $G$.
+Furthermore, $v$ has distance two from $x$ in the undetermined graph $G$.
 Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
@@
 
-\section{FPT and W[1]-hardness of exact realization}
+\section{FPT and W[1]-hardness of exact realization -- new version}
 In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
@@
 
-Before we start with the proof we fix the following notation. 
+Before we start with the proof of \cref{thm:FPTwrtFES} we fix the following notation. 
 Let $D$ be the input matrix of \deltaExact\ \ie
@@
 
-We now introduce an algorithm that determines the labeling of $G$, satisfying $D$, that runs in $f(k) \cdot \text{poly}(n)$ time.
+Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possible solutions.
+For example, let $u$ and $v$ be two vertices in a graph $G$. 
+We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
+This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
+and form multiple cases, 
+one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
+one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
+To correctly determine if the problem has a valid solution, we must check all cases.
+In each case we perform required calculations, 
+and we either come to the contradiction (meaning that the current guess was wrong) 
+or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
+
+Note that we can easily solve the \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
+But, this would create $f(n,m)$ guesses, and the running time of the algorithm would be too big.
+Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses.
+We solve each guess by creating an ILP instance with $f(k)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
+The ILP instance is a \textsc{Yes} instance if and only if $D$ is a \textsc{Yes} instance of \deltaExact.
+Moreover, from a positive solution of the ILP instance we can construct the desired labeling $\lambda$.
+Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
+Therefore we can solve our ILP instance in $f(k)$ time.
+
+We now introduce the algorithm, that determines the labeling of $G$, satisfying $D$, and runs in $f(k) \cdot \text{poly}(n)$ time.
 Our algorithm performs the following steps.
 \begin{enumerate}
-    \item Preprocessing on graph $G$. Determine the set $E$ of feedback edges and the set $U$ of vertices of interest, where $|E|, |U| \in O(k)$.
-    \item Guess the fastest temporal paths among vertices in $U$, for each guess create an ILP with variables corresponding to fastest temporal paths.
-    All in total create $f(k)$ partial ILP instances, each with $f(k)$ variables
-    \item For each partial ILP instance I:
+    \item Preprocessing on graph $G$.
+Determine the set $E$ of feedback edges, the set $U$ of vertices of interest and the set $U^*$ of neighbors of vertices of interest, where $|E|, |U|, |U^*| \in O(k)$.
+    \item Guess what are the fastest temporal paths among vertices in $U$ and 
+    what are the fastest temporal paths among the vertices in $U^*$, that are of some specific form.
     \begin{enumerate}
-        \item create $f(k)$ final instances $I_I$,
-        \item check if $I_I$ has a solution.
+        \item For each guess create an ILP instance $I$ with $f(k)$ variables.
+        \item Add constraints for all pairs of vertices.
     \end{enumerate}
+    \item Solve the ILP instance $I$ and check if a solution exists. In the positive case create its corresponding labeling $\lambda_I$ and check if it satisfies $D$.
+    All in total we create $f(k)$ partial ILP instances, each with $f(k)$ variables and $f(n)$ constraints.
 \end{enumerate}
-\begin{comment}
-\begin{enumerate}
-    \item Create $G'$ and $D'$ from $G$ and $D$ respectively, by removing all degree $1$ vertices from $G$ and $D$.
-    \item Compute a minimum feedback edge set $F$ in $G'$ (note, $F$ is also a minimum feedback edge set of $G$).
-    \item Determine vertices of interest $U$ of the graph $G'$.
-    \item \label{enum:FPT-labelingVerticesOfInterest} Guess the (partial) labeling $\lambda$ of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
-    \item \label{enum:FPT-labelingraphNoLeafs} Extend the partial labeling $\lambda$ to the labeling of the whole $G'$, respecting $D'$.
-    \item \label{enum:FPT-labelingWholeGraph} Extend the labeling $\lambda$ of $G'$ to the labeling of $G$, respecting $D$.
-\end{enumerate}
-
-It is important to point out, that in step~\ref{enum:FPT-labelingVerticesOfInterest}, our algorithm does not build a labeling satisfying conditions in this step,
-and then tries to extend it in steps~\ref{enum:FPT-labelingraphNoLeafs} and \ref{enum:FPT-labelingWholeGraph},
-but it
-builds (many different instances of) integer linear program (ILP) problem with $O(k)$ variables,
-with restrictions satisfying condition from steps~\ref{enum:FPT-labelingVerticesOfInterest}--\ref{enum:FPT-labelingWholeGraph}.
-At the end we solve the ILP problem on all instances and if there is a positive solution, it gives rise to the desired labeling $\lambda$ of $G$.
-For each of the steps we now argue its correctness and time complexity.
-\end{comment}
 
 \subsection{Step 1 of the FPT algorithm}
-In the first step of the algorithm we create an instance $D'$, with the underlying graph $G'$, from $D$ and $G$, by iteratively removing vertices of degree one from $G$ and their corresponding rows and columns from the matrix $D$.
-This part is executed in $O(n+m)$ time.
-
+From the underlying graph $G$ of $D$ we first create a graph $G'$ by
+iteratively removing vertices of degree one from $G$.
 Then we determine a minimum feedback edge set $F$ of $G'$ by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Lastly, we determine the set $U$ of \emph{vertices of interest}.
+Note that $F$ is also a minimum feedback edge set of the whole $G$.
+Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
 Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to some edges in $F$, and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$.
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ are incident to at least one edge in $F$,
+Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
+and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
+Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
 and $|V_3| \leq |V_1|$ by the properties of trees.
 We denote with $U = V_1 \cup V_2 \cup V_3$ the set of vertices of interest. It follows that $|U| \leq 4k$.
-We determine $F$ and $U$ in linear time.
+We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie $U^* = \{v \in V(G') \setminus U | u \in U, v \in N(u)\}$.
+Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $U^* \in O(k^2)$.
+
+The whole Step 1 is performed in $O(n + m)$ time.
 
 \subsection{Step 2 of the FPT algorithm}
-In this step we want to guess the structure of fastest paths (underlying paths) among all pairs of vertices of $U$. %and then determine their labeling.
+Let us denote with $Z$ the set of vertices removed from $G$ at the beginning of the algorithm, \ie $Z = V(G) \setminus V(G')$.
+By the construction it follows that $Z$ consists of disjoint trees. 
+Note that the fastest temporal paths among vertices of $G'$ are independent of vertices in $Z$.
+Let us remember the following basic property of the problem \deltaExact.
+A labeling $\lambda$ of $G$ satisfies $D$ if every fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$,
+and none other temporal path from $v_i$ to $v_j$ is faster.
+In order to find a labeling that satisfies this property we split our analysis in nine cases,
+where the first vertex is in one of the sets $U,V(G') \setminus U, Z$,
+and similarly the last vertex is in one of the sets $U,V(G') \setminus U, Z$.
+In each of these cases we guess the underlying path $P$ of the fastest temporal path from the vertex $v_i$ to $v_j$, 
+which results in one equality constraint for the labels on the path $P$. 
+For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
+This results in producing $f(n,m)$ constraints. We have to guarantee only, that the number of guesses, of faster temporal paths, is in $f(k)$ and not in $f(n)$.
+
+We start the algorithm by guessing the structure of 
+the fastest temporal paths (we guess the underlying paths) among all pairs of vertices of $U$. 
 For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$.
-Repeating this for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of fastest temporal paths among all vertices.
-
-Each partial ILP instance is connected to one list of specific fastest temporal paths among the vertices from $U$.
-From now on, for every par of vertices $u,v \in U$ we assume that we know exactly what is the underlying path of a fastest temporal path from $u$ to $v$.
-We describe now how to build a specific partial ILP instance from a specific list of fastest temporal paths.
+Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
+If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
+Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
+
+We now create one partial ILP instance for each guess of fastest temporal paths among the vertices from $U$,
+which we later on extend to $f(k)$ final ILP instances, after guessing some extra fastest temporal paths.
+From now on, for every pair of vertices $u,v \in U$ we assume that we know exactly what is the underlying path of a fastest temporal path from $u$ to $v$.
+
+For an easier understanding and the analysis of the algorithm we give the following definition.
+\begin{definition}
+    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
+    A path $P = (u=v_1,v_2, \dots, v_p = v)$ in $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
+    is called a \emph{segment}. Denote it with $S_{u,v}$.
+\end{definition}
+
+We describe now how to build one partial ILP instance from a specific list of fastest temporal paths.
 While building the ILP instances we exploit the following property greatly, that is why we state it as a separate observation.
@@
 
-In the following we prove that knowing the structure (the exact underlying path) of a fastest temporal path $P$, among two vertices of interest $u,v \in U$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ (with the exception of some constant number of edges), with respect to the label of the first edge.
-
-\begin{claim}
+In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$, from a vertex of interest $u$ to a vertex of interest $v$,
+results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
+(with the exception of some constant number of edges), with respect to the label of the first edge.
+More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges,
+and if $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges.
+For the exact formulation and proofs see \cref{claim:FPT-uv-Labelalledges,claim:FPT-uv-LabelAlmostalledges}.
+
+\begin{claim}\label{claim:FPT-uv-Labelalledges}
     Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
@@
 
-\begin{claim}
+\begin{claim}\label{claim:FPT-uv-LabelAlmostalledges}
     Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
@@
 or there exists a fastest temporal path $P' = (u, w_2, w_3, \dots, w_{p'} = v_i)$, for which $P \cap P' = \{u, v_i\}$.
-If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling the same as in previous case.
-So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD - George prooved it}
+If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{claim:FPT-uv-Labelalledges}.
+So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD - George proved it}
 \end{proof}
@@
 We use the above results in the following way.
-For all vertices of interest $u \in U$ and $v \in U \setminus \{v\}$, we know the underlying path $P_{u,v}$ of a fastest temporal path from $u$ to $v$. 
+Let $u, v \in U$ be two vertices of interest. 
+We know the underlying path $P_{u,v}$ of a fastest temporal path from $u$ to $v$. 
+Suppose that $P_{u,v}$ consist of $\ell$ segments $S_{u_i,v_i}$.
+Using \cref{claim:FPT-uv-LabelAlmostalledges} we determine the labels of all but $\ell -1$ edges on $P_{u,v}$, with respect to the value of the first edge.
+This equals to creating a constraint by setting the duration of the temporal path along $P_{u,v}$ to equal the value $D_{u,v}$.
+There are $f(k)$ different paths $P^i_{u,v}$ from $u$ to $v$ in $G$.
+We now have to iterate through all of them and add the constraint that the duration of $(P^i_{u,v}, \lambda)$ is greater or equal to $D_{u,v}$.
+We repeat the above procedure for all pairs of vertices in $U$.
+This results in producing $f(k)$ variables and constraints for our partial ILP.
+
+\begin{comment}
 We create a variable $c_{u,v}^{e_1} \in [\Delta]$ that corresponds to the label of the first edge of $P_{u,v}$ in $(G', \lambda')$ and potentially at most $\ell_{u,v}$ variables $c_{u,v}^{e_w} \in [\Delta]$ corresponding to
@@
 Repeating this procedure for all $u,v \in U$ creates at most $|U|^3 = O(k^3)$ new variables.
-
-\todo[inline]{Write example for variables and constrains this part produces.}
-
-\subsection{Step 3 of the FPT algorithm}
-
-After finishing the second step of the FPT algorithm labels on all edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge.
-There may still be some edges in the graph, that are unlabeled. Note that these edges are exactly the ones that are not a part of any fastest temporal path.
+\end{comment}
+\todo[inline]{Write examples for variables and constrains this part produces.}
+
+After finishing the previous step for all pairs of vertices in $U$,
+the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge.
+Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
+Note that these edges are exactly the ones that are not a part of any fastest temporal path.
 Let us first observe some properties of such edges.
@@
 \begin{claim}
-    Unlabeled edges form disjoint paths in $G'$, where each path $P$ starts and ends in some vertex of interest, 
-    \ie for every unlabeled path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+    Undetermined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
+    \ie for every undetermined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
 \end{claim}
-
 \begin{proof}
     We prove this claim in two steps.
-    First, all inner vertices of $P$, \ie vertices $v_i \in P \setminus \{u,v\}$ are of degree exactly $2$.
-They are of degree at least $2$ since they are on a path $P$ and are incident to two unlabeled edges in  $P$.
-    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter (sub)paths.
+    First, all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$.
+They are of degree at least $2$ since they are on a path $S$ and are incident to two undetermined edges in  $P$.
+    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
 
     Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
-As $u$ is the starting vertex of the unlabeled path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
+As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
     Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among some vertices of interest and $u$ would be an inner vertex on that path.
-    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one unlabeled edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
+    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
+
+    It follows that $P$ is a segment.
 \end{proof}
@@
 \begin{claim}
-    Among any pair of vertices of interest $u,v \in U$ there can be at most one unlabeled path $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+    Among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
 \end{claim}
 \begin{proof}
-    Suppose for the contradiction that there are two unlabeled paths among $u,v \in U$.
-    Denote them with $P$ and $P'$. 
-    Then $C = P \cup P'$ form a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
-   Since $C$ is a cycle, at least one of it's edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
+   Suppose for the contradiction that there are two undetermined segments among $u,v \in U$.
+   Denote them with $S_{u,v}$ and $S'_{u,v}$. 
+   Then $C = S_{u,v} \cup S_{u,v}'$ form a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
+   Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
    both endpoints of $e$ have to be in $U$.
-   So $P$ and $P'$ cannot be both fully unlabeled.
-\end{proof}
-
-From the above it follows that there are at most $f(k)$ (namely $O(|U|^2$) unlabeled paths in $G'$ after algorithm finishes Step 2.
-Now we want to extend the labeling from Step 2 to all unlabeled paths.
-To do this we want to relate the labeling of an unlabeled path to some labeled (\ie fastest temporal) path.
+   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
+\end{proof}
+
+From the above it follows that there are at most $f(k)$ (namely $O(|U|^2$) undetermined segments in $G'$ after algorithm finishes going through fastest temporal paths among vertices of interest.
+
+We now continue with guessing fastest temporal paths among all vertices in $U^*$, 
+which by similar arguing as for vertices in $U$, gives us $O(k^{k^6})$ guesses.
+Besides that we also guess fastest temporal paths of the following form.
+Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
+first one between vertices $u,v \in U$, second one between vertices $w, z \in U$, 
+where the first one includes $v_2, v_{p-1} \in U^*$, 
+and the second one includes $z_2, z_{p-1} \in U^*$.
+We want to guess the underlying paths of the fastest temporal paths from $v_2$ to $z_2$,
+where the first path goes 
+from $v_2$, through $u$, through $w$ and then to $z_2$,
+and the second one goes
+from $v_2$, through $u$, through $z$ and then to $z_2$.
+And two similar paths from $v_2$ to $z_{p-1}$.
+We repeat this procedure for all pairs of segments and all vertices from $U^*$ in those segments.
+There are $f(k)$ possible paths of this form, since there are $f(k)$ segments in $G'$.
+All together we made $f(k)$ new guesses for the structure of the fastest temporal paths.
+Each of the previous partial ILP instances is therefore extended into $f(k)$ new ILP instances.
+
+We now do the following.
+Let $S^i_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, let us
+fix a vertex $v_i \in S^i_{u,v} \setminus \{u,v\}$.
+Let 
+$S^j_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segments in $G'$.
+Now we check the matrix $D$ and determine which vertex $z_j \in S^j_{w,z} \setminus \{w,z\}$ 
+has the biggest value $D_{v_i,z_j}$.
+Let us call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
+Denote with $z_{j-1}$ and $z_{j-1}$
+
 Let us first observe some properties.
 
-Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an unlabeled path in $G'$, between vertices of interest $u,v \in U$,
+Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an undetermined segment in $G'$, between vertices of interest $u,v \in U$,
 let $P$ be the underlying path of a fastest temporal path from $u',v' \in U$.
@@
 \begin{lemma}\label{lem:FPT-DetermineLabelsOnUnlabeledNonFastestPaths}
-    Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an unlabeled path in $G'$, between vertices of interest $u,v \in U$,
+    Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an undetermined segment in $G'$, between vertices of interest $u,v \in U$,
     let $P$ be the underlying path of a fastest temporal path from $u',v' \in U$.
@@
 select an inner vertex $x$ of every fastest temporal path among vertices of interest $u'$ and $v'$,
-and for every unlabeled path among vertices of interest $u$ and $v$ we find such $y$ and $y_1, y_2$ from this path, that $y$ is furthest away from $x$ and $y_1, y_2$ are its neighbors.
+and for every endetermined path among vertices of interest $u$ and $v$ we find such $y$ and $y_1, y_2$ from this path, that $y$ is furthest away from $x$ and $y_1, y_2$ are its neighbors.
 We then enumerate $4$ possible ways that a fastest temporal path starts from $x$ and reaches $y$, 
 and then $2$ additional ways, how a fastest temporal path starts from $x$ to $y_1$ (resp.~$y_2$).
-For each of the possibilities we then precisely determine labels of the unlabeled path, up to the constant of the fastest $u',v'$ temporal path.
-
-Since there are at most $|U|^2$ fastest temporal paths among vertices of interest, we create at most $4|U|^2$ extra instances for each unlabeled path.
+For each of the possibilities we then precisely determine labels of the undetermined path, up to the constant of the fastest $u',v'$ temporal path.
+
+Since there are at most $|U|^2$ fastest temporal paths among vertices of interest, we create at most $4|U|^2$ extra instances for each undetermined path.
 Therefore one partial ILP instance $I$ is further extended into $O(|U|^3)=f(k)$ \todo{$O(2^k)$} final ILP instances $I_I$.
@@
 Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-In the case when the input instance as a solution, algorithm also provids us with one.
+In the case when the input instance has a solution, algorithm also provides us with one.
 

### 2023-01-18 RealizingTemporalGraphs.tex
Changes, Tuesday 17th January

@@
 Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore we can solve our ILP instance in $f(k)$ time.
+Therefore we can solve each of our ILP instances in $f(k)$ time.
 
@@
 Using \cref{claim:FPT-uv-LabelAlmostalledges} we determine the labels of all but $\ell -1$ edges on $P_{u,v}$, with respect to the value of the first edge.
-This equals to creating a constraint by setting the duration of the temporal path along $P_{u,v}$ to equal the value $D_{u,v}$.
-There are $f(k)$ different paths $P^i_{u,v}$ from $u$ to $v$ in $G$.
+This results in creating one constraint, by setting the duration of the temporal path along $P_{u,v}$ to be equal to the value $D_{u,v}$.
+There are $O(k^k)$ different paths $P^i_{u,v}$ from $u$ to $v$ in $G$.
 We now have to iterate through all of them and add the constraint that the duration of $(P^i_{u,v}, \lambda)$ is greater or equal to $D_{u,v}$.
 We repeat the above procedure for all pairs of vertices in $U$.
-This results in producing $f(k)$ variables and constraints for our partial ILP.
+This results in producing $O(k^{k^3})$ variables and constraints to our partial ILP.
 
@@
 
-    It follows that $P$ is a segment.
+    From all of the above, it follows that $P$ is a segment in $G'$.
 \end{proof}
@@
 
-From the above it follows that there are at most $f(k)$ (namely $O(|U|^2$) undetermined segments in $G'$ after algorithm finishes going through fastest temporal paths among vertices of interest.
+From the above it follows that there are at most $O(|U|^2$) undetermined segments in $G'$ after algorithm finishes going through fastest temporal paths among vertices of interest.
 
@@
 We repeat this procedure for all pairs of segments and all vertices from $U^*$ in those segments.
-There are $f(k)$ possible paths of this form, since there are $f(k)$ segments in $G'$.
-All together we made $f(k)$ new guesses for the structure of the fastest temporal paths.
-Each of the previous partial ILP instances is therefore extended into $f(k)$ new ILP instances.
+Since there are $O(k^3)$ segments in $G'$,
+there are $O(k^6)$ possible paths of this form.
+Lastly,
+for a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
+and a vertex of interest $w \in U$,
+we guess the underlying paths of the fastest temporal paths from $w$ to $v_2$, through $u$ and through $v$.
+Besides that we guess the underlying paths of the fastest temporal paths from $v_2$ to $w$ through $u$ and through $v$.
+For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(4 k^k)$ different possible such paths, therefore we make $O(k^6)$ guesses for these paths.
+All together we made $O(k^6)$ new guesses for the structure of all of the above mentioned fastest temporal paths.
+Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
 
@@
 $S^j_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segments in $G'$.
-Now we check the matrix $D$ and determine which vertex $z_j \in S^j_{w,z} \setminus \{w,z\}$ 
-has the biggest value $D_{v_i,z_j}$.
-Let us call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-Denote with $z_{j-1}$ and $z_{j-1}$
-
+Note that all inner vertices of $S^j_{w,z}$ (\ie vertices in $S^j_{w,z} \setminus \{w,z\}$)
+can be reached from $v_i$ by some path that has to go through $w$ oz $z$.
+In fact, this is true for all paths starting in any vertex not in $S^j_{w,z}$.
+Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
+the segment
+$S^j_{w,z}$ have to increase up to the certain point, when traversing the segment coming through $w$ and coming through $z$.
+Namely,
+let $z_j \in S^j_{w,z} \setminus \{w,z\}$ be the vertex with the biggest value $D_{v_i,z_j}$,
+we call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
+Then $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
+$D_{v_i,z_{p-1}} < D_{v_i,z_{p-2}} < \dots < D_{v_i,z_j}$.
+From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
+and 
+the fastest temporal paths from $v_i$ to $z_{p-1}, z_{p-2}, \dots, z_{j+1}$ go through $z$.
+We now have to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
+Similarly,
+all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
+which also gives us two extra guesses for the underlying path of the fastest temporal path from $v_i$ to $z_j$.
+Therefore, all together we have $4$ possibilities on how the underlying path of the fastest temporal path from $v_i$ to $z_j$ 
+starts and ends.
+For a fixed $S^i_{u,v}, v_i$ and $S^j_{w,z}$ we can find the vertex $z_j$ in polynomial time, 
+or determine that this kind of vertex does not exist.
+We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$.
+We repeat this procedure for all pairs of segments,
+which results in producing $O(k^6)$ new guesses.
+
+Before we can use the above information, let us first prove the following properties.
+\begin{claim}\label{claim:FPT-unlabeldPaths-01}
+    Suppose that
+    $S^i_{u,v}, S^j_{w,z}$ are two segments with $ v_i \in S^i_{u,v}$ and $z_j \in S^j_{w,z}$,
+    where $z_j$ is a split vertex of $v_i$ in the segment $S^j_{w,z}$.
+    Suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
+    Then the fastest temporal path from $v_i$ to any other vertex of $S^j_{w,z}$, that is closer to $w$,
+    travels through the same two vertices $u$ and $w$.
+    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or $z,v$.
+\end{claim}
+\begin{proof}
+    Let $z_\ell$ be a vertex of $S^j_{w,z}$, that is closer to $w$ than $z$ in the segment.
+    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
+    Denote with $P_{v_i,z_j}^\ell$
+    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
+    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
+    Let us observe the following possibilities.
+    \\
+    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
+    Denote this path as $P^1_{v_i,z_\ell}$.
+    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
+    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
+    \\
+    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
+    Denote this path as $P^2_{v_i,z_\ell}$.
+    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}^j$ from the vertex $w$ to $z_ell$.
+    Therefore since
+    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
+    and since there is unique way to
+    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
+    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
+    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
+    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
+    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
+    \\
+    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
+    Denote this path as $P^3_{v_i,z_\ell}$.
+    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
+\end{proof}
+
+We proceed with adding constraints to our ILP instance, by iterating through all pairs of vertices.
+We already studied the case of fastest paths starting and ending in a vertex of $U$,
+so now we have to study all other cases.
+
+Let us start with the case of determining the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
+We have two possibilities:
+\begin{enumerate}[(i)]
+    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$.
+    Suppose that $x$ lies on a segment $S_{w,z}$.
+    Then by \cref{claim:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$,
+    which hast to be of the duration $D_{u,x}$. This results in adding an equality constraint to our ILP.
+    We now have to iterate through all others temporal paths from $u$ to $x$ and add the constraint to ILP that states that their duration is not smaller than the value $D_{u,x}$.
+    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
+    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
+    Therefore we add $O(k^k)$ inequality constraints for all these paths.
+
+    \item Vertex $x$ is not on a fastest temporal paths from $u$ to any $v \in U$.
+    Suppose that $x$ lies on a segment $S_{w,z} = (w,z_1,2_3, \dots, z_p, z)$.
+    Since we know the underlying path of the fastest temporal path from $u$ to $z_1$ through $w$ and from $u$ to $z_p$ through $z$,
+    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
+    This is done,
+    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
+    and determining the split vertex $w^*$ from $u$ on the segment $S_{w,z}$.
+    If $x \neq w^*$, we know which part of the segment is used to reach $x$.
+    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
+    (\ie paths from $u$ to $z$ and then to $x$, and paths from $u$ to $w$ and then to $x$),
+    we add the inequalities constraints.
+    If $x = w^*$, we have two possibilities, we check the values of each one and set the minimum of them, to equal the $D_{u,x}$ (if possible, if one is to small we immediately reject),
+    and again set all other possibilities to the inequality constraint.
+    There are $O(k^3)$ different paths from $u$ to $w$ (resp.~$z$), therefore we add $O(k^k)$ inequality constraints for all these paths.   
+\end{enumerate}
+
+Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
+
+Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
+
+\bibliography{bibliography}
+
+\clearpage
+
+\appendix
+
+\section{FPT, Old proof -- need to move useful stuff above}
 Let us first observe some properties.
@@
 
-\begin{claim}\label{claim:FPT-unlabeldPaths-01}
+\begin{claim}\label{claim:FPT-unlabeldPaths-012}
     Suppose that the fastest temporal path from $x$ to $y$ uses at the beginning edge $\ell_x$.
@@
 Note, the minimum number of solutions of $I_I$ is at least $\delta$, since the graph is periodic and adding the same constant to every edge in the graph, dose not change the duration of any temporal path in $(G, \lambda)$.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-01-19 RealizingTemporalGraphs.tex
Changes Wednesday 18th of Jan

@@
 
+    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
+    \begin{observation}\label{obs:durationPwithWaitingTimes}
+        Let $P = (v_0, v_1, \dots, v_p)$ be the temporal path from $v_0$ to $v_p$..
+        Then $d(P) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
+    \end{observation}
+    \begin{proof}
+        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
+        Then
+        \begin{align*}
+        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
+        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
+        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
+        & = t_{p-1} - t_1 + 1\\
+        & = d(P)
+        \end{align*}
+        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
+        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
+    \end{proof}
+    We also get the following.
     \begin{observation}\label{obs:travel-delays-both-directions}
@@
 Note that we can easily solve the \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-But, this would create $f(n,m)$ guesses, and the running time of the algorithm would be too big.
+But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function), and the running time of the algorithm would be too big.
 Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses.
-We solve each guess by creating an ILP instance with $f(k)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
+We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
 The ILP instance is a \textsc{Yes} instance if and only if $D$ is a \textsc{Yes} instance of \deltaExact.
@@
 Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore we can solve each of our ILP instances in $f(k)$ time.
+Therefore we can solve each of our ILP instances in FPT time with respect to $k$.
 
@@
     \item Solve the ILP instance $I$ and check if a solution exists. In the positive case create its corresponding labeling $\lambda_I$ and check if it satisfies $D$.
-    All in total we create $f(k)$ partial ILP instances, each with $f(k)$ variables and $f(n)$ constraints.
+    All in total we create $f(k)$ partial ILP instances, each with $f(k)$ variables and $O(n^c)$ constraints.
 \end{enumerate}
 
-\subsection{Step 1 of the FPT algorithm}
+\subsection{Preprocessing of the input}
 From the underlying graph $G$ of $D$ we first create a graph $G'$ by
@@
 
-\subsection{Step 2 of the FPT algorithm}
 Let us denote with $Z$ the set of vertices removed from $G$ at the beginning of the algorithm, \ie $Z = V(G) \setminus V(G')$.
@@
 For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $f(n,m)$ constraints. We have to guarantee only, that the number of guesses, of faster temporal paths, is in $f(k)$ and not in $f(n)$.
-
-We start the algorithm by guessing the structure of 
-the fastest temporal paths (we guess the underlying paths) among all pairs of vertices of $U$. 
-For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-
-We now create one partial ILP instance for each guess of fastest temporal paths among the vertices from $U$,
-which we later on extend to $f(k)$ final ILP instances, after guessing some extra fastest temporal paths.
-From now on, for every pair of vertices $u,v \in U$ we assume that we know exactly what is the underlying path of a fastest temporal path from $u$ to $v$.
+This results in producing $poly(n,m)$ constraints. We have to guarantee only, that the number of guesses, of faster temporal paths, is exponential in $k$ and not in $n$.
 
@@
 \end{definition}
-
-We describe now how to build one partial ILP instance from a specific list of fastest temporal paths.
-While building the ILP instances we exploit the following property greatly, that is why we state it as a separate observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P)$ of $P$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}. Since the duration of $P$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$, from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges,
-and if $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges.
-For the exact formulation and proofs see \cref{claim:FPT-uv-Labelalledges,claim:FPT-uv-LabelAlmostalledges}.
-
-\begin{claim}\label{claim:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
-    such that the labeling $\lambda$ respects $D'$.
-\end{claim}
-
-\begin{proof}
-In this case we get that all other vertices in $P$ are reached from $u$ using a (sub)path of $P$.
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 + (v,v_{p-1}, \dots, v_i) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the first label of $P$ to be a constant $c_{uv}$.
-This gives us a unique label for each edge of $P$, that depends on the value $c_{u,v}$.
-\end{proof}
-
-\begin{claim}\label{claim:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
-    such that the labeling $\lambda$ respects $D'$.
-    Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
-\end{claim}
-
-\begin{proof}
-We denote with $v_i \in U$ a vertex of interest in $P \setminus \{u,v\}$.
-There are two options, either $v_i$ is reached from $u$ using the subpath $P_i = (u, v_2, v_3, \dots, v_i)$ of $P$,
-or there exists a fastest temporal path $P' = (u, w_2, w_3, \dots, w_{p'} = v_i)$, for which $P \cap P' = \{u, v_i\}$.
-If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{claim:FPT-uv-Labelalledges}.
-So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD - George proved it}
-\end{proof}
-
-We use the above results in the following way.
-Let $u, v \in U$ be two vertices of interest. 
-We know the underlying path $P_{u,v}$ of a fastest temporal path from $u$ to $v$. 
-Suppose that $P_{u,v}$ consist of $\ell$ segments $S_{u_i,v_i}$.
-Using \cref{claim:FPT-uv-LabelAlmostalledges} we determine the labels of all but $\ell -1$ edges on $P_{u,v}$, with respect to the value of the first edge.
-This results in creating one constraint, by setting the duration of the temporal path along $P_{u,v}$ to be equal to the value $D_{u,v}$.
-There are $O(k^k)$ different paths $P^i_{u,v}$ from $u$ to $v$ in $G$.
-We now have to iterate through all of them and add the constraint that the duration of $(P^i_{u,v}, \lambda)$ is greater or equal to $D_{u,v}$.
-We repeat the above procedure for all pairs of vertices in $U$.
-This results in producing $O(k^{k^3})$ variables and constraints to our partial ILP.
-
-\begin{comment}
-We create a variable $c_{u,v}^{e_1} \in [\Delta]$ that corresponds to the label of the first edge of $P_{u,v}$ in $(G', \lambda')$ and potentially at most $\ell_{u,v}$ variables $c_{u,v}^{e_w} \in [\Delta]$ corresponding to
-labels of edges $e_w \in P_{u,v}$ that are incident to a vertex of interest $w$, for which the underlying path $P_{u,w}$ of a fastest temporal path from $u$ to $w$ intersects $P_{u,v}$ only in vertices $u$ and $w$.
-Labels on all other edges of $P_{u,v}$ are determined exactly, in relation to the constant $c_{u,v}^{e_1}$.
-Repeating this procedure for all $u,v \in U$ creates at most $|U|^3 = O(k^3)$ new variables.
-\end{comment}
-\todo[inline]{Write examples for variables and constrains this part produces.}
-
-After finishing the previous step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge.
-Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
-Note that these edges are exactly the ones that are not a part of any fastest temporal path.
-Let us first observe some properties of such edges.
-
-\todo[inline]{Fix the following proof, add more details/definitions to the introduction.}
-\begin{claim}
-    Undetermined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
-    \ie for every undetermined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
-\end{claim}
-\begin{proof}
-    We prove this claim in two steps.
-    First, all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$.
-They are of degree at least $2$ since they are on a path $S$ and are incident to two undetermined edges in  $P$.
-    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
-
-    Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
-As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
-    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among some vertices of interest and $u$ would be an inner vertex on that path.
-    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
-
-    From all of the above, it follows that $P$ is a segment in $G'$.
-\end{proof}
-
-\begin{claim}
-    Among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
-\end{claim}
-\begin{proof}
-   Suppose for the contradiction that there are two undetermined segments among $u,v \in U$.
-   Denote them with $S_{u,v}$ and $S'_{u,v}$. 
-   Then $C = S_{u,v} \cup S_{u,v}'$ form a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
-   Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
-   both endpoints of $e$ have to be in $U$.
-   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
-\end{proof}
-
-From the above it follows that there are at most $O(|U|^2$) undetermined segments in $G'$ after algorithm finishes going through fastest temporal paths among vertices of interest.
-
-We now continue with guessing fastest temporal paths among all vertices in $U^*$, 
+From the definition it follows, that there are exactly $k^2$ segments in $G'$.
+Observe also that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
+%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
+
+\subsection{Creating ILP instances and determining variables}
+For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
+Each vertex of interest is incident to at most $k$ such edges, therefore we create $O(k^3)$ variables.
+We start the algorithm by guessing necessary structures.
+Note, whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of the fastest temporal path among those two vertices.
+In the case when we want to guess the fastest path from $u$ to $v$, that passes through the vertex $x$ we write it as a fastest path of form $u \rightarrow x \rightarrow v$.
+We guess the following structures.
+\begin{enumerate}
+    \item The fastest temporal paths among all pairs of vertices of $U$.
+    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
+    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
+    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
+    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
+    \item The fastest temporal paths among all vertices in $U^*$, 
     which by similar arguing as for vertices in $U$, gives us $O(k^{k^6})$ guesses.
-Besides that we also guess fastest temporal paths of the following form.
-Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
+    \item The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
+    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
+    This gives us $O(k^{k^5})$ guesses.
+    \item Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
     first one between vertices $u,v \in U$, second one between vertices $w, z \in U$, 
@@
     and the second one includes $z_2, z_{p-1} \in U^*$.
-We want to guess the underlying paths of the fastest temporal paths from $v_2$ to $z_2$,
-where the first path goes 
-from $v_2$, through $u$, through $w$ and then to $z_2$,
-and the second one goes
-from $v_2$, through $u$, through $z$ and then to $z_2$.
-And two similar paths from $v_2$ to $z_{p-1}$.
+    We want to guess the following fastest temporal paths
+    $v_2 \rightarrow u \rightarrow w \rightarrow z_2$,
+    $v_2 \rightarrow u \rightarrow z \rightarrow z_2$,
+    $v_2 \rightarrow u \rightarrow w \rightarrow z_{r-1}$ and
+    $v_2 \rightarrow u \rightarrow z \rightarrow z_{r-1}$.
     We repeat this procedure for all pairs of segments and all vertices from $U^*$ in those segments.
@@
     there are $O(k^6)$ possible paths of this form.
-Lastly,
-for a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
+    \item For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
     and a vertex of interest $w \in U$,
-we guess the underlying paths of the fastest temporal paths from $w$ to $v_2$, through $u$ and through $v$.
-Besides that we guess the underlying paths of the fastest temporal paths from $v_2$ to $w$ through $u$ and through $v$.
+    we guess the following fastest temporal paths
+    $w \rightarrow u \rightarrow v_2$, $w \rightarrow v \rightarrow v_2$,
+    and
+    $v_2 \rightarrow u \rightarrow w$, $v_2 \rightarrow v \rightarrow w$.
+    \\
     For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(4 k^k)$ different possible such paths, therefore we make $O(k^6)$ guesses for these paths.
     All together we made $O(k^6)$ new guesses for the structure of all of the above mentioned fastest temporal paths.
-Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-
-We now do the following.
-Let $S^i_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, let us
-fix a vertex $v_i \in S^i_{u,v} \setminus \{u,v\}$.
+%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
+    \item 
+    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
+    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
     Let 
-$S^j_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segments in $G'$.
-Note that all inner vertices of $S^j_{w,z}$ (\ie vertices in $S^j_{w,z} \setminus \{w,z\}$)
+    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segments in $G'$.
+    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
     can be reached from $v_i$ by some path that has to go through $w$ oz $z$.
-In fact, this is true for all paths starting in any vertex not in $S^j_{w,z}$.
+    In fact, this is true for all paths starting in any vertex not in $S_{w,z}$.
     Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
     the segment
-$S^j_{w,z}$ have to increase up to the certain point, when traversing the segment coming through $w$ and coming through $z$.
+    $S_{w,z}$ have to increase up to the certain point, when traversing the segment coming through $w$ and coming through $z$.
     Namely,
-let $z_j \in S^j_{w,z} \setminus \{w,z\}$ be the vertex with the biggest value $D_{v_i,z_j}$,
+    let $z_j \in S_{w,z} \setminus \{w,z\}$ be the vertex with the biggest value  $D_{v_i,z_j}$,
     we call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
@@
     all fastest temporal paths starting at $v_i$ have to go either through $u$ or   through $v$,
-which also gives us two extra guesses for the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-Therefore, all together we have $4$ possibilities on how the underlying path of the fastest temporal path from $v_i$ to $z_j$ 
-starts and ends.
-For a fixed $S^i_{u,v}, v_i$ and $S^j_{w,z}$ we can find the vertex $z_j$ in polynomial time, 
+    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
+    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
+    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in    polynomial time, 
     or determine that this kind of vertex does not exist.
@@
     which results in producing $O(k^6)$ new guesses.
-
-Before we can use the above information, let us first prove the following properties.
+    \item At the end we also guess the permutation of all $O(k^3)$ variables, \ie for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$.
+    This results in $O(k^k)$ guesses.
+\end{enumerate}
+We create all of the guesses iteratively.
+We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^6})$ new ones, that respond to the guessing in the second step, etc.
+After creating all of the guesses we end up with exponential in $k$ different cases.
+We now create one partial ILP instance for each case.
+From now on we assume that we know exactly the structure of all paths we have guessed and the permutation of all variables.
+
+\subsection{Properties of 
+\texorpdfstring{\deltaExact } {Simple Delta-TGR}
+}
+
+In this section we study the properties of our problem, that then help us creating constraints of our ILP.
+In our analysis we exploit the following greatly, that is why we state is as an observation.
+
+\begin{observation}\label{obs:FirstLabelAndDuration}
+    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
+    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
+    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
+\end{observation}
+The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
+Since the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
+where the label of last edge is considered with some delta periods,
+\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
+Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
+
+In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$, from a vertex of interest $u$ to a vertex of interest $v$,
+results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
+(with the exception of some constant number of edges), with respect to the label of the first edge.
+More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges,
+and if $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges.
+For the exact formulation and proofs see \cref{claim:FPT-uv-Labelalledges,claim:FPT-uv-LabelAlmostalledges}.
+
+\begin{claim}\label{claim:FPT-uv-Labelalledges}
+    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
+    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
+    Moreover suppose also that $P$ is a segment.
+    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
+    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
+    %such that the labeling $\lambda$ respects $D'$.
+\end{claim}
+
+\begin{proof}
+We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
+To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$.
+Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
+Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
+and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
+But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 + (v,v_{p-1}, \dots, v_i) > d(P) > d(P_i)$.
+
+Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
+therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
+where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
+we set the first label of $P$ to be a constant $c_{uv}$.
+This gives us a unique label for each edge of $P$, that depends on the value $c_{u,v}$.
+\end{proof}
+
+\begin{claim}\label{claim:FPT-uv-LabelAlmostalledges}
+    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
+    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
+    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
+    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
+    such that the labeling $\lambda$ respects $D'$.
+    Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
+\end{claim}
+
+\begin{proof}
+We denote with $v_i \in U$ a vertex of interest in $P \setminus \{u,v\}$.
+There are two options, either $v_i$ is reached from $u$ using the subpath $P_i = (u, v_2, v_3, \dots, v_i)$ of $P$,
+or there exists a fastest temporal path $P' = (u, w_2, w_3, \dots, w_{p'} = v_i)$, for which $P \cap P' = \{u, v_i\}$.
+If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{claim:FPT-uv-Labelalledges}.
+So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD - George proved it}
+\end{proof}
+
+%Observe also the following.
+
 \begin{claim}\label{claim:FPT-unlabeldPaths-01}
     Suppose that
-    $S^i_{u,v}, S^j_{w,z}$ are two segments with $ v_i \in S^i_{u,v}$ and $z_j \in S^j_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S^j_{w,z}$.
+    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
+    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
     Suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S^j_{w,z}$, that is closer to $w$,
+    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
     travels through the same two vertices $u$ and $w$.
@@
 \begin{proof}
-    Let $z_\ell$ be a vertex of $S^j_{w,z}$, that is closer to $w$ than $z$ in the segment.
+    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
     Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
@@
     Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}^j$ from the vertex $w$ to $z_ell$.
+    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_ell$.
     Therefore since
@@
 
+\subsection{Adding constraints to the ILP}
 We proceed with adding constraints to our ILP instance, by iterating through all pairs of vertices.
+We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
+Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
+and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
+Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
+Using \cref{obs:durationPwithWaitingTimes}
+we create an \emph{equality constraint} for $P$
+of the form 
+\begin{equation}\label{eq:FPT-equalityConstraint}
+    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
+\end{equation}
+and an \emph{inequality constraint} for $Q$ 
+\begin{equation}\label{eq:FPT-inequalityConstraint}
+    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
+\end{equation}
+In both cases we implicitly assume that if the difference is smaller than zero we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
+
+First case we observe is the case when we want to determine the labels on fastest paths from $u$ to $v$, where $u,v \in U$.
+
+After finishing the previous step for all pairs of vertices in $U$,
+the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge.
+Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
+Note that these edges are exactly the ones that are not a part of any fastest temporal path.
+Let us first observe some properties of such edges.
+
+\todo[inline]{Fix the following proof, add more details/definitions to the introduction.}
+\begin{claim}
+    Undetermined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
+    \ie for every undetermined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+\end{claim}
+\begin{proof}
+    We prove this claim in two steps.
+    First, all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$.
+They are of degree at least $2$ since they are on a path $S$ and are incident to two undetermined edges in  $P$.
+    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
+
+    Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
+As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
+    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among some vertices of interest and $u$ would be an inner vertex on that path.
+    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
+
+    From all of the above, it follows that $P$ is a segment in $G'$.
+\end{proof}
+
+\begin{claim}
+    Among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+\end{claim}
+\begin{proof}
+   Suppose for the contradiction that there are two undetermined segments among $u,v \in U$.
+   Denote them with $S_{u,v}$ and $S'_{u,v}$. 
+   Then $C = S_{u,v} \cup S_{u,v}'$ form a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
+   Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
+   both endpoints of $e$ have to be in $U$.
+   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
+\end{proof}
+
+From the above it follows that there are at most $O(|U|^2$) undetermined segments in $G'$ after algorithm finishes going through fastest temporal paths among vertices of interest.
+
 We already studied the case of fastest paths starting and ending in a vertex of $U$,

### 2023-01-20 RealizingTemporalGraphs.tex
Changes Friday 20th of January

@@
 \end{definition}
-From the definition it follows, that there are exactly $k^2$ segments in $G'$.
+From the definition it follows, that there are $O(k^2)$ segments in $G'$.
 Observe also that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
@@
 %Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item 
+    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
     Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
@@
     Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segments in $G'$.
+    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
     Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
@@
     the fastest temporal paths from $v_i$ to $z_{p-1}, z_{p-2}, \dots, z_{j+1}$ go through $z$.
-    We now have to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
+    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
     Similarly,
@@
     Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
+    Besides that we want to guess also hot the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
+    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
+    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
+    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
+    This introduces two extra guesses.
     For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
     or determine that this kind of vertex does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$.
+    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
+    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
     We repeat this procedure for all pairs of segments,
@@
 \end{equation}
-In both cases we implicitly assume that if the difference is smaller than zero we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-
-First case we observe is the case when we want to determine the labels on fastest paths from $u$ to $v$, where $u,v \in U$.
+In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is smaller than zero, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
+In \emph{TODO: claim ???}\todo{TBD} we prove that for any two consecutive edges we know if the difference of labels is positive or negative, therefore we know when $\Delta$ has to be added.
+
+First case we observe is the case when we want to determine the labels on fastest temporal paths among vertices of interest.
+We proceed in the following way.
+Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
+If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-Labelalledges}).
+%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
+In the case when $P{_u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
+In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
+%Since there are $\ell - 1$ edge labels that are not determined with respect to the label of the first edge, may be some  TODO from above??
 
 After finishing the previous step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge.
+the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
 Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
-Note that these edges are exactly the ones that are not a part of any fastest temporal path.
+If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a variable $x_e$.
+Note that the undetermined edges are exactly the ones that are not a part of any fastest temporal path.
 Let us first observe some properties of such edges.
 
-\todo[inline]{Fix the following proof, add more details/definitions to the introduction.}
 \begin{claim}
@@
     We prove this claim in two steps.
-    First, all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$.
-They are of degree at least $2$ since they are on a path $S$ and are incident to two undetermined edges in  $P$.
+    First we prove that all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$ and are not vertices of interest. 
+    They are of degree at least $2$ since they are on a path $P$ and are incident to two undetermined edges in  $P$.
     They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
@@
 As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
-    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among some vertices of interest and $u$ would be an inner vertex on that path.
+    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among two vertices of interest and $u$ would be an inner vertex on that path.
     Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
 
-    From all of the above, it follows that $P$ is a segment in $G'$.
+    From all of the above, it follows that $P$ is an undetermined segment in $G'$.
 \end{proof}
@@
 \begin{claim}
-    Among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+    After determining the labels of fastest temporal paths between all pairs of vertices of interest,
+    there can be at most one undetermined segment among each pair of them.
+    %among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
 \end{claim}
 \begin{proof}
-   Suppose for the contradiction that there are two undetermined segments among $u,v \in U$.
+   Suppose for the contradiction that after determining the labels of all fastest temporal paths between vertices of interest,
+   there are two undetermined segments among $u,v \in U$.
    Denote them with $S_{u,v}$ and $S'_{u,v}$. 
-   Then $C = S_{u,v} \cup S_{u,v}'$ form a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
+   Then $C = S_{u,v} \cup S_{u,v}'$ forms a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
    Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
    both endpoints of $e$ have to be in $U$.
+   If $e = uv$ then there are only two vertices of interest in $C$, but the label of edge $e$ is determined.
+   And if $e \neq uv$ then there are at least $3$ vertices of interest in $C$.
    So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
@@
 
-From the above it follows that there are at most $O(|U|^2$) undetermined segments in $G'$ after algorithm finishes going through fastest temporal paths among vertices of interest.
-
-We already studied the case of fastest paths starting and ending in a vertex of $U$,
-so now we have to study all other cases.
-
-Let us start with the case of determining the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
+%From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
+Now we want to relate the undetermined segments with the determined ones.
+Let $S_{u,v}$ and $S_{w,z}$ be two segments.
+At the beginning we have guessed what is a split vertex of a fixed vertex $v_i \in S_{u,v}$ in the segment  $S_{w,z}$. 
+Denote this vertex as $z_j$, denote its neighbor closer to $w$ in $S_{w,z}$ as $z_{j-1}$,
+and its neighbor closer to $z$ in $S_{w,z}$ as $z_{j+1}$.
+We also guessed how the fastest temporal path from $v_i$ to $z_{j-1}, z_j, z_{j+1}$ starts and ends, 
+\ie through which of two vertices $u,v$ it leaves the segment $S_{u,v}$ and 
+through which of the two vertices $w,z$ it enters the segment $S_{w,z}$.
+For the details see \cref{FPT:guess-splitFromAnotherSegmentAndPaths}.
+Now using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first label from the segment $S_{u,v}$,
+between 
+$w$ and $z_{j-1}$, and between $z$ and $z_{j+1}$, and the label of one of the edges $z_{j-1}z_j$ or $z_j z_{j+1}$ (depending which edge is used on the fastest temporal path from $v_i$ to $z_j$).
+We repeat this procedure for all pairs of segments.
+Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
+
+Now all the edges are determined with the exception of at most two edges per segment (the first one and potentially one extra somewhere in the segment).
+
+We continue to adding all necessary constraint to our ILP instance. 
+We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
+and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
+
+First we consider the case when $u,v$ are two vertices of interest.
+This was the case that we partially studied at the beginning of the algorithm,
+where we have already introduced all equality constraints for the fastest temporal paths among vertices of $U$.
+We now iterate through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
+There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^3)$ inequality constraints.
+
+Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
 We have two possibilities:
@@
 
-    \item Vertex $x$ is not on a fastest temporal paths from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w,z_1,2_3, \dots, z_p, z)$.
+    \item \label{item:FPT-uToxcase2}
+    Vertex $x$ is not on a fastest temporal paths from $u$ to any $v \in U$.
+    Suppose that $x$ lies on a segment $S_{w,z} = (w,z_1,z_3, \dots, z_p, z)$.
     Since we know the underlying path of the fastest temporal path from $u$ to $z_1$ through $w$ and from $u$ to $z_p$ through $z$,
@@
     we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities, we check the values of each one and set the minimum of them, to equal the $D_{u,x}$ (if possible, if one is to small we immediately reject),
-    and again set all other possibilities to the inequality constraint.
-    There are $O(k^3)$ different paths from $u$ to $w$ (resp.~$z$), therefore we add $O(k^k)$ inequality constraints for all these paths.   
+    If $x = w^*$, we have two possibilities, we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
+    if this is even possible, if one is too small we immediately reject.
+    Note, we know the durations of fastest temporal paths from $u$ to $z_1$ and $z_p$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
+    with the exception of at most one inner edge.
+    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
+    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
+    smaller than $D_{u,x}$, then we reject and stop the calculation.
+    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
+    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
+    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
+    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
+    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
+    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
 \end{enumerate}
@@
 Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
+%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
+Let $x$ a vertex in the segment $S_{w,z} = (w,z_1,z_2, \dots, z_p, z)$.
+We can easily determine the vertex $z_i \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
+Denote this vertex as $z^*$. 
+Then we know that all vertices in $S_{w,z}$ that are closer to $w$ than $z^*$ reach $u$ on the path that goes through $w$ and 
+all the vertices in $S_{w,z}$ that are closer to $z$ than $z^*$ reach $u$ on the path that goes through $z$.
+At the beginning we have also guessed the fastest path $z_1 \rightarrow w \rightarrow u$ (resp.~$z_p \rightarrow z \rightarrow u$).
+Using this information we know all the fastest paths from any vertex in $S_{w,z} \setminus \{ z^* \}$ to $u$.
+For all of these paths we introduce an equality constraint. 
+For $z^*$ we have to determine which of the paths, through $w$ or $z$, to $u$ is the fastest.
+Since we know the labels of all edges of $S_{w,z}$, with the exception of at most one edge, we can easily determine (procedure is similar as in case~\ref{item:FPT-uToxcase2} from above),
+which is the fastest temporal path from $z^*$ to $w$, which gives an equality constraint .
+Now
+we still need to add the inequality constraints for all other paths.
+There are $O(k^k)$ paths between $w$ (resp.~$z$) and $u$, and a unique path from $z^*$ to $w$ (resp.~$z$).
+For all paths from $w^*$ to $u$, that are not equal to the fastest, we introduce the inequality constraint.
+This results in adding $O(k^k)$ inequality constraints.
 
 Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
+Let $x$ be a vertex in the segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w,z_1,z_3, \dots, z_r, z)$.
+By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
+we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
+This implies that the fastest temporal paths from $x$ to all vertices $z_1, z_2, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_r$)  passes through $w$ (resp.~$z$).
+Now we determine the vertex $z_j \in S_{u,v} \setminus \{u,v\}$,
+for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
+This implies that the fastest temporal paths from the vertices $v_1, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_p$) to the vertex $y$ passes through $u$ (resp.~$v$).
+At the beginning we have also guessed the following fastest paths  
+$z_1 \rightarrow w \rightarrow u \rightarrow v_1$,
+$z_1 \rightarrow w \rightarrow v \rightarrow v_p$,
+$z_r \rightarrow z \rightarrow v \rightarrow v_p$ and
+$z_r \rightarrow z \rightarrow v \rightarrow v_p$.
+We distinguish following two cases,
+first when $\{x,y\} \neq \{v_i, z_j\}$ and the second where $\{x,y\} = \{v_i, z_j\}$ (note this case encapsulates also the two cases when $x = v_i$ or $y=z_j$).
+In the first case we know how the fastest temporal path from $x$ to $y$ exits the segment $S_{u,v}$ and enters the segment $S_{w,z}$.
+Combining this with the guessed fastest paths, we uniquely determine the fastest temporal path from $x$ to $y$. 
+For this path we add the equality constraint, and for all other paths (by similar arguing as in other cases there are $O(k^k)$ such paths) we add the inequality constraints.
+In the second case when $\{x,y\} = \{v_i, z_j\}$ we do the following.
+\todo{TODO}
+
+All of the above is enough to determine the labelling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
+Remember that removed vertices form disjoint trees in $G$.
+Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
+Since there is a unique (static) path between any two vertices $t_1, t_2$ in a tree $T_i$,
+it follows that there is also a unique (therefore also the fastest) temporal path among them.
+Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
+Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
+For a tree $T_i$ denote with $u_i$ the vertex in $G'$ that is a neighbor of some vertex in $T_i$, 
+call it a \emph{clip vertex of the tree $T_i$}
+and denote with $r_i$ the neighbor of $u_i$, \ie the root of the tree $T_i$.
+By construction (by iteratively removing vertices of degree one from $G$) it follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
+but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
+First observe that $|N_{G'}(u_i)|\geq 1$, if not also $u_i$ would be removed from $G$.
+To determine the correct label of all edges of $T_i$ we use the following property.
+\begin{claim}
+Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a root of $T_i$.
+Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
+Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
+\end{claim}
+\begin{proof}
+Suppose that this is not true.
+Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
+and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
+Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
+Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
+Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
+So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
+\end{proof}
+
+Because $(r_i,u_i,v)$ is the fastest temporal path from $r_i$ to $v$ we can determine the label of edge $r_iu_i$ as 
+$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
+Now using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
+We repeat this procedure for all trees in $Z$.
+We have to now add the equality and inequality constraints for the fastest temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
+
+Let us start with the case when we consider fastest paths from a vertex $t$ in some tree $T_i$ to a vertex of interest $u \in U$.
+Denote with $r_i$ the root of $T_i$.
+We distinguish the following two cases.
+\begin{enumerate}[(i)]
+    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
+    Note that since we have determined the label of the edge $w r_i$, we also know the waiting times 
+    at vertex $u$ coming from each of its neighbor $v_i$ and finishing in $r_i$. 
+    At the beginning we have also determined the fastest paths from $u$ to all $v_i \in N_{G'}(w)$.
+    Therefore we know the path $P$ that is the fastest from $u$ to $r_i$. 
+    Once we have determined $P$ we also know that the fastest path from $u$ to any other vertex in $T_i$ uses $P$ at the beginning, to go from $u$ to $r_i$.
+    Therefore we have determined the fastest paths from $u$ to all other vertices in $T_i$,
+    which gives rise to $|T_i|$ equality constraints.
+    We iterate now through all other $u \rightarrow w \rightarrow r_i$ paths and introduce inequality constraints for them.
+    There are $O(k^k)$ such paths.
+
+    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
+    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r )$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
+    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
+    Similarly as before we know the fastest paths from $u$ to $z_1$ and $z_r$.
+    We also know the waiting times at the clip vertex $x$ coming from $z_{i-1}$ and $z_{i+1}$. Therefore we can determine the fastest temporal path $P$ from $u$ to $r_i$.
+    Again this path is the one that is then extended to the fastest path from $u$ to all other vertices in $T_i$,
+    which gives rise to $|T_i|$ equality constraints.
+    We iterate through all other temporal paths and produce the inequality constraints.
+    There are $O(k^k)$ of them for each vertex in $T_i$.
+\end{enumerate}
+
+In the case when we want to determine the fastest path from a vertex $t$ in some tree $T_i$ to a vertex of interest $u \in U$,
+we use similar arguing as above.
+The procedure produces one equality constraint and $O(k^k)$ inequality ones.
+
+The only two cases to consider are the cases when we want to determine the fastest paths from some $x \in V(G)$, that is not a vertex of interest, to a vertex $t$ in some tree $T_i$, and vice versa.
+We again need to consider two cases, one where
 
@@
     Let us denote with $y$ the vertex of $Q$, for which the duration from $x$ to $y$ is the biggest, among vertices of $Q$,
-    more precisely $x$ is a vertex corresponding to $max_{v_i \in Q} D_{x,v_i}$.
+    more precisely $y$ is a vertex corresponding to $max_{v_i \in Q} D_{x,v_i}$.
     Denote 

### 2023-01-24 RealizingTemporalGraphs.tex
Work from Tuesday 24th of January

@@
     Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
     It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
@@
 Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
 \end{proof}
@@
 Furthermore, since $x$ and $v$ are non-adjacent, we also have that there is no temporal path from $v$ to $x$.
+\end{itemize}
+\end{proof}
+
+\section{W[1]-hardness}
+\begin{theorem}\label{thm:W1wrtFVS}
+    \deltaExactLong\ is W[1]-hard parameterized by the feedback vertex number.
+\end{theorem}
+\begin{proof}
+    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
+Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
+If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
+W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
+    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
+    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
+    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way.
+
+    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ as follows.
+To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to an edge connecting the two vertices.
+Afterwards, we describe the remaining entries of $D$.
+
+    We use the following subgraph $G_{i,j}$ as a \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We first describe the vertex set of $G_{i,j}$.
+    \begin{itemize}
+        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
+        \item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
+        \item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
+        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^v_{2n}\}$ for all $\ell\in[m]$.
+Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
+        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
+    \end{itemize}
+    Graph $G_{i,j}$ has the following edges.
+    \begin{itemize}
+        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{y_\ell,v_{i,j}^\star\}$, and $\{z_\ell,v_{i,j}^{\star\star}\}$.
+
+        Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
+        \item For all $\ell\in [m]$ and $\ell'\in [2n-1]$, we have edge $\{u^\ell_{\ell'},u^\ell_{\ell'+1}\}$.
+    \end{itemize}
+    This finishes the construction of the edge selection gadget $G_{i,j}$.
+
+    For each color $i$, we introduce the following vertices. Intuitively, what we describe in the following will be used as a \emph{verification gadget} for color $i$.
+    \begin{itemize}
+        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i$.
+        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_n$.
+    \end{itemize}
+    We add the following edges.
+Assume $1\neq i \neq k$.
+We describe the two cases $i=1$ and $i=k$ afterwards.
+Let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{v^i,u^\ell_{\ell'}\}$ between $v^i$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{1,i}$.
+
+    Let $1<j<i$ and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{j,i}$.
+    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget $G_{j,i}$.
+
+    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$.
+
+    Let $e_\ell\in F_{i,i+1}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,i+1}$.
+
+    Let $i<j\le k$ and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,j}$.
+    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget $G_{i,j}$.
+
+    Finally, we add two vertices $\hat{v},\hat{v}'$ and the following edges.
+Intuitively, what we describe next will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
+    \begin{itemize}
+        \item Edge $\{\hat{v},\hat{v}'\}$.
+        \item An edge between $\hat{v}$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
+        \item An edge between $\hat{v}'$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
     \end{itemize}
@@
     Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$ in $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment}. Denote it with $S_{u,v}$.
+    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
+    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
+    Note $S_{u,v} \neq S_{v,u}$.
 \end{definition}
@@
 \subsection{Creating ILP instances and determining variables}
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Each vertex of interest is incident to at most $k$ such edges, therefore we create $O(k^3)$ variables.
 We start the algorithm by guessing necessary structures.
 Note, whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of the fastest temporal path among those two vertices.
-In the case when we want to guess the fastest path from $u$ to $v$, that passes through the vertex $x$ we write it as a fastest path of form $u \rightarrow x \rightarrow v$.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
+Similarly it holds if we want to include more vertices, that has to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,
+if the path among two vertices is not uniquely determined, we denote it by $\leadsto$.
 We guess the following structures.
@@
     and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^5})$ guesses.
+    This gives us $O(k^{k^4})$ guesses.
     \item Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$, 
-    where the first one includes $v_2, v_{p-1} \in U^*$, 
-    and the second one includes $z_2, z_{p-1} \in U^*$.
+    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
     We want to guess the following fastest temporal paths
-    $v_2 \rightarrow u \rightarrow w \rightarrow z_2$,
-    $v_2 \rightarrow u \rightarrow z \rightarrow z_2$,
-    $v_2 \rightarrow u \rightarrow w \rightarrow z_{r-1}$ and
-    $v_2 \rightarrow u \rightarrow z \rightarrow z_{r-1}$.
-    We repeat this procedure for all pairs of segments and all vertices from $U^*$ in those segments.
-    Since there are $O(k^3)$ segments in $G'$,
-    there are $O(k^6)$ possible paths of this form.
-    \item For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
+    $v_2 \rightarrow u \leadsto w \rightarrow z_2$,
+    $v_2 \rightarrow u \leadsto z \rightarrow z_2$,
+    $v_2 \rightarrow u \leadsto w \rightarrow z_{r-1}$ and
+    $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$.
+    We repeat this procedure for all pairs of segments.
+    Since there are $O(k^2)$ segments in $G'$,
+    there are $O(k^{k^5})$ possible paths of this form.
+    \item \label{FPT:guess-uToSegment}
+    For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
     and a vertex of interest $w \in U$,
     we guess the following fastest temporal paths
-    $w \rightarrow u \rightarrow v_2$, $w \rightarrow v \rightarrow v_2$,
+    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_2$,
     and
-    $v_2 \rightarrow u \rightarrow w$, $v_2 \rightarrow v \rightarrow w$.
+    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v \leadsto w$.
     \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(4 k^k)$ different possible such paths, therefore we make $O(k^6)$ guesses for these paths.
-    All together we made $O(k^6)$ new guesses for the structure of all of the above mentioned fastest temporal paths.
+    For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
+    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
 %Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
@@
     can be reached from $v_i$ by some path that has to go through $w$ oz $z$.
-    In fact, this is true for all paths starting in any vertex not in $S_{w,z}$.
     Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
     the segment
-    $S_{w,z}$ have to increase up to the certain point, when traversing the segment coming through $w$ and coming through $z$.
-    Namely,
-    let $z_j \in S_{w,z} \setminus \{w,z\}$ be the vertex with the biggest value  $D_{v_i,z_j}$,
-    we call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
+    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
+    We split the analysis into two cases.
+    \begin{enumerate}
+        \item 
+    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
+    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
+    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
+    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
     $D_{v_i,z_{p-1}} < D_{v_i,z_{p-2}} < \dots < D_{v_i,z_j}$.
@@
     For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that this kind of vertex does not exist.
+    or determine that $z_j$ does not exist.
     We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
@@
     We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^6)$ new guesses.
-    \item At the end we also guess the permutation of all $O(k^3)$ variables, \ie for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$.
-    This results in $O(k^k)$ guesses.
+    which results in producing $O(k^{k^6})$ new guesses.
+    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
+    \item 
+    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
+    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
+    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{p-1}}$ and 
+    $D_{v_i,z_{p-1}} < D_{v_i,z_{p-2}} < \dots < D_{v_i,z_j}$.
+    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
+    and 
+    the fastest temporal paths from $v_i$ to $z_{p-1}, z_{p-2}, \dots, z_{j+1}$ go through $z$.
+    In this case we only need to guess the following two fastest temporal paths $u \leadsto w \rightarrow z_2$
+    and $u \leadsto z \rightarrow z_{p-1}$.
+    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
+    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
+    Note that in this case we do not introduce any new guesses, as we guessed these paths already in Step~\ref{FPT:guess-uToSegment}.
     \end{enumerate}
-We create all of the guesses iteratively.
+\end{enumerate}
+We create all of the guesses independently.
 We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^6})$ new ones, that respond to the guessing in the second step, etc.
@@
     Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
-    such that the labeling $\lambda$ respects $D'$.
+    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
+    such that the labeling $\lambda$ respects the values from $D$.
     Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
@@
     where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    Suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
+    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
     Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
@@
     Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_ell$.
+    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
     Therefore since
@@
 
-\subsection{Adding constraints to the ILP}
-We proceed with adding constraints to our ILP instance, by iterating through all pairs of vertices.
+\subsection{Adding constraints and variables to the ILP}
+First case we observe is the case when we want to determine the labels on fastest temporal paths among vertices of interest.
+We proceed in the following way.
+Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
+If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-Labelalledges}).
+%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
+In the case when $P{_u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
+%In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
+%Since there are $\ell - 1$ edge labels that are not determined with respect to the label of the first edge, may be some  TODO from above??
+
+After finishing the previous step for all pairs of vertices in $U$,
+the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
+Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
+If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
+Note that the undetermined edges are exactly the ones that are not a part of any fastest temporal path.
+Let us first observe some properties of such edges.
+
+\begin{claim}
+    Undetermined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
+    \ie for every undetermined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+\end{claim}
+\begin{proof}
+    We prove this claim in two steps.
+    First we prove that all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$ and are not vertices of interest. 
+    They are of degree at least $2$ since they are on a path $P$ and are incident to two undetermined edges in  $P$.
+    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
+
+    Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
+As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
+    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among two vertices of interest and $u$ would be an inner vertex on that path.
+    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
+
+    From all of the above, it follows that $P$ is an undetermined segment in $G'$.
+\end{proof}
+
+\begin{claim}
+    After determining the labels of fastest temporal paths between all pairs of vertices of interest,
+    there can be at most one undetermined segment among each pair of them.
+    %among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+\end{claim}
+\begin{proof}
+   Suppose for the contradiction that after determining the labels of all fastest temporal paths between vertices of interest,
+   there are two undetermined segments among $u,v \in U$.
+   Denote them with $S_{u,v}$ and $S'_{u,v}$. 
+   Then $C = S_{u,v} \cup S_{u,v}'$ forms a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
+   Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
+   both endpoints of $e$ have to be in $U$.
+   If $e = uv$ then there are only two vertices of interest in $C$, but the label of edge $e$ is determined.
+   And if $e \neq uv$ then there are at least $3$ vertices of interest in $C$.
+   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
+\end{proof}
+
+%From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
+Now we want to relate the undetermined segments with the determined ones.
+Let $S_{u,v}$ and $S_{w,z}$ be two segments.
+At the beginning we have guessed what is a split vertex of a fixed vertex $v_i \in S_{u,v}$ in the segment  $S_{w,z}$. 
+Denote this vertex as $z_j$, denote its neighbor closer to $w$ in $S_{w,z}$ as $z_{j-1}$,
+and its neighbor closer to $z$ in $S_{w,z}$ as $z_{j+1}$.
+We also guessed how the fastest temporal path from $v_i$ to $z_j$ starts and ends, which determined also the structure of the fastest temporal paths 
+from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$
+(for the details see \cref{FPT:guess-splitFromAnotherSegmentAndPaths}).
+W.l.o.g. assume that we have guessed that the fastest path from $v_i$ to $z_j$
+passes through $w$ and $z_{j-1}$.
+Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
+And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
+use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
+Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
+with the exception of the edge $z_j z_{j+1}$.
+Therefore all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
+Since we repeat that procedure for all pairs of segments,
+we get that for a fixed segment $S_{w,z}$ we end up with an undetermined edge $z_j z_{j+1}$
+if and only if, this is an undetermined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
+
+We repeat this procedure for all pairs of segments.
+Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
+At this point
+the edges of every segment are fully determined, 
+with the exception of at most two edges per segment (the first one and potentially one extra somewhere in the segment).
+For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
+Besides that we create one variable for each edge that is still undetermined on a segment.
+Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra undetermined edge, we create $O(k^2)$ variables.
+At the end we guess the permutation of all $O(k^2)$ variables,
+together with the relation of each variable to the labels of edges incident to these undetermined edges.
+Namely, for an edge $e$ that is undetermined, we set its value to $x_e$ and check labels of all of its neighbors,
+which are determined by some other label,
+and variables of the undetermined neighbors,
+and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
+So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
+and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
+$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
+This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
+and consequently
+each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
+
+We proceed with adding constraints to each of our ILP instances, by iterating through all pairs of vertices.
 We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
@@
 In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is smaller than zero, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-In \emph{TODO: claim ???}\todo{TBD} we prove that for any two consecutive edges we know if the difference of labels is positive or negative, therefore we know when $\Delta$ has to be added.
-
-First case we observe is the case when we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P{_u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
-In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
-%Since there are $\ell - 1$ edge labels that are not determined with respect to the label of the first edge, may be some  TODO from above??
-
-After finishing the previous step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
-Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a variable $x_e$.
-Note that the undetermined edges are exactly the ones that are not a part of any fastest temporal path.
-Let us first observe some properties of such edges.
-
-\begin{claim}
-    Undetermined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
-    \ie for every undetermined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
-\end{claim}
-\begin{proof}
-    We prove this claim in two steps.
-    First we prove that all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$ and are not vertices of interest. 
-    They are of degree at least $2$ since they are on a path $P$ and are incident to two undetermined edges in  $P$.
-    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
-
-    Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
-As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
-    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among two vertices of interest and $u$ would be an inner vertex on that path.
-    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
-
-    From all of the above, it follows that $P$ is an undetermined segment in $G'$.
-\end{proof}
-
-\begin{claim}
-    After determining the labels of fastest temporal paths between all pairs of vertices of interest,
-    there can be at most one undetermined segment among each pair of them.
-    %among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
-\end{claim}
-\begin{proof}
-   Suppose for the contradiction that after determining the labels of all fastest temporal paths between vertices of interest,
-   there are two undetermined segments among $u,v \in U$.
-   Denote them with $S_{u,v}$ and $S'_{u,v}$. 
-   Then $C = S_{u,v} \cup S_{u,v}'$ forms a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
-   Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
-   both endpoints of $e$ have to be in $U$.
-   If $e = uv$ then there are only two vertices of interest in $C$, but the label of edge $e$ is determined.
-   And if $e \neq uv$ then there are at least $3$ vertices of interest in $C$.
-   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
-\end{proof}
-
-%From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
-Now we want to relate the undetermined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed what is a split vertex of a fixed vertex $v_i \in S_{u,v}$ in the segment  $S_{w,z}$. 
-Denote this vertex as $z_j$, denote its neighbor closer to $w$ in $S_{w,z}$ as $z_{j-1}$,
-and its neighbor closer to $z$ in $S_{w,z}$ as $z_{j+1}$.
-We also guessed how the fastest temporal path from $v_i$ to $z_{j-1}, z_j, z_{j+1}$ starts and ends, 
-\ie through which of two vertices $u,v$ it leaves the segment $S_{u,v}$ and 
-through which of the two vertices $w,z$ it enters the segment $S_{w,z}$.
-For the details see \cref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-Now using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first label from the segment $S_{u,v}$,
-between 
-$w$ and $z_{j-1}$, and between $z$ and $z_{j+1}$, and the label of one of the edges $z_{j-1}z_j$ or $z_j z_{j+1}$ (depending which edge is used on the fastest temporal path from $v_i$ to $z_j$).
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-
-Now all the edges are determined with the exception of at most two edges per segment (the first one and potentially one extra somewhere in the segment).
-
-We continue to adding all necessary constraint to our ILP instance. 
+Note that we know if the difference of two consecutive labels is positive or negative. 
+In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
+if one or both consecutive labels are undetermined 
+then we have guessed in what kind of relation they are,
+the case when two consecutive labels are determined with respect to different labels $\lambda(e)$ and $\lambda(f)$.
+Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
+
 We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
@@
 First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm,
-where we have already introduced all equality constraints for the fastest temporal paths among vertices of $U$.
-We now iterate through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^3)$ inequality constraints.
+This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
+We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
+We then continue 
+through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
+There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
 
@@
 For $z^*$ we have to determine which of the paths, through $w$ or $z$, to $u$ is the fastest.
-Since we know the labels of all edges of $S_{w,z}$, with the exception of at most one edge, we can easily determine (procedure is similar as in case~\ref{item:FPT-uToxcase2} from above),
+Since we know the labels of all edges of $S_{w,z}$, with the exception of at most one edge, we can easily determine (procedure is similar as in Case~(\ref{item:FPT-uToxcase2}) from above),
 which is the fastest temporal path from $z^*$ to $w$, which gives an equality constraint .
@@
 
-All of the above is enough to determine the labelling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
+All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
 Remember that removed vertices form disjoint trees in $G$.
@@
 We repeat this procedure for all trees in $Z$.
-We have to now add the equality and inequality constraints for the fastest temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
+The remaining thing is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
 
@@
 \begin{enumerate}[(i)]
+    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
+    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r )$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
+    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
+    Similarly as before we know the following fastest paths $z_1 \rightarrow w \leadsto u$ and
+    $z_r \rightarrow z \leadsto u$.
+    Denote thew with $Q_1$ and $Q_r$ respetively.
+    There are two options.
+    \begin{itemize}
+        \item The segment $S_{w,z}$ has no undetermined edges, with the exception of the first/last one.
+        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
+        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
+        This results in knowing the value of waiting time
+        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
+        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
+        when traversing it from $r_i$ to $z_{i+1}$.
+        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
+        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
+        Denote with $P^{-} = (r_i, x, z_{i-1}, z_1) \cup Q_1$
+        and with $P^{+} = (r_i, x, z_{i+1}, z_r) \cup Q_r$.
+        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
+        and compare it to $D_{r_i,u}$.
+        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
+        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
+        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
+        For the fastest temporal path we introduce the equality constraint, 
+        for all other paths we introduce the inequality constraints.
+        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
+        \item The segment $S_{w,z}$ has an extra undetermined edge $p$. If $p \cap \{x\} = \emptyset$, 
+        we can proceed with the same approach as above.
+        So suppose now that $p = x z_{i+1}$. 
+        Then, from knowing that $p$ is and undetermined edge we conclude that
+        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$ (not trough $p$).
+        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$,
+        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
+        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
+        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
+        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
+        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
+        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
+        We do the following.
+        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
+        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
+        It can be of the form $P^- = (r_i,x,z_{i-1})$,
+        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_1, \dots, z_{i-1}$, where $Q$ is some path from $z$ to $w$.
+        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
+        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
+        Note $R^{i-1} \subset R^x$.
+        Similarly,
+        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
+        for which we know it goes through the vertex $z$.
+        \begin{itemize}
+            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
+            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
+            which cannot happen.
+            \item  If $c = D_{r_i,u}$, then 
+            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
+            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
+            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
+            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
+            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
+But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
+            therefore it includes a path from $r_i$ to $u$, which is even faster,
+            a contradiction.
+            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
+            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
+            \item If $c > D_{r_i,u}$, then 
+            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
+            We again have two options.
+            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
+            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
+            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
+            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
+            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
+            Suppose for the contradiction that this is not true. 
+            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
+            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
+            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
+            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
+            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
+            Therefore we get that in this case 
+            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
+        \end{itemize}
+       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
+       which gives us an equality constraint.
+       For all other paths we add the inequality constraints. 
+       There are $O(k^k)$ of paths like this.
+    \end{itemize}
+    We also know the waiting times at the clip vertex $x$ coming from $z_{i-1}$ and $z_{i+1}$. Therefore we can determine the fastest temporal path $P$ from $u$ to $r_i$.
+    Again this path is the one that is then extended to the fastest path from $u$ to all other vertices in $T_i$,
+    which gives rise to $|T_i|$ equality constraints.
+    We iterate through all other temporal paths and produce the inequality constraints.
+    There are $O(k^k)$ of them for each vertex in $T_i$.
+
     \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
@@
     which gives rise to $|T_i|$ equality constraints.
-    We iterate now through all other $u \rightarrow w \rightarrow r_i$ paths and introduce inequality constraints for them.
+    We iterate now through all other $u \leadsto w \rightarrow r_i$ paths and introduce inequality constraints for them.
     There are $O(k^k)$ such paths.
-
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r )$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as before we know the fastest paths from $u$ to $z_1$ and $z_r$.
-    We also know the waiting times at the clip vertex $x$ coming from $z_{i-1}$ and $z_{i+1}$. Therefore we can determine the fastest temporal path $P$ from $u$ to $r_i$.
-    Again this path is the one that is then extended to the fastest path from $u$ to all other vertices in $T_i$,
-    which gives rise to $|T_i|$ equality constraints.
-    We iterate through all other temporal paths and produce the inequality constraints.
-    There are $O(k^k)$ of them for each vertex in $T_i$.
 \end{enumerate}

### 2023-01-26 RealizingTemporalGraphs.tex
Changes Wednesday 25th of January

@@
 \let\endproof\relax
+
+\sloppy
 
@@
 
-    We use the following subgraph $G_{i,j}$ as a \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We first describe the vertex set of $G_{i,j}$.
+    We will construct $G$ using several gadgets. We first introduce an \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We start with describing the vertex set of the gadget.
     \begin{itemize}
@@
     \end{itemize}
-    Graph $G_{i,j}$ has the following edges.
+    The gadget has the following edges.
     \begin{itemize}
@@
 
-    For each color $i$, we introduce the following vertices. Intuitively, what we describe in the following will be used as a \emph{verification gadget} for color $i$.
+    For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget} for color $i$.
     \begin{itemize}
-        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i$.
+        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i_0$.
         \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_n$.
@@
     We add the following edges. 
-Assume $1\neq i \neq k$.
-We describe the two cases $i=1$ and $i=k$ afterwards.
-Let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i,u^\ell_{\ell'}\}$ between $v^i$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{1,i}$.
-
-    Let $1<j<i$ and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{j,i}$.
-    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget $G_{j,i}$.
+    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
+    If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
+
+    Let $1<j<i$ (skip if $i=1$) and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
+    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget of color combination $j,i$.
 
@@
     Let $e_\ell\in F_{i,i+1}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,i+1}$.
-
-    Let $i<j\le k$ and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,j}$.
-    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget $G_{i,j}$.
-
-    Finally, we add two vertices $\hat{v},\hat{v}'$ and the following edges.
-Intuitively, what we describe next will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
+Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.
+
+    Let $i<j\le k$ (skip if $i=k$) and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
+    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget of color combination $i,j$.
+
+    Next, we describe \emph{connector gadgets}.
+Intuitively, these gadgets will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
+Connector gadgets consist of three vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$.
+    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
+    Each connector gadget is associated with two sets $A,B$ containing vertices of other gadgets. 
+    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
+    The sets $A$ and $B$ will only play a role when defining the distance matrix $D$ later.
+Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
+    We have the following edges. 
     \begin{itemize}
-        \item Edge $\{\hat{v},\hat{v}'\}$.
-        \item An edge between $\hat{v}$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
-        \item An edge between $\hat{v}'$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
+        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\}$.
+        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
+        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
     \end{itemize}
+    We add two connector gadgets for each edge selection gadget and one connector gadget for each validation gadget.
+
+    The first connector gadget for the edge selection gadget of color combination $i,j$ with $i<j$ has the following sets.
+    \begin{itemize}
+        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
+        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
+        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
+        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
+    \end{itemize}
+    The second connector gadget for the edge selection gadget of color combination $i,j$ with $i<j$ has the following sets.
+    \begin{itemize}
+        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
+        %\item Set $A'$ contains all vertices in $X_{i,j}$.
+        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
+        \item Set $B$ is empty.
+    \end{itemize}
+
+    The connector gadget for the verification gadget of color $i$ has the following sets.
+    \begin{itemize}
+        \item Sets $A$ and $B$ contain all vertices of the verification gadget and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
+    \end{itemize}
+
+Lastly, we introduce an \emph{alignment gadget}.
+It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget and one vertex for each connector gadget.
+Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
+The vertex $x_1$ of each edge selection gadget is connected to exactly one vertex in $\hat{W}$ and the vertex $\hat{v}_1$ of each connector gadget is connected to exactly one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
+
+This finished the description of the underlying graph $G$. We can observe that the vertex set containing
+\begin{itemize}
+    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
+    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_n$ (if exists) of each validation gadget.
+    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
+    \item vertex $w^\star$ of the alignment gadget
+\end{itemize}
+forms a feedback vertex set in $G$ with size $O(k^2)$.
+
+We proceed with describing the distance matrix $D$. We use the notation $d(v,v'):= D_{v,v'}$. For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
+
+Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$ and with sets $A$ and $B$.
+Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
+We set the following distances.
+Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
+\begin{itemize}
+    \item We set $d(\hat{v}_0,\hat{v}_1)=2$, $d(\hat{v}_1,\hat{v}_2)=2$, and $d(\hat{v}_0,\hat{v}_2)=3$.
+    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$.
+    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
+\end{itemize}
+
+Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
 \end{proof}
@@
 In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices, that has to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,
+Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,
 if the path among two vertices is not uniquely determined, we denote it by $\leadsto$.
 We guess the following structures.
-\begin{enumerate}
+\begin{enumerate}[G-1.]
     \item The fastest temporal paths among all pairs of vertices of $U$.
@@
     first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal paths
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$,
-    $v_2 \rightarrow u \leadsto z \rightarrow z_2$,
-    $v_2 \rightarrow u \leadsto w \rightarrow z_{r-1}$ and
-    $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$.
+    We want to guess the following fastest temporal path
+    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
     We repeat this procedure for all pairs of segments.
@@
     there are $O(k^{k^5})$ possible paths of this form. 
+    \\
+    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
+Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
+Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
+    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
+    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
+    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
+    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
+    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
     \item \label{FPT:guess-uToSegment}
@@
 In this section we study the properties of our problem, that then help us creating constraints of our ILP.
+Remember, with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
+We start with an empty labeling of edges and start adding certain values to them.
+Note, these values are not (necessarily) numbers. 
+In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
 In our analysis we exploit the following greatly, that is why we state is as an observation.
@@
 from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$
-(for the details see \cref{FPT:guess-splitFromAnotherSegmentAndPaths}).
+(for the details see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}). \todo{Two cases.}
 W.l.o.g. assume that we have guessed that the fastest path from $v_i$ to $z_j$
@@
 with the exception of the edge $z_j z_{j+1}$.
-Therefore all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
+Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
 Since we repeat that procedure for all pairs of segments,
@@
 
+\subsubsection*{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$}
 First we consider the case when $u,v$ are two vertices of interest.
@@
 
+\subsubsection*{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$}
 Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-We have two possibilities:
+We have three possibilities:
 \begin{enumerate}[(i)]
+    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_p,v)$. 
+    If $x$ is on a fastest path from $u$ to some other vertex, then we know that the fastest path from $u$ to $x$ travels along the $S_{u,v}$.
+    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex.
+    Denote with $P$ the underlying path of the fastest temporal path from $u$ to $v$, 
+    and with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_p$ (which we know as we have guessed it).
+    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
+    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
+    Then we know that the fastest temporal paths from $u$ to $v_1 v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
+    and the fastest temporal paths from $u$ to $v_p, v_{p-1}, \dots, $.
+    \todo{Missing}
     \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$.
@@
 all the vertices in $S_{w,z}$ that are closer to $z$ than $z^*$ reach $u$ on the path that goes through $z$.
-At the beginning we have also guessed the fastest path $z_1 \rightarrow w \rightarrow u$ (resp.~$z_p \rightarrow z \rightarrow u$).
+At the beginning we have also guessed the fastest path $z_1 \rightarrow w \leadsto u$ (resp.~$z_p \rightarrow z \leadsto u$).
 Using this information we know all the fastest paths from any vertex in $S_{w,z} \setminus \{ z^* \}$ to $u$.
@@
 
+\subsubsection*{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$}
 Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
+We have two options.
+\begin{enumerate}[(i)]
+    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
+    Denote with $x = v_i$ and $y = v_j$, where $i < j$.
+    Let $v_k \in S_{u,v}$ be a vertex for which the distance from $v_i$ is the biggest.
+    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
+    Then we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
+    with the exception of path $x \leadsto v_k$.
+    \todo{Details}
+    \item Vertices $x$ and $y$ are in different segments. 
 Let $x$ be a vertex in the segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w,z_1,z_3, \dots, z_r, z)$.
@@
 At the beginning we have also guessed the following fastest paths  
-$z_1 \rightarrow w \rightarrow u \rightarrow v_1$,
-$z_1 \rightarrow w \rightarrow v \rightarrow v_p$,
-$z_r \rightarrow z \rightarrow v \rightarrow v_p$ and
-$z_r \rightarrow z \rightarrow v \rightarrow v_p$.
+$z_1 \rightarrow w \leadsto u \rightarrow v_1$,
+$z_1 \rightarrow w \leadsto v \rightarrow v_p$,
+$z_r \rightarrow z \leadsto v \rightarrow v_p$ and
+$z_r \rightarrow z \leadsto v \rightarrow v_p$.
 We distinguish following two cases,
@@
 \todo{TODO}
-
+\end{enumerate}
+
+\subsubsection*{\boldmath Considering the paths for vertices from $Z$}
 All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
@@
 The remaining thing is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-
-Let us start with the case when we consider fastest paths from a vertex $t$ in some tree $T_i$ to a vertex of interest $u \in U$.
-Denote with $r_i$ the root of $T_i$.
+Note that since 
+there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
+we present the study for cases when we find fastest temporal paths from and to the root vertex $r_i$ of tree $T_i$, 
+which can be uniquely extended to all vertices in $T_i$.
+
+\subsubsection*{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$}
+Let us start with the case when we want to determine the fastest temporal path from a root vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
 We distinguish the following two cases.
@@
     \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r )$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r , z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
     where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
@@
     $z_r \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respetively.
+    Denote thew with $Q_1$ and $Q_r$ respectively.
     There are two options.
@@
         It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_1, \dots, z_{i-1}$, where $Q$ is some path from $z$ to $w$.
+        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_1, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
         Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
@@
     \end{itemize}
-    We also know the waiting times at the clip vertex $x$ coming from $z_{i-1}$ and $z_{i+1}$. Therefore we can determine the fastest temporal path $P$ from $u$ to $r_i$.
-    Again this path is the one that is then extended to the fastest path from $u$ to all other vertices in $T_i$,
-    which gives rise to $|T_i|$ equality constraints.
-    We iterate through all other temporal paths and produce the inequality constraints.
-    There are $O(k^k)$ of them for each vertex in $T_i$.
 
@@
     which gives rise to $|T_i|$ equality constraints.
-    We iterate now through all other $u \leadsto w \rightarrow r_i$ paths and introduce inequality constraints for them.
+    We iterate now through all other $u \leadsto w \rightarrow r_i$ paths and introduce inequality constraints for them. \todo{FIX}
     There are $O(k^k)$ such paths.
@@
 
-In the case when we want to determine the fastest path from a vertex $t$ in some tree $T_i$ to a vertex of interest $u \in U$,
+In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a root vertex $r_i$ in $T_i$,
 we use similar arguing as above.
@@
 
-The only two cases to consider are the cases when we want to determine the fastest paths from some $x \in V(G)$, that is not a vertex of interest, to a vertex $t$ in some tree $T_i$, and vice versa.
-We again need to consider two cases, one where
+\subsubsection*{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$}
+The next two cases are the ones where we want to determine the fastest temporal path from root $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
+and vice versa.
+Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u, v_1, v_2, \dots, v_p, v)$. Let $y = v_j$, for some $j \in [p]$.
+We use the similar approach as above, to determine the fastest temporal path from $r_i$ to $y$, 
+where the difference is that 
+we know the fastest temporal path from the clip vertex of $T_i$ to $y$.
+Since $y \in S_{u,v}$ there are $O(k^{k^6})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
+and $O(k^{k^6})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
+In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
+For all other paths we add the inequality constraints.
+
+\subsubsection*{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$}
+The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
+Let $r_i, r_j$ be root vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their root vertices, respectively.
+If $w_i = w_j$, then there is a unique path among $r_i$ and $r_j$, which gives rise to the equality constraint.
+If $w_i \neq w_j$, we know the underlying paths of fastest paths 
+from $r_i$ to $w_j$, from $w_j$ to $r_i$,
+from $r_j$ to $w_i$, from $w_i$ to $r_j$,
+and from $w_i$ to $w_j$.
+Using similar approaches as above, we can uniquely determine the fastest paths from $r_i$ to $r_j$.
+We again have to consider multiple cases.
+One where $w_i,w_j \notin U$ and 
+split it into two subcases, when the edges of the tree $T_i$ are determined with respect to the
+label of the first edge of the segment of $w_i$, and similarly for $T_j$.
+And one where the edges of the tree are determined with respect to some undetermined edge incident to $w_i$ (resp.~$w_j$).
+The second case is when $\{w_i, w_j\} \cap U \neq \emptyset$.
+In all of these cases we can uniquely determine the underlying paths of the fastest paths between $r_i$ and $r_j$,
+which give rise to equality constraints for them. 
+Then we have to find all non-fastest temporal paths among $r_i$ and $r_j$, for which we introduce the inequality constraints. 
+There are at most $O(k^{k^6})$ such paths.
+
+\begin{comment}
+We have the following two cases.
+\begin{enumerate}[(i)]
+    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
+    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
+    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
+    Similarly as above, we determine two cases.
+    \begin{itemize}
+    \item $S_{w,z}$ has no undetermined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
+    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
+    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
+    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
+    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
+    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
+    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
+    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
+    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
+    We know how to determine $P'$, since
+    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
+    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
+
+    \item The segment $S_{w,z}$ has an extra undetermined edge $p$. Suppose that $p = x z_{i+1}$.
+
+    \end{itemize}
+
+    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
+    For all other paths we add the inequality constraints. 
+    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
+    There are $O(k^{k^6})$ such paths.
+
+    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
+
+\end{enumerate}
+\end{comment}
 

### 2023-01-29 RealizingTemporalGraphs.tex
Changes Saturday 28th January

@@
 }
+
+\newcounter{guesscounter}
 
@@
 Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
-Furthermore, $v$ has distance two from $x$ in the undetermined graph $G$.
+Furthermore, $v$ has distance two from $x$ in the underlying graph $G$.
 Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
@@
         \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i_0$.
-        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_n$.
+        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n+3$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{n+3}$.
     \end{itemize}
@@
     %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
 Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
 
-    Let $1<j<i$ (skip if $i=1$) and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+    Let $1\le j<i$ (skip if $i=1$), let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
 Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
@@
 
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$.
-
-    Let $e_\ell\in F_{i,i+1}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$) and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+    If $1\neq i\neq k$, then we add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[n+2]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. 
+    Let $e_\ell\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},u^\ell_{n+\ell'}\}$ between $\hat{u}^i_{n+3}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.
+If $i=1$, then we add edge $\{v^i_0,u^\ell_{n+\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.
+
+    Let $i<j\le k$ (skip if $i=k$), let $e_\ell\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
 Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
@@
     \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_n$ (if exists) of each validation gadget.
+    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists) of each validation gadget.
     \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
@@
 Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
+\begin{itemize}
+    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_\ell')=2(i+j)\cdot(\ell'-\ell)$.
+    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+4$.
+\end{itemize}
+
+Next, consider the validation gadget for color $i$.
+First, assume $1\neq i \neq k$.
+Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
+We set the following.
+\begin{itemize}
+    \item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
+    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
+\end{itemize}
+
+For all $0\le j<j'<i$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)$.
+\end{itemize}
 \end{proof}
 
-\section{FPT and W[1]-hardness of exact realization -- new version}
+\section{FPT}
 In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
@@
 \end{definition}
-From the definition it follows, that there are $O(k^2)$ segments in $G'$.
+From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
 Observe also that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
@@
 \begin{enumerate}[G-1.]
-    \item The fastest temporal paths among all pairs of vertices of $U$.
+    \item \label{FPT-guessFTPamongU}
+    The fastest temporal paths among all pairs of vertices of $U$.
     For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
@@
     Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item The fastest temporal paths among all vertices in $U^*$, 
+    \item \label{FPT-guessFTPamongUstar}
+    The fastest temporal paths among all vertices in $U^*$, 
     which by similar arguing as for vertices in $U$, gives us $O(k^{k^6})$ guesses.
-    \item The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
+    \item \label{FPT-guessFTPamongUandUstar}
+    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
     and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
     This gives us $O(k^{k^4})$ guesses.
-    \item Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
+    \item \label{FPT-guessFTPamongv2z2}
+    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
     first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
@@
     Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. 
-    \\
+    there are $O(k^{k^5})$ possible paths of this form. \\
     Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
@@
     ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    \item \label{FPT:guess-uToSegment}
+    \item \label{FPT:guess-uToSegmentz2}
     For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
@@
     we guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_2$,
+    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
     and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v \leadsto w$.
+    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
     \\
@@
     fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
+    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
+    If $S_{u,v}$ is not of length $4$, we fix an arbitrary vertex $v_i \in S_{u,v}$.
     Let 
@@
     Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{p-1}} < D_{v_i,z_{p-2}} < \dots < D_{v_i,z_j}$.
+    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
     From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
     and 
-    the fastest temporal paths from $v_i$ to $z_{p-1}, z_{p-2}, \dots, z_{j+1}$ go through $z$.
+    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
     We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
@@
     Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also hot the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
+    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
     Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
@@
     More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{p-1}}$ and 
-    $D_{v_i,z_{p-1}} < D_{v_i,z_{p-2}} < \dots < D_{v_i,z_j}$.
+    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{p-1}}$.
     From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
@@
     the fastest temporal paths from $v_i$ to $z_{p-1}, z_{p-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths $u \leadsto w \rightarrow z_2$
+    In this case we only need to guess the following two fastest temporal paths 
+    $u \leadsto w \rightarrow z_2$
     and $u \leadsto z \rightarrow z_{p-1}$.
@@
     which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we guessed these paths already in Step~\ref{FPT:guess-uToSegment}.
+    Note that in this case we do not introduce any new guesses, as we have aready guessed 
+    the fastest paths of form
+    $u \leadsto w \rightarrow z_2$
+    and $u \leadsto z \rightarrow z_{p-1}$
+    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
     \end{enumerate}
+    \item \label{FPT:guess-splitFromUtoAnotherSegment}
+    Let $w \in U$ be a vertex of interest and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
+    Similarly as above we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+    We again have two cases,
+    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
+    and the
+    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
+    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
+    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
+    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
+    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
+    or 
+    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
+    Which produces two new guesses.
+    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
+    Therefore no new guesses are needed.
+    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
+    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
+    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
+
+    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
+    We repeat this for all vertices of interest, and all segments,
+    which produces $O(k^{k^2})$ new guesses.
+    % counter for guesses continues
+    \setcounter{guesscounter}{\value{enumi}}
 \end{enumerate}
@@
 If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{claim:FPT-uv-Labelalledges}.
-So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.\todo{TBD - George proved it}
+So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.
+\todo[inline]{George proved it.
+Also: add notation that is used in the proof to the beginning of the section, namely: $d(u,v,P)$ is the duration of the temporal path from $u$ to $v$ that traverses the edges of $P$.}
 \end{proof}
@@
 
+\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
+Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
+\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
+It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
+is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
+\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
+In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
+\end{lemma}
+
+\begin{proof}
+    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
+    The case, when $S_{u,v}$ is longer easily follows from presented results.
+
+    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
+    We distinguish two cases, first when $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
+    and the second when  $f = v_3v_4$.
+    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
+    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
+
+    Case 1,  $f = v_2v_3$.
+    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
+    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
+    From our proposition it follows that
+    \begin{itemize}
+        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
+    is of the following form 
+    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
+    and
+        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
+    is of the following form 
+    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
+    \end{itemize}
+    It follows that 
+    $
+    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
+    $
+    and
+    $
+    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
+    $.
+    Let 
+    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
+    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
+    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
+    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
+    Summing now both of the above equations we get
+    \begin{equation}
+    \begin{split} \label{eq:FPT-prf-fUnlabeled}
+        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
+        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
+        %
+        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
+        %
+        2 + 
+        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
+        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
+        &\leq 
+        1 + (t_2 - t_1)_\Delta + 
+        1 + (t_1 - t_2)_\Delta\\
+        %
+        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
+        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
+        &\leq 
+        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
+    \end{split}
+    \end{equation}
+    Note that if $t_i \neq t_j$ we get that 
+    the sum
+    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
+    and if $t_i = t_j$ the sum equals $2\Delta$.
+    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
+    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
+    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
+    for any relation of labels $t_1,t_2, \dots, t_5$,
+    which is a contradiction.
+
+    Case 2,  $f = v_3v_4$.
+    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
+    By similar arguments as above we get
+    \begin{align*}
+        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
+    \end{align*}
+    which is impossible.
+
+    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
+    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
+
+    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
+    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
+    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
+    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
+    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
+    and similarly 
+    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
+    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
+    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
+    Again we get the following.
+    \begin{equation}
+    \begin{split}
+        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
+        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
+        %
+        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
+        %
+        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
+        &\leq 
+        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
+    \end{split}
+    \end{equation}
+    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
+    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.\\
+    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
+    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
+    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
+\end{proof}
+
 \subsection{Adding constraints and variables to the ILP}
@@
 %Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P{_u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
+In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
+\todo{Chenge/explain}
 %In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
@@
 the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
-Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
+Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{not yet determined} edges.
 If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-Note that the undetermined edges are exactly the ones that are not a part of any fastest temporal path.
+Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
 Let us first observe some properties of such edges.
@@
 \begin{claim}
-    Undetermined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
-    \ie for every undetermined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
+    Not yet determined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
+    \ie for every not yet determined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p=v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_{p-1} \in V(G') \setminus U$.
 \end{claim}
@@
     First we prove that all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$ and are not vertices of interest. 
-    They are of degree at least $2$ since they are on a path $P$ and are incident to two undetermined edges in  $P$.
+    They are of degree at least $2$ since they are on a path $P$ and are incident to two not yet determined edges in  $P$.
     They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
@@
     Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
-As $u$ is the starting vertex of the undetermined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
+As $u$ is the starting vertex of the not yet determined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
     Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among two vertices of interest and $u$ would be an inner vertex on that path.
-    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one undetermined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
-
-    From all of the above, it follows that $P$ is an undetermined segment in $G'$.
+    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one not yet determined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
+
+    From all of the above, it follows that $P$ is a not yet determined segment in $G'$.
 \end{proof}
@@
     After determining the labels of fastest temporal paths between all pairs of vertices of interest,
-    there can be at most one undetermined segment among each pair of them.
+    there can be at most one not yet determined segment among each pair of them.
     %among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
@@
    Suppose for the contradiction that after determining the labels of all fastest temporal paths between vertices of interest,
-   there are two undetermined segments among $u,v \in U$.
+   there are two not yet determined segments among $u,v \in U$.
    Denote them with $S_{u,v}$ and $S'_{u,v}$. 
@@
    And if $e \neq uv$ then there are at least $3$ vertices of interest in $C$.
-   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully undetermined.
+   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully not yet determined.
 \end{proof}
@@
 %From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
-Now we want to relate the undetermined segments with the determined ones.
+Now we want to relate the not yet determined segments with the determined ones.
 Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed what is a split vertex of a fixed vertex $v_i \in S_{u,v}$ in the segment $S_{w,z}$. 
-Denote this vertex as $z_j$, denote its neighbor closer to $w$ in $S_{w,z}$ as $z_{j-1}$,
-and its neighbor closer to $z$ in $S_{w,z}$ as $z_{j+1}$.
-We also guessed how the fastest temporal path from $v_i$ to $z_j$ starts and ends, which determined also the structure of the fastest temporal paths 
-from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$
-(for the details see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}). \todo{Two cases.}
+At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
+We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
+(remember we can have the case when $z_j = z_{j+1}$),
+and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
+and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
+when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
 W.l.o.g. assume that we have guessed that the fastest path from $v_i$ to $z_j$
@@
 Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with an undetermined edge $z_j z_{j+1}$
-if and only if, this is an undetermined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-
+we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
+if and only if, this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
+%
 We repeat this procedure for all pairs of segments.
@@
 the edges of every segment are fully determined, 
-with the exception of at most two edges per segment (the first one and potentially one extra somewhere in the segment).
+with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
+We will now relate also these edges.
+More precisely,
+let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
+and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
+From the above procedure (when we were determining labels of edges of segments with each other) 
+we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
+There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
+we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
+and then there follow the edges
+$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
+We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
+For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
+We proceed as follows.
+\begin{enumerate}[G-1.]
+    \setcounter{enumi}{\value{guesscounter}}
+    \item \label{FPT-guessFTPinSegmentTgroughEdge}
+    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
+    we guess which of the following fastest temporal paths pass through the edge $f$,
+    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
+    and 
+    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
+    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
+    % counter for guesses continues
+    \setcounter{guesscounter}{\value{enumi}}
+\end{enumerate}
+Once we know which two fastest temporal paths pass through $f$, 
+we can determine the label of edge $f$ 
+with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
+and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
+Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
+Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
+In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
+But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
+which results in a segment with two not yet determined edges.
+In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
+therefore these segments remain with three, two or one not yet determined edges, respectively.
+From now on we refer to segments of length less than $4$.
+
+At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
+that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
+or it depends on no other label.
+We now describe how we create variables and start building our ILP instances. 
 For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still undetermined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra undetermined edge, we create $O(k^2)$ variables.
-At the end we guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these undetermined edges.
-Namely, for an edge $e$ that is undetermined, we set its value to $x_e$ and check labels of all of its neighbors,
+Besides that we create one variable for each edge that is still not yet determined on a segment.
+Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
+At the end we create our final guess
+\begin{enumerate}[G-1.]
+% counter for guesses continues
+\setcounter{enumi}{\value{guesscounter}}
+%%
+    \item \label{FPT:guessallPermutations}
+We guess the permutation of all $O(k^2)$ variables,
+together with the relation of each variable to the labels of edges incident to these not yet determined edges.
+Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
 which are determined by some other label,
-and variables of the undetermined neighbors,
+and variables of the not yet determined neighbors,
 and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
@@
 each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-
-We proceed with adding constraints to each of our ILP instances, by iterating through all pairs of vertices.
+\end{enumerate}
+
+We proceed with adding constraints to each of our ILP instances.
+First we add all constraints for the labels of edges that we have determined up to now.
+We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~non-fastest) temporal paths among them.
+
 We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
@@
 \end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is smaller than zero, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
+In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
 Note that we know if the difference of two consecutive labels is positive or negative. 
 In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are undetermined 
-then we have guessed in what kind of relation they are,
-the case when two consecutive labels are determined with respect to different labels $\lambda(e)$ and $\lambda(f)$.
+if one or both consecutive labels are not yet determined 
+then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
 Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
@@
 and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
+For each pair we argue how we determine these paths.
 
@@
 Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
+From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
+In this case we create the equality constraint for the fastest path and
+iterate through all other paths, for which we introduce the inequality constraints.
+There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
+and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
+Therefore we add $O(k^k)$ inequality constraints.
+
+%%%%%%
+%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
+\begin{comment}
+
 We have three possibilities:
 \begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_p,v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex, then we know that the fastest path from $u$ to $x$ travels along the $S_{u,v}$.
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex.
-    Denote with $P$ the underlying path of the fastest temporal path from $u$ to $v$, 
-    and with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_p$ (which we know as we have guessed it).
+    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
+    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
+    We introduce the equality constraint for it.
+    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
+    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
+
+    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
+    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
     We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
     Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1 v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_p, v_{p-1}, \dots, $.
-    \todo{Missing}
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$.
+    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
+    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
+    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
+    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
+    for which we introduce the inequality constraints.
+    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
+    Therefore we introduce $O(k^k)$ inequality constraints.
+    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
+    but it does not lie on the segment $S_{u,v}$.
     Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{claim:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$,
-    which hast to be of the duration $D_{u,x}$. This results in adding an equality constraint to our ILP.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the constraint to ILP that states that their duration is not smaller than the value $D_{u,x}$.
+    Then by \cref{claim:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
+    This results in adding the equality constraint for this fastest temporal path.
+    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
     To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
@@
     \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal paths from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w,z_1,z_3, \dots, z_p, z)$.
-    Since we know the underlying path of the fastest temporal path from $u$ to $z_1$ through $w$ and from $u$ to $z_p$ through $z$,
+    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
+    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
+    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
+    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
     we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
@@
     by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $w^*$ from $u$ on the segment $S_{w,z}$.
-    If $x \neq w^*$, we know which part of the segment is used to reach $x$.
+    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
+    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
+    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
+    and similarly 
+    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
+    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
     We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths from $u$ to $z$ and then to $x$, and paths from $u$ to $w$ and then to $x$),
+    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
     we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities, we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
+    If $x = w^*$, we have two possibilities,
+
+    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
     if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_1$ and $z_p$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
+    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
     with the exception of at most one inner edge.
@@
 \end{enumerate} 
+\end{comment}
 
@@
 %We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w,z_1,z_2, \dots, z_p, z)$.
-We can easily determine the vertex $z_i \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote this vertex as $z^*$. 
-Then we know that all vertices in $S_{w,z}$ that are closer to $w$ than $z^*$ reach $u$ on the path that goes through $w$ and 
-all the vertices in $S_{w,z}$ that are closer to $z$ than $z^*$ reach $u$ on the path that goes through $z$.
-At the beginning we have also guessed the fastest path $z_1 \rightarrow w \leadsto u$ (resp.~$z_p \rightarrow z \leadsto u$).
-Using this information we know all the fastest paths from any vertex in $S_{w,z} \setminus \{ z^* \}$ to $u$.
-For all of these paths we introduce an equality constraint. 
-For $z^*$ we have to determine which of the paths, through $w$ or $z$, to $u$ is the fastest.
-Since we know the labels of all edges of $S_{w,z}$, with the exception of at most one edge, we can easily determine (procedure is similar as in Case~(\ref{item:FPT-uToxcase2}) from above),
-which is the fastest temporal path from $z^*$ to $w$, which gives an equality constraint .
-Now
-we still need to add the inequality constraints for all other paths.
-There are $O(k^k)$ paths between $w$ (resp.~$z$) and $u$, and a unique path from $z^*$ to $w$ (resp.~$z$).
-For all paths from $w^*$ to $u$, that are not equal to the fastest, we introduce the inequality constraint.
-This results in adding $O(k^k)$ inequality constraints.
+Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
+If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
+(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
+Therefore assume that $S_{w,z}$ is of length at least $4$.
+This implies that there are at most two not yet determined edges in it.
+We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
+Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
+and with $P^-$ the fastest temporal path of form $z_{p-1} \rightarrow w \leadsto u$.
+Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
+Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
+following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
+and
+all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
+following fastest temporal path
+$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
+Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
+We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
+We distinguish the following two options.
+\begin{enumerate}[(i)]
+    \item \label{FPT:equality-fromUtoX-twosplit}
+    $z_i \neq z_{i+1}$.
+    Then the fastest temporal path from $z_i$ to $u$ is 
+    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
+    and 
+    the fastest temporal path from $z_{i+1}$ to $u$ is 
+    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
+    \item \label{FPT:equality-fromUtoX-onesplit}
+    $z_i = z_{i+1}$.
+    In this case we have to determine if the fastest temporal path goes first through vertex $z_{i-1}$ (and then through $w$),
+    or it goes first through $z_{i+1}$ (and then through $z$).
+    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
+    and since there are at most two not yet determined labels in $S_{w,z}$,
+    we can uniquely determine one of the following
+    waiting times:
+    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
+    or
+    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
+    Suppose we know the former (for the latter case, analysis follows similarly).
+    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
+    We now compare $c$ and the value $D_{z_{i},u}$.
+    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
+    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
+    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
+\end{enumerate}
+Once the fastest temporal paths are determined and we introduce the equality constraints for them.
+For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
+we introduce the inequality constraints.
 
@@
 \begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$ and $y = v_j$, where $i < j$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the distance from $v_i$ is the biggest.
+    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
+    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
+    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
+
+    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
+    Denote with $x = v_i$.
+    Let $v_k \in S_{u,v}$ be a vertex for which the distance from $v_i$ is the biggest 
+    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
+    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
     Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Then we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of path $x \leadsto v_k$.
-    \todo{Details}
+    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
+    with the exception of the fastest path from $x$ to $v_k$.
+    Since there is at most one undetermined edge in $S_{u,v}$,
+    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
+    we can determine either
+    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
+    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
+    We then compare (one of) these values to $D_{x,v_k}$ which then 
+    uniquely determines the fastest temporal path from $x$ to $v_k$
+    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
     \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w,z_1,z_3, \dots, z_r, z)$.
+Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
 By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
 we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-This implies that the fastest temporal paths from $x$ to all vertices $z_1, z_2, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_r$)  passes through $w$ (resp.~$z$).
-Now we determine the vertex $z_j \in S_{u,v} \setminus \{u,v\}$,
+Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
+(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
+This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
+Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
 for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-This implies that the fastest temporal paths from the vertices $v_1, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_p$) to the vertex $y$ passes through $u$ (resp.~$v$).
-At the beginning we have also guessed the following fastest paths  
-$z_1 \rightarrow w \leadsto u \rightarrow v_1$,
-$z_1 \rightarrow w \leadsto v \rightarrow v_p$,
-$z_r \rightarrow z \leadsto v \rightarrow v_p$ and
-$z_r \rightarrow z \leadsto v \rightarrow v_p$.
-We distinguish following two cases,
-first when $\{x,y\} \neq \{v_i, z_j\}$ and the second where $\{x,y\} = \{v_i, z_j\}$ (note this case encapsulates also the two cases when $x = v_i$ or $y=z_j$).
-In the first case we know how the fastest temporal path from $x$ to $y$ exits the segment $S_{u,v}$ and enters the segment $S_{w,z}$.
-Combining this with the guessed fastest paths, we uniquely determine the fastest temporal path from $x$ to $y$. 
-For this path we add the equality constraint, and for all other paths (by similar arguing as in other cases there are $O(k^k)$ such paths) we add the inequality constraints.
-In the second case when $\{x,y\} = \{v_i, z_j\}$ we do the following.
-\todo{TODO}
+Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
+leave the segment $S_{u,v}$. 
+We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
+Knowing the vertex $v_j$
+implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
+Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
+$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
+$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
+$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
+$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
+we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
+
+We have to now consider the case when 
+$x = v_j$ and $y = z_i$.
+If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
+then this segment has no inner edges with not yet determined labels
+and
+we can uniquely determine the fastest path from $v_j$ to $z_i$,
+using 
+similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
+If at least one of them is of length $3$ or less,
+we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
+and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
+(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
+If both segments are of the length $4$, then we know how all vertices reach each other,
+as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
 \end{enumerate}
+Once the fastest paths are uniquely determined we introduce the equality constraints for them
+and iterate through all other paths, that produce inequalities.
+To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
+once the segment is reached there is a unique path how to traverse it.
+Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
 
@@
 Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $t_1, t_2$ in a tree $T_i$,
+Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
 it follows that there is also a unique (therefore also the fastest) temporal path among them.
@@
 We repeat this procedure for all trees in $Z$.
-The remaining thing is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
+What remains is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
 Note that since 
@@
     \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r , z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
     where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
     $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as before we know the following fastest paths $z_1 \rightarrow w \leadsto u$ and
-    $z_r \rightarrow z \leadsto u$.
+    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
+    $z_{r-1} \rightarrow z \leadsto u$.
     Denote thew with $Q_1$ and $Q_r$ respectively.
     There are two options.
-    \begin{itemize}
-        \item The segment $S_{w,z}$ has no undetermined edges, with the exception of the first/last one.
+    \begin{enumerate}[(a)]
+        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
         Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
@@
         W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_1) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_r) \cup Q_r$.
+        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
+        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
         Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
@@
         By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ has an extra undetermined edge $p$. If $p \cap \{x\} = \emptyset$, 
+        \item The segment $S_{w,z}$ is of length $4$ or less
+        and has an extra not yet determined edge $p$. 
+        If $p \cap \{x\} = \emptyset$, 
         we can proceed with the same approach as above.
         So suppose now that $p = x z_{i+1}$. 
-        Then, from knowing that $p$ is and undetermined edge we conclude that
+        Then, from knowing that $p$ is a not yet determined edge we conclude that
         all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$ (not trough $p$).
@@
         It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_1, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
+        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
         Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
@@
        There are $O(k^k)$ of paths like this.
-    \end{itemize}
+    \end{enumerate}
 
@@
 and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u, v_1, v_2, \dots, v_p, v)$. Let $y = v_j$, for some $j \in [p]$.
+Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
 We use the similar approach as above, to determine the fastest temporal path from $r_i$ to $y$, 
@@
 label of the first edge of the segment of $w_i$, and similarly for $T_j$.
-And one where the edges of the tree are determined with respect to some undetermined edge incident to $w_i$ (resp.~$w_j$).
+And one where the edges of the tree are determined with respect to some not yet determined edge incident to $w_i$ (resp.~$w_j$).
 The second case is when $\{w_i, w_j\} \cap U \neq \emptyset$.
@@
     \begin{itemize}
-    \item $S_{w,z}$ has no undetermined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
+    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
     Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
@@
 
-    \item The segment $S_{w,z}$ has an extra undetermined edge $p$. Suppose that $p = x z_{i+1}$.
+    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
 
@@
 
-\section{FPT, Old proof -- need to move useful stuff above}
-Let us first observe some properties.
-
-Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an undetermined segment in $G'$, between vertices of interest $u,v \in U$,
-let $P$ be the underlying path of a fastest temporal path from $u',v' \in U$.
-Let $P$ be such path that there exists a vertex $x \in P \setminus \{u,v\}$ of degree two (\ie $x\notin U$).
-
-Since $x$ is an inner vertex of $P$ and is of degree two, then we know the labels of its two edges incident to it.
-Denote with $\ell_x$ the edge incident to $x$ that is closer to $u'$ on the path $P$, and with $r_x$ the edge that is closer to $v'$ on $P$.
-Let $y$ be an inner vertex on the path $Q$.
-Similarly, denote with $\ell_y$ the edge incident to $y$ that is closer to $u$ on the path $Q$, and with $r_y$ the edge that is closer to $v$ on $Q$.
-Observe the following. 
-To reach $y$ from $x$ there are $4$ different options, at the start path uses either edge $\ell_y$ or $r_y$, 
-and at the end path must use either $\ell_x$ or $y_x$.
-Since this is true for any path (hence any temporal path), it holds also for the fastest temporal path from $x$ to $y$.
-
-\begin{claim}\label{claim:FPT-unlabeldPaths-012}
-    Suppose that the fastest temporal path from $x$ to $y$ uses at the beginning edge $\ell_x$.
-    We now claim that if the fastest temporal path from $x$ to $y$ uses edge $\ell_y$ (resp.~$r_y$) as the last edge,
-    then the fastest temporal path from $x$ to any other vertex of $Q$, that is closer to $u$ (resp.~$v$) 
-    uses the same edge $\ell_y$ (resp.~$r_y$) as the last edge and $\ell_x$ as the first edge.
-    Similarly holds if the first edge of the fastest temporal path is $r_x$.
-\end{claim}
-\begin{proof}
-    Suppose that $y, y'$ are two vertices of $Q$, where the distance from $u$ to $y'$, in $Q$, is shorter than the distance from $u$ to $y$.
-    Suppose also that the fastest temporal path from $x$ to $y$ uses the edges $\ell_x$ and $\ell_y$, and passes through $y'$. Denote this path as $P_{x,y}$.
-    Denote with $P_{x,y}^{y'}$ the subpath of the temporal path $P_{x,y}$ from $x$ to $y'$
-    Now observe the following possibilities. %
-    \\
-    First, suppose that a fastest temporal path from $x$ to $y'$ uses the edges $\ell_x$ and $r_y$, denote it with $P_{x,y'}^1$.
-    Then the duration of $d(P_{x,y}^{y'}) \geq  d(P_{x,y'}^1)$.
-    But since $P_{x,y'}^1$ passes through vertex $y$, the duration from $x$ to $y$ on $P_{x,y'}^1$ is strictly smaller than $d(P_{x,y'}^1)$, and conversely 
-    $d(P_{x,y})$ is strictly greater than $d(P_{x,y}^{y'})$,
-    therefore at vertex $y$ we get that 
-    $d(P_{x,y})$ is strictly bigger than the duration of the subpath of $P_{x,y'}^1$ from $x$ to $y$, which is not possible. %
-    \\
-    Second, suppose that a fastest temporal path from $x$ to $y'$ uses the edges $r_x$ and $\ell_y$, denote it with $P_{x,y'}^2$.
-    Therefore $d(P_{x,y'}^2) \leq d(P_{x,y}^{y'})$.
-    To get the duration of the initial $P_{x,y}$ we can split the problem into calculating the duration from $x$ to $y'$ and the duration from $y'$ to $y$, plus the waiting time at vertex $y'$.
-    Since there is a unique path from $u$ to $y'$ and then to $y$, the waiting time at $y'$ and the duration of the path from $y'$ to $y$ is independent of the choice of path from $x$ to $y'$. 
-    Therefore, from the fact that $P_{x,y}$ is a fastest temporal path from $x$ to $y$ we get that $d(P_{x,y'}^2) \geq d(P_{x,y}^{y'})$.
-    All together we conclude that $d(P_{x,y}^{y'})$ is a fastest temporal path from $x$ to $y'$.%
-    \\
-    Third, suppose that a fastest temporal path from $x$ to $y'$ uses the edges $r_x$ and $r_y$, denote it with $P_{x,y'}^3$.
-    Then the subpath of $P_{x,y'}^3$ from $x$ to $y$ would be strictly faster than $P_{x,y}$, which is not possible.
-\end{proof}
-%
-Using the results from above we can now prove the following.
-\begin{lemma}\label{lem:FPT-DetermineLabelsOnUnlabeledNonFastestPaths}
-    Suppose that $Q = (u,v_2,v_3, \dots, v_p, v)$, where $p \geq 2$ is an undetermined segment in $G'$, between vertices of interest $u,v \in U$,
-    let $P$ be the underlying path of a fastest temporal path from $u',v' \in U$.
-    Let $P$ be such path that there exists a vertex $x \in P \setminus \{u,v\}$ of degree two (\ie $x \notin U$).
-    Then we can precisely determine the labels on every edge of $Q$, but one, with respect to the label $c_{u'v'}$ of the first edge of path $P$.
-\end{lemma}
-\begin{proof}
-    %To prove this we use \cref{claim:FPT-unlabeldPaths-01} and \cref{obs:FirstLabelAndDuration}.
-    Let us denote with $y$ the vertex of $Q$, for which the duration from $x$ to $y$ is the biggest, among vertices of $Q$,
-    more precisely $y$ is a vertex corresponding to $max_{v_i \in Q} D_{x,v_i}$.
-    Denote 
-    with $\ell_x$ the edge incident to $x$ that is closer to $u'$ on path $P$, and with $r_x$ the edge that is closer to $v'$ on $P$.
-    Similarly, denote with $\ell_y$ the edge incident to $y$ that is closer to $u$ on the path $Q$, and with $r_y$ the edge that is closer to $v$ on $Q$.
-    Suppose that the fastest temporal path $P$ from $x$ to $y$ uses first edge $\ell_x$ and then edge $\ell_y$.
-    Then it follows from \cref{claim:FPT-unlabeldPaths-01} that all fastest temporal paths from $x$ to vertices between $u$ and $y$ use as a first edge $\ell_x$ and go through vertex $u$. 
-    Now using \cref{obs:FirstLabelAndDuration} it follows that we can determine labels on all edges between $u$ and $y$.
-
-    Denote now with $y'$ the neighbor of $y$ in $Q$, that is closer to $v$ than $u$. 
-    We know that we reach $y'$ starting from $x$ the fastest, when the path passes through vertex $v$.
-    There are two options how the fastest temporal path from $x$ to $y'$ departs from $x$. Either it first uses edge $\ell_x$ or edge $r_x$. 
-    Once we know which of these two options happens, we can determine all the labels on edges between $v$ and $y'$.
-
-    In total we have uniquely determined labels of all edges of $Q$, with respect to the labeling of edges in $P$ (\ie with respect to the label of the first edge on $P$), with the exception of edge $yy'$.
-\end{proof}
-
-Up to now we have determined the labels (the constraints for labels) of edges of $G'$. We will now extend the labeling to the initial graph $G$. 
-Recall, $G'$ was created from $G$ by iteratively removing all vertices of degree $1$ from $G$.
-
-Note that vertices from $V(G) \setminus V(G')$ form disjoint paths in $G$. 
-Each such path is incident to exactly one vertex from $G'$.
-
-Let $P' = (v_1, v_2, \dots, v_p=s)$ be a path in $G$ on vertices from $V(G) \setminus V(G')$  (\ie path on vertices that were removed from $G$)
-and let $u$ be a neighbor of $s$ in $G$,
-therefore $P=(v_1, v_2, \dots, v_p=s, u)$ is an induced path in $G$.
-First observe that $|N_{G'}(u)|\geq 1$, if not also $u$ would be removed from $G$ and $G$ would be a tree, for which we can solve the problem in polynomial time (see~\cref{thm:deltaExact-PolyTimeTrees}).
-
-To determine the correct label of all edges of $P$ we use the following property.
-\begin{claim}
-Let $P = (v_1, v_2, \dots, v_p=s)$ be a path in $G$ on vertices from $V(G) \setminus V(G')$
-and let $u$ be a neighbor of $s$ in $G$.
-Let $v_i \in N_{G'}(u)$ be the closest vertex to $v$, regarding the values of $D$, \ie  $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$.
-Then the path $P^*=(s,u,v_i)$ has to be the fastest temporal path from $s$ to $v_i$ in $G$.
-\end{claim}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $s$ to $v_i$, that goes through $u$ (as this is the only neighbor of $s$), through some other vertex $v_j \in N_{G'}(u) \setminus \{v_i \}$, 
-and through some other path $P'$ in $G$, before it finishes in $v_i$, where $P'$ is at least an edge (from $v_j$ to $v_i$). 
-Therefore $P^*_2= (s,u,v_j,P',v_i)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{s,v_i} \leq D_{s,v_j}$ for all $v_j \in N_{G'}(u)$ the first part of path $P^*_2$ from $s$ to $v_j$ takes at least $D_{s,v_i}$ time.
-Since $v_i \neq v_j$ we need at least one more time-step (one more edge) to traverse from $v_i$ to reach $v_j$. 
-So $d(P^*) \geq D_{s,v_i} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-
-Because $(s,u,v_i)$ is the fastest temporal path from $s$ to $v_i$ we calculate the label of edge $su$ as $\lambda (s,v_i) \equiv \lambda(u v_i) + 1 - D_{s,v_i} \pmod \Delta$.
-Since $P$ is a path, the fastest temporal path from all vertices of $P$ to $u$ is the temporal path along $P$, therefore using \cref{obs:FirstLabelAndDuration} and the value of the edge $su$, we can determine labels of all edges in $P$.
-
-We repeat the above procedure for paths in $G$ that we removed in Step 1, and we end up with the labeling $\lambda$ of the whole graph.
-
-\begin{comment}
-Now we have to make sure that all the new labels satisfy $D$, to do this we calculate the matrix $D'$ of fastest temporal paths among all pairs of vertices in $(G, \lambda)$ and compare the results with $D$, if any values differ, we stop and return a \textsc{No} answer, if $D = D'$ we return the labeling $\lambda$.
-
-To calculate $\lambda (s,v_i)$ we need $O(|N_{G'}(u)|) = O(n)$ time, therefore to calculate all labels of edges incident to vertices of degree one in $G$, we need $O(n^2)$ time, calculating $D'$ takes $O(n^3\log n)$ time (see \cref{lemma:calculatingD}), therefore the whole step is performed in polynomial time.
-\end{comment}
-%
-%
-\subsubsection*{Step 3(a) of the FPT algorithm}
-Using all of the above results we proceed in the following way.
-For a partial ILP instance $I$ we 
-select an inner vertex $x$ of every fastest temporal path among vertices of interest $u'$ and $v'$,
-and for every endetermined path among vertices of interest $u$ and $v$ we find such $y$ and $y_1, y_2$ from this path, that $y$ is furthest away from $x$ and $y_1, y_2$ are its neighbors.
-We then enumerate $4$ possible ways that a fastest temporal path starts from $x$ and reaches $y$, 
-and then $2$ additional ways, how a fastest temporal path starts from $x$ to $y_1$ (resp.~$y_2$).
-For each of the possibilities we then precisely determine labels of the undetermined path, up to the constant of the fastest $u',v'$ temporal path.
-
-Since there are at most $|U|^2$ fastest temporal paths among vertices of interest, we create at most $4|U|^2$ extra instances for each undetermined path.
-Therefore one partial ILP instance $I$ is further extended into $O(|U|^3)=f(k)$ \todo{$O(2^k)$} final ILP instances $I_I$.
-
-\subsubsection*{Step 3(b) of the FPT algorithm}
-Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-In the case when the input instance has a solution, algorithm also provides us with one.
-
-One final ILP instance $I_I$, that was built by our algorithm, has $f(k)$ variables. 
-Therefore one $I_I$ can be solved in FPT time with respect to $k$.
-
-We have build $f(k)$ different final ILP instances.
-If none of the instances is a \textsc{Yes} instance, then we conclude that there is no labeling $\lambda$ of $G$, that would satisfy the distances of the matrix $D$,
-and therefore $D$ is a \textsc{No} instance of \deltaExact.
-If there is a final ILP instance $I_I$, that is a \textsc{Yes} instance, then we take a solution $S$, provided by the algorithm from \cite{Lenstra1983Integer}, and determine the corresponding labeling $\lambda$ of $G$.
-Note, the minimum number of solutions of $I_I$ is at least $\delta$, since the graph is periodic and adding the same constant to every edge in the graph, dose not change the duration of any temporal path in $(G, \lambda)$.
-
-\section{
-\texorpdfstring{\deltaExact\ is (NOT) polynomial-time solvable}
-{\textsc{Simple Delta-TGR} is polynomial-time solvable}
-}\
-
-$G$ can be deduced easily from $D$.
-
-	Let $G$ be the underlying graph of matrix $D$ and let $v$ be an arbitrary vertex in $G$, we want to determine the labeling $\lambda: E(G) \rightarrow [\Delta]$, that assigns exactly one label to each edge in $G$ and satisfies the distances from $D$.
-	To do so we observe some properties of the problem.
-
-\subsection*{Inequalities}
-
-	Let $v \in V$ be an arbitrary vertex in $V(G)$ and let $u \in V \setminus \{v\}$ be a vertex, that is at distance at least $2$ from $v$, in the underlying graph $G$.
-	Let $\mathcal{P}_{u}^v$ be a set of all $P_3$ paths on $3$ vertices in $G$, of form $(v_1, v_2, u)$, where $v_1, v_2 \in V(G)$, \st $v_1 v_2, v_2 u \in E(G)$ and $d(v,v_1) < d(v,v_2) < d(v,u)$. 
-	Intuitively, we can imagine the set $\mathcal{P}_{u}^v$ as the set of all incoming temporal $P_3$ paths to vertex $u$, with respect to starting from vertex $v$.
-
-	Let $P = (v_1,v_2,u)$ be an arbitrary path from $\mathcal{P}_u^v$, denote with $\lambda_1, \lambda_2$ the labels of edges $(v_1,v_2)$ and $(v_2, u)$, respectively.
-	By the definition of $\mathcal{P}_u^v$ it follows that $v_1, v_2$ are reached by $v$ faster than $u$ is reached by $v$, therefore we get the following inequality:
-	\begin{equation}\label{eq:ineq-uv-onePath}
-	    \lambda_2 \geq_\Delta \lambda_1 + d(v,u)-d(v,v_2) \pmod \Delta
-	\end{equation}
- \todo[inline]{GM: WHY??? THIS IS WRONG}
-	We repeat the above procedure for every path $P \in \mathcal{P}$ and collect all the inequalities to a set $S_u^v$.
-	Similarly we proceed for every pair of vertices $u$ and $v$.
-	At the end we get the collection of sets, each containing inequalities of the form \cref{eq:ineq-uv-onePath}.
-
-	\begin{lemma}
-	\label{claim:exact-setsOfInequalities}
-    Let $D$ be \textsc{YES}-instance of \textsc{Simple $\Delta$-TGR}, and let 
-$(G,\lambda,\Delta)$ be a certificate for $D$, where $\lambda:E\rightarrow \{1,2,\ldots,\Delta\}$ a simple periodic labeling of $G$. Then, for every pair $u,v$ of non-adjacent vertices:
-	\begin{enumerate}
-	    \item \label{itemize:Claim-exact-AtLeastOneEquality-1} $\lambda$ satisfies all the inequalities of the set $S_u^v$, and 
-	    \item \label{itemize:Claim-exact-AtLeastOneEquality} at least one of the inequalities of $S_u^v$ is an equality.
-	\end{enumerate}
-	\end{lemma}
-
-    \begin{proof}
-    By the definition of $\mathcal{P}_u^v$, every fastest temporal path from $v$ to $u$ must reach $u$ using one of the $P_3$ paths of $\mathcal{P}_u^v$.
-    Let $P$ be an arbitrary temporal path from $v$ to $u$. 
-    An arbitrary path $P \in \mathcal{P}_u^v$ is either a part of the fastest path from $v$ to $u$, which means that the path arrives to $u$ at the time equal to $d(v,u)$,
-    or it is not a part of the fastest path, which means it arrives to $u$ at some time greater than $d(v,u)$.
-    This is how the inequalities from $S_u^v$ are constructed. 
-    \todo{GM: WHY? WRONG} 
-    Since the fastest path from $v$ to $u$ has to be of duration $d(v,u)$, at least one of the inequalities from $S_u^v$ has to be an equality.    
-    \end{proof}
-
-    \paragraph{Manipulation of inequalities modulo $\Delta$.}
-    Suppose we have a path $P$ on three vertices, of form $(v_1, v_2, u)$,
-    and suppose $d(v,v_1) < d(v,v_2) < d(v,u)$ for some $v \in V \setminus P$, with $d(v,v_2) = a, d(v,u)=b$. 
-    Let us denote with $\lambda_1 = \lambda(v_1 v_2), \lambda_2 = \lambda(v_2 u)$ and $k = b-a$, where $1 \leq k \leq \Delta$ as all edge labels have values from $1$ to $\Delta$.
-    Then by \cref{eq:ineq-uv-onePath} we know that 
-    \begin{equation}\label{eq:inequalities-properties-example}
-        \lambda_2 \geq_\Delta \lambda_1 + k \pmod \Delta.
-    \end{equation}
-    Note that if $\lambda_2 = \lambda_1$, the duration of temporal path $(P, \lambda) = ((v_1v_2, \lambda_1), (v_2u, \lambda_2))$ is exactly $\Delta+1$,
-    therefore $\lambda_1 = \lambda_2$ satisfies \cref{eq:inequalities-properties-example}.
-    We can rewrite \cref{eq:inequalities-properties-example} as
-    \begin{equation*}
-        \lambda_2 \in 
-        \{
-        \lambda_1 + k, \lambda_1 + (k + 1), \dots , \lambda_1 + (\Delta - 1), \lambda_1 + \Delta 
-        \} \pmod \Delta.
-    \end{equation*}
-    Suppose now we have the following two inequalities
-    \begin{align*}
-        & \lambda_2 \geq_\Delta \lambda_1 + k \pmod \Delta, \\
-        & \lambda_2 \geq_\Delta \lambda_1 + k' \pmod \Delta,
-    \end{align*}
-    for some $k' > k$, then the set of all possible solutions satisfying both equations is the following
-        \begin{equation*}
-        \lambda_2 \in 
-        \{
-        \lambda_1 + k', \lambda_1 + (k' + 1), \dots , \lambda_1 + (\Delta - 1), \lambda_1 + \Delta 
-        \} \pmod \Delta.
-    \end{equation*}
-
-    Observe now that without the condition~\ref{itemize:Claim-exact-AtLeastOneEquality} of \cref{claim:exact-setsOfInequalities}, all inequalities of condition~\ref{itemize:Claim-exact-AtLeastOneEquality-1} can be satisfied by setting the label of every edge of the graph to be the same.
-
-    \subsection*{Cycles}
-    \begin{definition}[Travel delays]
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTimes}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    \begin{observation}
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-    \begin{observation} \label{obs:exact-VertexSum}
-    Let $v$ be a vertex of $G$, and let $N(v)=\{u_1, u_2, \ldots, u_k\}$. Then 
-    \begin{equation*}
-        \sum_{i = 1}^k \tau_{v}^{u_{i}v_{i+1}} \equiv  0 \pmod \Delta,
-    \end{equation*}
-    where the indices of vertices $u_i$ are taken modulo $k$.
-    \end{observation}
-
-    \begin{proof}
-        tbd
-    \end{proof}
-
-\begin{observation} \label{obs:exact-CyclesSum}
-    Let $C = (v_1, v_2, \dots, v_k)$ be a cycle in $G$.
-    Then 
-    \begin{equation*}
-        \sum_{i = 1}^k \tau_{v_i}^{v_{i-1}v_{i+1}} \equiv  0 \pmod \Delta,
-    \end{equation*}
-    where the indices of vertices $v_i$ are taken modulo $k$ (\ie $v_{-1}=v_{k-1}, v_0 = v_k, v_1 = v_{k+1}, \dots$).
-    \end{observation}
-
-    \begin{proof}
-        Using \cref{eq:def-VertexWaitingTimes} and the fact that the indices of vertices $v_i$ are taken modulo $k$, we get the following:
-        \begin{align*}
-            &\sum_{i = 1}^k \tau_{v_i}^{v_{i-1}v_{i+1}}  \equiv  
-            \sum_{i = 1}^k  ( \lambda(v_i v_{i+1}) - \lambda (v_{i-1} v_i) ) \pmod \Delta \equiv \\
-            &\lambda(v_1 v_2) - \lambda(v_{k}v_1) + \lambda(v_2 v_3) - \lambda(v_2 v_1) + \dots + \lambda(v_k v_1) - \lambda(v_{k-1}v_k) \pmod \Delta.
-        \end{align*}
-    \end{proof}
-
-    \begin{claim}
-    labeling $\lambda$ is a solution for the \textsc{Exact Realization $(\Delta)$} if and only if
-    for every cycle $C$ of $(G,\lambda)$ it holds that the sum of the travel delays along $C$ is $0$ modulo $\Delta$.
-    \end{claim}
-
-    \begin{proof}
-        TBD
-    \end{proof}
-
-\begin{theorem}
-	\textsc{Exact Realization $(\Delta)$} can be solved in polynomial time on paths, cycles, trees and stars.
-\end{theorem}
-
-\begin{proof}[Idea:]
-    For a labeling $\lambda$ we know that it has to satisfy \cref{claim:exact-setsOfInequalities}.
-    There are at most $n^2$ different sets $S_u^v$, each containing at most $n^2$ inequalities. 
-    Therefore we have $O(n^4)$ inequalities to satisfy with at least of $n^2$ of them being equalities (one for each set $S_u^v$.
-
-    Besides that we can also use the fact from \cref{obs:exact-CyclesSum}, which produces some extra restrictions on all inequalities.
-    We believe we can create some ``base of cycles'' over $G$ that would help us use \cref{obs:exact-CyclesSum} efficiently.
-\end{proof}
-
 \end{document}

### 2023-01-30 RealizingTemporalGraphs.tex
Changes Sunday 29th of January

@@
     \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices of the verification gadget and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
+        \item Sets $A$ and $B$ contain all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
     \end{itemize}
@@
 \begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_\ell')=2(i+j)\cdot(\ell'-\ell)$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+4$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$.
-First, assume $1\neq i \neq k$.
-Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-We set the following.
-\begin{itemize}
-    \item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
+    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_\ell')=2n\cdot (i+j)\cdot(\ell'-\ell)+1$.
+    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+5$.
+\end{itemize}
+
+Next, consider the validation gadget for color $i$. First, assume $1\neq i \neq k$. 
+%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
+%\begin{itemize}
+    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
     %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-\end{itemize}
-
-For all $0\le j<j'<i$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)$.
-\end{itemize}
+%\end{itemize}
+%
+For all $0\le j<j'<i$ and all $i<j<j'\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)-1$.
+\end{itemize}
+For all $0\le j<i$ and $\ell\in[n+3]$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,\hat{u}^i_{\ell})=6(i-j-1)+2\ell-1$.
+\end{itemize}
+For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
+\begin{itemize}
+    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
+\end{itemize}
+For all $0\le j<i$ and all $i<j'\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)+2n-1$.
+\end{itemize}
+For all $\ell\in[n+3]$ and $i<j\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(\hat{u}^i_{\ell},v^i_j)=6(j-i)+2(n-\ell)+5$.
+\end{itemize}
+
+Finally, we consider the alignment gadget.
+Let $x_1$ belong to the edge selection gadget of color combination $i,j$.
+Then we set $d(w^\star,x_1)=6(i+j)$.
+Let $\hat{v}_1$ belong to some connector gadget.
+Then we set $d(w^\star,\hat{v}_1)=n^5$.
+
+All distances between non-adjacent vertex pairs that are not specified above are set to infinity.
+
+This finishes the construction of the \deltaExactLong\ instance, which can clearly be computed in polynomial time.
+As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
 \end{proof}
@@
     Note that since we have determined the label of the edge $w r_i$, we also know the waiting times 
-    at vertex $u$ coming from each of its neighbor $v_i$ and finishing in $r_i$. 
+    at vertex $u$ coming from each of its neighbors $v_i$ and finishing in $r_i$. 
     At the beginning we have also determined the fastest paths from $u$ to all $v_i \in N_{G'}(w)$.

### 2023-01-30 RealizingTemporalGraphs.tex
Monday 30th Jan

@@
 \end{definition}
-From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe also that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
+%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
+Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
+In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$, 
+which we prove later on (see~\cref{obs:FPT-k2segments}).
 %For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
@@
     In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length $4$, we fix an arbitrary vertex $v_i \in S_{u,v}$.
+    If $S_{u,v}$ is not of length $4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
     Let 
@@
     \end{enumerate}
+    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
+    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
     \item \label{FPT:guess-splitFromUtoAnotherSegment}
@@
 In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
-\todo{Chenge/explain}
+\todo{Change/explain what ``with respect to first label'' means}
 %In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
@@
 \end{proof}
-
-%From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
+From the above it follows that
+after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest
+there is at most one fully determined segment among two vertices of interest and at most one undetermined segment.
+Therefore the following holds.
+\begin{observation}\label{obs:FPT-k2segments}
+    There are at most $O(k^2)$ segments in $G'$.
+\end{observation}
+
 Now we want to relate the not yet determined segments with the determined ones.
@@
         Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$ (not trough $p$).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$,
+        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
+        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
+        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
         we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.

### 2023-01-30 RealizingTemporalGraphs.tex
Added figures. Monday 30th Janurary

@@
 \graphicspath{{Figures/}}
+
+\usepackage{tikz}
+
+\usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
+\usetikzlibrary{shapes,calc,patterns,arrows.meta,snakes}
+\tikzset{
+	vert/.style={circle,inner sep=1.5,fill=white,draw,minimum size=.3cm},
+	edge/.style={color=black, thick},
+	diredge/.style={->,>={Stealth[width=8pt,length=8pt]},color=black, thick},
+	timelabel/.style={fill=white,font=\footnotesize, text centered},
+	wave/.style={decorate,decoration={coil,aspect=0}},
+	dirwave/.style={->, >={Stealth[width=8pt,length=8pt]},decorate,decoration={coil,aspect=0}},
+	diredge2/.style={->,>={Stealth[width=8pt,length=8pt]}}
+}
 
@@
 \usepackage[noend]{algpseudocode}
+
+\newenvironment{claimproof}{\noindent\emph{Proof of Claim.}}{\hfill$\diamond$
+
+}
 
@@
 
-This finished the description of the underlying graph $G$. We can observe that the vertex set containing
+This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
 \begin{itemize}
@@
 \end{itemize}
+Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_1',\hat{v}_2'$ and with sets $A'$ and $B'$.
+\begin{itemize}
+    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
+    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
+    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
+    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
+\end{itemize}
 
@@
     \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_\ell')=2n\cdot (i+j)\cdot(\ell'-\ell)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+5$.
+    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+3$.
 \end{itemize}
@@
 Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$.
-Then we set $d(w^\star,x_1)=6(i+j)$.
-Let $\hat{v}_1$ belong to some connector gadget.
-Then we set $d(w^\star,\hat{v}_1)=n^5$.
+Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
+Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
+Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
+\begin{itemize}
+    \item We set $d(w^\star,x_1)=6(i+j)$.
+    \item We set $d(w,\hat{v}_1)=n^5-6(i+j)+1$ and $d(w,\hat{v}_2)=n^5-6(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w,v)=n^5-6(i+j)+3$.
+\end{itemize}
+Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^5$.
 
@@
 
+\begin{figure}%[t]
+\begin{center}
+\begin{tikzpicture}[line width=1pt, scale=.7]
+\footnotesize
+\draw[rounded corners, dashed, gray] (-13, 5) rectangle (8, 1.5) {};
+\node (A) at (-10.5,4.5) {alignment gadget};
+
+\draw[rounded corners, dotted, gray] (-12, -2.5) rectangle (-10, -7.5) {};
+\draw[rounded corners, dotted, gray] (-12, -10.5) rectangle (-10, -15.5) {};
+\draw[rounded corners, dotted, gray] (7, -2.5) rectangle (9, -7.5) {};
+\node[rotate=90] (A) at (-12.5,-13) {connector gadget};
+
+\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -27) {};
+\node (A) at (-4,-26) {edge selection gadget for $i,j$};
+
+\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -27) {};
+\node[rotate=-90] (A) at (7,-18) {verification gadget for $i$};
+
+    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
+    \node[vert] (W1) at (-6.5,2) {};
+    \node[vert] (W2) at (-10,2) {};
+    \node[vert] (W3) at (-12,2) {};
+    \node[vert] (W4) at (7,2) {};
+
+    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
+    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-11,-5) {}; 
+    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-11,-7) {};
+
+    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-11) {}; 
+    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-11,-13) {}; 
+    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-11,-15) {};
+
+    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
+    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (8,-5) {}; 
+    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (8,-7) {};
+
+    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
+    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
+    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
+    \node (A) at (-2,0) {$\ldots$};
+    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
+
+    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
+
+    \node[vert,label=left:$y_1$] (Y1) at (-8,-6) {}; 
+    \node[vert,label=left:$y_2$] (Y2) at (-6,-6) {}; 
+    \node[vert,label=left:$y_3$] (Y3) at (-4,-6) {}; 
+    \node (A) at (-2,-6) {$\ldots$};
+    \node[vert,label=right:$y_m$] (YM) at (0,-6) {};
+
+    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
+    \node[vert,label=left:$u^1_2$] (U12) at (-6,-8) {}; 
+    \node[vert,label=left:$u^1_3$] (U13) at (-4,-8) {}; 
+    \node (A) at (-2,-8) {$\ldots$};
+    \node[vert,label=right:$u^1_m$] (U1M) at (0,-8) {};
+
+    \node[vert,label=left:$u^2_1$] (U21) at (-8,-10) {}; 
+    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
+    \node[vert,label=left:$u^2_3$] (U23) at (-4,-10) {}; 
+    \node (A) at (-2,-10) {$\ldots$};
+    \node[vert,label=right:$u^2_m$] (U2M) at (0,-10) {};
+
+    \node (A) at (-8,-11.5) {$\vdots$}; 
+    \node (A) at (-6,-11.5) {$\vdots$}; 
+    \node (A) at (-4,-11.5) {$\vdots$}; 
+    \node (A) at (0,-11.5) {$\vdots$};
+
+    \node[vert,label=left:$u^n_1$] (UN1) at (-8,-13) {}; 
+    \node[vert,label=left:$u^n_2$] (UN2) at (-6,-13) {}; 
+    \node[vert,label=left:$u^n_3$] (UN3) at (-4,-13) {}; 
+    \node (A) at (-2,-13) {$\ldots$};
+    \node[vert,label=right:$u^n_m$] (UNM) at (0,-13) {};
+
+    \node[vert,label=left:$u^{n+1}_1$] (UN11) at (-8,-17) {}; 
+    \node[vert,label=left:$u^{n+1}_2$] (UN12) at (-6,-17) {}; 
+    \node[vert,label=left:$u^{n+1}_3$] (UN13) at (-4,-17) {}; 
+    \node (A) at (-2,-17) {$\ldots$};
+    \node[vert,label=right:$u^{n+1}_m$] (UN1M) at (0,-17) {};
+
+    \node (A) at (-8,-18.5) {$\vdots$}; 
+    \node (A) at (-6,-18.5) {$\vdots$}; 
+    \node (A) at (-4,-18.5) {$\vdots$}; 
+    \node (A) at (0,-18.5) {$\vdots$};
+
+    \node[vert,label=left:$u^{2n}_1$] (U2N1) at (-8,-20) {}; 
+    \node[vert,label=left:$u^{2n}_2$] (U2N2) at (-6,-20) {}; 
+    \node[vert,label=left:$u^{2n}_3$] (U2N3) at (-4,-20) {}; 
+    \node (A) at (-2,-20) {$\ldots$};
+    \node[vert,label=right:$u^{2n}_m$] (U2NM) at (0,-20) {};
+
+    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VSS) at (-4,-24.5) {};
+
+    \node[vert,label=right:$v_0^i$, fill=gray] (VI0) at (5,0) {};
+    \node[vert,label=right:$v_1^i$, fill=gray] (VI1) at (5,-3) {};
+    \node (A) at (5,-5) {$\vdots$};
+    \node[vert,label=right:$v_{j-1}^i$, fill=gray] (VIJ1) at (5,-7) {};
+    \node[vert,label=right:$v_{j}^i$, fill=gray] (VIJ) at (5,-11) {};
+    \node (A) at (5,-13) {$\vdots$};
+    \node[vert,label=right:$v_{i-1}^i$, fill=gray] (VII1) at (5,-15) {};
+    \node[vert,label=right:$\hat{u}_{1}^i$] (UI1) at (5,-17) {};
+    \node[vert,label=right:$\hat{u}_{2}^i$] (UI2) at (5,-19) {};
+    \node (A) at (5,-20.5) {$\vdots$};
+    \node[vert,label=right:$\hat{u}_{n+3}^i$, fill=gray] (UIN3) at (5,-22) {};
+    \node (A) at (5,-24) {$\vdots$};
+    \node[vert,label=right:$v_{k}^i$, fill=gray] (VIK) at (5,-26) {};
+
+	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
+	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
+	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
+	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
+
+    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
+	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
+	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
+	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
+
+    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
+	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
+	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
+	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
+
+    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
+	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
+	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
+	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
+
+    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+2$} (UN11);
+	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+2$} (UN12);
+	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+2$} (UN13);
+	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+2$} (UN1M);
+
+    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+4n+2$} (VSS);
+	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+4n+2$} (VSS);
+	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+4n+2$} (VSS);
+	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+4n+2$} (VSS);
+
+    \draw[edge] (VH11) --node[timelabel] {$n^5$} (VH12);
+	\draw[edge] (VH12) --node[timelabel] {$n^5+1$} (VH13);
+
+    \draw[edge] (VH21) --node[timelabel] {$n^5$} (VH22);
+	\draw[edge] (VH22) --node[timelabel] {$n^5+1$} (VH23);
+
+    \draw[edge] (VH31) --node[timelabel] {$n^5$} (VH32);
+	\draw[edge] (VH32) --node[timelabel] {$n^5+1$} (VH33);
+
+	\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
+	\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
+
+	\draw[edge] (W) --node[timelabel] {$1$} (W1);
+	\draw[edge] (W) --node[timelabel] {$1$} (W2);
+	\draw[edge] (W) --node[timelabel] {$1$} (W3);
+	\draw[edge] (W) --node[timelabel] {$1$} (W4);
+
+	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
+	\draw[edge] (VH11) --node[timelabel] {$n^5$} (W2);
+	\draw[edge] (VH21) edge[bend left=15] node[timelabel] {$n^5$} (W3);
+	\draw[edge] (VH31) --node[timelabel] {$n^5$} (W4);
+
+	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
+	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
+\end{tikzpicture}
+    \end{center}
+    \caption{...}\label{fig:hardness1}
+\end{figure}
+
 This finishes the construction of the \deltaExactLong\ instance, which can clearly be computed in polynomial time.
+For an illustration see \cref{fig:hardness1}.
 As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
+
+\emph{Correctness.} In the remainder we prove that $D$ is a yes-instance of \deltaExactLong\ if and only if the $H$ is a yes-instance of \textsc{Multicolored Clique}.
+
+$(\Rightarrow)$: Assume $D$ is a yes-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
+We have that the underlying graph $G$ is uniquely defined by $D$.
+We first prove a number of properties of $\lambda$.
 \end{proof}
@@
 Note that we can easily solve the \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function), and the running time of the algorithm would be too big.
-Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses.
+But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
+Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses (where $f$ is a super exponential function in the feedback edge number $k$).
 We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
@@
 Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore we can solve each of our ILP instances in FPT time with respect to $k$.
+Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
 
@@
     \item Preprocessing on graph $G$.
-Determine the set $E$ of feedback edges, the set $U$ of vertices of interest and the set $U^*$ of neighbors of vertices of interest, where $|E|, |U|, |U^*| \in O(k)$.
-    \item Guess what are the fastest temporal paths among vertices in $U$ and 
-    what are the fastest temporal paths among the vertices in $U^*$, that are of some specific form.
-    \begin{enumerate}
-        \item For each guess create an ILP instance $I$ with $f(k)$ variables.
-        \item Add constraints for all pairs of vertices.
-    \end{enumerate}
-    \item Solve the ILP instance $I$ and check if a solution exists. In the positive case create its corresponding labeling $\lambda_I$ and check if it satisfies $D$.
-    All in total we create $f(k)$ partial ILP instances, each with $f(k)$ variables and $O(n^c)$ constraints.
+    \item Guess desired structures and create ILP instances.
+    \item Add constraints to the ILP instances for all pairs of vertices.
+    \item Solve the ILP instances.
 \end{enumerate}
@@
     ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
+    %
+    For an example see~\cref{fig:FPT-guessG4}.
     \item \label{FPT:guess-uToSegmentz2}
@@
     For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
+    %
+    For an example see~\cref{fig:FPT-guessG5}.
     %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
@@
     \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
+    %
+    For an example see~\cref{fig:FPT-guessG6}.
     \item \label{FPT:guess-splitFromUtoAnotherSegment}
@@
     which produces $O(k^{k^2})$ new guesses.
+    %
+    For an example see~\cref{fig:FPT-guessG7}.
     % counter for guesses continues
@@
 \end{enumerate}
+%
+\begin{figure}[ht]
+	\begin{subfigure}{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+		\begin{tikzpicture}
+			%%%S_uv
+			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
+			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
+			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
+			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
+			\draw (v1) -- (v2) -- (vp1) -- (vp);
+
+			%%%% S_wz
+			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
+			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
+			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
+			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
+			\draw (z1) -- (z2) -- (zr1) -- (zr);
+
+			\draw [violet] (v2) edge[diredge2] (v1);
+
+			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
+			(v1) edge[dirwave] [out=250,in=120] (z1) 
+			(z1) edge[diredge2] (z2);
+
+			\draw [red] %[transform canvas={yshift=-0.5mm}] 
+			(v1) edge[dirwave] [out=300,in=90] (zr) 
+			(zr) edge[diredge2] (zr1);
+		\end{tikzpicture}}
+	\caption{Example of a guess G-4, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
+	\label{fig:FPT-guessG4}}
+	\end{subfigure}
+	\qquad
+	\begin{subfigure}{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+
+			\begin{tikzpicture}
+				%%%S_uv
+				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
+				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
+				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
+				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
+				\draw (v1) -- (v2) -- (vp1) -- (vp);
+
+				%%%% node w
+				\node[vert,label=below:$w$] (w) at (4,-3) {};
+
+				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
+				(w) edge[dirwave] [out=160,in=285] (v1) 
+				(v1) edge[diredge2] (v2);
+
+				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
+				(w) edge[dirwave] [out=20,in=255] (vp) 
+				(vp) edge[diredge2] (vp1);
+
+			\end{tikzpicture}}
+		\caption{Example of a guess G-5, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red). 
+			\label{fig:FPT-guessG5}}
+	\end{subfigure}
+	%
+	\begin{subfigure}{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+
+		\begin{tikzpicture}
+			%%%S_uv
+			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
+			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
+			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
+			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
+			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
+			\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
+
+			%%%% S_wz
+			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
+			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
+			\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
+			\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
+			\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
+			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
+			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
+			\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
+
+			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
+			(vi) -- (v2) edge[diredge2] (v1) 
+			(v1) edge[wave] (3,1.3) 
+			(3,1.3) edge[wave] (8,1.3)
+			(8,1.3) edge[dirwave] (zr) 
+			(zr) --(zr1) -- (zj+1)
+			(zj+1) edge[diredge2] (zj);
+
+			\draw [red]
+			(vi) -- (vp1) edge[diredge2] (vp) 
+			(vp) edge[dirwave] [out=250,in=60] (z1) 
+			(z1) --(z2)
+			(z2) edge[diredge2] (zj-1);
+
+		\end{tikzpicture}}
+		\caption{Example of a guess G-6, where, for fixed a vertex $v_i \in S_{u,v}$,
+		we calculated its corresponding split vertex $z_j \in S_{w,z}$,
+		and guessed the fastest paths of form
+		$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
+		and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
+			\label{fig:FPT-guessG6}}
+	\end{subfigure}
+	\qquad
+	\begin{subfigure}{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+		\begin{tikzpicture}
+			%%%S_uv
+			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
+			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
+			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
+			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
+			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
+			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
+			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
+
+			%%%% node w
+			\node[vert,label=below:$w$] (w) at (4,-3) {};
+
+			\draw [blue] 
+			(w) edge[dirwave] [out=160,in=285] (v1) 
+			(v1) -- (v2)
+			(v2) edge[diredge2] (vi);
+
+			\draw [red]
+			(w) edge[dirwave] [out=20,in=255] (vp) 
+			(vp) -- (vp1)
+			(vp1) edge[diredge2] (vi+1);
+
+		\end{tikzpicture}}
+	\caption{Example of a guess G-7, where, for a vertex of interest $w$, 
+		we
+		calculated its corresponding split vertex $v_i \in S_{u,v}$,
+		and guessed the fastest paths of form
+		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
+		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
+		\label{fig:FPT-guessG7}}
+	\end{subfigure}
+\caption{An example of guesses G-4, G-5, G-6 and G-7.}
+\end{figure}
+%
 We create all of the guesses independently.
@@
 
+\subsection{Solving ILP instances}
+All of the above finishes our construction of ILP instances.
+We have created $f(k)$ instances (where $f$ is a super exponential function), 
+each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a super exponential function).
+We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
+in the FPT time, with respect to $k$.
+If none of the ILP instances gives a positive solution, then there exsist no labeling $\lambda$ of $G$ that would preserve all the fastest durations from $D$.
+In the case when there is at least one $I$ that has a valid solution $X$, 
+we use the solution $X$ and produce our labelling $\lambda$.
+We use the following procedure,
+first we
+label each edge $e$, that corresponds to the variable $x_e$
+by assigning the value $\lambda(e) = x_e$.
+We then continue to set the labels of all other edges. 
+We know that all of the labels of these edges depend on the label of (at least one) of the edges that were determined in previous step. 
+Therefore we easily calculate the desired labels for all remaining edges.
+At the end we have a labeling $\lambda$ of $G$, that preserves all the distances from $D$.
+This follow from the fact that ILP consisted of constraints for all temporal paths,
+\ie
+it cannot happen that there is a fastest temporal path $P_{u,v}$ among two vertices $u,v$ in $(G,\lambda)$ 
+for which $P_{u,v} \neq D_{u,v}$.
+
 \begin{comment}

### 2023-01-31 RealizingTemporalGraphs.tex
Updates from Overleaf
merged
Changes Tuesday 31st of Jan

@@
 \usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
-\usetikzlibrary{shapes,calc,patterns,arrows.meta,snakes}
+\usetikzlibrary{shapes,calc,patterns,arrows.meta}
 \tikzset{
@@
 %% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Simple $\Delta$-periodic Exact Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Simple $\Delta$-TGR}}
+\newcommand{\deltaExactLong}{\textsc{Simple periodic Temporal Graph Realization}}
+\newcommand{\deltaExact}{\textsc{Simple TGR}}
 
@@
 	\maketitle
-
-\section{Ideas}
-\begin{itemize}
-    \item Symmetric distance matrix $D$: polytime?
-    \item Use $|D|_\infty$ (maximum value in $D$) + max degree $\Delta$ as parameter $\rightarrow$ should give FPT
-    \item FPT with feedback edge number
-    \item use as parameter $\max_{i,j} |D_{i,j}-D_{j,i}|$
-    \item approximation (additive or multiplicative), maybe with graph as input
-\end{itemize}
 
@@
 \problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$.}
+{An $n \times n$ matrix $D$, positive integer $\Delta$.}
 {Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
@@
 
-\problemdef{\kDeltaExactLong\ (\kDeltaExact)}
-{An $n \times n$ matrix $D$ of positive integers.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
-
-\problemdef{\kDeltaUpperBoundLong}
-{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{i,j}$.}
-
-\problemdef{\kDeltaLowerBoundLong}
-{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
-{Does there exist a graph $G=(V,E)$ on the vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at least} $D_{i,j}$.}
-\todo[inline]{NOT TEMPORALLY INTERESTING: the difficulty is to find a static graph with equal labels}
-
-\todo[inline]{The matrix $D$ is m x m, and capturing the distances from an edge e to an edge f (zoom 14 Nov 22, GH).}
-\todo[inline]{Check if the reduction works for the UPPER BOUNDED version (seems to work)}
-\todo[inline]{how to extend the poly algorithms of cycles? Easy candidate: FES, FVS, series-parallel graphs, or tw=2 graphs}
-\todo[inline]{FVS, $c$-factor approximation, hardness of approximation for $c<1.5$}
-
 Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$ that we are looking for in the above problems. 
@@
 
+\begin{comment}
 \begin{definition}[$D$-increasing temporal path]
@@
 \end{definition}
-
-\begin{observation}
-Let $D$ be a \textsc{YES}-instance of \textsc{$(k,\Delta)$-TGR}, and let 
-$(G,\lambda,\Delta)$ be a certificate for $D$, where $\lambda:E\rightarrow \{1,2,\ldots,\Delta\}^k$ is a $\Delta$-periodic labeling of $G$.
-Then, for every pair $u,v$ of vertices of $G$, every fastest temporal path from $u$ to $v$ is $D$-increasing.
-\end{observation}
+\end{comment}
 
@@
 Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wo et.~al. \cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
+In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
 $O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
@@
     \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the temporal path from $v_0$ to $v_p$..
+        Let $P = (v_0, v_1, \dots, v_p)$ be the temporal path from $v_0$ to $v_p$.
         Then $d(P) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
@@
 
-\begin{claim} \label{claim:unique-fastest-path-allDelays}
+\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
     Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact,
@@
     for all $i \in \{2,3, \dots, k-1\}$.
-\end{claim}
+\end{lemma}
 
@@
     Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $P_{i,j}$.
-    Now using \cref{claim:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
+    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
 \end{observation}
@@
     The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{claim:matrixT-travelDelays-tree}
+    \begin{lemma}\label{lemma:matrixT-travelDelays-tree}
         Matrix $T$ consists of travel delays of all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{proof}[Proof of \cref{claim:matrixT-travelDelays-tree}]
+    \end{lemma}
+    \begin{proof}[Proof of \cref{lemma:matrixT-travelDelays-tree}]
         Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
@@
 
-\begin{claim} \label{claim:poly-delta-cycle-monotonicity}
+\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
     If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
@@
     where the indices are taken modulo $n$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{claim:poly-delta-cycle-monotonicity} and \cref{claim:unique-fastest-path-allDelays},
+Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
 we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
@@
 Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{claim:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
+Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
 and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
@@
 the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{claim:poly-delta-cycle-monotonicity} and \cref{claim:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
+By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
 which we store in a list $T$ of length $n$,
@@
 
-\begin{claim}
+\begin{lemma}
 List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
     %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ containing vertices of other gadgets. 
+    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
     Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
@@
 \begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_1)=2$, $d(\hat{v}_1,\hat{v}_2)=2$, and $d(\hat{v}_0,\hat{v}_2)=3$.
+    \item We set $d(\hat{v}_0,\hat{v}_2)=2$.
     \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$.
@@
 We first prove a number of properties of $\lambda$.
+
+To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
+\begin{claim}\label{claim:1}
+    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
+\end{claim}
+\begin{claimproof}
+    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
+Let w.l.o.g.\ $t<t'$.
+Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
+\end{claimproof}
+\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
+
+Next, we analyse the labelings of connector gadgets.
+\begin{claim}\label{claim:2}
+    Let $\hat{v}_0$, $\hat{v}_1$, and $\hat{v}_2$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have the following:
+    \begin{itemize}
+        \item $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^5$.
+        \item $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^5+1$.
+        \item For all $v\in V^\star$ we have $\lambda(\{\hat{v}_1,v\})\ge n^5$ and $\lambda(\{\hat{v}_2,v\})\ge n^5$.
+        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^5$ and $\lambda(\{\hat{v}_2,v\})=n^5+2$.
+        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^5$ and $\lambda(\{\hat{v}_2,v\})=n^5$.
+        %\item For all $v\in V^\star \setminus A$ we have $\lambda(\{\hat{v}_1,v\})=n^5+2$ and $\lambda(\{\hat{v}_2,v\})=n^5$.
+    \end{itemize}
+\end{claim}
+\begin{claimproof}
+    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
+We have $d(w^\star,\hat{v}_0)=n^5$.
+It follows that $\lambda(\{w,\hat{v}_0\})=n^5$.
+Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^5$.
+    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$. Since $d(\hat{v}_0,\hat{v}_2)=2$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^5+1$.
+
+    %Let $v\in B$. Note that $d(\hat{v}_0,v)=\infty$ and $d(v,\hat{v}_0)=\infty$. It follows that $\lambda(\{\hat{v}_1,v\})=n^5$.
+Let $v\in V^\star$. Note that $d(v,\hat{v}_0)=\infty$. It follows that $\lambda(\{\hat{v}_1,v\})\ge n^5$.
+\end{claimproof}
 \end{proof}
@@
 But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses (where $f$ is a super exponential function in the feedback edge number $k$).
+Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses (where $f$ is a double exponential function in the feedback edge number $k$).
 We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
@@
 and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with $U = V_1 \cup V_2 \cup V_3$ the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie $U^* = \{v \in V(G') \setminus U | u \in U, v \in N(u)\}$.
+We denote with 
+$$U = V_1 \cup V_2 \cup V_3$$
+the set of vertices of interest. It follows that $|U| \leq 4k$.
+We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
+$$U^* = \{v \in V(G') \setminus U | u \in U, v \in N(u)\}.$$
 Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $U^* \in O(k^2)$.
-
-The whole Step 1 is performed in $O(n + m)$ time.
+Determining all of the above sets takes us linear time.
 
@@
 
-\subsection{Creating ILP instances and determining variables}
+\subsection{Guessing necessary structures}
 We start the algorithm by guessing necessary structures.
@@
 After creating all of the guesses we end up with exponential in $k$ different cases.
-We now create one partial ILP instance for each case.
+We now create one ILP instance for each case.
 From now on we assume that we know exactly the structure of all paths we have guessed and the permutation of all variables.
@@
 and if $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges.
-For the exact formulation and proofs see \cref{claim:FPT-uv-Labelalledges,claim:FPT-uv-LabelAlmostalledges}.
-
-\begin{claim}\label{claim:FPT-uv-Labelalledges}
+For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
+
+\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
     Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
@@
     %such that the labeling $\lambda$ respects $D'$.
-\end{claim}
+\end{lemma}
 
@@
 and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 + (v,v_{p-1}, \dots, v_i) > d(P) > d(P_i)$.
+But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
 
@@
 we set the first label of $P$ to be a constant $c_{uv}$.
-This gives us a unique label for each edge of $P$, that depends on the value $c_{u,v}$.
+This gives us a unique label for each edge of $P$, that depends on the value $c_{uv}$.
 \end{proof}
 
-\begin{claim}\label{claim:FPT-uv-LabelAlmostalledges}
+\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
     Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
@@
     Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
-\end{claim}
+\end{lemma}
 
@@
 or there exists a fastest temporal path $P' = (u, w_2, w_3, \dots, w_{p'} = v_i)$, for which $P \cap P' = \{u, v_i\}$.
-If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{claim:FPT-uv-Labelalledges}.
+If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{lemma:FPT-uv-Labelalledges}.
 So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.
@@
 
-\begin{claim}\label{claim:FPT-unlabeldPaths-01}
+\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
     Suppose that
@@
     Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or $z,v$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-Labelalledges}).
+If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
 %Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
+In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
 \todo{Change/explain what ``with respect to first label'' means}
@@
 
-\begin{claim}
+\begin{lemma}
     Not yet determined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
     \ie for every not yet determined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p=v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_{p-1} \in V(G') \setminus U$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{claim}
+\begin{lemma}
     After determining the labels of fastest temporal paths between all pairs of vertices of interest,
@@
     %among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 From the above it follows that
-after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest
+after we finish determining the labels for all fastest temporal paths among vertices of interest,
 there is at most one fully determined segment among two vertices of interest and at most one undetermined segment.
 Therefore the following holds.
-\begin{observation}\label{obs:FPT-k2segments}
+\begin{corollary}\label{obs:FPT-k2segments}
     There are at most $O(k^2)$ segments in $G'$.
-\end{observation}
+\end{corollary}
 
@@
     Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{claim:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
+    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
     This results in adding the equality constraint for this fastest temporal path.
@@
 To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{claim}
+\begin{lemma}
 Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a root of $T_i$.
@@
 Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a super exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a super exponential function).
+We have created $f(k)$ instances (where $f$ is a double exponential function), 
+each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
 We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
@@
 
+\section{Ideas}
+\begin{itemize}
+    \item Symmetric distance matrix $D$: polytime?
+    \item Use $|D|_\infty$ (maximum value in $D$) + max degree $\Delta$ as parameter $\rightarrow$ should give FPT
+    \item FPT with feedback edge number
+    \item use as parameter $\max_{i,j} |D_{i,j}-D_{j,i}|$
+    \item approximation (additive or multiplicative), maybe with graph as input
+\end{itemize}
+
+\problemdef{\kDeltaExactLong\ (\kDeltaExact)}
+{An $n \times n$ matrix $D$ of positive integers.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
+
+\problemdef{\kDeltaUpperBoundLong}
+{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{i,j}$.}
+
+\problemdef{\kDeltaLowerBoundLong}
+{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
+{Does there exist a graph $G=(V,E)$ on the vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at least} $D_{i,j}$.}
+\todo[inline]{NOT TEMPORALLY INTERESTING: the difficulty is to find a static graph with equal labels}
+
+\todo[inline]{The matrix $D$ is m x m, and capturing the distances from an edge e to an edge f (zoom 14 Nov 22, GH).}
+\todo[inline]{Check if the reduction works for the UPPER BOUNDED version (seems to work)}
+\todo[inline]{how to extend the poly algorithms of cycles? Easy candidate: FES, FVS, series-parallel graphs, or tw=2 graphs}
+\todo[inline]{FVS, $c$-factor approximation, hardness of approximation for $c<1.5$}
+
 \end{document}

### 2023-02-01 ICALP23-RealizingTemporalGraphs.tex
Changes 31st Jan

--- 2023-01-31 RealizingTemporalGraphs.tex
@@
-\documentclass[11pt,a4paper]{article}
-
-\usepackage[english]{babel}
-
-\usepackage{fullpage}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
+%This is a template for producing LIPIcs articles. 
+%See lipics-v2021-authors-guidelines.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+%for section-numbered lemmas etc., use "numberwithinsect"
+%for enabling cleveref support, use "cleveref"
+%for enabling autoref support, use "autoref"
+%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
+%for enabling thm-restate support, use "thm-restate"
+%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
+%for producing a PDF according the PDF/A standard, add "pdfa"
+
+%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 
 \usepackage{amsmath}
-\let\proof\relax
-\let\endproof\relax
+%\let\proof\relax
+%\let\endproof\relax
 
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{observation}{Observation}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\theoremstyle{remark}
-\newtheorem{remark}[theorem]{Remark}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[definition]{Example}
 \usepackage{comment}
@@
 \usepackage[noend]{algpseudocode}
-
-\newenvironment{claimproof}{\noindent\emph{Proof of Claim.}}{\hfill$\diamond$
-
-}
 
@@
 
-\usepackage[capitalise,nameinlink, noabbrev]{cleveref}
 \crefname{claim}{Claim}{Claims}
-\crefname{observation}{Observation}{Observations}
-
-\usepackage{authblk}
 
@@
 \newcommand{\ie}{i.\,e.,\ }
-\newcommand{\st}{s.\,t.,\ }
+\renewcommand{\st}{s.\,t.,\ }
 \newcommand{\NP}{\textrm{NP}}
@@
 
-\title{Realizing Temporal Graphs}
-\author{Nina Klobas, George B. Mertzios, Hendrik Molter, Paul G. Spirakis}
-
-\bibliographystyle{abbrv}
+\bibliographystyle{plainurl}% the mandatory bibstyle
+
+\title{Realizing temporal graphs from fastest travel times} %TODO Please add
+
+%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
+
+%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
+
+%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
+
+%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
+
+%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
+
+%\authorrunning{Nina Klobas, George B.
+Mertzios, Hendrik Molter, and Paul G.
+Spirakis} %TODO mandatory.
+First: Use abbreviated first/middle names.
+Second (only in severe cases): Use first author plus 'et al.'
+
+%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
+\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
+%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+
+\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
+
+\category{} %optional, e.g. invited paper
+
+\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%\relatedversiondetails[linktext={opt.
+text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
+Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
+
+%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+%\supplementdetails[linktext={opt.
+text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
+Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
+
+%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
+Please enter author specific funding statements as fifth argument of the \author macro.
+
+%\acknowledgements{I want to thank \dots}%optional
+
+%\nolinenumbers %uncomment to disable line numbering
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 \maketitle
+
+\begin{abstract}
+In this paper we study \emph{temporal design} problems of undirected temporally connected graphs. 
+The basic setting of these optimization problems is as follows: given an undirected graph~$G$, 
+what is the smallest number $|\lambda|$ of time-labels that we need to add to the edges of $G$ such that the resulting temporal graph $(G,\lambda)$ is temporally connected?
+
+\vspace{0,2cm}
+\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
+	clearly marked Appendix to be read at the discretion of the Program Committee.}
+\end{abstract}
+
+\section{Introduction}\label{intro-sec}
+
+Graph realization problems are fundamental graph-algorithmic questions where the objective is to (re)construct a graph, 
+given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
+are the vertex degrees~\cite{}, distances~\cite{}, eccentricities~\cite{}, connectivity~\cite{}, etc. 
+The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{.....}.
 
@@
 
+\section{Motivation}
+
+	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
+	which implies that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
+	then the shortest path from $u$ to $w$ is a subpath of $P$.
+	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
+	one can see that this property does not carry over.
+	For an example see~\cref{fig:ftpExample}.
+	Which makes all the standard intuition and work with these kind of paths, much harder.
+
+	\begin{figure}[h]
+    \centering
+	\begin{tikzpicture}[xscale=2]
+	%%%S_uv
+	\node[vert,label=below:$u$] (v1) at (1,0) {};
+	\node[vert] (v2) at (2,0) {};
+	\node[vert,label=below:$w$] (v3) at (3,0) {};
+	\node[vert] (v4) at (4,0) {};
+	\node[vert,label=below:$v$] (v5) at (5,0) {};
+	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
+	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
+
+	\draw[transform canvas={yshift=-1.5mm}, blue]
+	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
+
+	\draw[red]
+	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
+\end{tikzpicture}
+	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
+		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$ that is on a path $P_{u,v}$ is of duration $1$ and is not a subpath of $P_{u,v}$.		
+		\label{fig:ftpExample}}
+	\end{figure}
+
 %\section{Results}
 
-\section{
-\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}}
+\section{\deltaExact}
 
@@
 
-\subsection{
-\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}
-is polynomial-time solvable on trees and paths}
+\subsection{ \deltaExact\ is polynomial-time solvable on trees and paths}
 
@@
 
-\subsection{
-\texorpdfstring{\deltaExact\ } {Simple Delta-TGR}
+\subsection{ \deltaExact\
 is polynomial-time solvable on cycles}
@@
 
-    $d(c,x_F)=2$.
+    $d(c,x^F)=2$.
 
@@
 
-    $d(c,x_T)=2$.
+    $d(c,x^T)=2$.
     \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
@@
 \end{itemize}
+%
+\begin{figure}[h]
+	\noindent
+	\makebox[\textwidth]{
+		\centering
+\begin{tikzpicture}%[xscale=2]
+
+	%%Variable X1
+	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
+	\node[vert,label=right:$x_1^F$] (x1f) at (3,0) {};
+	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
+	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
+
+	%%Variable X2
+	\node[vert,label=left:$x_2^T$] (x2t) at (5,0) {};
+	\node[vert,label=right:$x_2^F$] (x2f) at (7,0) {};
+	\node[vert,label=above:$x_2$] (x2) at (6,1) {};
+	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
+
+	%%Variable x3
+	\node[vert,label=left:$x_3^T$] (x3t) at (9,0) {};
+	\node[vert,label=right:$x_3^F$] (x3f) at (11,0) {};
+	\node[vert,label=above:$x_3$] (x3) at (10,1) {};
+	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
+
+	%%Variable x4
+	\node[vert,label=left:$x_4^T$] (x4t) at (13,0) {};
+	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
+	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
+	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
+
+	%%vertices for clauses c1, c2 + vertex v
+	\node[vert,label=above:$v$] (v) at (8,3) {};
+	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
+	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
+
+	%%% edges between x1 gadget and v,c1,c2
+	\draw (x1t) to node[timelabel] {$1$} (c1);
+	\draw (x1t) to node[timelabel] {$1$} (c2);
+	\draw (x1t) to [out=90,in=190] (v);
+	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
+
+	%%% edges between x2 gadget and v,c1,c2
+	\draw (x2f) to node[timelabel] {$1$} (c1);
+	\draw (x2t) to node[timelabel] {$1$} (c2);
+	\draw (x2t) to [out=80,in=210]  (v);
+	\draw (x2f) to node[timelabel] {$3$} (v);
+
+	%%% edges between x3 gadget and v,c1
+	\draw (x3t) to node[timelabel] {$1$} (c1);
+	\draw (x3t) to node[timelabel] {$3$} (v);
+	\draw (x3f) to [out=100,in=330] (v);
+
+	%%% edges between x4 gadget and v,c2
+	\draw (x4t) to node[timelabel] {$1$} (c2);
+	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
+	\draw (x4f) to [out=90,in=360] (v);
+
+	%% edges among xt, xf vertices
+	%x1 to all
+	\draw [dotted] (x1t) [out=30,in=150] to (x2t);
+	\draw [dotted] (x1t) [out=30,in=150] to (x3t);
+	\draw [dotted] (x1t) [out=30,in=150] to (x4t);
+	\draw [dotted] (x1t) [out=30,in=150] to (x2f);
+	\draw [dotted] (x1t) [out=30,in=150] to (x3f);
+	\draw [dotted] (x1t) [out=30,in=150] to (x4f);
+
+	\draw [dotted] (x1f) [out=30,in=150] to (x2t);
+	\draw [dotted] (x1f) [out=30,in=150] to (x3t);
+	\draw [dotted] (x1f) [out=30,in=150] to (x4t);
+	\draw [dotted] (x1f) [out=30,in=150] to (x2f);
+	\draw [dotted] (x1f) [out=30,in=150] to (x3f);
+	\draw [dotted] (x1f) [out=30,in=150] to (x4f);
+	%x2 to all
+	\draw [dotted] (x2t) [out=30,in=150] to (x3t);
+	\draw [dotted] (x2t) [out=30,in=150] to (x4t);
+	\draw [dotted] (x2t) [out=30,in=150] to (x3f);
+	\draw [dotted] (x2t) [out=30,in=150] to (x4f);
+
+	\draw [dotted] (x2f) [out=30,in=150] to (x3t);
+	\draw [dotted] (x2f) [out=30,in=150] to (x4t);
+	\draw [dotted] (x2f) [out=30,in=150] to (x3f);
+	\draw [dotted] (x2f) [out=30,in=150] to (x4f);
+	%x3 to all
+	\draw [dotted] (x3t) [out=30,in=150] to (x4t);
+	\draw [dotted] (x3t) [out=30,in=150] to (x4f);
+
+	\draw [dotted] (x3f) [out=30,in=150] to (x4t);
+	\draw [dotted] (x3f) [out=30,in=150] to (x4f);
+\end{tikzpicture}
+}
+\caption{Example of the temporal graph $(G_\phi,\lambda)$ from the NP-hardness reduction, 
+	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
+For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neg j$) with a dotted line.
+Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
+where all unlabeled edges get the label $2$.}
+\end{figure}
 \end{proof}
@@
     Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way.
+    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
 
@@
         \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        \item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        \item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^v_{2n}\}$ for all $\ell\in[m]$.
+        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
+        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
+        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^\ell_{2n}\}$ for all $\ell\in[m]$.
 Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
@@
     \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{y_\ell,v_{i,j}^\star\}$, and $\{z_\ell,v_{i,j}^{\star\star}\}$.
-
-        Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [2n-1]$, we have edge $\{u^\ell_{\ell'},u^\ell_{\ell'+1}\}$.
+        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{2n},v_{i,j}^{\star\star}\}$.
+
+        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
+        \item For all $\ell\in [m]$ and $\ell'\in [2n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
     \end{itemize}
@@
 
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget of color combination $j,i$.
+    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
+Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'-1}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
+    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
 
     If $1\neq i\neq k$, then we add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[n+2]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. 
-    Let $e_\ell\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},u^\ell_{n+\ell'}\}$ between $\hat{u}^i_{n+3}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,u^\ell_{n+\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget of color combination $i,j$.
+    Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
+If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},u^\ell_{n+\ell'-1}\}$ between $\hat{u}^i_{n+3}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
+If $i=1$, then we add edge $\{v^i_0,u^\ell_{n+\ell'-1}\}$ between $v^i_0$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
+
+    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
+Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'-1}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
+    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
 
@@
 Intuitively, these gadgets will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
-Connector gadgets consist of three vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$.
+Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
     %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
@@
     \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\}$.
+        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
         \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
@@
 
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$ and with sets $A$ and $B$.
+Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2,\hat{v}_3$ and with sets $A$ and $B$.
 Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
@@
 \begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=2$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$.
+    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
+    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
+    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
     \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
 \end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_1',\hat{v}_2'$ and with sets $A'$ and $B'$.
+Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
 \begin{itemize}
@@
 \begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_\ell')=2n\cdot (i+j)\cdot(\ell'-\ell)+1$.
+    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot(\ell'-\ell)+1$.
     \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+3$.
@@
 
-Next, consider the validation gadget for color $i$. First, assume $1\neq i \neq k$. 
+Next, consider the validation gadget for color $i$. 
 %Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
@@
 \end{itemize}
+The next cases are only relevant if $1\neq i \neq k$. 
 For all $0\le j<i$ and $\ell\in[n+3]$ we set the following.
@@
     \item We set $d(w^\star,x_1)=6(i+j)$.
-    \item We set $d(w,\hat{v}_1)=n^5-6(i+j)+1$ and $d(w,\hat{v}_2)=n^5-6(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w,v)=n^5-6(i+j)+3$.
+    \item We set $d(w,\hat{v}_1)=n^6-6(i+j)+1$ and $d(w,\hat{v}_2)=n^6-6(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w,v)=n^6-6(i+j)+3$.
 \end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^5$.
+Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^6$.
 
@@
 \begin{figure}%[t]
-\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.7]
-\footnotesize
+\noindent\makebox[\textwidth]{
+\centering
+%\begin{center}
+\begin{tikzpicture}[line width=1pt, scale=.65]
+\scriptsize
+\node (A) at (12,0) {};
+
 \draw[rounded corners, dashed, gray] (-13, 5) rectangle (8, 1.5) {};
@@
 
-\draw[rounded corners, dotted, gray] (-12, -2.5) rectangle (-10, -7.5) {};
-\draw[rounded corners, dotted, gray] (-12, -10.5) rectangle (-10, -15.5) {};
-\draw[rounded corners, dotted, gray] (7, -2.5) rectangle (9, -7.5) {};
-\node[rotate=90] (A) at (-12.5,-13) {connector gadget};
+\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
+\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
+\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
+\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
 
@@
     \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-11,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-11,-7) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-11) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-11,-13) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-11,-15) {};
+    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
+    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
+    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
+    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
+    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
+
+    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
+    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
+    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
+    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
+    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
+    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
 
     \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (8,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (8,-7) {};
+    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
+    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
+    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
+    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
+    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
 
@@
 
-    \node[vert,label=left:$y_1$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$y_2$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$y_3$] (Y3) at (-4,-6) {}; 
+    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
+    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
+    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
     \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$y_m$] (YM) at (0,-6) {};
+    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
 
     \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^1_2$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^1_3$] (U13) at (-4,-8) {}; 
+    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
+    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
     \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^1_m$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^2_1$] (U21) at (-8,-10) {}; 
+    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
+
+    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
     \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^2_3$] (U23) at (-4,-10) {}; 
+    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
     \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^2_m$] (U2M) at (0,-10) {};
+    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
 
@@
 
-    \node[vert,label=left:$u^n_1$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^n_2$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^n_3$] (UN3) at (-4,-13) {}; 
+    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
+    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
+    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
     \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^n_m$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u^{n+1}_1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u^{n+1}_2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u^{n+1}_3$] (UN13) at (-4,-17) {}; 
+    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
+
+    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
+    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
+    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
     \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u^{n+1}_m$] (UN1M) at (0,-17) {};
+    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
 
@@
 
-    \node[vert,label=left:$u^{2n}_1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u^{2n}_2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u^{2n}_3$] (U2N3) at (-4,-20) {}; 
+    \node[vert,label=left:$u_{2n}^1$] (U2N1) at (-8,-20) {}; 
+    \node[vert,label=left:$u_{2n}^2$] (U2N2) at (-6,-20) {}; 
+    \node[vert,label=left:$u_{2n}^3$] (U2N3) at (-4,-20) {}; 
     \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u^{2n}_m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VSS) at (-4,-24.5) {};
+    \node[vert,label=right:$u_{2n}^m$] (U2NM) at (0,-20) {};
+
+    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24.5) {};
 
@@
 
-    \draw[edge] (VH11) --node[timelabel] {$n^5$} (VH12);
-	\draw[edge] (VH12) --node[timelabel] {$n^5+1$} (VH13);
-
-    \draw[edge] (VH21) --node[timelabel] {$n^5$} (VH22);
-	\draw[edge] (VH22) --node[timelabel] {$n^5+1$} (VH23);
-
-    \draw[edge] (VH31) --node[timelabel] {$n^5$} (VH32);
-	\draw[edge] (VH32) --node[timelabel] {$n^5+1$} (VH33);
+    \draw[edge] (VH11) --node[timelabel,sloped] {$n^6$} (VH12);
+	\draw[edge] (VH12) --node[timelabel,sloped] {$n^6+1$} (VH111);
+	\draw[edge] (VH12) --node[timelabel] {$n^6+1$} (VH13);
+    \draw[edge] (VH13) --node[timelabel,sloped] {$n^6$} (VH14);
+	\draw[edge] (VH13) --node[timelabel,sloped] {$n^6+1$} (VH144);
+
+    \draw[edge] (VH21) --node[timelabel,sloped] {$n^6$} (VH22);
+	\draw[edge] (VH22) --node[timelabel,sloped] {$n^6+1$} (VH211);
+	\draw[edge] (VH22) --node[timelabel] {$n^6+1$} (VH23);
+    \draw[edge] (VH23) --node[timelabel,sloped] {$n^6$} (VH24);
+	\draw[edge] (VH23) --node[timelabel,sloped] {$n^6+1$} (VH244);
+
+    \draw[edge] (VH31) --node[timelabel,sloped] {$n^6$} (VH32);
+	\draw[edge] (VH32) --node[timelabel,sloped] {$n^6+1$} (VH311);
+	\draw[edge] (VH32) --node[timelabel] {$n^6+1$} (VH33);
+    \draw[edge] (VH33) --node[timelabel,sloped] {$n^6$} (VH34);	
+    \draw[edge] (VH33) --node[timelabel,sloped] {$n^6+1$} (VH344);
 
@@
 	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^5$} (W2);
-	\draw[edge] (VH21) edge[bend left=15] node[timelabel] {$n^5$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^5$} (W4);
+	\draw[edge] (VH11) --node[timelabel] {$n^6$} (W2);
+	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^6$} (W3);
+	\draw[edge] (VH31) --node[timelabel] {$n^6$} (W4);
 
@@
 \end{tikzpicture}
-    \end{center}
-    \caption{...}\label{fig:hardness1}
+    %\end{center}
+    }
+    \caption{Illustration of part of the underlying graph $G$ and a possible labelling.
+Edges incident with vertices of connector gadgets are omitted.
+Gray vertices form a feedback vertex set.}\label{fig:hardness1}
 \end{figure}
@@
 \begin{claim}\label{claim:2}
-    Let $\hat{v}_0$, $\hat{v}_1$, and $\hat{v}_2$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have the following:
-    \begin{itemize}
-        \item $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^5$.
-        \item $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^5+1$.
-        \item For all $v\in V^\star$ we have $\lambda(\{\hat{v}_1,v\})\ge n^5$ and $\lambda(\{\hat{v}_2,v\})\ge n^5$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^5$ and $\lambda(\{\hat{v}_2,v\})=n^5+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^5$ and $\lambda(\{\hat{v}_2,v\})=n^5$.
-        %\item For all $v\in V^\star \setminus A$ we have $\lambda(\{\hat{v}_1,v\})=n^5+2$ and $\lambda(\{\hat{v}_2,v\})=n^5$.
-    \end{itemize}
+    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
+    %\begin{itemize}
+        %\item 
+        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^6$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^6+2$,
+        %\item 
+        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^6+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^6$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^6+2$. 
+        %\item For all $v\in V^\star$ we have $n^6\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^6+2$.
+        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^6$ and $\lambda(\{\hat{v}_2,v\})=n^6+2$.
+        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^6$ and $\lambda(\{\hat{v}_2,v\})=n^6$.
+        %\item 
+        Furthermore, for all $v\in V^\star$ we have $n^6\le \lambda(\{\hat{v}_1,v\})\le n^6+2$ and $n^6\le \lambda(\{\hat{v}_2,v\}) \le n^6+2$.
+    %\end{itemize}
 \end{claim}
@@
     Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^5$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^5$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^5$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$. Since $d(\hat{v}_0,\hat{v}_2)=2$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^5+1$.
-
-    %Let $v\in B$. Note that $d(\hat{v}_0,v)=\infty$ and $d(v,\hat{v}_0)=\infty$. It follows that $\lambda(\{\hat{v}_1,v\})=n^5$.
-Let $v\in V^\star$. Note that $d(v,\hat{v}_0)=\infty$. It follows that $\lambda(\{\hat{v}_1,v\})\ge n^5$.
+We have $d(w^\star,\hat{v}_0)=n^6$.
+It follows that $\lambda(\{w,\hat{v}_0\})=n^6$.
+Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^6$.
+    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
+Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^6+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^6+2$.
+Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
+Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^6$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^6+2$.
+
+%    
+Let $v\in V^\star$.
+Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
+It follows that $\lambda(\{\hat{v}_1,v\})\ge n^6$ and $\lambda(\{\hat{v}_2,v\})\ge n^6$.
+Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
+Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
+It follows that $\lambda(\{\hat{v}_1,v\})\le n^6+2$ and $\lambda(\{\hat{v}_2,v\})\le n^6+2$.
+Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
+%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^6$.
+%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^6+2$ or $\lambda(\{\hat{v}_2,v\})=n^6+2$.
 \end{claimproof}
+
+\begin{claim}\label{claim:3}
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})\le n^6+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+\end{claim}
+\begin{claimproof}
+    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0$, $\hat{v}_1$, and $\hat{v}_2$ and sets $A,B$.
+Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
+Furthermore, we have that $u_\ell^{2n}\notin B$ and hence $d(\hat{v}_0,u_\ell^{2n})=3$.
+By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^6$ we have that both edges incident with $\hat{v}_0$ have label $n^6$.
+It follows that a fastest temporal path from $\hat{v}_0$ to $u_\ell^{2n}$ arrives at $u_\ell^{2n}$ at time $n^6+2$.
+Now assume for contradiction that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})> n^6+2$.
+Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u_\ell^{2n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
+\end{claimproof}
+
+\begin{claim}\label{claim:4}
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell -2n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+\end{claim}
+\begin{claimproof}
+    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
+Note that $x_1$ is connected to the alignment gadget.
+Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
+Since $d(w^\star,x_1)=6(i+j)$ we have that $\lambda(\{w,x_1\})=6(i+j)$.
+
+    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<6(i+j)$.
+Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
+However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
+    Next, assume that $6(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^6+2$.
+Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^6-6(i+j)+3$.
+However, we have that $d(w,v_{i,j}^\star)=n^6-6(i+j)+3$, a contradiction.
+    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^6+2$.
+Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
+This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
+It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^6$.
+However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^6+2$.
+It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
+
+    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=6(i+j)$.
+Now let $1<\ell\le m$.
+We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell -2n+6)$.
+Assume that $(i+j)\cdot (2n\ell -2n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^6+2$.
+Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
+Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
+By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^6$ and at most $n^6+2$.
+Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^6$ and at most $n^6+2$.
+It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell-1)+1$.
+Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
+In both cases we have a contradiction.
+    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^6+2$.
+Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
+Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^6$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^6+2$, a contradiction.
+\end{claimproof}
+
+\begin{claim}\label{claim:5}
+    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) -2n+6)+4n+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+\end{claim}
+\begin{claimproof}
+    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=4n+3$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^6$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
+In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
+
+    Now consider $v_{i,j}^{\star\star}$.
+By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^6+2$.
+It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
+
+    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^6$ except the ones to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
+By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^4$.
+    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u_{\ell'}^{2n}$ for some $\ell'\in[m]$ as its second last vertex.
+Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 4n+3$ (for sufficiently large $n$), a contradiction.
+
+    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u_{\ell'}^{2n}$ for some $\ell'\in[m]$ as its second last vertex.
+Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
+Hence, we have that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=4n+3$.
+    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell -2n+6)$.
+It follows that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell -2n+6)+4n+2$.
+We set $\sigma_{i,j}(\ell')=\ell$.
+
+    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
+Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
+Then we have that $\lambda(\{u_{\ell}^{2n},v_{i,j}^{\star\star}\})=\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})$.
+However, by \cref{claim:4} we have that all edges from $v_{i,j}$ to a vertex in $X_{i,j}$ have distinct labels.
+Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ as its second last vertex.
+Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=4n+3$, we must have that all edges from vertices in $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
+Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
+\end{claimproof}
+
+For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}.
+We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}.
+Consider the following set $X$ of edges from $H$.
+\[
+X=\{e_\ell^{i,j}\in F_{i,j}\mid \sigma_{i,j}(\ell)=1\}
+\]
+We claim that $X$ forms a multicolored clique in $H$.
+From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
+We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
+
+Before we proceed, we show another property of $\lambda$.
+
+\begin{claim}\label{claim:6}
+    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[2n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) -2n+6)+2\ell'$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
+\end{claim}
+\begin{claimproof}
+    To do.
+\end{claimproof}
+
+Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$. 
+Consider the verification gadget for color $i$. We first consider the case that $1\neq i\neq k$.
+
 \end{proof}
@@
 \begin{figure}[ht]
-	\begin{subfigure}{0.48\textwidth}
+    \centering
+	\begin{subfigure}[b]{0.48\textwidth}
 		\centering
@@
 	\end{subfigure}
-	\qquad
-	\begin{subfigure}{0.48\textwidth}
+	\quad
+	\begin{subfigure}[b]{0.48\textwidth}
 		\centering
@@
 	\end{subfigure}
+
+	\begin{subfigure}[b]{0.48\textwidth}
+			\centering
+			\resizebox{1.2\linewidth}{!}{
 				%
-	\begin{subfigure}{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-		\begin{tikzpicture}
+				\begin{tikzpicture}[scale=1]
 					%%%S_uv
@@
 					(vi) -- (v2) edge[diredge2] (v1) 
-			(v1) edge[wave] (3,1.3) 
-			(3,1.3) edge[wave] (8,1.3)
-			(8,1.3) edge[dirwave] (zr) 
+					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
 					(zr) --(zr1) -- (zj+1)
@@
 		\end{subfigure}
-	\qquad
-	\begin{subfigure}{0.48\textwidth}
+	\quad
+	\begin{subfigure}[b]{0.48\textwidth}
 		\centering

### 2023-02-01 Older Versions/OLD-OLD-RealizingTemporalGraphs.tex
Changes 31st Jan

--- 2023-02-01 ICALP23-RealizingTemporalGraphs.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
-
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+\documentclass[11pt,a4paper]{article}
+
+\usepackage[english]{babel}
+
+\usepackage{fullpage}
 
 \usepackage{amsmath}
-%\let\proof\relax
-%\let\endproof\relax
+\let\proof\relax
+\let\endproof\relax
 
@@
 
+\newtheorem{theorem}{Theorem}
+\newtheorem{observation}{Observation}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{claim}[theorem]{Claim}
+\newtheorem{conjecture}[theorem]{Conjecture}
+\theoremstyle{remark}
+\newtheorem{remark}[theorem]{Remark}
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[definition]{Example}
 \usepackage{comment}
@@
 
+\usepackage[capitalise,nameinlink, noabbrev]{cleveref}
 \crefname{claim}{Claim}{Claims}
+\crefname{observation}{Observation}{Observations}
+
+\usepackage{authblk}
 
@@
 \newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
+\newcommand{\st}{s.\,t.,\ }
 \newcommand{\NP}{\textrm{NP}}
@@
 
-\bibliographystyle{plainurl}% the mandatory bibstyle
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\title{Realizing Temporal Graphs}
+\author{Nina Klobas, George B. Mertzios, Hendrik Molter, Paul G. Spirakis}
+
+\bibliographystyle{abbrv}
 \begin{document}
 	\maketitle
-
-\begin{abstract}
-In this paper we study \emph{temporal design} problems of undirected temporally connected graphs. 
-The basic setting of these optimization problems is as follows: given an undirected graph~$G$, 
-what is the smallest number $|\lambda|$ of time-labels that we need to add to the edges of $G$ such that the resulting temporal graph $(G,\lambda)$ is temporally connected?
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-Graph realization problems are fundamental graph-algorithmic questions where the objective is to (re)construct a graph, 
-given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
-are the vertex degrees~\cite{}, distances~\cite{}, eccentricities~\cite{}, connectivity~\cite{}, etc. 
-The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{.....}.
 
@@
 \end{itemize}
-The next cases are only relevant if $1\neq i \neq k$. 
+
+The following cases are only relevant if $1\neq i \neq k$. 
 For all $0\le j<i$ and $\ell\in[n+3]$ we set the following.
@@
 \begin{figure}%[t]
-\noindent\makebox[\textwidth]{
+\noindent
+\makebox[\textwidth]{
 \centering
@@
 \scriptsize
-\node (A) at (12,0) {};
-
 \draw[rounded corners, dashed, gray] (-13, 5) rectangle (8, 1.5) {};
@@
 Let us denote with $Z$ the set of vertices removed from $G$ at the beginning of the algorithm, \ie $Z = V(G) \setminus V(G')$.
-By the construction it follows that $Z$ consists of disjoint trees. 
+By the construction it follows that $Z$ consists of disjoint trees. %%TBDNKL
 Note that the fastest temporal paths among vertices of $G'$ are independent of vertices in $Z$.

### 2023-02-01 ICALP23-RealizingTemporalGraphs.tex
Small changes 1st Feb

@@
 This finishes the construction of $G$.
+For an example see~\cref{fig:NP-example}.
 
@@
 Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
-where all unlabeled edges get the label $2$.}
+where all unlabeled edges get the label $2$.
+\label{fig:NP-example}}
 \end{figure}
@@
 %
-\begin{figure}[ht]
+\begin{figure}[h]
     \centering

### 2023-02-02 ICALP23-RealizingTemporalGraphs.tex
Changing NP-hardness for Delta (not infinity). To see old infinity versions check previous files (1 or 2 iterations back)

@@
 
+SKELETON:
+\begin{itemize}
+    \item graph realization problems in general, well studied and motivated for different types of graph attributes (among the most natural ones are distances and degree sequences), mention the two perspectives: verification and network design.
+    \item Some observations and references about distance realization known results on static graphs.
+    \item In modern network applications, network structure changes over time
+    \item In this paper we focus on distance attributes (one of the most fundamental graph attributes)
+    \item What is distances in temporal graphs? Fastest, etc, periodic
+    \item Our contributions
+    \item Related work on temporal network design etc
+\end{itemize}
+
 \section{Preliminaries}
@@
 
-	\begin{figure}[h]
+	\begin{figure}[htb]
     \centering
@@
 \begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact of dimension $n \times n$.
+    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
     Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
@@
 
-\section{Hardness of Exact Realization}
-
-\todo[inline]{HM: For the following hardness I assume that we only consider strict temporal paths. (NK: Yes you are right, all paths are strict, sorry forgot to specify). \\
-Furthermore, I can currently only make it work if we do not have periods ($\Delta=\infty$). I am not sure the idea also works if we have periods.}
+\section{\deltaExact\ is NP-hard}
 
 \begin{theorem}
-	\textsc{Exact Realization $(\infty)$} is \NP-hard.
+	\deltaExactLong\ is \NP-hard.
 \end{theorem}
@@
 Here, we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
-We construct an instance of \textsc{Exact Realization $(\infty)$} as follows.
-
- We start by describing the vertex set of the underlying graph $G$.
+We construct an instance $D^\phi$ of \deltaExact\ as follows.
+
+ We start by describing the vertex set of the underlying graph $G$ of  $D^\phi$.
 \begin{itemize}
@@
 \item For each variable $x$ in $\phi$ we add the following five edges: 
-
-$\{x, x^T\}, \{x, x^F\}, \{x^T, x^F\}, \{x^T, v\}, \{x^F,v\}$.
-\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges
-
-$\{x^T,y^T\},\{x^T,y^F\}, \{x^F,y^T\},\{x^F,y^F\}$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal.
-Let $x$ appear in $c$.
-If $X$ appears non-negated in $c$ we add edge $\{c,x^T\}$.
-If $x$ appears negated in $c$ we add edge $\{c, x^F\}$.
+$x x^T, x x^F, x^T x^F, x^T v$ and $ x^Fv$.
+\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges: 
+$x^T y^T, x^Ty^F, x^Fy^T$ and $x^Fy^F$.
+\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x$ appear in $c$. If $x$ appears non-negated in $c$ we add edge $c x^T$. 
+If $x$ appears negated in $c$ we add edge $c x^F$.
 \end{itemize}
@@
 
-Now we specify the distances between all vertex pairs. Naturally, the distance between all pairs of adjacent vertices is one.
+Now we specify the distances in the matrix $D^\phi$ between all vertex pairs.
+For the sake of simplicity we write $D^\phi _{x,y}$ as $d(x,y)$,
+where $x,y$ are two vertices. 
+We start by setting the value of $d(x,y) = 1$ where $x$ and $y$ are two adjacent vertices in $G$.
 \begin{itemize}
     %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-
     %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following distances:
-
+    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
     %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x$ in $\phi$ we specify the following distances to the super vertex $v$:
-
+    \item For each variable $x$ in $\phi$ we specify the following distance to the super vertex $v$:
     $d(x,v)=2$. %, $d(x_2,v)=3$.
 
-    \item For each clause $c$ in $\phi$ we specify the following distances to the super vertex $v$:
-
+    \item For each clause $c$ in $\phi$ we specify the following distance to the super vertex $v$:
     $d(c,v)=2$
-    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distances:
-
+    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distance:
     $d(c,x)=2$.
-
-    If $x$ appears non-negated in $c$ we specify the following distances:
-
+    If $x$ appears non-negated in $c$ we specify the following distance:
     $d(c,x^F)=2$.
-
-    If $x$ appears negated in $c$ we specify the following distances:
-
+    If $x$ appears negated in $c$ we specify the following distance:
     $d(c,x^T)=2$.
-    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
-
+    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distance:
     $d(c,x^T)=d(c,x^F)=2$.
@@
 
-This finishes the construction of the \textsc{Exact Realization $(\infty)$} which can clearly be done in polynomial time.
-In the remainder we show that it is a yes-instance if and only if $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed \textsc{Exact Realization $(\infty)$} is a yes-instance.
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path between from $u$ to $w$ has exactly duration $d(u,w)$.
-In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$, then we set $x$ to \texttt{true}, otherwise we set $x$ to \texttt{false}.
+This finishes the construction of an instance $D^\phi$ of \deltaExact\, which can clearly be done in polynomial time.
+In the remainder we show that $D^\phi$ is a yes-instance if and only if $\phi$ is satisfiable.
+
+$(\Rightarrow)$: Assume the constructed instance $D^\phi$ of \deltaExact\ is a yes-instance. 
+Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
+%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
+
+We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(x x^T)=\lambda(x^T v)$, then we set $x$ to \textsc{True}, otherwise we set $x$ to \textsc{False}.
 
@@
 
-Let $\lambda(\{x,x^T\})=t$ and $\lambda(\{x,x^F\})=t'$, for an arbitrary variable $x$. 
-If both $\lambda(\{x^T,v\})\neq t+1$ and $\lambda(\{x^F,v\})\neq t'+1$, then $d(x,v)>2$, which is a contradiction. 
-Thus, for every variable $x$, we have that $\lambda(\{x^T,v\})= t+1$ or $\lambda(\{x^F,v\})= t'+1$ (or both). 
-In particular, this means that if $\lambda(\{x,x^F\})=\lambda(\{x^F,v\})$, then we set $x$ to \texttt{false}, since in this case $\lambda(\{x,x^T\})\neq\lambda(\{x^T,v\})$.
+Let $\lambda(x x^T)=t$ and $\lambda(x x^F)=t'$, for an arbitrary variable $x$. 
+If both $\lambda(x^T v)\neq t+1$ and $\lambda(x^F v)\neq t'+1$, then $d(x,v)>2$, which is a contradiction. 
+Thus, for every variable $x$, we have that $\lambda(x^T v)= t+1$ or $\lambda(x^F v)= t'+1$ (or both). 
+In particular, this means that if $\lambda(x x^F)=\lambda(x^F v)$, then we set $x$ to \textsc{False}, since in this case $\lambda(x x^T)\neq\lambda(x^T v)$.
 
@@
 Assume w.l.o.g\ that $x$ appears in $c$ non-negated (the case of a negated appearance of $x$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x^T$. 
-Then we have that $\lambda(\{c,x^T\})=\lambda(\{x^T,v\})-1$.
-Furthermore, since $d(c,x)=2$ we also have that $\lambda(\{c,x^T\})=\lambda(\{x,x^T\})-1$.
-It follows that $\lambda(\{x,x^T\})=\lambda(\{x^T,v\})$.
-However, this implies that $x$ is set to \texttt{true} in the satisfying assignment and thus the clause $c$ is satisfied, a contradiction.
+Then we have that $\lambda(c x^T)=\lambda(x^T v)-1$.
+Furthermore, since $d(c,x)=2$ we also have that $\lambda(c x^T)=\lambda(x x^T)-1$.
+It follows that $\lambda(x x^T)=\lambda(x^T v)$.
+However, this implies that $x$ is set to \textsc{True} in the satisfying assignment and thus the clause $c$ is satisfied, a contradiction.
 
@@
     %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x$ is set to \texttt{true}, we set $\lambda(\{x^F,v\})=3$.
-    \item If variable $x$ is set to \texttt{false}, we set $\lambda(\{x^T,v\})=3$.
+    \item If variable $x$ is set to \textsc{True}, we set $\lambda(x^F v)=3$.
+    \item If variable $x$ is set to \textsc{False}, we set $\lambda(x^T v)=3$.
     \item We set the labels of all other edges to two.
@@
 
-    If $x$ is set to \texttt{true}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(\{x,x^F\})=2$ and $\lambda(\{x^F,v\})=3$.
-If $x$ is set to \texttt{false}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(\{x,x^T\})=2$ and $\lambda(\{x^T,v\})=3$.
+    If $x$ is set to \textsc{True}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(x x^F)=2$ and $\lambda(x^F v)=3$.
+If $x$ is set to \textsc{False}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(x x^T)=2$ and $\lambda(x^T v)=3$.
 
@@
     Since we have a satisfying assignment there is a variable $x$ appearing in $c$ that is set to a truth-value that satisfies $c$.
-If $x$ appears non-negated in $c$ (and hence is set to \texttt{true}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x^T,v\})=2$.
-If $x$ appears negated in $c$ (and hence is set to \texttt{false}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x^F,v\})=2$.
+If $x$ appears non-negated in $c$ (and hence is set to \textsc{True}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(c x^T)=1$ and $\lambda(x^T v)=2$.
+If $x$ appears negated in $c$ (and hence is set to \textsc{False}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x^F v)=2$.
     \item Let $x$ be a variable that appears in clause $c$.
@@
 
-    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(\{c,x^T\})=1$ and $\lambda(\{x,x^T\})=\lambda(\{x^T,x^F\})=2$.
+    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(c x^T)=1$ and $\lambda(x x^T)=\lambda(x^T x^F)=2$.
 
@@
 
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(\{c,x^F\})=1$ and $\lambda(\{x,x^F\})=\lambda(\{x^T,x^F\})=2$.
+    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$.
     \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we have $d(c,x^T)=d(c,x^F)=2$:
@@
     Let $y$ be a variable that appears non-negated in $c$ (the case where $y$ appears negated is symmetrical).
-Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(\{c,y^T\})=1$ and $\lambda(\{y^T,x^T\})=\lambda(\{y^T,x^F\})=2$.
+Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(c y^T)=1$ and $\lambda(y^T x^T)=\lambda(y^T x^F)=2$.
 \end{itemize}
@@
 %
-\begin{figure}[h]
+\begin{figure}[htb]
 	\noindent
@@
 Afterwards, we describe the remaining entries of $D$.
-
-    We will construct $G$ using several gadgets. We first introduce an \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We start with describing the vertex set of the gadget.
+    We will construct $G$ using several gadgets.
+
+    \subparagraph{Edge Selection Gadget.} We first introduce an \emph{edge selection gadget for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
     \begin{itemize}
@@
     \end{itemize}
-    This finishes the construction of the edge selection gadget $G_{i,j}$.
-
-    For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget} for color $i$.
-    \begin{itemize}
-        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i_0$.
+    %This finishes the construction of the edge selection gadget.
+
+    \subparagraph{Verification Gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
+    \begin{itemize}
+        \item We have one vertex $y^i$, one vertex $v^i_0$, and $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$.
+        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{n}$ and $n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{n}$.
         \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n+3$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{n+3}$.
     \end{itemize}
-    We add the following edges. 
+    We add the following edges. We add edge $\{y^i,v^i_0\}$.
+    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
+    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
     %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
@@
     Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'-1}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
+Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
+    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
 
@@
     Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},u^\ell_{n+\ell'-1}\}$ between $\hat{u}^i_{n+3}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,u^\ell_{n+\ell'-1}\}$ between $v^i_0$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'-1}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    Next, we describe \emph{connector gadgets}.
+If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
+If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
+Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
+
+    Let $i+1<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
+Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{n},u^\ell_{n+\ell'-1}\}$ between $a^{i,j,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
+    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{n},u^\ell_{n+\ell'}\}$ between $b^{i,j,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
+
+    \subparagraph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
 Intuitively, these gadgets will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
@@
 
-    The first connector gadget for the edge selection gadget of color combination $i,j$ with $i<j$ has the following sets.
+    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
     \begin{itemize}
@@
     \end{itemize}
-    The second connector gadget for the edge selection gadget of color combination $i,j$ with $i<j$ has the following sets.
+    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
     \begin{itemize}
@@
     \end{itemize}
-
-    The connector gadget for the verification gadget of color $i$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-    \end{itemize}
-
-Lastly, we introduce an \emph{alignment gadget}.
+    The \emph{connector gadget for the verification gadget of color $i$} has the following sets.
+    \begin{itemize}
+        \item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
+        \item Set $B$ contains all vertices vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists).
+    \end{itemize}
+
+\subparagraph{Alignment Gadget.} Lastly, we introduce an \emph{alignment gadget}.
 It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget and one vertex for each connector gadget.
 Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget is connected to exactly one vertex in $\hat{W}$ and the vertex $\hat{v}_1$ of each connector gadget is connected to exactly one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-
-This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
+The vertex $x_1$ of each edge selection gadget is connected to exactly one vertex in $\hat{W}$, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget is connected to exactly one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
+
+\subparagraph{Feedback Vertex Number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
 \begin{itemize}
     \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists) of each validation gadget.
+    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists) of each verification gadget.
     \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
@@
 
-We proceed with describing the distance matrix $D$. We use the notation $d(v,v'):= D_{v,v'}$. For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
+\subparagraph{Distance Matrix.} We proceed with describing the distance matrix $D$.
+For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
+For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
 
@@
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)-1$.
+    \item We set $d(v^i_j,v^i_{j'})=(2n+2)(j'-j)-1$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(v^i_j,\hat{u}^i_{\ell})=6(i-j-1)+2\ell-1$.
+    \item We set $d(v^i_j,\hat{u}^i_{\ell})=(2n+2)(i-j-1)+2\ell-1$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)+2n-1$.
+    \item We set $d(v^i_j,v^i_{j'})=(2n+2)(j'-j)+2n-1$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(\hat{u}^i_{\ell},v^i_j)=6(j-i)+2(n-\ell)+5$.
+    \item We set $d(\hat{u}^i_{\ell},v^i_j)=(2n+2)(j-i)+2(n-\ell)+5$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(w^\star,x_1)=6(i+j)$.
-    \item We set $d(w,\hat{v}_1)=n^6-6(i+j)+1$ and $d(w,\hat{v}_2)=n^6-6(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w,v)=n^6-6(i+j)+3$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^6$.
+    \item We set $d(w^\star,x_1)=(2n+2)(i+j)$.
+    \item We set $d(w^\star,\hat{v}_1)=n^7$, $d(w,\hat{v}_2)=n^7$, $d(w,\hat{v}_1)=n^7-(2n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^7-(2n+2)(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^7+2$ and $d(w,v)=n^7-(2n+2)(i+j)+3$.
+\end{itemize}
+
+Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
+Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
+Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
+Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
+\begin{itemize}
+    \item We set $d(w^\star,y^i)=n^6-1$ and $d(w',v^i_0)=2$.
+    \item We set $d(w^\star,\hat{v}_1)=n^7$, $d(w^\star,\hat{v}_2)=n^7$, $d(w',\hat{v}_1)=n^7-n^6$, and $d(w',\hat{v}_2)=n^7-n^6$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^7+1$, $d(w,v)=n^7-n^6+2$, and $d(y^i,v)=n^7-n^6+2$.
+\end{itemize}
+Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^7$.
 
@@
 
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -27) {};
-\node (A) at (-4,-26) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -27) {};
-\node[rotate=-90] (A) at (7,-18) {verification gadget for $i$};
+\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
+\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
+
+\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
+\node[rotate=-90] (A) at (7,-16) {verification gadget for $j$};
 
@@
     \node[vert] (W4) at (7,2) {}; 
+    \node[vert] (W5) at (3.5,2) {};
 
@@
 
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24.5) {};
-
-    \node[vert,label=right:$v_0^i$, fill=gray] (VI0) at (5,0) {};
-    \node[vert,label=right:$v_1^i$, fill=gray] (VI1) at (5,-3) {};
-    \node (A) at (5,-5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^i$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{j}^i$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-13) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^i$, fill=gray] (VII1) at (5,-15) {};
-    \node[vert,label=right:$\hat{u}_{1}^i$] (UI1) at (5,-17) {};
-    \node[vert,label=right:$\hat{u}_{2}^i$] (UI2) at (5,-19) {};
-    \node (A) at (5,-20.5) {$\vdots$};
-    \node[vert,label=right:$\hat{u}_{n+3}^i$, fill=gray] (UIN3) at (5,-22) {};
-    \node (A) at (5,-24) {$\vdots$};
-    \node[vert,label=right:$v_{k}^i$, fill=gray] (VIK) at (5,-26) {};
+    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
+
+    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
+    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
+    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
+    \node (A) at (5,-5.5) {$\vdots$};
+    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
+    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
+    \node (A) at (5,-12.5) {$\vdots$};
+    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
+    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
+    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
+    \node (A) at (5,-19.5) {$\vdots$};
+    \node[vert,label=right:$\hat{u}_{n+3}^j$, fill=gray] (UIN3) at (5,-21) {};
+    \node (A) at (5,-22.5) {$\vdots$};
+    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
 
@@
 
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^6$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^6+1$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^6+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^6$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^6+1$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^6$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^6+1$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^6+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^6$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^6+1$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^6$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^6+1$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^6+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^6$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^6+1$} (VH344);
-
-	\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
+    \draw[edge] (VH11) --node[timelabel,sloped] {$n^7$} (VH12);
+	\draw[edge] (VH12) --node[timelabel,sloped] {$n^7+1$} (VH111);
+	\draw[edge] (VH12) --node[timelabel] {$n^7+1$} (VH13);
+    \draw[edge] (VH13) --node[timelabel,sloped] {$n^7$} (VH14);
+	\draw[edge] (VH13) --node[timelabel,sloped] {$n^7+1$} (VH144);
+
+    \draw[edge] (VH21) --node[timelabel,sloped] {$n^7$} (VH22);
+	\draw[edge] (VH22) --node[timelabel,sloped] {$n^7+1$} (VH211);
+	\draw[edge] (VH22) --node[timelabel] {$n^7+1$} (VH23);
+    \draw[edge] (VH23) --node[timelabel,sloped] {$n^7$} (VH24);
+	\draw[edge] (VH23) --node[timelabel,sloped] {$n^7+1$} (VH244);
+
+    \draw[edge] (VH31) --node[timelabel,sloped] {$n^7$} (VH32);
+	\draw[edge] (VH32) --node[timelabel,sloped] {$n^7+1$} (VH311);
+	\draw[edge] (VH32) --node[timelabel] {$n^7+1$} (VH33);
+    \draw[edge] (VH33) --node[timelabel,sloped] {$n^7$} (VH34);	
+    \draw[edge] (VH33) --node[timelabel,sloped] {$n^7+1$} (VH344);
+
+	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
+	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
+
+    \draw[edge,double] (VIJ1) --node {} (U13);
+	\draw[edge,double] (VIJ) --node {} (U23);
 
@@
 	\draw[edge] (W) --node[timelabel] {$1$} (W4);
+	\draw[edge] (W) --node[timelabel] {$1$} (W5);
 
 	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^6$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^6$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^6$} (W4);
+	\draw[edge] (VH11) --node[timelabel] {$n^7$} (W2);
+	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^7$} (W3);
+	\draw[edge] (VH31) --node[timelabel] {$n^7$} (W4);
+	\draw[edge] (YI) --node[timelabel] {$n^6-1$} (W5);
+
+	\draw[edge] (YI) --node[timelabel] {$n^6$} (VI0);
 
@@
 
-This finishes the construction of the \deltaExactLong\ instance, which can clearly be computed in polynomial time.
+\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance, which can clearly be computed in polynomial time.
 For an illustration see \cref{fig:hardness1}.
@@
 
-\emph{Correctness.} In the remainder we prove that $D$ is a yes-instance of \deltaExactLong\ if and only if the $H$ is a yes-instance of \textsc{Multicolored Clique}.
-
-$(\Rightarrow)$: Assume $D$ is a yes-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
+In the remainder we prove that $D$ is a yes-instance of \deltaExactLong\ if and only if the $H$ is a yes-instance of \textsc{Multicolored Clique}.
+
+\subparagraph{$(\Rightarrow)$:} Assume $D$ is a yes-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
 We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$.
+We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
 
@@
 Next, we analyse the labelings of connector gadgets.
+We show that all edges incident with vertices of connector gadgets have labels of at least $n^7$ and at most $n^7+2$.
+More precisely, we show the following.
 \begin{claim}\label{claim:2}
@@
         %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^6$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^6+2$,
+        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^7$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^7+2$,
         %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^6+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^6$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^6+2$. 
-        %\item For all $v\in V^\star$ we have $n^6\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^6+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^6$ and $\lambda(\{\hat{v}_2,v\})=n^6+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^6$ and $\lambda(\{\hat{v}_2,v\})=n^6$.
+        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^7+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^7$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^7+2$. 
+        %\item For all $v\in V^\star$ we have $n^7\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^7+2$.
+        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^7$ and $\lambda(\{\hat{v}_2,v\})=n^7+2$.
+        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^7$ and $\lambda(\{\hat{v}_2,v\})=n^7$.
         %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^6\le \lambda(\{\hat{v}_1,v\})\le n^6+2$ and $n^6\le \lambda(\{\hat{v}_2,v\}) \le n^6+2$.
+        Furthermore, for all $v\in V^\star$ we have $n^7\le \lambda(\{\hat{v}_1,v\})\le n^7+2$ and $n^7\le \lambda(\{\hat{v}_2,v\}) \le n^7+2$.
     %\end{itemize}
@@
     Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^6$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^6$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^6$.
+We have $d(w^\star,\hat{v}_0)=n^7$.
+It follows that $\lambda(\{w,\hat{v}_0\})=n^7$.
+Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^7$.
     Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^6+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^6+2$.
+Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^7+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^7+2$.
 Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^6$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^6+2$.
+Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^7$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^7+2$.
 
@@
 Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^6$ and $\lambda(\{\hat{v}_2,v\})\ge n^6$.
+It follows that $\lambda(\{\hat{v}_1,v\})\ge n^7$ and $\lambda(\{\hat{v}_2,v\})\ge n^7$.
 Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
 Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^6+2$ and $\lambda(\{\hat{v}_2,v\})\le n^6+2$.
+It follows that $\lambda(\{\hat{v}_1,v\})\le n^7+2$ and $\lambda(\{\hat{v}_2,v\})\le n^7+2$.
 Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^6$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^6+2$ or $\lambda(\{\hat{v}_2,v\})=n^6+2$.
+%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^7$.
+%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^7+2$ or $\lambda(\{\hat{v}_2,v\})=n^7+2$.
 \end{claimproof}
 
+Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
+
 \begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})\le n^6+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})\le n^7+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
 Furthermore, we have that $u_\ell^{2n}\notin B$ and hence $d(\hat{v}_0,u_\ell^{2n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^6$ we have that both edges incident with $\hat{v}_0$ have label $n^6$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u_\ell^{2n}$ arrives at $u_\ell^{2n}$ at time $n^6+2$.
-Now assume for contradiction that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})> n^6+2$.
+By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^7$ we have that both edges incident with $\hat{v}_0$ have label $n^7$.
+It follows that a fastest temporal path from $\hat{v}_0$ to $u_\ell^{2n}$ arrives at $u_\ell^{2n}$ at time $n^7+2$.
+Now assume for contradiction that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})> n^7+2$.
 Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u_\ell^{2n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
@@
 \begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell -2n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell +2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
 Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=6(i+j)$ we have that $\lambda(\{w,x_1\})=6(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<6(i+j)$.
+Since $d(w^\star,x_1)=(2n+2)(i+j)$ we have that $\lambda(\{w,x_1\})=(2n+2)(i+j)$.
+
+    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(2n+2)(i+j)$.
 Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
 However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $6(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^6+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^6-6(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^6-6(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^6+2$.
+    Next, assume that $(2n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^7+2$.
+Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^7-(2n+2)(i+j)+3$.
+However, we have that $d(w,v_{i,j}^\star)=n^7-(2n+2)(i+j)+3$, a contradiction.
+    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^7+2$.
 Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
 This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^6$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^6+2$.
+It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^7$.
+However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^7+2$.
 It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
 
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=6(i+j)$.
+    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(2n+2)(i+j)$.
 Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell -2n+6)$.
-Assume that $(i+j)\cdot (2n\ell -2n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^6+2$.
+We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell +2)$.
+Assume that $(i+j)\cdot (2n\ell 2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^7+2$.
 Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
 Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^6$ and at most $n^6+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^6$ and at most $n^6+2$.
+By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^7$ and at most $n^7+2$.
+Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^7$ and at most $n^7+2$.
 It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell-1)+1$.
@@
 In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^6+2$.
+    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^7+2$.
 Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^6$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^6+2$, a contradiction.
+Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^7$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^7+2$, a contradiction.
 \end{claimproof}
@@
 \begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) -2n+6)+4n+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +2)+4n+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
     For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=4n+3$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^6$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
+From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^7$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
 In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
@@
     Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^6+2$.
+By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^7+2$.
 It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
 
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^6$ except the ones to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
+    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^7$ except the ones to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
 By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^4$.
@@
 Hence, we have that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=4n+3$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell -2n+6)$.
-It follows that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell -2n+6)+4n+2$.
+    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell +2)$.
+It follows that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell +2)+4n+2$.
 We set $\sigma_{i,j}(\ell')=\ell$.
@@
 
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}.
-We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}.
-Consider the following set $X$ of edges from $H$.
+For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
+Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
+To this end, consider the following set $X$ of edges from $H$.
 \[
@@
 \]
-We claim that $X$ forms a multicolored clique in $H$.
+We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
 From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
 We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-
-Before we proceed, we show another property of $\lambda$.
+This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
+
+Before we proceed, we show some further properties of $\lambda$. First, we have a closer look at the labels on edges of the edge selection gadgets.
 
 \begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[2n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) -2n+6)+2\ell'$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
+    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[2n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +2)+2\ell'$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
 \end{claim}
@@
 
+Now, we investigate the labels of the verification gadgets.
+
+\begin{claim}\label{claim:7}
+    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^6$.
+\end{claim}
+\begin{claimproof}
+    Let $w\in \hat{E}$ denote the neighbor of $y^i$ in the alignment gadget.
+Note that we have $d(w^\star,y^i)=n^6-1$.
+It follows that $\lambda(\{w,y^i\})=n^6-1$.
+Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
+It follows that $\lambda(\{y^i,v_0^i\})=n^6$.
+\end{claimproof}
+
+\begin{claim}\label{claim:8}
+    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
+    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
+    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1})\le n^6$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^7+2$.
+    For all $i=1$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,2,\ell}_{1})\le n^6$ or $\lambda(\{v_0^i,a^{i,2,\ell}_{1}\})\ge n^7+2$.
+\end{claim}
+\begin{claimproof}
+    Let $1<i\le k$ and $\ell\in[m]$.
+Assume that $n^6<\lambda(\{v_0^i,a^{i,1,\ell}_{1})< n^7+2$.
+The there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^7+2$.
+However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^7+2$, a contradiction.
+The argument for case where $i=1$ is analogous.
+\end{claimproof}
+
+\begin{claim}\label{claim:9}
+    Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
+Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^7+2$.
+\end{claim}
+\begin{claimproof}
+    To do.
+\end{claimproof}
+
+Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
 Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
@@
 
+\subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution. To do.
 \end{proof}
@@
 
-Note that we can easily solve the \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
+Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
 But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
@@
 From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$.
+iteratively removing vertices of degree one from $G$,
+and denote with 
+$$
+Z = V(G) \setminus V(G').
+$$
 Then we determine a minimum feedback edge set $F$ of $G'$ by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
@@
 $$U^* = \{v \in V(G') \setminus U | u \in U, v \in N(u)\}.$$
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $U^* \in O(k^2)$.
-Determining all of the above sets takes us linear time.
-
-Let us denote with $Z$ the set of vertices removed from $G$ at the beginning of the algorithm, \ie $Z = V(G) \setminus V(G')$.
-By the construction it follows that $Z$ consists of disjoint trees. 
-Note that the fastest temporal paths among vertices of $G'$ are independent of vertices in $Z$.
+Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
+From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
+it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
+For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
+and call it a \emph{clip vertex of the tree $T_i$}.
+It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
+but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
+Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
+from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
+that are clipped at the same vertex $u_i \in V(G')$.
+For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
+and call it \emph{a representative vertex of the tree $T_{u_i}$}.
+We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
+where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
+$$
+Z^* = \{ r_i | r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
+$$
+Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
+Note that determining sets $U, U^*$ and $Z^*$ takes linear time.
+
 Let us remember the following basic property of the problem \deltaExact.
@@
     Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
+    \item \label{FPT-guessFTPamongZstar}
+    The fastest temporal paths among all vertices in $Z^*$, 
+    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
     \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^6})$ guesses.
+    The fastest temporal paths among all vertices in $U^*$.
+    This gives us $O(k^{k^6})$ guesses.
     \item \label{FPT-guessFTPamongUandUstar}
@@
     and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
+    This gives us $O(k^{k^4})$ guesses.
+    \item \label{FPT-guessFTPamongUandZstar}
+    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
+    and vice versa.
+    This gives us $O(k^{k^3})$ guesses.
+    \item \label{FPT-guessFTPamongUstarandZstar}
+    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
+    and vice versa.
     This gives us $O(k^{k^4})$ guesses.
@@
     \item \label{FPT:guess-uToSegmentz2}
-    For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$
-    and a vertex of interest $w \in U$,
-    we guess the following fastest temporal paths
+    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
+    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
+    We want to
+    guess the following fastest temporal paths
     $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
@@
     \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
+    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
     %
@@
     \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U$ be a vertex of interest and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
+    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
+    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
     We again have two cases,
@@
 %
-\begin{figure}[h]
+\begin{figure}[htb]
     \centering
@@
 		\end{tikzpicture}}
-	\caption{Example of a guess G-4, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
 	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
@@
 			\end{tikzpicture}}
-		\caption{Example of a guess G-5, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red). 
+		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
 			\label{fig:FPT-guessG5}}
@@
 			\end{tikzpicture}}
-			\caption{Example of a guess G-6, where, for fixed a vertex $v_i \in S_{u,v}$,
+			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
 				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
@@
 		\end{tikzpicture}}
-	\caption{Example of a guess G-7, where, for a vertex of interest $w$, 
+	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
 		we
@@
 
-\subsection{Properties of 
-\texorpdfstring{\deltaExact } {Simple Delta-TGR}
-}
+\subsection{Properties of \deltaExact}
 
@@
 Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-For a tree $T_i$ denote with $u_i$ the vertex in $G'$ that is a neighbor of some vertex in $T_i$, 
-call it a \emph{clip vertex of the tree $T_i$}
-and denote with $r_i$ the neighbor of $u_i$, \ie the root of the tree $T_i$.
-By construction (by iteratively removing vertices of degree one from $G$) it follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-First observe that $|N_{G'}(u_i)|\geq 1$, if not also $u_i$ would be removed from $G$.
+Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
+and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
 To determine the correct label of all edges of $T_i$ we use the following property.
 \begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a root of $T_i$.
+Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
 Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
@@
 \end{proof}
-
-Because $(r_i,u_i,v)$ is the fastest temporal path from $r_i$ to $v$ we can determine the label of edge $r_iu_i$ as 
+Suppose now that we know that 
+$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
+Then
+we can determine the label of edge $r_i u_i$ as 
 $\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
+Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
 We repeat this procedure for all trees in $Z$.
-What remains is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
+What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
 Note that since 
 there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the root vertex $r_i$ of tree $T_i$, 
-which can be uniquely extended to all vertices in $T_i$.
+we present the study for cases when we find fastest temporal paths from and to the 
+representative vertex $r_i$ of tree $T_i$.
+Each of these paths are then uniquely extended to all vertices in $T_i$.
 
 \subsubsection*{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$}
-Let us start with the case when we want to determine the fastest temporal path from a root vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
+Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
 We distinguish the following two cases.
 \begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
+    \item \label{FPT:z-u-clipnotU}
+    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
     Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
@@
     \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    Note that since we have determined the label of the edge $w r_i$, we also know the waiting times 
-    at vertex $u$ coming from each of its neighbors $v_i$ and finishing in $r_i$. 
-    At the beginning we have also determined the fastest paths from $u$ to all $v_i \in N_{G'}(w)$.
-    Therefore we know the path $P$ that is the fastest from $u$ to $r_i$. 
-    Once we have determined $P$ we also know that the fastest path from $u$ to any other vertex in $T_i$ uses $P$ at the beginning, to go from $u$ to $r_i$.
-    Therefore we have determined the fastest paths from $u$ to all other vertices in $T_i$,
-    which gives rise to $|T_i|$ equality constraints.
-    We iterate now through all other $u \leadsto w \rightarrow r_i$ paths and introduce inequality constraints for them. \todo{FIX}
-    There are $O(k^k)$ such paths.
+    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
+    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
+    We create an equality constraint for this path,
+    and create inequality constraints for all other paths.
+    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
+    we create $O(k^k)$ inequality constraints. .
 \end{enumerate}
 
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a root vertex $r_i$ in $T_i$,
-we use similar arguing as above.
-The procedure produces one equality constraint and $O(k^k)$ inequality ones.
+In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
+again have to split the analysis in two cases.
+\begin{itemize}
+    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
+    In this case
+we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
+which is enough to determine the exact fastest path from $u$ to $r_i$ 
+(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
+\item The clip vertex of $T_i$ is a vertex of interest.
+    In this case
+we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
+\end{itemize}
+The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
 
 \subsubsection*{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$}
-The next two cases are the ones where we want to determine the fastest temporal path from root $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
+The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
 and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as above, to determine the fastest temporal path from $r_i$ to $y$, 
-where the difference is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$.
-Since $y \in S_{u,v}$ there are $O(k^{k^6})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k^6})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
+Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
+We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
+to determine the fastest temporal path from $r_i$ to $y$. 
+The difference in this case is that 
+we know the fastest temporal path from the clip vertex of $T_i$ to $y$
+(when the clip vertex is not a vertex of interest),
+or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
+(when the clip vertex is a vertex of interest).
+The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
+%
+Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
+and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
 In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
@@
 
+In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
+to a representative vertex $r_i$ in $T_i$, 
+we 
+again have to split the analysis in two cases. 
+\begin{itemize}
+    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
+In this case we
+know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
+which is enough to determine the exact fastest path from $x$ to $r_i$ 
+(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
+    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
+Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
+In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
+Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
+we use the same procedure as in the 
+case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
+to determine which is the fastest path from $y$ to $r_i$.
+\end{itemize}
+The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
+
 \subsubsection*{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$}
 The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be root vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their root vertices, respectively.
-If $w_i = w_j$, then there is a unique path among $r_i$ and $r_j$, which gives rise to the equality constraint.
-If $w_i \neq w_j$, we know the underlying paths of fastest paths 
-from $r_i$ to $w_j$, from $w_j$ to $r_i$,
-from $r_j$ to $w_i$, from $w_i$ to $r_j$,
-and from $w_i$ to $w_j$.
-Using similar approaches as above, we can uniquely determine the fastest paths from $r_i$ to $r_j$.
-We again have to consider multiple cases.
-One where $w_i,w_j \notin U$ and 
-split it into two subcases, when the edges of the tree $T_i$ are determined with respect to the
-label of the first edge of the segment of $w_i$, and similarly for $T_j$.
-And one where the edges of the tree are determined with respect to some not yet determined edge incident to $w_i$ (resp.~$w_j$).
-The second case is when $\{w_i, w_j\} \cap U \neq \emptyset$.
-In all of these cases we can uniquely determine the underlying paths of the fastest paths between $r_i$ and $r_j$,
-which give rise to equality constraints for them. 
-Then we have to find all non-fastest temporal paths among $r_i$ and $r_j$, for which we introduce the inequality constraints. 
-There are at most $O(k^{k^6})$ such paths.
+Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
+We distinguish following cases.
+\begin{itemize}
+    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
+    In this case $r_i, r_j \in Z^*$
+    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
+    \item One clip vertex is a vertex of interest and the other is not.
+    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
+    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
+    We know the fastest paths from the representative $r_i$ of tree $T_i$,
+    to vertices $w_{j-1},w_j,w_{j+1}$ 
+    (we determined them in the above case 
+    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
+
+    Now we use the same procedure as in
+    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
+    to determine the exact fastest path from $r_i$ to $r_j$.
+    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
+    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
+    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
+    and 
+    similarly with 
+    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
+    We know all the fastest paths from
+    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
+    and similarly all fastest paths 
+    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
+    together with all the fastest paths among 
+    each pair of the following vertices
+    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
+
+    Now we use the same procedure as in
+    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
+    to determine the exact fastest path from $r_i$ to $r_j$.
+\end{itemize}
+The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
 

### 2023-02-02 ICALP23-RealizingTemporalGraphs.tex
Finished NP-hardness construction

@@
 \begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem 3-SAT~\cite{Karp1972Reducibility}.
-Here, we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
+	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
+Here we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
+    A NAE clause evaluates to \textsc{True} iff not all of its literals are equal.
     We construct an instance $D^\phi$ of \deltaExact\ as follows.
@@
 \begin{itemize}
-\item For each variable $x$ in $\phi$, we create three variable vertices $x, x^T, x^F$.
+\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
 \item For each clause $c$ in $\phi$, we create one clause vertex $c$.
@@
 \begin{itemize}
-\item For each variable $x$ in $\phi$ we add the following five edges: 
-$x x^T, x x^F, x^T x^F, x^T v$ and $ x^Fv$.
-\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges: 
-$x^T y^T, x^Ty^F, x^Fy^T$ and $x^Fy^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x$ appear in $c$. If $x$ appears non-negated in $c$ we add edge $c x^T$. 
-If $x$ appears negated in $c$ we add edge $c x^F$.
+\item For each variable $x_i$ in $\phi$ we add the following five edges: 
+$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
+\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
+$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
+\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
+If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
 \end{itemize}
@@
 
-Now we specify the distances in the matrix $D^\phi$ between all vertex pairs.
-For the sake of simplicity we write $D^\phi _{x,y}$ as $d(x,y)$,
-where $x,y$ are two vertices. 
-We start by setting the value of $d(x,y) = 1$ where $x$ and $y$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x$ in $\phi$ we specify the following distance to the super vertex $v$:
-    $d(x,v)=2$. %, $d(x_2,v)=3$.
-
-    \item For each clause $c$ in $\phi$ we specify the following distance to the super vertex $v$:
-    $d(c,v)=2$
-    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distance:
-    $d(c,x)=2$.
-    If $x$ appears non-negated in $c$ we specify the following distance:
-    $d(c,x^F)=2$.
-    If $x$ appears negated in $c$ we specify the following distance:
-    $d(c,x^T)=2$.
-    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distance:
-    $d(c,x^T)=d(c,x^F)=2$.
-\end{itemize}
-All distances between non-adjacent vertex pairs that are not defined above are set to $\infty$.
-
-This finishes the construction of an instance $D^\phi$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $D^\phi$ is a yes-instance if and only if $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $D^\phi$ of \deltaExact\ is a yes-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(x x^T)=\lambda(x^T v)$, then we set $x$ to \textsc{True}, otherwise we set $x$ to \textsc{False}.
-
-To show that this yields a satisfying assignment, we need to show some following properties of $\lambda$.
-First, observe that adding some integer $t$ to all time labels does not change the duration of any temporal path.
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$, then there is a shortest path from $u$ to $w$ in $G$ such that $\lambda$ puts consecutive time labels on the edges of that shortest path.
-
-Let $\lambda(x x^T)=t$ and $\lambda(x x^F)=t'$, for an arbitrary variable $x$. 
-If both $\lambda(x^T v)\neq t+1$ and $\lambda(x^F v)\neq t'+1$, then $d(x,v)>2$, which is a contradiction. 
-Thus, for every variable $x$, we have that $\lambda(x^T v)= t+1$ or $\lambda(x^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x x^F)=\lambda(x^F v)$, then we set $x$ to \textsc{False}, since in this case $\lambda(x x^T)\neq\lambda(x^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for contradiction that the described assignment is not satisfying.
-Then there exists a clause $c$ that is not satisfied.
-Recall that we require $d(c,v)=2$.
-Hence, we must have a temporal path consisting of two edges from $c$ to $v$ such that the two edges have consecutive labels.
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$.
-Assume w.l.o.g\ that $x$ appears in $c$ non-negated (the case of a negated appearance of $x$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x^T$. 
-Then we have that $\lambda(c x^T)=\lambda(x^T v)-1$.
-Furthermore, since $d(c,x)=2$ we also have that $\lambda(c x^T)=\lambda(x x^T)-1$.
-It follows that $\lambda(x x^T)=\lambda(x^T v)$.
-However, this implies that $x$ is set to \textsc{True} in the satisfying assignment and thus the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x$ is set to \textsc{True}, we set $\lambda(x^F v)=3$.
-    \item If variable $x$ is set to \textsc{False}, we set $\lambda(x^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-
-Next, we verify that all distances are realized.
-\begin{itemize}
-    \item For each variable $x$ in $\phi$ we have $d(x,v)=2$:
-
-    If $x$ is set to \textsc{True}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(x x^F)=2$ and $\lambda(x^F v)=3$.
-If $x$ is set to \textsc{False}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(x x^T)=2$ and $\lambda(x^T v)=3$.
-
-    \item For each clause $c$ in $\phi$ we have that $d(c,v)=2$:
-
-    Since we have a satisfying assignment there is a variable $x$ appearing in $c$ that is set to a truth-value that satisfies $c$.
-If $x$ appears non-negated in $c$ (and hence is set to \textsc{True}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(c x^T)=1$ and $\lambda(x^T v)=2$.
-If $x$ appears negated in $c$ (and hence is set to \textsc{False}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x^F v)=2$.
-    \item Let $x$ be a variable that appears in clause $c$.
-    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_F)=2$:
-
-    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(c x^T)=1$ and $\lambda(x x^T)=\lambda(x^T x^F)=2$.
-
-    If $x$ appears negated in $c$ we have $d(c,x)=d(c,x_T)=2$:
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$.
-    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we have $d(c,x^T)=d(c,x^F)=2$:
-
-    Let $y$ be a variable that appears non-negated in $c$ (the case where $y$ appears negated is symmetrical).
-Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(c y^T)=1$ and $\lambda(y^T x^T)=\lambda(y^T x^F)=2$.
-\end{itemize}
-Lastly, we show that all non-adjacent vertex pairs $u,w$ with $d(u,w)=\infty$ are not temporally connected in $(G,\lambda)$.
-\begin{itemize}
-\item For all pairs of clause vertices $c,c'$ we have $d(c,c')=\infty$: 
-\todo[inline]{New matrix entries D for period Delta: d(c,c')=Delta+1 (using three edges, with labels L, L+1, L).}
-
-Since all edges incident with clause vertices have label one and clause vertices are pairwise non-adjacent, there cannot be a temporal path from one clause vertex to another.
-\item For all variable vertices $x$ and clause vertices $c$ we have $d(x,c)=\infty$:
-\todo[inline]{New matrix entries D for period Delta: if x appears (negated or not) in c, then d(x,c)=Delta (using two edges, with label L+1, L).
-Otherwise D(x,c)=2Delta (using three edges, with labels L, L, L-1).}
-
-Since all edges incident with variable vertices $x$ have label two and all edges incident with clause vertices $c$ have label one, there cannot be a temporal path from a variable vertex $x$ to a clause vertex $c$.
-\item For all pairs of variable vertices $x,y$ we have $d(x,y)=\infty$:
-\todo[inline]{New matrix entries D for period Delta: d(x,y)=2Delta+1 (using three edges, each with the same label).}
-
-Since all edges incident with variable vertices $x$ have label two and variable vertices $x$ are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
-\item For all pairs of variable vertices $x,y$ we have $d(y^T,x)=d(y^F,x)=\infty$:
-\todo[inline]{New matrix entries D for period Delta: $d(y^T,x)=d(y^F,x)=Delta+1$ (using two edges, with equal labels).}
-
-Since all edges incident with variable vertices $x$ have label two and all edges incident with variable vertices $y^T, y^F$ have labels two or three and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from a variable vertex $y^T$ or $y^F$ to variable vertex $x$.
-\item For all pairs of variable vertices $x,y$ we have $d(x,y^T)=d(x,y^F)=\infty$:
-\todo[inline]{New matrix entries D for period Delta: $d(x,y^T)=d(x,y^F)=Delta+1$ (using two edges, with equal labels).}
-
-Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$.
-Furthermore, $v$ has distance two from $x$ in the underlying graph $G$.
-Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three.
-Hence, there is no temporal path from $x$ to $y^T, y^F$ using an edge with label three.
-Since all edges incident with $x$ have label two and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from variable vertex $x$ to variable vertex $y^T$ or $y^F$.
-\item For all variable vertices $x$ and clause vertices $c$ we have $d(v,x)=d(v,c)=\infty$:
-\todo[inline]{New matrix entries D for period Delta: d(v,x)=Delta (using two edges, with labels L+1,L). 
-New matrix entries D for period Delta: d(v,c)=Delta (using two edges, with labels L,L-1).}
-
-All edges incident with $v$ have labels two or three.
-All edges incident with $x$ have label two and all edges incident with $c$ have label one.
-We immediately have that there is no temporal path from $v$ to $c$.
-Furthermore, since $x$ and $v$ are non-adjacent, we also have that there is no temporal path from $v$ to $x$.
-\end{itemize}
 %
@@
 	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
-For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neg j$) with a dotted line.
+For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with a dotted line.
 Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
@@
 \end{figure}
+%
+Now we specify the distances in the matrix $D^\phi$ between all vertex pairs.
+For the sake of simplicity we write $D^\phi _{u,v}$ as $d(u,v)$,
+where $u,v$ are two vertices of $G$. 
+We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
+\begin{itemize}
+    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
+    %$d(x_1,x_2)=2$. 
+    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
+    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
+    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
+    we specify the following distances:
+    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
+    \item For each clause $c$ in $\phi$ and the super vertex $v$
+    we specify the following distances:
+    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
+    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following distances:
+    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
+    If $x_i$ appears non-negated in $c$ we specify the following distances:
+    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
+    If $x_i$ appears negated in $c$ we specify the following distances:
+    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
+    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
+    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
+    and
+    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
+    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following distances:
+    $d(x_i,x_j)=2\Delta +1$ and
+    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
+    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following distances:
+    $d(c_i,c_j)= \Delta + 1$.
+\end{itemize}
+This finishes the construction of an instance $D^\phi$ of \deltaExact\, which can clearly be done in polynomial time.
+In the remainder we show that $D^\phi$ is a yes-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
+
+$(\Rightarrow)$: Assume the constructed instance $D^\phi$ of \deltaExact\ is a yes-instance. 
+Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
+%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
+
+We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
+if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{True}, otherwise we set $x_i$ to \textsc{False}.
+
+To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
+First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
+Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
+(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
+then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
+the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
+
+Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
+If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
+Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
+In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{False}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
+
+%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
+Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
+
+Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
+Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
+Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
+The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
+such that the two edges have consecutive labels. 
+By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
+Assume w.l.o.g\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
+Let us denote with $t = \lambda(x_1^T v)$.
+It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
+Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
+Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
+Which implies that $x_1$ is set to \textsc{True}.
+%
+Let us observe paths from $v$ to $c_1$.
+We know that $d(v,c)=\Delta -1$.
+The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
+Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
+$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
+This implies that
+the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
+Since there are only two other vertices connected to $c$, 
+we have only two other edges incident to $c$, that can be used on a fastest temporal path
+$v$ to $c$.
+Suppose now w.l.o.g\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta$ goes through vertex $x_2^T$.
+Let us denote with $t' = \lambda(x_2^T v)$.
+Since the fastest temporal path from $v$ to $c$ is of the duration $\delta - 1$,
+and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
+it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
+Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
+Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
+Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
+In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
+which implies that $x_2$ is set to \textsc{True}.
+But now we have that $x_1,x_2$ both appear in $c$, where one of them is \textsc{True}, while the other is \textsc{False},
+which implies that the clause $c$ is satisfied, a contradiction.
+
+%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
+Then we have that $\{c,x^T\}\in E(G)$.
+Assume that $\lambda(\{c,x^T\})=t$.
+Recall that we have specified $d(c,x_2)=2$.
+Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
+
+$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
+
+We construct a labeling $\lambda$ as follows.
+\begin{itemize}
+    \item All edges incident with a clause vertex $c$ obtain label one.
+    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
+    \item If variable $x_i$ is set to \textsc{True}, we set $\lambda(x_i^F v)=3$.
+    \item If variable $x_i$ is set to \textsc{False}, we set $\lambda(x_i^T v)=3$.
+    \item We set the labels of all other edges to two.
+\end{itemize}
+For an example of the constructed temporal graph see~\cref{fig:NP-example}.
+We now verify that all distances are realized.
+\begin{itemize}
+    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
+    and $d(v,x_i)=\Delta$.
+
+    If $x_i$ is set to \textsc{True}, then there is a temporal path from $x_i$ to $v$ via 
+    $x_i^F$ of duration $2$, since
+    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
+    For a temporal path from $v$ to $x_i$ we observe the following.
+    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
+    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
+    cannot finish before the time $\Delta + 2$.
+    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
+    and continue to $x_i$ at time $\Delta + 2$,
+    which gives us the desired duration $\Delta$.
+
+    If $x_i$ is set to \textsc{False}, then, by similar arguing, 
+    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
+    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
+
+    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
+    and $d(v,c)=\Delta - 1$:
+
+    Suppose $x_i,x_j,x_k$ appear in $c$.
+    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{True} and at least one to \textsc{False}. 
+    Suppose $x_i$ is the variable of the literal that is \textsc{True} in $c$,
+    and $x_j$ is the variable of the literal that is \textsc{False} in $c$.
+    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{True} (the case when $x_i$ appears negated in $c$ and is set to \textsc{False} is symmetric).
+    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
+    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{False} 
+    (the case when $x_j$ appears negated in $c$ and is set to \textsc{True} is symmetric).
+    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
+    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
+
+    \item Let $x_i$ be a variable that appears in clause $c$.
+    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
+    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
+
+    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
+    which proves the first equality.
+    There are also the following two temporal paths,
+    first, from $x_i$ to $c$ through $x_i^T$ and
+    second, from $x_i^F$ to $c$ through $x_i^T$.
+    Both of the temporal paths start on the edge with label $2$, as 
+    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
+    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
+
+    If $x$ appears negated in $c$ we have to check that 
+    $d(c,x_i)=d(c,x_i^T)=2$
+    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
+
+    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
+    which proves the first inequality.
+    There are also the following two temporal paths,
+    first, from $x_i$ to $c$ through $x_i^F$ and
+    second, from $x_i^T$ to $c$ through $x_i^F$.
+    Both of the temporal paths start on the edge with label $2$, as 
+    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
+    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
+    Which proves the second equality.
+
+    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
+    first,
+    $d(c,x_i^T)=d(c,x_i^F)=2$,
+    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
+    third, $d(x_i,c)=\Delta$,
+    and fourth $d(c,x_i)=2 \Delta + 2$.
+
+    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
+    Then there is a temporal path 
+    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
+    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
+    which proves the first equality.
+    Using the same temporal path in the opposite direction,
+    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
+    yields the second equality.
+    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
+    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
+    with labels $1, 2, 2$ respectively.
+    This proves the second equality.
+    Now for the case of a temporal path from $x_i$ to $c$,
+    we use the same three edges, but in the opposite direction,
+    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
+    again with labels $2, 2, 1$, respectively,
+    which proves the last equality.
+    Note that all of the above temporal paths are also the shortest possible, 
+    and since the labels of first and last edges (of these paths) are unique,
+    it follows that we cannot find faster temporal paths.
+
+    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
+    $d(x_i,x_j)=2\Delta +1$ and
+    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
+
+    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
+    $x_i^T$ or $x_i^F$, 
+    and then through one of the vertices $x_j^T$ or $x_j^F$.
+    This temporal path is of length $3$, where all of the edges have label $2$,
+    which proves the first equality.
+    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
+    passes through one of the vertices $x_i^T$ or $x_i^F$.
+    This path is of length two, where all of the edges have label $2$,
+    which proves the second equality.
+    Note that all of the above temporal paths are also the shortest possible, 
+    and since the labels of first and last edges (of these paths) are unique,
+    it follows that we cannot find faster temporal paths.
+
+    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
+    $d(c_i,c_j)= \Delta + 1$.
+
+    Let $x_k$ be a variable that appears non-negated in $c_i$
+    and $x_\ell$ the variable that appears non-negated in $c_j$
+    (all other cases are symmetric).
+    There is a path of length three from $c_i$ to $c_j$
+    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
+    Therefore the temporal path from $c_i$ to $c_j$
+    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
+    which proves the desired equality.
+    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
+    therefore it follows that this is the fastest temporal path.
+\end{itemize}
+%
 \end{proof}
@@
         \item We have one vertex $y^i$, one vertex $v^i_0$, and $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{n}$ and $n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{n}$.
+        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
         \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n+3$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{n+3}$.
@@
     %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
+    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
     %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
@@
     Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
+Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
+    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
 
@@
     Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
+If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
+If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
+Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
 
     Let $i+1<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{n},u^\ell_{n+\ell'-1}\}$ between $a^{i,j,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{n},u^\ell_{n+\ell'}\}$ between $b^{i,j,\ell}_{n}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
+Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
+    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
 
@@
     \end{itemize}
-    We add two connector gadgets for each edge selection gadget and one connector gadget for each validation gadget.
+    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
 
@@
     \end{itemize}
-    The \emph{connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Set $B$ contains all vertices vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists).
+    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
+    \begin{itemize}
+        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
+        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists).
+    \end{itemize}
+The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
+    \begin{itemize}
+        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists).
+        \item Set $B$ is empty.
     \end{itemize}
@@
 
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2,\hat{v}_3$ and with sets $A$ and $B$.
+Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
 Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
@@
     \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot(\ell'-\ell)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+3$.
+    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+5$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(2n+2)(j'-j)-1$.
+    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)-1$.
 \end{itemize}
 The next cases are only relevant if $1\neq i \neq k$. 
-For all $0\le j<i$ and $\ell\in[n+3]$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,\hat{u}^i_{\ell})=(2n+2)(i-j-1)+2\ell-1$.
-\end{itemize}
-For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-\begin{itemize}
-    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-\end{itemize}
+For all $0\le j<i$ %and $\ell\in[n+3]$ 
+we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+2)(i-j-1)+2n+5$.
+\end{itemize}
+%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
+%\begin{itemize}
+%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
+%\end{itemize}
 For all $0\le j<i$ and all $i<j'\le k$ we set the following.
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(2n+2)(j'-j)+2n-1$.
-\end{itemize}
-For all $\ell\in[n+3]$ and $i<j\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(\hat{u}^i_{\ell},v^i_j)=(2n+2)(j-i)+2(n-\ell)+5$.
+    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+2n+5$.
+\end{itemize}
+For all 
+%$\ell\in[n+3]$ and 
+$i<j\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+2)(j-i)-1$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(w^\star,x_1)=(2n+2)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^7$, $d(w,\hat{v}_2)=n^7$, $d(w,\hat{v}_1)=n^7-(2n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^7-(2n+2)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^7+2$ and $d(w,v)=n^7-(2n+2)(i+j)+3$.
+    \item We set $d(w^\star,x_1)=(20n+2)(i+j)$.
+    \item We set $d(w^\star,\hat{v}_1)=n^7$, $d(w,\hat{v}_2)=n^7$, $d(w,\hat{v}_1)=n^7-(20n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^7-(20n+2)(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^7+2$ and $d(w,v)=n^7-(20n+2)(i+j)+3$.
 \end{itemize}
@@
 \scriptsize
-\node (A) at (12,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (8, 1.5) {};
+\node (A) at (14,0) {};
+
+\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
 \node (A) at (-10.5,4.5) {alignment gadget};
@@
 \draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
+\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
 \node[rotate=90] (A) at (-14.5,-16) {connector gadget};
@@
 \draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-16) {verification gadget for $j$};
+\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
 
@@
     \node[vert] (W5) at (3.5,2) {};
+    \node[vert] (W6) at (9,2) {};
 
@@
     \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
+
+    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
+    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
+    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
+    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
+    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
+    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
 
@@
 
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+2$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+2$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+2$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+2$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+4n+2$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+4n+2$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+4n+2$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+4n+2$} (VSS);
+    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
+	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
+	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
+	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
+
+    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+4n+4$} (VSS);
+	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+4n+4$} (VSS);
+	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+4n+4$} (VSS);
+	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+4n+4$} (VSS);
 
@@
 
+    \draw[edge] (VH41) --node[timelabel,sloped] {$n^7$} (VH42);
+	\draw[edge] (VH42) --node[timelabel,sloped] {$n^7+1$} (VH411);
+	\draw[edge] (VH42) --node[timelabel] {$n^7+1$} (VH43);
+    \draw[edge] (VH43) --node[timelabel,sloped] {$n^7$} (VH44);	
+    \draw[edge] (VH43) --node[timelabel,sloped] {$n^7+1$} (VH444);
+
 	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
@@
 	\draw[edge] (W) --node[timelabel] {$1$} (W5);
+	\draw[edge] (W) --node[timelabel] {$1$} (W6);
 
@@
 	\draw[edge] (YI) --node[timelabel] {$n^6-1$} (W5);
+	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^7$} (W6);
 
@@
 \begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0$, $\hat{v}_1$, and $\hat{v}_2$ and sets $A,B$.
+    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
 Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
@@
 \begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell +2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell +18n+2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
 Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(2n+2)(i+j)$ we have that $\lambda(\{w,x_1\})=(2n+2)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(2n+2)(i+j)$.
+Since $d(w^\star,x_1)=(20n+2)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+2)(i+j)$.
+
+    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+2)(i+j)$.
 Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
 However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(2n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^7+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^7-(2n+2)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^7-(2n+2)(i+j)+3$, a contradiction.
+    Next, assume that $(20n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^7+2$.
+Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^7-(20n+2)(i+j)+3$.
+However, we have that $d(w,v_{i,j}^\star)=n^7-(20n+2)(i+j)+3$, a contradiction.
     Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^7+2$.
@@
 
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(2n+2)(i+j)$.
+    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+2)(i+j)$.
 Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell +2)$.
-Assume that $(i+j)\cdot (2n\ell 2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^7+2$.
+We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell +18n+2)$.
+Assume that $(i+j)\cdot (2n\ell +18n+2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^7+2$.
 Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
@@
 \begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +2)+4n+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +18n+2)+4n+4$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+
+    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u_{\ell'}^{2n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
 \end{claim}
 \begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=4n+3$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=4n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
 From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^7$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
@@
     It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u_{\ell'}^{2n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 4n+3$ (for sufficiently large $n$), a contradiction.
+Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 4n+5$ (for sufficiently large $n$), a contradiction.
 
@@
 Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=4n+3$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell +2)$.
-It follows that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell +2)+4n+2$.
+Hence, we have that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=4n+5$.
+    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell+18n +2)$.
+It follows that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell +18n+2)+4n+4$.
 We set $\sigma_{i,j}(\ell')=\ell$.
@@
 Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=4n+3$, we must have that all edges from vertices in $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
+Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=4n+5$, we must have that all edges from vertices in $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
 Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
@@
 \begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[2n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +2)+2\ell'$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
+    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[2n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +18n+2)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
 \end{claim}
 \begin{claimproof}
-    To do.
+    Let $1\le i<j\le k$ and $\ell\in[m]$.
+    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u_{\ell}^{2n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
+    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {\sigma_{i,j}(\ell)}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell)+18n +2)+4n+4$.
+It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u_\ell^{2n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {\sigma_{i,j}(\ell)} +18n+2)$ and arrives at $u_\ell^{2n}$ earlier than $(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +18n+2)+4n+4$.
+Hence, the temporal path $P$ has duration at most $4n+3$.
+
+    We investigate the temporal path $P$ from its destination $u_\ell^{2n}$ back to its start vertex $v_{i,j}^\star$.
+Consider the neighbors of $u_\ell^{2n}$ that are different from $v_{i,j}^{\star\star}$.
+By \cref{claim:2} we have that all edges from $u_\ell^{2n}$ to neighbors of $u_\ell^{2n}$ that are vertices of connector gadgets have a label of at least $n^7$.
+Hence, $P$ does not visit any of those neighbors.
+Next, consider neighbors of $u_\ell^{2n}$ is verification gadgets.
+Assume $u_\ell^{2n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
+Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
+Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$, since all these vertices have degree two.
+However, then $P$ would have a duration larger than $4n+3$.
+We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$.
+It follows that $P$ visits $u_\ell^{2n-1}$.
+    Here, we can make an analogous investigation.
+Additionally, we have to consider the case that $P$ visits a neighbor of $u_\ell^{2n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
+However, we can exclude this by a similar argument as above.
+
+    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u_\ell^{2n-1}\mid 0\le \ell'\le 2n\}$ and $v_{i,j}^\star$.
+    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
+Note that all vertices visited by $P$ are contained in $A\setminus B$.
+It follows that all pairs of non-adjacent vertices visited by $P$ have distance $3$.
+In particular, we have $d(u_\ell^{\ell'-1},u_\ell^{\ell'+1})=3$ for all $\ell'\in[2n-1]$ and $d(v_{i,j}^\star,u_\ell^{1})=3$.
+If follows that for every $\ell'\in[2n-1]$ we have that $\lambda(\{u_\ell^{\ell'},u_\ell^{\ell'+1}\})-\lambda(\{u_\ell^{\ell'-1},u_\ell^{\ell'}\})\ge 2$ and $\lambda(\{u_\ell^{1},u_\ell^{2}\})-\lambda(\{v_{i,j}^\star,u_\ell^{1}\})\ge 2$.
+
+    By investigating the sets $A,B$ of the first connector gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u_\ell^{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u_\ell^{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
+Furthermore, we get that $d(u_\ell^{2n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u_\ell^{2n}\})-\lambda(\{u_\ell^{2n-1},u_\ell^{2n}\})\ge 2$.
+Considering that $P$ visits $2n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $4n+3$ or we have that $\lambda(\{v_{i,j}^\star,u_\ell^{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u_\ell^{2n}\})-\lambda(\{u_\ell^{2n-1},u_\ell^{2n}\})< 2$.
+Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u_\ell^{2n}\})$ determined, all labels of edges traversed by $P$ are also determined and the claim follows.
     \end{claimproof}
@@
     %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1})\le n^6$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^7+2$.
-    For all $i=1$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,2,\ell}_{1})\le n^6$ or $\lambda(\{v_0^i,a^{i,2,\ell}_{1}\})\ge n^7+2$.
+    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^6$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^7+2$.
+    For all $i=1$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,2,\ell}_{1}\})\le n^6$ or $\lambda(\{v_0^i,a^{i,2,\ell}_{1}\})\ge n^7+2$.
 \end{claim}
@@
     Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^6<\lambda(\{v_0^i,a^{i,1,\ell}_{1})< n^7+2$.
-The there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^7+2$.
+Assume that $n^6<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^7+2$.
+Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^6$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^7+2$.
 However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^7+2$, a contradiction.
@@
 \begin{claim}\label{claim:9}
-    Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
+    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^7+2$.
+    For all $i=k$ and all $\ell\in[m]$ we have that $\lambda(\{v_{k-1}^i,b^{i,k-1,\ell}_{1}\})\le n^7+2$.
+%
+    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
 Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^7+2$.
@@
 \begin{claimproof}
-    To do.
+    Let $1\le i< k$ and $\ell\in[m]$.
+    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
+Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
+Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
+By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^7$ we have that both edges incident with $\hat{v}_0$ have label $n^7$.
+It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^7+2$.
+Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^7+2$.
+Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
+    The argument for case where $i=k$ is analogous.
 \end{claimproof}

### 2023-02-03 ICALP23-RealizingTemporalGraphs.tex
All changes of Thursday 2nd Feb

@@
 \begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard parameterized by the feedback vertex number.
+    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number.
 \end{theorem}
@@
 
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ as follows.
+We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+At the end of the proof we show how to obtain the result for finite $\Delta$ and a distance matrix $D$ that only has integer entries.
+
+    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
 To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to an edge connecting the two vertices.
@@
     \begin{itemize}
-        \item We have one vertex $y^i$, one vertex $v^i_0$, and $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$.
+        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
         \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n+3$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{n+3}$.
+        \item We have a set $\hat{U}_i$ of $11n$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{11n}$.
     \end{itemize}
@@
 
-    If $1\neq i\neq k$, then we add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[n+2]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. 
-    Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
+    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[11n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{11n},v^i_i\}$. 
+    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
 If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
 If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i+1<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
+%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
+
+    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
 Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
@@
         %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists).
+        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
     \end{itemize}
@@
     \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists).
+        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
         \item Set $B$ is empty.
@@
     \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_{n+3}$ (if exists) of each verification gadget.
+    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget.
     \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
@@
 %
-For all $0\le j<j'<i$ and all $i<j<j'\le k$ we set the following.
+For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
 \begin{itemize}
@@
 \end{itemize}
-The next cases are only relevant if $1\neq i \neq k$. 
-For all $0\le j<i$ %and $\ell\in[n+3]$ 
-we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+2)(i-j-1)+2n+5$.
-\end{itemize}
+%The next cases are only relevant if $1\neq i \neq k$. 
+%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
+%\begin{itemize}
+%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+2)(i-j-1)+2n+5$.
+%\end{itemize}
 %For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
@@
 %\end{itemize}
-For all $0\le j<i$ and all $i<j'\le k$ we set the following.
+For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+2n+5$.
+    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+2n-1$.
 \end{itemize}
-For all 
+%For all 
 %$\ell\in[n+3]$ and 
-$i<j\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+2)(j-i)-1$.
-\end{itemize}
+%$i<j\le k$ we set the following.
+%\begin{itemize}
+%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+2)(j-i)-1$.
+%\end{itemize}
 
@@
     \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$\hat{u}_{n+3}^j$, fill=gray] (UIN3) at (5,-21) {};
+    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
     \node (A) at (5,-22.5) {$\vdots$};
@@
     For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^6$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^7+2$.
-    For all $i=1$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,2,\ell}_{1}\})\le n^6$ or $\lambda(\{v_0^i,a^{i,2,\ell}_{1}\})\ge n^7+2$.
+    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^6$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^7+2$.
 \end{claim}
@@
     For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^7+2$.
-    For all $i=k$ and all $\ell\in[m]$ we have that $\lambda(\{v_{k-1}^i,b^{i,k-1,\ell}_{1}\})\le n^7+2$.
+    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{11n}\})\le n^7+2$.
 %
@@
 Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. We first consider the case that $1\neq i\neq k$.
+Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+2)+2n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
+We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
+
+\begin{claim}\label{claim:10}
+Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
+\end{claim}
+\begin{claimproof}
+Assume for contradiction that $P$ visits a vertex of a connector gadget.
+Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^7$.
+By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^7+2$.
+This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
+Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^6$.
+It follows that the arrival time of $P$ must be smaller than $n^7$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
+\end{claimproof}
+
+\begin{claim}\label{claim:11}
+Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
+\end{claim}
+\begin{claimproof}
+    Note that $P$ starts outside the alignment gadget.
+This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
+However, these vertices have degree two and the edge to $w^\star$ has label one.
+It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
+\end{claimproof}
+
+It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
+In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'}\mid \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
+From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$.
+Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
+In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$ until it reaches $v^i_1$.
+More generally, we can make the following observation.
+\begin{claim}\label{claim:12}
+    Let $i,j\in\{0,1,\ldots,k\}$.
+Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $11n+3$ vertices and no vertex of a connector gadget or the alignment gadget.
+Then $P$ cannot visit vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
+\end{claim}
+\begin{claimproof}
+    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
+Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
+    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
+    \begin{itemize}
+        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''}\mid \ell''\in[5n]\}$,
+        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''}\mid \ell''\in[5n]\}$, 
+        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''}\mid \ell''\in[5n]\}$, and
+        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''}\mid \ell''\in[5n]\}$.
+    \end{itemize}
+    Furthermore, by construction of $G$, we have that the distance of $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
+
+    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
+This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$.
+Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''}\mid \ell''\in[5n]\}$.
+
+    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
+From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $n+3$.
+Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $11n+3$ vertices.
+
+    Lastly, consider the case that $j=i-1$ or $j=i$.
+Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $11n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$.
+The claim follows.
+\end{claimproof}
+Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
+\begin{claim}\label{claim:13}
+    Let $i,j\in\{0,1,\ldots,k\}$.
+Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
+Then $P$ has duration at least $20n$.
+\end{claim}
+\begin{claimproof}
+    As argued in the proof of \cref{claim:11}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $11n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$.
+We analyse the former case first.
+
+    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
+It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ have distance (according to $D$) three.
+It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
+Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
+It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
+
+    In the latter case, where $P$ traverses a segment of the $11n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
+\end{claimproof}
+
+Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+2)+2n-1$.
+By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
+Next, we analyse which vertices in this set are visited by $P$.
+
+\begin{claim}\label{claim:14}
+Let $i\in[k]$.
+Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
+Then $P$ visits all vertices in $\{v^j_i\mid 0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i\mid 0\le j\le k\}$.
+\end{claim}
+\begin{claimproof}
+    To do.
+\end{claimproof}
+
+Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
+We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+1$.
+The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $22n+1$.
+To do.
 
 \subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution. To do.
+
+\subparagraph{Infinity Gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$. To this end, we introduce the \emph{infinity gadget}. To do.
 \end{proof}

### 2023-02-05 ICALP23-RealizingTemporalGraphs.tex
Finished W[1]-hardness by Hendrik, one direction. Sunday 5th feb

@@
 \section{Preliminaries}
-
-Let $G=(V,E)$ and $k,\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ be an edge-labeling function that assigns to every edge of $G$ exactly $k$ different labels from $\{1,\ldots,\Delta\}$.
+An interval on $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] \coloneqq \{ i\in \mathbb N_0 \mid a \leq i \leq b\}$
+and $[a] \coloneqq [1,a]$.
+An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
+and a set~$E \subseteq V \times V$ of edges.
+For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
+We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
+For the simplicity and the sake of an easier representation we sometimes denote an edge $e$ also as a sequence $uv$.
+A path~$P \subset G$ is a graph with a vertex set~$V(P)=\{v_1,\dots,v_k\}$ of distinct vertices and edge set~$E(P)=\{\{v_i,v_{i+1}\}\mid 1\leq i<k\}$
+(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
+
+\begin{definition}[temporal graph~\cite{KKK00}]
+\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
+where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
+\end{definition}
+
+Let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ one of the labels from $\{1,\ldots,\Delta\}$.
 Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,\lambda_{\Delta})$, where for every edge $e\in E$ we have $\lambda_{\Delta}(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$.
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. If $k=1$, we call $\lambda$ a \emph{simple $\Delta$-periodic labeling} of $G$.
+In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$.
+When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is $\Delta$ periodic temporal graph.
 
 \begin{definition}[temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph.
-A \emph{temporal path} $P$ from $u=u_0$ to $v=u_k$ in $(G,\lambda)$ is a sequence $(u_0 u_1,t_1),(u_1 u_2,t_2),\ldots,(u_{k-1} u_k,t_k)$, where $(u_0,u_1,\ldots,u_k)$ is a path in the underlying static graph $G$, $t_i\in \lambda(u_{i-1}u_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$.
-The \emph{duration} of this temporal path $P$ from $u$ to $v$ is $d(P)=t_k - t_1 + 1$.
-A \emph{fastest} temporal path $P$ from $u$ to $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest possible duration.
+Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} $(P,\lambda)$ from $u=u_0$ to $v=u_k$ in $(G,\lambda)$ is a sequence $(u_0 u_1,t_1),(u_1 u_2,t_2),\ldots,(u_{k-1} u_k,t_k)$, 
+where $P=(u_0,u_1,\ldots,u_k)$ is a path in the underlying static graph $G$ (we usually say that $P$ is the underlying path of $(P,\lambda)$), 
+$t_i\in \lambda(u_{i-1}u_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
+The \emph{duration} of this temporal path $(P,\lambda)$ from $u$ to $v$ is $d(P,\lambda)=t_k - t_1 + 1$.
+A \emph{fastest} temporal path $(P,\lambda)$ from $u$ to $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest possible duration.
 The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
@@
 
+Let $P$ be a path from $u$ to $v$ in $G$. 
+We denote with $d(P,u,v)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(P,u,v) \geq d(u,v)$.
+
 \problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, positive integer $\Delta$.}
+{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
 {Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a simple $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to the entry $D_{i,j}$.}
 
 Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$ that we are looking for in the above problems. 
-For simplicity of the presentation (and with a slight abuse of notation), we may refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we might put as indices of the matrix $D$ the corresponding vertices of $G$ instead of their numbering.
+For simplicity of the presentation (and with a slight abuse of notation), we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
+$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ instead of their numbering.
+Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
+as a temporal path in $(G,\lambda)$,
+where we actually mean that $(P,\lambda)$ is a temporal path with the underlyg path $P$.
 
@@
     \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the temporal path from $v_0$ to $v_p$.
-        Then $d(P) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
+        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
+        $(P, \lambda)$ from $v_0$ to $v_p$.
+        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
     \end{observation}
@@
     Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $P=P_{1,k}$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $P_{1,i}$ the sub-path of temporal path $P_{1,k}$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that $P_{1,i}$ is also the fastest temporal path from $u=v_1$ to any other vertex $v_i$ in $P$.
-    Then we can determine travel delays on $P$ using the following equation
+    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
+    Suppose that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to any other vertex $v_i$ in $P$.
+    Then we can determine travel delays on vertices of $P$ using the following equation
     \begin{equation}\label{eq:trav-delays-paths}
@@
 \begin{proof}
-    Let $P$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
+    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
     Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
@@
 Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $P_{i,j}$ from $v_i$ to $v_j$ and $P_{j,i}$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
+Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
 and therefore are the fastest.
@@
     1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j}) & \text{else}
+    d(P_{i,j},\lambda) & \text{else}
     \end{cases},
 \end{equation*}
-where $d(P_{i,j})$ is the duration of the (unique) temporal path $P_{i,j}$ from $v_i$ to $v_j$.
+where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
 
@@
     Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $P_{i,j}$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j}) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $P_{i,j}$.
+    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
+    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
     Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
@@
 
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know how it looks like.
+    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
     For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
@@
     We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, which has to also be the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+    We now take the unique path $P_{i,j}$ in $G$, 
+    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
     We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$.
-All other values of $T$ are set to \textsc{Null}.
+    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
+    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
     Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
@@
     Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing a label of one arbitrary edge as $a$, where $a \in [\Delta]$.
+    We start by fixing a label of an arbitrary edge as $a$, where $a \in [\Delta]$.
     Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
@@
 Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the fastest temporal path from $v_i$ to $v_j$, using the positive (resp.~negative) side of the cycle, 
+Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
+using positive (resp.~negative) side of the cycle, 
 \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
@@
 
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1} = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
+    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
     W.l.o.g. we can suppose that $a \geq a'$.
     Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
+    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
     Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
+    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
     $b - b' < a - a'$.
     Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \delta + b') -b + 1$, for some non-negative integer $k'$.
+    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
+    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
     Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \delta + b') -b + 1 < \delta + a - a + 1$.
-    Which is equivalent to  $(k' \delta + b') -b < \delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \delta + b' -b < \delta + a' - a $ which is equivalent to $b' -b < a' - a$.
+    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
+    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
+This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
     This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
@@
 $(\Rightarrow)$: Assume the constructed instance $D^\phi$ of \deltaExact\ is a yes-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
+Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
 %In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
@@
 Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\delta - 1$,
+Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
 and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
@@
         %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^\ell_{2n}\}$ for all $\ell\in[m]$.
-Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
+        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
+        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
+        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
+        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
         \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
@@
     \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{2n},v_{i,j}^{\star\star}\}$.
+        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
 
         %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [2n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
+        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
     \end{itemize}
@@
         \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $11n$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{11n}$.
+        \item We have a set $\hat{U}_i$ of $13n$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n}$.
     \end{itemize}
@@
 
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[11n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{11n},v^i_i\}$. 
+    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[11n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n},v^i_i\}$. 
     %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
@@
     Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
+Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
+    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
 
@@
 \begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot(\ell'-\ell)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=4n+5$.
+    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
+    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+2n-1$.
+    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+6n-1$.
 \end{itemize}
@@
     \item We set $d(w^\star,x_1)=(20n+2)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^7$, $d(w,\hat{v}_2)=n^7$, $d(w,\hat{v}_1)=n^7-(20n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^7-(20n+2)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^7+2$ and $d(w,v)=n^7-(20n+2)(i+j)+3$.
+    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+2)(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+2)(i+j)+3$.
 \end{itemize}
@@
 \begin{itemize}
-    \item We set $d(w^\star,y^i)=n^6-1$ and $d(w',v^i_0)=2$.
-    \item We set $d(w^\star,\hat{v}_1)=n^7$, $d(w^\star,\hat{v}_2)=n^7$, $d(w',\hat{v}_1)=n^7-n^6$, and $d(w',\hat{v}_2)=n^7-n^6$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^7+1$, $d(w,v)=n^7-n^6+2$, and $d(y^i,v)=n^7-n^6+2$.
+    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
+    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
 \end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^7$.
+Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
 
@@
 
-    \node[vert,label=left:$u_{2n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{2n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{2n}^3$] (U2N3) at (-4,-20) {}; 
+    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
+    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
+    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
     \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{2n}^m$] (U2NM) at (0,-20) {};
+    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
 
@@
 
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+4n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+4n+4$} (VSS);
+    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
+	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
 	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+4n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+4n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^7$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^7+1$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^7+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^7$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^7+1$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^7$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^7+1$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^7+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^7$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^7+1$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^7$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^7+1$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^7+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^7$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^7+1$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^7$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^7+1$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^7+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^7$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^7+1$} (VH444);
+	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
+
+    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
+	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
+	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
+    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
+	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
+
+    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
+	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
+	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
+    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
+	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
+
+    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
+	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
+	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
+    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
+    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
+
+    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
+	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
+	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
+    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
+    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
 
@@
 	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^7$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^7$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^7$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^6-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^7$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^6$} (VI0);
+	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
+	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
+	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
+	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
+	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
+
+	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
 
@@
 Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^7$ and at most $n^7+2$.
+We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
 More precisely, we show the following.
@@
         %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^7$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^7+2$,
+        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
         %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^7+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^7$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^7+2$. 
-        %\item For all $v\in V^\star$ we have $n^7\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^7+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^7$ and $\lambda(\{\hat{v}_2,v\})=n^7+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^7$ and $\lambda(\{\hat{v}_2,v\})=n^7$.
+        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
+        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
+        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
+        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
         %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^7\le \lambda(\{\hat{v}_1,v\})\le n^7+2$ and $n^7\le \lambda(\{\hat{v}_2,v\}) \le n^7+2$.
+        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
     %\end{itemize}
@@
     Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^7$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^7$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^7$.
+We have $d(w^\star,\hat{v}_0)=n^9$.
+It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
+Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
     Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^7+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^7+2$.
+Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
 Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^7$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^7+2$.
+Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
 
@@
 Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^7$ and $\lambda(\{\hat{v}_2,v\})\ge n^7$.
+It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
 Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
 Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^7+2$ and $\lambda(\{\hat{v}_2,v\})\le n^7+2$.
+It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
 Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^7$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^7+2$ or $\lambda(\{\hat{v}_2,v\})=n^7+2$.
+%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
+%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
 \end{claimproof}
@@
 \begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})\le n^7+2$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
 Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u_\ell^{2n}\notin B$ and hence $d(\hat{v}_0,u_\ell^{2n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^7$ we have that both edges incident with $\hat{v}_0$ have label $n^7$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u_\ell^{2n}$ arrives at $u_\ell^{2n}$ at time $n^7+2$.
-Now assume for contradiction that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})> n^7+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u_\ell^{2n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
+Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
+By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
+It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
+Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
+Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
 \end{claimproof}
@@
 \begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell +18n+2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
 However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^7+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^7-(20n+2)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^7-(20n+2)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^7+2$.
+    Next, assume that $(20n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
+Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+2)(i+j)+3$.
+However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+2)(i+j)+3$, a contradiction.
+    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
 Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
 This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^7$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^7+2$.
+It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^9$.
+However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
 It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
@@
 Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell +18n+2)$.
-Assume that $(i+j)\cdot (2n\ell +18n+2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^7+2$.
+We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+2)$.
+Assume that $(i+j)\cdot (2n\ell^2 +18n+2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
 Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
 Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^7$ and at most $n^7+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^7$ and at most $n^7+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell-1)+1$.
+By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
+Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
+It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
 Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
 In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^7+2$.
+    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
 Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^7$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^7+2$, a contradiction.
+Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
 \end{claimproof}
@@
 \begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +18n+2)+4n+4$, where $u_\ell^{2n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u_{\ell'}^{2n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
+    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
+
+    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
 \end{claim}
 \begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=4n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^7$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
+    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
 In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
@@
     Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^7+2$.
+By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
 It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
 
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^7$ except the ones to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^4$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u_{\ell'}^{2n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 4n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u_{\ell'}^{2n}$ for some $\ell'\in[m]$ as its second last vertex.
+    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
+By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
+    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
+Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
+
+    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
 Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=4n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell+18n +2)$.
-It follows that $\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell +18n+2)+4n+4$.
+Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
+    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
+It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+2)+8n+4$.
 We set $\sigma_{i,j}(\ell')=\ell$.
@@
 Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u_{\ell}^{2n},v_{i,j}^{\star\star}\})=\lambda(\{u_{\ell'}^{2n},v_{i,j}^{\star\star}\})$.
+Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
 However, by \cref{claim:4} we have that all edges from $v_{i,j}$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=4n+5$, we must have that all edges from vertices in $\{u_{\ell''}^{2n}\mid \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
+Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n}\mid \ell''\in[m]\}$ as its second last vertex.
+Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n}\mid \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
 Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
@@
 \begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[2n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +18n+2)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
+    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
 \end{claim}
@@
     Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u_{\ell}^{2n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {\sigma_{i,j}(\ell)}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u_\ell^{2n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell)+18n +2)+4n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u_\ell^{2n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {\sigma_{i,j}(\ell)} +18n+2)$ and arrives at $u_\ell^{2n}$ earlier than $(i+j)\cdot (2n\cdot \sigma_{i,j}(\ell) +18n+2)+4n+4$.
-Hence, the temporal path $P$ has duration at most $4n+3$.
-
-    We investigate the temporal path $P$ from its destination $u_\ell^{2n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u_\ell^{2n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u_\ell^{2n}$ to neighbors of $u_\ell^{2n}$ that are vertices of connector gadgets have a label of at least $n^7$.
+    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
+    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
+It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+2)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+8n+4$.
+Hence, the temporal path $P$ has duration at most $8n+3$.
+
+    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
+Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
+By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
 Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u_\ell^{2n}$ is verification gadgets.
-Assume $u_\ell^{2n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
+Next, consider neighbors of $u^\ell_{4n}$ is verification gadgets.
+Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
 Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
 Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$, since all these vertices have degree two.
-However, then $P$ would have a duration larger than $4n+3$.
-We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$.
-It follows that $P$ visits $u_\ell^{2n-1}$.
+   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
+Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ have distance (according to $D$) three and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
+    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
     Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u_\ell^{2n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
+Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
 However, we can exclude this by a similar argument as above.
 
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u_\ell^{2n-1}\mid 0\le \ell'\le 2n\}$ and $v_{i,j}^\star$.
+    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'}\mid 0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
     Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
@@
 It follows that all pairs of non-adjacent vertices visited by $P$ have distance $3$.
-In particular, we have $d(u_\ell^{\ell'-1},u_\ell^{\ell'+1})=3$ for all $\ell'\in[2n-1]$ and $d(v_{i,j}^\star,u_\ell^{1})=3$.
-If follows that for every $\ell'\in[2n-1]$ we have that $\lambda(\{u_\ell^{\ell'},u_\ell^{\ell'+1}\})-\lambda(\{u_\ell^{\ell'-1},u_\ell^{\ell'}\})\ge 2$ and $\lambda(\{u_\ell^{1},u_\ell^{2}\})-\lambda(\{v_{i,j}^\star,u_\ell^{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u_\ell^{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u_\ell^{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u_\ell^{2n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u_\ell^{2n}\})-\lambda(\{u_\ell^{2n-1},u_\ell^{2n}\})\ge 2$.
-Considering that $P$ visits $2n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $4n+3$ or we have that $\lambda(\{v_{i,j}^\star,u_\ell^{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u_\ell^{2n}\})-\lambda(\{u_\ell^{2n-1},u_\ell^{2n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u_\ell^{2n}\})$ determined, all labels of edges traversed by $P$ are also determined and the claim follows.
+In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
+If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
+
+    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
+Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
+Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
+Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ determined, all labels of edges traversed by $P$ are also determined and the claim follows.
     \end{claimproof}
@@
 \begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^6$.
+    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
 \end{claim}
@@
     Let $w\in \hat{E}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^6-1$.
-It follows that $\lambda(\{w,y^i\})=n^6-1$.
+Note that we have $d(w^\star,y^i)=n^8-1$.
+It follows that $\lambda(\{w,y^i\})=n^8-1$.
 Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^6$.
+It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
 \end{claimproof}
@@
     %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^6$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^7+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^6$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^7+2$.
+    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
+    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
 \end{claim}
@@
     Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^6<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^7+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^6$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^7+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^7+2$, a contradiction.
+Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
+Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
+However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
 The argument for case where $i=1$ is analogous.
@@
 \begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^7+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{11n}\})\le n^7+2$.
+    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
+    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{11n}\})\le n^9+2$.
 %
     %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^7+2$.
+Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
 \end{claim}
@@
 Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^7$ we have that both edges incident with $\hat{v}_0$ have label $n^7$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^7+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^7+2$.
+By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
+It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
+Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
 Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
@@
 Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+2)+2n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
+Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+2)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
 We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
@@
 Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^7$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^7+2$.
+Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
+By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
 This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^6$.
-It follows that the arrival time of $P$ must be smaller than $n^7$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
+Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
+It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
 \end{claimproof}
@@
 Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$ until it reaches $v^i_1$.
+In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$ until it reaches $v^i_1$.
 More generally, we can make the following observation.
@@
     Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $11n+3$ vertices and no vertex of a connector gadget or the alignment gadget.
+Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n$ vertices and no vertex of a connector gadget or the alignment gadget.
 Then $P$ cannot visit vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
@@
     We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $n+3$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $11n+3$ vertices.
+From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
+Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n$ vertices.
 
     Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $11n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$.
+Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$.
 The claim follows.
@@
 \begin{claimproof}
-    As argued in the proof of \cref{claim:11}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $11n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$.
+    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$.
 We analyse the former case first.
@@
 
-    In the latter case, where $P$ traverses a segment of the $11n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell\mid \ell\in[11n]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
+    In the latter case, where $P$ traverses a segment of the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
 \end{claimproof}
 
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+2)+2n-1$.
+Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+2)+6n-1$.
 By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
@@
 Then $P$ visits all vertices in $\{v^j_i\mid 0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i\mid 0\le j\le k\}$.
+Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
 \end{claim}
 \begin{claimproof}
-    To do.
+Let $X\subseteq \{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
+By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+2)+6n-1$, a contradiction.
+
+    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
+    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
+    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
+    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
+    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
+
+    %Consider the first potential. 
+    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
+    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
+We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
+    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
+    We can conclude that $|X|=k+1$.
+    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
+
+    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
+However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
+As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
+More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
+To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell\in[m]$.
+Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$.
+
+By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'}\mid \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
+The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''}\mid \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
+By construction of $G$, the distance between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
+Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
+
+It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
+Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
+We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
+Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
+However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+2)+6n-1$, a contradiction.
+
+We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
+%
+   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
+    %
     \end{claimproof}
@@
 We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+1$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $22n+1$.
+The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+1$.
 To do.
 
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution. To do.
-
-\subparagraph{Infinity Gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$. To this end, we introduce the \emph{infinity gadget}. To do.
+\begin{claim}\label{claim:15}
+    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
+Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
+If $P$ has duration at most $20n+1$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
+\end{claim}
+\begin{claimproof}
+    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+1$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'}\mid \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$.
+By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
+By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
+If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+1$.
+\end{claimproof}
+
+\begin{claim}\label{claim:16}
+    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+1$.
+\end{claim}
+\begin{claimproof}
+    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$.
+Assume $P$ follows this path.
+By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
+It follows that $P$ has duration at least $26n+1$.
+By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
+If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
+By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
+Hence, the duration of $P$ is at least $40n$.
+\end{claimproof}
+
+\begin{claim}\label{claim:17}
+Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
+\end{claim}
+\begin{claimproof}
+    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
+\end{claimproof}
+
+From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest path temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
+\begin{enumerate}
+    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+1$.
+    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+1$.
+    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
+\end{enumerate}
+If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
+
+Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
+By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
+%By construction of $G$ we have that $\ell'\in[n]$.
+By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
+Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
+%By construction of $G$ we have that $\ell'\in[n]$.
+By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+2)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
+We have that
+\begin{align*}
+%\[
+& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
+%\]
+%\[
+& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+2)+2\ell'''+2\\
+& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2) = \\
+%\]
+%\[
+& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 2
+%\]
+\end{align*}
+By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
+\[
+\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+2.
+\]
+It follows that 
+\[
+(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
+\]
+Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
+However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
+We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
+In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
+It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
+
+Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
+By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
+Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
+Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
+
+Assume now that $1\neq i\neq k$.
+By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+1$.
+Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
+By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
+By analogous arguments as above and the fact that the duration of $P_i$ is $26n+1$ we get that 
+\[
+\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+2.
+\]
+It follows that 
+\[
+(2i+1)\cdot (20n+2)+2\ell'''+2 -((2i-1)\cdot (20n+2)+2\ell'+2) = 46n+2,
+\]
+and hence $\ell'''-\ell'=3n$.
+By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''}\mid \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''}\mid \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
+Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''}\mid \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''}\mid \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
+
+Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
+Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
+By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
+It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
+
+We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
+
+\subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution. We construct the following labelling for $G$.
+
+We start with the labels for edges from the alignment gadget. 
+\begin{itemize}
+    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
+    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
+    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$.
+    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+2)$.
+\end{itemize}
+
+Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
+\begin{itemize}
+    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
+    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
+    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
+    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
+    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
+    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
+(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
+\end{itemize}
+
+\subparagraph{Infinity Gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
+To this end, we introduce the \emph{infinity gadget}.
+We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
+Let $V$ denote the set of all remaining vertices.
+We set the following distances.
+\begin{itemize}
+    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
+    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
+    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
+    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
+    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
+    \item For every pair of vertices $v,v'\in V$ where previously the distance from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
+\end{itemize}
+Now we analyse which implications we get for the labels on the newly introduced edges.
+Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
+%\begin{itemize}
+    %\item 
+    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
+    %\item 
+    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
+    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
+    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
+%\end{itemize}
+For an illustration see \cref{fig:hardness2}.
+It is easy to check that all distances requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all distance requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
+Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
+
+\begin{figure}[t]
+%\noindent\makebox[\textwidth]{
+\centering
+%\begin{center}
+\begin{tikzpicture}[line width=1pt, scale=.65]
+\scriptsize
+
+\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
+\node (A) at (2,-7) {$V$};
+
+    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
+    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
+    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
+    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
+
+    \node[vert,label=below:$v$] (V) at (-2,-7) {};
+    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
+
+    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
+    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
+    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
+
+    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
+    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
+    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
+    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
+\end{tikzpicture}
+    %\end{center}
+%    }
+    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
+\end{figure}
+
+Lastly, consider two vertices $v,v'\in V$.
+Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
+Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
+This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
+Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
+For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
+We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
 \end{proof}
@@
 
+\todo[inline]{George proved it. Added proof inside. Check if OK?\\
+Check the proof below and correct it/make it pretty.}
+
 \begin{proof}
@@
 So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.
-\todo[inline]{George proved it.
-Also: add notation that is used in the proof to the beginning of the section, namely: $d(u,v,P)$ is the duration of the temporal path from $u$ to $v$ that traverses the edges of $P$.}
+
+In the following, we only consider \emph{wasteless} temporal paths. A temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ is \emph{wasteless}
+if, for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
+
+	\begin{definition}
+		\label{arrival-duration-def}Let $u,v\in V$, and let $t\in 
+		%TCIMACRO{\U{2115} }%
+		%BeginExpansion
+		\mathbb{N}
+		%EndExpansion
+		$. Given that a temporal path starts within the period $[t,t+\Delta -1]$,
+		the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$ is $%
+		A_{t}(u,v)$, and the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$
+		to $v$ is $A_{t}(u,v,P)$.
+	\end{definition}
+
+	Whenever $t=1$, we may omit the index $t$, i.e. we may write $%
+	A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$. The following refers to
+	Figure~\ref{conj-fig}.
+
+	Initial assumptions:
+
+	\begin{enumerate}
+		\item $d(u_{0},u_{i})=d(u_{0},u_{i},P)\leq d(u_{0},u_{i},Q)$; denote $\delta
+		_{0}=d(u_{0},u_{i},Q)-d(u_{0},u_{i})\geq 0$.
+
+		\item $d(u_{0},u_{k})=d(u_{0},u_{k},Q\cup R)\leq d(u_{0},u_{k},P\cup R)$.
+	\end{enumerate}
+
+	General properties:
+
+	\begin{itemize}
+		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
+		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
+		u$ to $v$.
+	\end{itemize}
+
+	\bigskip
+
+	Let $t_{u_{1}}\in \lbrack 1,\Delta ]$ be the label of the edge $u_{0}u_{1}$,
+	and denote by $t_{v_{1}}$ the appearance of the edge $u_{0}v_{1}$ within the
+	period $[t_{u_{1}},t_{u_{1}}+\Delta -1]$. Note that $1\leq t_{u_{1}}\leq
+	\Delta $ and that $t_{u_{1}}\leq t_{v_{1}}\leq 2\Delta $. By the first
+	initial assumption, we have:
+
+	\begin{equation*}
+		\delta
+		_{0}=d(u_{0},u_{i},Q)-d(u_{0},u_{i})=A_{t_{u_{1}}}(u_{0},u_{i},Q)-A_{t_{u_{1}}}(u_{0},u_{i},P)+\left( t_{v_{1}}-t_{u_{1}}\right)
+	\end{equation*}%
+	and thus%
+	\begin{equation}
+		A_{t_{u_{1}}}(u_{0},u_{i},P)-A_{t_{u_{1}}}(u_{0},u_{i},Q)=t_{v_{1}}-(t_{u_{1}}+\delta _{0})
+		\label{basic-eq-1}
+	\end{equation}
+
+	\begin{lemma}
+		\label{lem-1}If $t_{v_{1}}\neq t_{u_{1}}$ then $\delta _{0}\leq \Delta -2$
+		and $t_{v_{1}}\geq t_{u_{1}}+\delta _{0}+1$.
+	\end{lemma}
+
+	\begin{proof}
+		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by (\ref%
+		{basic-eq-1}) that $%
+		A_{t_{u_{1}}}(u_{0},u_{i},P)-A_{t_{u_{1}}}(u_{0},u_{i},Q)\leq
+		t_{v_{1}}-t_{u_{1}}-\Delta +1\leq 0$, and thus $A_{t_{u_{1}}}(u_{0},u_{i},P)%
+		\leq A_{t_{u_{1}}}(u_{0},u_{i},Q)$. Therefore, since we can traverse path $P$
+		from $u_{0}$ to $u_{i}$ by departing at time $t_{v_{1}}\geq t_{u_{1}}+1$ and
+		by arriving no later than traversing path $Q$, we have that $d(u_{0},u_{k},P\cup Q)<d(u_{0},u_{k},Q\cup R)$, which is a contradiction to the
+		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
+
+		Now assume that $t_{u_{1}}+1\leq t_{v_{1}}\leq t_{u_{1}}+\delta _{0}$. Then,
+		it follows by (\ref{basic-eq-1}) that $A_{t_{u_{1}}}(u_{0},u_{i},P)\leq
+		A_{t_{u_{1}}}(u_{0},u_{i},Q)$ which is, similarly to the previous case, a
+		contradiction. Therefore $t_{v_{1}}\geq t_{u_{1}}+\delta _{0}+1$.
 	\end{proof}
 
+	\medskip
+
+	The next corollary follows immediately from Lemma \ref{lem-1}.
+
+	\begin{corollary}
+		\label{cor-1}If $t_{v_{1}}\neq t_{u_{1}}$ then $1\leq
+		A_{t_{u_{1}}}(u_{0},u_{i},P)-A_{t_{u_{1}}}(u_{0},u_{i},Q)\leq \Delta
+		-1-\delta _{0}$.
+	\end{corollary}
+
+	\begin{lemma}
+		\label{lem-2}$d(u_{0},u_{i-1},P\cup \{u_{i}u_{i-1}\})>d(u_{0},u_{i-1},Q\setminus
+		\{u_{i}u_{i-1}\})$.
+	\end{lemma}
+
+	\begin{proof}
+		Let $e\in \lbrack 1,\Delta ]$ be the label of the edge $u_{i-1}u_{i}$, and
+		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
+		edge $u_{i}u_{i+1}$ after time $e$. Let $A_{t_{u_{i}}}(u_{0},u_{i},Q)=x%
+		\Delta +e$. Then $A_{t_{u_{i}}}(u_{0},u_{i+1},Q\cup\{u_{i}u_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
+		that $A_{t_{u_{i}}}(u_{0},u_{i},P)=x\Delta +g$.
+
+		\emph{Case 1: }$t_{v_{1}}\neq t_{u_{1}}$\emph{.} Then Corollary \ref{cor-1}
+		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
+		Then, we can traverse path $P$ from $u_{0}$ to $u_{i}$ by departing at time $%
+		t_{v_{1}}\geq t_{u_{1}}+1$ and by arriving at most at time $x\Delta +f-1$,
+		and thus $d(u_{0},u_{k},P\cup R)<d(u_{0},u_{k},Q\cup R)$, which is a
+		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
+		\begin{equation}
+			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  \label{basic-eq-2}
+		\end{equation}
+
+		Consider the path $P^{\ast }=P\cup \{u_{i}u_{i-1}\}$. Assume that we start
+		traversing $P^{\ast }$ at time $t_{v_{1}}$. Then we arrive at $u_{i}$ at
+		time $x\Delta +g$, and we continue by traversing edge $u_{i}u_{i-1}$ at time 
+		$(x+1)\Delta +e$. That is, $d(u_{0},u_{i-1},P^{\ast })=(x+1)\Delta
+		+e-t_{v_{1}}+1$.
+
+		Now consider the path $Q^{\ast }=Q\setminus \{u_{i}u_{i-1}\}$. Let $h\in
+		\lbrack 1,\Delta ]$ be such that $A_{t_{u_{i}}}(u_{0},u_{i-1},Q^{\ast
+		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
+		at time $t_{u_{1}}$, we arrive at $u_{i-1}$ at time $x\Delta +e-h$, i.e. $%
+		d(u_{0},u_{i-1},Q^{\ast })=x\Delta +e-h-t_{u_{1}}+1$. Summarizing, we have:%
+		\begin{eqnarray*}
+			d(u_{0},u_{i-1},P^{\ast })-d(u_{0},u_{i-1},Q^{\ast }) &=&\Delta
+			+h-(t_{v_{1}}-t_{u_{1}}) \\
+			&\geq &(\Delta -\delta _{0})+h>0,
+		\end{eqnarray*}%
+		which proves the statement of the lemma.
+
+		\emph{Case 2: }$t_{v_{1}}=t_{u_{1}}$\emph{.} Then, it follows by (\ref%
+		{basic-eq-1}) that $%
+		A_{t_{u_{1}}}(u_{0},u_{i},P)=A_{t_{u_{1}}}(u_{0},u_{i},Q)-\delta _{0}\leq
+		A_{t_{u_{1}}}(u_{0},u_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
+		above, consider the paths $P^{\ast }=P\cup \{u_{i}u_{i-1}\}$ and $Q^{\ast
+		}=Q\setminus \{u_{i}u_{i-1}\}$. Assume that we start traversing $P^{\ast }$
+		at time $t_{v_{1}}=t_{u_{1}}$. Then we arrive at $u_{i}$ at time $x\Delta +g$%
+		, and we continue by traversing edge $u_{i}u_{i-1}$, either at time $%
+		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
+		case where $g\neq e$). That is, $d(u_{0},u_{i-1},P^{\ast })\geq x\Delta
+		+e-t_{u_{1}}+1$.
+
+		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
+		A_{t_{u_{i}}}(u_{0},u_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
+		traversing $Q^{\ast }$ at time $t_{u_{1}}$, we arrive at $u_{i-1}$ at time $%
+		x\Delta +e-h$, i.e. $d(u_{0},u_{i-1},Q^{\ast })=x\Delta +e-h-t_{u_{1}}+1$.
+		Summarizing, we have:%
+		\begin{equation*}
+			d(u_{0},u_{i-1},P^{\ast })-d(u_{0},u_{i-1},Q^{\ast })\geq h\geq 1,
+		\end{equation*}%
+		which proves the statement of the lemma.
+	\end{proof}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.6\linewidth]{conj-fig}
+		\caption{Figure of the conjecture.}
+		\label{conj-fig}
+	\end{figure}
+
+\end{proof}
+
 %Observe also the following.
+\todo[inline]{Check all of the above and correct it/make it pretty.}
 

### 2023-02-06 ICALP23-RealizingTemporalGraphs.tex
Changes from Monday 6th Feb

@@
 given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
-are the vertex degrees~\cite{}, distances~\cite{}, eccentricities~\cite{}, connectivity~\cite{}, etc. 
-The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{.....}.
+are the vertex degrees~\cite{cai2000solution,rfgh611961hu,hakimi1962realizability,barNoy2019graphRealizations,barNoy2021selected}, distances~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance}, eccentricities~\cite{barNoy2020efficiently,hell2009linear}, connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,erdos1960graphs}, etc.
+The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{augustine2022distributed}.
 
@@
 In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$.
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is $\Delta$ periodic temporal graph.
+When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a $\Delta$-periodic temporal graph.
 
@@
 	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
-	which implies that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
+	which states that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
 	then the shortest path from $u$ to $w$ is a subpath of $P$.
 	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
-	one can see that this property does not carry over.
-	For an example see~\cref{fig:ftpExample}.
+	one can see that this property does not carry over
+	(for an example see~\cref{fig:ftpExample}).
 	Which makes all the standard intuition and work with these kind of paths, much harder.
@@
 	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$ that is on a path $P_{u,v}$ is of duration $1$ and is not a subpath of $P_{u,v}$.		
+		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
 		\label{fig:ftpExample}}
@@
         \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n}$.
+        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
     \end{itemize}
@@
 
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[11n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n},v^i_i\}$. 
+    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
     %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
@@
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)-1$.
+    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
 \end{itemize}
@@
 %\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+2)(i-j-1)+2n+5$.
+%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
 %\end{itemize}
@@
 \begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+6n-1$.
+    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
 \end{itemize}
@@
 %\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+2)(j-i)-1$.
+%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
 %\end{itemize}
@@
 \begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+2)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+2)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+2)(i+j)+3$.
+    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
+    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
 \end{itemize}
@@
 \begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
 \end{claim}
@@
 Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+2)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+2)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+2)(i+j)$.
+Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
+
+    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
 Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
 However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+2)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+2)(i+j)+3$, a contradiction.
+    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
+Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
+However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
     Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
@@
 
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+2)(i+j)$.
+    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
 Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+2)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
+We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
+Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
 Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
@@
 \begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
+    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
 
@@
     By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+2)+8n+4$.
+It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
 We set $\sigma_{i,j}(\ell')=\ell$.
@@
 \begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
+    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
 \end{claim}
@@
     Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+2)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+8n+4$.
+It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
 Hence, the temporal path $P$ has duration at most $8n+3$.
@@
     For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{11n}\})\le n^9+2$.
+    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
 %
@@
 Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+2)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
+Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
 We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
@@
 Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$ until it reaches $v^i_1$.
+In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$ until it reaches $v^i_1$.
 More generally, we can make the following observation.
@@
     Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n$ vertices and no vertex of a connector gadget or the alignment gadget.
+Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
 Then $P$ cannot visit vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
@@
 From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n$ vertices.
+Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
 
     Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$.
+Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$.
 The claim follows.
@@
 \begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$.
+    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$.
 We analyse the former case first.
@@
 
-    In the latter case, where $P$ traverses a segment of the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
+    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
 \end{claimproof}
 
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+2)+6n-1$.
+Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
 By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
@@
 Let $X\subseteq \{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+2)+6n-1$, a contradiction.
+By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
 
@@
 Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+2)+6n-1$, a contradiction.
+However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
 
@@
 Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+1$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+1$.
+We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
+The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
 To do.
@@
 Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+1$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
+If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
 \end{claim}
 \begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+1$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'}\mid \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$.
+    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'}\mid \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$.
 By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
 By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+1$.
+If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
 \end{claimproof}
@@
 \begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+1$.
+    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
 \end{claim}
 \begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$.
+    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$.
 Assume $P$ follows this path.
 By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+1$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
+It follows that $P$ has duration at least $26n+5$.
+By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
 If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
@@
 \begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+1$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+1$.
+    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
+    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
     \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
@@
 %By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
+By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
 Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
 %By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+2)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
+By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
 We have that
@@
 %\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+2)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2) = \\
+& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
+& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
 %\]
 %\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 2
+& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
 %\]
@@
 \[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+2.
+\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
 \]
@@
 Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+1$.
+By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
 Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
 By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+1$ we get that 
+By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
 \[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+2.
+\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
 \]
@@
 \[
-(2i+1)\cdot (20n+2)+2\ell'''+2 -((2i-1)\cdot (20n+2)+2\ell'+2) = 46n+2,
+(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
 \]
@@
 
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution. We construct the following labelling for $G$.
+\subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
+We construct the following labelling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
 
@@
     \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+2)$.
+    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
+    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
 \end{itemize}
@@
 (Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
+\end{itemize}
+
+Recall that the following distance requirements were specified in the construction of the instance.
+It is straightforward to verify that distance requirements we recall in the following are all met, assuming no faster connections are introduced.
+\begin{itemize}
+    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
+    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
+    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
+    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
+\end{itemize}
+For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following distances.
+\begin{itemize}
+    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
+    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
+    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
+    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
+\end{itemize}
+
+ Next, consider the alignment gadget.
+Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
+Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
+Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
+\begin{itemize}
+    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
+    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
+\end{itemize}
+
+Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
+Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
+Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
+Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
+\begin{itemize}
+    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
+    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
+\end{itemize}
+Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
+
+We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
+Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
+
+Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
+To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
+Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
+Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
+We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
+For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
+
+Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
+\begin{itemize}
+    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
+\end{itemize}
+Note that using these labels, we obey the following distance constraints.
+\begin{itemize}
+    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
+\end{itemize}
+Furthermore, we set the following labels.
+\begin{itemize}
+    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
+    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
+    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
+\end{itemize}
+It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
+
+Finally, consider the validation gadget for color $i$. 
+For all $j\in[k]\setminus\{i\}$.
+Assume $j<i$, the case of $j>i$ is analogous.
+Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$.
+Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
+Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
+Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
+\begin{itemize}
+    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell-2$ for all $\ell''''$ such that this edge exists.
+    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell-10n-4$.
+    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell-2(5n-\ell'')$.
+    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell+6$ for all $\ell''''$ such that this edge exists.
+    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell+10n+8$.
+    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell+2(5n-\ell'')+6$.
+\end{itemize}
+
+For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
+\end{itemize}
+For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
 \end{itemize}
@@
 where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the first label of $P$ to be a constant $c_{uv}$.
-This gives us a unique label for each edge of $P$, that depends on the value $c_{uv}$.
+we set the label of the first edge of $P$ to be a constant form $[\Delta]$.
+This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
 \end{proof}
+
+\todo[inline]{George proved it. Added proof inside. Check if OK?\\}
 
@@
     such that the labeling $\lambda$ respects the values from $D$.
-    Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
+    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
 \end{lemma}
 
-\todo[inline]{George proved it. Added proof inside. Check if OK?\\
-Check the proof below and correct it/make it pretty.}
-
-\begin{proof}
-We denote with $v_i \in U$ a vertex of interest in $P \setminus \{u,v\}$.
-There are two options, either $v_i$ is reached from $u$ using the subpath $P_i = (u, v_2, v_3, \dots, v_i)$ of $P$,
-or there exists a fastest temporal path $P' = (u, w_2, w_3, \dots, w_{p'} = v_i)$, for which $P \cap P' = \{u, v_i\}$.
-If the temporal path from $u$ to $v_i$ is a subpath of $P$, then we determine the labeling of $P$ using \cref{lemma:FPT-uv-Labelalledges}.
-So we can suppose that the fastest temporal path from $u$ to $v_i$ is of form $P'$.
-
-In the following, we only consider \emph{wasteless} temporal paths. A temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ is \emph{wasteless}
-if, for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-	\begin{definition}
-		\label{arrival-duration-def}Let $u,v\in V$, and let $t\in 
-		%TCIMACRO{\U{2115} }%
-		%BeginExpansion
-		\mathbb{N}
-		%EndExpansion
-		$. Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-		the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$ is $%
-		A_{t}(u,v)$, and the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$
-		to $v$ is $A_{t}(u,v,P)$.
-	\end{definition}
-
-	Whenever $t=1$, we may omit the index $t$, i.e. we may write $%
-	A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$. The following refers to
-	Figure~\ref{conj-fig}.
-
-	Initial assumptions:
-
+For the proof of the above lemma, we first prove a weaker statement,
+for which we need to introduce some extra definitions and fix some notations.
+%
+In the following
+we only consider \emph{wasteless} temporal paths. 
+We call 
+a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
+if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
+
+Let $u,v\in V$, and let $t\in \mathbb{N}$. 
+Given that a temporal path starts within the period $[t,t+\Delta -1]$,
+we denote with $A_{t}(u,v)$
+the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
+with $A_{t}(u,v,P)$,
+the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
+%
+Whenever $t=1$, we may omit the index $t$, i.e. we may write 
+$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
+
+Suppose now that 
+we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
+Let $v_i \neq u,v$ be a vertex of interest on the path $P_{u,v}$.
+Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
+We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
+(for details see~\cref{fig:FPT-uv-Labelalledges}).
+
+From the above we get the following assumptions:
 	\begin{enumerate}
-		\item $d(u_{0},u_{i})=d(u_{0},u_{i},P)\leq d(u_{0},u_{i},Q)$; denote $\delta
-		_{0}=d(u_{0},u_{i},Q)-d(u_{0},u_{i})\geq 0$.
-
-		\item $d(u_{0},u_{k})=d(u_{0},u_{k},Q\cup R)\leq d(u_{0},u_{k},P\cup R)$.
+		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
+		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
 	\end{enumerate}
-
-	General properties:
-
+In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
+It follows that:
 	\begin{itemize}
@@
 
-	\bigskip
-
-	Let $t_{u_{1}}\in \lbrack 1,\Delta ]$ be the label of the edge $u_{0}u_{1}$,
-	and denote by $t_{v_{1}}$ the appearance of the edge $u_{0}v_{1}$ within the
-	period $[t_{u_{1}},t_{u_{1}}+\Delta -1]$. Note that $1\leq t_{u_{1}}\leq
-	\Delta $ and that $t_{u_{1}}\leq t_{v_{1}}\leq 2\Delta $. By the first
-	initial assumption, we have:
-
+ Let $t_{v_2}\in \lbrack 1,\Delta ]$ be the label of the edge $uv_2$,
+	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
+	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
+	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
+    From the assumption~\ref{assumption1-FPT} we get :
 	\begin{equation*}
 		\delta
-		_{0}=d(u_{0},u_{i},Q)-d(u_{0},u_{i})=A_{t_{u_{1}}}(u_{0},u_{i},Q)-A_{t_{u_{1}}}(u_{0},u_{i},P)+\left( t_{v_{1}}-t_{u_{1}}\right)
+		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
 	\end{equation*}%
@@
 	\begin{equation}
-		A_{t_{u_{1}}}(u_{0},u_{i},P)-A_{t_{u_{1}}}(u_{0},u_{i},Q)=t_{v_{1}}-(t_{u_{1}}+\delta _{0})
+		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
 		\label{basic-eq-1}
@@
 
+\begin{figure}[h]
+	\centering
+	\begin{tikzpicture}[scale=.85]
+		%%%S_uv
+		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
+		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
+		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
+		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
+		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
+		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
+		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
+
+		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
+
+		\draw (v1) to [out=80,in=100,distance=3cm]
+		node[pos=0.1,label={left:$t_{u_2}$}] {}
+		node[vert,pos=0.15,label=above:$u_2$] {}
+		node[vert,pos=0.3,label=above:$u_3$] {}
+		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
+		node[pos=0.9,label={right:$g$}] {} (vi);
+
+		%\draw[transform canvas={yshift=0mm}, blue]
+		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
+
+		%\draw[red]
+		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
+	\end{tikzpicture}
+	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
+		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
+		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
+		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
+		\label{fig:FPT-uv-Labelalledges}}
+\end{figure}
+
+We use all of the above discussion, to prove the following lemma.
  	\begin{lemma}
-		\label{lem-1}If $t_{v_{1}}\neq t_{u_{1}}$ then $\delta _{0}\leq \Delta -2$
-		and $t_{v_{1}}\geq t_{u_{1}}+\delta _{0}+1$.
+		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$ then $\delta _{0}\leq \Delta -2$
+		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
 	\end{lemma}
@@
 		{basic-eq-1}) that $%
-		A_{t_{u_{1}}}(u_{0},u_{i},P)-A_{t_{u_{1}}}(u_{0},u_{i},Q)\leq
-		t_{v_{1}}-t_{u_{1}}-\Delta +1\leq 0$, and thus $A_{t_{u_{1}}}(u_{0},u_{i},P)%
-		\leq A_{t_{u_{1}}}(u_{0},u_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u_{0}$ to $u_{i}$ by departing at time $t_{v_{1}}\geq t_{u_{1}}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u_{0},u_{k},P\cup Q)<d(u_{0},u_{k},Q\cup R)$, which is a contradiction to the
+		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
+		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
+		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
+		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
+		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
 		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
 
-		Now assume that $t_{u_{1}}+1\leq t_{v_{1}}\leq t_{u_{1}}+\delta _{0}$. Then,
-		it follows by (\ref{basic-eq-1}) that $A_{t_{u_{1}}}(u_{0},u_{i},P)\leq
-		A_{t_{u_{1}}}(u_{0},u_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{v_{1}}\geq t_{u_{1}}+\delta _{0}+1$.
+		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
+		it follows by (\ref{basic-eq-1}) that $A_{t_{v_2}}(u,v_{i},P)\leq
+		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
+		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
 	\end{proof}
 
-	\medskip
-
  The next corollary follows immediately from Lemma \ref{lem-1}.
@@
 	\begin{corollary}
-		\label{cor-1}If $t_{v_{1}}\neq t_{u_{1}}$ then $1\leq
-		A_{t_{u_{1}}}(u_{0},u_{i},P)-A_{t_{u_{1}}}(u_{0},u_{i},Q)\leq \Delta
+		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$ then $1\leq
+		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
 		-1-\delta _{0}$.
@@
 
-	\begin{lemma}
-		\label{lem-2}$d(u_{0},u_{i-1},P\cup \{u_{i}u_{i-1}\})>d(u_{0},u_{i-1},Q\setminus
-		\{u_{i}u_{i-1}\})$.
+	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
+		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
+		\{v_{i}v_{i-1}\})$.
 	\end{lemma}
-
+We are now ready to prove the follwing result.
 	\begin{proof}
-		Let $e\in \lbrack 1,\Delta ]$ be the label of the edge $u_{i-1}u_{i}$, and
+		Let $e\in \lbrack 1,\Delta ]$ be the label of the edge $v_{i-1}v_{i}$, and
 		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $u_{i}u_{i+1}$ after time $e$. Let $A_{t_{u_{i}}}(u_{0},u_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{u_{i}}}(u_{0},u_{i+1},Q\cup\{u_{i}u_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{u_{i}}}(u_{0},u_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{v_{1}}\neq t_{u_{1}}$\emph{.} Then Corollary \ref{cor-1}
+		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
+		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
+		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
+
+		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$\emph{.} Then Corollary \ref{cor-1}
 		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u_{0}$ to $u_{i}$ by departing at time $%
-		t_{v_{1}}\geq t_{u_{1}}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u_{0},u_{k},P\cup R)<d(u_{0},u_{k},Q\cup R)$, which is a
+		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
+		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
+		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
 		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
@@
 
-		Consider the path $P^{\ast }=P\cup \{u_{i}u_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{v_{1}}$. Then we arrive at $u_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $u_{i}u_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u_{0},u_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{v_{1}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{u_{i}u_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{u_{i}}}(u_{0},u_{i-1},Q^{\ast
+		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
+		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
+		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
+		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
+		+e-t_{u_{2}}+1$.
+
+		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
+		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
 		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{u_{1}}$, we arrive at $u_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u_{0},u_{i-1},Q^{\ast })=x\Delta +e-h-t_{u_{1}}+1$. Summarizing, we have:%
+		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
+		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
 		\begin{eqnarray*}
-			d(u_{0},u_{i-1},P^{\ast })-d(u_{0},u_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{v_{1}}-t_{u_{1}}) \\
+			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
+			+h-(t_{u_{2}}-t_{v_2}) \\
 			&\geq &(\Delta -\delta _{0})+h>0,
@@
 
-		\emph{Case 2: }$t_{v_{1}}=t_{u_{1}}$\emph{.} Then, it follows by (\ref%
+		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$\emph{.} Then, it follows by (\ref%
 		{basic-eq-1}) that $%
-		A_{t_{u_{1}}}(u_{0},u_{i},P)=A_{t_{u_{1}}}(u_{0},u_{i},Q)-\delta _{0}\leq
-		A_{t_{u_{1}}}(u_{0},u_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{u_{i}u_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{u_{i}u_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{v_{1}}=t_{u_{1}}$. Then we arrive at $u_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $u_{i}u_{i-1}$, either at time $%
+		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
+		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
+		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
+		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
+		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
+		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
 		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u_{0},u_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{u_{1}}+1$.
+		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
+		+e-t_{v_2}+1$.
 
 		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{u_{i}}}(u_{0},u_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{u_{1}}$, we arrive at $u_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u_{0},u_{i-1},Q^{\ast })=x\Delta +e-h-t_{u_{1}}+1$.
+		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
+		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
+		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
 		Summarizing, we have:%
 		\begin{equation*}
-			d(u_{0},u_{i-1},P^{\ast })-d(u_{0},u_{i-1},Q^{\ast })\geq h\geq 1,
+			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
 		\end{equation*}%
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.6\linewidth]{conj-fig}
-		\caption{Figure of the conjecture.}
-		\label{conj-fig}
-	\end{figure}
-
+ From the above it follows that if $P$ is a fastest path from $u$ to $v$,
+ then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
+ are reached using the same path $P$.
+ We use this fact in the following proof.
+
+\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
+For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
+we have two options.
+First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
+a subpath of $P$.
+In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
+Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
+not a subpath of $P$. 
+In this case we know exactly how to label all of the edges of $P$,
+with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
 \end{proof}
@@
 %Observe also the following.
-\todo[inline]{Check all of the above and correct it/make it pretty.}
+\todo[inline]{Check all of the above and correct it}
 

### 2023-02-07 ICALP23-RealizingTemporalGraphs.tex
Tuesday 7th February

@@
 given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
-are the vertex degrees~\cite{cai2000solution,rfgh611961hu,hakimi1962realizability,barNoy2019graphRealizations,barNoy2021selected}, distances~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance}, eccentricities~\cite{barNoy2020efficiently,hell2009linear}, connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,erdos1960graphs}, etc.
-The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{augustine2022distributed}.
+are the vertex degrees~\cite{cai2000solution,rfgh611961hu,hakimi1962realizability,barNoy2019graphRealizations,barNoy2021selected,erdos1960graphs}, distances~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance}, eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, etc.
+The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{augustine2022distributed,grotschel1995design}.
 
@@
 \end{itemize}
+
+Sections for ICALP:
+\begin{enumerate}
+    \item Intro 2 PAGES (GEORGE + PAUL)
+    \item Prelims 1 PAGE
+    \item Hardness (HENDRIK SHORTENS)
+    \begin{enumerate}
+        \item NP 1/2 PAGE (APPENDIX)
+        \item W1 (3 PAGES)
+    \end{enumerate}
+    \item Algos (NINA SHORTENS)
+    \begin{enumerate}
+        \item Tree ALGO 2 PAGE
+        \item FPT ALGO (6 PAGES)
+        \item Cylce ALGO (APPENDIX)
+    \end{enumerate}
+    \item Conclusion (?) 1/2 PAGE
+\end{enumerate}
+
+\section{Motivation}
+
+	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
+	which states that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
+	then the shortest path from $u$ to $w$ is a subpath of $P$.
+	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
+	one can see that this property does not carry over
+	(for an example see~\cref{fig:ftpExample}).
+	Which makes all the standard intuition and work with these kind of paths, much harder.
+    This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
+    where one first determines $O(k)$ special vertices,
+    guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
+    An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
+    In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
+    that could at the end be extended to the whole $G$.
+
+	\begin{figure}[htb]
+    \centering
+	\begin{tikzpicture}[xscale=2]
+	%%%S_uv
+	\node[vert,label=below:$u$] (v1) at (1,0) {};
+	\node[vert] (v2) at (2,0) {};
+	\node[vert,label=below:$w$] (v3) at (3,0) {};
+	\node[vert] (v4) at (4,0) {};
+	\node[vert,label=below:$v$] (v5) at (5,0) {};
+	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
+	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
+
+	\draw[transform canvas={yshift=-1.5mm}, blue]
+	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
+
+	\draw[red]
+	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
+\end{tikzpicture}
+	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
+		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
+		\label{fig:ftpExample}}
+	\end{figure}
 
@@
 
-\section{Motivation}
-
-	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
-	which states that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the shortest path from $u$ to $w$ is a subpath of $P$.
-	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
-	one can see that this property does not carry over
-	(for an example see~\cref{fig:ftpExample}).
-	Which makes all the standard intuition and work with these kind of paths, much harder.
-
-	\begin{figure}[htb]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
 %\section{Results}
@@
 
-In this section we study the hardness of \deltaExact. We first start with defining certain notions, that will be of use when solving the problem.
+In this section 
+we show that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree or a cycle,
+we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
+We first start with defining certain notions, that will be of use when solving the problem.
 
@@
 \end{proof}
-
+All of the above is used in the design of the following polynomial-time algorithms.
 \subsection{ \deltaExact\ is polynomial-time solvable on trees and paths}
-
+%
 Let $D$ be a matrix from \deltaExact, when the underlying graph $G$ of $D$ is a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
@@
 Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself. This corresponds with all diagonal entries of $D$ being $0$.
+By the definition, each vertex is on distance, and therefore also duration $0$ from itself. This corresponds with all diagonal entries of $D$ being $0$.
 Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
@@
     Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum distance from every vertex $v_j \in C_n \setminus \{v_i\}$.
+    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
     It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
@@
 
-\section{\deltaExact\ is NP-hard}
+\section{Hardness Results}  
+\subsection{\deltaExact\ is NP-hard}
+In this section we prove that it is NP-hard to determine the $\Delta$-periodic temporal graph $(G,\lambda)$,
+for a general instance $(D, \Delta)$ of \deltaExact\,
+where $\Delta \geq 3$.
 
 \begin{theorem}
-	\deltaExactLong\ is \NP-hard.
+	\deltaExactLong\ is \NP-hard for a general $(D,\Delta)$, where $\Delta \geq 3$.
 \end{theorem}
@@
 %
-Now we specify the distances in the matrix $D^\phi$ between all vertex pairs.
+Now we specify the durations in the matrix $D^\phi$ between all vertex pairs.
 For the sake of simplicity we write $D^\phi _{u,v}$ as $d(u,v)$,
@@
     \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following distances:
+    we specify the following durations:
     $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
     \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following distances:
+    we specify the following durations:
     $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following distances:
+    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
     $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following distances:
+    If $x_i$ appears non-negated in $c$ we specify the following durations:
     $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following distances:
+    If $x_i$ appears negated in $c$ we specify the following duratios:
     $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
+    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
     $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
@@
     $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following distances:
+    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
     $d(x_i,x_j)=2\Delta +1$ and
     $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following distances:
+    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
     $d(c_i,c_j)= \Delta + 1$.
@@
 For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all distances are realized.
+We now verify that all duratios are realized.
 \begin{itemize}
@@
 \end{itemize}
-%
+Lastly, observe that $\Delta$ has to be greater or equal to $3$, as the above constructed labeling $\lambda$ uses values from $\{1,2,3\}$.
 \end{proof}
 
-\section{W[1]-hardness}
+\subsection{W[1]-hardness}
 \begin{theorem}\label{thm:W1wrtFVS}
@@
 We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for finite $\Delta$ and a distance matrix $D$ that only has integer entries.
+At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
 
     Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to an edge connecting the two vertices.
+To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
 Afterwards, we describe the remaining entries of $D$.
@@
 
-    \subparagraph{Edge Selection Gadget.} We first introduce an \emph{edge selection gadget for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
+    \subparagraph{Edge Selection Gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
     \begin{itemize}
@@
     Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the distance matrix $D$ later.
+    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
 Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
@@
 
-\subparagraph{Distance Matrix.} We proceed with describing the distance matrix $D$.
+\subparagraph{Matrix $D$.} We proceed with describing the matrix $D$, of durations of fastest paths.
 For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
@@
 Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following distances.
+We set the following durations.
 Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
@@
 
-All distances between non-adjacent vertex pairs that are not specified above are set to infinity.
+All durations between non-adjacent vertex pairs that are not specified above are set to infinity.
 
@@
 	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+4n+4$} (VSS);
+	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
 	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
@@
     }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labelling.
-Edges incident with vertices of connector gadgets are omitted.
-Gray vertices form a feedback vertex set.}\label{fig:hardness1}
+    \caption{Illustration of part of the underlying graph $G$ and a possible labelling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
+    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
+    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
+    consist of $5n$ vertices $a_1^{i,j,3},a_2^{i,j,3},\dots,a_{5n}^{i,j,3}$ 
+    and $b_1^{i,j,3},b_2^{i,j,3},\dots,b_{5n}^{i,j,3}$, respectively.
+    }\label{fig:hardness1}
 \end{figure}
@@
 This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
+    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
+However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
 It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
@@
 
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
+    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
 By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
@@
 Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}$ to a vertex in $X_{i,j}$ have distinct labels.
+However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
 Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n}\mid \ell''\in[m]\}$ as its second last vertex.
@@
 
-Before we proceed, we show some further properties of $\lambda$. First, we have a closer look at the labels on edges of the edge selection gadgets.
+Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges, of the edge selection gadgets.
 
@@
 Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ is verification gadgets.
+Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
 Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
@@
    Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ have distance (according to $D$) three and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
+Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
     It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
@@
 Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ have distance $3$.
+It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
 In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
@@
 Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ determined, all labels of edges traversed by $P$ are also determined and the claim follows.
+Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
     \end{claimproof}
@@
 \begin{claimproof}
-    Let $w\in \hat{E}$ denote the neighbor of $y^i$ in the alignment gadget.
+    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
 Note that we have $d(w^\star,y^i)=n^8-1$.
@@
     \end{itemize}
-    Furthermore, by construction of $G$, we have that the distance of $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
+    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
 
@@
     Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ have distance (according to $D$) three.
+It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
 It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
@@
 The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''}\mid \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the distance between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
+By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
 Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
@@
 The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-To do.
 
@@
 
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest path temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
+From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
 \begin{enumerate}
@@
 
-Recall that the following distance requirements were specified in the construction of the instance.
-It is straightforward to verify that distance requirements we recall in the following are all met, assuming no faster connections are introduced.
+Recall that the following duration requirements were specified in the construction of the instance.
+It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
 \begin{itemize}
@@
 \end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following distances.
+For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
 \begin{itemize}
@@
 \end{itemize}
-Note that using these labels, we obey the following distance constraints.
+Note that using these labels, we obey the following duration constraints.
 \begin{itemize}
@@
 Finally, consider the validation gadget for color $i$. 
-For all $j\in[k]\setminus\{i\}$.
-Assume $j<i$, the case of $j>i$ is analogous.
+%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
+Let $1\le j<i$. 
 Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
 Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
+Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
 Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
 \begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell-2$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell-10n-4$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell-2(5n-\ell'')$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell+6$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell+10n+8$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell+2(5n-\ell'')+6$.
-\end{itemize}
-
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
+    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
+    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
+    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
+    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
+    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
+    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
+\end{itemize}
+For all $\ell''\in[13n]$ we set the following.
+\begin{itemize}
+    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
+    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
+    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
+\end{itemize}
+Let $i<j\le k$. 
+Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
+Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
+Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
+Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
+\begin{itemize}
+    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
+    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
+    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
+    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
+    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
+    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
+\end{itemize}
+
+Now we verify that we meet the duration requirements.
+For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
 \begin{itemize}
@@
 \end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
+To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
+Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
+Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
+From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$ to arrive at $v^i_j$.
+By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
+To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
+By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
+The case where $i\le j<j'\le k$ is analogous.
+
+For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
 \begin{itemize}
@@
 \end{itemize}
+Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
+Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''}\mid \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
+By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
+
+This finishes the proof.
 
@@
 Let $V$ denote the set of all remaining vertices.
-We set the following distances.
+We set the following durations.
 \begin{itemize}
@@
     \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the distance from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
+    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
 \end{itemize}
@@
 For an illustration see \cref{fig:hardness2}.
-It is easy to check that all distances requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all distance requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
+It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
 Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
@@
 
-\section{FPT}
+\section{\deltaExact\ is FPT}
+In this section we present an FPT algorithm for \deltaExact\ parameterized it by the feedback edge number of the underlying graph.
 In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
@@
 \begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is FPT parameterized by the feedback edge number.
+    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
 \end{theorem}
@@
 
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possible solutions.
+\todo[inline]{HM: not sure if the discussion below is necessary.
+i think guessing is a pretty established term in algorithm design.
+also, i think the name comes from the idea of using non-determinism.}
+Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
 For example, let $u$ and $v$ be two vertices in a graph $G$. 
@@
 
-Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-Therefore, we approach the problem using some special properties, which allow us to create $f(k)$ different guesses (where $f$ is a double exponential function in the feedback edge number $k$).
+%%%%% HM: the two sentences below seem trivial to me.
+%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
+%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
+We approach the problem using some special properties, which allow us to create $f(k)$ different guesses (where $f$ will be a double exponential function in the feedback edge number $k$).
 We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-The ILP instance is a \textsc{Yes} instance if and only if $D$ is a \textsc{Yes} instance of \deltaExact.
+If the ILP instance is a \textsc{Yes} instance then we can will show that also $D$ is a \textsc{Yes} instance of \deltaExact.
 Moreover, from a positive solution of the ILP instance we can construct the desired labeling $\lambda$.
-Using results from \cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
+If all constructed ILP instances are \textsc{No} instances, then we will show that $D$ is a \textsc{No} instance of \deltaExact.
+Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
 Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
 
-We now introduce the algorithm, that determines the labeling of $G$, satisfying $D$, and runs in $f(k) \cdot \text{poly}(n)$ time.
+We now introduce the algorithm, that determines a labeling of $G$ satisfying $D$, or determines that no such labeling exists, and that runs in $f(k) \cdot \text{poly}(n)$ time.
 Our algorithm performs the following steps.
@@
 and denote with 
-$$
+\[
 Z = V(G) \setminus V(G').
-$$
-Then we determine a minimum feedback edge set $F$ of $G'$ by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of the whole $G$.
+\]
+Then we determine a minimum feedback edge set $F$ of $G'$.
+%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
+Note that $F$ is also a minimum feedback edge set of $G$.
 Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
@@
 We denote with 
-$$U = V_1 \cup V_2 \cup V_3$$
+\[U = V_1 \cup V_2 \cup V_3\]
 the set of vertices of interest. It follows that $|U| \leq 4k$.
 We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-$$U^* = \{v \in V(G') \setminus U | u \in U, v \in N(u)\}.$$
+\[U^* = \{v \in V(G') \setminus U \mid u \in U, v \in N(u)\}.\]
 Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
@@
 where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-$$
+\[
 Z^* = \{ r_i | r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-$$
+\]
 Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U, U^*$ and $Z^*$ takes linear time.
-
-Let us remember the following basic property of the problem \deltaExact.
-A labeling $\lambda$ of $G$ satisfies $D$ if every fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$,
-and none other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases,
-where the first vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the last vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ of the fastest temporal path from the vertex $v_i$ to $v_j$, 
+Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
+
+%Let us remember the following basic property of the problem \deltaExact.
+Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
+%, and no other temporal path from $v_i$ to $v_j$ is faster.
+In order to find a labeling that satisfies this property we split our analysis in nine cases.
+We consider fastest temporal paths 
+where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
+and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
+In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
 which results in one equality constraint for the labels on the path $P$. 
 For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. We have to guarantee only, that the number of guesses, of faster temporal paths, is exponential in $k$ and not in $n$.
+This results in producing $poly(n,m)$ constraints. 
+Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
+%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
 
@@
 We start the algorithm by guessing necessary structures.
-Note, whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of the fastest temporal path among those two vertices.
+Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
 In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,
-if the path among two vertices is not uniquely determined, we denote it by $\leadsto$.
+Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
+if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
 We guess the following structures.
@@
     In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length $4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
+    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
     Let 
@@
     Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ oz $z$.
+    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
     Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
@@
 In this section we study the properties of our problem, that then help us creating constraints of our ILP.
-Remember, with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and start adding certain values to them.
-Note, these values are not (necessarily) numbers. 
-In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
+Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
+We start with an empty labeling of edges and start specifying the labels of edges.
+Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels. 
+%In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
 In our analysis we exploit the following greatly, that is why we state is as an observation.
@@
 The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-Since the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
+This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
 where the label of last edge is considered with some delta periods,
@@
 
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$, from a vertex of interest $u$ to a vertex of interest $v$,
+In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
 results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
 (with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges,
-and if $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges.
+More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
+If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
 For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
@@
 We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$.
+To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
 Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
@@
 where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant form $[\Delta]$.
+we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
 This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
@@
 \todo[inline]{George proved it. Added proof inside. Check if OK?\\}
+
+\todo[inline]{HM: the last sentence in \cref{lemma:FPT-uv-LabelAlmostalledges} is strange. it doesn't say anything. either give the specific restrictions or remove it.}
 
@@
     is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
+    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
     We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
@@
 we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i \neq u,v$ be a vertex of interest on the path $P_{u,v}$.
+Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
 Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
@@
 (for details see~\cref{fig:FPT-uv-Labelalledges}).
+
+\todo[inline]{HM: check whether we introduced the notation $d(u,v,P)$.}
 
@@
 In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-It follows that:
-	\begin{itemize}
-		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-		u$ to $v$.
-	\end{itemize}
-
- Let $t_{v_2}\in \lbrack 1,\Delta ]$ be the label of the edge $uv_2$,
+%%%%%% HM: the following is never used..
+%It follows that:
+%	\begin{itemize}
+%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
+%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
+%		u$ to $v$.
+%	\end{itemize}
+%
+ Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
 	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
@@
 	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From the assumption~\ref{assumption1-FPT} we get :
+    From Assumption~\ref{assumption1-FPT} we get
 	\begin{equation*}
@@
 
-\begin{figure}[h]
+\begin{figure}[htb]
 	\centering
@@
  	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$ then $\delta _{0}\leq \Delta -2$
+		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
 		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
@@
 	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by (\ref%
-		{basic-eq-1}) that $%
+		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
+		{basic-eq-1} that $%
 		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
@@
 		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by (\ref{basic-eq-1}) that $A_{t_{v_2}}(u,v_{i},P)\leq
+		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
 		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
@@
 
- The next corollary follows immediately from Lemma \ref{lem-1}.
+ The next corollary follows immediately from \cref{lem-1}.
 
 	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$ then $1\leq
+		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
 		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
@@
 	\end{corollary}
+
+We are now ready to prove the following result.
 
@@
 	\end{lemma}
-We are now ready to prove the follwing result.
 	\begin{proof}
-		Let $e\in \lbrack 1,\Delta ]$ be the label of the edge $v_{i-1}v_{i}$, and
+		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
 		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
@@
 
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$\emph{.} Then Corollary \ref{cor-1}
+		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
 		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
@@
 		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  \label{basic-eq-2}
-		\end{equation}
+		\begin{equation*}
+			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
+		\end{equation*}
 
@@
 
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$\emph{.} Then, it follows by (\ref%
+		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
 		{basic-eq-1}) that $%
@@
 %Observe also the following.
-\todo[inline]{Check all of the above and correct it}
+\todo[inline]{Check all of the above and correct it   HM: i checked it and didnt find any issues.}
 
@@
     travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or $z,v$.
+    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
 \end{lemma}
@@
     Let us observe the following possibilities.
-    \\
+
     First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
@@
     the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-    \\
+
     Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
@@
     therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-    \\
+
     Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
@@
     For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case, when $S_{u,v}$ is longer easily follows from presented results.
+    The case where $S_{u,v}$ is longer easily follows from presented results.
 
     Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first when $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second when  $f = v_3v_4$.
+    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
+    and the second that  $f = v_3v_4$.
     Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
@@
 
-    Case 1,  $f = v_2v_3$.
+    \emph{Case 1: }$f = v_2v_3$.
     Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
@@
 
-    Case 2,  $f = v_3v_4$.
+    \emph{Case 2: }$f = v_3v_4$.
     Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
@@
     Again we get the following.
-    \begin{equation}
+    \begin{equation*}
     \begin{split}
@@
     \end{split}
-    \end{equation}
+    \end{equation*}
     The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.\\
+    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
+
     Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
@@
 \subsection{Adding constraints and variables to the ILP}
-First case we observe is the case when we want to determine the labels on fastest temporal paths among vertices of interest.
+We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
 We proceed in the following way.
@@
 In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-\todo{Change/explain what ``with respect to first label'' means}
 %In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
@@
     Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the distance from $v_i$ is the biggest 
+    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
     (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
@@
 Therefore we easily calculate the desired labels for all remaining edges.
-At the end we have a labeling $\lambda$ of $G$, that preserves all the distances from $D$.
+At the end we have a labeling $\lambda$ of $G$, that preserves all the durations from $D$.
 This follow from the fact that ILP consisted of constraints for all temporal paths,

### 2023-02-07 ICALP23-RealizingTemporalGraphs.tex
Changes to last section - ILP solution

@@
 
+Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
+
 SKELETON:
@@
 In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$.
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a $\Delta$-periodic temporal graph.
+When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
 
@@
 where $P=(u_0,u_1,\ldots,u_k)$ is a path in the underlying static graph $G$ (we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(u_{i-1}u_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
+$t_i\in \lambda_\Delta(u_{i-1}u_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
 The \emph{duration} of this temporal path $(P,\lambda)$ from $u$ to $v$ is $d(P,\lambda)=t_k - t_1 + 1$.
@@
 Let $P$ be a path from $u$ to $v$ in $G$. 
-We denote with $d(P,u,v)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(P,u,v) \geq d(u,v)$.
+We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
 
@@
 as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda)$ is a temporal path with the underlyg path $P$.
+where we actually mean that $(P,\lambda)$ is a temporal path with the underlying path $P$.
+
+In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
+that runs in polynomial-time.
+Using their algorithm, given a temporal graph $(G,\lambda)$, one can determine the whole matrix $D$ in polynomial-time,
+where $D$ consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda)$.
 
 \begin{comment}
-\begin{definition}[$D$-increasing temporal path]
-Let $(G,\lambda,\Delta)$ be a $\Delta$-periodic temporal graph on $n$ vertices, and let $D$ be an $n\times n $ matrix of positive integers. 
-Let $P$ be a temporal path from $u_0$ to $u_k$ on the vertices $u_0,u_1,\ldots,u_k$, and let $P^\textsc{ST}=(u_0,u_1,\ldots,u_k)$ be the underlying \emph{static} path in $G$.
-Then $P$ is \emph{$D$-increasing} in $G$ if $0=D_{u_0,u_0}<D_{u_0,u_1}<D_{u_0,u_2}< \ldots < D_{u_0,u_k}$.
-\end{definition}
-\end{comment}
-
 Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
@@
 Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-
+\end{comment}
 %\section{Results}
@@
     \begin{definition}[Travel delays]
-    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact.
+    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of \deltaExact.
     Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
@@
 
-\subparagraph{Matrix $D$.} We proceed with describing the matrix $D$, of durations of fastest paths.
+\subparagraph{\boldmath Duration Matrix $D$.} We proceed with describing the matrix $D$, of durations of fastest paths.
 For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
@@
 Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$, 
-which we prove later on (see~\cref{obs:FPT-k2segments}).
+Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following.
+\begin{corollary}\label{obs:FPT-k2segments}
+    There are at most $O(k^2)$ segments in $G'$.
+\end{corollary}
+In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
+%, which we prove later on (see~\cref{obs:FPT-k2segments}).
 %For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
@@
     Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
+    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
     Moreover suppose also that $P$ is a segment.
@@
 
-\todo[inline]{HM: the last sentence in \cref{lemma:FPT-uv-LabelAlmostalledges} is strange. it doesn't say anything. either give the specific restrictions or remove it.}
+%\todo[inline]{HM: the last sentence in \cref{lemma:FPT-uv-LabelAlmostalledges} is strange. it doesn't say anything. either give the specific restrictions or remove it.}
 
@@
     Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
+    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
     Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
@@
     such that the labeling $\lambda$ respects the values from $D$.
-    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
+%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
 \end{lemma}
@@
 (for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-\todo[inline]{HM: check whether we introduced the notation $d(u,v,P)$.}
 
@@
 Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
+If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
 %Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
 In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-%In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
-%Since there are $\ell - 1$ edge labels that are not determined with respect to the label of the first edge, may be some  TODO from above??
-
-After finishing the previous step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
-Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{not yet determined} edges.
+We call these $\ell - 1$ edges, \emph{partially determined} edges.
+After repeating this step for all pairs of vertices in $U$,
+the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
+or are partially determined.
 If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
+All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
+are called the \emph{not yet determined} edges.
 Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-Let us first observe some properties of such edges.
-
-\begin{lemma}
-    Not yet determined edges form disjoint segments in $G'$, where each segment starts and ends in some vertex of interest, 
-    \ie for every not yet determined path $P$ there exist $u,v \in U$, such that $P = (u, v_1, v_2, \dots, v_p=v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_{p-1} \in V(G') \setminus U$.
-\end{lemma}
-\begin{proof}
-    We prove this claim in two steps.
-    First we prove that all inner vertices of $P$, \ie vertices $v_i \in  S \setminus \{u,v\}$ are of degree exactly $2$ and are not vertices of interest. 
-    They are of degree at least $2$ since they are on a path $P$ and are incident to two not yet determined edges in  $P$.
-    They are of degree at most $2$ as if they were of a higher degree they would be vertices of interest and in this case we could split $P$ into shorter segments (subpaths).
-
-    Second, suppose that $P$ does not start in a vertex of interest, therefore $u \notin U$.
-As $u$ is the starting vertex of the not yet determined path $P$, there must exist a vertex of interest $u'$ such that a path between $u$ and $u'$ is labeled.
-    Since $u$ is not a vertex of interest, the only reason to label edges between $u'$ and $u$ would be if they were a part of some fastest temporal path among two vertices of interest and $u$ would be an inner vertex on that path.
-    Therefore $u$ would have to be incident to two labeled edges (that are part of some fastest temporal path) and one not yet determined edge, but in this case the degree of $u$ would be at least $3$ and therefore $u$ would be a vertex of interest.
-
-    From all of the above, it follows that $P$ is a not yet determined segment in $G'$.
-\end{proof}
-
-\begin{lemma}
-    After determining the labels of fastest temporal paths between all pairs of vertices of interest,
-    there can be at most one not yet determined segment among each pair of them.
-    %among any pair of vertices of interest $u,v \in U$ there can be at most one undetermined segment $S = (u, v_1, v_2, \dots, v_p, v)$, where $p \geq 0$ and $v_1,v_2,\dots,v_p \in V(G') \setminus U$.
-\end{lemma}
-\begin{proof}
-   Suppose for the contradiction that after determining the labels of all fastest temporal paths between vertices of interest,
-   there are two not yet determined segments among $u,v \in U$.
-   Denote them with $S_{u,v}$ and $S'_{u,v}$. 
-   Then $C = S_{u,v} \cup S_{u,v}'$ forms a cycle in $G'$. Since $G'$ admits no loops, the cycle $C$ is of length at least $3$.
-   Since $C$ is a cycle, at least one of its edges $e \in E(C)$ has to be in the feedback edge set $F$, and therefore, by the definition of vertices of interest $U$, 
-   both endpoints of $e$ have to be in $U$.
-   If $e = uv$ then there are only two vertices of interest in $C$, but the label of edge $e$ is determined.
-   And if $e \neq uv$ then there are at least $3$ vertices of interest in $C$.
-   So $S_{u,v}$ and $S_{u,v}'$ cannot be both fully not yet determined.
-\end{proof}
-From the above it follows that
-after we finish determining the labels for all fastest temporal paths among vertices of interest,
-there is at most one fully determined segment among two vertices of interest and at most one undetermined segment.
-Therefore the following holds.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
 
@@
 when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g. assume that we have guessed that the fastest path from $v_i$ to $z_j$
+W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
 passes through $w$ and $z_{j-1}$.
@@
 we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if, this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
+if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
 %
@@
 Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess
+At the end we create our final guess.
 \begin{enumerate}[G-1.]
@@
 First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~non-fastest) temporal paths among them.
+We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
 
@@
 
-\subsubsection*{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$}
+\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
 First we consider the case when $u,v$ are two vertices of interest.
@@
 
-\subsubsection*{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$}
+\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
 Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
@@
 
-\subsubsection*{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$}
+\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
 Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
@@
 
-\subsubsection*{\boldmath Considering the paths for vertices from $Z$}
+\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
 All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
@@
 
-\subsubsection*{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$}
+\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
 Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
@@
 
-\subsubsection*{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$}
+\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
 The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
@@
 
-\subsubsection*{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$}
+\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
 The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
@@
 \subsection{Solving ILP instances}
+\todo[inline]{HM: i think we should elaborate a little bit more on correctness.
+basically saying that because we do exhaustive search, we are not overlooking solutions.
+and because we add all constraints, we can be sure that if the ILP is a yes-instance, there is actually a labeling.}
 All of the above finishes our construction of ILP instances.
@@
 in the FPT time, with respect to $k$.
-If none of the ILP instances gives a positive solution, then there exsist no labeling $\lambda$ of $G$ that would preserve all the fastest durations from $D$.
-In the case when there is at least one $I$ that has a valid solution $X$, 
-we use the solution $X$ and produce our labelling $\lambda$.
-We use the following procedure,
-first we
+%
+If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
+If there is at least one $I$ that has a valid solution, 
+we use this solution and produce our labelling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
+This is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
+Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
+This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
+and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
+for all pairs of vertices $u,v$.
+Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
+But if there is an instance with a positive solution, then this instance gives rise to the desired labelling, as it satisfies all of the constraints.
+
+To create the labelling $\lambda$ from a solution $X$, of a positive ILP instance,
+we use the following procedure.
+First we
 label each edge $e$, that corresponds to the variable $x_e$
@@
 We then continue to set the labels of all other edges. 
-We know that all of the labels of these edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore we easily calculate the desired labels for all remaining edges.
-At the end we have a labeling $\lambda$ of $G$, that preserves all the durations from $D$.
-This follow from the fact that ILP consisted of constraints for all temporal paths,
-\ie
-it cannot happen that there is a fastest temporal path $P_{u,v}$ among two vertices $u,v$ in $(G,\lambda)$ 
-for which $P_{u,v} \neq D_{u,v}$.
+We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
+Therefore, we easily calculate the desired labels for all remaining edges.
 
@@
 
-\section{Ideas}
-\begin{itemize}
-    \item Symmetric distance matrix $D$: polytime?
-    \item Use $|D|_\infty$ (maximum value in $D$) + max degree $\Delta$ as parameter $\rightarrow$ should give FPT
-    \item FPT with feedback edge number
-    \item use as parameter $\max_{i,j} |D_{i,j}-D_{j,i}|$
-    \item approximation (additive or multiplicative), maybe with graph as input
-\end{itemize}
-
-\problemdef{\kDeltaExactLong\ (\kDeltaExact)}
-{An $n \times n$ matrix $D$ of positive integers.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
-
-\problemdef{\kDeltaUpperBoundLong}
-{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{i,j}$.}
-
-\problemdef{\kDeltaLowerBoundLong}
-{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
-{Does there exist a graph $G=(V,E)$ on the vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at least} $D_{i,j}$.}
-\todo[inline]{NOT TEMPORALLY INTERESTING: the difficulty is to find a static graph with equal labels}
-
-\todo[inline]{The matrix $D$ is m x m, and capturing the distances from an edge e to an edge f (zoom 14 Nov 22, GH).}
-\todo[inline]{Check if the reduction works for the UPPER BOUNDED version (seems to work)}
-\todo[inline]{how to extend the poly algorithms of cycles? Easy candidate: FES, FVS, series-parallel graphs, or tw=2 graphs}
-\todo[inline]{FVS, $c$-factor approximation, hardness of approximation for $c<1.5$}
-
 \end{document}

### 2023-02-07 ICALP23-RealizingTemporalGraphs.tex
Removed last comment

@@
 \subsection{Solving ILP instances}
-\todo[inline]{HM: i think we should elaborate a little bit more on correctness.
-basically saying that because we do exhaustive search, we are not overlooking solutions.
-and because we add all constraints, we can be sure that if the ILP is a yes-instance, there is actually a labeling.}
 All of the above finishes our construction of ILP instances.

### 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
Final versions_001

@@
 \usepackage{thm-restate}
+\usepackage{cite}
 
@@
 %% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Simple periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Simple TGR}}
+\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
+\newcommand{\deltaExact}{\textsc{Periodic TGR}}
 
@@
 \bibliographystyle{plainurl}% the mandatory bibstyle
+\usepackage{cite} %order citations by increasing number
 
@@
 \begin{abstract}
-In this paper we study \emph{temporal design} problems of undirected temporally connected graphs. 
-The basic setting of these optimization problems is as follows: given an undirected graph~$G$, 
-what is the smallest number $|\lambda|$ of time-labels that we need to add to the edges of $G$ such that the resulting temporal graph $(G,\lambda)$ is temporally connected?
+In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
+while we focus on periodic temporal graphs. 
+Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
+such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
+The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
+
+As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
+First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
+Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
+For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
+We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
 
@@
 
-Graph realization problems are fundamental graph-algorithmic questions where the objective is to (re)construct a graph, 
-given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
-are the vertex degrees~\cite{cai2000solution,rfgh611961hu,hakimi1962realizability,barNoy2019graphRealizations,barNoy2021selected,erdos1960graphs}, distances~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance}, eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, etc.
-The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{augustine2022distributed,grotschel1995design}.
-
-Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-SKELETON:
-\begin{itemize}
-    \item graph realization problems in general, well studied and motivated for different types of graph attributes (among the most natural ones are distances and degree sequences), mention the two perspectives: verification and network design.
-    \item Some observations and references about distance realization known results on static graphs.
-    \item In modern network applications, network structure changes over time
-    \item In this paper we focus on distance attributes (one of the most fundamental graph attributes)
-    \item What is distances in temporal graphs? Fastest, etc, periodic
-    \item Our contributions
-    \item Related work on temporal network design etc
-\end{itemize}
-
-Sections for ICALP:
-\begin{enumerate}
-    \item Intro 2 PAGES (GEORGE + PAUL)
-    \item Prelims 1 PAGE
-    \item Hardness (HENDRIK SHORTENS)
-    \begin{enumerate}
-        \item NP 1/2 PAGE (APPENDIX)
-        \item W1 (3 PAGES)
-    \end{enumerate}
-    \item Algos (NINA SHORTENS)
-    \begin{enumerate}
-        \item Tree ALGO 2 PAGE
-        \item FPT ALGO (6 PAGES)
-        \item Cylce ALGO (APPENDIX)
-    \end{enumerate}
-    \item Conclusion (?) 1/2 PAGE
-\end{enumerate}
-
-\section{Motivation}
-
-	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
-	which states that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the shortest path from $u$ to $w$ is a subpath of $P$.
-	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
-	one can see that this property does not carry over
-	(for an example see~\cref{fig:ftpExample}).
-	Which makes all the standard intuition and work with these kind of paths, much harder.
-    This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    where one first determines $O(k)$ special vertices,
-    guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    that could at the end be extended to the whole $G$.
-
-	\begin{figure}[htb]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-\section{Preliminaries}
-An interval on $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] \coloneqq \{ i\in \mathbb N_0 \mid a \leq i \leq b\}$
-and $[a] \coloneqq [1,a]$.
+The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
+The motivation for graph realization problems stems both from ``verification'' applications, 
+where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
+and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
+Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
+Among the most well studied such parameters for graph realization 
+are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
+on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
+%%%%barNoy2021selected,cai2000solution
+on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
+
+In the simplest version of a graph realization problem with respect to vertex distances, 
+we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
+This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
+Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
+If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
+Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
+Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
+
+In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
+
+\begin{definition}[temporal graph~\cite{KKK00}]
+\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
+where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
+\end{definition}
+
+Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
+In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
+The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
+causality, entities and information in temporal graphs can ``flow'' only along sequences of
+edges whose time-labels are strictly increasing.
+
+\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
+Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
+in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
+where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
+%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
+$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
+The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
+is $t_k - t_1 + 1$.
+A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
+The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
+\end{definition}
+
+%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
+
+In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
+In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
+Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
+For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
+As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
+
+Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
+Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
+In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
+When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
+Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
+We call the graph defined by those edges as the \emph{underlying graph} of $D$.
+
+\subparagraph{Our contribution.}
+%In this work, 
+We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
+
+\problemdef{\deltaExactLong\ (\deltaExact)}
+{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
+
+We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
+To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
+
+Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
+That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
+
+We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
+To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
+We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
+The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
+
+We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
+Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
+Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
+The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
+We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
+
+Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
+To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
+
+%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
+
+\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
+
+To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
+However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
+
+There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
+
+Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
+The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
+Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
+In all cases the duration of the temporal connections is not of interest.
+
+The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
+The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
+
+\subparagraph{Preliminaries and notation.}
+We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
+
+An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
 An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
@@
 We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the simplicity and the sake of an easier representation we sometimes denote an edge $e$ also as a sequence $uv$.
-A path~$P \subset G$ is a graph with a vertex set~$V(P)=\{v_1,\dots,v_k\}$ of distinct vertices and edge set~$E(P)=\{\{v_i,v_{i+1}\}\mid 1\leq i<k\}$
+For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
+A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
 (we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
 
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,\lambda_{\Delta})$, where for every edge $e\in E$ we have $\lambda_{\Delta}(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$.
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$.
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-
-\begin{definition}[temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} $(P,\lambda)$ from $u=u_0$ to $v=u_k$ in $(G,\lambda)$ is a sequence $(u_0 u_1,t_1),(u_1 u_2,t_2),\ldots,(u_{k-1} u_k,t_k)$, 
-where $P=(u_0,u_1,\ldots,u_k)$ is a path in the underlying static graph $G$ (we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda_\Delta(u_{i-1}u_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path $(P,\lambda)$ from $u$ to $v$ is $d(P,\lambda)=t_k - t_1 + 1$.
-A \emph{fastest} temporal path $(P,\lambda)$ from $u$ to $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest possible duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-Let $P$ be a path from $u$ to $v$ in $G$. 
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to the entry $D_{i,j}$.}
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$ that we are looking for in the above problems. 
-For simplicity of the presentation (and with a slight abuse of notation), we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ instead of their numbering.
+Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
+For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
+$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
 Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
 as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda)$ is a temporal path with the underlying path $P$.
-
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-that runs in polynomial-time.
-Using their algorithm, given a temporal graph $(G,\lambda)$, one can determine the whole matrix $D$ in polynomial-time,
-where $D$ consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda)$.
+where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
+We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
+
+We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
+%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
+%that runs in polynomial-time.
+Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
+which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
 
@@
 
-\section{\deltaExact}
-
-In this section 
-we show that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree or a cycle,
-we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda, \Delta)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to any other vertex $v_i$ in $P$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-All of the above is used in the design of the following polynomial-time algorithms.
-\subsection{ \deltaExact\ is polynomial-time solvable on trees and paths}
-%
-Let $D$ be a matrix from \deltaExact, when the underlying graph $G$ of $D$ is a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{lemma}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays of all vertices of degree at least $2$ in $G$.
-    \end{lemma}
-    \begin{proof}[Proof of \cref{lemma:matrixT-travelDelays-tree}]
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{proof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing a label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{ \deltaExact\
-is polynomial-time solvable on cycles}
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance, and therefore also duration $0$ from itself. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\section{Hardness Results}  
-\subsection{\deltaExact\ is NP-hard}
-In this section we prove that it is NP-hard to determine the $\Delta$-periodic temporal graph $(G,\lambda)$,
-for a general instance $(D, \Delta)$ of \deltaExact\,
-where $\Delta \geq 3$.
-
-\begin{theorem}
-	\deltaExactLong\ is \NP-hard for a general $(D,\Delta)$, where $\Delta \geq 3$.
+\subparagraph{Organization of the paper.}
+In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
+In \cref{sec:algos} we present our algorithmic results.
+First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
+In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
+In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
+Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
+
+\section{Hardness results for \deltaExact}\label{sec:hardness}
+In this section we present our main computational hardness results.
+In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
+In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
+We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
+
+\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
+In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
+even if $\Delta$ is a small constant.
+
+\begin{theorem}\label{thm:NPhardness}
+	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
 \end{theorem}
@@
 	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{True} iff not all of its literals are equal.
-    We construct an instance $D^\phi$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of  $D^\phi$.
+Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
+    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
+    We are asked whether $\phi$ admits a satisfying assignment.
+
+    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
+
+ We start by describing the vertex set of the underlying graph $G$ of $D$.
 \begin{itemize}
@@
 This finishes the construction of $G$.
-For an example see~\cref{fig:NP-example}.
+For an illustration see~\cref{fig:NP-example}.
 
 %
-\begin{figure}[htb]
+\begin{figure}[t]
 	\noindent
@@
 	%%Variable X1
+	\node (x1t) at (1,0) {};
+	\node (x1f) at (3,0) {};
+
+	%%Variable X2
+	\node (x2t) at (5,0) {};
+	\node (x2f) at (7,0) {};
+
+	%%Variable x3
+	\node (x3t) at (9,0) {};
+	\node (x3f) at (11,0) {};
+
+	%%Variable x4
+	\node (x4t) at (13,0) {};
+	\node (x4f) at (15,0) {};
+
+	%% edges among xt, xf vertices
+	%x1 to all
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
+
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
+	%x2 to all
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
+
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
+	%x3 to all
+	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
+
+	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
+
+	%%Variable X1
 	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label=right:$x_1^F$] (x1f) at (3,0) {};
+	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
 	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
@@
 	%%Variable X2
-	\node[vert,label=left:$x_2^T$] (x2t) at (5,0) {};
-	\node[vert,label=right:$x_2^F$] (x2f) at (7,0) {};
-	\node[vert,label=above:$x_2$] (x2) at (6,1) {};
+	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
+	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
+	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
 	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
@@
 	%%Variable x3
-	\node[vert,label=left:$x_3^T$] (x3t) at (9,0) {};
-	\node[vert,label=right:$x_3^F$] (x3f) at (11,0) {};
-	\node[vert,label=above:$x_3$] (x3) at (10,1) {};
+	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
+	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
+	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
 	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
@@
 	%%Variable x4
-	\node[vert,label=left:$x_4^T$] (x4t) at (13,0) {};
+	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
 	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
@@
 
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted] (x3f) [out=30,in=150] to (x4f);
 \end{tikzpicture}
 }
-\caption{Example of the temporal graph $(G_\phi,\lambda)$ from the NP-hardness reduction, 
-	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
-For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with a dotted line.
-Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
+\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
+	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
+To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
+Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
 where all unlabeled edges get the label $2$.
-\label{fig:NP-example}}
+}\label{fig:NP-example}
 \end{figure}
 %
-Now we specify the durations in the matrix $D^\phi$ between all vertex pairs.
-For the sake of simplicity we write $D^\phi _{u,v}$ as $d(u,v)$,
+We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
+For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
 where $u,v$ are two vertices of $G$. 
@@
 \end{itemize}
-This finishes the construction of an instance $D^\phi$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $D^\phi$ is a yes-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $D^\phi$ of \deltaExact\ is a yes-instance. 
+This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
+In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
+
+$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
 Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
@@
 We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{True}, otherwise we set $x_i$ to \textsc{False}.
+if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
 
@@
 Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{False}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
+In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
 
@@
 By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
+Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
 Let us denote with $t = \lambda(x_1^T v)$.
@@
 Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{True}.
+Which implies that $x_1$ is set to \textsc{true}.
 %
@@
 $v$ to $c$.
-Suppose now w.l.o.g\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta$ goes through vertex $x_2^T$.
+Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
 Let us denote with $t' = \lambda(x_2^T v)$.
@@
 In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{True}.
-But now we have that $x_1,x_2$ both appear in $c$, where one of them is \textsc{True}, while the other is \textsc{False},
+which implies that $x_2$ is set to \textsc{false}.
+But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
 which implies that the clause $c$ is satisfied, a contradiction.
@@
     %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{True}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{False}, we set $\lambda(x_i^T v)=3$.
+    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
+    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
     \item We set the labels of all other edges to two.
@@
 
-    If $x_i$ is set to \textsc{True}, then there is a temporal path from $x_i$ to $v$ via 
+    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
     $x_i^F$ of duration $2$, since
@@
 
-    If $x_i$ is set to \textsc{False}, then, by similar arguing, 
+    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
     there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
@@
     Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{True} and at least one to \textsc{False}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{True} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{False} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{True} (the case when $x_i$ appears negated in $c$ and is set to \textsc{False} is symmetric).
+    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
+    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
+    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
+    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
     Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{False} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{True} is symmetric).
+    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
+    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
     Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
@@
 \end{itemize}
-Lastly, observe that $\Delta$ has to be greater or equal to $3$, as the above constructed labeling $\lambda$ uses values from $\{1,2,3\}$.
+Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
 \end{proof}
 
-\subsection{W[1]-hardness}
+\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
+
+In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
+We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
+The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
+The set $X$ is called a \emph{feedback vertex set}.
+Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
+
 \begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number.
+    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
 \end{theorem}
@@
 
-    \subparagraph{Edge Selection Gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
+    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
     \begin{itemize}
@@
 
-    \subparagraph{Verification Gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
+    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
     \begin{itemize}
@@
 
-    \subparagraph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
+    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
+Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
 Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
@@
 
-\subparagraph{Alignment Gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget and one vertex for each connector gadget.
+\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
+It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
 Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget is connected to exactly one vertex in $\hat{W}$, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget is connected to exactly one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-
-\subparagraph{Feedback Vertex Number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
+The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
+Intuitively, this gadget is used to relate labels of different gadgets to each other.
+
+\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
 \begin{itemize}
     \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget.
+    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
     \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
@@
 
-\subparagraph{\boldmath Duration Matrix $D$.} We proceed with describing the matrix $D$, of durations of fastest paths.
+\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
 For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
@@
 
-All durations between non-adjacent vertex pairs that are not specified above are set to infinity.
+All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
 
@@
     }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labelling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
+    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
     The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
     and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{i,j,3},a_2^{i,j,3},\dots,a_{5n}^{i,j,3}$ 
-    and $b_1^{i,j,3},b_2^{i,j,3},\dots,b_{5n}^{i,j,3}$, respectively.
+    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
+    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
     }\label{fig:hardness1}
@@
 
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance, which can clearly be computed in polynomial time.
+\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
 For an illustration see \cref{fig:hardness1}.
@@
 
-In the remainder we prove that $D$ is a yes-instance of \deltaExactLong\ if and only if the $H$ is a yes-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a yes-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
+In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
+
+\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
 We have that the underlying graph $G$ is uniquely defined by $D$.
@@
 However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n}\mid \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n}\mid \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
+Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
+Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
 Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
@@
 \[
-X=\{e_\ell^{i,j}\in F_{i,j}\mid \sigma_{i,j}(\ell)=1\}
+X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
 \]
@@
 
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges, of the edge selection gadgets.
+Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
 
@@
 Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
+Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
+   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
+Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
     It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
@@
 
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'}\mid 0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
+    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
     Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
@@
 
-Now, we investigate the labels of the verification gadgets.
+Next, we investigate the labels of the verification gadgets.
 
@@
 It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'}\mid \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$ until it reaches $v^i_1$.
+In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
+From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
+Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
+In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
 More generally, we can make the following observation.
@@
 Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
+Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
 \end{claim}
@@
     \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''}\mid \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''}\mid \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''}\mid \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''}\mid \ell''\in[5n]\}$.
+        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
+        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
+        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
+        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
     \end{itemize}
@@
     Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''}\mid \ell''\in[5n]\}$.
+This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
+Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
 
@@
     Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$.
+Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
 The claim follows.
@@
 \begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$.
+    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
 We analyse the former case first.
 
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
+    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
+It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
 It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
 Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
+It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
+
+    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
 \end{claimproof}
@@
 Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
+By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
 Next, we analyse which vertices in this set are visited by $P$.
@@
 Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i\mid 0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i\mid 0\le j\le k\}$.
+Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
 Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
@@
 \begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
+Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
 By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
@@
     Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
+    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
+We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
+    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
     We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
+    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
 
@@
 However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
+As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
 More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''}\mid \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'}\mid \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''}\mid \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
+To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
+Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
+
+By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
+The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
 By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
@@
 %
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'}\mid i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
+   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
     %
@@
 \begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'}\mid \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$.
+    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
 By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
@@
 \begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$.
+    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
 Assume $P$ follows this path.
@@
 It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell\mid \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'}\mid \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
+By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
+If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
 By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
@@
 \end{claimproof}
+
+Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
 
@@
 Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
+By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
 Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
@@
 and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''}\mid \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''}\mid \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''}\mid \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''}\mid \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
+By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
+Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
 
@@
 
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a yes-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labelling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
+\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
+We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
 
@@
 
- Next, consider the alignment gadget.
+ For the alignment gadget the following requirements were specified.
 Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
@@
 \end{itemize}
+
 It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
+Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
+To see this, consider the following.
+Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
+By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
+We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
+
+ Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
+By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
 
@@
 Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''}\mid \ell''\in[5n]\}$ to arrive at $v^i_j$.
+Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
+From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
 By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
@@
 Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''}\mid \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
+Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
 By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
 
+By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
+
 This finishes the proof.
 
-\subparagraph{Infinity Gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
+\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
 To this end, we introduce the \emph{infinity gadget}.
@@
 
-\section{\deltaExact\ is FPT}
-In this section we present an FPT algorithm for \deltaExact\ parameterized it by the feedback edge number of the underlying graph.
+\section{Algorithms for \deltaExact}\label{sec:algos}
+In this section we provide several algorithms for \deltaExact.
+By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
+
+We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
+In \cref{sec:FPT} we generalize this result.
+We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
+Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
+Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
+Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
+
+We first start with defining certain notions, that will be of use when solving the problem.
+
+    \begin{definition}[Travel delays]
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
+    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+    More specifically:
+    \begin{equation}\label{eq:def-VertexWaitingTime}
+       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+    \end{equation}
+    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    \end{definition}
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
+
+    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
+    \begin{observation}\label{obs:durationPwithWaitingTimes}
+        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
+        $(P, \lambda)$ from $v_0$ to $v_p$.
+        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
+    \end{observation}
+    \begin{proof}
+        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
+        Then
+        \begin{align*}
+        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
+        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
+        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
+        & = t_{p-1} - t_1 + 1\\
+        & = d(P)
+        \end{align*}
+        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
+        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
+    \end{proof}
+    We also get the following.
+    \begin{observation}\label{obs:travel-delays-both-directions}
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
+    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{observation}
+
+    \begin{proof}
+        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
+        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{proof}
+
+\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
+    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
+    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
+    Then we can determine travel delays on vertices of $P$ using the following equation
+    \begin{equation}\label{eq:trav-delays-paths}
+        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
+    \end{equation}
+    for all $i \in \{2,3, \dots, k-1\}$.
+\end{lemma}
+
+\begin{proof}
+    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
+    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
+    \begin{align*}
+        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
+        & \equiv 
+        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
+        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
+        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
+        \end{align*}
+    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
+\end{proof}
+
+\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
+%All of the above is used in the design of the following polynomial-time algorithms.
+We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
+Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
+Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
+and therefore are the fastest.
+Then $D$ is of the following form:
+\begin{equation*}
+    D_{i,j} =
+    \begin{cases}
+    0 & \text{if $i = j$}, \\
+    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
+    d(P_{i,j},\lambda) & \text{else}
+    \end{cases},
+\end{equation*}
+where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
+
+\begin{observation}\label{obs:travel-delays-in-trees}
+    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
+    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
+    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
+    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
+\end{observation}
+
+\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
+    \deltaExact\ can be solved in polynomial time on trees.
+\end{theorem}
+
+\begin{proof}
+    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
+    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
+    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
+At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
+    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
+    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
+
+    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
+    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
+
+    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
+    We now take the unique path $P_{i,j}$ in $G$, 
+    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
+    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
+    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
+    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
+    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
+    When we have exhausted the $i$-th row of $D$,
+    \ie vertex $v_i$ now reaches every vertex of $G$,
+    we continue and repeat the procedure for all other vertices.
+    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
+    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
+    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
+    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
+        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
+    \end{claim}
+    \begin{claimproof}
+        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
+        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
+        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
+        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
+        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
+        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
+        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
+        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
+    \end{claimproof}
+
+    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
+    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
+    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
+Therefore, all together the whole algorithm is performed in polynomial time.
+\end{proof}
+
+\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
+
+In this section we show how to generalize the result presented in \cref{sec:treealgo}.
+Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
+\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
+Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
+
 In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
@@
 
-Before we start with the proof of \cref{thm:FPTwrtFES} we fix the following notation. 
+We first give an informal and very high-level description of the main ideas of the algorithm.
+It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
+Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
+These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
+We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
+An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
+
+In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
+This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
+Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
+
+	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
+ When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
+	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
+	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
+ For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
+	%This makes all the standard intuition and work with these kind of paths, much harder.
+    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
+    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
+    %where one first determines $O(k)$ special vertices,
+    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
+    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
+    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
+    %that could at the end be extended to the whole $G$.
+
+	\begin{figure}[t]
+    \centering
+	\begin{tikzpicture}[xscale=2]
+	%%%S_uv
+	\node[vert,label=below:$u$] (v1) at (1,0) {};
+	\node[vert] (v2) at (2,0) {};
+	\node[vert,label=below:$w$] (v3) at (3,0) {};
+	\node[vert] (v4) at (4,0) {};
+	\node[vert,label=below:$v$] (v5) at (5,0) {};
+	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
+	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
+
+	\draw[transform canvas={yshift=-1.5mm}, blue]
+	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
+
+	\draw[red]
+	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
+\end{tikzpicture}
+	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
+		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
+		\label{fig:ftpExample}}
+	\end{figure}
+
+To overcome the above mentioned difficulties, we propose the following high-level strategy.
+\begin{itemize}
+    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
+    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
+    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
+    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
+    \item We compute a solution to the ILP and construct a labeling from that solution.
+Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
+\end{itemize}
+
+For the remainder of this section, we fix the following notation. 
 Let $D$ be the input matrix of \deltaExact\ \ie
 the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-Let $F$ be a minimum feedback edge set of $G$ and let $k$ be the feedback edge number of $G$.
+With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
+We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
+We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
+Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
+At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
+
+\begin{comment}
 
@@
 %But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses (where $f$ will be a double exponential function in the feedback edge number $k$).
+We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
 We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{Yes} instance then we can will show that also $D$ is a \textsc{Yes} instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we can construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{No} instances, then we will show that $D$ is a \textsc{No} instance of \deltaExact.
+If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
+Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
+If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
 Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
 Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-
-We now introduce the algorithm, that determines a labeling of $G$ satisfying $D$, or determines that no such labeling exists, and that runs in $f(k) \cdot \text{poly}(n)$ time.
-Our algorithm performs the following steps.
-\begin{enumerate}
-    \item Preprocessing on graph $G$.
-    \item Guess desired structures and create ILP instances.
-    \item Add constraints to the ILP instances for all pairs of vertices.
-    \item Solve the ILP instances.
-\end{enumerate}
-
-\subsection{Preprocessing of the input}
+\end{comment}
+%
+
+\subsubsection{Preprocessing of the input}
 From the underlying graph $G$ of $D$ we first create a graph $G'$ by
@@
 We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U \mid u \in U, v \in N(u)\}.\]
+\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
 Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
@@
 \[
-Z^* = \{ r_i | r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
+Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
 \]
@@
 Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following.
+Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
 \begin{corollary}\label{obs:FPT-k2segments}
@@
 \end{corollary}
-In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
+%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
 %, which we prove later on (see~\cref{obs:FPT-k2segments}).
@@
 
-\subsection{Guessing necessary structures}
-We start the algorithm by guessing necessary structures.
+\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
+Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
 Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
@@
     More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{p-1}}$.
+    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
     From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
     and 
-    the fastest temporal paths from $v_i$ to $z_{p-1}, z_{p-2}, \dots, z_{j+1}$ go through $z$.
+    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
     In this case we only need to guess the following two fastest temporal paths 
     $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{p-1}$.
+    and $u \leadsto z \rightarrow z_{r-1}$.
     Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
@@
     $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{p-1}$
+    and $u \leadsto z \rightarrow z_{r-1}$
     (see guess~G-\ref{FPT:guess-uToSegmentz2}).
@@
 %
-\begin{figure}[htb]
+\begin{figure}[t]
     \centering
@@
 	\end{subfigure}
-\caption{An example of guesses G-4, G-5, G-6 and G-7.}
+\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
 \end{figure}
@@
 We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^6})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with exponential in $k$ different cases.
+We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
+After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
 We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed and the permutation of all variables.
-
-\subsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP.
+From now on we assume that we know exactly the structure of all paths we have guessed.
+
+\subsubsection{Properties of \deltaExact}
+
+In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
 Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and start specifying the labels of edges.
+We start with an empty labeling of edges and try to specify each one of them.
 Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-%In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
+We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
+
 In our analysis we exploit the following greatly, that is why we state is as an observation.
@@
 Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
+Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
 
@@
 \end{proof}
-
-\todo[inline]{George proved it. Added proof inside. Check if OK?\\}
-
-%\todo[inline]{HM: the last sentence in \cref{lemma:FPT-uv-LabelAlmostalledges} is strange. it doesn't say anything. either give the specific restrictions or remove it.}
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centering
@@
 \end{proof}
-
-%Observe also the following.
-\todo[inline]{Check all of the above and correct it   HM: i checked it and didnt find any issues.}
 
@@
 
-\subsection{Adding constraints and variables to the ILP}
+\subsubsection{Adding constraints and variables to the ILP}
 We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
@@
 \end{enumerate}
-
+We have now finished creating all ILP instances.
+From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
 We proceed with adding constraints to each of our ILP instances.
@@
 Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{p-1} \rightarrow w \leadsto u$.
+and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
 Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
@@
     \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$.
-    In this case we have to determine if the fastest temporal path goes first through vertex $z_{i-1}$ (and then through $w$),
+    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
+    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
     or it goes first through $z_{i+1}$ (and then through $z$).
@@
 
-\subsection{Solving ILP instances}
+\subsubsection{Solving ILP instances}
 All of the above finishes our construction of ILP instances.
@@
 If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labelling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-This is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
+we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
+We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
 Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
@@
 for all pairs of vertices $u,v$.
-Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
-But if there is an instance with a positive solution, then this instance gives rise to the desired labelling, as it satisfies all of the constraints.
-
-To create the labelling $\lambda$ from a solution $X$, of a positive ILP instance,
+Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
+For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
+Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
+
+To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
 we use the following procedure.
@@
 Therefore, we easily calculate the desired labels for all remaining edges.
+
+\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
+In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
+Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
+
+Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
+By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
+Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
+therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
+This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
+The matrix $D$ is of the following form
+\begin{equation} \label{eq:D-matrixForCycles}
+  D = 
+  \begin{bmatrix}
+    0 & 1 &  &  &  & 1\\
+    1 & 0 & 1 &  &  & \\
+    & 1 & 0 & 1 & & \\
+    & & \ddots & \ddots & \ddots &   \\
+    &   & &1 &  0 & 1\\ 
+    1 &  &  &  &1 &  0 
+  \end{bmatrix},
+\end{equation}
+where the empty entries consists of positive integers different than $1$.
+
+Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
+If it is not of correct form, our algorithm stops and returns the negative answer.
+From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
+
+Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
+Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
+and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
+Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
+and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
+Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
+
+\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
+    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
+    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
+    using the same, positive (resp.~negative) side of the cycle,
+    where the indices are taken modulo $n$.
+\end{lemma}
+\begin{proof}
+    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
+    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
+    for which $D_{i,k} \neq d^+(i,k)$.
+    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
+    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
+    So 
+    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
+        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
+    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
+    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
+    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
+    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
+This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
+    In the above construction vertex $v_k$ is visited twice.
+By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
+Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
+    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
+\end{proof}
+
+Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
+Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
+using positive (resp.~negative) side of the cycle, 
+\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
+Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
+we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
+
+Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
+Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
+and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
+Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
+Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
+$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
+Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
+Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
+Let us denote these two values as $m_i^1$ and $m_i^2$.
+The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
+the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
+and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
+where indices are taken modulo $n$.
+
+Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
+To determine these two sets we do the following.
+We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
+We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
+for which it has to hold that
+$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
+$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
+Note, it can also happen that $m_i^1 = m_i^2$. 
+Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
+the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
+By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
+which we store in a list $T$ of length $n$,
+where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
+Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
+We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
+Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
+
+To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
+
+\begin{lemma}
+List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
+\end{lemma}
+\begin{proof}
+    Throughout the proof we
+    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
+    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
+    where indices are taken modulo $n$.
+
+    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
+    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
+    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
+    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
+    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
+    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
+    Since $v_i$ has to be on the maximum duration from both of them 
+    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
+    we know that 
+    \begin{align}\label{eq:cycle-travel-delays-all}
+        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
+        & d^-(i-1,i+1) < d^+(i-1,i+1).
+    \end{align}
+    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
+
+    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
+    W.l.o.g. we can suppose that $a \geq a'$.
+    Therefore, using the definition for the duration of temporal paths, we get that
+    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
+    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
+    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
+    $b - b' < a - a'$.
+    Now again using the definition of the duration, we get
+    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
+    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
+    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
+    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
+    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
+This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
+    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
+
+    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
+\end{proof}
+
+All of the above observations imply the following result.
+\begin{theorem}
+    \deltaExact\ can be solved in polynomial time on cycles.
+\end{theorem}
+
+\begin{proof}
+As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
+Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
+We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
+Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+\end{proof}
 
@@
 
+\section{Conclusion}\label{sec:conclusion}
+We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
+We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
+Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
+For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
+We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
+Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
+
+We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
+
+\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
+\begin{itemize}
+    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
+We believe this is a promising parameter to obtain tractability.
+    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
+We leave the parameterized complexity of our problem with respect to this parameter open.
+    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
+\end{itemize}
+Furthermore, we can consider combining a structural parameter with $\Delta$.
+Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
+However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
+This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
+We believe that investigating such parameter combinations is a promising future research direction.
+
+\subparagraph{Further problem variants.}
+There are many natural variants of our problem that are well-motivated and warrant consideration.
+In the following, we give two specific examples.
+We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
+A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
+Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
+
 \bibliography{bibliography}

### 2023-02-09 ICALP23-shortversion.tex
Final versions_001

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 \usepackage{thm-restate}
-\usepackage{cite}
 
 \usepackage{caption} %for subfigure - join multiple figures and add captions
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
@@
 %% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
+\newcommand{\deltaExactLong}{\textsc{Simple periodic Temporal Graph Realization}}
+\newcommand{\deltaExact}{\textsc{Simple TGR}}
 
@@
 \usepackage{cite} %order citations by increasing number
-
 \title{Realizing temporal graphs from fastest travel times} %TODO Please add
@@
 
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
+Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
 
@@
 \subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
+We already introduced the most central notion and concepts. There are some additional definitions we need, to present our proofs and results which we give in the following.
 
@@
 where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
 
@@
 
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
+\section{Hardness results for \deltaExact}  
 In this section we present our main computational hardness results.  
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
+We first show that \deltaExact\ is NP-hard even for constant $\Delta$. 
+%Then we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
 We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
 
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
+%\subparagraph{NP-hardness of \deltaExact.}\label{sec:nphardness}
+%We prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
+%even if $\Delta$ is a small constant.
+
+\begin{theorem}[$\star$]\label{thm:NPhardness}
+	\deltaExact\ is \NP-hard for all $\Delta \geq 3$.
 \end{theorem}
+
+\begin{comment}
 
@@
 %
-\begin{figure}[t]
+\begin{figure}[htb]
 	\noindent
@@
 \end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
+This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. We defer the correctness proof to the appendix.
 \end{proof}
 
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
+\end{comment}
+
+%\subparagraph{Parameterized Hardness of \deltaExact.}\label{sec:w1hardness}
+
+Next, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
 We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
+The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest. The set $X$ is called a \emph{feedback vertex set}. 
+Note that, in contrast to the previous results (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
+
+\begin{theorem}[$\star$]\label{thm:W1wrtFVS}
+    \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
 \end{theorem}
@@
 
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
 At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
 
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
+    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExact\ (with infinity entries and no periods) as follows.
 To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
@@
 
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
+    \emph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
     \begin{itemize}
@@
 
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
+    \emph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
     \begin{itemize}
@@
 
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
+\begin{comment}
+
+    \emph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
 Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
@@
 
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
+\emph{Alignment Gadget.} Lastly, we introduce an \emph{alignment gadget}.
 It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
@@
 The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
+
+\end{comment}
+
+Furthermore, we use \emph{connector gadgets}, two for each edge selection gadget, and two for every verification gadget.
+They consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and, intuitively, are used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
+Finally, we have an \emph{alignment gadget}, which is a star with a center vertex $w^\star$ and a leaf for every other gadget.
 Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
+A formal description of these two gadgets is given in the Appendix.
+
+This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
+%\begin{itemize}
+ %   \item 
+    vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
+    %\item 
+    vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
+    %\item 
+    vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
+    %\item 
+    vertex $w^\star$ of the alignment gadget
+%\end{itemize}
 forms a feedback vertex set in $G$ with size $O(k^2)$.
 
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
+\begin{comment}
+\emph{Duration Matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
 For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
@@
 
-\begin{figure}%[t]
+\end{comment}
+
+\begin{figure}[t]
 \noindent\makebox[\textwidth]{
@@
 %\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
+\begin{tikzpicture}[line width=1pt, scale=.65, yscale=.6]
 \scriptsize
@@
 
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
+\draw[rounded corners, dashed, gray] (-13, 5.4) rectangle (10, 1.6) {};
 \node (A) at (-10.5,4.5) {alignment gadget};
@@
 
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
+\draw[rounded corners, dashed, gray] (-9.5, 1.4) rectangle (1.5, -26) {};
 \node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
 
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
+\draw[rounded corners, dashed, gray] (3.5, 1.4) rectangle (6.5, -26) {};
+\node[rotate=-90] (A) at (7,-21.5) {verification gadget for $j$};
 
@@
 
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
+	\draw[edge, line width=1.5pt] (X1) --node[] {} (VS);
+	\draw[edge] (X2) --node[] {} (VS);
+	\draw[edge] (X3) --node[] {} (VS);
+	\draw[edge] (XM) --node[] {} (VS);
+
+    \draw[edge] (Y1) --node[] {} (VS);
+	\draw[edge] (Y2) --node[] {} (VS);
+	\draw[edge, line width=1.5pt] (Y3) --node[] {} (VS);
+	\draw[edge] (YM) --node[] {} (VS);
+
+    \draw[edge] (Y1) --node[] {} (U11);
+	\draw[edge] (Y2) --node[] {} (U12);
+	\draw[edge, line width=1.5pt] (Y3) --node[] {} (U13);
+	\draw[edge] (YM) --node[] {} (U1M);
+
+    \draw[edge] (U21) --node[] {} (U11);
+	\draw[edge] (U22) --node[] {} (U12);
+	\draw[edge, line width=1.5pt] (U23) --node[] {} (U13);
+	\draw[edge] (U2M) --node[] {} (U1M);
+
+    \draw[edge] (UN1) --node[] {} (UN11);
+	\draw[edge] (UN2) --node[] {} (UN12);
+	\draw[edge, line width=1.5pt] (UN3) --node[] {} (UN13);
+	\draw[edge] (UNM) --node[] {} (UN1M);
+
+    \draw[edge] (U2N1) --node[] {} (VSS);
+	\draw[edge] (U2N2) --node[] {} (VSS);
+	\draw[edge, line width=1.5pt] (U2N3) --node[] {} (VSS);
+	\draw[edge] (U2NM) --node[] {} (VSS);
+
+    \draw[edge] (VH11) --node[] {} (VH12);
+	\draw[edge] (VH12) --node[] {} (VH111);
+	\draw[edge] (VH12) --node[] {} (VH13);
+    \draw[edge] (VH13) --node[] {} (VH14);
+	\draw[edge] (VH13) --node[] {} (VH144);
+
+    \draw[edge] (VH21) --node[] {} (VH22);
+	\draw[edge] (VH22) --node[] {} (VH211);
+	\draw[edge] (VH22) --node[] {} (VH23);
+    \draw[edge] (VH23) --node[] {} (VH24);
+	\draw[edge] (VH23) --node[] {} (VH244);
+
+    \draw[edge] (VH31) --node[] {} (VH32);
+	\draw[edge] (VH32) --node[] {} (VH311);
+	\draw[edge] (VH32) --node[] {} (VH33);
+    \draw[edge] (VH33) --node[] {} (VH34);	
+    \draw[edge] (VH33) --node[] {} (VH344);
+
+    \draw[edge] (VH41) --node[] {} (VH42);
+	\draw[edge] (VH42) --node[] {} (VH411);
+	\draw[edge] (VH42) --node[] {} (VH43);
+    \draw[edge] (VH43) --node[] {} (VH44);	
+    \draw[edge] (VH43) --node[] {} (VH444);
 
@@
 
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
+	\draw[edge] (W) --node[] {} (W1);
+	\draw[edge] (W) --node[] {} (W2);
+	\draw[edge] (W) --node[] {} (W3);
+	\draw[edge] (W) --node[] {} (W4);
+	\draw[edge] (W) --node[] {} (W5);
+	\draw[edge] (W) --node[] {} (W6);
+
+	\draw[edge] (X1) --node[] {} (W1);
+	\draw[edge] (VH11) --node[] {} (W2);
+	\draw[edge] (VH21) edge[bend left=50] node[] {} (W3);
+	\draw[edge] (VH31) --node[] {} (W4);
+	\draw[edge] (YI) --node[] {} (W5);
+	\draw[edge] (VH41) edge[bend right=50] node[] {} (W6);
+
+	\draw[edge] (YI) --node[] {} (VI0);
+
+	\draw[edge] (VII1) --node[] {} (UI1);
+	\draw[edge] (UI1) --node[] {} (UI2);
 \end{tikzpicture}
@@
     }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
+    \caption{Illustration of part of the underlying graph $G$. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
     The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
@@
 
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
+%This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
 For an illustration see \cref{fig:hardness1}.
@@
 
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
+Due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
+
+\emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
 To this end, we introduce the \emph{infinity gadget}.
@@
 %\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
+\begin{tikzpicture}[line width=1pt, scale=.65,yscale=.7]
 \scriptsize
@@
 %    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
+    \caption{Illustration of the infinity gadget. Gray vertices are added to the feedback vertex set.}\label{fig:hardness2}
 \end{figure}
@@
 
-\section{Algorithms for \deltaExact}\label{sec:algos}
+%\pagebreak
+
+\section{Algorithms for \deltaExact}
 In this section we provide several algorithms for \deltaExact.
@@
 Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
+In the Appendix we give also a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
 Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
 
+\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
 We first start with defining certain notions, that will be of use when solving the problem.
@@
     \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
     \end{definition}
     Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
+    From the above definition and the definition of the duration of the temporal path $P$ we get the following results.
+    \begin{observation}[$\star$]\label{obs:durationPwithWaitingTimes}
         Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
@@
     \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
+    \begin{observation}[$\star$]\label{obs:travel-delays-both-directions}
     Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
@@
     \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
+\begin{lemma} [$\star$]\label{lemma:unique-fastest-path-allDelays}
     Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
@@
     \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
+        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i}, \text{ for all $i \in \{2,3, \dots, k-1\}$.}
     \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
 \end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
 %All of the above is used in the design of the following polynomial-time algorithms.
@@
 \begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
+    Let $v_i,v_j$  be arbitrary vertices in a tree $G$. 
+    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it follows that $d(P_{i,j},\lambda) = D_{i,j}$. 
+    Moreover, all vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
 \end{observation}
@@
 \begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
+    \deltaExact\ can be solved in polynomial-time on trees.
 \end{theorem}
@@
     Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
+    In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
+    If at this point we encounter a problem, our algorithm stops and returns a negative answer.
+
+    Let $V(G) = \{v_1, v_2, \dots, v_n\}$.
     We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
     We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate waiting times at all inner vertices.
     We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
@@
     \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
+    We repeat the above procedure from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
     When we have exhausted the $i$-th row of $D$,
@@
     The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
+    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
         Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
     \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
     Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
@@
     Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+    %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
     It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
@@
 
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
+\begin{theorem}[$\star$]\label{thm:FPTwrtFES}
+    \deltaExact\ is in FPT when parameterized by the feedback edge number of the underlying graph.
 \end{theorem}
@@
     \centering
-	\begin{tikzpicture}[xscale=2]
+	\begin{tikzpicture}[xscale=2,yscale=0.6]
 	%%%S_uv
@@
 \end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
+	\caption{An example of a temporal graph (with $\Delta \geq 9$), where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
 		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
@@
 the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
+%With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
 We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
@@
 
-\subsubsection{Preprocessing of the input}
+\subparagraph{Preprocessing of the input.}
 From the underlying graph $G$ of $D$ we first create a graph $G'$ by
@@
 \]
-Then we determine a minimum feedback edge set $F$ of $G'$.
+Then we determine a minimum feedback edge set $F$ of $G'$, and denote with $k = |F|$.
 %by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
+%Note that $F$ is also a minimum feedback edge set of $G$.
+%Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
+Let $T$ be a spanning tree of $G'$ and
+let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
 and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
@@
 \[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
+the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
 We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
@@
 
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
+\subparagraph{Guessing necessary structures. \label{sec:FPT-guessing}}
+Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
+Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
+Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
+if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
+We guess $11$ different structures, we present here just a few of them, for all the others we refer the reader to the Appendix.
+\begin{enumerate}[G-1.]
+    \item \label{FPT-guessFTPamongU}
+    The fastest temporal paths among all pairs of vertices of $U$.
+    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
+    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
+    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
+    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
+    \item \label{FPT-guessFTPamongZstar}
+    The fastest temporal paths among all vertices in $Z^*$, 
+    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
+
+    \setcounter{enumi}{3}
+
+    \item \label{FPT-guessFTPamongUandUstar}
+    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
+    and the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
+    This gives us $O(k^{k^4})$ guesses.
+\end{enumerate}
+%
+We create all of the guesses independently.
+We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
+After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential function).
+We now create one ILP instance for each case.
+From now on we assume that we know exactly the structure of all paths we have guessed.
+
+\subparagraph{Properties of \deltaExact.}
+
+In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
+	We want to determine labeling $\lambda$ of each edge of $G$.
+	We start with an empty labeling of edges and try to specify each one of them.
+	Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
+    We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$. 
+	%In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
+	%In our analysis we exploit the following results greatly.
+    We are now ready, to present some basic properties of our problem.
 \begin{definition}
@@
 \end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
+
+	\begin{observation}[$\star$]\label{obs:FirstLabelAndDuration}
 		Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
@@
 	\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
+ If $\lambda(e_1)$ and $\lambda(e_p)$ (from the above observation) are both unknown, then we can determine one with respect to the other.
+ %\begin{definition}\label{FPT:def-segment}
+%	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
+%	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
+%	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
+%	Note $S_{u,v} \neq S_{v,u}$.
+%\end{definition}
+
+	\begin{lemma}[$\star$]\label{lemma:FPT-uv-LabelAlmostalledges}
 		Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
@@
 	\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
+    Note that in the case when path $P$ from $u$ to $v$ admits no extra vertices of interest, beside $u$ and $v$, then we can determine labels of all of its edges, with respect to the label of the first edge.
+    The procedure to determine the labeling relies on \cref{obs:FirstLabelAndDuration} (for details see Appendix).
+
+\subparagraph{Adding constraints and variables to the ILP.}
+%Using the above guessed structures, and certain properties of the problem, we proceed with adding constraints to each of our ILP instances.
+
+Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
+In order to find a labeling that satisfies this property we split our analysis in nine cases.
+We consider fastest temporal paths 
+where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
+and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
+In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
+which results in one equality constraint for the labels on the path $P$. 
+For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
+Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
+To ensure this 
+we split the graph into $O(k^2)$ segments, and introduce at most $3$ variables for each segment,
+therefore each of our ILP instances admits $O(k^3)$ number of variables (for details see Appendix).
+
+We now describe how we add constraints to a specific path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
 Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
@@
 In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
+Note that we know if the difference of two consecutive labels is positive or negative (for details see Appendix),
+which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
+
+%We iterate through all pairs of vertices $x,y$ in $G$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint}, and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
+%For each pair we argue how we determine these paths.
+We now present one example of how to determine the fastest temporal paths among a fixed pair of vertices, for all other cases we refer the reader to the Appendix.
+
+\emph{Fastest paths from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.}
+\begin{figure}[t]
+		\centering
+		%\resizebox{\linewidth}{!}{
+
+			\begin{tikzpicture}[yscale=0.3]
+				%%%S_uv
+				\node[vert,label=above:$w {=} z_1$] (v1) at (1,0) {};
+				\node[vert,label=above:$z_2$] (v2) at (2,0) {};
+				\node[vert,label=above:$z_{r-1}$] (vp1) at (6,0) {};
+				\node[vert,label=above:$z_r {=} z$] (vp) at (7,0) {};
+				\draw (v1) -- (v2) -- (vp1) -- (vp);
+
+				%%%% node w
+				\node[vert,label=below:$u$] (w) at (4,-3) {};
+
+				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
+				(v1) edge[dirwave] [out=290,in=160] (w) 
+				(v2) edge[diredge2] (v1);
+
+				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
+				(vp) edge[dirwave] [out=240,in=20] (w) 
+				(vp1) edge[diredge2] (vp);
+
+			\end{tikzpicture}%}
+		\caption{Example of a guess G-8, where we guessed the fastest paths of form $z_2 \rightarrow w \leadsto u$ (in blue) and $z_{r-1} \rightarrow z \leadsto u$ (in red), where $u$ is a vertex of interest and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
+\label{fig:FPT-4casesGuess}}
+\end{figure}
+
+We want to determine the fastest path from $x$ to $u$.
 %We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
+Let $x$ be a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
 If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
@@
 Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
+This implies that there are at most two not yet determined edges in it (intuitively, these are the edges whose labels are not determined with respect to any other edge label), which means that all of the labels of edges in the segment $S_{w,z}$ are determined with respect to (at most) two different values $\lambda(e)$ and $\lambda(f)$, for some edges $e,f$ in $S_{w,z}$.
+For a detailed explanation see Appendix.
 We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
+Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow w \leadsto u$,
+and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow z \leadsto u$.
+Note that we know these paths from the guess~G-8 (depicted in \cref{fig:FPT-4casesGuess}, for details see Appendix).
+Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_{i+1}$ reach $u$ on the 
 following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
 and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
+all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i$ reach $u$ on the 
 following fastest temporal path
@@
 
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
+\subparagraph{Solving ILP instances.}
 All of the above finishes our construction of ILP instances.
@@
 Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
+%Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
 
@@
 We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
+Therefore, we easily calculate the desired labeling.
 
 \section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
 We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
 
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
+%\subparagraph{Further parameterizations.} 
+There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
+We believe that the \emph{vertex cover number} or the \emph{tree depth} are promising candidates.
+Furthermore, we can consider combining a structural parameter such as the \emph{treewidth} with $\Delta$.
+
+%\subparagraph{Further problem variants.}
 There are many natural variants of our problem that are well-motivated and warrant consideration. 
-In the following, we give two specific examples.
+%In the following, we give two specific examples. 
 We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.

### 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
Submission

@@
 
+%%% APPENDIX
+\usepackage{fancyhdr}
+\setlength{\headheight}{30pt}
+\pagestyle{fancyplain} { % define first page header and footer
+% \fancyhead[L]{Course Report}
+\fancyhead[C]{\textbf{APPENDIX}}
+% \fancyhead[R]{\thepage of \pageref{LastPage}}
+% \fancyfoot[L]{Jinho Hwang}
+% \fancyfoot[C]{GWU}
+% \fancyfoot[R]{CS}
+}
+\fancyhf{}
+\renewcommand{\headrulewidth}{0pt} % remove header lines and reset formats
+\renewcommand{\footrulewidth}{0pt} % remove footer lines and reset formats
+
+% define the rest of pages header and footer
+% \fancyhead[L]{Course Report}
+\fancyhead[OC]{\huge \textbf{APPENDIX}}
+\fancyhead[EC]{\huge \textbf{APPENDIX}}
+% \fancyhead[R]{\thepage of \pageref{LastPage}}
+% \fancyfoot[L]{Jinho Hwang}
+\fancyfoot[OC]{\thepage}
+\fancyfoot[EC]{\thepage}
+% \fancyfoot[R]{CS}
+
 \begin{document}
@@
 
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
+%\vspace{0,2cm}
+%\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
+%	clearly marked Appendix to be read at the discretion of the Program Committee.}
 \end{abstract}
@@
 In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
+When it is clear from the context, we drop $\Delta$ form the notation and 
+we denote the ($\Delta$-periodic) temporal graph by $(G,\lambda)$.
 Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
@@
 
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
+We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number $k$ of the underlying graph (\cref{thm:FPTwrtFES}). 
+Our FPT algorithm works as follows on a high level. 
+First we distinguish $O(k)$ vertices which we call ``interesting vertices''. 
+Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of $k$. 
+Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (i.e.~bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
+For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than $D_{i,j}$.
+This naturally leads us to build one Integer Linear Program (ILP) for each of these configurations.
+We manage to formulate all these ILPs by having a number of variables that is upper-bounded by a function of $k$.
+Finally we use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve each of these ILPs in FPT time.
+At the end, our initial instance is a \textsc{Yes}-instance if and only if at least one of these ILPs is feasible.
+
+The above results provide a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph which measure ``tree-likeness''.
 To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
@@
 To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
+However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
 
@@
 Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
+as a temporal path in $(G,\lambda,\Delta)$,
 where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
@@
 This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
+In the remainder we show that $(D,\Delta)$ is a \textsc{Yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
+
+$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{Yes}-instance. 
 Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
@@
     \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
+Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{Yes}-instances much easier.
 Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
@@
 
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
+In the remainder we prove that $D$ is a \textsc{Yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{Yes}-instance of \textsc{Multicolored Clique}.
+
+\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{Yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
 We have that the underlying graph $G$ is uniquely defined by $D$.
@@
 
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
+\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{Yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
 We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
@@
 Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
+Furthermore, if $D$ is a \textsc{Yes}-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
 This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
@@
 For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
+We can conclude that the originally constructed instance $D$ is a \textsc{Yes}-instance if and only if it remains a \textsc{Yes}-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
 \end{proof}
@@
     \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
+    \item For each additive constant and each non-determined label along such a path we introduce a variable for an Integer Linear Program (ILP). 
     \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
@@
 We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
+If the ILP instance is a \textsc{Yes}-instance then we will show that also $D$ is a \textsc{Yes}-instance of \deltaExact.
 Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
+If all constructed ILP instances are \textsc{No}-instances, then we will show that $D$ is a \textsc{No}-instance of \deltaExact.
 Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.

### 2023-02-16 abstract.tex
ArXiv version

--- 2023-02-09 ICALP23-shortversion.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
-
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
-
-\usepackage{amsmath}
-%\let\proof\relax
-%\let\endproof\relax
-
-\sloppy
-
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{wrapfig} %wrap the text around the picture
-
-\usepackage{thmtools} 
-\usepackage{thm-restate}
-
-\usepackage{caption} %for subfigure - join multiple figures and add captions
-%\usepackage{subcaption}
-\usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
-\usepackage{mathtools} % write text [under]{over} arrow $\xrightarrow[\text{world}]{\text{hello}}$
-
-\usepackage{graphicx}
-\graphicspath{{Figures/}}
-
-\usepackage{tikz}
-
-\usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
-\usetikzlibrary{shapes,calc,patterns,arrows.meta}
-\tikzset{
-	vert/.style={circle,inner sep=1.5,fill=white,draw,minimum size=.3cm},
-	edge/.style={color=black, thick},
-	diredge/.style={->,>={Stealth[width=8pt,length=8pt]},color=black, thick},
-	timelabel/.style={fill=white,font=\footnotesize, text centered},
-	wave/.style={decorate,decoration={coil,aspect=0}},
-	dirwave/.style={->, >={Stealth[width=8pt,length=8pt]},decorate,decoration={coil,aspect=0}},
-	diredge2/.style={->,>={Stealth[width=8pt,length=8pt]}}
-}
-
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Simple periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Simple TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
+In this paper we initiate the study of the temporal graph realization problem with respect to the fastest path durations among its vertices, while we focus on periodic temporal graphs.
+Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices such that the duration of a fastest path from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist.
 The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
 
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
+As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.
+non-temporal) counterpart.
 First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
@@
 For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need, to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\section{Hardness results for \deltaExact}  
-In this section we present our main computational hardness results.  
-We first show that \deltaExact\ is NP-hard even for constant $\Delta$. 
-%Then we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-%\subparagraph{NP-hardness of \deltaExact.}\label{sec:nphardness}
-%We prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-%even if $\Delta$ is a small constant.
-
-\begin{theorem}[$\star$]\label{thm:NPhardness}
-	\deltaExact\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{comment}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[htb]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. We defer the correctness proof to the appendix.
-\end{proof}
-
-\end{comment}
-
-%\subparagraph{Parameterized Hardness of \deltaExact.}\label{sec:w1hardness}
-
-Next, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest. The set $X$ is called a \emph{feedback vertex set}. 
-Note that, in contrast to the previous results (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}[$\star$]\label{thm:W1wrtFVS}
-    \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExact\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \emph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \emph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-\begin{comment}
-
-    \emph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\emph{Alignment Gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-
-\end{comment}
-
-Furthermore, we use \emph{connector gadgets}, two for each edge selection gadget, and two for every verification gadget.
-They consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and, intuitively, are used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Finally, we have an \emph{alignment gadget}, which is a star with a center vertex $w^\star$ and a leaf for every other gadget.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-A formal description of these two gadgets is given in the Appendix.
-
-This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-%\begin{itemize}
- %   \item 
-    vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    %\item 
-    vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    %\item 
-    vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    %\item 
-    vertex $w^\star$ of the alignment gadget
-%\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\begin{comment}
-\emph{Duration Matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\end{comment}
-
-\begin{figure}[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65, yscale=.6]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5.4) rectangle (10, 1.6) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1.4) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1.4) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-21.5) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[] {} (VS);
-	\draw[edge] (X2) --node[] {} (VS);
-	\draw[edge] (X3) --node[] {} (VS);
-	\draw[edge] (XM) --node[] {} (VS);
-
-    \draw[edge] (Y1) --node[] {} (VS);
-	\draw[edge] (Y2) --node[] {} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[] {} (VS);
-	\draw[edge] (YM) --node[] {} (VS);
-
-    \draw[edge] (Y1) --node[] {} (U11);
-	\draw[edge] (Y2) --node[] {} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[] {} (U13);
-	\draw[edge] (YM) --node[] {} (U1M);
-
-    \draw[edge] (U21) --node[] {} (U11);
-	\draw[edge] (U22) --node[] {} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[] {} (U13);
-	\draw[edge] (U2M) --node[] {} (U1M);
-
-    \draw[edge] (UN1) --node[] {} (UN11);
-	\draw[edge] (UN2) --node[] {} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[] {} (UN13);
-	\draw[edge] (UNM) --node[] {} (UN1M);
-
-    \draw[edge] (U2N1) --node[] {} (VSS);
-	\draw[edge] (U2N2) --node[] {} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[] {} (VSS);
-	\draw[edge] (U2NM) --node[] {} (VSS);
-
-    \draw[edge] (VH11) --node[] {} (VH12);
-	\draw[edge] (VH12) --node[] {} (VH111);
-	\draw[edge] (VH12) --node[] {} (VH13);
-    \draw[edge] (VH13) --node[] {} (VH14);
-	\draw[edge] (VH13) --node[] {} (VH144);
-
-    \draw[edge] (VH21) --node[] {} (VH22);
-	\draw[edge] (VH22) --node[] {} (VH211);
-	\draw[edge] (VH22) --node[] {} (VH23);
-    \draw[edge] (VH23) --node[] {} (VH24);
-	\draw[edge] (VH23) --node[] {} (VH244);
-
-    \draw[edge] (VH31) --node[] {} (VH32);
-	\draw[edge] (VH32) --node[] {} (VH311);
-	\draw[edge] (VH32) --node[] {} (VH33);
-    \draw[edge] (VH33) --node[] {} (VH34);	
-    \draw[edge] (VH33) --node[] {} (VH344);
-
-    \draw[edge] (VH41) --node[] {} (VH42);
-	\draw[edge] (VH42) --node[] {} (VH411);
-	\draw[edge] (VH42) --node[] {} (VH43);
-    \draw[edge] (VH43) --node[] {} (VH44);	
-    \draw[edge] (VH43) --node[] {} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[] {} (W1);
-	\draw[edge] (W) --node[] {} (W2);
-	\draw[edge] (W) --node[] {} (W3);
-	\draw[edge] (W) --node[] {} (W4);
-	\draw[edge] (W) --node[] {} (W5);
-	\draw[edge] (W) --node[] {} (W6);
-
-	\draw[edge] (X1) --node[] {} (W1);
-	\draw[edge] (VH11) --node[] {} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[] {} (W3);
-	\draw[edge] (VH31) --node[] {} (W4);
-	\draw[edge] (YI) --node[] {} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[] {} (W6);
-
-	\draw[edge] (YI) --node[] {} (VI0);
-
-	\draw[edge] (VII1) --node[] {} (UI1);
-	\draw[edge] (UI1) --node[] {} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-%This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-Due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
-
-\emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65,yscale=.7]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices are added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-%\pagebreak
-
-\section{Algorithms for \deltaExact}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-In the Appendix we give also a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following results.
-    \begin{observation}[$\star$]\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{observation}[$\star$]\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-\begin{lemma} [$\star$]\label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i}, \text{ for all $i \in \{2,3, \dots, k-1\}$.}
-    \end{equation}
-\end{lemma}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it follows that $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Moreover, all vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial-time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
-    If at this point we encounter a problem, our algorithm stops and returns a negative answer.
-
-    Let $V(G) = \{v_1, v_2, \dots, v_n\}$.
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    We repeat the above procedure from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}[$\star$]\label{thm:FPTwrtFES}
-    \deltaExact\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2,yscale=0.6]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph (with $\Delta \geq 9$), where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-%With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subparagraph{Preprocessing of the input.}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$, and denote with $k = |F|$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-%Note that $F$ is also a minimum feedback edge set of $G$.
-%Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$ and
-let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-\subparagraph{Guessing necessary structures. \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess $11$ different structures, we present here just a few of them, for all the others we refer the reader to the Appendix.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-
-    \setcounter{enumi}{3}
-
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-\end{enumerate}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential function).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subparagraph{Properties of \deltaExact.}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-	We want to determine labeling $\lambda$ of each edge of $G$.
-	We start with an empty labeling of edges and try to specify each one of them.
-	Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-    We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$. 
-	%In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
-	%In our analysis we exploit the following results greatly.
-    We are now ready, to present some basic properties of our problem.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-
-	\begin{observation}[$\star$]\label{obs:FirstLabelAndDuration}
-		Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-		Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-		Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-	\end{observation}
- If $\lambda(e_1)$ and $\lambda(e_p)$ (from the above observation) are both unknown, then we can determine one with respect to the other.
- %\begin{definition}\label{FPT:def-segment}
-%	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-%	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-%	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-%	Note $S_{u,v} \neq S_{v,u}$.
-%\end{definition}
-
-	\begin{lemma}[$\star$]\label{lemma:FPT-uv-LabelAlmostalledges}
-		Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-		is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-		Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-		We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-		such that the labeling $\lambda$ respects the values from $D$.
-		%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-	\end{lemma}
-    Note that in the case when path $P$ from $u$ to $v$ admits no extra vertices of interest, beside $u$ and $v$, then we can determine labels of all of its edges, with respect to the label of the first edge.
-    The procedure to determine the labeling relies on \cref{obs:FirstLabelAndDuration} (for details see Appendix).
-
-\subparagraph{Adding constraints and variables to the ILP.}
-%Using the above guessed structures, and certain properties of the problem, we proceed with adding constraints to each of our ILP instances.
-
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-To ensure this 
-we split the graph into $O(k^2)$ segments, and introduce at most $3$ variables for each segment,
-therefore each of our ILP instances admits $O(k^3)$ number of variables (for details see Appendix).
-
-We now describe how we add constraints to a specific path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative (for details see Appendix),
-which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-%We iterate through all pairs of vertices $x,y$ in $G$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint}, and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-%For each pair we argue how we determine these paths.
-We now present one example of how to determine the fastest temporal paths among a fixed pair of vertices, for all other cases we refer the reader to the Appendix.
-
-\emph{Fastest paths from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.}
-\begin{figure}[t]
-		\centering
-		%\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}[yscale=0.3]
-				%%%S_uv
-				\node[vert,label=above:$w {=} z_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$z_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$z_{r-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$z_r {=} z$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$u$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(v1) edge[dirwave] [out=290,in=160] (w) 
-				(v2) edge[diredge2] (v1);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(vp) edge[dirwave] [out=240,in=20] (w) 
-				(vp1) edge[diredge2] (vp);
-
-			\end{tikzpicture}%}
-		\caption{Example of a guess G-8, where we guessed the fastest paths of form $z_2 \rightarrow w \leadsto u$ (in blue) and $z_{r-1} \rightarrow z \leadsto u$ (in red), where $u$ is a vertex of interest and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-\label{fig:FPT-4casesGuess}}
-\end{figure}
-
-We want to determine the fastest path from $x$ to $u$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ be a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it (intuitively, these are the edges whose labels are not determined with respect to any other edge label), which means that all of the labels of edges in the segment $S_{w,z}$ are determined with respect to (at most) two different values $\lambda(e)$ and $\lambda(f)$, for some edges $e,f$ in $S_{w,z}$.
-For a detailed explanation see Appendix.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow w \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow z \leadsto u$.
-Note that we know these paths from the guess~G-8 (depicted in \cref{fig:FPT-4casesGuess}, for details see Appendix).
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{Solving ILP instances.}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-%Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labeling.
-
-\section{Conclusion}\label{sec:conclusion}
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-%\subparagraph{Further parameterizations.} 
-There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-We believe that the \emph{vertex cover number} or the \emph{tree depth} are promising candidates.
-Furthermore, we can consider combining a structural parameter such as the \emph{treewidth} with $\Delta$.
-
-%\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration. 
-%In the following, we give two specific examples. 
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
-
-\end{document}
+We show that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, while we show that it is in FPT when parameterized by the feedback edge number of the underlying graph.

### 2023-02-16 arxiv.tex
ArXiv version

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
 %This is a template for producing LIPIcs articles. 
@@
 
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
+\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
 
@@
 
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
+\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
+
+\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
+
+\author{Hendrik~Molter}{Department of Computer Science, Ben-Gurion~University~of~the~Negev, 
+Beer-Sheva, 
+Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1456/18, and the ERC, grant number 949707.}
+
+\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
+
+\authorrunning{Nina Klobas, George B.
 Mertzios, Hendrik Molter, and Paul G.
@@
 
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
 
@@
 
-%\nolinenumbers %uncomment to disable line numbering
+\nolinenumbers %uncomment to disable line numbering
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% APPENDIX
-\usepackage{fancyhdr}
-\setlength{\headheight}{30pt}
-\pagestyle{fancyplain} { % define first page header and footer
-% \fancyhead[L]{Course Report}
-\fancyhead[C]{\textbf{APPENDIX}}
-% \fancyhead[R]{\thepage of \pageref{LastPage}}
-% \fancyfoot[L]{Jinho Hwang}
-% \fancyfoot[C]{GWU}
-% \fancyfoot[R]{CS}
-}
-\fancyhf{}
-\renewcommand{\headrulewidth}{0pt} % remove header lines and reset formats
-\renewcommand{\footrulewidth}{0pt} % remove footer lines and reset formats
-
-% define the rest of pages header and footer
-% \fancyhead[L]{Course Report}
-\fancyhead[OC]{\huge \textbf{APPENDIX}}
-\fancyhead[EC]{\huge \textbf{APPENDIX}}
-% \fancyhead[R]{\thepage of \pageref{LastPage}}
-% \fancyfoot[L]{Jinho Hwang}
-\fancyfoot[OC]{\thepage}
-\fancyfoot[EC]{\thepage}
-% \fancyfoot[R]{CS}
 

### 2023-02-16 Figures/fig-NP-reduction.tex
arxiv figures working

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
-
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
-
-\usepackage{amsmath}
-%\let\proof\relax
-%\let\endproof\relax
-
-\sloppy
-
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{wrapfig} %wrap the text around the picture
-
-\usepackage{thmtools} 
-\usepackage{thm-restate}
-\usepackage{cite}
-
-\usepackage{caption} %for subfigure - join multiple figures and add captions
-\usepackage{subcaption}
-\usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
-\usepackage{mathtools} % write text [under]{over} arrow $\xrightarrow[\text{world}]{\text{hello}}$
-
-\usepackage{graphicx}
-\graphicspath{{Figures/}}
-
-\usepackage{tikz}
+% tikzpic.tex
+\documentclass[crop,tikz]{standalone}% 'crop' is the default for v1.0, before it was 'preview'
 
@@
 }
-
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
 \begin{tikzpicture}%[xscale=2]
@@
 \end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
-
 \end{document}

### 2023-02-16 Figures/fig-W1-reduction.tex
arxiv figures working

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
 	\begin{tikzpicture}[line width=1pt, scale=.65]
@@
 	\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-02-16 Figures/fig-lemma.tex
arxiv figures working

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
 	\begin{tikzpicture}[scale=.85]
@@
 	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-02-16 Figures/fig-motivationExample.tex
arxiv figures working

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
 \begin{tikzpicture}[xscale=2]
@@
 \end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-02-27 Arxiv-17-2-23/abstract.tex
arxiv version

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
-
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
-
-\usepackage{amsmath}
-%\let\proof\relax
-%\let\endproof\relax
-
-\sloppy
-
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{wrapfig} %wrap the text around the picture
-
-\usepackage{thmtools} 
-\usepackage{thm-restate}
-\usepackage{cite}
-
-\usepackage{caption} %for subfigure - join multiple figures and add captions
-\usepackage{subcaption}
-\usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
-\usepackage{mathtools} % write text [under]{over} arrow $\xrightarrow[\text{world}]{\text{hello}}$
-
-\usepackage{graphicx}
-\graphicspath{{Figures/}}
-
-\usepackage{tikz}
-
-\usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
-\usetikzlibrary{shapes,calc,patterns,arrows.meta}
-\tikzset{
-	vert/.style={circle,inner sep=1.5,fill=white,draw,minimum size=.3cm},
-	edge/.style={color=black, thick},
-	diredge/.style={->,>={Stealth[width=8pt,length=8pt]},color=black, thick},
-	timelabel/.style={fill=white,font=\footnotesize, text centered},
-	wave/.style={decorate,decoration={coil,aspect=0}},
-	dirwave/.style={->, >={Stealth[width=8pt,length=8pt]},decorate,decoration={coil,aspect=0}},
-	diredge2/.style={->,>={Stealth[width=8pt,length=8pt]}}
-}
-
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
+In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, while we focus on periodic temporal graphs.
+Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist.
 The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
 
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
+As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.
+non-temporal) counterpart.
 First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
@@
 We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
-
-\end{document}

### 2023-02-27 Arxiv-17-2-23/arxiv.tex
arxiv version

--- 2023-02-16 arxiv.tex
@@
 		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
+	\includegraphics{fig-NP-reduction}
 }
@@
 \centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
+\includegraphics{fig-W1-reduction}
     }
@@
 \centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
+
+\includegraphics{fig-W1-infinity}
     \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
@@
     \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
+	\includegraphics{fig-motivationExample}
 	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
@@
 		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
+		\includegraphics{fig-guess1}}
 	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
@@
 
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
+			\includegraphics{fig-guess2}}
 		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
@@
 				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
+				\includegraphics{fig-guess3}}
 			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
@@
 		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
+		\includegraphics{fig-guess4}}
 	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
@@
 	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
+	\includegraphics{fig-lemma}
 	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},

### 2023-03-21 New Paper/Realizing TG - extended.tex
New paper

--- 2023-02-09 ICALP23-shortversion.tex
@@
 \usepackage{caption} %for subfigure - join multiple figures and add captions
-%\usepackage{subcaption}
+\usepackage{subcaption}
 \usepackage{changepage} %inside figure we can put \begin{adjustwidth}{-1cm}{-1cm} \end{adjustwidth} and we can ignore the margins
@@
 \bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
+
 \title{Realizing temporal graphs from fastest travel times} %TODO Please add
@@
 \begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need, to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\section{Hardness results for \deltaExact}  
-In this section we present our main computational hardness results.  
-We first show that \deltaExact\ is NP-hard even for constant $\Delta$. 
-%Then we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-%\subparagraph{NP-hardness of \deltaExact.}\label{sec:nphardness}
-%We prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-%even if $\Delta$ is a small constant.
-
-\begin{theorem}[$\star$]\label{thm:NPhardness}
-	\deltaExact\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{comment}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
+\section{Ideas}
 \begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[htb]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. We defer the correctness proof to the appendix.
-\end{proof}
-
-\end{comment}
-
-%\subparagraph{Parameterized Hardness of \deltaExact.}\label{sec:w1hardness}
-
-Next, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest. The set $X$ is called a \emph{feedback vertex set}. 
-Note that, in contrast to the previous results (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}[$\star$]\label{thm:W1wrtFVS}
-    \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExact\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \emph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \emph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-\begin{comment}
-
-    \emph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
+    \item Symmetric distance matrix $D$: polytime?
+    \item Use $|D|_\infty$ (maximum value in $D$) + max degree $\Delta$ as parameter $\rightarrow$ should give FPT
+    \item FPT with feedback edge number
+    \item use as parameter $\max_{i,j} |D_{i,j}-D_{j,i}|$
+    \item approximation (additive or multiplicative), maybe with graph as input
 \end{itemize}
 
-\emph{Alignment Gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
+\problemdef{\kDeltaExactLong\ (\kDeltaExact)}
+{An $n \times n$ matrix $D$ of positive integers.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}^k$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is equal to $D_{i,j}$.}
 
-\end{comment}
+\problemdef{\kDeltaUpperBoundLong}
+{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{i,j}$.}
 
-Furthermore, we use \emph{connector gadgets}, two for each edge selection gadget, and two for every verification gadget.
-They consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and, intuitively, are used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Finally, we have an \emph{alignment gadget}, which is a star with a center vertex $w^\star$ and a leaf for every other gadget.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-A formal description of these two gadgets is given in the Appendix.
+\problemdef{\kDeltaLowerBoundLong}
+{An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}
+{Does there exist a graph $G=(V,E)$ on the vertices $\{v_1,\ldots,v_{n}\}$ with $n+k-1$ edges 
+and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at least} $D_{i,j}$.}
+\todo[inline]{NOT TEMPORALLY INTERESTING: the difficulty is to find a static graph with equal labels}
 
-This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-%\begin{itemize}
- %   \item 
-    vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    %\item 
-    vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    %\item 
-    vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    %\item 
-    vertex $w^\star$ of the alignment gadget
-%\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\begin{comment}
-\emph{Duration Matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\end{comment}
-
-\begin{figure}[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65, yscale=.6]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5.4) rectangle (10, 1.6) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1.4) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1.4) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-21.5) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[] {} (VS);
-	\draw[edge] (X2) --node[] {} (VS);
-	\draw[edge] (X3) --node[] {} (VS);
-	\draw[edge] (XM) --node[] {} (VS);
-
-    \draw[edge] (Y1) --node[] {} (VS);
-	\draw[edge] (Y2) --node[] {} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[] {} (VS);
-	\draw[edge] (YM) --node[] {} (VS);
-
-    \draw[edge] (Y1) --node[] {} (U11);
-	\draw[edge] (Y2) --node[] {} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[] {} (U13);
-	\draw[edge] (YM) --node[] {} (U1M);
-
-    \draw[edge] (U21) --node[] {} (U11);
-	\draw[edge] (U22) --node[] {} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[] {} (U13);
-	\draw[edge] (U2M) --node[] {} (U1M);
-
-    \draw[edge] (UN1) --node[] {} (UN11);
-	\draw[edge] (UN2) --node[] {} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[] {} (UN13);
-	\draw[edge] (UNM) --node[] {} (UN1M);
-
-    \draw[edge] (U2N1) --node[] {} (VSS);
-	\draw[edge] (U2N2) --node[] {} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[] {} (VSS);
-	\draw[edge] (U2NM) --node[] {} (VSS);
-
-    \draw[edge] (VH11) --node[] {} (VH12);
-	\draw[edge] (VH12) --node[] {} (VH111);
-	\draw[edge] (VH12) --node[] {} (VH13);
-    \draw[edge] (VH13) --node[] {} (VH14);
-	\draw[edge] (VH13) --node[] {} (VH144);
-
-    \draw[edge] (VH21) --node[] {} (VH22);
-	\draw[edge] (VH22) --node[] {} (VH211);
-	\draw[edge] (VH22) --node[] {} (VH23);
-    \draw[edge] (VH23) --node[] {} (VH24);
-	\draw[edge] (VH23) --node[] {} (VH244);
-
-    \draw[edge] (VH31) --node[] {} (VH32);
-	\draw[edge] (VH32) --node[] {} (VH311);
-	\draw[edge] (VH32) --node[] {} (VH33);
-    \draw[edge] (VH33) --node[] {} (VH34);	
-    \draw[edge] (VH33) --node[] {} (VH344);
-
-    \draw[edge] (VH41) --node[] {} (VH42);
-	\draw[edge] (VH42) --node[] {} (VH411);
-	\draw[edge] (VH42) --node[] {} (VH43);
-    \draw[edge] (VH43) --node[] {} (VH44);	
-    \draw[edge] (VH43) --node[] {} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[] {} (W1);
-	\draw[edge] (W) --node[] {} (W2);
-	\draw[edge] (W) --node[] {} (W3);
-	\draw[edge] (W) --node[] {} (W4);
-	\draw[edge] (W) --node[] {} (W5);
-	\draw[edge] (W) --node[] {} (W6);
-
-	\draw[edge] (X1) --node[] {} (W1);
-	\draw[edge] (VH11) --node[] {} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[] {} (W3);
-	\draw[edge] (VH31) --node[] {} (W4);
-	\draw[edge] (YI) --node[] {} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[] {} (W6);
-
-	\draw[edge] (YI) --node[] {} (VI0);
-
-	\draw[edge] (VII1) --node[] {} (UI1);
-	\draw[edge] (UI1) --node[] {} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-%This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-Due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
-
-\emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65,yscale=.7]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices are added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-%\pagebreak
-
-\section{Algorithms for \deltaExact}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-In the Appendix we give also a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following results.
-    \begin{observation}[$\star$]\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{observation}[$\star$]\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-\begin{lemma} [$\star$]\label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i}, \text{ for all $i \in \{2,3, \dots, k-1\}$.}
-    \end{equation}
-\end{lemma}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it follows that $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Moreover, all vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial-time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
-    If at this point we encounter a problem, our algorithm stops and returns a negative answer.
-
-    Let $V(G) = \{v_1, v_2, \dots, v_n\}$.
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    We repeat the above procedure from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}[$\star$]\label{thm:FPTwrtFES}
-    \deltaExact\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2,yscale=0.6]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph (with $\Delta \geq 9$), where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-%With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subparagraph{Preprocessing of the input.}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$, and denote with $k = |F|$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-%Note that $F$ is also a minimum feedback edge set of $G$.
-%Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$ and
-let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-\subparagraph{Guessing necessary structures. \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess $11$ different structures, we present here just a few of them, for all the others we refer the reader to the Appendix.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-
-    \setcounter{enumi}{3}
-
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-\end{enumerate}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential function).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subparagraph{Properties of \deltaExact.}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-	We want to determine labeling $\lambda$ of each edge of $G$.
-	We start with an empty labeling of edges and try to specify each one of them.
-	Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-    We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$. 
-	%In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
-	%In our analysis we exploit the following results greatly.
-    We are now ready, to present some basic properties of our problem.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-
-	\begin{observation}[$\star$]\label{obs:FirstLabelAndDuration}
-		Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-		Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-		Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-	\end{observation}
- If $\lambda(e_1)$ and $\lambda(e_p)$ (from the above observation) are both unknown, then we can determine one with respect to the other.
- %\begin{definition}\label{FPT:def-segment}
-%	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-%	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-%	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-%	Note $S_{u,v} \neq S_{v,u}$.
-%\end{definition}
-
-	\begin{lemma}[$\star$]\label{lemma:FPT-uv-LabelAlmostalledges}
-		Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-		is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-		Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-		We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-		such that the labeling $\lambda$ respects the values from $D$.
-		%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-	\end{lemma}
-    Note that in the case when path $P$ from $u$ to $v$ admits no extra vertices of interest, beside $u$ and $v$, then we can determine labels of all of its edges, with respect to the label of the first edge.
-    The procedure to determine the labeling relies on \cref{obs:FirstLabelAndDuration} (for details see Appendix).
-
-\subparagraph{Adding constraints and variables to the ILP.}
-%Using the above guessed structures, and certain properties of the problem, we proceed with adding constraints to each of our ILP instances.
-
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-To ensure this 
-we split the graph into $O(k^2)$ segments, and introduce at most $3$ variables for each segment,
-therefore each of our ILP instances admits $O(k^3)$ number of variables (for details see Appendix).
-
-We now describe how we add constraints to a specific path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative (for details see Appendix),
-which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-%We iterate through all pairs of vertices $x,y$ in $G$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint}, and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-%For each pair we argue how we determine these paths.
-We now present one example of how to determine the fastest temporal paths among a fixed pair of vertices, for all other cases we refer the reader to the Appendix.
-
-\emph{Fastest paths from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.}
-\begin{figure}[t]
-		\centering
-		%\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}[yscale=0.3]
-				%%%S_uv
-				\node[vert,label=above:$w {=} z_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$z_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$z_{r-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$z_r {=} z$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$u$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(v1) edge[dirwave] [out=290,in=160] (w) 
-				(v2) edge[diredge2] (v1);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(vp) edge[dirwave] [out=240,in=20] (w) 
-				(vp1) edge[diredge2] (vp);
-
-			\end{tikzpicture}%}
-		\caption{Example of a guess G-8, where we guessed the fastest paths of form $z_2 \rightarrow w \leadsto u$ (in blue) and $z_{r-1} \rightarrow z \leadsto u$ (in red), where $u$ is a vertex of interest and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-\label{fig:FPT-4casesGuess}}
-\end{figure}
-
-We want to determine the fastest path from $x$ to $u$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ be a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it (intuitively, these are the edges whose labels are not determined with respect to any other edge label), which means that all of the labels of edges in the segment $S_{w,z}$ are determined with respect to (at most) two different values $\lambda(e)$ and $\lambda(f)$, for some edges $e,f$ in $S_{w,z}$.
-For a detailed explanation see Appendix.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow w \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow z \leadsto u$.
-Note that we know these paths from the guess~G-8 (depicted in \cref{fig:FPT-4casesGuess}, for details see Appendix).
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{Solving ILP instances.}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-%Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labeling.
-
-\section{Conclusion}\label{sec:conclusion}
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-%\subparagraph{Further parameterizations.} 
-There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-We believe that the \emph{vertex cover number} or the \emph{tree depth} are promising candidates.
-Furthermore, we can consider combining a structural parameter such as the \emph{treewidth} with $\Delta$.
-
-%\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration. 
-%In the following, we give two specific examples. 
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
-
+\todo[inline]{The matrix $D$ is m x m, and capturing the distances from an edge e to an edge f (zoom 14 Nov 22, GH).}
+\todo[inline]{Check if the reduction works for the UPPER BOUNDED version (seems to work)}
+\todo[inline]{how to extend the poly algorithms of cycles? Easy candidate: FES, FVS, series-parallel graphs, or tw=2 graphs}
+\todo[inline]{FVS, $c$-factor approximation, hardness of approximation for $c<1.5$}
 \end{document}

### 2023-03-21 New Paper/Realizing TG - extended.tex
starting writing some basic observations

@@
 
+\usepackage{cleveref}
 \usepackage{amsthm}
@@
 
-\newcounter{guesscounter}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
@@
 \newcommand{\deltaExact}{\textsc{Simple TGR}}
+
+\newcommand{\deltaSymExactLong}{\textsc{Simple symmetric periodic Temporal Graph Realization}}
+\newcommand{\deltaSymExact}{\textsc{Simple Symmetric TGR}}
 
@@
 
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
+\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
 
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
+\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
 
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
+\author{Hendrik~Molter}{Department of Computer Science, Ben-Gurion~University~of~the~Negev, 
+	Beer-Sheva, 
+	Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1456/18, and the ERC, grant number 949707.}
 
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
+\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
 
-%\authorrunning{Nina Klobas, George B.
+\authorrunning{Nina Klobas, George B.
 Mertzios, Hendrik Molter, and Paul G.
@@
 \begin{document}
+	\maketitle
+
+\problemdef{\deltaSymExactLong\ (\deltaSymExact)}
+{An $n \times n$ symmetric matrix $D$, a positive integer $\Delta$.}
+{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
+	and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+	for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
+
+\problemdef{\kDeltaUpperBoundLong}
+{A static graph $G=(V,E)$ with $n$ vertices, $n \times n$ matrix $D$ of positive integers and a bijective mapping $\phi$ from vertices $V$ of $G$ to the rows/columns of the matrix $D$.}
+{Does there exist a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
+	for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is \emph{at most} $D_{\phi(i),\phi(j)}$.}
+
+\section{Preliminaries and notation}
+\todo[inline]{This section is copied from our paper}
+
+An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
+An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
+and a set~$E \subseteq V \times V$ of edges.
+For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
+We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
+For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
+A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
+(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
+
+Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
+For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
+$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
+
+We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
+
+We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
+Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
+which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
+
+\begin{definition}[Travel delays]
+	Let $(G, \lambda)$ be a $\Delta$-periodic temporal graph.
+	Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+	We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+	as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+	More specifically:
+	\begin{equation}\label{eq:def-VertexWaitingTime}
+		\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+	\end{equation}
+	Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+\end{definition}
+Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
+
+\section{D is symmetric}
+Before studying the problem in general let us first focus on two restricted cases.
+\begin{theorem}
+	If the input graph $G$ of \deltaSymExact\ is a clique or a $C_4$ then the problem is polynomial-time solvable. 
+\end{theorem}
+
+\begin{proof}
+	We split the proof in two cases.
+
+	First, when the input graph is a clique. In this case the desired labeling $\lambda$ can be arbitrary (i.e. $\lambda(e) \in [\Delta]$ for all $e \in E$), 
+	as all vertices are on distance (and duration) $1$ from each other.
+	Therefore 
+	\begin{equation*}
+		D_{i,j} =
+		\begin{cases}
+			0 & \text{if $i = j$}, \\
+			1 & \text{else}
+		\end{cases},
+	\end{equation*}
+	which is a symmetric matrix.
+
+	Second, when the input graph $G$ is a $C_4$. Let $v_1, v_2, v_3, v_4$ be the vertices of $G$ with edges $e_1 = v_1 v_2, e_2 = v_2 v_3, e_3 = v_3 v_4, e_4 = v_4 v_1$.
+	Now we set $\lambda(e_1) = \lambda (e_3) = \alpha$ and $\lambda(e_2) = \lambda(e_4) = \beta$, where w.l.o.g. $\alpha > \beta$.
+	Let $\gamma = min \{ \alpha - \beta, \Delta + \beta - \alpha\}$,
+	i.e. $\gamma$ is the minimum travel delay at vertex $v_i$ when traversing edges $e_{i-1}, e_i$, where indices are taken modulo $4$.
+	We get that 
+	\begin{equation*}
+		D_{i,j} =
+		\begin{cases}
+			0 & \text{if $i = j$}, \\
+			1 & \text{if $v_i$ and $v_j$ are neighbors},\\
+			\gamma + 1 & \text{else}\\
+		\end{cases}
+	\end{equation*}
+	Note, if $\alpha = \beta$ then the values in $D$ of non-neighboring vertices (i.e. vertices on distance $2$ from each other)
+	are exactly $\Delta + 1$.
+\end{proof}
+
+Observe the following.
+\begin{claim}
+	Let $P = (u, v, w)$ be a path of length $2$, and let $(P,\lambda)$ be a $\Delta$-periodic temporal graph,
+	 then $D_{u,w} = D_{w,v}$ iff $\tau_v^{uw} = \tau_v^{wu}$. 
+\end{claim}
+\begin{proof}
+	Let us denote with $\alpha = \lambda(uv)$ and  $\beta = \lambda(vw)$,
+	w.l.o.g. we suppose also that $\alpha > \beta$.
+	Then $d(u,w) = \Delta + \beta - \alpha + 1$ 
+	and $d(w,u) = \alpha - \beta + 1$.
+	By the definition of travel delays we get $d(u,w) = \tau_v^{uw} + 1$ and $d(w,u) = \tau_v^{wu} + 1$. 
+	Since $D_{u,w} = D_{w,v}$ we get that $\tau_v^{uw} = \tau_v^{wu}$.
+\end{proof}
+
+From the above claim we get the following.
+
+\begin{claim}
+	Let $P = (u, v, w)$ be a path of length $2$, and let $(P,\lambda)$ be a $\Delta$-periodic temporal graph, 
+	then $D_{u,w} = D_{w,v}$
+	iff
+	$\lambda(e) \in \{\frac{\Delta}{2}, \Delta\}$, if $\Delta$ is even and
+	$\lambda(e) \in \{\Delta\}$, if $\Delta$ is odd,
+	for all $e \in E(P)$.
+\end{claim}
+
+\begin{proof}
+		Let us denote with $\alpha = \lambda(uv)$ and  $\beta = \lambda(vw)$,
+		w.l.o.g. we suppose also that $\alpha > \beta$.
+		Since
+		$\tau_v^{uw} = \tau_v^{wu}$
+		we get that
+		\begin{equation*}
+			\Delta + \beta - \alpha \equiv \alpha - \beta \pmod\Delta,
+		\end{equation*}
+		which is equivalent to
+		\begin{equation}\label{eq:sol-delta}
+			\Delta  \equiv 2 (\alpha - \beta) \pmod\Delta.
+		\end{equation}
+		Since $\alpha > \beta$, the only possible solution of \cref{eq:sol-delta} is when $\beta \equiv \frac{\alpha}{2} \pmod \Delta$, which exists only in the case when $\Delta$ is even.
+		If we now allow $\alpha = \beta$ then we get another solution of \cref{eq:sol-delta}.
+
+		W.l.o.g. we can now suppose that $\alpha = \Delta$.
+		If $\Delta$ is odd, we have a unique solution with the value $\alpha=\beta = \Delta$,
+		while in the case when $\Delta$ is odd we get that $\alpha, \beta \in \{\Delta, \frac{\Delta}{2}\}$. 
+\end{proof}
+
+We can extend the above result to all graphs as we want to have a periodic labeling of a graph $G$, that gives rise to a symmetric matrix $D$. 
+Then the above has to hold for all pairs of vertices on distance $2$.
+Therefore we get the following two results.
+
+\begin{claim}\label{claim:symmetric-odd}
+	When $\Delta$ is odd, the only possibility of the matrix $D$, of all durations, being symmetric is when all labels of $G$ are the same.
+\end{claim}
+
+\begin{claim}\label{claim:symmetric-even}
+	When $\Delta$ is even, the only possibility of the matrix $D$, of all durations, being symmetric is when all labels of $G$ are from $\{\frac{\Delta}{2}, \Delta\}$.
+\end{claim}
+
+From all of the above we get the following result.
+\begin{theorem}
+	\deltaSymExact\ can be solved in polynomial time.
+\end{theorem}
+
+\begin{proof}
+	TODO
+\end{proof}
+
+\section{Upper bounds in the matrix D}
+
+\clearpage
+
 \section{Ideas}
@@
 \todo[inline]{FVS, $c$-factor approximation, hardness of approximation for $c<1.5$}
+
+\bibliography{../bibliography}	
 \end{document}

### 2023-03-21 arxiv.tex
starting writing some basic observations

@@
         &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
+        & = (t_2 - t_1) + (t_3 - t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
         & = t_{p-1} - t_1 + 1\\
@@
 and therefore are the fastest.
-Then $D$ is of the following form:
+Then $D$ is of the following fo\rm:
 \begin{equation*}

### 2023-03-22 Response.txt
starting response for rebuttal

We would like to thank the reviewers for their work and comments.

ANSWER TO REVIEWER 1:
The main issue the reviewer had was with the motivation of the problem. It is remarked that the idea of extending the problem from a static case to the temporal is not interesting enough on its own, while this is one of the main approaches in the field of temporal graphs - how to (in the most natural way) extend the problems from static graphs to temporal, and then study the complexity of derived problem(s).
We introduced the idea of periodic edges as this makes two vertices trivially connected, which makes the argument of finding a temporal path of fastest duration more interesting.
We believe the idea of realizing fastest temporal paths is the most natural as it is easy to calculate these values and therefore check if temporal graph is really 'good' (in the opposite to proposed "minimization of the maximum/average duration under some constraints").

Since we proved that the problem is NP-hard in general and polynomial-time solvable on trees, the next natural question is how can the tree-like structure help us with solving the problem exactly. We show that FPT is possible only in the case when parameter is FES (which we agree, it is not a 'good' parameter in practice), but we show that this is the smallest parameter that still gives us an FPT algorithm. In the case of parameterizing the problem already with the FVS we show that the problem is W[1]-hard. Therefore all other 'smaller' parameters, cannot give us an FPT result.

We thank the reviewer for suggesting the paper "Dynamic networks: models and algorithms" by Kuhn and Oshman, 
we will cite it in our final version.

ANSWER TO REVIEWER 2:
Definition 13 defines segments as paths between two vertices of interest. There cannot exist more than two segments among the same pair of vertices of interest (where one is just an edge). As two vertices of interest are the endpoints of one edge (from FES), therefore one segment is an edge and the other is the rest of the cycle. In the case when vertices of interest have degree > 2 then there is a unique segment among each pair of them.

ANSWER TO REVIEWER 3:
Each connector gadget contributes 2 vertices to the FVS. We will add the missing edges to the figure.
We will also define the MULTICOLORED CLIQUE problem, as suggested.

### 2023-03-24 Response.txt
Response for ICALP

@@
 ANSWER TO REVIEWER 1:
-The main issue the reviewer had was with the motivation of the problem.
-It is remarked that the idea of extending the problem from a static case to the temporal is not interesting enough on its own, while this is one of the main approaches in the field of temporal graphs - how to (in the most natural way) extend the problems from static graphs to temporal, and then study the complexity of derived problem(s).
-We introduced the idea of periodic edges as this makes two vertices trivially connected, which makes the argument of finding a temporal path of fastest duration more interesting.
-We believe the idea of realizing fastest temporal paths is the most natural as it is easy to calculate these values and therefore check if temporal graph is really 'good' (in the opposite to proposed "minimization of the maximum/average duration under some constraints").
+Regarding the movitation of periodicity: We want to point out that, since every edge having the same period is clearly a special case of every edge having *some* period, our hardness results also hold for the more general/realistic setting that the reviewer described.
+An even more general setting would be to allow more than one label per edge per periods (this can model different periods by taking the LCM of them as a global period).
+We propose this as a future research direction in the conclusion (lines 603-604).
+However, we believe that thoroughly understanding the fundamental case of having the same period and exactly one label per edge per period is vital before moving towards understanding more general/realistic settings.
 
-Since we proved that the problem is NP-hard in general and polynomial-time solvable on trees, the next natural question is how can the tree-like structure help us with solving the problem exactly.
-We show that FPT is possible only in the case when parameter is FES (which we agree, it is not a 'good' parameter in practice), but we show that this is the smallest parameter that still gives us an FPT algorithm.
-In the case of parameterizing the problem already with the FVS we show that the problem is W[1]-hard.
-Therefore all other 'smaller' parameters, cannot give us an FPT result.
+Regarding the motivation of considering durations: We agree that from the "design-perspective" many other properties to realize might be well-motivated, such as the ones proposed by the reviewer.
+However, from the "verification-perspective" (cf.
+lines 28-31) it is well-motivated that a matrix of e.g.
+measured duration-values is given, and we are asked to reconstruct the temporal network displaying exactly those durations.
 
-We thank the reviewer for suggesting the paper "Dynamic networks: models and algorithms" by Kuhn and Oshman, 
-we will cite it in our final version.
+Regarding the motivation of studying parameterized complexity: This is a canonical and well-established way to approach NP-hard problems when exact algorithms are desired.
+We did not study approximation because our problem does not have a canonical formulation as an optimization problem.
+What would be the objective function?
+If we want to get the durations as close as possible to the ones prescribed in the matrix, it opens new questions such as e.g.
+"How many edges are we allowed to put into the graph?".
+Since this is a study of a new problem, we believe it is natural to initially focus on exact algorithms.
+
+Since we identified a restricted setting (where the underlying graph is a forest) in which our problem is solvable in polynomial time, it is natural to explore how this algorithm generalizes.
+This polynomial-time solvable special case of trees gives a strong (theoretical) motivation to study parameters that measure "tree-likeness".
+From a practical standpoint, for many real-world networks it is well-motivated to assume that they are very structured, which motivates the study of structural graph parameters.
+Tree-likeness is a fairly common assumption, in particular for transportation networks (see e.g.
+reference [19]).
+
+Note that our main parameterized hardness result (Theorem 4) rules out the possibility of obtaining FPT algorithms for many structural graph parameters, and not only for the ones that measure tree-likeness.
+So the question rather becomes "Which structural properties of the underlying graph allow for efficient algorithms?".
+Note that e.g.
+the arboricity can be upper-bounded by a function of the feedback vertex number, and hence we cannot expect to obtain fixed-parameter tractability for this parameter.
+Note that also parameters that can be small in dense graphs, such as the cliquewidth or the vertex-deletion-distance to chordal graphs, can be upper-bounded by a function of the feedback vertex number.
+Hence, we do have a strong (theoretical) justification for obtaining fixed-parameter tractability with the feedback edge number (although it is a rather large parameter), because we can rule out fixed-parameter tractability for most smaller parameters (as discussed e.g.
+in lines 363-364).
+We indeed leave the parameterized complexity wrt.
+pathwidth open, and in the conclusion of the full version we suggest studying this (see appendix lines 2198-2199).
+
+We thank the reviewer for pointing us towards "dynamic graphs" and we will add a discussion about this to the related work section.
+However, this is a related but *different* mathematical model.
+Note that we explicitly construct a (periodic) temporal graph, that is, the mathematical object contains all information about how the graph changes (deterministically).
+In dynamic graphs, as described in the work "Dynamic networks: models and algorithms" by Kuhn and Oshman, the assumption is that the changes are adversarial or random (while obeying some constraints such as connectivity) and not necessarily known in advance.
 
 ANSWER TO REVIEWER 2:
+We made great effort to provide intuitive explanations of the main ideas and techniques we use, as well as some technical details that convey an intuition about the remaining steps necessary to complete the proofs (which are given in the appendix).
+We believe that our work is relevant to a larger audience as it initiates the research of a well-motivated new problem setting and generates several future research directions.
+We see much potential for positive results.
+
 Definition 13 defines segments as paths between two vertices of interest.
-There cannot exist more than two segments among the same pair of vertices of interest (where one is just an edge).
-As two vertices of interest are the endpoints of one edge (from FES), therefore one segment is an edge and the other is the rest of the cycle.
-In the case when vertices of interest have degree > 2 then there is a unique segment among each pair of them.
+Indeed, these path segments should be non-trivial (i.e.
+they must have at least two edges), we will clarify this in teh final version.
+If there were two (non-trivial) segments between two vertices of interest, then there would be a cycle which contains a feedback edge.
+It follows that one of the segments must contain a further vertex of interest, which is not allowed by the definition.
 
 ANSWER TO REVIEWER 3:
-Each connector gadget contributes 2 vertices to the FVS. We will add the missing edges to the figure.
-We will also define the MULTICOLORED CLIQUE problem, as suggested.
+Each connector gadget contributes 2 vertices to the FVS, since many other vertices are connected to \hat{v}_1 and \hat{v}_2.
+The edges are omitted from the picture to avoid cluttering.
+We will add indications of the missing edges to the figure and clarify this in the figure caption.
+
+We provide a definition of the problem MULTICOLORED CLIQUE in lines 187-188.

### 2023-04-12 New Paper/Realizing TG - extended.tex
Added algorithm for D upper bounds for paths - as discussed with George and Paul on 11th of April

@@
 %% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
+\newcommand{\DeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
+\newcommand{\deltaUpperBound}{\textsc{Simple Upper-Bounded TGR}}
 
@@
 
-\problemdef{\kDeltaUpperBoundLong}
+\problemdef{\DeltaUpperBoundLong}
 {A static graph $G=(V,E)$ with $n$ vertices, $n \times n$ matrix $D$ of positive integers and a bijective mapping $\phi$ from vertices $V$ of $G$ to the rows/columns of the matrix $D$.}
@@
 \section{Upper bounds in the matrix D}
+We start by investigating the hardness of the problem on paths.
+We first reduce the input matrix $D$, by performing a series of modifications.
+
+Denote with $P = (v_1, v_2, \dots, v_n)$ a path on $n$ vertices,
+and let $D$ be the duration matrix with upper bounds.
+For any two vertices $v_i, v_j$ from $P$ we get that:
+\begin{itemize}
+	\item if the value of $D_{i,j} < D_{i,k}$, where $k \in [1+1,j-1]$
+	we set $D_{i,k} = D_{i,j}$.
+\end{itemize}
+%
+By the definition of temporal paths, it follows that $d(i,j) = d(i,k) + d(k-1, j) - 1$, where $i,j \in [n]$, with $i<j$ and $k \in [i+1,j-1]$.
+Therefore,
+\begin{itemize}
+	\item if $D_{i,j} > D_{i,k} + D_{k-1,j} -1$ we set the value of $D_{i,j}$ to $D_{i,k} + D_{k-1,j} -1$. 
+\end{itemize}
+%
+And lastly, to any $i$-th row of the matrix $D$, we make the following modifications:
+\begin{itemize}
+	\item if there are two entries $j< k$ with the same values, \ie $D_{i,j} = D_{i,k}$ where both $j,k$ are bigger than $i$ (resp.~smaller than $i$),
+	then we set $D_{i,j} = D_{i,k} - (k-j)$ (resp.~ $D_{i,k} = D_{i,j} - (k-j)$).
+\end{itemize}
+We iteratively repeat all of the above steps and produce a reduce matrix $D'$.
+It is easy to see that if there exists a labeling of $P$ for $D'$, then this labeling satisfies also $D$.
+
+\begin{theorem}
+	\deltaUpperBound\ can be solved in polynomial time on paths.
+\end{theorem}
+
+\begin{proof}[Proof idea:]
+	Let $P = (v_1, v_2, \dots, v_n)$ be a path on $n$ vertices.
+	For the sake of simplicity we denote with $a_i$ label of edge $e_i =v_iv_{i+1}$, for all $i \in [n-1]$.
+	By the definition, for any two vertices $v_i,v_j \in P$, we have the following inequality:
+	\begin{equation*}
+		(a_{i+1} - a_i)_\Delta + (a_{i+2} - a_{i+1})_\Delta + \cdots + (a_{j-1} - a_{j-2})_\Delta + 1
+		\leq D_{i,j}.
+	\end{equation*}
+	For the sake of simplicity we refer to the inequality that a temporal path from $v_i$ to $v_j$ has to respect (\ie~the above inequality) 
+	as $I_{i,j}$.
+	Note that we can rewrite the inequality $I_{i,j}$ also without the modulo $\Delta$ part as:
+	\begin{equation*}
+		k_{i+1,i} \Delta + (a_{i+1} - a_i)+ k_{i+2,i+1} \Delta + (a_{i+2} - a_{i+1}) + \cdots + k_{j-1,j-2} \Delta + (a_{j-1} - a_{j-2})+ 1
+		\leq D_{i,j},
+	\end{equation*}
+	where all $k_{i,i+1} \in \{0,1\}$.
+
+	W.l.o.g. we can assume also that $a_i \neq a_{i+1}$ for all $i \in [n-1]$,
+	this follows from the fact that the duration among two vertices $v_i, v_{i+2}$ on distance $2$ in $P$ equals to $\Delta + 1$ when the two consecutive labels are the same, but if the labels are not the same, the duration can be at most $\Delta$, which still satisfies the condition from before.
+	Therefore, for any two consecutive labels $a_i$ and $a_{i+1}$ (\ie for any two vertices $v_i, v_{i+2}$ on distance $2$ in $P$), 
+	it follows that 
+	$k_{i, i+1} = 1 - k_{i+1,i}$, where $k_{i+1,i} \in \{0,1\}$, which makes also $k_{i,i+1} \in \{0,1\}$, as required.
+	If we now sum up the two inequalities $I_{i,i+2}, I_{i+2,i}$ we get the following:
+	\begin{equation*}
+		(a_i-a_{i+1})_\Delta + (a_{i+1}-a_i)_\Delta +1 +1 = \Delta + 2.
+	\end{equation*}
+	It follows that for any two vertices $v_i, v_j$ in $P$, that are on distance $k$ apart, 
+	we get that $d(i,j) + d(j,i) = (k-1) \Delta + 2$.
+
+	To satisfy the inequalities $I_{1,n}$ and $I_{n,1}$ we have to correctly determine which of $k_{i+1,i}$ have value $1$, and consequently set $k_{i,i+1} = 0$,
+	and vice versa.
+
+	From the value $D_{1,n}$ (resp.~$D_{n,1}$) we can determine how many of $k_{i+1,i}$ (resp.$k_{i,i+1}$) can be non-zero. Suppose that there are $m$ non-zero ones (resp.~$n-m-1$).
+	Then to determine which $m$ of the $k_{i,i+1}$ are non-zero we look at every two vertices $v_i, v_{i+2}$ at the distance $2$ in $P$ 
+	and based on the inequalities $I_{i,i+2}, I_{i+2,i}$ determine if $k_{i+1,i}$ has a value $1$ or $0$,
+	i.e.~if $e_{i+1}$ is bigger or smaller than $e_i$.
+	We start determining the values $k_{i+1,i}$ from ``left to right'' (i.e~first we determine $k_{2,1}$, then $k_{3,2}$, \dots, and at last $k_{i-1,i-2}$).
+	Now that the relations of every two consecutive labels of $P$ are determined, 
+	we select the values for each label, such that the inequalities among them hold.
+	\begin{claim}
+		The above procedure produces a labeling of $P$ that satisfies durations from $D$.
+	\end{claim}
+\end{proof}
 
@@
 
-\problemdef{\kDeltaUpperBoundLong}
+\problemdef{\DeltaUpperBoundLong}
 {An $n \times n$ matrix $D$ of positive integers and an integer $k\in \mathbb{N}$.}

### 2023-04-24 MFCS23/MFCS23-shortversion.tex
MFCS short version

--- 2023-02-09 ICALP23-shortversion.tex
@@
     \emph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
+Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{Yes}-instances much easier.
 Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
@@
 The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-
-\end{comment}
-
-Furthermore, we use \emph{connector gadgets}, two for each edge selection gadget, and two for every verification gadget.
-They consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and, intuitively, are used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Finally, we have an \emph{alignment gadget}, which is a star with a center vertex $w^\star$ and a leaf for every other gadget.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-A formal description of these two gadgets is given in the Appendix.
-
-This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-%\begin{itemize}
- %   \item 
-    vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    %\item 
-    vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    %\item 
-    vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    %\item 
-    vertex $w^\star$ of the alignment gadget
-%\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\begin{comment}
-\emph{Duration Matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
 
@@
 
+Furthermore, we use \emph{connector gadgets}, two for each edge selection gadget, and two for every verification gadget.
+They consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and, intuitively, are used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{Yes}-instances much easier.
+Finally, we have an \emph{alignment gadget}, which is a star with a center vertex $w^\star$ and a leaf for every other gadget.
+Intuitively, this gadget is used to relate labels of different gadgets to each other.
+A formal description of these two gadgets is given in the Appendix.
+
+This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
+%\begin{itemize}
+ %   \item 
+    vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
+    %\item 
+    vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
+    %\item 
+    vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
+    %\item 
+    vertex $w^\star$ of the alignment gadget
+%\end{itemize}
+forms a feedback vertex set in $G$ with size $O(k^2)$.
+
+\begin{comment}
+\emph{Duration Matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
+For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
+For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
+
+Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
+Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
+We set the following durations.
+Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
+\begin{itemize}
+    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
+    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
+    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
+    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
+\end{itemize}
+Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
+\begin{itemize}
+    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
+    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
+    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
+    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
+\end{itemize}
+
+Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
+\begin{itemize}
+    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
+    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
+\end{itemize}
+
+Next, consider the validation gadget for color $i$. 
+%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
+%\begin{itemize}
+    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
+    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
+%\end{itemize}
+%
+For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
+\end{itemize}
+%The next cases are only relevant if $1\neq i \neq k$. 
+%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
+%\begin{itemize}
+%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
+%\end{itemize}
+%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
+%\begin{itemize}
+%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
+%\end{itemize}
+For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
+\begin{itemize}
+    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
+\end{itemize}
+%For all 
+%$\ell\in[n+3]$ and 
+%$i<j\le k$ we set the following.
+%\begin{itemize}
+%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
+%\end{itemize}
+
+Finally, we consider the alignment gadget.
+Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
+Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
+Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
+\begin{itemize}
+    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
+    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
+\end{itemize}
+
+Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
+Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
+Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
+Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
+\begin{itemize}
+    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
+    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
+    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
+\end{itemize}
+Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
+
+All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
+
+\end{comment}
+
 %This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
@@
     More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
+    %\begin{equation}\label{eq:def-VertexWaitingTime}
+       $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.$
+    %\end{equation}
     %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
@@
     Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i}, \text{ for all $i \in \{2,3, \dots, k-1\}$.}
-    \end{equation}
+    %\begin{equation}\label{eq:trav-delays-paths}
+        $\tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},$ for all $i \in \{2,3, \dots, k-1\}$.
+    %\end{equation}
 \end{lemma}
@@
 Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+\begin{comment}
 Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
@@
 where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
+\end{comment}
 
@@
 \begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
+    Let $D$ be an input matrix of \deltaExact\ with dimension $n \times n$.
     In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
-    If at this point we encounter a problem, our algorithm stops and returns a negative answer.
+    %If at this point we encounter a problem, our algorithm stops and returns a negative answer.
 
@@
     We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate waiting times at all inner vertices.
+    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate travel delays at all inner vertices.
     We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    We repeat the above procedure from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
+    Matrix $T$ stores at the position $(k,j,\ell)$ the value  $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
+    We repeat the above procedure from vertex $v_i$, for vertices $v_{j'}$ that are not marked as visited yet.
     When we have exhausted the $i$-th row of $D$,
@@
     we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
+    If at any point we get two different numerical values for the same entry of $T$ we stop and return the negative answer.
     The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
@@
     \end{claim}
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
+    Given the matrix $T$, we can easily determine a labeling $\lambda$ that satisfies $D$.
     We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+    Knowing the label of one edge, and all waiting times in $T$, we uniquely determine the labels of all other edges.
     More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
     the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+    Since there are $\Delta$ options to fix the first label, there are $\Delta$ different labelings satisfying $D$.
     %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
+    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time.
+    %as we have to traverse the graph exactly once, to successfully fix the labeling. 
     Therefore, all together the whole algorithm is performed in polynomial time.
@@
 The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
+Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$.%, \ie $F = E(G) \setminus E(T)$.
 
@@
 
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
+For the remainder of this section, let $D$ be the input matrix of \deltaExact\, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
 %With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
 We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
+We start with a preprocessing procedure for $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
 Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
@@
 \subparagraph{Preprocessing of the input.}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$, and denote with $k = |F|$.
+From $G$ we create $G'$ by
+iteratively removing vertices of degree one. With $Z$ we denote the set of all removed vertices.
 %by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
@@
 %Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$ and
-let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
+Let $T$ be a spanning tree of $G'$, that gives rise to a minimum feedback edge set $F$ (denote $k = |F|$), 
+and
+let $V_1 \subset V(G')$ be the set of leaves in $T$, $V_2 \subset V(G')$ the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
 and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
@@
 We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
+$
+U = V_1 \cup V_2 \cup V_3
+$
 the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
 We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
+$
+U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.
+$
 Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
+Note that determining all of the above sets takes linear time.
+
+\begin{comment}
+From the construction it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
 For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
@@
 where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
+$
 Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
+$
 Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
 Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time. 
-
+\end{comment}
 \subparagraph{Guessing necessary structures. \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
+Once the sets $U, U^*$ %and $Z^*$ 
+are determined, we are ready to start guessing  the necessary structures.
 Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes to $v$ via an edge (or a unique path), we write it as a fastest path of form $u \leadsto x \rightarrow v$.
+%Similarly it holds if we want to include more vertices that have to be visited by the path. 
+%If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$, if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
 We guess $11$ different structures, we present here just a few of them, for all the others we refer the reader to the Appendix.
@@
     For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
+    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path, respecting the value from $D$.
     %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
+    Repeating this procedure for all pairs $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ variations of the fastest temporal paths among all vertices in $U$.
+
+    %\item \label{FPT-guessFTPamongZstar}
+    %The fastest temporal paths among all vertices in $Z^*$, which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
+
+    %\item \label{FPT-guessFTPamongUstar}
+    %The fastest temporal paths among all vertices in $U^*$. This gives us $O(k^{k^6})$ guesses.
 
@@
 We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
+We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^4})$ new ones, that respond to the guessing in the next step, etc.
 After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential function).
@@
     Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
+    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in $G'$, of length at least $2$, where $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
     is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
@@
 		Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-		Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
+		Symmetrically, knowing $\lambda(e_p)$ and $d(P,\lambda)$, we can uniquely determine $\lambda(e_1)$.
 	\end{observation}
@@
 	\end{lemma}
+\begin{comment}
     Note that in the case when path $P$ from $u$ to $v$ admits no extra vertices of interest, beside $u$ and $v$, then we can determine labels of all of its edges, with respect to the label of the first edge.
     The procedure to determine the labeling relies on \cref{obs:FirstLabelAndDuration} (for details see Appendix).
+\end{comment}
 
@@
 
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
+%Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
+In order to find a labeling $\lambda$ satisfyinf $D$ 
+%that satisfies this property 
+we split our analysis in nine cases.
 We consider fastest temporal paths 
@@
 therefore each of our ILP instances admits $O(k^3)$ number of variables (for details see Appendix).
-
+%
+\begin{comment}
 We now describe how we add constraints to a specific path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
@@
 %For each pair we argue how we determine these paths.
+\end{comment}
+%
 We now present one example of how to determine the fastest temporal paths among a fixed pair of vertices, for all other cases we refer the reader to the Appendix.
@@
 
-We want to determine the fastest path from $x$ to $u$.
+%We want to determine the fastest path from $x$ to $u$.
 %We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
+\noindent
 Let $x$ be a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
@@
 %
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
+If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$. 
+%(\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
 If there is at least one $I$ that has a valid solution, 
 we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
+\begin{comment}
 We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
 Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
+%This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$, and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$, for all pairs of vertices $u,v$.
 Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
@@
 Therefore, we easily calculate the desired labeling.
+\end{comment}
 

### 2023-04-26 MFCS23/MFCS23-shortversion.tex
MFCS

@@
 The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
+The motivation for graph realization problems stems both from ``verification'' and from network design applications in engineering. 
+In \emph{verification} applications, given the outcomes of some experimental measurements (resp.~some computations) on a network, 
+the aim is to (re)construct an input network which complies with them. 
+If such a reconstruction is not possible, this proves that the measurements are incorrect or implausible (resp.~that the algorithm which made the computations is incorrectly implemented). 
+One example of a graph realization (or reconstruction) problem is the recognition of probe interval graphs, in the context of the physical mapping of DNA, see~\cite{McMorris98,McConnellS02} and~\cite[Chapter 4]{GolumbicTrenk04}.
+In \emph{network design} applications, the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
 Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
+Among the most studied such parameters for graph realization 
 are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
@@
 If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
+Non-trivial variations of this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
 Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
@@
 
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
+In this paper we consider \emph{periodic} temporal graphs, i.e.~temporal graphs in which the temporal availability of each edge of the underlying graph is periodic. 
+Many natural and technological systems exhibit a periodic temporal behavior. For example, in railway networks an edge is present at a time step $t$ if and
+only if a train is scheduled to run on the respective rail segment at time $t$~\cite{Arrighi2023Multi}. 
+Similarly, a satellite, which makes pre-determined periodic movements, can establish a communication link (i.e.~a temporal edge) with another satellite whenever they are sufficiently close to each other; the existence of these communication links is also periodic.
+In a railway (resp.~satellite) network, a fastest temporal path from $u$ to $v$ represents the fastest railway connection between two stations 
+(resp.~the quickest communication delay between two moving satellites). 
+Furthermore, periodicity appears also in (the otherwise quite complex) social networks which describe the dynamics of people meeting~\cite{snapnets,sapiezynski2015tracking}, as every person individually follows mostly a daily routine~\cite{Arrighi2023Multi}.
+
+Although periodic temporal graphs have already been studied 
+(see~\cite[Class 8]{casteigts2012time} and~\cite{Arrighi2023Multi,ErlebachS20,morawietz2021timecop,morawietz2020timecop}), 
+we make here the first attempt to understand the complexity of a graph realization problem in the context of temporal graphs. 
+Therefore, we focus in this paper on the most fundamental case, where all edges have the same period $\Delta$ 
+(while in the more general case, each edge $e$ in the underlying graph has a period $\Delta_e$).
+As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
+
+%In an arbitrary (non-periodic) temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected.
+
+%In order to focus on the smallest duration of temporal paths, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
+
+%Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
 For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
 
@@
 %In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
+We initiate the study of naturally motivated graph realization problems in the temporal setting. 
+Our target is not to model unreliable communication, but instead to \emph{verify} that particular measurements regarding fastest temporal paths in a periodic temporal graph are plausible (i.e.~``realizable'').
+To this end, we introduce and investigate the following problem, capturing the setting described above:
 
@@
 
+We focus on exact algorithms.
 We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
@@
 The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number $k$ of the underlying graph (\cref{thm:FPTwrtFES}). 
+Note that our parameterized hardness result rule out fixed-parameter tractability for several popular graph parameters such as treewidth and arboricity.
+
+We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number $k$ of the underlying graph (\cref{thm:FPTwrtFES}), a parameter that is larger than the feedback vertex number.
 Our FPT algorithm works as follows on a high level. 
 First we distinguish $O(k)$ vertices which we call ``interesting vertices''. 
-Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of $k$. 
+Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of~$k$. 
 Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (i.e.~bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
-For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than $D_{i,j}$.
+For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than~$D_{i,j}$.
 This naturally leads us to build one Integer Linear Program (ILP) for each of these configurations.
@@
 \subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction. 
-
 To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
@@
 
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
+There are some problem settings that share similarities with ours, which we discuss now in more detail.
 
@@
 Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
+In all these cases, the duration of the temporal paths has not been considered.
+
+%work on the temporal cops and robber game~\cite{morawietz2021timecop,morawietz2020timecop,ErlebachS20}.
 The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
+Several other works on periodic temporal graphs were mentioned in the introduction.
+
+Finally, there are many models for dynamic networks in the context of distributed computing~\cite{Kuhn2011Dynamic}. 
+These models have some similarity to temporal graphs, in the sense that in both cases the edges appear and disappear over time. 
+However, there are notable differences. For example, one important assumption in the distributed setting 
+can be that the edge changes are adversarial or random (while obeying some constraints such as connectivity), 
+and therefore they are not necessarily known in advance~\cite{Kuhn2011Dynamic}.
 
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \noindent\makebox[\textwidth]{
@@
 %\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65, yscale=.6]
+\begin{tikzpicture}[line width=1pt, scale=.65, yscale=.7]
 \scriptsize
@@
 
-	\draw[edge, line width=1.5pt] (X1) --node[] {} (VS);
+	\draw[edge] (X1) --node[] {} (VS);
 	\draw[edge] (X2) --node[] {} (VS);
@@
 	\draw[edge] (Y2) --node[] {} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[] {} (VS);
+	\draw[edge] (Y3) --node[] {} (VS);
 	\draw[edge] (YM) --node[] {} (VS);
@@
 	\draw[edge] (Y2) --node[] {} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[] {} (U13);
+	\draw[edge] (Y3) --node[] {} (U13);
 	\draw[edge] (YM) --node[] {} (U1M);
@@
 	\draw[edge] (U22) --node[] {} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[] {} (U13);
+	\draw[edge] (U23) --node[] {} (U13);
 	\draw[edge] (U2M) --node[] {} (U1M);
@@
 	\draw[edge] (UN2) --node[] {} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[] {} (UN13);
+	\draw[edge] (UN3) --node[] {} (UN13);
 	\draw[edge] (UNM) --node[] {} (UN1M);
@@
 	\draw[edge] (U2N2) --node[] {} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[] {} (VSS);
+	\draw[edge] (U2N3) --node[] {} (VSS);
 	\draw[edge] (U2NM) --node[] {} (VSS);
@@
     }
-    \caption{Illustration of part of the underlying graph $G$. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
+    \caption{Illustration of part of the underlying graph $G$. Edges incident with vertices $\hat{v}_1,\hat{v}_2$ of connector gadgets are omitted. Gray vertices form a feedback vertex set.
     The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
@@
 Due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
-
+%
+\begin{comment}
 \emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
@@
 We can conclude that the originally constructed instance $D$ is a \textsc{Yes}-instance if and only if it remains a \textsc{Yes}-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
+\end{comment}
 \end{proof}
@@
 By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
+%
+The first case, when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, we get the following result.
+
+\begin{theorem}[$\star$]\label{thm:deltaExact-PolyTimeTrees}
+    \deltaExact\ can be solved in polynomial-time on trees.
+\end{theorem}
+
+%We first show %in \cref{sec:treealgo} 
+%that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time. 
+In the case when the underlying graph is unrestricted, we show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
 Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
@@
 
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    %\begin{equation}\label{eq:def-VertexWaitingTime}
-       $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.$
-    %\end{equation}
-    %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following results.
-    \begin{observation}[$\star$]\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{observation}[$\star$]\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-\begin{lemma} [$\star$]\label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    %\begin{equation}\label{eq:trav-delays-paths}
-        $\tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},$ for all $i \in \{2,3, \dots, k-1\}$.
-    %\end{equation}
-\end{lemma}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-\begin{comment}
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-\end{comment}
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it follows that $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Moreover, all vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial-time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix of \deltaExact\ with dimension $n \times n$.
-    In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
-    %If at this point we encounter a problem, our algorithm stops and returns a negative answer.
-
-    Let $V(G) = \{v_1, v_2, \dots, v_n\}$.
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate travel delays at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value  $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    We repeat the above procedure from vertex $v_i$, for vertices $v_{j'}$ that are not marked as visited yet.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different numerical values for the same entry of $T$ we stop and return the negative answer.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    Given the matrix $T$, we can easily determine a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, there are $\Delta$ different labelings satisfying $D$.
-    %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time.
-    %as we have to traverse the graph exactly once, to successfully fix the labeling. 
-    Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
+% \subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
+% We first start with defining certain notions, that will be of use when solving the problem.
+
+%     \begin{definition}[Travel delays]
+%     Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
+%     Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+%     We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+%     as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+%     More specifically:
+%     %\begin{equation}\label{eq:def-VertexWaitingTime}
+%        $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.$
+%     %\end{equation}
+%     %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+%     \end{definition}
+%     Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
+%     From the above definition and the definition of the duration of the temporal path $P$ we get the following results.
+%     \begin{observation}[$\star$]\label{obs:durationPwithWaitingTimes}
+%         Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
+%         $(P, \lambda)$ from $v_0$ to $v_p$.
+%         Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
+%     \end{observation}
+%     \begin{observation}[$\star$]\label{obs:travel-delays-both-directions}
+%     Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
+%     For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+%     \end{observation}
+% \begin{lemma} [$\star$]\label{lemma:unique-fastest-path-allDelays}
+%     Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
+%     and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+%     Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
+%     Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
+%     Then we can determine travel delays on vertices of $P$ using the following equation
+%     %\begin{equation}\label{eq:trav-delays-paths}
+%         $\tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},$ for all $i \in \{2,3, \dots, k-1\}$.
+%     %\end{equation}
+% \end{lemma}
+% %All of the above is used in the design of the following polynomial-time algorithms.
+% We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
+% Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+% \begin{comment}
+% Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
+% Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
+% and therefore are the fastest.
+% Then $D$ is of the following form:
+% \begin{equation*}
+%     D_{i,j} =
+%     \begin{cases}
+%     0 & \text{if $i = j$}, \\
+%     1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
+%     d(P_{i,j},\lambda) & \text{else}
+%     \end{cases},
+% \end{equation*}
+% where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
+% \end{comment}
+
+% \begin{observation}\label{obs:travel-delays-in-trees}
+%     Let $v_i,v_j$  be arbitrary vertices in a tree $G$. 
+%     Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it follows that $d(P_{i,j},\lambda) = D_{i,j}$. 
+%     Moreover, all vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
+% \end{observation}
+
+%We start by providing a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
+
+%\begin{theorem}[$\star$]\label{thm:deltaExact-PolyTimeTrees}
+%    \deltaExact\ can be solved in polynomial-time on trees.
+%\end{theorem}
+
+% \begin{proof}
+%     Let $D$ be an input matrix of \deltaExact\ with dimension $n \times n$.
+%     In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
+%     %If at this point we encounter a problem, our algorithm stops and returns a negative answer.
+
+%     Let $V(G) = \{v_1, v_2, \dots, v_n\}$.
+%     We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
+%     We now take the unique path $P_{i,j}$ in $G$, 
+%     which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate travel delays at all inner vertices.
+%     We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
+%     Matrix $T$ stores at the position $(k,j,\ell)$ the value  $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
+%     We repeat the above procedure from vertex $v_i$, for vertices $v_{j'}$ that are not marked as visited yet.
+%     When we have exhausted the $i$-th row of $D$,
+%     \ie vertex $v_i$ now reaches every vertex of $G$,
+%     we continue and repeat the procedure for all other vertices.
+%     If at any point we get two different numerical values for the same entry of $T$ we stop and return the negative answer.
+%     The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
+%     \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
+%         Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
+%     \end{claim}
+%     Given the matrix $T$, we can easily determine a labeling $\lambda$ that satisfies $D$.
+%     We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
+%     Knowing the label of one edge, and all waiting times in $T$, we uniquely determine the labels of all other edges.
+%     More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+%     the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+%     Since there are $\Delta$ options to fix the first label, there are $\Delta$ different labelings satisfying $D$.
+%     %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+%     It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time.
+%     %as we have to traverse the graph exactly once, to successfully fix the labeling. 
+%     Therefore, all together the whole algorithm is performed in polynomial time.
+% \end{proof}
 
@@
 
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
+In this section we show how to generalize the polynomial-time algorithm for trees.
 Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
@@
     \centering
-	\begin{tikzpicture}[xscale=2,yscale=0.6]
+	\begin{tikzpicture}[xscale=2,yscale=0.4]
 	%%%S_uv
@@
 %If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$, if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess $11$ different structures, we present here just a few of them, for all the others we refer the reader to the Appendix.
+We guess $11$ different structures $G-1,G-2,\dots,G-11$, we present here just $G-1,G-4$, for all the others we refer the reader to the Appendix.
 \begin{enumerate}[G-1.]
@@
 %Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-In order to find a labeling $\lambda$ satisfyinf $D$ 
+In order to find a labeling $\lambda$ satisfying $D$ 
 %that satisfies this property 
@@
 We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
+where the starting vertex $v_i$ is in one of the sets $U,V(G') \setminus U, Z$,
+and similarly the destination vertex $v_j$ is in one of the sets $U,V(G') \setminus U, Z$.
+In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from\ $v_i$ to $v_j$ follows, 
 which results in one equality constraint for the labels on the path $P$. 
@@
 
-			\begin{tikzpicture}[yscale=0.3]
+			\begin{tikzpicture}[yscale=0.25]
 				%%%S_uv
@@
 \end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
+Once the fastest temporal paths are determined we introduce the equality constraints for them.
 For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
@@
 we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-\begin{comment}
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
+%\begin{comment}
+We have proven %in the previous subsections that 
+that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
 Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
@@
 For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-%Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
-
+Since we consider all configurations, one of the produced ILP instances will correspond to the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
+Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
+\begin{comment}
 To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,

### 2023-04-26 New Paper/Realizing TG - extended.tex
MFCS

@@
 
-\begin{definition}[Travel delays]
+\begin{definition}[Travel delays] \label{def:travelDelays}
 	Let $(G, \lambda)$ be a $\Delta$-periodic temporal graph.
@@
 \section{Upper bounds in the matrix D}
-We start by investigating the hardness of the problem on paths.
-We first reduce the input matrix $D$, by performing a series of modifications.
+We start by investigating the complexity of the problem \DeltaUpperBoundLong\ in the case when the underlying graph $G$, of the input instance, is a path.
+To do this efficiently we first present a procedure that reduces the values in the matrix $D$, of the input instance, as much as possible, without effecting solutions.
+This procedure is based on the basic properties of fastest temporal paths.
 
-Denote with $P = (v_1, v_2, \dots, v_n)$ a path on $n$ vertices,
-and let $D$ be the duration matrix with upper bounds.
-For any two vertices $v_i, v_j$ from $P$ we get that:
-\begin{itemize}
-	\item if the value of $D_{i,j} < D_{i,k}$, where $k \in [1+1,j-1]$
-	we set $D_{i,k} = D_{i,j}$.
-\end{itemize}
-%
-By the definition of temporal paths, it follows that $d(i,j) = d(i,k) + d(k-1, j) - 1$, where $i,j \in [n]$, with $i<j$ and $k \in [i+1,j-1]$.
-Therefore,
-\begin{itemize}
-	\item if $D_{i,j} > D_{i,k} + D_{k-1,j} -1$ we set the value of $D_{i,j}$ to $D_{i,k} + D_{k-1,j} -1$. 
-\end{itemize}
-%
-And lastly, to any $i$-th row of the matrix $D$, we make the following modifications:
-\begin{itemize}
-	\item if there are two entries $j< k$ with the same values, \ie $D_{i,j} = D_{i,k}$ where both $j,k$ are bigger than $i$ (resp.~smaller than $i$),
-	then we set $D_{i,j} = D_{i,k} - (k-j)$ (resp.~ $D_{i,k} = D_{i,j} - (k-j)$).
-\end{itemize}
-We iteratively repeat all of the above steps and produce a reduce matrix $D'$.
+Let $(G,D)$ be an instance of \deltaUpperBound\, where $G$ is a path of length $n$.
+Denote with $v_0,v_1, v_2, \dots, v_n$ the vertices of $G$ where $v_{i}v_{i+1} \in E(G)$, for all $i \in [n]$.
+Observe the following properties.
+\begin{enumerate}
+	\item Let $i,j,k \in [n]$, where $i < k < j$, and let $D_{i,j} \leq D_{i,k}$. 
+ Then the temporal path $P_{i,k}$ from $v_i$ to $v_k$ cannot be of duration more than $D_{i,j} - (k-j)$,
+ which implies that $D_{i,k} \leq D_{i,j} - (k-j)$.
+
+ This holds because $P_{i,k}$ is a subpath of the temporal path $P_{i,j}$ from $v_i$ to $v_j$,
+ therefore we can brake down $P_{i,j}$ into two parts, $P_{i,k}$ and the path $P_{k,j}$ from $v_k$ to $v_j$.
+ Since $P_{k,j}$ consists of $k-j$ edges we need at least $k-j$ time to traverse it, so the duration of $P_{i,k}$ cannot take more than $D_{i,j} - (k-j)$ time.
+
+    \item From the definition of temporal paths, it follows that $d(i,j) = d(i,k) + d(k-1, j) - 1$, where $i,j \in [n]$, with $i<j$ and $k \in [i+1,j-1]$.
+    Therefore $D_{i,j} \leq D_{i,k} + D_{k-1,j} -1$.
+
+    \item 
+\end{enumerate}
+
+We iteratively repeat the steps below and produce a reduce matrix $D'$ from the input matrix $D$.
 It is easy to see that if there exists a labeling of $P$ for $D'$, then this labeling satisfies also $D$.
@@
 
+\begin{proof}[Proof idea -- new:]
+We are given an instance  $(G,\Delta), D$ of \deltaUpperBound\, where $G$ is a path on vertices $v_0, v_1, \dots, v_n$.
+Let us denote with $\tau_i^+$ the waiting time at vertex $v_i$ when passing from vertex $v_{i-1}$ to $v_{i+1}$, and with $\tau_i^-$ the waiting time at $v_i$ when traversing through $v_i$ from other direction (for details see~\cref{def:travelDelays}).
+Since $\tau_i^- = \Delta - \tau_i^+$, we denote with $\tau_i = \tau_i^+$, and replace $\tau_i^-$ with $ \Delta - \tau_i$.
+By the definition it also follows that the duration of a fastest path among two vertices $v_i, v_j$ in $(G,\lambda)$, for $i < j$
+is 
+\begin{equation}\label{eq:path-positive}
+    d(v_i,v_j)=\sum_{k = i+1}^{j-1} \tau_k + 1,
+\end{equation}
+and for $i > j$ is 
+\begin{equation}\label{eq:path-negative}
+d(v_i,v_j)=\sum_{k = i+1}^{j-1} (\Delta - \tau_k) + 1.
+\end{equation}
+
+We want to determine the values of all $\tau_i$, and consequently the labeling $\lambda$, such that the distance matrix $D$ is satisfied,
+namely $d(v_i,v_j) \leq D_{i,j}$ for all $v_i,v_j$ in $G$.
+To do this we build an ILP. We do this as follows.
+
+For every pair of vertices $v_i, v_j \in G$ where $|i-j| \geq 2$, we create an inequality of form $d(v_i,v_j) \leq D_{i.j}$, where $d(v_i,v_j)$ equals the expression from \cref{eq:path-positive} if $i < j$, and \cref{eq:path-negative} if $i > j$.
+We build a system of $O(n^2)$ inequalities with $n$ variables $d_1,d_2, \dots, d_n$,
+where each $d_i \in [\Delta]$. Let us denote this system of inequalities as $I_D$.
+We need to prove first that produced system $I_D$ is in fact an (integer) linear program and then show how we can find a solution of it in polynomial time.
+
+Before starting with the analysis of $I_D$ let us observe some basic properties that have to hold for $D$, which will make our computation easier.
+\begin{enumerate}
+    \item f
+\end{enumerate}
+
+\end{proof}
+
 \clearpage

### 2023-04-26 arxivNEW.tex
MFCS

--- 2023-03-21 arxiv.tex
@@
 
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
+Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
 
 \subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction. 
-
 To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
@@
 Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
+In all these cases, the duration of the temporal paths has not been considered.
+
+%work on the temporal cops and robber game~\cite{morawietz2021timecop,morawietz2020timecop,ErlebachS20}.
 The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
+Several other works on periodic temporal graphs were mentioned in the introduction.
+
+Finally, there are many models for dynamic networks in the context of distributed computing~\cite{Kuhn2011Dynamic}. 
+These models have some similarity to temporal graphs, in the sense that in both cases the edges appear and disappear over time. 
+However, there are notable differences. For example, one important assumption in the distributed setting 
+can be that the edge changes are adversarial or random (while obeying some constraints such as connectivity), 
+and therefore they are not necessarily known in advance~\cite{Kuhn2011Dynamic}.
 
 \subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
+We already introduced the most central notion and concepts. There are some additional definitions we need, to present our proofs and results which we give in the following.
 
@@
 which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
 
@@
 \caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
+	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(x_1, x_2, x_4)$.
 To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
@@
     \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
+    $d(x_i,c)=2 \Delta$, $d(c,x_i)=\Delta + 2$
     and
@@
     second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
+    third, $d(c,x_i)=\Delta + 2$,
+    and fourth $d(x_i,c)=2 \Delta$.
 
@@
     Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
+    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$ at times $2$ and $\Delta + 1$, respectively,
     yields the second equality.
@@
     $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
+    with labels $1, 2, 2$ respectively (\ie the path traverses them at time $1,2$ and $\Delta + 2$, respectively), which proves the third equality.
     Now for the case of a temporal path from $x_i$ to $c$,
@@
     namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
+    again at times $2, \Delta + 2, 2\Delta + 1$, respectively,
     which proves the last equality.
@@
     Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
+    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$ (at times $1, 2, \delta + 1$), respectively,
     which proves the desired equality.
@@
 \end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
+Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, therefore $\Delta\ge 3$.
 \end{proof}
@@
     }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
+    \caption{Illustration of part of the underlying graph $G$ and a possible labeling.
+Edges incident with vertices $\hat{v}_1,\hat{v}_2$ of connector gadgets are omitted.
+Gray vertices form a feedback vertex set.
     The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
@@
         & = t_{p-1} - t_1 + 1\\
-        & = d(P)
+        & = d(P, \lambda)
         \end{align*}
@@
     \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact problem.
     For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
@@
 \begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact problem,
     and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.

### 2023-04-26 MFCS23/MFCS23-longversion.tex
MFCS submission - wednesday (1st iteration)

--- 2023-04-26 arxivNEW.tex
@@
 
-\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
 
@@
 
-\nolinenumbers %uncomment to disable line numbering
+%\nolinenumbers %uncomment to disable line numbering
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% APPENDIX
+\usepackage{fancyhdr}
+\setlength{\headheight}{30pt}
+\pagestyle{fancyplain} { % define first page header and footer
+% \fancyhead[L]{Course Report}
+\fancyhead[C]{\textbf{APPENDIX}}
+% \fancyhead[R]{\thepage of \pageref{LastPage}}
+% \fancyfoot[L]{Jinho Hwang}
+% \fancyfoot[C]{GWU}
+% \fancyfoot[R]{CS}
+}
+\fancyhf{}
+\renewcommand{\headrulewidth}{0pt} % remove header lines and reset formats
+\renewcommand{\footrulewidth}{0pt} % remove footer lines and reset formats
+
+% define the rest of pages header and footer
+% \fancyhead[L]{Course Report}
+\fancyhead[OC]{\huge \textbf{APPENDIX}}
+\fancyhead[EC]{\huge \textbf{APPENDIX}}
+% \fancyhead[R]{\thepage of \pageref{LastPage}}
+% \fancyfoot[L]{Jinho Hwang}
+\fancyfoot[OC]{\thepage}
+\fancyfoot[EC]{\thepage}
+% \fancyfoot[R]{CS}
 

### 2023-04-28 TGR Extended - New paper/Realizing TG - extended.tex
Working on new paper

--- 2023-04-26 New Paper/Realizing TG - extended.tex
@@
 \section{Upper bounds in the matrix D}
-We start by investigating the complexity of the problem \DeltaUpperBoundLong\ in the case when the underlying graph $G$, of the input instance, is a path.
-To do this efficiently we first present a procedure that reduces the values in the matrix $D$, of the input instance, as much as possible, without effecting solutions.
-This procedure is based on the basic properties of fastest temporal paths.
+We start by investigating the complexity of the problem \DeltaUpperBoundLong\ in the case when the underlying graph of the input instance is a path.
+First we observe some properties of the problem.
 
@@
 Denote with $v_0,v_1, v_2, \dots, v_n$ the vertices of $G$ where $v_{i}v_{i+1} \in E(G)$, for all $i \in [n]$.
-Observe the following properties.
-\begin{enumerate}
-	\item Let $i,j,k \in [n]$, where $i < k < j$, and let $D_{i,j} \leq D_{i,k}$. 
+And let $\lambda$ be a labelling that we are trying to construct (\ie a labeling satisfying conditions of the problem).
+The following must hold.
+\begin{enumerate}[(a)]
+	\item \label{path:enum-1}
+ Let $i,j,k \in [n]$, where $i < k < j$, and let $D_{i,j} \leq D_{i,k}$. 
  Then the temporal path $P_{i,k}$ from $v_i$ to $v_k$ cannot be of duration more than $D_{i,j} - (k-j)$,
@@
 
-    \item From the definition of temporal paths, it follows that $d(i,j) = d(i,k) + d(k-1, j) - 1$, where $i,j \in [n]$, with $i<j$ and $k \in [i+1,j-1]$.
-    Therefore $D_{i,j} \leq D_{i,k} + D_{k-1,j} -1$.
+    \item \label{path:enum-2}
+     For any two vertices $v_i, v_{i+2}$ on distance two apart the following holds $d(i, i+2) + d(i+2, i) = \Delta + 2$.
+     Therefore $D_{i,i+2} + D_{i+2,i} \geq \Delta + 2$.
+     We can generalize this observation for any two vertices on distance $k$ apart and get 
+     $D_{i,i+k} + D_{i+k,i} \geq (k-1) \Delta + 2$.
 
-    \item 
+    %    \item \label{path:enum-3}
+    %    From the definition of temporal paths, it follows that $d(i,j) = d(i,k) + d(k-1, j) - 1$, where $i,j \in [n]$, with $i<j$ and $k \in [i+1,j-1]$.
+    %    Therefore $D_{i,j} \leq D_{i,k} + D_{k-1,j} -1$.
 \end{enumerate}
 
-We iteratively repeat the steps below and produce a reduce matrix $D'$ from the input matrix $D$.
-It is easy to see that if there exists a labeling of $P$ for $D'$, then this labeling satisfies also $D$.
+From all of the above properties we create a polynomial-time algorithm that transforms the input matrix $D$ into a reduced one, without affecting any potential solutions.
+The algorithm performs the following steps.
+\begin{enumerate}
+    \item A vertex $v_i$ is on the distance $0$ from itself, and at distance $1$ from its neighbors,
+    which means it is also on the duration $0$ and $1$ from them, respectively.
+    Therefore we set all the diagonal values of $D$ to $0$, and the upper and lower diagonals to $1$.
+    \item 
+    From the property~(\ref{path:enum-1}) it follows that the values in every row $i$ the values have to be strictly increasing (resp.~decreasing) from $D_{i,i}$ to $D_{i,n}$ (resp.~$D_{i,1}$).
+    Therefore we loop through each row of $D$ and whenever we encounter 
+    a row that does not obey this rule, we use the property~(\ref{path:enum-1}) to modify its entries.
+\end{enumerate}
+For the matrix $D$ we can also check that the property~(\ref{path:enum-2}) holds, by checking all $O(n^2)$ possible equations.
+If one of them does not hold then we can conclude that there is no labeling $\lambda$ of $G$ that would realize $D$.
 
-\begin{theorem}
+From now on we assume that $D$ is reduced and satisfies the above conditions.
+
+\begin{theorem}\label{thm:paths-upperBound}
 	\deltaUpperBound\ can be solved in polynomial time on paths.
@@
 
-\begin{proof}[Proof idea:]
+\begin{proof}[Proof idea for \cref{thm:paths-upperBound} -- new:]
+We are given an instance  $(G,D)$ of \deltaUpperBound\, where $G$ is a path on vertices $v_0, v_1, \dots, v_n$. 
+Let $\lambda$ be a labeling satisfying this instance.
+We denote with $\tau_i^+$ the waiting time at vertex $v_i$ when passing from vertex $v_{i-1}$ to $v_{i+1}$ in $(G,\lambda)$, with $\tau_i^-$ the waiting time at $v_i$ when traversing through $v_i$ from the other direction (for details see~\cref{def:travelDelays}).
+Since $\tau_i^- = \Delta - \tau_i^+$, we denote with $\tau_i = \tau_i^+$, and replace $\tau_i^-$ with $ \Delta - \tau_i$.
+By the definition it also follows that the duration of a fastest path among two vertices $v_i, v_j$ in $(G,\lambda)$, for $i < j$
+is 
+\begin{equation}\label{eq:path-positive}
+    d(v_i,v_j)=\sum_{k = i+1}^{j-1} \tau_k + 1,
+\end{equation}
+and for $i > j$ is 
+\begin{equation}\label{eq:path-negative}
+d(v_i,v_j)=\sum_{k = i+1}^{j-1} (\Delta - \tau_k) + 1.
+\end{equation}
+
+We want to determine the values of all $\tau_i$, and consequently the labeling $\lambda$, such that the distance matrix $D$ is satisfied,
+namely $d(v_i,v_j) \leq D_{i,j}$ for all $v_i,v_j$ in $G$.
+To do this we build an ILP. We do this as follows.
+
+For every pair of vertices $v_i, v_j \in G$ where $|i-j| \geq 2$, we create an inequality of form $d(v_i,v_j) \leq D_{i.j}$, where $d(v_i,v_j)$ equals the expression from \cref{eq:path-positive} if $i < j$, and \cref{eq:path-negative} if $i > j$.
+We build a system of $O(n^2)$ inequalities with $n$ variables $d_1,d_2, \dots, d_n$,
+where each $d_i \in [\Delta]$. Let us denote this system of inequalities as $I_D$.
+We need to prove first that produced system $I_D$ is in fact an (integer) linear program and then show how we can find a solution, if there is one, in polynomial time.
+
+\begin{claim}
+    The produce system of inequalities $I_D$ is an integer linear program.
+\end{claim}
+\begin{claimproof}
+d
+\end{claimproof}
+
+\end{proof}
+
+\begin{proof}[Proof idea for \cref{thm:paths-upperBound} -- old:]
 	Let $P = (v_1, v_2, \dots, v_n)$ be a path on $n$ vertices.
@@
 
-\begin{proof}[Proof idea -- new:]
-We are given an instance  $(G,\Delta), D$ of \deltaUpperBound\, where $G$ is a path on vertices $v_0, v_1, \dots, v_n$.
-Let us denote with $\tau_i^+$ the waiting time at vertex $v_i$ when passing from vertex $v_{i-1}$ to $v_{i+1}$, and with $\tau_i^-$ the waiting time at $v_i$ when traversing through $v_i$ from other direction (for details see~\cref{def:travelDelays}).
-Since $\tau_i^- = \Delta - \tau_i^+$, we denote with $\tau_i = \tau_i^+$, and replace $\tau_i^-$ with $ \Delta - \tau_i$.
-By the definition it also follows that the duration of a fastest path among two vertices $v_i, v_j$ in $(G,\lambda)$, for $i < j$
-is 
-\begin{equation}\label{eq:path-positive}
-    d(v_i,v_j)=\sum_{k = i+1}^{j-1} \tau_k + 1,
-\end{equation}
-and for $i > j$ is 
-\begin{equation}\label{eq:path-negative}
-d(v_i,v_j)=\sum_{k = i+1}^{j-1} (\Delta - \tau_k) + 1.
-\end{equation}
-
-We want to determine the values of all $\tau_i$, and consequently the labeling $\lambda$, such that the distance matrix $D$ is satisfied,
-namely $d(v_i,v_j) \leq D_{i,j}$ for all $v_i,v_j$ in $G$.
-To do this we build an ILP. We do this as follows.
-
-For every pair of vertices $v_i, v_j \in G$ where $|i-j| \geq 2$, we create an inequality of form $d(v_i,v_j) \leq D_{i.j}$, where $d(v_i,v_j)$ equals the expression from \cref{eq:path-positive} if $i < j$, and \cref{eq:path-negative} if $i > j$.
-We build a system of $O(n^2)$ inequalities with $n$ variables $d_1,d_2, \dots, d_n$,
-where each $d_i \in [\Delta]$. Let us denote this system of inequalities as $I_D$.
-We need to prove first that produced system $I_D$ is in fact an (integer) linear program and then show how we can find a solution of it in polynomial time.
-
-Before starting with the analysis of $I_D$ let us observe some basic properties that have to hold for $D$, which will make our computation easier.
-\begin{enumerate}
-    \item f
-\end{enumerate}
-
-\end{proof}
-
 \clearpage

### 2023-04-28 TGR Extended - New paper/Realizing TG - extended.tex
symbolic link to bibliography
Updates from Overleaf

@@
 \section{Upper bounds in the matrix D}
+
+\subsection{The underlying graph is a path}
 We start by investigating the complexity of the problem \DeltaUpperBoundLong\ in the case when the underlying graph of the input instance is a path.
@@
 
-From now on we assume that $D$ is reduced and satisfies the above conditions.
+Suppose that $(G, D)$ is a yes instance and let $\lambda$ be a labeling of $G$ s.t. $(G,\lambda)$ realizes $D$.
+W.l.o.g. we can assume that $\lambda(v_{i-1} v_{i}) \neq \lambda (v_{i}v_{i+1})$ for all $i \in [n-1]$.
+This follows from the fact that the duration among two vertices $v_i, v_{i+2}$ on distance $2$ in $P$ equals to $\Delta + 1$ when the two consecutive labels are the same, but if the labels are not the same, the duration can be at most $\Delta$.
+Therefore if $D_{i,i+2}= \Delta + 1$ and $\lambda(v_{i-1} v_{i}) \neq \lambda (v_{i}v_{i+1})$ we get that $d(i, i+2) \leq \Delta \leq D_{i,i+2}$ which still satisfies the conditions.
+
+From now on we assume that $D$ is a reduced matrix, that satisfies the above conditions, and that the labeling $\lambda$ of $G$, if it exists, does not label two consecutive edges using the same label.
 
@@
 namely $d(v_i,v_j) \leq D_{i,j}$ for all $v_i,v_j$ in $G$.
-To do this we build an ILP. We do this as follows.
+To do this we build the following integer linear program (ILP).
 
 For every pair of vertices $v_i, v_j \in G$ where $|i-j| \geq 2$, we create an inequality of form $d(v_i,v_j) \leq D_{i.j}$, where $d(v_i,v_j)$ equals the expression from \cref{eq:path-positive} if $i < j$, and \cref{eq:path-negative} if $i > j$.
-We build a system of $O(n^2)$ inequalities with $n$ variables $d_1,d_2, \dots, d_n$,
+We build a system of $O(n^2)$ linear inequalities with $n$ variables $d_1,d_2, \dots, d_n$,
 where each $d_i \in [\Delta]$. Let us denote this system of inequalities as $I_D$.
-We need to prove first that produced system $I_D$ is in fact an (integer) linear program and then show how we can find a solution, if there is one, in polynomial time.
+The produced system $I_D$ is an ILP. 
+We need to show that we can, in polynomial-time, determine if $I_D$ admits a solution,
+and in the positive case construct one such solution.
+A solution for $I_D$ determines the values of each $\tau_i$. We then use this information to determine a labeling $\lambda$, which is a solution for our instance of \deltaUpperBound.
+We do this using the following steps.
+First we prove that our ILP $I_D$ has a solution if and only if the (relaxed) LP version of it admits one .
+Second, we prove that if we have a (non-necessary integer) solution $S'$ of the LP instance $I_D$, then we can modify the solution $S'$ to get an integer solution $S$ of the ILP version of $I_D$.
+\begin{claim}
+    Integer version of the LP for $I_D$ has a solution if and only if the LP for $I_D$ has a solution.
+\end{claim}
 
-\begin{claim}
-    The produce system of inequalities $I_D$ is an integer linear program.
-\end{claim}
 \begin{claimproof}
-d
+Clearly, if the LP for $I_D$ admits no solution, then also the Integer version of the LP for $I_D$ admits no solution, as any integer solution for ILP would also be a solution for LP.
+Therefore we only need to prove that if the LP for $I_D$ admits a solution, then also the ILP or $I_D$ admits one (not necessarily the same one).
+
 \end{claimproof}
@@
 
+\subsection{\deltaUpperBound\ on general graphs}
+In this section we prove that \deltaUpperBound\ becomes NP-hard when the underlying graph is unrestricted, even when $\Delta$ is small.
+
+\begin{theorem}\label{thm:NP-upperBound}
+	\deltaUpperBound\ is NP-hard for all $\Delta \geq 3$.
+\end{theorem}
+
+\begin{proof}
+    We describe a polynomial-time reduction from the  NAE 3-SAT problem, which is known to be NP-hard~\cite{Schaefer1978complexity}.
+The problem involves a formula $\phi$ that comprises a series of NAE (not-all-equal) clauses, where each clause has three distinct literals associated with three different variables.
+    A NAE clause is considered \textsc{true} if and only if not all of its literals are equivalent, meaning that at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
+The problem we are tasked with is to determine if a satisfying assignment exists for $\phi$.
+
+    Given an instance $\phi$ of NAE 3-SAT with $n$ variables $x_1,x_2 \dots , x_n$ and $m$ clauses $c_1, c_2, \dots, c_m$, we build an instance $(D,\Delta)$ of \deltaUpperBound\ using the following procedure.
+
+\begin{figure}[t]
+	\noindent
+	\makebox[\textwidth]{
+		\centering
+\begin{tikzpicture}%[xscale=2]
+
+	%%Variable X1
+	\node (x1t) at (1,0) {};
+	\node (x1f) at (3,0) {};
+
+	%%Variable X2
+	\node (x2t) at (5,0) {};
+	\node (x2f) at (7,0) {};
+
+	%%Variable x3
+	\node (x3t) at (9,0) {};
+	\node (x3f) at (11,0) {};
+
+	%%Variable x4
+	\node (x4t) at (13,0) {};
+	\node (x4f) at (15,0) {};
+
+	%% edges among xt, xf vertices
+	%x1 to all
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
+
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
+	%x2 to all
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
+
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
+	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
+	%x3 to all
+	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
+
+	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
+	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
+
+	%%Variable X1
+	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
+	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
+	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
+	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
+
+	%%Variable X2
+	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
+	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
+	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
+	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
+
+	%%Variable x3
+	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
+	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
+	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
+	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
+
+	%%Variable x4
+	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
+	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
+	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
+	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
+
+	%%vertices for clauses c1, c2 + vertex v
+	\node[vert,label=above:$v$] (v) at (8,3) {};
+	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
+	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
+
+	%%% edges between x1 gadget and v,c1,c2
+	\draw (x1t) to node[timelabel] {$1$} (c1);
+	\draw (x1t) to node[timelabel] {$1$} (c2);
+	\draw (x1t) to [out=90,in=190] (v);
+	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
+
+	%%% edges between x2 gadget and v,c1,c2
+	\draw (x2f) to node[timelabel] {$1$} (c1);
+	\draw (x2t) to node[timelabel] {$1$} (c2);
+	\draw (x2t) to [out=80,in=210]  (v);
+	\draw (x2f) to node[timelabel] {$3$} (v);
+
+	%%% edges between x3 gadget and v,c1
+	\draw (x3t) to node[timelabel] {$1$} (c1);
+	\draw (x3t) to node[timelabel] {$3$} (v);
+	\draw (x3f) to [out=100,in=330] (v);
+
+	%%% edges between x4 gadget and v,c2
+	\draw (x4t) to node[timelabel] {$1$} (c2);
+	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
+	\draw (x4f) to [out=90,in=360] (v);
+
+\end{tikzpicture}
+}
+\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
+	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(x_1, x_2, x_4)$.
+    Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$.
+}\label{fig:NP-example}
+\end{figure}
+
+\end{proof}
+
 \clearpage

### 2023-04-28 TGR Extended - New paper/Realizing TG - extended.tex
NP-hardness picture - new paper

@@
 \tikzset{
-	vert/.style={circle,inner sep=1.5,fill=white,draw,minimum size=.3cm},
+	vert/.style={circle,inner sep=1.5,fill=white,draw=black,minimum size=.3cm},
+    dummy/.style={circle,fill=black,draw=black,inner sep=2.5},
 	edge/.style={color=black, thick},
@@
 	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
 	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
@@
 	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
 
@@
 	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
 
@@
 	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
 
@@
 	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
 
@@
 
+    %%%%%% EDGES
+
 	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
+    %x1 is TRUE
+    %x1 to clause
+    \draw (x1t) to node[timelabel] {$3$} (c1);
+	\draw (x1t) to node[timelabel,pos=0.25] {$3$} (c2);
+    %x1 gadget
+    \draw (x1t) to [out=90,in=190] node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
+	\draw (x1f) to [out=90,in=200] node[dummy] {}
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
+    \draw (x1t) to node[timelabel] {$3$} (x1) to node[timelabel] {$1$} (x1f);
 
 	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
+    %x2 is TRUE
+    %x2 to clause
+	\draw (x2f) to node[timelabel,pos=0.75] {$1$} (c1);
+	\draw (x2t) to node[timelabel,pos=0.75] {$1$} (c2);
+    %x2 gadget
+	\draw (x2t) to [out=80,in=210] node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
+	\draw (x2f) to node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
+    \draw (x2t) to node[timelabel] {$3$} (x2) to node[timelabel] {$1$} (x2f);
 
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
+    %% edges between x3 gadget and v,c1
+    %x3 is FALSE
+    %x3 to clause
+	\draw (x3t) to node[timelabel,pos=0.75] {$1$} (c1);
+    %x3 gadget
+	\draw (x3t) to node[timelabel] node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
+	\draw (x3f) to [out=100,in=330] node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
+    \draw (x3t) to node[timelabel, pos=0.5] {$1$} (x3) to node[timelabel, pos=0.5] {$3$} (x3f);
 
     %%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
+    %x4 is false
+    %x4 to clause
+	\draw (x4t) to node[timelabel,pos=0.75] {$1$} (c2);
+    %x4 gadget
+	\draw (x4t) to [out=90,in=340] node[timelabel] node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
+	\draw (x4f) to [out=90,in=360] node[dummy] {} 
+    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
+    \draw (x4t) to node[timelabel, pos=0.5] {$1$} (x4) to node[timelabel, pos=0.5] {$3$} (x4f);
 

### 2023-05-01 TGR Extended - New paper/Realizing TG - extended.tex
Changes Monday 1st of May

@@
 
-\begin{figure}[t]
+\begin{figure}[hbt]
 	\noindent
@@
     %x3 gadget
-	\draw (x3t) to node[timelabel] node[dummy] {} 
+	\draw (x3t) to node[dummy] {} 
     node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
@@
     %x4 gadget
-	\draw (x4t) to [out=90,in=340] node[timelabel] node[dummy] {} 
+	\draw (x4t) to [out=90,in=340] node[dummy] {} 
     node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
@@
 
-\bibliography{../bibliography}	
+\bibliography{bibliography}	
 \end{document}

### 2023-05-01 Arxiv-1-5-23/ARXIV_realizing-temporal_1-5-23.tex
Arxiv submission 1st of May

--- 2023-04-26 arxivNEW.tex
@@
 \usepackage{graphicx}
-\graphicspath{{Figures/}}
+%%%%\graphicspath{{../Figures/}}
 
@@
 
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
+\begin{thebibliography}{10}
+
+	\bibitem{akrida2017complexity}
+	Eleni~C Akrida, Leszek G{\k{a}}sieniec, George~B. Mertzios, and Paul~G
+	Spirakis.
+	\newblock The complexity of optimal design of temporally connected graphs.
+	\newblock {\em Theory of Computing Systems}, 61:907--944, 2017.
+
+	\bibitem{Akrida-explorer-21}
+	Eleni~C. Akrida, George~B. Mertzios, Paul~G. Spirakis, and Christoforos
+	Raptopoulos.
+	\newblock The temporal explorer who returns to the base.
+	\newblock {\em Journal of Computer and System Sciences}, 120:179--193, 2021.
+
+	\bibitem{Arrighi2023Multi}
+	Emmanuel Arrighi, Niels Gr{\"u}ttemeier, Nils Morawietz, Frank Sommer, and
+	Petra Wolf.
+	\newblock Multi-parameter analysis of finding minors and subgraphs
+	in edge-periodic temporal graphs.
+	\newblock In {\em Proceedings of the 48th International Conference on Current
+		Trends in Theory and Practice of Computer Science (SOFSEM)}, pages 283--297,
+	2023.
+
+	\bibitem{augustine2022distributed}
+	John Augustine, Keerti Choudhary, Avi Cohen, David Peleg, Sumathi
+	Sivasubramaniam, and Suman Sourav.
+	\newblock Distributed graph realizations.
+	\newblock {\em IEEE Transactions on Parallel and Distributed Systems},
+	33(6):1321--1337, 2022.
+
+	\bibitem{barNoy2020efficiently}
+	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
+	\newblock Efficiently realizing interval sequences.
+	\newblock {\em SIAM Journal on Discrete Mathematics}, 34(4):2318--2337, 2020.
+
+	\bibitem{Bar-NoyCPR20}
+	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
+	\newblock Graph realizations: Maximum degree in vertex neighborhoods.
+	\newblock In {\em Proceedings of the 17th Scandinavian Symposium and Workshops
+		on Algorithm Theory (SWAT)}, pages 10:1--10:17, 2020.
+
+	\bibitem{barNoy2021composed}
+	Amotz Bar{-}Noy, David Peleg, Mor Perry, and Dror Rawitz.
+	\newblock Composed degree-distance realizations of graphs.
+	\newblock In {\em Proceedings of the 32nd International Workshop on
+		Combinatorial Algorithms ({IWOCA})}, pages 63--77, 2021.
+
+	\bibitem{barNoy2022GraphRealization}
+	Amotz Bar-Noy, David Peleg, Mor Perry, and Dror Rawitz.
+	\newblock Graph realization of distance sets.
+	\newblock In {\em Proceedings of the 47th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 13:1--13:14,
+	2022.
+
+	\bibitem{behzad1976eccentric}
+	Mehdi Behzad and James~E Simpson.
+	\newblock Eccentric sequences and eccentric sets in graphs.
+	\newblock {\em Discrete Mathematics}, 16(3):187--193, 1976.
+
+	\bibitem{bixby1988almost}
+	Robert~E Bixby and Donald~K Wagner.
+	\newblock An almost linear-time algorithm for graph realization.
+	\newblock {\em Mathematics of Operations Research}, 13(1):99--123, 1988.
+
+	\bibitem{xuan_computing_2003}
+	Binh-Minh Bui-Xuan, Afonso Ferreira, and Aubin Jarry.
+	\newblock Computing shortest, fastest, and foremost journeys in dynamic
+	networks.
+	\newblock {\em International Journal of Foundations of Computer Science},
+	14(02):267--285, 2003.
+
+	\bibitem{CasteigtsCS22}
+	Arnaud Casteigts, Timoth{\'{e}}e Corsini, and Writika Sarkar.
+	\newblock Invited paper: Simple, strict, proper, happy: A study of reachability
+	in temporal graphs.
+	\newblock In {\em Proceedings of the 24th International Symposium on
+		Stabilization, Safety, and Security of Distributed Systems ({SSS})}, pages
+	3--18, 2022.
+
+	\bibitem{casteigts2012time}
+	Arnaud Casteigts, Paola Flocchini, Walter Quattrociocchi, and Nicola Santoro.
+	\newblock Time-varying graphs and dynamic networks.
+	\newblock {\em International Journal of Parallel, Emergent and Distributed
+		Systems}, 27(5):387--408, 2012.
+
+	\bibitem{casteigts2021finding}
+	Arnaud Casteigts, Anne-Sophie Himmel, Hendrik Molter, and Philipp Zschoche.
+	\newblock Finding temporal paths under waiting time constraints.
+	\newblock {\em Algorithmica}, 83(9):2754--2802, 2021.
+
+	\bibitem{chen1966realization}
+	Wai-Kai Chen.
+	\newblock On the realization of a $(p, s)$-digraph with prescribed degrees.
+	\newblock {\em Journal of the Franklin Institute}, 281(5):406--422, 1966.
+
+	\bibitem{chung2001distance}
+	Fan Chung, Mark Garrett, Ronald Graham, and David Shallcross.
+	\newblock Distance realization problems with applications to internet
+	tomography.
+	\newblock {\em Journal of Computer and System Sciences}, 63(3):432--448, 2001.
+
+	\bibitem{culberson1989fast}
+	Joseph~C. Culberson and Piotr Rudnicki.
+	\newblock A fast algorithm for constructing trees from distance matrices.
+	\newblock {\em Information Processing Letters}, 30(4):215--220, 1989.
+
+	\bibitem{deligkas2022optimizing}
+	Argyrios Deligkas and Igor Potapov.
+	\newblock Optimizing reachability sets in temporal graphs by delaying.
+	\newblock {\em Information and Computation}, 285:104890, 2022.
+
+	\bibitem{enright2021deleting}
+	Jessica Enright, Kitty Meeks, George~B. Mertzios, and Viktor Zamaraev.
+	\newblock Deleting edges to restrict the size of an epidemic in temporal
+	networks.
+	\newblock {\em Journal of Computer and System Sciences}, 119:60--77, 2021.
+
+	\bibitem{enright2021assigning}
+	Jessica Enright, Kitty Meeks, and Fiona Skerman.
+	\newblock Assigning times to minimise reachability in temporal graphs.
+	\newblock {\em Journal of Computer and System Sciences}, 115:169--186, 2021.
+
+	\bibitem{EMM22}
+	Jessica~A. Enright, Kitty Meeks, and Hendrik Molter.
+	\newblock Counting temporal paths.
+	\newblock {\em CoRR}, abs/2202.12055, 2022.
+	\newblock URL: \url{https://arxiv.org/abs/2202.12055}.
+
+	\bibitem{erdos1960graphs}
+	Paul Erd{\"o}s and Tibor Gallai.
+	\newblock Graphs with prescribed degrees of vertices.
+	\newblock {\em Mat. Lapok}, 11:264--274, 1960.
+
+	\bibitem{erlebach2021temporal}
+	Thomas Erlebach, Michael Hoffmann, and Frank Kammer.
+	\newblock On temporal graph exploration.
+	\newblock {\em Journal of Computer and System Sciences}, 119:1--18, 2021.
+
+	\bibitem{ErlebachS20}
+	Thomas Erlebach and Jakob~T. Spooner.
+	\newblock A game of cops and robbers on graphs with periodic edge-connectivity.
+	\newblock In {\em Proceedings of the 46th International Conference on Current
+		Trends in Theory and Practice of Informatics (SOFSEM)}, pages 64--75, 2020.
+
+	\bibitem{fellows2009multipleinterval}
+	Michael~R. Fellows, Danny Hermelin, Frances Rosamond, and St{\'e}phane
+	Vialette.
+	\newblock On the parameterized complexity of multiple-interval graph problems.
+	\newblock {\em Theoretical Computer Science}, 410(1):53--61, 2009.
+
+	\bibitem{FJR13}
+	Michael~R. Fellows, Bart M.~P. Jansen, and Frances~A. Rosamond.
+	\newblock Towards fully multivariate algorithmics: {P}arameter ecology and the
+	deconstruction of computational complexity.
+	\newblock {\em European Journal of Combinatorics}, 34(3):541--566, 2013.
+
+	\bibitem{Flu+19a}
+	Till Fluschnik, Hendrik Molter, Rolf Niedermeier, Malte Renken, and Philipp
+	Zschoche.
+	\newblock Temporal graph classes: A view through temporal separators.
+	\newblock {\em Theoretical Computer Science}, 806:197--218, 2020.
+
+	\bibitem{frank1992augmenting}
+	Andr{\'a}s Frank.
+	\newblock Augmenting graphs to meet edge-connectivity requirements.
+	\newblock {\em SIAM Journal on Discrete Mathematics}, 5(1):25--53, 1992.
+
+	\bibitem{frank1994connectivity}
+	Andr{\'a}s Frank.
+	\newblock Connectivity augmentation problems in network design.
+	\newblock {\em Mathematical Programming: State of the Art 1994}, 1994.
+
+	\bibitem{frank1970connectivity}
+	H.~Frank and Wushow Chou.
+	\newblock Connectivity considerations in the design of survivable networks.
+	\newblock {\em IEEE Transactions on Circuit Theory}, 17(4):486--490, 1970.
+
+	\bibitem{FMNR22a}
+	Eugen F\"uchsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
+	\newblock Delay-robust routes in temporal graphs.
+	\newblock In {\em Proceedings of the 39th International Symposium on
+		Theoretical Aspects of Computer Science (STACS)}, pages 30:1--30:15, 2022.
+
+	\bibitem{FuchsleMNR22}
+	Eugen F{\"{u}}chsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
+	\newblock Temporal connectivity: Coping with foreseen and unforeseen delays.
+	\newblock In {\em Proceedings of the 1st Symposium on Algorithmic Foundations
+		of Dynamic Networks ({SAND})}, pages 17:1--17:17, 2022.
+
+	\bibitem{fulkerson1960zero}
+	D.R. Fulkerson.
+	\newblock Zero-one matrices with zero trace.
+	\newblock {\em Pacific Journal of Mathematics}, 10(3):831--836, 1960.
+
+	\bibitem{GolovachM17}
+	Petr~A. Golovach and George~B. Mertzios.
+	\newblock Graph editing to a given degree sequence.
+	\newblock {\em Theoretical Computer Science}, 665:1--12, 2017.
+
+	\bibitem{GolumbicTrenk04}
+	Martin~Charles Golumbic and Ann~N. Trenk.
+	\newblock {\em Tolerance Graphs}.
+	\newblock Cambridge Studies in Advanced Mathematics. Cambridge University
+	Press, 2004.
+
+	\bibitem{gomory1961multi}
+	Ralph~E Gomory and Tien~Chung Hu.
+	\newblock Multi-terminal network flows.
+	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
+	9(4):551--570, 1961.
+
+	\bibitem{grotschel1995design}
+	Martin Gr{\"o}tschel, Clyde~L Monma, and Mechthild Stoer.
+	\newblock Design of survivable networks.
+	\newblock {\em Handbooks in Operations Research and Management Science},
+	7:617--672, 1995.
+
+	\bibitem{GHN04}
+	Jiong Guo, Falk H{\"u}ffner, and Rolf Niedermeier.
+	\newblock A structural view on parameterizing problems: Distance from
+	triviality.
+	\newblock In {\em Proceedings of the 1st International Workshop on
+		Parameterized and Exact Computation (IWPEC)}, pages 162--173, 2004.
+
+	\bibitem{hakimi1962realizability}
+	S.~Louis Hakimi.
+	\newblock On realizability of a set of integers as degrees of the vertices of a
+	linear graph.~{I}.
+	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
+	10(3):496--506, 1962.
+
+	\bibitem{hakimi1965distance}
+	S.~Louis Hakimi and Stephen~S. Yau.
+	\newblock Distance matrix of a graph and its realizability.
+	\newblock {\em Quarterly of applied mathematics}, 22(4):305--317, 1965.
+
+	\bibitem{hell2009linear}
+	Pavol Hell and David Kirkpatrick.
+	\newblock Linear-time certifying algorithms for near-graphical sequences.
+	\newblock {\em Discrete Mathematics}, 309(18):5703--5713, 2009.
+
+	\bibitem{KKK00}
+	David Kempe, Jon~M. Kleinberg, and Amit Kumar.
+	\newblock Connectivity and inference problems for temporal networks.
+	\newblock {\em Journal of Computer and System Sciences}, 64(4):820--842, 2002.
+
+	\bibitem{klobas2023interference}
+	Nina Klobas, George~B. Mertzios, Hendrik Molter, Rolf Niedermeier, and Philipp
+	Zschoche.
+	\newblock Interference-free walks in time: Temporally disjoint paths.
+	\newblock {\em Autonomous Agents and Multi-Agent Systems}, 37(1):1, 2023.
+
+	\bibitem{KlobasMMS22}
+	Nina Klobas, George~B. Mertzios, Hendrik Molter, and Paul~G. Spirakis.
+	\newblock The complexity of computing optimum labelings for temporal
+	connectivity.
+	\newblock In {\em Proceedings of the 47th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 62:1--62:15,
+	2022.
+
+	\bibitem{Kuhn2011Dynamic}
+	Fabian Kuhn and Rotem Oshman.
+	\newblock Dynamic networks: Models and algorithms.
+	\newblock {\em SIGACT News}, 42(1):82–96, mar 2011.
+
+	\bibitem{Lenstra1983Integer}
+	Hendrik~W. Lenstra.
+	\newblock Integer programming with a fixed number of variables.
+	\newblock {\em Mathematics of Operations Research}, 8:538--548, 1983.
+
+	\bibitem{snapnets}
+	Jure Leskovec and Andrej Krevl.
+	\newblock {SNAP Datasets}: {Stanford} large network dataset collection.
+	\newblock \url{http://snap.stanford.edu/data}, June 2014.
+
+	\bibitem{lesniak1975eccentric}
+	Linda Lesniak.
+	\newblock Eccentric sequences in graphs.
+	\newblock {\em Periodica Mathematica Hungarica}, 6:287--293, 1975.
+
+	\bibitem{McConnellS02}
+	Ross~M. McConnell and Jeremy~P. Spinrad.
+	\newblock Construction of probe interval models.
+	\newblock In {\em Proceedings of the 13th Annual {ACM-SIAM} Symposium on
+		Discrete Algorithms (SODA)}, pages 866--875, 2002.
+
+	\bibitem{McMorris98}
+	F.R. McMorris, Chi Wang, and Peisen Zhang.
+	\newblock On probe interval graphs.
+	\newblock {\em Discrete Applied Mathematics}, 88(1):315--324, 1998.
+	\newblock Computational Molecular Biology DAM - CMB Series.
+
+	\bibitem{MertziosMS19}
+	George~B. Mertzios, Othon Michail, and Paul~G. Spirakis.
+	\newblock Temporal network optimization subject to connectivity constraints.
+	\newblock {\em Algorithmica}, 81(4):1416--1449, 2019.
+
+	\bibitem{Mertzios-transitivity21}
+	George~B. Mertzios, Hendrik Molter, Malte Renken, Paul~G. Spirakis, and Philipp
+	Zschoche.
+	\newblock The complexity of transitively orienting temporal graphs.
+	\newblock In {\em Proceedings of the 46th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 75:1--75:18,
+	2021.
+
+	\bibitem{MolterRZ21}
+	Hendrik Molter, Malte Renken, and Philipp Zschoche.
+	\newblock Temporal reachability minimization: Delaying vs. deleting.
+	\newblock In {\em Proceedings of the 46th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 76:1--76:15,
+	2021.
+
+	\bibitem{morawietz2020timecop}
+	Nils Morawietz, Carolin Rehs, and Mathias Weller.
+	\newblock A timecop's work is harder than you think.
+	\newblock In {\em Proceedings of the 45th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, volume 170, pages
+	71--1, 2020.
+
+	\bibitem{morawietz2021timecop}
+	Nils Morawietz and Petra Wolf.
+	\newblock A timecop’s chase around the table.
+	\newblock In {\em Proceedings of the 46th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, 2021.
+
+	\bibitem{Patrinos-Hakimi-72}
+	A.N. Patrinos and S.~Louis Hakimi.
+	\newblock The distance matrix of a graph and its tree realization.
+	\newblock {\em Quarterly of Applied Mathematics}, 30:255--269, 1972.
+
+	\bibitem{Rubei16}
+	Elena Rubei.
+	\newblock Weighted graphs with distances in given ranges.
+	\newblock {\em Journal of Classification}, 33:282–--297, 2016.
+
+	\bibitem{sapiezynski2015tracking}
+	Piotr Sapiezynski, Arkadiusz Stopczynski, Radu Gatej, and Sune Lehmann.
+	\newblock Tracking human mobility using wifi signals.
+	\newblock {\em PloS one}, 10(7):e0130824, 2015.
+
+	\bibitem{Schaefer1978complexity}
+	Thomas~J. Schaefer.
+	\newblock The complexity of satisfiability problems.
+	\newblock In {\em Proceedings of the 10th Annual {ACM} Symposium on Theory of
+		Computing (STOC)}, pages 216--226, 1978.
+
+	\bibitem{Tamura93}
+	H.~Tamura, M.~Sengoku, S.~Shinoda, and T.~Abe.
+	\newblock Realization of a network from the upper and lower bounds of the
+	distances (or capacities) between vertices.
+	\newblock In {\em Proceedings of the 1993 IEEE International Symposium on
+		Circuits and Systems (ISCAS)}, pages 2545–--2548, 1993.
+
+	\bibitem{Wu2016Efficient}
+	Huanhuan Wu, James Cheng, Yiping Ke, Silu Huang, Yuzhen Huang, and Hejun Wu.
+	\newblock Efficient algorithms for temporal path computation.
+	\newblock {\em {IEEE} Transactions on Knowledge and Data Engineering},
+	28(11):2927--2942, 2016.
+
+	\bibitem{Zsc+19}
+	Philipp Zschoche, Till Fluschnik, Hendrik Molter, and Rolf Niedermeier.
+	\newblock The complexity of finding separators in temporal graphs.
+	\newblock {\em Journal of Computer and System Sciences}, 107:72--92, 2020.
+
+\end{thebibliography}
 

### 2023-05-01 Figures/fig-W1-reduction.tex
Arxiv submission 1st of May

@@
 
-		\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
+	\draw[rounded corners, dashed, gray] (-13, 5.4) rectangle (10, 1.6) {};
 	\node (A) at (-10.5,4.5) {alignment gadget};
@@
 
-		\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
+	\draw[rounded corners, dashed, gray] (-9.5, 1.4) rectangle (1.5, -26) {};
 	\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
 
-		\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-		\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
+	\draw[rounded corners, dashed, gray] (3.5, 1.4) rectangle (6.5, -26) {};
+	\node[rotate=-90] (A) at (7,-21.5) {verification gadget for $j$};
 
@@
 
-		\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-		\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-		\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-		\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
+	\draw[edge] (X1) --node[] {} (VS);
+	\draw[edge] (X2) --node[] {} (VS);
+	\draw[edge] (X3) --node[] {} (VS);
+	\draw[edge] (XM) --node[] {} (VS);
 
-		\draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-		\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-		\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-		\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
+	\draw[edge] (Y1) --node[] {} (VS);
+	\draw[edge] (Y2) --node[] {} (VS);
+	\draw[edge] (Y3) --node[] {} (VS);
+	\draw[edge] (YM) --node[] {} (VS);
 
-		\draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-		\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-		\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-		\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
+	\draw[edge] (Y1) --node[] {} (U11);
+	\draw[edge] (Y2) --node[] {} (U12);
+	\draw[edge] (Y3) --node[] {} (U13);
+	\draw[edge] (YM) --node[] {} (U1M);
 
-		\draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-		\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-		\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-		\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
+	\draw[edge] (U21) --node[] {} (U11);
+	\draw[edge] (U22) --node[] {} (U12);
+	\draw[edge] (U23) --node[] {} (U13);
+	\draw[edge] (U2M) --node[] {} (U1M);
 
-		\draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-		\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-		\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-		\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
+	\draw[edge] (UN1) --node[] {} (UN11);
+	\draw[edge] (UN2) --node[] {} (UN12);
+	\draw[edge] (UN3) --node[] {} (UN13);
+	\draw[edge] (UNM) --node[] {} (UN1M);
 
-		\draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-		\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-		\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-		\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
+	\draw[edge] (U2N1) --node[] {} (VSS);
+	\draw[edge] (U2N2) --node[] {} (VSS);
+	\draw[edge] (U2N3) --node[] {} (VSS);
+	\draw[edge] (U2NM) --node[] {} (VSS);
 
-		\draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-		\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-		\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-		\draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-		\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
+	\draw[edge] (VH11) --node[] {} (VH12);
+	\draw[edge] (VH12) --node[] {} (VH111);
+	\draw[edge] (VH12) --node[] {} (VH13);
+	\draw[edge] (VH13) --node[] {} (VH14);
+	\draw[edge] (VH13) --node[] {} (VH144);
 
-		\draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-		\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-		\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-		\draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-		\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
+	\draw[edge] (VH21) --node[] {} (VH22);
+	\draw[edge] (VH22) --node[] {} (VH211);
+	\draw[edge] (VH22) --node[] {} (VH23);
+	\draw[edge] (VH23) --node[] {} (VH24);
+	\draw[edge] (VH23) --node[] {} (VH244);
 
-		\draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-		\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-		\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-		\draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-		\draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
+	\draw[edge] (VH31) --node[] {} (VH32);
+	\draw[edge] (VH32) --node[] {} (VH311);
+	\draw[edge] (VH32) --node[] {} (VH33);
+	\draw[edge] (VH33) --node[] {} (VH34);	
+	\draw[edge] (VH33) --node[] {} (VH344);
 
-		\draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-		\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-		\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-		\draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-		\draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
+	\draw[edge] (VH41) --node[] {} (VH42);
+	\draw[edge] (VH42) --node[] {} (VH411);
+	\draw[edge] (VH42) --node[] {} (VH43);
+	\draw[edge] (VH43) --node[] {} (VH44);	
+	\draw[edge] (VH43) --node[] {} (VH444);
 
@@
 
-		\draw[edge] (W) --node[timelabel] {$1$} (W1);
-		\draw[edge] (W) --node[timelabel] {$1$} (W2);
-		\draw[edge] (W) --node[timelabel] {$1$} (W3);
-		\draw[edge] (W) --node[timelabel] {$1$} (W4);
-		\draw[edge] (W) --node[timelabel] {$1$} (W5);
-		\draw[edge] (W) --node[timelabel] {$1$} (W6);
+	\draw[edge] (W) --node[] {} (W1);
+	\draw[edge] (W) --node[] {} (W2);
+	\draw[edge] (W) --node[] {} (W3);
+	\draw[edge] (W) --node[] {} (W4);
+	\draw[edge] (W) --node[] {} (W5);
+	\draw[edge] (W) --node[] {} (W6);
 
-		\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-		\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-		\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-		\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-		\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-		\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
+	\draw[edge] (X1) --node[] {} (W1);
+	\draw[edge] (VH11) --node[] {} (W2);
+	\draw[edge] (VH21) edge[bend left=50] node[] {} (W3);
+	\draw[edge] (VH31) --node[] {} (W4);
+	\draw[edge] (YI) --node[] {} (W5);
+	\draw[edge] (VH41) edge[bend right=50] node[] {} (W6);
 
-		\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
+	\draw[edge] (YI) --node[] {} (VI0);
 
-		\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-		\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
+	\draw[edge] (VII1) --node[] {} (UI1);
+	\draw[edge] (UI1) --node[] {} (UI2);
 \end{tikzpicture}

### 2023-05-01 ICALP 2023/ICALP23-RealizingTemporalGraphs.tex
Arxiv submission 1st of May

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 \caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
+	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(x_1, x_2, x_4)$.
 	To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.

### 2023-05-05 TGR Extended - New paper/Realizing TG - extended.tex
Poly-time algorithm for paths

@@
 \usepackage{amsmath}
+\usepackage{cite}
 %\let\proof\relax
@@
 
-\begin{proof}[Proof idea for \cref{thm:paths-upperBound} -- new:]
-We are given an instance  $(G,D)$ of \deltaUpperBound\, where $G$ is a path on vertices $v_0, v_1, \dots, v_n$. 
+\begin{proof}
+We are given an instance  $(G,D)$ of \deltaUpperBound\, where $G$ is a path on vertices $v_0, v_1, \dots, v_{n+1}$. 
 Let $\lambda$ be a labeling satisfying this instance.
-We denote with $\tau_i^+$ the waiting time at vertex $v_i$ when passing from vertex $v_{i-1}$ to $v_{i+1}$ in $(G,\lambda)$, with $\tau_i^-$ the waiting time at $v_i$ when traversing through $v_i$ from the other direction (for details see~\cref{def:travelDelays}).
-Since $\tau_i^- = \Delta - \tau_i^+$, we denote with $\tau_i = \tau_i^+$, and replace $\tau_i^-$ with $ \Delta - \tau_i$.
-By the definition it also follows that the duration of a fastest path among two vertices $v_i, v_j$ in $(G,\lambda)$, for $i < j$
+We denote with $\tau_i^+$ the waiting time at vertex $v_i$ when passing from vertex $v_{i-1}$ to $v_{i+1}$ in $(G,\lambda)$,
+and with $\tau_i^-$ the waiting time at $v_i$ when traversing through $v_i$ from the other direction (for details see~\cref{def:travelDelays}).
+Since $\tau_i^- = \Delta - \tau_i^+$, we can simplify the above notation and replace $\tau_i^+$ with $\tau_i$, and $\tau_i^-$ with $ \Delta - \tau_i$.
+Therefore, by the definition, it follows that the duration of a fastest path among two vertices $v_i, v_j$ in $(G,\lambda)$, for $i < j$
 is 
@@
 namely $d(v_i,v_j) \leq D_{i,j}$ for all $v_i,v_j$ in $G$.
-To do this we build the following integer linear program (ILP).
+To do this we build a system of inequalities $I_D$, using the following procedure.
 
 For every pair of vertices $v_i, v_j \in G$ where $|i-j| \geq 2$, we create an inequality of form $d(v_i,v_j) \leq D_{i.j}$, where $d(v_i,v_j)$ equals the expression from \cref{eq:path-positive} if $i < j$, and \cref{eq:path-negative} if $i > j$.
-We build a system of $O(n^2)$ linear inequalities with $n$ variables $d_1,d_2, \dots, d_n$,
-where each $d_i \in [\Delta]$. Let us denote this system of inequalities as $I_D$.
-The produced system $I_D$ is an ILP. 
-We need to show that we can, in polynomial-time, determine if $I_D$ admits a solution,
-and in the positive case construct one such solution.
-A solution for $I_D$ determines the values of each $\tau_i$. We then use this information to determine a labeling $\lambda$, which is a solution for our instance of \deltaUpperBound.
-We do this using the following steps.
-First we prove that our ILP $I_D$ has a solution if and only if the (relaxed) LP version of it admits one .
-Second, we prove that if we have a (non-necessary integer) solution $S'$ of the LP instance $I_D$, then we can modify the solution $S'$ to get an integer solution $S$ of the ILP version of $I_D$.
+This results in creating $O(n^2)$ linear inequalities with $n$ variables $\tau_1,\tau_2, \dots, \tau_n$,
+where each $\tau_i \in [\Delta]$.
+
+Let us observe the following properties of the system of inequalities $I_D$, which will help us to express it as a linear program (LP) in a canonical form.
+
+From observing vertices $v_i$ and $v_j$, we get the following two inequalities:
+\begin{equation}
+\sum_{k = i+1}^{j-1} \tau_k + 1 \leq D_{i,j}
+\Leftrightarrow
+\sum_{k = i+1}^{j-1} \tau_k \leq D_{i,j} - 1
+\end{equation}
+and
+\begin{equation}
+\sum_{k = i+1}^{j-1} (\Delta - \tau_k) + 1
+\Leftrightarrow
+\sum_{k = i+1}^{j-1} - \tau_k \leq  D_{i,j} - 1 -(j-i+1)\Delta .
+\end{equation}
+From the condition $\tau_i \in [\Delta]$, we add the inequality $\tau_i \leq \Delta$ and $\tau_i \geq 0$.
+
+Let us now describe our LP.
+We want to find an assignment of values for each $\tau_i$, that satisfy the inequalities:
+\begin{equation} \label{eq:paths-inequalities-A}
+\begin{aligned}
+\tau_1 & \leq \Delta \\
+\tau_2 & \leq \Delta \\
+& \vdots \\
+\tau_n &\leq \Delta \\
+%%%% \tau \leq Delta
+\tau_1 &\leq D_{0,2} -1 \\
+\tau_1 + \tau_2 &\leq D_{0,3} -1 \\
+\tau_1 + \tau_2 + \tau_3 &\leq D_{0,4} -1 \\
+& \vdots \\
+\tau_1 + \cdots + \tau_n &\leq D_{0,n+1} -1 \\
+%%%% all with \tau_1
+\tau_2 & \leq D_{1,3} -1 \\
+\tau_2 + \tau_3 &\leq D_{1,4} - 1\\
+& \vdots \\
+\tau_n &\leq D_{n-1,n+1} - 1 \\
+%%% all positive tau
+%%%
+- \tau_1 &\leq D_{2,0} -1 - \Delta \\
+- \tau_1 - \tau_2 &\leq D_{3,0} -1 -2 \Delta \\
+& \vdots \\
+- \tau_n &\leq D_{n+1,n-1} - 1 - \Delta
+\end{aligned}
+\end{equation}
+where all $\tau_i$ are positive integers.
+We can write the above set of inequalities in the matrix form as $A t \leq b$, where $t$ is a vector of variables $\tau_1,\tau_2,\dots, \tau_n$.
+Therefore we can form the following LP, in the canonical form
+\begin{equation} \label{eq:paths-LP}
+\begin{aligned}
+\text{find a vector} &&& t \\
+\text{that maximizes} &&& \sum_i \tau_i \\
+\text{subject to} && A t  &\leq b, \\
+\text{and} && t &\geq 0. \\
+\end{aligned}
+\end{equation}
+Note that in our case we do not necessarily want to maximize the sum of all $\tau_i$ variables, but just to find an assignment of variables that will satisfy our conditions.
+Clearly if there is a solution to our system then there is also a solution that will maximize the sum, and vice versa.
+
+In their work Hoffman and Kruskal~\cite{Hoffman1956Integral} prove that if the coefficient matrix  $A$, from the \cref{eq:paths-LP} is totally unimodular (that is, any square submatrix has determinant $\pm 1$, or $0$), and the vector $b$ is integral,
+then the extreme (corner) points of the feasible polyhedron $\{ t \mid A t  \leq b, t \geq 0\}$ are integral. 
+Which implies that using the simplex method to solve the LP, which takes polynomial time, results in an integral solution.
+Therefore we have to prove that $A$ really is totally unimodular.
+
 \begin{claim}
-    Integer version of the LP for $I_D$ has a solution if and only if the LP for $I_D$ has a solution.
+    The coefficient matrix $A$ of linear program $I_D$ is totally unimodular.
 \end{claim}
@@
 \begin{claimproof}
-Clearly, if the LP for $I_D$ admits no solution, then also the Integer version of the LP for $I_D$ admits no solution, as any integer solution for ILP would also be a solution for LP.
-Therefore we only need to prove that if the LP for $I_D$ admits a solution, then also the ILP or $I_D$ admits one (not necessarily the same one).
+    From the definition it follows that $U$ is a totally unimodular matrix if and only if $U^T$ is totally unimodular.
+    It is not hard to prove that if $U$ is a totally unimodular matrix then also $[I U]$ and $[U -U]$ are totally unimodular, where $I$ is the identitiy matrix.
+    We use these facts to prove that our coefficient matrix $A$ is totally unimodular.
 
+    From the first $n$ inequalities from \cref{eq:paths-inequalities-A} it follows that the first $n$ rows of $A$ form an identity matrix $I$ of size $n \times n$.
+    Let us now split the rest of the matrix $A$ into two parts, one where all the non-zero coefficient are positive ($+1$) and the second where they are negative ($-1$).
+    Note that the second part (with the negative non-zero coefficients) is the same as the first part, where each coefficient changes the sign.
+    Therefore we can write the matrix $A$ as
+    \begin{equation*}
+    A =
+        \begin{bmatrix}
+        I \\
+        B \\
+        -B
+        \end{bmatrix},
+    \end{equation*}
+    where $I$ is the identity matrix and $B$ is a matrix of the following form
+    \begin{equation*}
+    B =
+        \begin{bmatrix}
+        1 & & & & \\
+        1 & 1 & & \\
+        1 & 1 & 1 & \cdots & 1 \\
+        \vdots & & & \ddots & \\
+        1 & 1 & 1 & \cdots & 1\\
+        & 1 & & & \\
+        & 1 & 1 & & \\
+        & \vdots & & \ddots & \\
+        & 1 & 1 & \cdots & 1\\
+        & & & \ddots & \\
+        & & & & 1
+        \end{bmatrix}.
+    \end{equation*}
+    Note that $B$ is a matrix in which for every row all non-zero entries ($1$-s) appear consecutively.
+    It is known\cite{Hoffman1956Integral,Fulkerson1965Incidence} that $B$ is a totally unimodular matrix.
+    Using this result and the above mentioned properties of totally unimodular matrices, it follows that $A$ is totally unimodular.
 \end{claimproof}
-
-\end{proof}
-
-\begin{proof}[Proof idea for \cref{thm:paths-upperBound} -- old:]
-	Let $P = (v_1, v_2, \dots, v_n)$ be a path on $n$ vertices.
-	For the sake of simplicity we denote with $a_i$ label of edge $e_i =v_iv_{i+1}$, for all $i \in [n-1]$.
-	By the definition, for any two vertices $v_i,v_j \in P$, we have the following inequality:
-	\begin{equation*}
-		(a_{i+1} - a_i)_\Delta + (a_{i+2} - a_{i+1})_\Delta + \cdots + (a_{j-1} - a_{j-2})_\Delta + 1
-		\leq D_{i,j}.
-	\end{equation*}
-	For the sake of simplicity we refer to the inequality that a temporal path from $v_i$ to $v_j$ has to respect (\ie~the above inequality) 
-	as $I_{i,j}$.
-	Note that we can rewrite the inequality $I_{i,j}$ also without the modulo $\Delta$ part as:
-	\begin{equation*}
-		k_{i+1,i} \Delta + (a_{i+1} - a_i)+ k_{i+2,i+1} \Delta + (a_{i+2} - a_{i+1}) + \cdots + k_{j-1,j-2} \Delta + (a_{j-1} - a_{j-2})+ 1
-		\leq D_{i,j},
-	\end{equation*}
-	where all $k_{i,i+1} \in \{0,1\}$.
-
-	W.l.o.g. we can assume also that $a_i \neq a_{i+1}$ for all $i \in [n-1]$,
-	this follows from the fact that the duration among two vertices $v_i, v_{i+2}$ on distance $2$ in $P$ equals to $\Delta + 1$ when the two consecutive labels are the same, but if the labels are not the same, the duration can be at most $\Delta$, which still satisfies the condition from before.
-	Therefore, for any two consecutive labels $a_i$ and $a_{i+1}$ (\ie for any two vertices $v_i, v_{i+2}$ on distance $2$ in $P$), 
-	it follows that 
-	$k_{i, i+1} = 1 - k_{i+1,i}$, where $k_{i+1,i} \in \{0,1\}$, which makes also $k_{i,i+1} \in \{0,1\}$, as required.
-	If we now sum up the two inequalities $I_{i,i+2}, I_{i+2,i}$ we get the following:
-	\begin{equation*}
-		(a_i-a_{i+1})_\Delta + (a_{i+1}-a_i)_\Delta +1 +1 = \Delta + 2.
-	\end{equation*}
-	It follows that for any two vertices $v_i, v_j$ in $P$, that are on distance $k$ apart, 
-	we get that $d(i,j) + d(j,i) = (k-1) \Delta + 2$.
-
-	To satisfy the inequalities $I_{1,n}$ and $I_{n,1}$ we have to correctly determine which of $k_{i+1,i}$ have value $1$, and consequently set $k_{i,i+1} = 0$,
-	and vice versa.
-
-	From the value $D_{1,n}$ (resp.~$D_{n,1}$) we can determine how many of $k_{i+1,i}$ (resp.$k_{i,i+1}$) can be non-zero. Suppose that there are $m$ non-zero ones (resp.~$n-m-1$).
-	Then to determine which $m$ of the $k_{i,i+1}$ are non-zero we look at every two vertices $v_i, v_{i+2}$ at the distance $2$ in $P$ 
-	and based on the inequalities $I_{i,i+2}, I_{i+2,i}$ determine if $k_{i+1,i}$ has a value $1$ or $0$,
-	i.e.~if $e_{i+1}$ is bigger or smaller than $e_i$.
-	We start determining the values $k_{i+1,i}$ from ``left to right'' (i.e~first we determine $k_{2,1}$, then $k_{3,2}$, \dots, and at last $k_{i-1,i-2}$).
-	Now that the relations of every two consecutive labels of $P$ are determined, 
-	we select the values for each label, such that the inequalities among them hold.
-	\begin{claim}
-		The above procedure produces a labeling of $P$ that satisfies durations from $D$.
-	\end{claim}
+We have now proved that we can, in polynomial time, determine the values of $\tau_i$ satisfying inequalities from $I_D$, if such $\tau_i$ exist.
+We now have to determine the labeling $\lambda$ from the waiting times $\tau_i$.
+Note that knowing the label $\lambda(v_{i-1}v_i)$ and $\tau_i$ we uniquely determine the label $\lambda(v_iv_{i+1})$ as $(\tau_i - \lambda(v_{i-1}v_i))\pmod{\Delta}$.
+Therefore the algorithm to build the whole labelling $\lambda$ of $G$
+starts by fixing the label of the first edge $\lambda(v_0v_1) = 1$, and then iteratively determines the label of each consecutive edge.
+At the end we have build a labeling $\lambda$ that satisfies all inequalities from $I_D$, which implies that for all $v_i,v_j \in V(G)$ we have $d(v_i,v_j) \leq D_{i,j}$.
 \end{proof}
@@
 
+\clearpage
+\section{Old (not useful?) results}
+\begin{proof}[Proof idea for \cref{thm:paths-upperBound} -- old:]
+	Let $P = (v_1, v_2, \dots, v_n)$ be a path on $n$ vertices.
+	For the sake of simplicity we denote with $a_i$ label of edge $e_i =v_iv_{i+1}$, for all $i \in [n-1]$.
+	By the definition, for any two vertices $v_i,v_j \in P$, we have the following inequality:
+	\begin{equation*}
+		(a_{i+1} - a_i)_\Delta + (a_{i+2} - a_{i+1})_\Delta + \cdots + (a_{j-1} - a_{j-2})_\Delta + 1
+		\leq D_{i,j}.
+	\end{equation*}
+	For the sake of simplicity we refer to the inequality that a temporal path from $v_i$ to $v_j$ has to respect (\ie~the above inequality) 
+	as $I_{i,j}$.
+	Note that we can rewrite the inequality $I_{i,j}$ also without the modulo $\Delta$ part as:
+	\begin{equation*}
+		k_{i+1,i} \Delta + (a_{i+1} - a_i)+ k_{i+2,i+1} \Delta + (a_{i+2} - a_{i+1}) + \cdots + k_{j-1,j-2} \Delta + (a_{j-1} - a_{j-2})+ 1
+		\leq D_{i,j},
+	\end{equation*}
+	where all $k_{i,i+1} \in \{0,1\}$.
+
+	W.l.o.g. we can assume also that $a_i \neq a_{i+1}$ for all $i \in [n-1]$,
+	this follows from the fact that the duration among two vertices $v_i, v_{i+2}$ on distance $2$ in $P$ equals to $\Delta + 1$ when the two consecutive labels are the same, but if the labels are not the same, the duration can be at most $\Delta$, which still satisfies the condition from before.
+	Therefore, for any two consecutive labels $a_i$ and $a_{i+1}$ (\ie for any two vertices $v_i, v_{i+2}$ on distance $2$ in $P$), 
+	it follows that 
+	$k_{i, i+1} = 1 - k_{i+1,i}$, where $k_{i+1,i} \in \{0,1\}$, which makes also $k_{i,i+1} \in \{0,1\}$, as required.
+	If we now sum up the two inequalities $I_{i,i+2}, I_{i+2,i}$ we get the following:
+	\begin{equation*}
+		(a_i-a_{i+1})_\Delta + (a_{i+1}-a_i)_\Delta +1 +1 = \Delta + 2.
+	\end{equation*}
+	It follows that for any two vertices $v_i, v_j$ in $P$, that are on distance $k$ apart, 
+	we get that $d(i,j) + d(j,i) = (k-1) \Delta + 2$.
+
+	To satisfy the inequalities $I_{1,n}$ and $I_{n,1}$ we have to correctly determine which of $k_{i+1,i}$ have value $1$, and consequently set $k_{i,i+1} = 0$,
+	and vice versa.
+
+	From the value $D_{1,n}$ (resp.~$D_{n,1}$) we can determine how many of $k_{i+1,i}$ (resp.$k_{i,i+1}$) can be non-zero. Suppose that there are $m$ non-zero ones (resp.~$n-m-1$).
+	Then to determine which $m$ of the $k_{i,i+1}$ are non-zero we look at every two vertices $v_i, v_{i+2}$ at the distance $2$ in $P$ 
+	and based on the inequalities $I_{i,i+2}, I_{i+2,i}$ determine if $k_{i+1,i}$ has a value $1$ or $0$,
+	i.e.~if $e_{i+1}$ is bigger or smaller than $e_i$.
+	We start determining the values $k_{i+1,i}$ from ``left to right'' (i.e~first we determine $k_{2,1}$, then $k_{3,2}$, \dots, and at last $k_{i-1,i-2}$).
+	Now that the relations of every two consecutive labels of $P$ are determined, 
+	we select the values for each label, such that the inequalities among them hold.
+	\begin{claim}
+		The above procedure produces a labeling of $P$ that satisfies durations from $D$.
+	\end{claim}
+\end{proof}
+
 \bibliography{bibliography}	

### 2023-09-18 ISAAC2023/ISAAC23-longversion.tex
ISAC changes

--- 2023-04-26 MFCS23/MFCS23-longversion.tex
@@
 \begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
+In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations between its vertices, 
 while we focus on periodic temporal graphs. 
@@
 such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
+The variations of the problem on static graphs has been well studied and understood since the 1960's (e.g.\ [Erd\H{o}s and Gallai, 1960], [Hakimi and Yau, 1965]), and this area of research remains active until nowadays.
 
@@
 The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
+Furthermore, the investigated properties are temporal connectivity between all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
 In all these cases, the duration of the temporal paths has not been considered.
@@
 Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
+which consists of durations of fastest temporal paths between all pairs of vertices in $(G,\lambda,\Delta)$.
 
@@
 \item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
+$\{x_i, x_i^T\}$, $\{x_i, x_i^F\}$, $\{x_i^T, x_i^F\}$, $\{x_i^T, v\}$, and $\{x_i^F,v\}$.
 \item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
+$\{x_i^T, x_j^T\}$, $\{x_i^T,x_j^F\}$, $\{x_i^F,x_j^T\}$, and $\{x_i^F,x_j^F\}$.
+\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $\{c, x_i^T\}$. 
+If $x_i$ appears negated in $c$ we add edge $\{c, x_i^F\}$.
 \end{itemize}
@@
 \caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(x_1, x_2, x_4)$.
+	where the NAE 3-SAT formula $\phi$ is of the form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(x_1, x_2, x_4)$.
 To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
@@
 We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
+if $\lambda(\{x_i, x_i^T\})=\lambda(\{x_i^T, v\})$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
 
@@
 
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
+Let $\lambda(\{x_i, x_i^T\})=t$ and $\lambda(\{x_i, x_i^F\})=t'$, for an arbitrary variable $x_i$. 
+If both $\lambda(\{x_i^T, v\})\neq t+1$ and $\lambda(\{x_i^F, v\})\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
+Thus, for every variable $x_i$, we have that $\lambda(\{x_i^T, v\})= t+1$ or $\lambda(\{x_i^F, v\})= t'+1$ (or both). 
+In particular, this means that if $\lambda(\{x_i, x_i^F\})=\lambda(\{x_i^F, v\})$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(\{x_i, x_i^T\})\neq\lambda(\{x_i^T, v\})$.
 
@@
 Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
+Let us denote with $t = \lambda(\{x_1^T, v\})$.
+It follows that $\lambda(\{x_1^T, c\})=\lambda(\{x_1^T, v\})-1 = t - 1$.
+Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(\{x_1^T, c\})=\lambda(\{x_1, x_1^T\})-1$. 
+Therefore $\lambda(\{x_1, x_1^T\})=\lambda(\{x_1^T, v\}) = t$. 
 Which implies that $x_1$ is set to \textsc{true}.
 %
-Let us observe paths from $v$ to $c_1$.
+Let us observe paths from $v$ to $c$.
 We know that $d(v,c)=\Delta -1$.
 The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
+Since $\lambda(\{x_1^T,c\}) > \lambda(\{x_1^T, v\})$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
 $d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
@@
 Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
+Let us denote with $t' = \lambda(\{x_2^T, v\})$.
 Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
+and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $\{x_2^T, v\}$,
+it follows that $\lambda(\{x_2^T, c\}) \geq \lambda(\{x_2^T, v\}) - 2 = t' - 2$.
+Since $d(x_2,v) = 2$ it follows that $\lambda(\{x_2, x_2^T\}) = \lambda (\{x_2^T, v\}) - 1 = t' - 1$.
+Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(\{x_2^T, c\})$ must be equal to $t'-2$.
+Therefore the fastest temporal path from $v$ to $c$ passes through edges $\{x_2^T,v\}$ and $\{x_2^T,c\}$.
+In the above we have also determined that $\lambda(\{x_2,x_2^T\}) \neq \lambda ( \{x_2^T,v\})$,
 which implies that $x_2$ is set to \textsc{false}.
@@
     %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
+    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(\{x_i^F, v\})=3$.
+    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(\{x_i^T, v\})=3$.
     \item We set the labels of all other edges to two.
@@
     $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
+    $\lambda(\{x_i, x_i^F\})=2$ and $\lambda(\{x_i^F, v\})=3$.
     For a temporal path from $v$ to $x_i$ we observe the following.
@@
     cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
+    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $\{x_i^F,v\}$ with label $3$,
     and continue to $x_i$ at time $\Delta + 2$,
@@
     Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
+    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(\{x_i^T, c\})=1$ and $\lambda(\{x_i^T, v\})=2$. 
     Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
     (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
+    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(\{x_j^T, v\})=3$ and $\lambda(\{x_j^T, c\})=1$,
     which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
@@
 
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
+    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(\{x_i^T, c\})=1$ and $\lambda(\{x_i, x_i^T\})=\lambda(\{x_i^T, x_i^F\})=2$,
     which proves the first equality.
@@
     Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
+    $\lambda(\{x_i, x_i^T\}) = \lambda (\{x_i^T, x_i^F\})=2$ and 
+    finish on the edge with label $1$, as $\lambda(\{x_i^T, c\}) = 1$.
 
@@
 
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
+    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(\{c, x^F\})=1$ and $\lambda(\{x, x^F\})=\lambda(\{x^T, x^F\})=2$,
     which proves the first inequality.
@@
     Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
+    $\lambda(\{x_i, x_i^F\}) = \lambda (\{x_i^T, x_i^F\})=2$ and 
+    finish on the edge with label $1$, as $\lambda(\{x_i^F, c\}) = 1$.
     Which proves the second equality.
@@
     from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
+    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(\{x_j^T, c\})=1$ and $\lambda(\{x_j^T, x_i^T\})=\lambda(\{x_j^T, x_i^F\})=2$,
     which proves the first equality.
     Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$ at times $2$ and $\Delta + 1$, respectively,
+    \ie first the edge $x_j^T c$ and then one of the edges $\{x_j^T, x_i^F\}$ or $\{x_j^T, x_i^T\}$ at times $2$ and $\Delta + 1$, respectively,
     yields the second equality.
     For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively (\ie the path traverses them at time $1,2$ and $\Delta + 2$, respectively), which proves the third equality.
+    $\{x_j^T, c\}$, $\{x_j^T, x_i^F\}$, and $\{x_i^F,x_i\}$,
+    with labels $1$, $2$, and $2$ respectively (\ie the path traverses them at time $1,2$ and $\Delta + 2$, respectively), which proves the third equality.
     Now for the case of a temporal path from $x_i$ to $c$,
     we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again at times $2, \Delta + 2, 2\Delta + 1$, respectively,
+    namely $\{x_i^F,x_i\}$, $\{x_j^T, x_i^F\}$, and $\{x_j^T, c\}$,
+    again at times $2$, $\Delta + 2$, and $2\Delta + 1$, respectively,
     which proves the last equality.
@@
     Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$ (at times $1, 2, \delta + 1$), respectively,
+    uses the edges $\{x_k^T, c_i\}$, $\{x_\ell^T, c_j\}$, and $\{x_k^T, x_\ell ^T\}$, with labels $1$,~$2$, and $1$ (at times $1$,~$2$, and $\delta + 1$), respectively,
     which proves the desired equality.
@@
     Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
+    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$.
+We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$  (if not we can add $k \max_{i,j}|F_{i,j}|$ vertices to each $W_i$ and use those to add up to $\max_{i,j}|F_{i,j}|$ additional isolated edges to each $F_{i,j}$).
     Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
 
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, the sought temporal graph is not periodic) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+Note that, given the matrix $D$, we can easily compute the underlying graph $G$, as follows.
+Two vertices $v,v'$ are adjacent if $G$ if and only if $D_{v,v'}=1$, as having an edge between $v$ and $v'$ is the only way that there exists a temporal path from $v$ to $v'$ with duration 1.
+For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D(v,v')=1$) and then we provide the remaining entries of $D$.
 At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
 
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
+In the following, we give an informal description of the main ideas of the reduction.
+The construction uses several gadgets, where the main ones are an ``edge selection gadget'' and a ``verification gadget''.
+
+Every \emph{edge selection gadget} is associated with a color combination $i,j$ in the \textsc{Multicolored Clique} instance, and its main purpose is to ``select'' an edge connecting a vertex from color $i$ with a vertex from color $j$.
+Roughly speaking, the edge selection gadget consists of $m$ paths, one for every edge in $F_{i,j}$ (see \cref{fig:hardness1} for reference).
+The distance matrix $D$ will enforce that the labels on those paths effectively order them temporally, that is, in particular, the labels on one of the paths will be smaller than the labels on all other paths.
+The edge corresponding to this path is selected.
+
+ We have a \emph{verification gadget} for every color $i$. They interact with the edge selection gadgets as follows.
+ The verification gadget for color $i$ is connected to all edge selection gadgets that involve color $i$.
+More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see \cref{fig:hardness1}) for reference.
+Intuitively, the distances in the verification gadget are only realizable if the selected edges all have the same endpoint of color $i$.
+Hence, the distances of all verification gadgets can be realized if and only if the selected edges form a clique.
+
+Furthermore, we use an \emph{alignment gadget} which, intuitively, ensures that the labelings of all gadgets use the same range of time labels.
+Finally, we use \emph{connector gadgets} which create shortcuts between all vertex pairs that are irrelevant for the functionality of the other gadgets.
+This allows us to easily fill in the distance matrix with the corresponding values.
+We ensure that all our gadgets have a constant feedback vertex number, hence the overall feedback vertex number is quadratic in the number of colors of the \textsc{Multicolored Clique} instance and we get the parameterized hardness result.
+
+In the following, for every gadget, we first give a formal description of the underlying graph of this gadget (i.e.~not the complete distance sub-matrix of the gadget).
+Afterwards, we define the corresponding entries in the distance matrix $D$.
+
+    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExact\ (with infinity entries and no periods) as follows.
 
@@
 
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
+    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell''\in[13n]$ we add edge $\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
     %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
@@
     Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
+    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all verification gadgets.
     The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
@@
     \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
+    We add two connector gadgets for each edge selection gadget and two connector gadgets for each verification gadget.
 
@@
         \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
+        %\item Set $A'$ contains all vertices from all edge selection gadgets and all verification gadgets except $X_{i,j}$.
+        %\item Set $B$ contains all vertices from all edge selection gadgets and all verification gadgets, except $v_{i,j}^{\star\star}$.
         %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
@@
         %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
+        %\item Set $B$ contains all vertices from all edge selection gadgets and all verification gadgets.
         \item Set $B$ is empty.
@@
 Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
+Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and verification gadgets) except the ones in $B$.
 We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
+Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all verification gadgets.
 \begin{itemize}
@@
 
-Next, consider the validation gadget for color $i$. 
+Next, consider the verification gadget for color $i$. 
 %Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
@@
     \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
+(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all verification gadgets).
 \end{itemize}
@@
 
-Finally, consider the validation gadget for color $i$. 
+Finally, consider the verification gadget for color $i$. 
 %For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
@@
     \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact problem.
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem.
     For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
@@
 
+Furthermore, we can make the following observation concerning subpaths of a fastest temporal path.
+
 \begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact problem,
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
     and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
@@
 Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
+Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ between them.
 Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
@@
     Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
+\end{observation}
+
 Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
 
@@
     \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
+    Now we repeat the following procedure. From vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
     We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
@@
 Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
+These paths would then be used to create (representatives of) fastest temporal paths between vertex pairs in $(G,\lambda)$.
 We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
@@
 
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
+In our case, however, it is not enough to consider fastest temporal paths between some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
 This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
@@
 	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
+ When considering the problem of finding shortest paths between vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
 	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
@@
     %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
+    %guesses desired structures between them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
     %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
@@
 Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
+the matrix of the fastest temporal paths between all pairs of $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
 With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
@@
 \[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
+Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, since every neighbor of $u$ is the first vertex of a (unique) path to another vertex in $U$.
+It follows that $|U^*| \in O(k^2)$.
 From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
@@
 For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
+\begin{definition}\label{def:segments}
     Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
+    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
     is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
 \end{definition}
 %From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
+Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$, since we consider paths to be directed.
 Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
@@
 Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
+Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
+if the fastest path between two vertices is not uniquely determined, we denote it by $\leadsto$.
 We guess the following structures.
@@
     \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
+    The fastest temporal paths between all pairs of vertices of $U$.
     For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
@@
     %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
+    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths between all pairs of vertices in $U$.
     \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
+    The fastest temporal paths between all pairs of vertices in $Z^*$, 
     which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
     \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
+    The fastest temporal paths between all pairs of vertices in $U^*$.
     This gives us $O(k^{k^6})$ guesses.
@@
     Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
+    the fastest paths of the form
     $u \leadsto w \rightarrow z_2$
@@
 		\includegraphics{fig-guess1}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
 	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
@@
 			\includegraphics{fig-guess2}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
 			\label{fig:FPT-guessG5}}
@@
 				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
+				and guessed the fastest paths of the form
 				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
@@
 		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
+		and guessed the fastest paths of the form
 		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
@@
 Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
+we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path between vertices of interest $u$ and $v$ in $G'$.
 Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
@@
 It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
+is not a part of any fastest temporal path, of length at least $2$, between vertices in $S_{u,v}$,
 \ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
@@
     Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
+    Suppose for the contradiction, that none of the fastest temporal paths between vertices of $S_{u,v}$ traverses the edge $f$.
 
     \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
+    Let us observe the case of fastest temporal paths between $v_{1}$ and $v_{3}$.
     Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
@@
     \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
+    Here we consider the fastest paths between vertices $v_{2}$ and $v_{4}$.
     By similar arguments as above we get
@@
     In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
+    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, between vertices in $S{_u,v}$, avoid an edge $f$.
 
@@
     Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
+    Suppose that the fastest temporal paths between $v_1$ and $v_3$ do not use the edge $f$.
     We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
+    which is of the form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
     and similarly 
     with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
+    of the form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
     We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
@@
 
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
+    Repeating the analysis for the fastest paths between $v_2$ and $v_4$,
     we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
@@
 \subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
+We start by analyzing the case where we want to determine the labels on fastest temporal paths between vertices of interest.
 We proceed in the following way.
@@
 or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
+If the fastest temporal path between two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
 All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
@@
 We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
+For this we use the fact that at least one of the temporal paths between vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
 We proceed as follows.
@@
 First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
+We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths between them.
 
@@
 Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
+In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference between them is easy to determine,
 if one or both consecutive labels are not yet determined 
@@
 
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
+\subparagraph{\boldmath Fastest paths between $u,v$ where $u \in U$ and $v \in V$.}
 First we consider the case when $u,v$ are two vertices of interest.
@@
 
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
+\subparagraph{\boldmath Fastest paths between $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
 Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
@@
     We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
+    We iterate through all possible paths of the form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
     Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
@@
     Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
+    Denote with $Q$ the fastest temporal path of the form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
     We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
@@
     Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
+    Since we the fastest paths $Q^+$ of the form $u \leadsto w \rightarrow z_2$ and 
+    $Q^-$ of the form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of the form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
     we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
@@
     We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
+    (\ie paths of the form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of the form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
     we add the inequalities constraints.
@@
 We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
+Denote with $P^+$ the fastest temporal path of the form $z_2 \rightarrow z \leadsto u$,
+and with $P^-$ the fastest temporal path of the form $z_{r-1} \rightarrow w \leadsto u$.
 Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
@@
     If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
+    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of the form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
+    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of the form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
 \end{enumerate}
 Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
+For all other $O(k^k)$ paths (which correspond to all paths of the form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
 we introduce the inequality constraints.
 
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
+\subparagraph{\boldmath Fastest paths between $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
 Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
@@
     \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
+    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path between vertices.
     Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
@@
 and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
+To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ between vertices of interest, that are the endpoints of observed segments,
 once the segment is reached there is a unique path how to traverse it.
@@
 Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
+it follows that there is also a unique (therefore also the fastest) temporal path between them.
 Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
@@
 
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
+\subparagraph{\boldmath Fastest paths between $z,u$ where $z \in Z$ and $u \in U$.}
 Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
@@
         Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
+        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of the form 
         $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
@@
             \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
+            the fastest temporal path is of the form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
             We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
@@
             \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
+            the fastest temporal path is of the form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
             We again have two options.
@@
 
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
+\subparagraph{\boldmath Fastest paths between $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
 The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
@@
 
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
+\subparagraph{\boldmath Fastest paths between $z,z'$ where $z \in Z$ and $z' \in Z$.}
+The last case to consider is when we want to determine the fastest temporal paths between two vertices from $Z$.
 Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
@@
     In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
+    and therefore we know the fastest paths between them (see guess G-\ref{FPT:guess-uToSegmentz2}).
     \item One clip vertex is a vertex of interest and the other is not.
@@
     from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
+    together with all the fastest paths between 
     each pair of the following vertices
@@
 we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
+We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths between vertices).
+Besides that, in each ILP instance we add also the constraints for durations of all temporal paths between each pair of vertices.
 This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
@@
     If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
+    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of the form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
     We know how to determine $P'$, since

### 2023-09-18 ISAAC2023/ISAAC23-shortversion.tex
ISAC changes

--- 2023-04-26 MFCS23/MFCS23-shortversion.tex
@@
 \caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
+	where the NAE 3-SAT formula $\phi$ is of the form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
 To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
@@
 The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest. The set $X$ is called a \emph{feedback vertex set}. 
-Note that, in contrast to the previous results (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
+Note that, in contrast to the previous result (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
 
@@
     Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
+    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$.
+We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$ (if not we can add $k \max_{i,j}|F_{i,j}|$ vertices to each $W_i$ and use those to add up to $\max_{i,j}|F_{i,j}|$ additional isolated edges to each $F_{i,j}$).
     Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
 
-We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, the sought temporal graph is not periodic) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+Note that, given the matrix $D$, we can easily compute the underlying graph $G$, as follows.
+Two vertices $v,v'$ are adjacent if $G$ if and only if $D_{v,v'}=1$, as having an edge between $v$ and $v'$ is the only way that there exists a temporal path from $v$ to $v'$ with duration 1.
+For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D(v,v')=1$) and then we provide the remaining entries of $D$.
 At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
 
+In the following, we give an informal description of the main ideas of the reduction.
+The construction uses several gadgets, where the main ones are an ``edge selection gadget'' and a ``verification gadget''.
+
+Every \emph{edge selection gadget} is associated with a color combination $i,j$ in the \textsc{Multicolored Clique} instance, and its main purpose is to ``select'' an edge connecting a vertex from color $i$ with a vertex from color $j$.
+Roughly speaking, the edge selection gadget consists of $m$ paths, one for every edge in $F_{i,j}$ (see \cref{fig:hardness1} for reference).
+The distance matrix $D$ will enforce that the labels on those paths effectively order them temporally, that is, in particular, the labels on one of the paths will be smaller than the labels on all other paths.
+The edge corresponding to this path is selected.
+
+ We have a \emph{verification gadget} for every color $i$. They interact with the edge selection gadgets as follows.
+ The verification gadget for color $i$ is connected to all edge selection gadgets that involve color $i$.
+More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see \cref{fig:hardness1}) for reference.
+Intuitively, the distances in the verification gadget are only realizable if the selected edges all have the same endpoint of color $i$.
+Hence, the distances of all verification gadgets can be realized if and only if the selected edges form a clique.
+
+Furthermore, we use an \emph{alignment gadget} which, intuitively, ensures that the labelings of all gadgets use the same range of time labels.
+Finally, we use \emph{connector gadgets} which create shortcuts between all vertex pairs that are irrelevant for the functionality of the other gadgets.
+This allows us to easily fill in the distance matrix with the corresponding values.
+We ensure that all our gadgets have a constant feedback vertex number, hence the overall feedback vertex number is quadratic in the number of colors of the \textsc{Multicolored Clique} instance and we get the parameterized hardness result.
+
+In the following, for every gadget, we give a formal description of the underlying graph of this gadget (i.e.~not the complete distance sub-matrix of the gadget).
+Due to space constraints, we defer the description of the distance matrix $D$ and the formal proof of correctness for the reduction to the Appendix.
+
     Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExact\ (with infinity entries and no periods) as follows. 
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
+    %To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
 Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
+    %We will construct $G$ using several gadgets.
 
@@
 
-This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
+This finishes the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
 %\begin{itemize}
@@
 
+As mentioned before, due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
+
 \begin{comment}
@@
 
-Due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
 %
-\begin{comment}
+%\begin{comment}
 \emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
@@
 We can conclude that the originally constructed instance $D$ is a \textsc{Yes}-instance if and only if it remains a \textsc{Yes}-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{comment}
+%\end{comment}
 \end{proof}
@@
 \section{Algorithms for \deltaExact}
+\begin{comment}
 In this section we provide several algorithms for \deltaExact.
@@
 
-%We first show %in \cref{sec:treealgo} 
-%that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time. 
 In the case when the underlying graph is unrestricted, we show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
@@
 Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-% \subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-% We first start with defining certain notions, that will be of use when solving the problem.
-
-%     \begin{definition}[Travel delays]
-%     Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-%     Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-%     We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-%     as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-%     More specifically:
-%     %\begin{equation}\label{eq:def-VertexWaitingTime}
-%        $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.$
-%     %\end{equation}
-%     %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-%     \end{definition}
-%     Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-%     From the above definition and the definition of the duration of the temporal path $P$ we get the following results.
-%     \begin{observation}[$\star$]\label{obs:durationPwithWaitingTimes}
-%         Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-%         $(P, \lambda)$ from $v_0$ to $v_p$.
-%         Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-%     \end{observation}
-%     \begin{observation}[$\star$]\label{obs:travel-delays-both-directions}
-%     Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-%     For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-%     \end{observation}
-% \begin{lemma} [$\star$]\label{lemma:unique-fastest-path-allDelays}
-%     Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-%     and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-%     Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-%     Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-%     Then we can determine travel delays on vertices of $P$ using the following equation
-%     %\begin{equation}\label{eq:trav-delays-paths}
-%         $\tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},$ for all $i \in \{2,3, \dots, k-1\}$.
-%     %\end{equation}
-% \end{lemma}
-% %All of the above is used in the design of the following polynomial-time algorithms.
-% We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-% Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-% \begin{comment}
-% Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-% Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-% and therefore are the fastest.
-% Then $D$ is of the following form:
-% \begin{equation*}
-%     D_{i,j} =
-%     \begin{cases}
-%     0 & \text{if $i = j$}, \\
-%     1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-%     d(P_{i,j},\lambda) & \text{else}
-%     \end{cases},
-% \end{equation*}
-% where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-% \end{comment}
-
-% \begin{observation}\label{obs:travel-delays-in-trees}
-%     Let $v_i,v_j$  be arbitrary vertices in a tree $G$. 
-%     Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it follows that $d(P_{i,j},\lambda) = D_{i,j}$. 
-%     Moreover, all vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-% \end{observation}
-
-%We start by providing a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-
-%\begin{theorem}[$\star$]\label{thm:deltaExact-PolyTimeTrees}
-%    \deltaExact\ can be solved in polynomial-time on trees.
-%\end{theorem}
-
-% \begin{proof}
-%     Let $D$ be an input matrix of \deltaExact\ with dimension $n \times n$.
-%     In polynomial time we construct the underlying graph $G$ of $D$ and check if it is a tree.
-%     %If at this point we encounter a problem, our algorithm stops and returns a negative answer.
-
-%     Let $V(G) = \{v_1, v_2, \dots, v_n\}$.
-%     We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-%     We now take the unique path $P_{i,j}$ in $G$, 
-%     which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees,lemma:unique-fastest-path-allDelays} calculate travel delays at all inner vertices.
-%     We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-%     Matrix $T$ stores at the position $(k,j,\ell)$ the value  $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-%     We repeat the above procedure from vertex $v_i$, for vertices $v_{j'}$ that are not marked as visited yet.
-%     When we have exhausted the $i$-th row of $D$,
-%     \ie vertex $v_i$ now reaches every vertex of $G$,
-%     we continue and repeat the procedure for all other vertices.
-%     If at any point we get two different numerical values for the same entry of $T$ we stop and return the negative answer.
-%     The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-%     \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
-%         Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-%     \end{claim}
-%     Given the matrix $T$, we can easily determine a labeling $\lambda$ that satisfies $D$.
-%     We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-%     Knowing the label of one edge, and all waiting times in $T$, we uniquely determine the labels of all other edges.
-%     More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-%     the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-%     Since there are $\Delta$ options to fix the first label, there are $\Delta$ different labelings satisfying $D$.
-%     %Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-%     It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time.
-%     %as we have to traverse the graph exactly once, to successfully fix the labeling. 
-%     Therefore, all together the whole algorithm is performed in polynomial time.
-% \end{proof}
+\end{comment}
+
+In this section we provide several algorithms for \deltaExact.
+By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
+
+We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
+In \cref{sec:FPT} we generalize this result.
+We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
+Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
+In the appendix we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
+Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
+
+We first start with defining certain notions, that will be of use when solving the problem.
+
+    \begin{definition}[Travel delays]
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
+    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+    More specifically:
+    \begin{equation}\label{eq:def-VertexWaitingTime}
+       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+    \end{equation}
+    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    \end{definition}
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
+
+    We can make the following observation concerning subpaths of a fastest temporal path.
+
+\begin{lemma}[$\star$]\label{lemma:unique-fastest-path-allDelays}
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
+    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
+    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
+    Then we can determine travel delays on vertices of $P$ using the following equation
+    \begin{equation}\label{eq:trav-delays-paths}
+        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
+    \end{equation}
+    for all $i \in \{2,3, \dots, k-1\}$.
+\end{lemma}
+
+\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
+%All of the above is used in the design of the following polynomial-time algorithms.
+We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
+Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
+Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
+and therefore are the fastest.
+Then $D$ is of the following fo\rm:
+\begin{equation*}
+    D_{i,j} =
+    \begin{cases}
+    0 & \text{if $i = j$}, \\
+    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
+    d(P_{i,j},\lambda) & \text{else}
+    \end{cases},
+\end{equation*}
+where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
+
+\begin{observation}\label{obs:travel-delays-in-trees}
+    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
+    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
+    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
+    \end{observation}
+    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of $P_{i,j}$.
+
+\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
+    \deltaExact\ can be solved in polynomial time on trees.
+\end{theorem}
+
+\begin{proof}
+    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
+    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
+    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
+At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
+    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
+    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
+
+    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
+    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
+
+    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
+    We now take the unique path $P_{i,j}$ in $G$, 
+    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
+    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
+    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
+    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
+    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
+    When we have exhausted the $i$-th row of $D$,
+    \ie vertex $v_i$ now reaches every vertex of $G$,
+    we continue and repeat the procedure for all other vertices.
+    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
+    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
+    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
+    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
+        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
+    \end{claim}
+
+    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
+    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
+    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
+Therefore, all together the whole algorithm is performed in polynomial time.
+\end{proof}
 
@@
 
-We first give an informal and very high-level description of the main ideas of the algorithm.
+We only give an informal and very high-level description of the main ideas of the algorithm
+The detailed description and correctness proof of the algorithm are deferred to the appendix, due to space constraints.
 It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
@@
 
+ \begin{comment}
 	\begin{figure}[t]
@@
 	\end{figure}
+\end{comment}
 
@@
 
+\begin{comment}
+
 For the remainder of this section, let $D$ be the input matrix of \deltaExact\, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
@@
 At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{Yes}-instance then we will show that also $D$ is a \textsc{Yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{No}-instances, then we will show that $D$ is a \textsc{No}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
 
@@
 
-\begin{comment}
-From the construction it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-$
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-$
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time. 
-\end{comment}
 \subparagraph{Guessing necessary structures. \label{sec:FPT-guessing}}
@@
 Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes to $v$ via an edge (or a unique path), we write it as a fastest path of form $u \leadsto x \rightarrow v$.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes to $v$ via an edge (or a unique path), we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
 %Similarly it holds if we want to include more vertices that have to be visited by the path. 
@@
 	\end{lemma}
-\begin{comment}
-    Note that in the case when path $P$ from $u$ to $v$ admits no extra vertices of interest, beside $u$ and $v$, then we can determine labels of all of its edges, with respect to the label of the first edge.
-    The procedure to determine the labeling relies on \cref{obs:FirstLabelAndDuration} (for details see Appendix).
-\end{comment}
 
@@
 %
-\begin{comment}
-We now describe how we add constraints to a specific path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative (for details see Appendix),
-which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-%We iterate through all pairs of vertices $x,y$ in $G$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint}, and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-%For each pair we argue how we determine these paths.
-\end{comment}
 %
@@
 			\end{tikzpicture}%}
-		\caption{Example of a guess G-8, where we guessed the fastest paths of form $z_2 \rightarrow w \leadsto u$ (in blue) and $z_{r-1} \rightarrow z \leadsto u$ (in red), where $u$ is a vertex of interest and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
+		\caption{Example of a guess G-8, where we guessed the fastest paths of the form $z_2 \rightarrow w \leadsto u$ (in blue) and $z_{r-1} \rightarrow z \leadsto u$ (in red), where $u$ is a vertex of interest and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
 \label{fig:FPT-4casesGuess}}
@@
 We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow w \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow z \leadsto u$.
+Denote with $P^+$ the fastest temporal path of the form $z_2 \rightarrow w \leadsto u$,
+and with $P^-$ the fastest temporal path of the form $z_{r-1} \rightarrow z \leadsto u$.
 Note that we know these paths from the guess~G-8 (depicted in \cref{fig:FPT-4casesGuess}, for details see Appendix).
@@
     If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
+    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of the form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
+    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of the form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
 \end{enumerate}
 Once the fastest temporal paths are determined we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
+For all other $O(k^k)$ paths (which correspond to all paths of the form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
 we introduce the inequality constraints.
@@
 Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
-\begin{comment}
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labeling.
+
 \end{comment}

### 2023-09-20 STACS2023/nina_shortversion.tex
trying to make a shorter version for STACS

--- 2023-09-18 ISAAC2023/ISAAC23-shortversion.tex
@@
 \usepackage{graphicx}
-\graphicspath{{Figures/}}
+\graphicspath{{../Figures/}}
 
@@
 
-We only give an informal and very high-level description of the main ideas of the algorithm
-The detailed description and correctness proof of the algorithm are deferred to the appendix, due to space constraints.
+We first give an informal and very high-level description of the main ideas of the algorithm.
+We then present the first part in more details and deffer the reader to the appendix, for the remaining part and correctness proof.
 It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
@@
 
- \begin{comment}
 	\begin{figure}[t]
@@
 	\end{figure}
-\end{comment}
 
@@
     \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
+    \item We compute a solution to each of the ILPs (if it exists) and construct a labeling from that solution.
 Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
 \end{itemize}
-
-\begin{comment}
-
-For the remainder of this section, let $D$ be the input matrix of \deltaExact\, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-%With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\subparagraph{Preprocessing of the input.}
-From $G$ we create $G'$ by
-iteratively removing vertices of degree one. With $Z$ we denote the set of all removed vertices.
+It is important to point out that each guess of fastest paths, gives rise to one ILP. Since there are many guesses ($f(k)$ many, where $f$ is a double exponential function), we get many ILPs.
+If none of the ILP instances gives a positive solution, then there exists no labeling realizing given matrix.
+This is true because considering all guesses of fastest temporal paths is equivalent to exhaustively searching through all possible temporal paths between vertices.
+
+\subsubsection{First part of the FPT algorithm}
+We now present the first part of our FPT algorithm.
+Let $D$ be the input matrix of \deltaExact\, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
+%\subsubsection*{Preprocessing of the input}
+From the underlying graph $G$ of $D$ we first create a graph $G'$ by
+iteratively removing vertices of degree one from $G$,
+and denote with 
+$
+Z = V(G) \setminus V(G')
+$, the set of removed vertices.
+%Then we determine a minimum feedback edge set $F$ of $G'$.
 %by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
 %Note that $F$ is also a minimum feedback edge set of $G$.
-%Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, that gives rise to a minimum feedback edge set $F$ (denote $k = |F|$), 
-and
-let $V_1 \subset V(G')$ be the set of leaves in $T$, $V_2 \subset V(G')$ the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
+Then we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
+Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
+Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
 and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
@@
 We denote with 
-$
-U = V_1 \cup V_2 \cup V_3
-$
-the set of \emph{vertices of interest}. It follows that $|U| \leq 4k$.
+\[U = V_1 \cup V_2 \cup V_3\]
+the set of vertices of interest. It follows that $|U| \leq 4k$.
 We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-$
-U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.
-$
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-Note that determining all of the above sets takes linear time.
-
-\subparagraph{Guessing necessary structures. \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ %and $Z^*$ 
-are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes to $v$ via an edge (or a unique path), we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
-%Similarly it holds if we want to include more vertices that have to be visited by the path. 
-%If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$, if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess $11$ different structures $G-1,G-2,\dots,G-11$, we present here just $G-1,G-4$, for all the others we refer the reader to the Appendix.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path, respecting the value from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ variations of the fastest temporal paths among all vertices in $U$.
-
-    %\item \label{FPT-guessFTPamongZstar}
-    %The fastest temporal paths among all vertices in $Z^*$, which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-
-    %\item \label{FPT-guessFTPamongUstar}
-    %The fastest temporal paths among all vertices in $U^*$. This gives us $O(k^{k^6})$ guesses.
-
-    \setcounter{enumi}{3}
-
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-\end{enumerate}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^4})$ new ones, that respond to the guessing in the next step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential function).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subparagraph{Properties of \deltaExact.}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-	We want to determine labeling $\lambda$ of each edge of $G$.
-	We start with an empty labeling of edges and try to specify each one of them.
-	Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-    We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$. 
-	%In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
-	%In our analysis we exploit the following results greatly.
-    We are now ready, to present some basic properties of our problem.
-\begin{definition}
+\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
+Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, since every neighbor of $u$ is the first vertex of a (unique) path to another vertex in $U$.
+It follows that $|U^*| \in O(k^2)$.
+From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
+it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
+For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
+and call it a \emph{clip vertex of the tree $T_i$}.
+It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
+but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
+Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
+from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
+that are clipped at the same vertex $u_i \in V(G')$.
+For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
+and call it \emph{a representative vertex of the tree $T_{u_i}$}.
+We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
+where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
+\[
+Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
+\]
+Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
+Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
+
+%Let us remember the following basic property of the problem \deltaExact.
+Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
+%, and no other temporal path from $v_i$ to $v_j$ is faster.
+In order to find a labeling that satisfies this property we split our analysis in nine cases.
+We consider fastest temporal paths 
+where $v_i$ is in one of the sets $U,V(G') \setminus U, Z$,
+and $v_j$ is in one of the sets $U,V(G') \setminus U, Z$.
+In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from $v_i$ to $v_j$ follows, 
+which results in one equality constraint for the labels on the path $P$. 
+For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
+This results in producing $poly(n,m)$ constraints. 
+Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
+
+For an easier understanding and the analysis of the algorithm we give the following definition.
+\begin{definition}\label{def:segments}
 	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in $G'$, of length at least $2$, where $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
+	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
 	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
 \end{definition}
 %From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
+Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$, since we consider paths to be directed.
 Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
@@
 \end{corollary}
-
-	\begin{observation}[$\star$]\label{obs:FirstLabelAndDuration}
-		Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-		Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-		Symmetrically, knowing $\lambda(e_p)$ and $d(P,\lambda)$, we can uniquely determine $\lambda(e_1)$.
-	\end{observation}
- If $\lambda(e_1)$ and $\lambda(e_p)$ (from the above observation) are both unknown, then we can determine one with respect to the other.
- %\begin{definition}\label{FPT:def-segment}
-%	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-%	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-%	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-%	Note $S_{u,v} \neq S_{v,u}$.
-%\end{definition}
-
-	\begin{lemma}[$\star$]\label{lemma:FPT-uv-LabelAlmostalledges}
-		Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-		is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-		Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-		We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-		such that the labeling $\lambda$ respects the values from $D$.
-		%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-	\end{lemma}
-
-\subparagraph{Adding constraints and variables to the ILP.}
-%Using the above guessed structures, and certain properties of the problem, we proceed with adding constraints to each of our ILP instances.
-
-%Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-In order to find a labeling $\lambda$ satisfying $D$ 
-%that satisfies this property 
-we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex $v_i$ is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex $v_j$ is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from\ $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-To ensure this 
-we split the graph into $O(k^2)$ segments, and introduce at most $3$ variables for each segment,
-therefore each of our ILP instances admits $O(k^3)$ number of variables (for details see Appendix).
+%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
+%, which we prove later on (see~\cref{obs:FPT-k2segments}).
+%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
+
+%\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
+Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
+Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
+%Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
+%if the fastest path between two vertices is not uniquely determined, we denote it by $\leadsto$.
+We guess the following structures.
+%\noindent\textbf{Basic guesses:}
+\begin{enumerate}[G-1.]
+	\setcounter{enumi}{\value{guesscounter}}
+	\item \label{FPT-guessFTPamongU}
+	The fastest temporal paths between all pairs of vertices of $U$.
+	For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
+	Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
+	%If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
+	Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths between all pairs of vertices in $U$.
+	\item \label{FPT-guessFTPamongZstar}
+	The fastest temporal paths between all pairs of vertices in $Z^*$, 
+	which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
+	\item \label{FPT-guessFTPamongUstar}
+	The fastest temporal paths between all pairs of vertices in $U^*$.
+	This gives us $O(k^{k^6})$ guesses.
+	\item \label{FPT-guessFTPamongUandUstar}
+	The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
+	and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
+	This gives us $O(k^{k^4})$ guesses.
+	\item \label{FPT-guessFTPamongUandZstar}
+	The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
+	and vice versa.
+	This gives us $O(k^{k^3})$ guesses.
+	\item \label{FPT-guessFTPamongUstarandZstar}
+	The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
+	and vice versa.
+	This gives us $O(k^{k^4})$ guesses.
+	\setcounter{guesscounter}{\value{enumi}}
+\end{enumerate}
+\noindent
+\begin{enumerate}[G-1.]
+	\setcounter{enumi}{\value{guesscounter}}
+	\item \label{FPT-guessFTPamongv2z2}
+	\textbf{Inner segment guess I}.
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
+	first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
+	We want to guess the following fastest temporal path
+	$v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
+	We repeat this procedure for all pairs of segments.
+	Since there are $O(k^2)$ segments in $G'$,
+	there are $O(k^{k^5})$ possible paths of this form. \\
+	Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
+Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
+Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
+	${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
+	${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
+	${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
+	${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
+	${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
 	%
+	For an example see~\cref{fig:FPT-guessG4}.
+	\item \label{FPT:guess-uToSegmentz2}
+	\textbf{Inner segment guess II}.
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
+	and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest.
+	We want to
+	guess the following fastest temporal paths
+	$w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
+	and
+	$v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
+	\\
+	For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
 	%
-We now present one example of how to determine the fastest temporal paths among a fixed pair of vertices, for all other cases we refer the reader to the Appendix.
-
-\emph{Fastest paths from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.}
+	For an example see~\cref{fig:FPT-guessG5}.
+	%All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
+	%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
+	\item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
+	\textbf{Split vertex guess I}.
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
+	fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
+	In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
+	If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
+	Let 
+	$S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
+	Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
+	can be reached from $v_i$ by some path that has to go through $w$ or $z$.
+	Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
+	the segment
+	$S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
+	We split the analysis into two cases.
+	\begin{enumerate}
+		\item 
+		There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
+		More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
+		We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
+		Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
+		$D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
+		From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
+		and 
+		the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
+		We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
+		Similarly,
+		all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
+		which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
+		Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
+		Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
+		Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
+		\ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
+		Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
+		This introduces two extra guesses.
+		For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
+		or determine that $z_j$ does not exist.
+		We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
+		for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
+		We repeat this procedure for all pairs of segments,
+		which results in producing $O(k^{k^6})$ new guesses.
+		Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
+		\item 
+		There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
+		More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
+		Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
+		From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
+		and 
+		the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
+		In this case we only need to guess the following two fastest temporal paths 
+		$u \leadsto w \rightarrow z_2$
+		and $u \leadsto z \rightarrow z_{r-1}$.
+		Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
+		which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
+		Note that in this case we do not introduce any new guesses, as we have aready guessed 
+		the fastest paths of the form
+		$u \leadsto w \rightarrow z_2$
+		and $u \leadsto z \rightarrow z_{r-1}$
+		(see guess~G-\ref{FPT:guess-uToSegmentz2}).
+	\end{enumerate}
+	Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
+	\ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
+	%
+	For an example see~\cref{fig:FPT-guessG6}.
+	\item \label{FPT:guess-splitFromUtoAnotherSegment}
+	\textbf{Split vertex guess II}.
+	Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest,
+	and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
+	We want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+	We again have two cases,
+	first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
+	and the
+	second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
+	\begin{comment}
+	In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
+	travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
+	Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
+	we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
+	or 
+	$v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
+	Which produces two new guesses.
+	In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
+	Therefore no new guesses are needed.
+	Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
+	uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
+	(this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
+	\end{comment}
+
+	All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
+	We repeat this for all vertices of interest, and all segments,
+	which produces $O(k^{k^2})$ new guesses.
+	%
+	For an example see~\cref{fig:FPT-guessG7}.
+	Detailed analysis follows arguing from above (as in G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}) and is deferred to Appendix.
+	% counter for guesses continues
+	\setcounter{guesscounter}{\value{enumi}}
+\end{enumerate}
+%
 \begin{figure}[t]
 	\centering
-		%\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}[yscale=0.25]
-				%%%S_uv
-				\node[vert,label=above:$w {=} z_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$z_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$z_{r-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$z_r {=} z$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$u$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(v1) edge[dirwave] [out=290,in=160] (w) 
-				(v2) edge[diredge2] (v1);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(vp) edge[dirwave] [out=240,in=20] (w) 
-				(vp1) edge[diredge2] (vp);
-
-			\end{tikzpicture}%}
-		\caption{Example of a guess G-8, where we guessed the fastest paths of the form $z_2 \rightarrow w \leadsto u$ (in blue) and $z_{r-1} \rightarrow z \leadsto u$ (in red), where $u$ is a vertex of interest and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-\label{fig:FPT-4casesGuess}}
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+			\includegraphics{fig-guess1}}
+		\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
+			\label{fig:FPT-guessG4}}
+	\end{subfigure}
+	\quad
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+
+			\includegraphics{fig-guess2}}
+		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+			\label{fig:FPT-guessG5}}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{1.2\linewidth}{!}{
+			%
+			\includegraphics{fig-guess3}}
+		\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for a fixed vertex $v_i \in S_{u,v}$,
+			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
+			and guessed the fastest paths of the form
+			$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
+			and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
+			\label{fig:FPT-guessG6}}
+	\end{subfigure}
+	\quad
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{\linewidth}{!}{
+			\includegraphics{fig-guess4}}
+		\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
+			we
+			calculated its corresponding split vertex $v_i \in S_{u,v}$,
+			and guessed the fastest paths of the form
+			$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
+			and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
+			\label{fig:FPT-guessG7}}
+	\end{subfigure}
+	\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
 \end{figure}
-
-%We want to determine the fastest path from $x$ to $u$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-\noindent
-Let $x$ be a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it (intuitively, these are the edges whose labels are not determined with respect to any other edge label), which means that all of the labels of edges in the segment $S_{w,z}$ are determined with respect to (at most) two different values $\lambda(e)$ and $\lambda(f)$, for some edges $e,f$ in $S_{w,z}$.
-For a detailed explanation see Appendix.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of the form $z_2 \rightarrow w \leadsto u$,
-and with $P^-$ the fastest temporal path of the form $z_{r-1} \rightarrow z \leadsto u$.
-Note that we know these paths from the guess~G-8 (depicted in \cref{fig:FPT-4casesGuess}, for details see Appendix).
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of the form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of the form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of the form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{Solving ILP instances.}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
 %
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$. 
-%(\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-%\begin{comment}
-We have proven %in the previous subsections that 
-that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-%This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$, and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$, for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond to the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-Therefore, if there is no ILP instance with a positive solution, then there exists no possible labeling of $G$, that would realize the matrix $D$.
-
-\end{comment}
+We create all of the above guesses independently.
+We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
+After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential) 
+and create one ILP instance for each case.
+
+For each of the ILP instances we iterate through all pairs of vertices $u,v \in V(G)$ and, using the above guesses, determine, not only the fastest path $P$ from $u$ to $v$, but also all other paths $P'_i$.
+For the labels of edges of the fastest path $P$ we introduce the equality constraint, while for the labels of the edges of all other paths $P'_i$ we introduce the inequality constraint (\ie the duration $d(P_i')$ of any $P'_i$ cannot be smaller than $d(P)=D_{u,v}$).
+We can do this efficiently, while introducing only a small number of variables,
+which ensures that each ILP is solved in an FPT-time.
+For detailed explanation and proofs of this part see Appendix.
+
+\todo{Argue why each (some) of the guesses are important}
 

### 2023-09-21 STACS2023/nina_shortversion.tex
Shorter version in progress

@@
 The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$.%, \ie $F = E(G) \setminus E(T)$.
+Determining $F$ can be done in linear time, by simply removing edges of a spanning tree (forest) from the given graph.
+%one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$.%, \ie $F = E(G) \setminus E(T)$.
 
@@
 We first give an informal and very high-level description of the main ideas of the algorithm.
-We then present the first part in more details and deffer the reader to the appendix, for the remaining part and correctness proof.
+We then present the first part in more details and deffer the reader to the appendix for the remaining part and correctness proof.
 It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
@@
 An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
+%
+%In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
 This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
@@
 
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
+In our case, however, this approach does not work. Mainly because of the
+	%A further difficulty arises from the 
+ somewhat unintuitive characteristic of fastest paths in temporal graphs.
  When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
@@
  For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
+ Besides that, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
 	%This makes all the standard intuition and work with these kind of paths, much harder.
@@
 \begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an Integer Linear Program (ILP).
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
+    \item We identify a small number of ``interesting vertices'' and specific ``graph constructions'' between which we guess representative fastest paths.
+    \item For each guess %(also called ``paths configuration'') 
+    we create one Integer Linear Program (ILP).
+    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine is small. 
+    \item For each additive constant and each non-determined label we introduce a variable for an Integer Linear Program (ILP).
+    \item We use equality and inequality constraints in each ILP to ensure that the fastest temporal path from $u$ to $v$ is of duration $D_{u,v}$, while any other path is of duration at least $D_{u,v}$.
     \item We compute a solution to each of the ILPs (if it exists) and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-It is important to point out that each guess of fastest paths, gives rise to one ILP. Since there are many guesses ($f(k)$ many, where $f$ is a double exponential function), we get many ILPs.
-If none of the ILP instances gives a positive solution, then there exists no labeling realizing given matrix.
+Since each ILP has a few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
+    If none of the ILP instances give a positive solution, then there exists no labeling realizing given matrix.
     This is true because considering all guesses of fastest temporal paths is equivalent to exhaustively searching through all possible temporal paths between vertices.
+\end{itemize}
 
@@
 %, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where $v_i$ is in one of the sets $U,V(G') \setminus U, Z$,
-and $v_j$ is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
+In order to find a labeling that satisfies this property we iterate through all pairs of vertices $v_i, v_j \in V(G)$ and 
+first guess the underlying path $P$ of a fastest temporal path from $v_i$ to $v_j$, which results in one equality constraint for the labels on the path $P$. 
 For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
 This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-
+It is important to point out that the number of constraint and number of variables are not related, while we introduced all of the necessary constraints, we manage to create only a small number of variables (upper-bounded by some function in $k$).
+%Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$, therefore we do not 
+%
 For an easier understanding and the analysis of the algorithm we give the following definition.
@@
 %From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$, since we consider paths to be directed.
+Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$. 
 Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
@@
 	\textbf{Inner segment guess I}.
-	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-	first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments. %,
+	%first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
 	We want to guess the following fastest temporal path
@@
 	Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
+Furthermore note that we did not assume that $\{u,v\} \cap \{w,z\} = \emptyset$.
 Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
@@
 	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-	and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest.
+	and let $w \in U \cup Z^*$. %be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest.
 	We want to
@@
 	\\
-	For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
+	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
 	%
@@
 	fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-	In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-	If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
+	In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex, else we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
 	Let 
 	$S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-	Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-	can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-	Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-	the segment
-	$S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
+	We want to determine the fastest paths from $v_i$ to all inner vertices of $S_{w,z}$. We do this by inspecting the values in matrix $D$ from $v_i$ to inner vertices of $S_{w,z}$.
 	We split the analysis into two cases.
@@
 		which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-		Note that in this case we do not introduce any new guesses, as we have aready guessed 
+		In this case we do not introduce any new guesses, as we have aready guessed 
 		the fastest paths of the form
@@
 	\textbf{Split vertex guess II}.
-	Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest,
-	and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
+	Let $w \in U \cup Z^*$ 
+	and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$.
 	We want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
@@
 	\end{comment}
-
 	All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
@@
 			\includegraphics{fig-guess1}}
-		\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+		\caption{Example of an Inner segment guess I (G-\ref{FPT-guessFTPamongv2z2}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
 			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
@@
 			\includegraphics{fig-guess2}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+		\caption{Example of an Inner segment guess II (G-\ref{FPT:guess-uToSegmentz2}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
 			\label{fig:FPT-guessG5}}
@@
 			\includegraphics{fig-guess3}}
-		\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for a fixed vertex $v_i \in S_{u,v}$,
+		\caption{Example of a Split vertex guess I (G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}), where, for a fixed vertex $v_i \in S_{u,v}$,
 			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
@@
 			\includegraphics{fig-guess4}}
-		\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
+		\caption{Example of a Split vertex guess II (G-\ref{FPT:guess-splitFromUtoAnotherSegment}), where, for a vertex of interest $w$, 
 			we

### 2023-09-22 Figures/fig-exampleg10.tex
example of why we need new guesses

% tikzpic.tex
\documentclass[crop,tikz]{standalone}% 'crop' is the default for v1.0, before it was 'preview'

\usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
\usetikzlibrary{shapes,calc,patterns,arrows.meta}
\tikzset{
	vert/.style={circle,inner sep=1.5,fill=white,draw,minimum size=.3cm},
	edge/.style={color=black, thick},
	diredge/.style={->,>={Stealth[width=8pt,length=8pt]},color=black, thick},
	timelabel/.style={fill=white,font=\footnotesize, text centered},
	wave/.style={decorate,decoration={coil,aspect=0}},
	dirwave/.style={->, >={Stealth[width=8pt,length=8pt]},decorate,decoration={coil,aspect=0}},
	diredge2/.style={->,>={Stealth[width=8pt,length=8pt]}}
}
\begin{document}

	\begin{tikzpicture}
		%%%S_uv
		\node[vert,label=left:$v_1$,label={[text=gray]above:$3$}] (v1) at (1,0) {};
		\node[vert,label=below:$v_2$,label={[text=gray]above:$5$}] (v2) at (2,0) {};
		\node[vert,label=below:$v_3$,label={[text=gray]above:$6$}] (v3) at (3,0) {};
		\node[vert,label=below:$v_4$,label={[text=gray]above:$7$}] (v4) at (4,0) {};
		\node[vert,label=below:$v_5$,label={[text=gray]above:$11$}] (v5) at (5,0) {};
		\node[vert,label=below:$v_6$,label={[text=gray]above:$17$}] (v6) at (6,0) {};
		\node[vert,label=below:$v_7$,label={[text=gray]above:$14$}] (v7) at (7,0) {};
		\node[vert,label=below:$v_8$,label={[text=gray]above:$10$}] (v8) at (8,0) {};
		\node[vert,label=below:$v_9$,label={[text=gray]above:$9$}] (v9) at (9,0) {};
		\node[vert,label=below:$v_{10}$,label={[text=gray]above:$8$}] (v10) at (10,0) {};
		\node[vert,label=right:$v_{11}$,label={[text=gray]above:$5$}] (v11) at (11,0) {};
		\draw (v1) -- (v2) -- (v3) -- (v4) -- (v5) -- 
		(v6) -- (v7) -- (v8) -- 
		(v9) -- (v10) --  (v11);

		%%%% node w
		\node[vert,label=below:$w$] (w) at (6,-1.5) {};

		\draw [blue] 
		(w) edge[dirwave] [out=172,in=315] node[pos=0.6,below,yshift=-2mm, text=black] {$P$} (v1) 
		(v1) edge[diredge2] (v2);

		\draw [red]
		(w) edge[dirwave] [out=8,in=225] node[pos=0.6,below,yshift=-2mm, text=black] {$Q$} (v11) 
		(v11) edge[diredge2] (v10);

	\end{tikzpicture}

\end{document}

\begin{figure}[h]
	\centering
	\includegraphics{fig-exampleg10}
	\caption{In the above graph vertices $v_1, v_{11}, w$ are in $U$, while $v_2, v_{10}$ are in $U^*$. 
		Numbers above all $v_i$ represent the values of the fastest temporal paths from $w$ to each of them (\ie the entries in the $w$-th row of matrix $D$).
		From the basic guesses we know the fastest temporal path $P$ from $w$ to $v_2$ (depicted in blue) and the fastest temporal path $Q$ from $w$ to $v_{10}$.
		From the values of durations from $w$ to each $v_i$ we cannot 
		determine the fastest paths from $w$ to all $v_i$.
		More precisely, we know that $w$ reaches $v_2, v_3, v_4, v_5$ (resp.~$v_{10}, v_{9}, v_{9}, v_{7}$) 
		by first using the path $P$ (resp.~$Q$) and then proceeding through the vertices,
		but we do not know how $w$ reaches $v_6$ the fastest.
		Therefore we have to introduce some more guesses.}
\end{figure}

### 2023-09-22 STACS2023/nina_shortversion.tex

@@
     we create one Integer Linear Program (ILP).
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine is small. 
-    \item For each additive constant and each non-determined label we introduce a variable for an Integer Linear Program (ILP).
+    \item We show that we can determine most labels along each path. We show that the number of labels we cannot determine is small. 
+    \item For each non-determined label we introduce a variable for an ILP.
     \item We use equality and inequality constraints in each ILP to ensure that the fastest temporal path from $u$ to $v$ is of duration $D_{u,v}$, while any other path is of duration at least $D_{u,v}$.

### 2023-09-22 STACS2023/STACS23-shortversion.tex

--- 2023-09-22 STACS2023/nina_shortversion.tex
@@
 \usepackage{graphicx}
-\graphicspath{{../Figures/}}
+\graphicspath{{Figures/}}
 
@@
 
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
+As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (\ie non-temporal) counterpart. 
 First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
@@
 \end{abstract}
+
+\clearpage
 
@@
 
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
+In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, \ie of graphs whose \emph{topology changes over time}.
 
@@
 
-In this paper we consider \emph{periodic} temporal graphs, i.e.~temporal graphs in which the temporal availability of each edge of the underlying graph is periodic. 
+In this paper we consider \emph{periodic} temporal graphs, \ie temporal graphs in which the temporal availability of each edge of the underlying graph is periodic. 
 Many natural and technological systems exhibit a periodic temporal behavior. For example, in railway networks an edge is present at a time step $t$ if and
 only if a train is scheduled to run on the respective rail segment at time $t$~\cite{Arrighi2023Multi}. 
-Similarly, a satellite, which makes pre-determined periodic movements, can establish a communication link (i.e.~a temporal edge) with another satellite whenever they are sufficiently close to each other; the existence of these communication links is also periodic.
+Similarly, a satellite, which makes pre-determined periodic movements, can establish a communication link (\ie a temporal edge) with another satellite whenever they are sufficiently close to each other; the existence of these communication links is also periodic.
 In a railway (resp.~satellite) network, a fastest temporal path from $u$ to $v$ represents the fastest railway connection between two stations 
@@
 
-%In order to focus on the smallest duration of temporal paths, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
+%In order to focus on the smallest duration of temporal paths, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, \ie on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
 
@@
 We initiate the study of naturally motivated graph realization problems in the temporal setting. 
-Our target is not to model unreliable communication, but instead to \emph{verify} that particular measurements regarding fastest temporal paths in a periodic temporal graph are plausible (i.e.~``realizable'').
+Our target is not to model unreliable communication, but instead to \emph{verify} that particular measurements regarding fastest temporal paths in a periodic temporal graph are plausible (\ie ``realizable'').
 To this end, we introduce and investigate the following problem, capturing the setting described above:
@@
 Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of~$k$. 
-Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (i.e.~bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
+Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (\ie bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
 For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than~$D_{i,j}$.
@@
 Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
+For simplicity of the presentation (and with a slight abuse of notation) we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as $D_{a,b}$, where $a=v_i$ and $b=v_j$. 
+That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
+
+Let $P=(u=v_1, v_2, \dots, v_p=v)$ be a path from $u$ to $v$ in $G$. 
+Recall that, in our paper, every edge has exactly one time label in every period of $\Delta$ consecutive time steps. 
+Therefore, as we are only interested in the fastest duration of temporal paths, 
+many times we refer to $(P,\lambda,\Delta)$ as any of the temporal paths from $u=v_1$ to $v=v_p$ along the edges of $P$, which starts at the edge $v_1 v_2$ at time $\lambda(v_1 v_2) + c \Delta$, for some $c\in \mathbb{N}$, and then sequentially visits the rest of the edges of $P$ as early as possible.
+We denote by $d(P,\lambda,\Delta)$, or simply by $d(P,\lambda)$ when $\Delta$ is clear from the context, the duration of any of the temporal paths $(P,\lambda,\Delta)$; note that they all have the same duration.
 Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
@@
 
-In the following, for every gadget, we give a formal description of the underlying graph of this gadget (i.e.~not the complete distance sub-matrix of the gadget).
+In the following, for every gadget, we give a formal description of the underlying graph of this gadget (\ie not the complete distance sub-matrix of the gadget).
 Due to space constraints, we defer the description of the distance matrix $D$ and the formal proof of correctness for the reduction to the Appendix.
@@
 By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
+In \cref{sec:treealgo} that if the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
 In \cref{sec:FPT} we generalize this result.
@@
 Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-In the appendix we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
+%In the appendix we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
 Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
 
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    We can make the following observation concerning subpaths of a fastest temporal path.
-
-\begin{lemma}[$\star$]\label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
+%We first start with defining certain notions, that will be of use when solving the problem.
+
+%    \begin{definition}[Travel delays]
+%    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
+%    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+%    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+%    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+%    More specifically:
+%    \begin{equation}\label{eq:def-VertexWaitingTime}
+%       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+%    \end{equation}
+%    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+%    \end{definition}
+%    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
+
+%    We can make the following observation concerning subpaths of a fastest temporal path.
+
+%\begin{lemma}[$\star$]\label{lemma:unique-fastest-path-allDelays}
+%    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
+%    and let $(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+%    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
+%    Suppose that, for any $v_i$ in $P$, we have that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
+%    Then we can determine travel delays on vertices of $P$ using the following equation
+%    \begin{equation}\label{eq:trav-delays-paths}
+%        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
+%    \end{equation}
+%    for all $i \in \{2,3, \dots, k-1\}$.
+%\end{lemma}
 
@@
 %All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following fo\rm:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    \end{observation}
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of $P_{i,j}$.
+We now provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
+Let $D$ be the input matrix and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+Let $v_i,v_j$ be two arbitrary vertices in $G$, then we know that there exists a unique (static) path $P_{i,j}$ from $v_i$ to $v_j$. We will heavily exploit this in our algorithm.
+%Consequently, the temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ is also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
+%and therefore are the fastest.
+%Then $D$ is of the following form:
+%\begin{equation*}
+%    D_{i,j} =
+%    \begin{cases}
+%    0 & \text{if $i = j$}, \\
+%    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
+%    d(P_{i,j},\lambda) & \text{else}
+%    \end{cases},
+%\end{equation*}
+%where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
+
+%\begin{observation}\label{obs:travel-delays-in-trees}
+%    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
+%    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
+%    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
+%    \end{observation}
+%    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of $P_{i,j}$.
 
@@
 
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
+    Having computed $G$, our algorithm proceeds as follows.
+We pick an arbitrary edge $e$ and give it label one, that is, $\lambda(e)=1$.
+Now we push all edges incident with $e$ into a (initially empty) queue.
+Now we repeat the following as long as the queue is not empty:
+\begin{itemize}
+    \item Pop edge $e=\{u,v\}$ from the queue.
+Since $e$ was pushed into the queue, there is an edge $e'$ incident with $e$ that already obtained a label.
+Let w.l.o.g.\ $e'=\{v,w\}$.
+Then we set $\lambda(e)=(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
+    \item Push all edges incident with $e$ that have not received a label yet into the queue.
+\end{itemize}
+When the queue is empty, all edges have received a label.
+Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$.
+If this check succeeds for all vertex pairs, output the labelling $\lambda$, otherwise abort.
+
+It is easy to see that the described algorithm runs in polynomial time. In the remainder, we proof that it is correct.
+
+$(\Rightarrow)$: Since the algorithm checks at the end whether all durations specified in $D$ are realized by the corresponding fastest paths, we clearly face a yes-instance whenever the algorithm outputs a labeling.
+
+$(\Leftarrow)$: Assume we face a yes-instance, then there exists a labeling $\lambda^\star$ that realizes all durations specified in $D$.
+Let $e^\star$ denote the edge initially picked by the algorithm.
+For all edges $e$ let $\lambda(e)=(\lambda^\star(e)-\lambda^\star(e^\star)+1)\bmod \Delta$.
+Clearly, the labeling $\lambda$ also realizes all durations specified in $D$ since $\lambda$ is obtained by adding the constant $(1-\lambda^\star(e^\star))$ modulo $\Delta$ to all labels of $\lambda^\star$ which does not change the duration of any temporal path, that is all durations in $(G,\lambda^\star)$ are the same as their counterparts in $(G,\lambda)$.
+We claim that our algorithm computes and outputs $\lambda$.
+
+Prove that our algorithm computes $\lambda$ by induction on the distance of the labeled edges to $e^\star$, where the distance of two edges $e,e'$ is defined as the length of a shortest path that uses $e$ as its first edge and $e'$ as its last edge.
+
+Initially, our algorithm labels $e^\star$ with one, which equals $\lambda(e^\star)$.
+Now let $e$ be an edge popped off the queue by the algorithm in some iteration.
+Let $e'$ be the edge incident with $e$ that already obtained a label and is considered by the algorithm.
+Since $G$ is a tree, we have that $e'$ is closer to $e^\star$ than $e$.
+By induction we have that the algorithm labeled $e'$ with $\lambda(e')$.
+Assume that $e=\{u,v\}$ and $e'=\{v,w\}$.
+Since $G$ is a tree there is only one path from $u$ to $w$ in $G$ and it uses edges $e$ and $e'$.
+It follows that $\lambda(e')-\lambda(e)+1=D_{u,w}$ if $\lambda(e')>\lambda(e)$, and $\lambda(e')-\lambda(e)+\Delta+1=D_{u,w}$ otherwise.
+Our algorithm labels $e$ with $(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
+It is straightforward to verify that the label of $e$ computed by the algorithm equals $\lambda(e)$.
+It follows that the algorithm computes $\lambda$.
+%    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
+%    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
+%    
+%    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
+%    We now take the unique path $P_{i,j}$ in $G$, 
+%    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
+%    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
+%    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
+%    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
+%    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
+%    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
+%    When we have exhausted the $i$-th row of $D$,
+%    \ie vertex $v_i$ now reaches every vertex of $G$,
+%    we continue and repeat the procedure for all other vertices.
+%    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
+%    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
+%    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
+%    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
+%        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
+%    \end{claim}
+%
+%
+%    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
+%    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
+%    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
+%    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
+%    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
+%    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
+%    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
+%    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
 Therefore, all together the whole algorithm is performed in polynomial time.
@@
 
-In this section we show how to generalize the polynomial-time algorithm for trees.
+Recall from \cref{sec:treealgo} that the main reason, for which \deltaExact\ is straightforward to solve on trees, is twofold: 
+\begin{itemize}
+    \item between any pair of vertices $v_i$ and $v_j$ in the tree $T$, there is a \emph{unique} path $P$ in $T$ from $v_i$ to $v_j$, and 
+    \item in any periodic temporal graph $(T,\lambda,\Delta)$ and any fastest temporal path $P=((e_1,t_1),\ldots,(e_i,t_i),\ldots,(e_j,t_j),\ldots,(e_\ell,t_\ell))$ from $v_1$ to $v_{\ell}$ we have that the sub-path $P'=((e_i,t_i),\ldots,(e_j,t_j))$ is also a fastest temporal path from $v_i$ to $v_j$.
+\end{itemize}
+However, these two nice properties do not hold when the underlying graph is not a tree.
+For example, in~\cref{fig:ftpExample}, the fastest temporal path from $u$ to $v$ is $P_{u,v}$ (depicted in blue) goes through~$w$, however the sub-path of $P_{u,v}$ that stops at $w$ is not the fastest temporal path from $u$ to $w$.
+The fastest temporal path from $u$ to $w$ consists only on the direct edge $uw$ (with label 9 and duration 1, depicted in red).
+%, while the fastest temporal path from $u$ to $v$ contains the four other edges (with labels 1, 3, 5, 7 and duration 7).
+
+Nevertheless, we prove in this section that we can still solve \deltaExact\ efficiently if the underlying graph is similar to a tree; more specifically we show the following result, which turns out to be non-trivial.
+
+% In this section we show how to generalize the polynomial-time algorithm for trees.
 Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
@@
 
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
+% In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subseteq E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
 The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
@@
 %one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$.%, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}[$\star$]\label{thm:FPTwrtFES}
-    \deltaExact\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-We then present the first part in more details and deffer the reader to the appendix for the remaining part and correctness proof.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-%
-%In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-In our case, however, this approach does not work. Mainly because of the
-	%A further difficulty arises from the 
- somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
- Besides that, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
 
@@
 
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' and specific ``graph constructions'' between which we guess representative fastest paths.
-    \item For each guess %(also called ``paths configuration'') 
-    we create one Integer Linear Program (ILP).
-    \item We show that we can determine most labels along each path. We show that the number of labels we cannot determine is small. 
-    \item For each non-determined label we introduce a variable for an ILP.
-    \item We use equality and inequality constraints in each ILP to ensure that the fastest temporal path from $u$ to $v$ is of duration $D_{u,v}$, while any other path is of duration at least $D_{u,v}$.
-    \item We compute a solution to each of the ILPs (if it exists) and construct a labeling from that solution.
-Since each ILP has a few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-    If none of the ILP instances give a positive solution, then there exists no labeling realizing given matrix.
-    This is true because considering all guesses of fastest temporal paths is equivalent to exhaustively searching through all possible temporal paths between vertices.
-\end{itemize}
-
-\subsubsection{First part of the FPT algorithm}
+\begin{theorem}[$\star$]\label{thm:FPTwrtFES}
+    \deltaExact\ is in FPT when parameterized by the feedback edge number of the underlying graph.
+\end{theorem}
+
+From \cref{thm:W1wrtFVS} and \cref{thm:FPTwrtFES} we immediately get the following, which is the main result of the paper.
+
+\begin{corollary}
+\deltaExact\ is:
+\begin{itemize}
+    \item in FPT when parameterized by the \emph{feedback edge number} or any larger parameter, such as the \emph{maximum leaf number}.
+    \item W[1]-hard when parameterized by the \emph{feedback vertex number} or any smaller parameter, such as: 
+    \emph{treewidth}, 
+    \emph{degeneracy}, 
+    \emph{cliquewidth}, 
+    \emph{distance to chordal graphs}, and 
+    \emph{distance to outerplanar graphs}.
+\end{itemize}
+\end{corollary}
+
+Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph.
+Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$. 
+However, 
+% due to the difficulties illustrated in~\cref{fig:ftpExample}, 
+for an FPT algorithm with respect to $k$, we cannot afford to guess the edges of the fastest temporal path for each of the $O(n^2)$ pairs of vertices. 
+To overcome this difficulty, our algorithm follows this high-level strategy:
+\begin{itemize}
+    %%%\item We perform a preprocessing step by iteratively removing all vertices of degree one.
+    \item We identify a small number $f(k)$ of ``important vertices''; these consist of the sets that we call $U, U^{\ast}, Z^{\ast}$.
+    \item For each pair $u,v$ of important vertices, we guess the edges of the fastest temporal path from $u$ to $v$ (and from $v$ to $u$).
+    \item From these guesses we can still not deduce the edges of the fastest temporal paths between many pairs of non-important vertices.
+However, as we prove, it suffices to guess only a small number of specific auxiliary structures (to be defined later).
+    \item From these guesses we deduce fixed relationships between the labels of most of the edges of the graph. 
+    \item For all the edges, for which we do not have deduced a label yet, we introduce a \emph{variable}. Using all these variables, we build an Integer Linear Program (ILP). 
+    Among the constraints in this ILP we have that, for each of the $O(n^2)$ pairs of vertices $u,v$ in the graph, the duration of one specific temporal path from $u$ to $v$ (according to our guesses) is \emph{equal} to the desired duration $D_{u,v}$, while the duration of each of the other temporal paths from $u$ to $v$ is \emph{at least} $D_{u,v}$.
+    \item By making any of the above guesses, we restrict the solution space for the problem \deltaExact.
+This restricted solution space coincides with the set of feasible solutions to the resulting ILP.
+Furthermore, the set of feasible solutions for all constructed ILPs coincide with the set of all solutions to \deltaExact\ (\ie regardless of our guesses).
+As each ILP can be solved in FPT time with respect to $k$ by Lenstra's Theorem~\cite{Lenstra1983Integer} (the number of variables is upper bounded by a function of $k$), we obtain our FPT algorithm for \deltaExact\ with respect to $k$.
+\end{itemize}
+
 We now present the first part of our FPT algorithm.
+
+\subparagraph{Important vertices.}
 Let $D$ be the input matrix of \deltaExact\, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
@@
 %Note that $F$ is also a minimum feedback edge set of $G$.
-Then we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
+Then we determine the set $U$ (the \emph{``vertices of interest''}), and the set $U^*$ (the neighbors of the vertices of interest), as follows.
 Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
+Let $V_1 \subseteq V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subseteq V(G')$ be the set of vertices of degree two in $T$ which are incident to at least one edge in $F$, 
+and let $V_3 \subseteq V(G')$ be the set of vertices of degree at least $3$ in $T$. 
 Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
@@
 Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we iterate through all pairs of vertices $v_i, v_j \in V(G)$ and 
-first guess the underlying path $P$ of a fastest temporal path from $v_i$ to $v_j$, which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-It is important to point out that the number of constraint and number of variables are not related, while we introduced all of the necessary constraints, we manage to create only a small number of variables (upper-bounded by some function in $k$).
-%Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$, therefore we do not 
-%
-For an easier understanding and the analysis of the algorithm we give the following definition.
+Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
+
+% \medskip 
+% \noindent We can solve \deltaExact\  by 
+% for every pair of vertices $v_i, v_j \in V(G)$ we
+% \begin{itemize}
+%     \item determine the underlying path $P$ of the fastest temporal path from $v_i$ to $v_j$,
+% for which we introduce the equality constraint (\ie $d(P) = D_{v_i, v_j}$), and %in the ILP
+% \item make sure that every other path $P'$ from $v_i$ to $v_j$ is not faster than $P$ (\ie $d(P') \geq D_{v_i, v_j}$). %in the ILP
+% \end{itemize}
+% One could easily achieve this by ``guessing'' the fastest paths among each pair of vertices, but this would result in too many guesses. 
+% With this in mind we create the following guesses.
+
+\subparagraph{Guesses.} 
+For every pair of important vertices $u,v \in U \cup U^{\ast} \cup Z^{\ast}$, we guess the sequence of edges in the fastest temporal path from $u$ to $v$.
+Since $U \cup U^{\ast} \cup Z^{\ast}\in O(k^2)$ and there are $k^{O(k)}$ possibilities for a sequence of edges between a fixed vertex pair, we have $k^{O(k^5)}$ overall possible guesses.
+We  defer further details to the Appendix (see guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-6}}}).
+
+\setcounter{guesscounter}{6}
+
+Unfortunately the above guesses do not provide us with enough information to be able to determine all fastest paths. For example consider the case depicted in the FIGURE TODO. 
+Therefore we introduce some more guesses. To do this we have to first define the following.
 \begin{definition}\label{def:segments}
@@
 \end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$. 
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
+Note by \cref{def:segments} that $S_{u,v} \neq S_{v,u}$. 
+Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or it consists of a sequence of some segments.
 Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
@@
 \end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-%\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
-%Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
-%if the fastest path between two vertices is not uniquely determined, we denote it by $\leadsto$.
+
+% We now continue with our guessing.
+To describe the next guesses, we introduce the following notation.
+Let $u,v,x$ be three vertices in $G'$.
+We write $u \leadsto x \rightarrow v$ to denote a temporal path from $u$ to $v$ that passes through $x$, and then goes directly to $v$ (via one edge).
+%In the case when we want to guess the fastest path from $u$, that passes through vertex $x$ (not necessarily via one edge), and then goes directly to $v$ (via one edge), we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
 We guess the following structures.
-%\noindent\textbf{Basic guesses:}
-\begin{enumerate}[G-1.]
-	\setcounter{enumi}{\value{guesscounter}}
-	\item \label{FPT-guessFTPamongU}
-	The fastest temporal paths between all pairs of vertices of $U$.
-	For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-	Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-	%If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-	Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths between all pairs of vertices in $U$.
-	\item \label{FPT-guessFTPamongZstar}
-	The fastest temporal paths between all pairs of vertices in $Z^*$, 
-	which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-	\item \label{FPT-guessFTPamongUstar}
-	The fastest temporal paths between all pairs of vertices in $U^*$.
-	This gives us $O(k^{k^6})$ guesses.
-	\item \label{FPT-guessFTPamongUandUstar}
-	The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-	and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-	This gives us $O(k^{k^4})$ guesses.
-	\item \label{FPT-guessFTPamongUandZstar}
-	The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-	and vice versa.
-	This gives us $O(k^{k^3})$ guesses.
-	\item \label{FPT-guessFTPamongUstarandZstar}
-	The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-	and vice versa.
-	This gives us $O(k^{k^4})$ guesses.
-	\setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-\noindent
 \begin{enumerate}[G-1.]
@@
 		and $u \leadsto z \rightarrow z_{r-1}$
-		(see guess~G-\ref{FPT:guess-uToSegmentz2}).
+		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-uToSegmentz2}}}}).
 	\end{enumerate}
@@
 	For an example see~\cref{fig:FPT-guessG7}.
-	Detailed analysis follows arguing from above (as in G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}) and is deferred to Appendix.
+	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
 	% counter for guesses continues
@@
 			\includegraphics{fig-guess1}}
-		\caption{Example of an Inner segment guess I (G-\ref{FPT-guessFTPamongv2z2}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
 			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
@@
 			\includegraphics{fig-guess2}}
-		\caption{Example of an Inner segment guess II (G-\ref{FPT:guess-uToSegmentz2}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
 			\label{fig:FPT-guessG5}}
@@
 			\includegraphics{fig-guess3}}
-		\caption{Example of a Split vertex guess I (G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}), where, for a fixed vertex $v_i \in S_{u,v}$,
+		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
 			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
@@
 			\includegraphics{fig-guess4}}
-		\caption{Example of a Split vertex guess II (G-\ref{FPT:guess-splitFromUtoAnotherSegment}), where, for a vertex of interest $w$, 
+		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
 			we
@@
 	\end{subfigure}
-	\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
+	\caption{An example of guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
 \end{figure}
 %
-We create all of the above guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential) 
-and create one ILP instance for each case.
-
-For each of the ILP instances we iterate through all pairs of vertices $u,v \in V(G)$ and, using the above guesses, determine, not only the fastest path $P$ from $u$ to $v$, but also all other paths $P'_i$.
-For the labels of edges of the fastest path $P$ we introduce the equality constraint, while for the labels of the edges of all other paths $P'_i$ we introduce the inequality constraint (\ie the duration $d(P_i')$ of any $P'_i$ cannot be smaller than $d(P)=D_{u,v}$).
-We can do this efficiently, while introducing only a small number of variables,
-which ensures that each ILP is solved in an FPT-time.
+
+There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that are deferred to the Appendix.
+We prove that there are $f(k)$ combinations of guesses and for each one we create an ILP with $f(k)$ variables and $f(k)\cdot |D|^{O(1)}$ constraints.
+%We create all of the above guesses independently.
+%We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
+%After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential) 
+%and create one ILP instance for each case.
+%
+%For each of the ILP instances we iterate through all pairs of vertices $u,v \in V(G)$ and, using the above guesses, determine, not only the fastest path $P$ from $u$ to $v$, but also all other paths $P'_i$.
+%For the labels of edges of the fastest path $P$ we introduce the equality constraint, while for the labels of the edges of all other paths $P'_i$ we introduce the inequality constraint (\ie the duration $d(P_i')$ of any $P'_i$ cannot be smaller than $d(P)=D_{u,v}$).
+%We can do this efficiently, while introducing only a small number of variables,
+%which ensures that each ILP is solved in an FPT-time.
 For detailed explanation and proofs of this part see Appendix.
-
-\todo{Argue why each (some) of the guesses are important}
 

### 2023-09-22 STACS2023/nina_shortversion.tex

@@
 Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we iterate through all pairs of vertices $v_i, v_j \in V(G)$ and 
-first guess the underlying path $P$ of a fastest temporal path from $v_i$ to $v_j$, which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-It is important to point out that the number of constraint and number of variables are not related, while we introduced all of the necessary constraints, we manage to create only a small number of variables (upper-bounded by some function in $k$).
-%Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$, therefore we do not 
-%
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}\label{def:segments}
-	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
-	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$. 
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-	There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-%\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
+To solve \deltaExact\ correctly it is necessary that for every pair of vertices $v_i, v_j \in V(G)$ we
+\begin{itemize}
+    \item determine the underlying path $P$ of the fastest temporal path from $v_i$ to $v_j$,
+for which we introduce the equality constraint (\ie $d(P) = D_{v_i, v_j}$), and %in the ILP
+\item make sure that every other path $P'$ from $v_i$ to $v_j$ is not faster than $P$ (\ie $d(P') \geq D_{v_i, v_j}$). %in the ILP
+\end{itemize}
+One could easily achieve this by ``guessing'' the fastest paths among each pair of vertices, but this would result in too many guesses. 
+For problem to remain feasible, one should create only a small number of guesses.
+With this in mind we create the following guesses.
+%It's important to mention that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
 %Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
 %if the fastest path between two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
 %\noindent\textbf{Basic guesses:}
@@
 \end{enumerate}
-\noindent
+
+Unfortunately the above guesses do not provide us with enough information to be able to determine all fastest paths. For example consider the case depicted in the FIGURE TODO. 
+Therefore we introduce some more guesses. To do this we have to first define the following.
+\begin{definition}\label{def:segments}
+	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
+	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
+	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
+\end{definition}
+Note, from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$. 
+Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
+Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
+\begin{corollary}\label{obs:FPT-k2segments}
+	There are at most $O(k^2)$ segments in $G'$.
+\end{corollary}
+We now continue with our guessing.
+In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
+We guess the following structures.
 \begin{enumerate}[G-1.]
@@
 
-\todo{Argue why each (some) of the guesses are important}
-
 \section{Conclusion}\label{sec:conclusion}

### 2023-09-22 STACS2023/STACS23-shortversion.tex
Changes of the short version

@@
 		and $u \leadsto z \rightarrow z_{r-1}$
-		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-uToSegmentz2}}}}).
+		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
 	\end{enumerate}
@@
 	For an example see~\cref{fig:FPT-guessG7}.
-	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
+	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
 	% counter for guesses continues
@@
 			\includegraphics{fig-guess1}}
-		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
 			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
@@
 			\includegraphics{fig-guess2}}
-		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
 			\label{fig:FPT-guessG5}}
@@
 			\includegraphics{fig-guess3}}
-		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
+		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
 			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
@@
 			\includegraphics{fig-guess4}}
-		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
+		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
 			we

### 2023-09-22 STACS2023/STACS23-longversion.tex
STACS23 initial files

--- 2023-09-18 ISAAC2023/ISAAC23-longversion.tex
@@
 
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
+In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subseteq E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
 The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
@@
 Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
+Let $V_1 \subseteq V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subseteq V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
+and let $V_3 \subseteq V(G')$ be the set of vertices of degree at least $3$ in $T$. 
 Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
@@
         and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
+        Note $R^{i-1} \subseteq R^x$.
         Similarly,

### 2023-09-22 STACS2023/STACS23-shortversion.tex

@@
 
-Unfortunately the above guesses do not provide us with enough information to be able to determine all fastest paths. For example consider the case depicted in the FIGURE TODO. 
+\begin{figure}[t]
+	\centering
+	%\includegraphics{fig-exampleg10}
+	\caption{In the above graph vertices $v_1, v_{11}, w$ are in $U$, while $v_2, v_{10}$ are in $U^*$. 
+		Numbers above all $v_i$ represent the values of the fastest temporal paths from $w$ to each of them (\ie the entries in the $w$-th row of matrix $D$).
+		From the basic guesses we know the fastest temporal path $P$ from $w$ to $v_2$ (depicted in blue) and the fastest temporal path $Q$ from $w$ to $v_{10}$.
+		From the values of durations from $w$ to each $v_i$ we cannot 
+		determine the fastest paths from $w$ to all $v_i$.
+		More precisely, we know that $w$ reaches $v_2, v_3, v_4, v_5$ (resp.~$v_{10}, v_{9}, v_{9}, v_{7}$) 
+		by first using the path $P$ (resp.~$Q$) and then proceeding through the vertices,
+		but we do not know how $w$ reaches $v_6$ the fastest.
+		Therefore we have to introduce some more guesses.
+  \label{fig:guesses-advanced}}
+\end{figure}
+
+Unfortunately the above guesses do not provide us with enough information to be able to determine all fastest paths. For example consider the case depicted in \cref{fig:guesses-advanced}. 
 Therefore we introduce some more guesses. To do this we have to first define the following.
@@
 There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that are deferred to the Appendix. 
-We prove that there are $f(k)$ combinations of guesses and for each one we create an ILP with $f(k)$ variables and $f(k)\cdot |D|^{O(1)}$ constraints.
+We prove in the Appendix that, for all guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-12}}}, there are in total at most $f(k)$ possible choices, and for each one of them we create an ILP with at most $f(k)$ variables and at most $f(k)\cdot |D|^{O(1)}$ constraints.
+Each of these ILPs can be solved in FPT time by Lenstra's Theorem~\cite{Lenstra1983Integer}.
 %We create all of the above guesses independently.

### 2023-09-25 Figures/fig-motivationExample.tex
Final version of the STACS submission

@@
 	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
+	\draw (v1) -- node[label=above:$1$] {} (v2) -- node[label=above:$3$] {}  (v3) -- node[label=above:$5$] {} (v4) -- node[label=above:$7$] {} (v5);
+	\draw (v1) to [out=80,in=100,distance=2cm] node[label=above:$9$] {} (v3);
 

### 2023-09-25 STACS2023/STACS23-shortversion.tex
Final version of the STACS submission

@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate, anonymous]{lipics-v2021}
 %This is a template for producing LIPIcs articles. 
@@
 \usepackage{cite} %order citations by increasing number
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
+\title{Temporal graph realization from fastest paths} %TODO Please add
+%%%Realizing temporal graphs from fastest travel times
 
@@
 
-\author{Hendrik~Molter}{Department of Computer Science, Ben-Gurion~University~of~the~Negev, 
-Beer-Sheva, 
-Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1456/18, and the ERC, grant number 949707.}
+\author{Hendrik~Molter}{Department of Computer Science, Ben-Gurion~University~of~the~Negev, Beer-Sheva, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1456/18, and the ERC, grant number 949707.}
 
@@
 such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's (e.g.\ [Erd\H{o}s and Gallai, 1960], [Hakimi and Yau, 1965]), and this area of research remains active until nowadays.
+The variations of the problem on static graphs has been well studied and understood since the 1960's (e.g.\ [Erd\H{o}s and Gallai, 1960], [Hakimi and Yau, 1965]).
+% , and this area of research remains active until nowadays.
 
 As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (\ie non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
+First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree.
 Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
+We prove a tight classification between such parameters that allow fixed-parameter tractability (FPT)
+and those which imply W[1]-hardness. 
+We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} (and therefore also any smaller parameter such as \emph{treewidth}, \emph{degeneracy}, and \emph{cliquewidth}) of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} (and therefore also any larger parameter such as \emph{maximum leaf number}) of the underlying graph.
 
@@
 
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
+The (static) \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
 The motivation for graph realization problems stems both from ``verification'' and from network design applications in engineering. 
@@
 
-In the simplest version of a graph realization problem with respect to vertex distances, 
+In the simplest version of a (static) graph realization problem with respect to vertex distances, 
 we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
@@
 A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
+The \emph{duration} of the fastest temporal path from $u$ to $v$ is denoted by $d(u,v)$.
 \end{definition}
@@
 
-%In an arbitrary (non-periodic) temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected.
-
-%In order to focus on the smallest duration of temporal paths, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, \ie on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-
-%Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-
 Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
 Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
+In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of~$G$; see \cref{fig:periodic-example} for an illustration. 
 When it is clear from the context, we drop $\Delta$ form the notation and 
 we denote the ($\Delta$-periodic) temporal graph by $(G,\lambda)$.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
+Given a duration matrix~$D$, it is easy to observe that, similarly to the static case, if $D_{i,j}=1$ then $v_i$ and $v_j$ must be connected by an edge.
+We call the graph defined by these edges the \emph{underlying graph} of $D$.
 
@@
 
+\begin{figure}[t]
+    \centering
+	\begin{tikzpicture}[xscale=1.5]
+		%%%S_uv
+		\node[vert,label=below:$v_1$] (1) at (1,0) {};
+		\node[vert,label=below:$v_2$] (2) at (3,0) {};
+		\node[vert,label=below:$v_3$] (3) at (5,0) {};
+		\node[vert,label=below:$v_4$] (4) at (7,0) {};
+		\node[vert,label=below:$v_5$] (5) at (9,0) {};
+		\draw (1) -- node[label=above:$10t+7$] {} (2) -- node[label=above:$10t+3$] {}  (3) -- node[label=above:$10t+5$] {} (4) -- node[label=above:$10t+1$] {} (5);	
+	\end{tikzpicture}
+	\caption{An example of a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, where $\Delta = 10$ and the 10-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,10\}$ is as follows: $\lambda(v_1 v_2)=7$, $\lambda(v_2 v_3)=3$, $\lambda(v_3 v_4)=5$, and $\lambda(v_4 v_5)=1$.
+    Here, the fastest temporal path from $u$ to $v$ traverses the first edge $v_1v_2$ at time $7$, second edge $v_2v_3$ a time $13$, third edge $v_3v_4$ at time $15$ and the last edge $v_4v_5$ at time $21$.
+    This results in the total duration of $15$ for the fastest temporal path from $v_1$ to $v_5$.
+	\label{fig:periodic-example}}
+\end{figure}
+
 We focus on exact algorithms.
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
+We start by showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
 To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
@@
 
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
+We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph (\cref{thm:W1wrtFVS}). 
 To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
@@
 The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-Note that our parameterized hardness result rule out fixed-parameter tractability for several popular graph parameters such as treewidth and arboricity.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number $k$ of the underlying graph (\cref{thm:FPTwrtFES}), a parameter that is larger than the feedback vertex number.
+Note that our parameterized hardness result with respect to the feedback vertex number 
+also implies W[1]-hardness for any smaller parameter, such as \emph{treewidth}, \emph{degeneracy}, \emph{cliquewidth}, 
+\emph{distance to chordal graphs}, and \emph{distance to outerplanar graphs}.
+
+We complement this hardness result by showing that \deltaExact\ is fixed-parameter tractable (FPT) with respect to the \emph{feedback edge number} $k$ of the underlying graph (\cref{thm:FPTwrtFES}). 
+This result also implies an FPT algorithm for any larger parameter, such as the \emph{maximum leaf number}. 
+A similar phenomenon of getting W[1]-hardness with respect to the feedback vertex number, while getting an FPT algorithm with respect to the feedback edge number, has been observed only in a few other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
+
 Our FPT algorithm works as follows on a high level. 
-First we distinguish $O(k)$ vertices which we call ``interesting vertices''. 
-Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of~$k$. 
-Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (\ie bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
+First we distinguish $O(k^2)$ vertices which we call ``important vertices''. 
+Then, we guess the fastest temporal paths for each pair of these important vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of~$k$. 
+Then we also need to make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (\ie bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
 For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than~$D_{i,j}$.
@@
 To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
 Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
@@
 At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
+    When $G$ is constructed we run DFS algorithm on it and check that it has no cycles.
     If at any step we encounter a problem, our algorithm stops and returns a negative answer.
@@
     \centering
-	\begin{tikzpicture}[xscale=2,yscale=0.4]
+	\begin{tikzpicture}[xscale=2.2,yscale=0.5]
 	%%%S_uv
@@
 	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
 
@@
 	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
+
+	\draw (v1) -- node[label=above:$1$] {} (v2) -- node[label=above:$3$] {}  (v3) -- node[label=above:$5$] {} (v4) -- node[label=above:$7$] {} (v5);
+	\draw (v1) to [out=80,in=100,distance=2cm] node[label=above:$9$] {} (v3);
+
 \end{tikzpicture}
@@
 
-We now present the first part of our FPT algorithm.
+We now present the first part of our FPT algorithm, that is, identifying important vertices and guessing information about the fastest temporal paths.
+A full description of the algorithm is deferred to the Appendix.
 
@@
 Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
+For an illustration see \cref{fig:labelingVertices}.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{fig-example-names-vertices}
+	\caption{An example of a graph with its important vertices: $U$ (in blue), $U^*$ (in green) and $Z^*$ (in orange).
+    Corresponding feedback edges are marked with a thick red line, while dashed edges represent the edges (and vertices) ``removed'' from $G'$ at the initial step.
+	\label{fig:labelingVertices}}
+\end{figure}
 
@@
 	\centering
-	%\includegraphics{fig-exampleg10}
+	\includegraphics[width=0.75\columnwidth]{fig-exampleg10}
 	\caption{In the above graph vertices $v_1, v_{11}, w$ are in $U$, while $v_2, v_{10}$ are in $U^*$. 
@@
 
-Unfortunately the above guesses do not provide us with enough information to be able to determine all fastest paths. For example consider the case depicted in \cref{fig:guesses-advanced}. 
-Therefore we introduce some more guesses. To do this we have to first define the following.
+With the information provided by the described guesses we are still not able to determine all fastest paths. For example consider the case depicted in \cref{fig:guesses-advanced}. 
+Therefore we introduce additional guesses that provide us with sufficient information to determine all fastest paths. To do this we have to first define the following.
 \begin{definition}\label{def:segments}
@@
 \end{corollary}
-
 % We now continue with our guessing.
@@
 	%first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-	We want to guess the following fastest temporal path
+	We want to guess the fastest temporal path
 	$v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
@@
 	Since there are $O(k^2)$ segments in $G'$,
-	there are $O(k^{k^5})$ possible paths of this form. \\
+	there are $k^{O(k^5)}$ possible paths of this form. \\
 	Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
@@
 	\\
-	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
+	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $k^{O(k)}$ different possible such paths, therefore we make $k^{O(k^4)}$ guesses for these paths.
 	%
@@
 		We repeat this procedure for all pairs of segments,
-		which results in producing $O(k^{k^6})$ new guesses.
+		which results in producing $k^{O(k^5)}$ new guesses.
 		Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
@@
 	We repeat this for all vertices of interest, and all segments,
-	which produces $O(k^{k^2})$ new guesses.
+	which produces $k^{O(k^2)}$ new guesses.
 	%
@@
 		\centering
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.88\linewidth}{!}{
 			\includegraphics{fig-guess1}}
@@
 		\centering
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.88\linewidth}{!}{
 
@@
 	\begin{subfigure}[b]{0.48\textwidth}
+		\vspace{-0.4cm}
         \centering
-		\resizebox{1.2\linewidth}{!}{
+		\resizebox{0.98\linewidth}{!}{
 			%
@@
 		\centering
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.88\linewidth}{!}{
 			\includegraphics{fig-guess4}}
@@
 	\end{subfigure}
-	\caption{An example of guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
+	\caption{Illustration of the guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
 \end{figure}
@@
 
-\clearpage
-
-\appendix
+%\clearpage
+
+%\appendix
 

### 2023-09-25 TGR Extended - New paper/Realizing TG - extended.tex
Final version of the STACS submission

@@
 
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
+\title{Realizing temporal graphs from fastest paths II} %TODO Please add
 
@@
 
-\problemdef{\DeltaUpperBoundLong}
+\problemdef{\DeltaUpperBoundLong (\deltaUpperBound)}
 {A static graph $G=(V,E)$ with $n$ vertices, $n \times n$ matrix $D$ of positive integers and a bijective mapping $\phi$ from vertices $V$ of $G$ to the rows/columns of the matrix $D$.}
@@
 	Let $\gamma = min \{ \alpha - \beta, \Delta + \beta - \alpha\}$,
-	i.e. $\gamma$ is the minimum travel delay at vertex $v_i$ when traversing edges $e_{i-1}, e_i$, where indices are taken modulo $4$.
+	i.e. $\gamma$ is the minimum travel delay at vertex $v_i$ when traversing first the edge $e_{i-1}$ and then $e_i$ (indices are taken modulo $4$).
 	We get that 
@@
 	then $D_{u,w} = D_{w,v}$
-	iff
-	$\lambda(e) \in \{\frac{\Delta}{2}, \Delta\}$, if $\Delta$ is even and
-	$\lambda(e) \in \{\Delta\}$, if $\Delta$ is odd,
-	for all $e \in E(P)$.
+	if and only if
+    for every edge $e \in E(P)$ it holds that that
+	$\lambda(e) \in \{\frac{\Delta}{2}, \Delta\}$, when $\Delta$ is even and
+	$\lambda(e) = \Delta$, when $\Delta$ is odd.
 \end{claim}
@@
 		If $\Delta$ is odd, we have a unique solution with the value $\alpha=\beta = \Delta$,
-		while in the case when $\Delta$ is odd we get that $\alpha, \beta \in \{\Delta, \frac{\Delta}{2}\}$. 
+		while in the case when $\Delta$ is even we get that $\alpha, \beta \in \{\Delta, \frac{\Delta}{2}\}$. 
 \end{proof}
 
-We can extend the above result to all graphs as we want to have a periodic labeling of a graph $G$, that gives rise to a symmetric matrix $D$. 
-Then the above has to hold for all pairs of vertices on distance $2$.
+In the case of a general graph $G$, the above still has to hold for any two vertices on distance $2$ apart.
 Therefore we get the following two results.
@@
 \end{theorem}
-
+\todo[inline]{Not all edges need to have labels from $\{\Delta, \Delta/2 \}$ - some of them can have whatever label.
+Think how these edges/graphs look like (example ``diamond with an inner path of length 2'' aka, $C_4$ with an extra vertex in the middle connecting a pair of opposite vertices).}
 \begin{proof}

### 2023-09-25 STACS2023/STACS23-longversion.tex
Final version of the STACS submission
Changes

@@
 
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
+\title{Temporal graph realization from fastest temporal paths} %TODO Please add
 
@@
 Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
+We prove a tight classification between such parameters that allow fixed-parameter tractability (FPT)
+and those which imply W[1]-hardness. 
+We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} (and therefore also any smaller parameter such as \emph{treewidth}, \emph{degeneracy}, and \emph{cliquewidth}) of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} (and therefore also any larger parameter such as \emph{maximum leaf number}) of the underlying graph.
 
@@
 Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
+In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of~$G$; see \cref{fig:periodic-example} for an illustration. 
 When it is clear from the context, we drop $\Delta$ form the notation and 
 we denote the ($\Delta$-periodic) temporal graph by $(G,\lambda)$.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
+Given a duration matrix~$D$, it is easy to observe that, similarly to the static case, if $D_{i,j}=1$ then $v_i$ and $v_j$ must be connected by an edge.
+We call the graph defined by these edges the \emph{underlying graph} of $D$.
+
+\begin{figure}[t]
+    \centering
+	\begin{tikzpicture}[xscale=1.5]
+		%%%S_uv
+		\node[vert,label=below:$v_1$] (1) at (1,0) {};
+		\node[vert,label=below:$v_2$] (2) at (3,0) {};
+		\node[vert,label=below:$v_3$] (3) at (5,0) {};
+		\node[vert,label=below:$v_4$] (4) at (7,0) {};
+		\node[vert,label=below:$v_5$] (5) at (9,0) {};
+		\draw (1) -- node[label=above:$10t+7$] {} (2) -- node[label=above:$10t+3$] {}  (3) -- node[label=above:$10t+5$] {} (4) -- node[label=above:$10t+1$] {} (5);	
+	\end{tikzpicture}
+	\caption{An example of a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, where $\Delta = 10$ and the 10-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,10\}$ is as follows: $\lambda(v_1 v_2)=7$, $\lambda(v_2 v_3)=3$, $\lambda(v_3 v_4)=5$, and $\lambda(v_4 v_5)=1$.
+    Here, the fastest temporal path from $u$ to $v$ traverses the first edge $v_1v_2$ at time $7$, second edge $v_2v_3$ a time $13$, third edge $v_3v_4$ at time $15$ and the last edge $v_4v_5$ at time $21$.
+    This results in the total duration of $15$ for the fastest temporal path from $v_1$ to $v_5$.
+	\label{fig:periodic-example}}
+\end{figure}
 
@@
 We focus on exact algorithms.
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
+We start by showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
 To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
@@
 The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-Note that our parameterized hardness result rule out fixed-parameter tractability for several popular graph parameters such as treewidth and arboricity.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number $k$ of the underlying graph (\cref{thm:FPTwrtFES}), a parameter that is larger than the feedback vertex number.
+Note that our parameterized hardness result rule out fixed-parameter tractability for several popular graph parameters such as \emph{treewidth}, \emph{degeneracy}, \emph{cliquewidth}, 
+\emph{distance to chordal graphs}, and \emph{distance to outerplanar graphs}.
+
+We complement this hardness result by showing that \deltaExact\ is fixed-parameter tractable (FPT) with respect to the \emph{feedback edge number} $k$ of the underlying graph (\cref{thm:FPTwrtFES}). 
+This result also implies an FPT algorithm for any larger parameter, such as the \emph{maximum leaf number}. 
+A similar phenomenon of getting W[1]-hardness with respect to the feedback vertex number, while getting an FPT algorithm with respect to the feedback edge number, has been observed only in a few other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
+
 Our FPT algorithm works as follows on a high level. 
-First we distinguish $O(k)$ vertices which we call ``interesting vertices''. 
-Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of~$k$. 
-Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (i.e.~bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
+First we distinguish $O(k^2)$ vertices which we call ``important vertices''. 
+Then, we guess the fastest temporal paths for each pair of these important vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of~$k$. 
+Then we also need to make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (\ie bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices.
 For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than~$D_{i,j}$.
@@
 To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
 
@@
 Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths between all pairs of vertices in $(G,\lambda,\Delta)$.
+which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
 
@@
 In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
+First we give in \cref{sec:treealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
 In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
@@
 Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ between them.
+Let $v_i,v_j$ be two arbitrary vertices in $G$. Then, by the properties of trees, we know that there exists a unique (static) path $P$ between them.
 Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
 and therefore are the fastest.
-Then $D$ is of the following fo\rm:
+Then $D$ is of the following form:
 \begin{equation*}
@@
 
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subseteq E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
+Recall from \cref{sec:treealgo} that the main reason, for which \deltaExact\ is straightforward to solve on trees, is twofold: 
+\begin{itemize}
+    \item between any pair of vertices $v_i$ and $v_j$ in the tree $T$, there is a \emph{unique} path $P$ in $T$ from $v_i$ to $v_j$, and 
+    \item in any periodic temporal graph $(T,\lambda,\Delta)$ and any fastest temporal path $P=((e_1,t_1),\ldots,(e_i,t_i),\ldots,(e_j,t_j),\ldots,(e_\ell,t_\ell))$ from $v_1$ to $v_{\ell}$ we have that the sub-path $P'=((e_i,t_i),\ldots,(e_j,t_j))$ is also a fastest temporal path from $v_i$ to $v_j$.
+\end{itemize}
+However, these two nice properties do not hold when the underlying graph is not a tree.
+For example, in~\cref{fig:ftpExample}, the fastest temporal path from $u$ to $v$ is $P_{u,v}$ (depicted in blue) goes through~$w$, however the sub-path of $P_{u,v}$ that stops at $w$ is not the fastest temporal path from $u$ to $w$.
+The fastest temporal path from $u$ to $w$ consists only on the direct edge $uw$ (with label 9 and duration 1, depicted in red).
+%, while the fastest temporal path from $u$ to $v$ contains the four other edges (with labels 1, 3, 5, 7 and duration 7).
+
+Nevertheless, we prove in this section that we can still solve \deltaExact\ efficiently if the underlying graph is similar to a tree; more specifically we show the following result, which turns out to be non-trivial.
 
@@
     \centering
-	\includegraphics{fig-motivationExample}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
+	\begin{tikzpicture}[xscale=2.2,yscale=0.5]
+	%%%S_uv
+	\node[vert,label=below:$u$] (v1) at (1,0) {};
+	\node[vert] (v2) at (2,0) {};
+	\node[vert,label=below:$w$] (v3) at (3,0) {};
+	\node[vert] (v4) at (4,0) {};
+	\node[vert,label=below:$v$] (v5) at (5,0) {};
+
+	\draw[transform canvas={yshift=-1.5mm}, blue]
+	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
+
+	\draw[red]
+	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
+
+	\draw (v1) -- node[label=above:$1$] {} (v2) -- node[label=above:$3$] {}  (v3) -- node[label=above:$5$] {} (v4) -- node[label=above:$7$] {} (v5);
+	\draw (v1) to [out=80,in=100,distance=2cm] node[label=above:$9$] {} (v3);
+
+\end{tikzpicture}
+	\caption{An example of a temporal graph (with $\Delta \geq 9$), where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
 		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}\label{sec:conclusion}

### 2023-09-25 STACS2023/STACS23-shortversion.tex
Changes

@@
 \usepackage{cite} %order citations by increasing number
-\title{Temporal graph realization from fastest paths} %TODO Please add
+\title{Temporal graph realization from fastest temporal paths} %TODO Please add
 %%%Realizing temporal graphs from fastest travel times
@@
 By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-In \cref{sec:treealgo} that if the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
+We first show in \cref{sec:treealgo} that if the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
 In \cref{sec:FPT} we generalize this result.
@@
 
-Prove that our algorithm computes $\lambda$ by induction on the distance of the labeled edges to $e^\star$, where the distance of two edges $e,e'$ is defined as the length of a shortest path that uses $e$ as its first edge and $e'$ as its last edge.
+We prove that our algorithm computes $\lambda$ by induction on the distance of the labeled edges to $e^\star$, where the distance of two edges $e,e'$ is defined as the length of a shortest path that uses $e$ as its first edge and $e'$ as its last edge.
 

### 2023-09-25 STACS2023/STACS23-longversion.tex
All changes to STACS long done

@@
 
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths between vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths between some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths between vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures between them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
 \begin{figure}[t]
@@
 
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an Integer Linear Program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
+\begin{theorem}\label{thm:FPTwrtFES}
+    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
+\end{theorem}
+
+From \cref{thm:W1wrtFVS} and \cref{thm:FPTwrtFES} we immediately get the following, which is the main result of the paper.
+
+\begin{corollary}
+\deltaExact\ is:
+\begin{itemize}
+    \item in FPT when parameterized by the \emph{feedback edge number} or any larger parameter, such as the \emph{maximum leaf number}.
+    \item W[1]-hard when parameterized by the \emph{feedback vertex number} or any smaller parameter, such as: 
+    \emph{treewidth}, 
+    \emph{degeneracy}, 
+    \emph{cliquewidth}, 
+    \emph{distance to chordal graphs}, and 
+    \emph{distance to outerplanar graphs}.
+\end{itemize}
+\end{corollary}
+
+Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph.
+Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$. 
+However, 
+% due to the difficulties illustrated in~\cref{fig:ftpExample}, 
+for an FPT algorithm with respect to $k$, we cannot afford to guess the edges of the fastest temporal path for each of the $O(n^2)$ pairs of vertices. 
+To overcome this difficulty, our algorithm follows this high-level strategy:
+\begin{itemize}
+    %%%\item We perform a preprocessing step by iteratively removing all vertices of degree one.
+    \item We identify a small number $f(k)$ of ``important vertices''; these consist of the sets that we call $U, U^{\ast}, Z^{\ast}$.
+    \item For each pair $u,v$ of important vertices, we guess the edges of the fastest temporal path from $u$ to $v$ (and from $v$ to $u$).
+    \item From these guesses we can still not deduce the edges of the fastest temporal paths between many pairs of non-important vertices.
+However, as we prove, it suffices to guess only a small number of specific auxiliary structures (to be defined later).
+    \item From these guesses we deduce fixed relationships between the labels of most of the edges of the graph. 
+    \item For all the edges, for which we do not have deduced a label yet, we introduce a \emph{variable}. Using all these variables, we build an Integer Linear Program (ILP). 
+    Among the constraints in this ILP we have that, for each of the $O(n^2)$ pairs of vertices $u,v$ in the graph, the duration of one specific temporal path from $u$ to $v$ (according to our guesses) is \emph{equal} to the desired duration $D_{u,v}$, while the duration of each of the other temporal paths from $u$ to $v$ is \emph{at least} $D_{u,v}$.
+    \item By making any of the above guesses, we restrict the solution space for the problem \deltaExact.
+This restricted solution space coincides with the set of feasible solutions to the resulting ILP.
+Furthermore, the set of feasible solutions for all constructed ILPs coincide with the set of all solutions to \deltaExact\ (\ie regardless of our guesses).
+As each ILP can be solved in FPT time with respect to $k$ by Lenstra's Theorem~\cite{Lenstra1983Integer} (the number of variables is upper bounded by a function of $k$), we obtain our FPT algorithm for \deltaExact\ with respect to $k$.
 \end{itemize}
@@
 Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
+For an illustration see \cref{fig:labelingVertices}. Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{fig-example-names-vertices}
+	\caption{An example of a graph with its important vertices: $U$ (in blue), $U^*$ (in green) and $Z^*$ (in orange).
+    Corresponding feedback edges are marked with a thick red line, while dashed edges represent the edges (and vertices) ``removed'' from $G'$ at the initial step.
+	\label{fig:labelingVertices}}
+\end{figure}
 

### 2023-10-05 STACS2023/STACS23-longversion.tex
Some changes, added new meeting whiteboard

@@
 
-\title{Temporal graph realization from fastest temporal paths} %TODO Please add
+\title{Temporal graph realization from fastest paths} %TODO Please add
 
@@
 \begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations between its vertices, 
+In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
 while we focus on periodic temporal graphs. 
@@
 such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's (e.g.\ [Erd\H{o}s and Gallai, 1960], [Hakimi and Yau, 1965]), and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
+The variations of the problem on static graphs has been well studied and understood since the 1960's (e.g.\ [Erd\H{o}s and Gallai, 1960], [Hakimi and Yau, 1965]).
+% , and this area of research remains active until nowadays.
+
+As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (\ie non-temporal) counterpart. 
+First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree.
 Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
@@
 \end{abstract}
+
+% \clearpage
 
@@
 In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
 Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
@@
 \begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
+	\deltaExact\ is \NP-hard for all $\Delta \geq 3$.
 \end{theorem}
@@
 \begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
+    \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
 \end{theorem}
@@
 
-In the following, for every gadget, we first give a formal description of the underlying graph of this gadget (i.e.~not the complete distance sub-matrix of the gadget).
+In the following, for every gadget, we first give a formal description of the underlying graph of this gadget (\ie not the complete distance sub-matrix of the gadget).
 Afterwards, we define the corresponding entries in the distance matrix $D$.
@@
 By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
+We first show in \cref{sec:treealgo} that if the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
 In \cref{sec:FPT} we generalize this result.
@@
 Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3 - t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P, \lambda)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-Furthermore, we can make the following observation concerning subpaths of a fastest temporal path.
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
 
 \subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then, by the properties of trees, we know that there exists a unique (static) path $P$ between them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-\end{observation}
-
-Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
+We now provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
+Let $D$ be the input matrix and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
+Let $v_i,v_j$ be two arbitrary vertices in $G$, then we know that there exists a unique (static) path $P_{i,j}$ from $v_i$ to $v_j$. We will heavily exploit this in our algorithm.
 
@@
 At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
+    When $G$ is constructed we run DFS algorithm on it and check that it has no cycles.
     If at any step we encounter a problem, our algorithm stops and returns a negative answer.
 
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat the following procedure. From vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
+    Having computed $G$, our algorithm proceeds as follows.
+We pick an arbitrary edge $f$ and give it label one, that is, $\lambda(f)=1$.
+Now we push all edges incident with $f$ into a (initially empty) queue.
+Now we repeat the following as long as the queue is not empty:
+\begin{itemize}
+    \item Pop edge $e=\{u,v\}$ from the queue.
+Since $e$ was pushed into the queue, there is an edge $e'$ incident with $e$ that already obtained a label.
+Let w.l.o.g.\ $e'=\{v,w\}$.
+Then we set $\lambda(e)=(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
+    \item Push all edges incident with $e$ that have not received a label yet into the queue.
+\end{itemize}
+When the queue is empty, all edges have received a label.
+Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$.
+If this check succeeds for all vertex pairs, output the labelling $\lambda$, otherwise abort.
+
+It is easy to see that the described algorithm runs in polynomial time. In the remainder, we proof that it is correct.
+
+$(\Rightarrow)$: Since the algorithm checks at the end whether all durations specified in $D$ are realized by the corresponding fastest paths, we clearly face a yes-instance whenever the algorithm outputs a labeling.
+
+$(\Leftarrow)$: Assume we face a yes-instance, then there exists a labeling $\lambda^\star$ that realizes all durations specified in $D$.
+Let $e^\star$ denote the edge initially picked by the algorithm.
+For all edges $e$ let $\lambda(e)=(\lambda^\star(e)-\lambda^\star(e^\star)+1)\bmod \Delta$.
+Clearly, the labeling $\lambda$ also realizes all durations specified in $D$ since $\lambda$ is obtained by adding the constant $(1-\lambda^\star(e^\star))$ modulo $\Delta$ to all labels of $\lambda^\star$ which does not change the duration of any temporal path, that is all durations in $(G,\lambda^\star)$ are the same as their counterparts in $(G,\lambda)$.
+We claim that our algorithm computes and outputs $\lambda$.
+
+We prove that our algorithm computes $\lambda$ by induction on the distance of the labeled edges to $e^\star$, where the distance of two edges $e,e'$ is defined as the length of a shortest path that uses $e$ as its first edge and $e'$ as its last edge.
+
+Initially, our algorithm labels $e^\star$ with one, which equals $\lambda(e^\star)$.
+Now let $e$ be an edge popped off the queue by the algorithm in some iteration.
+Let $e'$ be the edge incident with $e$ that already obtained a label and is considered by the algorithm.
+Since $G$ is a tree, we have that $e'$ is closer to $e^\star$ than $e$.
+By induction we have that the algorithm labeled $e'$ with $\lambda(e')$.
+Assume that $e=\{u,v\}$ and $e'=\{v,w\}$.
+Since $G$ is a tree there is only one path from $u$ to $w$ in $G$ and it uses edges $e$ and $e'$.
+It follows that $\lambda(e')-\lambda(e)+1=D_{u,w}$ if $\lambda(e')>\lambda(e)$, and $\lambda(e')-\lambda(e)+\Delta+1=D_{u,w}$ otherwise.
+Our algorithm labels $e$ with $(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
+It is straightforward to verify that the label of $e$ computed by the algorithm equals $\lambda(e)$.
+It follows that the algorithm computes $\lambda$.
 \end{proof}
@@
 For example, in~\cref{fig:ftpExample}, the fastest temporal path from $u$ to $v$ is $P_{u,v}$ (depicted in blue) goes through~$w$, however the sub-path of $P_{u,v}$ that stops at $w$ is not the fastest temporal path from $u$ to $w$.
-The fastest temporal path from $u$ to $w$ consists only on the direct edge $uw$ (with label 9 and duration 1, depicted in red).
+The fastest temporal path from $u$ to $w$ consists only of the single edge $uw$ (with label $9$ and duration $1$, depicted in red).
 %, while the fastest temporal path from $u$ to $v$ contains the four other edges (with labels 1, 3, 5, 7 and duration 7).
@@
 \begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
+    \deltaExact\ is in FPT when parameterized by the feedback edge number of the underlying graph.
 \end{theorem}
@@
 Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
+Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
 For an illustration see \cref{fig:labelingVertices}. Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
@@
 For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
+This results in producing $f(k) \cdot |D| ^ {O(1)}$ constraints. 
 Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
@@
 Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
+To describe the guesses, we introduce the following notation.
+Let $u,v,x$ be three vertices in $G'$.
+We write $u \leadsto x \rightarrow v$ to denote a temporal path from $u$ to $v$ that passes through $x$, and then goes directly to $v$ (via one edge).
+If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
 if the fastest path between two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
+
+For every pair of important vertices $u,v \in U \cup U^{\ast} \cup Z^{\ast}$, we guess the sequence of edges in the fastest temporal path from $u$ to $v$.
+Since $U \cup U^{\ast} \cup Z^{\ast}\in O(k^2)$ and there are $k^{O(k)}$ possibilities for a sequence of edges between a fixed vertex pair, we have $k^{O(k^5)}$ overall possible guesses.
 \begin{enumerate}[G-1.]
+	\setcounter{enumi}{\value{guesscounter}}
     \item \label{FPT-guessFTPamongU}
     The fastest temporal paths between all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
+    For a pair $u,v$ of vertices in $U$, there are $k^{O(k)}$ possible paths in $G'$ between them. 
+    Therefore, we have to try all $k^{O(k)}$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
     %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths between all pairs of vertices in $U$.
+    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $k^{O(k^3)}$ different variations of the fastest temporal paths between all pairs of vertices in $U$.
     \item \label{FPT-guessFTPamongZstar}
     The fastest temporal paths between all pairs of vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
+    which by similar arguing as for vertices in $U$, gives us $k^{O(k^3)}$ guesses.
     \item \label{FPT-guessFTPamongUstar}
     The fastest temporal paths between all pairs of vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
+    This gives us $k^{O(k^5)}$ guesses.
     \item \label{FPT-guessFTPamongUandUstar}
@@
     and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
+    This gives us $k^{O(k^4)}$ guesses.
     \item \label{FPT-guessFTPamongUandZstar}
@@
     and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
+    This gives us $k^{O(k^3)}$ guesses.
     \item \label{FPT-guessFTPamongUstarandZstar}
@@
     and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
+    This gives us $k^{O(k^4)}$ guesses.
+	\setcounter{guesscounter}{\value{enumi}}
+\end{enumerate}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.75\columnwidth]{fig-exampleg10}
+	\caption{In the above graph vertices $v_1, v_{11}, w$ are in $U$, while $v_2, v_{10}$ are in $U^*$. 
+		Numbers above all $v_i$ represent the values of the fastest temporal paths from $w$ to each of them (\ie the entries in the $w$-th row of matrix $D$).
+		From the basic guesses we know the fastest temporal path $P$ from $w$ to $v_2$ (depicted in blue) and the fastest temporal path $Q$ from $w$ to $v_{10}$.
+		From the values of durations from $w$ to each $v_i$ we cannot 
+		determine the fastest paths from $w$ to all $v_i$.
+		More precisely, we know that $w$ reaches $v_2, v_3, v_4, v_5$ (resp.~$v_{10}, v_{9}, v_{9}, v_{7}$) 
+		by first using the path $P$ (resp.~$Q$) and then proceeding through the vertices,
+		but we do not know how $w$ reaches $v_6$ the fastest.
+		Therefore we have to introduce some more guesses.
+  \label{fig:guesses-advanced}}
+\end{figure}
+
+With the information provided by the described guesses we are still not able to determine all fastest paths. For example consider the case depicted in \cref{fig:guesses-advanced}. 
+Therefore we introduce additional guesses that provide us with sufficient information to determine all fastest paths.
+We guess the following structures.
+\begin{enumerate}[G-1.]
+	\setcounter{enumi}{\value{guesscounter}}
 	\item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
+	\textbf{Inner segment guess I}.
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments. %,
+	%first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
+	We want to guess the fastest temporal path
 	$v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
@@
 	Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
+	there are $k^{O(k^5)}$ possible paths of this form. \\
 	Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
+Furthermore note that we did not assume that $\{u,v\} \cap \{w,z\} = \emptyset$.
 Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
@@
 	\item \label{FPT:guess-uToSegmentz2}
+	\textbf{Inner segment guess II}.
 	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
+	and let $w \in U \cup Z^*$. %be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest.
 	We want to
@@
 	\\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
+	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $k^{O(k)}$ different possible such paths, therefore we make $k^{O(k^4)}$ guesses for these paths.
 	%
@@
 	\item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
+	\textbf{Split vertex guess I}.
 	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
 	fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
+	In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex, else we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
 	Let 
 	$S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
+	We want to determine the fastest paths from $v_i$ to all inner vertices of $S_{w,z}$. We do this by inspecting the values in matrix $D$ from $v_i$ to inner vertices of $S_{w,z}$.
 	We split the analysis into two cases.
@@
 		We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
+		which results in producing $k^{O(k^5)}$ new guesses.
 		Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
@@
 		which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
+		In this case we do not introduce any new guesses, as we have aready guessed 
 		the fastest paths of the form
@@
 		and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
+		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
 	\end{enumerate}
@@
 	\item \label{FPT:guess-splitFromUtoAnotherSegment}
+	\textbf{Split vertex guess II}.
 Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
     and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+    Similarly as above, in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
     We again have two cases,
@@
     Therefore no new guesses are needed.
+    Note that the above guesses, together with the guesses from \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}},
+    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
+    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
+
+    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
+    We repeat this for all vertices of interest, and all segments,
+    which produces $k^{O(k^2)}$ new guesses.
+    %
+    For an example see~\cref{fig:FPT-guessG7}.
+ %
+%	Let $w \in U \cup Z^*$ 
+%	and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$.
+%	We want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+%	We again have two cases,
+%	first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
+%	and the
+%	second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
+	\begin{comment}
+	In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
+	travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
+	Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
+	we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
+	or 
+	$v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
+	Which produces two new guesses.
+	In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
+	Therefore no new guesses are needed.
 	Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
@@
 	(this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
+	\end{comment}
+%	All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
+%	We repeat this for all vertices of interest, and all segments,
+%	which produces $k^{O(k^2)}$ new guesses.
 	%
-    For an example see~\cref{fig:FPT-guessG7}.
+%	For an example see~\cref{fig:FPT-guessG7}.
+%	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
 	% counter for guesses continues
@@
 		\centering
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.88\linewidth}{!}{
 			\includegraphics{fig-guess1}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
 			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
@@
 		\centering
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.88\linewidth}{!}{
 
 			\includegraphics{fig-guess2}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
 			\label{fig:FPT-guessG5}}
@@
 	\begin{subfigure}[b]{0.48\textwidth}
+		\vspace{-0.4cm}
         \centering
-			\resizebox{1.2\linewidth}{!}{
+		\resizebox{0.98\linewidth}{!}{
 			%
 			\includegraphics{fig-guess3}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
+		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
 			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
@@
 		\centering
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.88\linewidth}{!}{
 			\includegraphics{fig-guess4}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
+		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
 			we
@@
 	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
+	\caption{Illustration of the guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
 \end{figure}
 %
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
+%We create all of the guesses independently.
+%We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
+%After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
+%We now create one ILP instance for each case.
+%From now on we assume that we know exactly the structure of all paths we have guessed.
+
+There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that we make during the creation of the ILP instances, we explain these guesses in detail in \cref{sec:constraints}.
+We will prove that, for all guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-12}}}, there are in total at most $f(k)$ possible choices, and for each one of them we create an ILP with at most $f(k)$ variables and at most $f(k)\cdot |D|^{O(1)}$ constraints.
+Each of these ILPs can be solved in FPT time by Lenstra's Theorem~\cite{Lenstra1983Integer}.
 
@@
 We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
+
+We first start with defining certain notions, that will be of use when solving the problem.
+
+    \begin{definition}[Travel delays]
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
+    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
+    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
+    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+    More specifically:
+    \begin{equation}\label{eq:def-VertexWaitingTime}
+       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+    \end{equation}
+    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    \end{definition}
+    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
+
+    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
+    \begin{observation}\label{obs:durationPwithWaitingTimes}
+        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
+        $(P, \lambda)$ from $v_0$ to $v_p$.
+        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
+    \end{observation}
+    \begin{proof}
+        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
+        Then
+        \begin{align*}
+        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
+        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
+        & = (t_2 - t_1) + (t_3 - t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
+        & = t_{p-1} - t_1 + 1\\
+        & = d(P, \lambda)
+        \end{align*}
+        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
+        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
+    \end{proof}
+    We also get the following.
+    \begin{observation}\label{obs:travel-delays-both-directions}
+    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem.
+    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{observation}
+
+    \begin{proof}
+        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
+        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
+    \end{proof}
+
+%Furthermore, we can make the following observation concerning subpaths of a fastest temporal path.
+
+%\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
+%    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
+%    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
+%    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
+%    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
+%    Then we can determine travel delays on vertices of $P$ using the following equation
+%    \begin{equation}\label{eq:trav-delays-paths}
+%        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
+%    \end{equation}
+%    for all $i \in \{2,3, \dots, k-1\}$.
+%\end{lemma}
+
+%\begin{proof}
+%    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
+%    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
+%    \begin{align*}
+%        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
+%        & \equiv 
+%        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
+%        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
+%        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
+%        \end{align*}
+%    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
+%\end{proof}
 
@@
 %
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
+Whenever $t=1$, we may omit the index $t$, \ie we may write 
 $A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
@@
 		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
+		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, \ie $%
 		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
@@
 		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
+		x\Delta +e-h$, \ie $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
 		Summarizing, we have:%
@@
         %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
+        3 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
         1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
@@
 
-\subsubsection{Adding constraints and variables to the ILP}
+\subsubsection{Adding constraints and variables to the ILP}\label{sec:constraints}
 We start by analyzing the case where we want to determine the labels on fastest temporal paths between vertices of interest.
@@
     \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
+    Let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  be a segment with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$. 
+    For the fastest temporal paths from $v_{i-1}$ to $v_{i+1}$, from $v_{i+1}$ to $v_{i-1}$, from $v_{i}$ and $v_{i+2}$, and $v_{i+2}$ and $v_{i}$, we guess whether it passes through the edge $f$. 
+    Thus we create $4$ guesses for every such segment $S_{u,v}$, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
     % counter for guesses continues
@@
 $x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
+This results in $O(k^2)! = k^{O(k^2)}$ guesses
 and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
+each of the ILP instances we created up to now is further split into $k^{O(k^2)}$ new ones.
 \end{enumerate}
@@
 if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
+then we have guessed in what kind of relation they are (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guessallPermutations}}}}).
 Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
@@
 
-\subparagraph{\boldmath Fastest paths between $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths between $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
+\subparagraph{\boldmath Fastest paths between $u,v \in U$.}
+Let $u,v\in U$, \ie both $u,v$ are vertices of interest.
+%This was the case that we partially studied at the beginning of the algorithm, and it helped us determine certain labels of the graph.
+For the path from $u$ to $v$ (resp.~from $v$ to $u$) in $G'$, which we guessed that it coincides with the fastest in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongU}}}}, we introduce an equality constraint.
+We then iterate over all other paths from $u$ to $v$ (resp.~from $v$ to $u$) in $G'$, and for each one we introduce an inequality constraint.
+There are $O(k^2)$ pairs of vertices $u,v\in U$, and there are $k^{O(k)}$ possible paths from $u$ to $v$ (resp.~from $v$ to $u$) in $G'$, therefore in this step we introduce $k^{O(k^3)}$ constraints in total.
+
+\subparagraph{\boldmath Fastest paths from $u \in U$ to $x \in V(G') \setminus U$.}
+%%%First we deal with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
+From the guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}} we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
+In this case we create an equality constraint for the fastest path and we 
 iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
+There are $k^{O(k)}$ possible paths of the form $u \leadsto w$ (resp.~$u \leadsto v$),
+and a unique way how to extend these paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
+Therefore we add $k^{O(k)}$ inequality constraints for the pair $u,x$.
 
@@
 
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
+\subparagraph{\boldmath Fastest paths from $x \in V(G') \setminus U$ to $u \in U$.}
+% Now we proceed with the case of %determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
 %We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
+Let $x$ be a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$, and let $u\in U$.
 If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
+(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongUandUstar}}}}).
+Assume that $S_{w,z}$ is of length at least $4$.
 This implies that there are at most two not yet determined edges in it.
@@
 and with $P^-$ the fastest temporal path of the form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
+Note that we know these paths from guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}.
 Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
@@
 \end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of the form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths between $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
+Once the fastest temporal path from $c$ to $u$ is determined, we introduce an equality constraint for it.
+For each of the other $k^{O(k)}$ paths from $x$ to $u$ (which correspond to all paths of the form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
+we introduce an inequality constraint. Therefore we add $k^{O(k)}$ inequality constraints for the pair $x,u$.
+
+\subparagraph{\boldmath Fastest paths between $x,y\in V(G') \setminus U$.}
+Let $x,y \in V(G') \setminus U$.
 We have two options.
@@
     uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
+    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')\setminus U$ to $u \in U$).
     \item Vertices $x$ and $y$ are in different segments. 
@@
 implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
+Since we know the following fastest temporal paths (see guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}) 
 $z_2 \rightarrow w \leadsto u \rightarrow v_2$,
@@
 and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
+we can uniquely determine the fastest path from~$v_j$ to $z_i$,
 using 
@@
 If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
+we can again uniquely determine the fastest path from~$v_j$ to~$z_i$, using the same approach, 
+and the knowledge of fastest paths to (or from) all vertices of the segment of length~$3$
+(as we guessed them in guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}).
 If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
+as we guessed the fastest paths in guesses~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}} and~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}.
 \end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ between vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
+Once the fastest path is determined we introduce the equality constraint for it
+and iterate through all other paths, for which we introduce inequality constraints.
+To enumerate all these non-fastest temporal paths, we just consider all possible paths $u \leadsto w$, where 
+$u$ and $w$ are the vertices of interest that are the endpoints of segments to which $x$ and $y$ belong;
+once the correct segment is reached, there is a unique path to the desired vertex $x$ (resp.~$y$). 
+Therefore we introduce $k^{O(k)}$ inequality constraints for each pair of vertices $x,y$.
 
@@
 
-\subparagraph{\boldmath Fastest paths between $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
+\subparagraph{\boldmath Fastest paths from $z \in Z$ to $u \in U$.}
+Let $u\in U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
 We distinguish the following two cases.
@@
     $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
+    From guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
     $z_{r-1} \rightarrow z \leadsto u$.
@@
         for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
+        By similar arguing as in cases above, we introduce $k^{O(k)}$ inequality constraints.
         \item The segment $S_{w,z}$ is of length $4$ or less
@@
        which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
+       For all other $k^{O(k)}$ paths we add the inequality constraints. 
     \end{enumerate}
@@
     In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
+    (we determined it in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
     We create an equality constraint for this path,
     and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
+    Since there are $k^{O(k)}$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
+    we create $k^{O(k)}$ inequality constraints.
 \end{enumerate}
 
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
+\subparagraph{\boldmath Fastest path from $u \in U$ to $z \in Z$.}
+Let $u\in U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
+In this case we split again the analysis in two cases.
 \begin{itemize}
@@
     In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths between $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
+we know exactly what is the fastest path (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
+\end{itemize}
+The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.
+
+\subparagraph{\boldmath Fastest path from $z \in Z$ to $y \in V(G') \setminus U$.}
+Let $y \in V(G') \setminus U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
+%%%We now want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest, and vice versa.
 Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
+We use the similar approach as in the above case, when we were determining paths between vertices in $Z$ and $U$, 
 to determine the fastest temporal path from $r_i$ to $y$. 
@@
 (when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
+The latter follows from the guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.\\
 %
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
+Since $y \in S_{u,v}$ there are $k^{O(k)}$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
+and $k^{O(k)}$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
 In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
@@
 
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
+\subparagraph{\boldmath Fastest path from $y \in V(G') \setminus U$ to $z \in Z$.}
+Let $y \in V(G') \setminus U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
+In this case we split again the analysis in two cases. 
 \begin{itemize}
@@
 Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
+In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
 Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
@@
 \end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
+The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.
 
 \subparagraph{\boldmath Fastest paths between $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths between two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
+Let $z,z'\in Z$, and let $z$ (resp.~$z'$) belong to the tree $T_i$ (resp.~$T_j$).
+Let $r_i, r_j$ be representative vertices and let $w_i, w_j$ be the clip vertices of the trees $T_i$ and $T_j$, respectively.
 We distinguish following cases.
@@
     In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths between them (see guess G-\ref{FPT:guess-uToSegmentz2}).
+    and therefore we know the fastest paths between them (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
     \item One clip vertex is a vertex of interest and the other is not.
@@
 \end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
+The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.
 
@@
 We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
+each with $O(k^2)$ variables and $O(n^2) g(k)$ constraints (again, $g$ is a double exponential function).
 We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
@@
 
+\begin{comment}
 \subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
@@
 \end{proof}
+\end{comment}
 

### 2023-10-05 STACS2023/STACS23-shortversion.tex
Some changes, added new meeting whiteboard

@@
 \usepackage{cite} %order citations by increasing number
-\title{Temporal graph realization from fastest temporal paths} %TODO Please add
+\title{Temporal graph realization from fastest paths} %TODO Please add
 %%%Realizing temporal graphs from fastest travel times
@@
     Having computed $G$, our algorithm proceeds as follows.
-We pick an arbitrary edge $e$ and give it label one, that is, $\lambda(e)=1$.
-Now we push all edges incident with $e$ into a (initially empty) queue.
+We pick an arbitrary edge $f$ and give it label one, that is, $\lambda(f)=1$.
+Now we push all edges incident with $f$ into a (initially empty) queue.
 Now we repeat the following as long as the queue is not empty:

### 2023-10-05 STACS2023/abstract.tex
Some changes, added new meeting whiteboard

--- 2023-02-16 abstract.tex
@@
 Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices such that the duration of a fastest path from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist.
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
+The variations of the problem on static graphs has been well studied and understood since the 1960's (e.g.
+[Erdos and Gallai, 1960], [Hakimi and Yau, 1965]).
 
@@
 non-temporal) counterpart.
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
+First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree.
 Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, while we show that it is in FPT when parameterized by the feedback edge number of the underlying graph.
+We prove a tight classification between such parameters that allow fixed-parameter tractability (FPT) and those which imply W[1]-hardness.
+We show that our problem is W[1]-hard when parameterized by the feedback vertex number (and therefore also any smaller parameter such as treewidth, degeneracy, and cliquewidth) of the underlying graph, while we show that it is in FPT when parameterized by the feedback edge number (and therefore also any larger parameter such as maximum leaf number) of the underlying graph.

### 2023-10-05 TGR Extended - New paper/Realizing TG - extended.tex
Some changes, added new meeting whiteboard

@@
 We start by investigating the complexity of the problem \DeltaUpperBoundLong\ in the case when the underlying graph of the input instance is a path.
-First we observe some properties of the problem.
 
+\begin{comment}
 Let $(G,D)$ be an instance of \deltaUpperBound\, where $G$ is a path of length $n$.
@@
 From now on we assume that $D$ is a reduced matrix, that satisfies the above conditions, and that the labeling $\lambda$ of $G$, if it exists, does not label two consecutive edges using the same label.
+\end{comment}
 
@@
 \end{theorem}
+
+Before stating the proof let us observe the following.
+Suppose that $(G, D)$ is a yes instance of \deltaUpperBound\, where $G$ is a path on vertices $v_0, v_1, v_2, \dots, v_n$, 
+and let $\lambda$ be a labeling of $G$ s.t. $(G,\lambda)$ realizes $D$.
+Then, w.l.o.g. we can assume that $\lambda(v_{i-1} v_{i}) \neq \lambda (v_{i}v_{i+1})$ for all $i \in [n-1]$, \ie any two consecutive edges are labeled with a different label.
+This follows from the fact that the duration among two vertices $v_i, v_{i+2}$ on distance $2$ in $G$ equals to $\Delta + 1$ when the two consecutive labels are the same, 
+and the duration is at most $\Delta$,
+when the two consecutive labels are not the same,
+Therefore, if the value $D_{i,i+2}= \Delta + 1$ and $\lambda(v_{i-1} v_{i}) \neq \lambda (v_{i}v_{i+1})$, we get that the duration $d(v_i, v_{i+2})$ from vertex $v_i$ to $v_{i+2}$ in $(G, \lambda)$ is at most $\Delta$
+and therefore $d(v_i, v_{i+2}) \leq D_{i,i+2}$,
+which still satisfies the conditions of \deltaUpperBound.
+
+From now on we assume that the labeling $\lambda$ of $G$, if it exists, does not label two consecutive edges using the same label.
 
@@
 and with $\tau_i^-$ the waiting time at $v_i$ when traversing through $v_i$ from the other direction (for details see~\cref{def:travelDelays}).
-Since $\tau_i^- = \Delta - \tau_i^+$, we can simplify the above notation and replace $\tau_i^+$ with $\tau_i$, and $\tau_i^-$ with $ \Delta - \tau_i$.
+Since $\tau_i^- = \Delta - \tau_i^+$, 
+\todo[inline]{NK: Done - paragraph above the proof \\
+GM: not correct, they can be both Delta !
+THIS MUST BE WRITTEN.
+THE TRICK IS THAT, FOR A PATH, WE WILL NEVER CHOOSE TO HAVE TWO CONSECUTIVE LABELS EQUAL, SINCE THIS WOULD JUST INCREASE THE FASTEST TIMES ARTIFICIALLY.
+BUT THIS IS NOT TRUE FOR A GRAPH THAT IS NOT A PATH !}
+we can simplify the above notation and replace $\tau_i^+$ with $\tau_i$, and $\tau_i^-$ with $ \Delta - \tau_i$.
 Therefore, by the definition, it follows that the duration of a fastest path among two vertices $v_i, v_j$ in $(G,\lambda)$, for $i < j$
@@
 \begin{equation}\label{eq:path-negative}
-d(v_i,v_j)=\sum_{k = i+1}^{j-1} (\Delta - \tau_k) + 1.
+d(v_i,v_j)=\sum_{k = j-1}^{i+1} (\Delta - \tau_k) + 1.
 \end{equation}
+\todo[inline]{NK: Done \\
+GM: WRONG INDICES: CHANGE IT HERE AND BELOW}
 
@@
 \begin{equation}
-\sum_{k = i+1}^{j-1} (\Delta - \tau_k) + 1
+\sum_{k = j-1}^{i+1} (\Delta - \tau_k) + 1 \leq D_{j,i}
 \Leftrightarrow
-\sum_{k = i+1}^{j-1} - \tau_k \leq  D_{i,j} - 1 -(j-i+1)\Delta .
+\sum_{k = i+1}^{j-1} - \tau_k \leq  D_{j,i} - 1 -(j-i+1)\Delta .
 \end{equation}
-From the condition $\tau_i \in [\Delta]$, we add the inequality $\tau_i \leq \Delta$ and $\tau_i \geq 0$.
+\todo[inline]{NK: Done \\
+GM: MISSING INEQUALITY ON THE LEFT SIDE}
+From the condition $\tau_i \in [\Delta]$, we add the inequality $\tau_i \leq \Delta$ and $\tau_i \geq 1$.
 
@@
 \end{equation}
+\todo[inline]{GM: WE DO NOT WANT AN OBJECTIVE FUNCTION, BUT EVEN IF WE WANT, WHY MAX AND NOT MIN? WE WANT HERE FEASIBILITY LP}
 Note that in our case we do not necessarily want to maximize the sum of all $\tau_i$ variables, but just to find an assignment of variables that will satisfy our conditions.

### 2023-11-22 TGR Extended - New paper/Realizing TG - extended.tex
Reviews

@@
 
-\subsection{The underlying graph is a path}
+\subsection{\deltaUpperBound\ on paths}
 We start by investigating the complexity of the problem \DeltaUpperBoundLong\ in the case when the underlying graph of the input instance is a path.
@@
 
+\subsection{\deltaUpperBound\ on stars}
+
+Let $G$ be a star graph with a central vertex $s$ and $n$ leaf vertices $v_1, v_2, \dots, v_n$.
+Then all of the paths in $G$ are of length at most $2$.
+Since vertices on distance $1$ are connected by a path of duration $1$, we are only interested in the duration of paths between leaf vertices.
+Observe, that a path of distance $2$ is of duration $\Delta + 1$ only in the case when two consecutive edges are labeled with the same label. In any other case, the duration will be  at most $\Delta$.
+With this in mind we first modify the input duration matrix $D$ as follows:
+we iterate through the whole matrix $D$ and in the case when the input value $D_{i,j}  > \Delta + 1$ we set it to $D_{i,j} = \Delta + 1$. 
+Clearly, the newly modified matrix is realizable if and only if the starting, input matrix is realisable.
+
+Let us now fix the following notation.
+For every edge $sv_i$ we denote its label as $\lambda_i$.
+For every pair of vertices $v_i, v_j$ we denote the exact duration from $v_i$ to $v_j$ as $d_{i,j}$, while we always refer to the upper bound, given by the input matrix, as $D_{i,j}$.
+By the definition of the problem we have $d_{i,j} \leq D_{i,j}$.
+\begin{observation}
+Let $v_i,v_j$ be two leaf vertices in a star.
+Then
+\begin{equation}
+    d_{i,j} + d_{j,i} =
+    \begin{cases}
+    \Delta + 2, &\text{ when $\lambda_i \neq \lambda_j$} \\
+    2 \Delta + 2, &\text{ when $\lambda_i = \lambda_j$}
+    \end{cases}.
+\end{equation}
+\end{observation}
+\begin{proof}
+    We distinguish two cases. Suppose first that $\lambda_i \neq \lambda_j$ and w.l.o.g. we can assume also that $\lambda_i < \lambda_j$.
+    Then, by the definition of the duration, we get that
+    \begin{align*}
+        d_{i,j} + d_{j,i} &= (\lambda_j - \lambda_i + 1) + (\Delta + \lambda_i - \lambda_j + 1) \\
+        &= \Delta + 2.
+    \end{align*}
+    Suppose now that $\lambda_i = \lambda_j$ then we get
+    \begin{align*}
+        d_{i,j} + d_{j,i} &= (\Delta + \lambda_j - \lambda_i + 1) + (\Delta + \lambda_i - \lambda_j + 1) \\
+        &= 2\Delta + 2.
+    \end{align*}
+\end{proof}
+For any pair of vertices $v_i,v_j$, where both of the values $D_{i,j}, D_{j,i}$ are $\Delta + 1$, we know that the conditions on path durations will be satisfied regardless of what labels $\lambda_i$ and $\lambda_j$ are.
+Therefore, for this case, we do not have to satisfy any constraint.
+Using the above observation, for all $i < j$, where the sum $D_{i,j} + D_{j,i} \leq 2\Delta + 2$ we introduce the following new values:
+$D_{i,j} + D_{j,i} = \Delta + 2 + \epsilon_{i,j}$, where $0 \leq \epsilon_{i,j} < \Delta $,
+and 
+$D_{i,j} = d_{i,j} + c_{i,j}$, with $D_{j,i} = d_{j,i} + (\epsilon_{i,j} - c_{i,j})$, where 
+$0 \leq c_{i,j} \leq \epsilon_{i,j}$.
+Intuitively, the value of $c_{i,j}$ tells us how much slack/extra time we have between the moment when the temporal path from $v_i$ to $v_j$ finishes and the upper bound for its duration in the matrix $D$.
+Note that the values $\epsilon_{i,j}$ are uniquely determined already with the values from the input matrix $D$.
+
+\subsubsection*{Suppose that $n = 4$, \ie the star has only $4$ leaves.}
+To start determining the values of labels $\lambda_i$, 
+we can w.l.o.g. first fix $\lambda_1 = 1$.
+Now suppose that $D_{i,j} \leq \Delta$ for all $i,j$ (if there is a case when $D_{i,j} = D_{j,i} = \Delta + 1$ then we do not introduce any of the equalities presented below).
+By the definition of durations of temporal paths,
+for all $i \in \{2,3,4\}$ we get that 
+\begin{equation}\label{eq:lambdai-from1}
+    \lambda_i = d_{1,i} = D_{1,i} - c_{1,i}.
+\end{equation}
+Comparing all other paths of length two we get
+\begin{align}
+    \lambda_3 - \lambda_2 + 1 & \equiv D_{2,3} - c_{2,3} \pmod{\Delta} \label{eq:D23} \\
+    \lambda_4 - \lambda_3 + 1 & \equiv D_{3,4} - c_{3,4} \pmod{\Delta} \label{eq:D34} \\
+    \lambda_4 - \lambda_2 + 1 & \equiv D_{2,4} - c_{2,4} \pmod{\Delta}.\label{eq:D24} 
+\end{align}
+Joining the equations together we get the following
+\begin{align}
+    c_{1,2} + c_{2,3} - c_{1,3} & \equiv D_{1,2} + D_{2,3} - D_{1,3} -1 \pmod{\Delta} \label{eq:c123} \\
+    c_{1,3} + c_{3,4} - c_{1,4} & \equiv D_{1,3} + D_{3,4} - D_{1,4} -1 \pmod{\Delta} \label{eq:c134} \\
+    c_{1,2} + c_{2,4} - c_{1,4} & \equiv D_{1,2} + D_{2,4} - D_{1,4} -1 \pmod{\Delta} \label{eq:c124} \\
+    c_{2,3} + c_{3,4} - c_{2,4} & \equiv D_{2,3} + D_{3,4} - D_{2,4} -1 \pmod{\Delta}. \label{eq:c234}
+\end{align}
+
+For all $i,j,k,\ell \in [n]$ also the following holds
+$
+    d_{i,j} + d_{j,k} \equiv d_{i, \ell} + d_{\ell, k} \pmod \Delta.
+$
+In fact we can generalize the above statement even further and get the consequent.
+\begin{observation}
+    Let $G$ be a star with $n$ leaf vertices $v_1, v_2, \dots, v_n$.
+    Then
+    \begin{equation}\label{eq:d-congruences}
+    d_{i,k} + \ell \equiv d_{i, {j_1}} + d_{j_1, {j_2}} + \cdots + d_{j_{\ell -1}, {j_\ell}} + d_{j_\ell,k} \pmod \Delta,
+    \end{equation}
+    where $\ell \geq 0$ and $i \neq k \neq j_1 \neq j_2 \neq \dots \neq j_\ell$.
+\end{observation}
+%
+\begin{proof}
+    By the definition $d_{i,k} \equiv \lambda_k - \lambda_i + 1 \pmod \Delta$
+    and
+    \begin{align*}
+        & 
+        d_{i, {j_1}} + d_{i, {j_2}} + \cdots + d_{i, {j_\ell}} + d_{j_\ell,k}
+        \equiv \\
+        &
+        (\lambda_{j_1} - \lambda_i + 1) +
+        (\lambda_{j_2} - \lambda_{j_1} + 1) + \cdots +
+        (\lambda_{k} - \lambda_{j_\ell} + 1)
+        \equiv \\
+        &
+        \lambda_k - \lambda_i + \ell + 1 
+        \pmod \Delta.
+    \end{align*}
+    All of the above gives us the equality from \cref{eq:d-congruences}.
+\end{proof}
+
 \subsection{\deltaUpperBound\ on general graphs}

### 2023-12-20 STACS2023/rebuttal_response.txt
dec 20

We thank all of the reviewers for their detailed analysis of our work. We will take in consideration all of the remarks and incorporate them to our paper before the final submission. We now provide a short response to each of the reviewers separately.

REVIEWER 1
We appreciate the reviewer's thoughts and would like to gently clarify an aspect of our research problem. 
We are focused on the fastest temporal paths, rather than the shortest paths. Fastest temporal paths can be thought of as an extension of the concept of shortest paths on (static) graphs, to the setting of temporal graphs, where due to causality, entities and information can "flow" only along sequences of edges whose time-labels are strictly increasing.
In our context, a fastest temporal path from vertex u to v is defined as the temporal path that uses the smallest possible duration to travel from u to v. This "duration" is essentially the "travel time" from the starting vertex to the ending one. In our example in Figure 1, the journey from v_1 to v_k can begin at time 7 and finish a time 21, which results in a travel time of 15 units and not 21. The initial six units of time before the journey do not contribute to the travel time. To put it into a real-life scenario, consider the example of travelling: we normally do not start measuring the travel duration at 00:00 on the day of travel, but at the specific time we live our home.

REVIEWER 2

#MINOR REMARKS
- l 230: We will remove the requirement, that every vertex has at least one neighbor of every color. This was accidentally kept from an earlier draft of the reduction, and is not needed in the reduction presented in the paper.
- Figure 5: One of the degree one neighbors of the bottom left green vertex should be in Z^*, we made a mistake.
- l 505: The reviewer is right, segment is unique whenever it does not consist of a single edge. We will add this detail. Note that our algorithm remains correct, since there can be at most 1 (constant) such segment between a pair of important vertices.

REVIEWER 3

#MAJOR REMARKS
1)
The reviewer is correct. In our W[1]-hardness proof we do not explicitly describe the values of the D matrix for all pairs of vertices. We apologise for this oversight and acknowledge that we failed to mention a crucial remark, that the values for durations of fastest paths among non-adjacent vertex pairs, that we do not explicitly specify in the proof, are set to infinity. We will clarify this in the updated version of the paper (in the full version this is mentioned - see Appendix in lines 563-564).

2)
When discussing the FPT algorithm, we use the term "guessing" where we mean that we enumerate all possible outcomes. We will state this more clearly in the next iteration of the paper.

3)
At the start of the algorithm, we chose a spanning tree T of G' and use it to determine the set of feedback edges F and set(s) of important vertices. We then "guess" the fastest paths among the determined important vertices in the whole graph G'. This implies that the fastest paths use the edges of our spanning tree T and the feedback edges F. Therefore, the choice of a spanning tree (and consequently the feedback edges F) does not influence the structure of fastest paths.

#MINOR REMARKS
Considering the graph realization on temporal graphs we agree that there are many different settings one could study, and for each of them argue why it is interesting.
A nice property in periodic temporal graphs is that a temporal path among each pair of vertices exists (whenever the underlying graph is connected), which is not necessarily true in the non-periodic case. This is why we chose to study the problem on periodic temporal graphs.
Initiating the study we tried to create the simplest possible setting, which resulted in labeling each edge with exactly one label in a fixed time period.
We do state that the periodic case with all edges having the same period is the most fundamental case, where the more evolved variant would be graphs with the edges admitting different periods.
As the reviewer mentioned, there are also other possible definitions of temporal paths that would be worth exploring, such as the shortest or foremost paths, both with the increasing or non-decreasing time labels. We focused on the fastest temporal paths with strictly increasing time labels, as we believe they are the most natural in our setting.

Answering the questions about the FPT algorithm. 
- To guess a fastest path among two vertices we produce f(k) guesses. Thus guessing a path among n^2 pairs of vertices would result in f(k)^{n^2} guesses, which is not an FPT running time anymore. 
We believe this explanation answers also the reasoning behind the number of guesses in lines 496-498. 
- Let us shortly outline why the set Z^* is necessary. Let u be a clip vertex of a tree T_u, w \in V(T_u) a vertex from Z^*, and v an arbitrary vertex from the graph. Suppose that P is a fastest temporal path from v to u, of duration d that reaches u at time 1 (mod delta), and let Q be another (v,u)-temporal path that reaches u at time 5 (modulo delata) and is of duration d+1.
Suppose also that the edge uw is labeled with 6. Then the (u,w)-temporal path R_1 = Q \cup {uw} is of smaller duration than R_2 = P \cup {uw}. Which implies that knowing the fastest temporal path from v to u does not provide enough information to uniquely determine the fastest temporal path from v to w (or to any other vertex from T_u).
Now observe that knowing the label of one edge of the tree T_u results in uniquely determining all other labels, because of the fact that there is a unique (static) path between any two vertices of T_u (we can use our tree algorithm for this part).
-line 506: one path is indeed reverse of the other.

### 2023-12-20 STACS2023/STACS23-shortversion.tex
dec 20

@@
 \problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
+{An integer $n \times n$ matrix $D$, a positive integer $\Delta$.}
 {Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
@@
 	\caption{An example of a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, where $\Delta = 10$ and the 10-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,10\}$ is as follows: $\lambda(v_1 v_2)=7$, $\lambda(v_2 v_3)=3$, $\lambda(v_3 v_4)=5$, and $\lambda(v_4 v_5)=1$.
-    Here, the fastest temporal path from $u$ to $v$ traverses the first edge $v_1v_2$ at time $7$, second edge $v_2v_3$ a time $13$, third edge $v_3v_4$ at time $15$ and the last edge $v_4v_5$ at time $21$.
-    This results in the total duration of $15$ for the fastest temporal path from $v_1$ to $v_5$.
+    Here, the fastest temporal path from $v_1$ to $v_2$ traverses the first edge $v_1v_2$ at time $7$, second edge $v_2v_3$ a time $13$, third edge $v_3v_4$ at time $15$ and the last edge $v_4v_5$ at time $21$.
+    This results in the total duration of $21 - 7 + 1 = 15$ for the fastest temporal path from $v_1$ to $v_5$.
 	\label{fig:periodic-example}}
@@
  The verification gadget for color $i$ is connected to all edge selection gadgets that involve color $i$.
-More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see \cref{fig:hardness1}) for reference.
+More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see \cref{fig:hardness1} for reference).
 Intuitively, the distances in the verification gadget are only realizable if the selected edges all have the same endpoint of color $i$.
@@
     Among the constraints in this ILP we have that, for each of the $O(n^2)$ pairs of vertices $u,v$ in the graph, the duration of one specific temporal path from $u$ to $v$ (according to our guesses) is \emph{equal} to the desired duration $D_{u,v}$, while the duration of each of the other temporal paths from $u$ to $v$ is \emph{at least} $D_{u,v}$.
-    \item By making any of the above guesses, we restrict the solution space for the problem \deltaExact.
+    \item 
+    %%%By making any of the above guesses, we restrict the solution space for the problem \deltaExact.
 This restricted solution space coincides with the set of feasible solutions to the resulting ILP.
 Furthermore, the set of feasible solutions for all constructed ILPs coincide with the set of all solutions to \deltaExact\ (\ie regardless of our guesses).
+    By making each of the above combinations of guesses, we essentially enumerate all possible ways that our instance of \deltaExact\ has a solution, and for each of these possible ways we create an ILP.
+That is, our instance of \deltaExact\ has a solution if and only if at least one of these ILPs has a feasible solution.
     As each ILP can be solved in FPT time with respect to $k$ by Lenstra's Theorem~\cite{Lenstra1983Integer} (the number of variables is upper bounded by a function of $k$), we obtain our FPT algorithm for \deltaExact\ with respect to $k$.
@@
 \subparagraph{Important vertices.}
-Let $D$ be the input matrix of \deltaExact\, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
+Let $D$ be the input matrix of \deltaExact, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
 %\subsubsection*{Preprocessing of the input}

### 2023-12-20 SAND2024/Figures/fig-W1-infinity.tex
SAND

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
 \begin{tikzpicture}[line width=1pt, scale=.65]
@@
 \end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-12-20 SAND2024/Figures/fig-guess1.tex
SAND

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
 			\begin{tikzpicture}
@@
 		(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
 	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-12-20 SAND2024/Figures/fig-guess2.tex
SAND

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
-
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
 
@@
 
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
 \end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-12-20 SAND2024/Figures/fig-guess3.tex
SAND

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
 \begin{tikzpicture}[scale=1]
@@
 
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-			\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
-
-			%%%% node w
-			\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-			\draw [blue] 
-			(w) edge[dirwave] [out=160,in=285] (v1) 
-			(v1) -- (v2)
-			(v2) edge[diredge2] (vi);
-
-			\draw [red]
-			(w) edge[dirwave] [out=20,in=255] (vp) 
-			(vp) -- (vp1)
-			(vp1) edge[diredge2] (vi+1);
-
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
 \end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-12-20 SAND2024/Figures/fig-guess4.tex
SAND

--- 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
@@
 }
+\begin{document}
 
-%\usepackage{enumitem} %enumerate 
-\usepackage{enumerate}
-\usepackage{todonotes}
-\newcommand{\todonkl}[2][]{\todo[color=red!100!green!33,#1]{NKL:\\ #2}} %todo note that starts with NKL:
-\setlength{\marginparwidth}{3.7cm} %setting the length of todonote
-
-\usepackage{comment}
-
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-
-%font encoding
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-
-\usepackage{hyperref}
-
-\crefname{claim}{Claim}{Claims}
-
-%\usepackage{natbib}
-
-\newcommand{\ie}{i.\,e.,\ }
-\renewcommand{\st}{s.\,t.,\ }
-\newcommand{\NP}{\textrm{NP}}
-\newcommand{\APX}{\textrm{APX}}
-\newcommand{\FPT}{\textrm{FPT}}
-\newcommand{\XP}{\textrm{XP}}
-
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\QQ}{\mathbb{Q}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining a problem
-%%%%%%%%%%%%%%%%%%\problemdef{NAME} {Input} {Output}
-\usepackage{tabularx}
-\newcommand{\problemdef}[3]{
-	\begin{center}
-		\begin{minipage}{0.95\textwidth}
-			\noindent
-			#1
-			\vspace{5pt}\\
-			\setlength{\tabcolsep}{3pt}
-			\begin{tabularx}{\textwidth}{@{}lX@{}}
-				\textbf{Input:}& #2 \\
-				\textbf{Question:}& #3
-			\end{tabularx}
-		\end{minipage}
-	\end{center}
-}
-
-\newcounter{guesscounter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEMS NAMES
-%% One label per edge, period Delta, exact realization
-\newcommand{\deltaExactLong}{\textsc{Periodic Temporal Graph Realization}}
-\newcommand{\deltaExact}{\textsc{Periodic TGR}}
-
-%% k labels per edge, period Delta, exact realization
-\newcommand{\kDeltaExactLong}{\textsc{$(k,\Delta)$-periodic Exact Temporal Graph Realization}}
-\newcommand{\kDeltaExact}{\textsc{$(k,\Delta)$-TGR}}
-
-%% One label per edge, period Delta, upper-bounded realization
-\newcommand{\kDeltaUpperBoundLong}{\textsc{Simple $\Delta$-periodic Upper-Bounded Temporal Graph Realization}}
-%\newcommand{\deltaUpperBound}{}
-
-%% k labels per edge, period Delta, lower-bound realization
-\newcommand{\kDeltaLowerBoundLong}{\textsc{Simple $\Delta$-periodic Lower-Bounded Temporal Graph Realization}}
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-\usepackage{cite} %order citations by increasing number
-
-\title{Realizing temporal graphs from fastest travel times} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}
-
-%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}
-
-%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}
-
-%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}
-
-%\authorrunning{Nina Klobas, George B.
-Mertzios, Hendrik Molter, and Paul G.
-Spirakis} %TODO mandatory.
-First: Use abbreviated first/middle names.
-Second (only in severe cases): Use first author plus 'et al.'
-
-%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
-\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
-%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-In this paper we initiate the study of the \emph{temporal graph realization} problem with respect to the fastest path durations among its vertices, 
-while we focus on periodic temporal graphs. 
-Given an $n \times n$ matrix $D$ and a $\Delta \in \mathbb{N}$, the goal is to construct a $\Delta$-periodic temporal graph with $n$ vertices 
-such that the duration of a \emph{fastest path} from $v_i$ to $v_j$ is equal to $D_{i,j}$, or to decide that such a temporal graph does not exist. 
-The variations of the problem on static graphs has been well studied and understood since the 1960's, and this area of research remains active until nowadays.
-
-As it turns out, the periodic temporal graph realization problem has a very different computational complexity behavior than its static (i.e.~non-temporal) counterpart. 
-First we show that the problem is NP-hard in general, but polynomial-time solvable if the so-called underlying graph is a tree or a cycle.
-Building upon those results, we investigate its parameterized computational complexity with respect to structural parameters of the underlying static graph which measure the ``tree-likeness''.
-For those parameters, we essentially give a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We show that our problem is W[1]-hard when parameterized by the \emph{feedback vertex number} of the underlying graph, while we show that it is in FPT when parameterized by the \emph{feedback edge number} of the underlying graph.
-
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
-\end{abstract}
-
-\section{Introduction}\label{intro-sec}
-
-The \emph{graph realization} problem with respect to a graph property $\mathcal{P}$ is to find a graph that satisfies property $\mathcal{P}$, or to decide that no such graph exists. 
-The motivation for graph realization problems stems both from ``verification'' applications, 
-where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, 
-and from network design applications in engineering, where the goal is to design network topologies having a desired property~\cite{augustine2022distributed,grotschel1995design}.
-Analyzing the computational complexity of the graph realization problems for various natural and fundamental graph properties $\mathcal{P}$ requires a deep understanding of these properties.
-Among the most well studied such parameters for graph realization 
-are constraints on the distances between vertices~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance,chung2001distance,bixby1988almost,culberson1989fast}, 
-on the vertex degrees~\cite{GolovachM17,gomory1961multi,hakimi1962realizability,Bar-NoyCPR20,erdos1960graphs}, 
-%%%%barNoy2021selected,cai2000solution
-on the eccentricities~\cite{barNoy2020efficiently,hell2009linear,behzad1976eccentric,lesniak1975eccentric}, and on connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,frank1994connectivity,frank1970connectivity,gomory1961multi}, among others.
-
-In the simplest version of a graph realization problem with respect to vertex distances, 
-we are given a symmetric $n \times n$ matrix $D$ and we are looking for an $n$-vertex undirected and unweighted graph $G$ such that $D_{i,j}$ equals the distance between vertices $v_i$ and $v_j$ in~$G$.
-This problem can be trivially solved in polynomial time in two steps~\cite{hakimi1965distance}: First, we build the graph $G=(V,E)$ such that $v_i v_j \in E$ if and only if $D_{i,j}=1$.
-Second, from this graph $G$ we compute the matrix $D_G$ which captures the shortest distances for all pairs of vertices.
-If $D_G = D$ then $G$ is the desired graph, otherwise there is no graph having $D$ as its distance matrix.
-Non-trivial variations this problem have been extensively studied, such as for weighted graphs~\cite{hakimi1965distance,Patrinos-Hakimi-72}, as well as for cases where the realizing graph has to belong to a specific graph family~\cite{hakimi1965distance, barNoy2021composed}.
-Other variations of the problem include the cases where every entry of the input matrix $D$ may contain a range of consecutive permissible values~\cite{barNoy2021composed,Rubei16,Tamura93}, or even an arbitrary set of acceptable values~\cite{barNoy2022GraphRealization} for the distance between the corresponding two vertices.
-
-In this paper we make the first attempt to understand the complexity of the graph realization problem with respect to vertex distances in the context of \emph{temporal graphs}, i.e.~of graphs whose \emph{topology changes over time}.
-
-\begin{definition}[temporal graph~\cite{KKK00}]
-\label{temp-graph-def} A \emph{temporal graph} is a pair $(G,\lambda)$,
-where $G=(V,E)$ is an underlying (static) graph and $\lambda :E\rightarrow 2^\mathbb{N}$ is a \emph{time-labeling} function which assigns to every edge of $G$ a set of discrete time-labels.
-\end{definition}
-
-Here, whenever $t \in \lambda(e)$, we say that the edge $e$ is \emph{active} or \emph{available} at time $t$.
-In the context of temporal graphs, where the notion of vertex adjacency is time-dependent, the notions of path and distance also need to be redefined.
-The most natural temporal analogue of a path is that of a \emph{temporal} (or \emph{time-dependent}) path, which is motivated by the fact that, due to
-causality, entities and information in temporal graphs can ``flow'' only along sequences of
-edges whose time-labels are strictly increasing.
-
-\begin{definition}[fastest temporal path] \label{def:temporalPath+Duration}
-Let $(G,\lambda)$ be a temporal graph. A \emph{temporal path} 
-in $(G,\lambda)$ is a sequence $(e_1,t_1),(e_2,t_2),\ldots,(e_k,t_k)$, 
-where $P=(e_1,\ldots,e_k)$ is a path in the underlying static graph $G$, 
-%(we usually say that $P$ is the underlying path of $(P,\lambda)$), 
-$t_i\in \lambda(e_i)$ for every $i=1,\ldots,k$, and $t_1<t_2<\ldots<t_k$. 
-The \emph{duration} of this temporal path %$(P,\lambda)$ from $u$ to $v$ 
-is $t_k - t_1 + 1$.
-A \emph{fastest} temporal path from a vertex $u$ to a vertex $v$ in $(G,\lambda)$ is a temporal path from $u$ to $v$ with the smallest duration.
-The duration of the \emph{fastest} temporal path from $u$ to $v$ is denoted by $d(u,v)$.
-\end{definition}
-
-%Other temporal analogues of a shortest path are temporal paths with the smallest total number of edges (\emph{shortest} temporal path), or the smallest earliest arrival time (\emph{foremost} temporal path), respectively.
-
-In an arbitrary temporal graph $(G,\lambda)$ there can be pairs of vertices $u,v$ where there is no temporal path at all from $u$ to $v$, even if the underlying graph $G$ is undirected and connected. 
-In order to focus on the smallest duration of temporal graphs, rather than on temporal reachability between vertices, we consider in this paper only \emph{periodic} temporal graphs, i.e.~on temporal graphs in which the availability times of every edge are periodic (all edges having the same period $\Delta$)~\cite{casteigts2012time}.
-Apart from the theoretical interest of periodic temporal graphs, which have not been well studied and understood in the literature, they capture naturally many application areas too, such as transportation or satellite networks, where entities move according to repeating schedules or time tables.
-For example, a fastest temporal path from vertex $u$ to vertex $v$ in the temporal graph defined by a transportation (resp.~satellite) network represents the shortest travel time (resp.~the shortest communication delay) from $u$ to $v$.
-As it turns out, the periodic temporal graph realization problem with respect to a given $n \times n$ matrix $D$ of the fastest duration times has a very different computational complexity behavior than the classic graph realization problem with respect to shortest path distances in static graphs.
-
-Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$.
-Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
-In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
-When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
-Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge.
-We call the graph defined by those edges as the \emph{underlying graph} of $D$.
-
-\subparagraph{Our contribution.}
-%In this work, 
-We initiate the study of naturally motivated graph realization problems in the temporal setting. To this end, we introduce and investigate the following problem, capturing the setting described above:
-
-\problemdef{\deltaExactLong\ (\deltaExact)}
-{An $n \times n$ matrix $D$, a positive integer $\Delta$.}
-{Does there exist a graph $G=(V,E)$ with vertices $\{v_1,\ldots,v_{n}\}$ 
-and a $\Delta$-periodic labeling $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ such that, 
-for every $i,j$, the duration of the fastest temporal path from $v_i$ to $v_j$ in the $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$ is $D_{i,j}$?}
-
-We start with showing NP-hardness of the problem (\cref{thm:NPhardness}), even if $\Delta$ is a small constant.
-To establish a baseline for tractability, we show that \deltaExact\ is polynomial-time solvable if the underlying graph is a tree (\cref{thm:deltaExact-PolyTimeTrees}).
-
-Building upon these initial results, we explore the possibilities to generalize our polynomial-time algorithm using the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}.
-That is, we investigate the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure its ``tree-likeness''.
-
-We obtain the following results. We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph (\cref{thm:W1wrtFVS}). 
-To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
-The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
-
-We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
-Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures.
-Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets.
-The notion of segment is crucial for adding the necessary and sufficient number of linear constraints.
-We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.
-
-Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-
-%Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to Appendix.
-
-\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction.
-
-To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
-
-There are two problem settings that share similarities with our setting, which we discuss in more detail in the following.
-
-Several problems have been studied where the goal is to assign labels to (sets of) edges of a given static graph in order to achieve certain connectivity-related properties~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity,enright2021assigning}.
-The main difference to our problem setting is that in the mentioned works, the input is a graph and the sought labeling is not periodic.
-Furthermore, the investigated properties are temporal connectivity among all vertices~\cite{KlobasMMS22,MertziosMS19,akrida2017complexity}, temporal connectivity among a subset of vertices~\cite{KlobasMMS22}, or reducing reachability among the vertices~\cite{enright2021assigning}.
-In all cases the duration of the temporal connections is not of interest.
-
-The only work we are aware of that studies problems on periodic temporal graphs is work on the temporal cops and robber game~\cite{Morawietz021,MorawietzRW20,ErlebachS20}.
-The question here is (in its basic case) whether a certain number of cops are able to catch a robber, if everybody can move along one edge at every time step and the robber is considered caught if it occupies the same vertex as a cop at the same time.
-
-\subparagraph{Preliminaries and notation.}
-We already introduced the most central notion and concepts. There are some additional definitions we need to present our proofs and results which we give in the following.
-
-An interval in $\mathbb N$ from $a$ to $b$ is denoted by $[a,b] = \{ i\in \mathbb N  :  a \leq i \leq b\}$; similarly, $[a] = [1,a]$.
-An undirected graph~$G=(V,E)$ consists of a set~$V$ of vertices 
-and a set~$E \subseteq V \times V$ of edges.
-For a graph~$G$, we also denote by~$V(G)$ and~$E(G)$ the vertex and edge set of~$G$, respectively.
-We denote an edge $e \in E$ between vertices $u,v \in V$ as a set $e=\{u,v\}$.
-For the sake of simplicity of the representation, an edge $e$ is sometimes also denoted by $uv$. 
-A path~$P$ in $G$ is a subgraph of $G$ with vertex set~$V(P)=\{v_1,\dots,v_k\}$ and edge set~$E(P)=\{\{v_i,v_{i+1}\} :  1\leq i<k\}$
-(we often represent path~$P$ by the tuple~$(v_1,v_2,\dots,v_k)$).
-
-Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
-For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
-$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
-Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
-as a temporal path in $(G,\lambda)$,
-where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
-We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.
-
-We remark that a fastest path between two vertices in a temporal graph can be computed in polynomial time~\cite{xuan_computing_2003,Wu2016Efficient}.
-%Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$, in a temporal graph $(G,\lambda)$, to all other vertices,
-%that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
-which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
-
-\begin{comment}
-Let $(G,\lambda)$ be a temporal graph with  $n = |V(G)|$ and  $m=|E(G)|$.
-Let $v \in V(G)$ be an arbitrary vertex of $G$, denote with $deg_{max}$ the maximum degree of all vertices in $V(G)$ and let $S_v$ be the set of time edges in $(G,\lambda)$, incident to $v$, \ie $S_v = \{(uv, \lambda(uv)) | uv \in E(G)\}$.
-In their work Wu et~al.~\cite{Wu2016Efficient} provide an algorithm that computes the duration of the fastest temporal path from a source vertex $v$ to all other vertices in $G$ in
-$O(n + m \log c)$ time, where $c = \min \{|S_v|, deg_{max}\}$.
-From this result, we can deduce the following. 
-\begin{lemma} \label{lemma:calculatingD}
-Let $(G, \lambda, \Delta)$ be a $\Delta$-periodic temporal graph, where $\lambda$ assigns exactly $k$ labels to every edge of $G$. 
-Denote with $deg_{max}$ the maximum degree of vertices in $G$, let $deg(v_i)$ be the degree of vertex $v_i \in V(G)$,
-and let $c_{v_i} = \min \{ k \cdot deg(v_i), deg_{max}\}$.\\
-To calculate the durations of all fastest temporal paths from a fixed vertex $v \in V(G)$ to all other vertices, it takes $O(n + m \log c_v)$ time. \\
-To calculate the durations of the fastest temporal paths among all pairs of vertices we then need $O(n^2 + m \sum_{v \in V(G)} \log c_v)$ time.
-\end{lemma}
-
-Observe that $O(n + m \log c_v) = O(n + m \log deg_{max}) = O(n + m \log n) = O(n^2 \log n)$ and similarly
-$O(n^2 + m \sum_{v \in V(G)} \log c_v) = O(n^2 + mn \log deg_{max}) = O(n + mn \log n) = O(n^3 \log n)$.
-Since an instance $I$ of \kDeltaExact\ problem is an $n \times n$ matrix $D$, the running time of calculating one row of $D$ (\ie the fastest temporal paths from a single vertex to all others) takes $O(|I|\log \sqrt{|I|})$-time and calculating the whole matrix $D$ (\ie the fastest temporal paths among all pairs of vertices) takes $O(|I|^{3/2} \log \sqrt{|I|})$ time.
-Therefore, from now on we say that calculating (a row of) $D$ takes polynomial time.
-\end{comment}
-%\section{Results}
-
-\subparagraph{Organization of the paper.}
-In \cref{sec:hardness} we present our hardness results, first the NP-hardness in \cref{sec:nphardness} and then the parameterized hardness in \cref{sec:w1hardness}.
-In \cref{sec:algos} we present our algorithmic results.
-First we give in \cref{sec:cyclealgo} a polynomial-time algorithm for the case where the underlying graph is a tree.
-In \cref{sec:FPT} we generalize this and present our FPT result, which is the main result in the paper.
-In \cref{sec:cyclealgo} we provide a simple polynomial-time algorithm for the case where the underlying graph is a cycle.
-Finally, we conclude in \cref{sec:conclusion} and discuss some future work directions.
-
-\section{Hardness results for \deltaExact}\label{sec:hardness}
-In this section we present our main computational hardness results.
-In \cref{sec:nphardness} we show that \deltaExact\ is NP-hard even for constant $\Delta$.
-In \cref{sec:w1hardness} we investigate the parameterized computational hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that \deltaExact\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-
-\subsection{NP-hardness of \deltaExact}\label{sec:nphardness}
-In this section we prove that in general it is NP-hard to determine a $\Delta$-periodic temporal graph $(G,\lambda)$ respecting a duration matrix $D$,
-even if $\Delta$ is a small constant.
-
-\begin{theorem}\label{thm:NPhardness}
-	\deltaExactLong\ is \NP-hard for all $\Delta \geq 3$.
-\end{theorem}
-
-\begin{proof}
-	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
-    A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
-    We are asked whether $\phi$ admits a satisfying assignment.
-
-    Given an instance $\phi$ of NAE 3-SAT, we construct an instance $(D,\Delta)$ of \deltaExact\ as follows.
-
- We start by describing the vertex set of the underlying graph $G$ of $D$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
-\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
-\item We add one additional super vertex $v$.
-\end{itemize}
-Next, we describe the edge set of $G$.
-\begin{itemize}
-\item For each variable $x_i$ in $\phi$ we add the following five edges: 
-$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
-\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
-$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
-\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
-If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
-\end{itemize}
-This finishes the construction of $G$.
-For an illustration see~\cref{fig:NP-example}.
-
-%
-\begin{figure}[t]
-	\noindent
-	\makebox[\textwidth]{
-		\centering
-\begin{tikzpicture}%[xscale=2]
-
-	%%Variable X1
-	\node (x1t) at (1,0) {};
-	\node (x1f) at (3,0) {};
-
-	%%Variable X2
-	\node (x2t) at (5,0) {};
-	\node (x2f) at (7,0) {};
-
-	%%Variable x3
-	\node (x3t) at (9,0) {};
-	\node (x3f) at (11,0) {};
-
-	%%Variable x4
-	\node (x4t) at (13,0) {};
-	\node (x4f) at (15,0) {};
-
-	%% edges among xt, xf vertices
-	%x1 to all
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
-	%x2 to all
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
-	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
-	%x3 to all
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);
-
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
-	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);
-
-	%%Variable X1
-	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
-	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
-	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
-	\draw (x1t) -- (x1f) -- (x1) -- (x1t);
-
-	%%Variable X2
-	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
-	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
-	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
-	\draw (x2t) -- (x2f) -- (x2) -- (x2t);
-
-	%%Variable x3
-	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
-	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
-	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
-	\draw (x3t) -- (x3f) -- (x3) -- (x3t);
-
-	%%Variable x4
-	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
-	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
-	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
-	\draw (x4t) -- (x4f) -- (x4) -- (x4t);
-
-	%%vertices for clauses c1, c2 + vertex v
-	\node[vert,label=above:$v$] (v) at (8,3) {};
-	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
-	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};
-
-	%%% edges between x1 gadget and v,c1,c2
-	\draw (x1t) to node[timelabel] {$1$} (c1);
-	\draw (x1t) to node[timelabel] {$1$} (c2);
-	\draw (x1t) to [out=90,in=190] (v);
-	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);
-
-	%%% edges between x2 gadget and v,c1,c2
-	\draw (x2f) to node[timelabel] {$1$} (c1);
-	\draw (x2t) to node[timelabel] {$1$} (c2);
-	\draw (x2t) to [out=80,in=210]  (v);
-	\draw (x2f) to node[timelabel] {$3$} (v);
-
-	%%% edges between x3 gadget and v,c1
-	\draw (x3t) to node[timelabel] {$1$} (c1);
-	\draw (x3t) to node[timelabel] {$3$} (v);
-	\draw (x3f) to [out=100,in=330] (v);
-
-	%%% edges between x4 gadget and v,c2
-	\draw (x4t) to node[timelabel] {$1$} (c2);
-	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
-	\draw (x4f) to [out=90,in=360] (v);
-
-\end{tikzpicture}
-}
-\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
-	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
-To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
-Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
-where all unlabeled edges get the label $2$.
-}\label{fig:NP-example}
-\end{figure}
-%
-We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
-For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
-where $u,v$ are two vertices of $G$. 
-We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
-\begin{itemize}
-    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
-    %$d(x_1,x_2)=2$. 
-    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
-    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
-    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
-    \item For each clause $c$ in $\phi$ and the super vertex $v$
-    we specify the following durations:
-    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
-    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
-    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
-    If $x_i$ appears non-negated in $c$ we specify the following durations:
-    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
-    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
-    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
-    and
-    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
-    $d(c_i,c_j)= \Delta + 1$.
-\end{itemize}
-This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time.
-In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
-
-$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
-Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$.
-%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.
-
-We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
-if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{true}, otherwise we set $x_i$ to \textsc{false}.
-
-To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
-First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
-Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
-(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
-then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
-the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.
-
-Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
-If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
-Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
-In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{false}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.
-
-%Furthermore, we have that if $x$ appears non-negated in clause $c$, then $\lambda(\{c,x^T\})=t-1$, otherwise we have $d(c,x^T)>2$.
-Symmetrically, we have that if $x$ appears negated in clause $c$, then $\lambda(\{c,x^F\})=t'-1$, otherwise we have $d(c,x^F)>2$.
-
-Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
-Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
-Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
-The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
-such that the two edges have consecutive labels. 
-By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
-Assume w.l.o.g.\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
-Let us denote with $t = \lambda(x_1^T v)$.
-It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
-Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
-Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
-Which implies that $x_1$ is set to \textsc{true}.
-%
-Let us observe paths from $v$ to $c_1$.
-We know that $d(v,c)=\Delta -1$.
-The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
-Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
-$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
-This implies that
-the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
-Since there are only two other vertices connected to $c$, 
-we have only two other edges incident to $c$, that can be used on a fastest temporal path
-$v$ to $c$.
-Suppose now w.l.o.g.\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta-1$ goes through vertex $x_2^T$.
-Let us denote with $t' = \lambda(x_2^T v)$.
-Since the fastest temporal path from $v$ to $c$ is of the duration $\Delta - 1$,
-and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
-it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
-Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
-Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
-Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
-In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
-which implies that $x_2$ is set to \textsc{false}.
-But now we have that $x_1,x_2$ both appear in $c$ non-negated, where one of them is \textsc{true}, while the other is \textsc{false},
-which implies that the clause $c$ is satisfied, a contradiction.
-
-%Assume w.l.o.g.\ that variable $x$ appears non-negated in clause $c$.
-Then we have that $\{c,x^T\}\in E(G)$.
-Assume that $\lambda(\{c,x^T\})=t$.
-Recall that we have specified $d(c,x_2)=2$.
-Hence we have that $\lambda(\{x_2,x^T\})=t+1$.
-
-$(\Leftarrow)$: Assume that $\phi$ is satisfiable. Then there exists a satisfying assignment for the variables in $\phi$.
-
-We construct a labeling $\lambda$ as follows.
-\begin{itemize}
-    \item All edges incident with a clause vertex $c$ obtain label one.
-    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
-    \item If variable $x_i$ is set to \textsc{true}, we set $\lambda(x_i^F v)=3$.
-    \item If variable $x_i$ is set to \textsc{false}, we set $\lambda(x_i^T v)=3$.
-    \item We set the labels of all other edges to two.
-\end{itemize}
-For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
-\begin{itemize}
-    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
-    and $d(v,x_i)=\Delta$.
-
-    If $x_i$ is set to \textsc{true}, then there is a temporal path from $x_i$ to $v$ via 
-    $x_i^F$ of duration $2$, since
-    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
-    For a temporal path from $v$ to $x_i$ we observe the following.
-    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
-    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
-    cannot finish before the time $\Delta + 2$.
-    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
-    and continue to $x_i$ at time $\Delta + 2$,
-    which gives us the desired duration $\Delta$.
-
-    If $x_i$ is set to \textsc{false}, then, by similar arguing, 
-    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
-    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.
-
-    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
-    and $d(v,c)=\Delta - 1$:
-
-    Suppose $x_i,x_j,x_k$ appear in $c$.
-    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{true} and at least one to \textsc{false}. 
-    Suppose $x_i$ is the variable of the literal that is \textsc{true} in $c$,
-    and $x_j$ is the variable of the literal that is \textsc{false} in $c$.
-    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{true} (the case when $x_i$ appears negated in $c$ and is set to \textsc{false} is symmetric).
-    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
-    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{false} 
-    (the case when $x_j$ appears negated in $c$ and is set to \textsc{true} is symmetric).
-    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
-    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.
-
-    \item Let $x_i$ be a variable that appears in clause $c$.
-    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
-    and $d(x_i,c)=d(x_i^F,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
-    which proves the first equality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^T$ and
-    second, from $x_i^F$ to $c$ through $x_i^T$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.
-
-    If $x$ appears negated in $c$ we have to check that 
-    $d(c,x_i)=d(c,x_i^T)=2$
-    and $d(x_i,c)=d(x_i^T,c)= \Delta$.
-
-    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
-    which proves the first inequality.
-    There are also the following two temporal paths,
-    first, from $x_i$ to $c$ through $x_i^F$ and
-    second, from $x_i^T$ to $c$ through $x_i^F$.
-    Both of the temporal paths start on the edge with label $2$, as 
-    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
-    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
-    Which proves the second equality.
-
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
-    first,
-    $d(c,x_i^T)=d(c,x_i^F)=2$,
-    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
-    third, $d(x_i,c)=\Delta$,
-    and fourth $d(c,x_i)=2 \Delta + 2$.
-
-    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
-    Then there is a temporal path 
-    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
-    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
-    which proves the first equality.
-    Using the same temporal path in the opposite direction,
-    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
-    yields the second equality.
-    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
-    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
-    with labels $1, 2, 2$ respectively.
-    This proves the second equality.
-    Now for the case of a temporal path from $x_i$ to $c$,
-    we use the same three edges, but in the opposite direction,
-    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
-    again with labels $2, 2, 1$, respectively,
-    which proves the last equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
-    $d(x_i,x_j)=2\Delta +1$ and
-    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-
-    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
-    $x_i^T$ or $x_i^F$, 
-    and then through one of the vertices $x_j^T$ or $x_j^F$.
-    This temporal path is of length $3$, where all of the edges have label $2$,
-    which proves the first equality.
-    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
-    passes through one of the vertices $x_i^T$ or $x_i^F$.
-    This path is of length two, where all of the edges have label $2$,
-    which proves the second equality.
-    Note that all of the above temporal paths are also the shortest possible, 
-    and since the labels of first and last edges (of these paths) are unique,
-    it follows that we cannot find faster temporal paths.
-
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
-    $d(c_i,c_j)= \Delta + 1$.
-
-    Let $x_k$ be a variable that appears non-negated in $c_i$
-    and $x_\ell$ the variable that appears non-negated in $c_j$
-    (all other cases are symmetric).
-    There is a path of length three from $c_i$ to $c_j$
-    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
-    Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
-    which proves the desired equality.
-    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
-    therefore it follows that this is the fastest temporal path.
-\end{itemize}
-Lastly, observe that the above constructed labeling $\lambda$ uses values $\{1,2,3\}\subseteq[\Delta]$, since we have $\Delta\ge 3$.
-\end{proof}
-
-\subsection{Parameterized hardness of \deltaExact}\label{sec:w1hardness}
-
-In this section, we investigate the parameterized hardness of \deltaExact\ with respect to structural parameters of the underlying graph.
-We show that the problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-The \emph{feedback vertex number} of a graph $G$ is the cardinality of a minimum vertex set $X\subseteq V(G)$ such that $G-X$ is a forest.
-The set $X$ is called a \emph{feedback vertex set}.
-Note that, in contrast to the result of the previous section (\cref{thm:NPhardness}), the reduction we use to obtain the following result does not produce instances with a constant $\Delta$.
-
-\begin{theorem}\label{thm:W1wrtFVS}
-    \deltaExactLong\ is W[1]-hard when parameterized by the feedback vertex number of the underlying graph.
-\end{theorem}
-\begin{proof}
-    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.
-Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$.
-If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
-    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
-    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
-    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way, that is, $F_{i,j}=\{e^{i,j}_1,e^{i,j}_2,\ldots,e^{i,j}_m\}$.
-
-We give a reduction to a variant of \deltaExactLong\ where the period $\Delta$ is infinite (that is, there are no periods) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
-
-    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ (with infinity entries and no periods) as follows.
-To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to be an edge connecting the two vertices.
-Afterwards, we describe the remaining entries of $D$.
-    We will construct $G$ using several gadgets.
-
-    \subparagraph{Edge selection gadget.} We first introduce an \emph{edge selection gadget $G_{i,j}$ for color combination $i,j$} with $i<j$. We start with describing the vertex set of the gadget.
-    \begin{itemize}
-        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
-        %\item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
-        %\item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
-        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $4n+1$ vertices each, that is, $U_\ell=\{u^\ell_0, u^\ell_1, u^\ell_2,\ldots, 
-        %u^\ell_n, u^\ell_{n+1},\ldots, u^\ell_{4n-1}, 
-        u^\ell_{4n}\}$ for all $\ell\in[m]$. 
-        %Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
-        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The gadget has the following edges.
-    \begin{itemize}
-        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{v_{i,j}^\star,u^\ell_0\}$, and $\{u^\ell_{4n},v_{i,j}^{\star\star}\}$.
-
-        %Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
-        \item For all $\ell\in [m]$ and $\ell'\in [4n]$, we have edge $\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}$.
-    \end{itemize}
-    %This finishes the construction of the edge selection gadget.
-
-    \subparagraph{Verification gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
-    \begin{itemize}
-        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
-        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
-        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
-    \end{itemize}
-    We add the following edges. We add edge $\{y^i,v^i_0\}$.
-    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
-    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
-    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
-    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$.
-Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.
-
-    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
-
-    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
-    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$.
-If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
-%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.
-
-    Let $i<j\le k$ (skip if $i=k$), let $e_\ell^{i,j}\in F_{i,j}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,j}$.
-Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and edge $\{a^{i,j,\ell}_{5n},u^\ell_{3n+\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'-1}$ of the edge selection gadget of color combination $i,j$.
-    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{3n+\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{3n+\ell'}$ of the edge selection gadget of color combination $i,j$.
-
-    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\subparagraph{Alignment gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-Intuitively, this gadget is used to relate labels of different gadgets to each other.
-
-\subparagraph{Feedback vertex number.} This finished the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
-\begin{itemize}
-    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
-    \item vertices $v^i_\ell$ with $0\le \ell\le k$ of each verification gadget,
-    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
-    \item vertex $w^\star$ of the alignment gadget
-\end{itemize}
-forms a feedback vertex set in $G$ with size $O(k^2)$.
-
-\subparagraph{\boldmath Duration matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\begin{figure}%[t]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
-	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
-	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
-	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
-	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
-	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);
-
-    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
-	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
-	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
-	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);
-
-    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
-	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
-	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
-	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);
-
-    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
-	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
-	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
-	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);
-
-    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
-	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
-	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
-	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);
-
-    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
-	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
-	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
-    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
-	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);
-
-    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
-	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
-	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
-    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
-	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);
-
-    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
-	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
-	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
-    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);
-
-    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
-	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
-	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
-    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[timelabel] {$1$} (W1);
-	\draw[edge] (W) --node[timelabel] {$1$} (W2);
-	\draw[edge] (W) --node[timelabel] {$1$} (W3);
-	\draw[edge] (W) --node[timelabel] {$1$} (W4);
-	\draw[edge] (W) --node[timelabel] {$1$} (W5);
-	\draw[edge] (W) --node[timelabel] {$1$} (W6);
-
-	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
-	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
-	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
-	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);
-
-	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);
-
-	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
-	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
-\subparagraph{Correctness.} This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.
-
-\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution.
-We have that the underlying graph $G$ is uniquely defined by $D$.
-We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.
-
-To start, consider the alignment gadget. We can observe that all edges incident with $w^\star$ have the same label.
-\begin{claim}\label{claim:1}
-    For all $w\in \hat{W}$ we have that $\lambda(\{w^\star,w\})=t$ for some $t\in\mathbb{N}$.
-\end{claim}
-\begin{claimproof}
-    Assume for contradiction that there are $w,w'\in \hat{W}$ such that $\lambda(\{w^\star,w\})=t$ and $\lambda(\{w^\star,w'\})=t'$ with $t\neq t'$.
-Let w.l.o.g.\ $t<t'$.
-Then $w$ can reach $w'$, however we have that $d(w,w')=\infty$, a contradiction.
-\end{claimproof}
-\cref{claim:1} allows us to assume w.l.o.g.\ that all edges incident with vertex $w^\star$ of the alignment gadget have label $1$. From now we will assume that this is the case.
-
-Next, we analyse the labelings of connector gadgets.
-We show that all edges incident with vertices of connector gadgets have labels of at least $n^9$ and at most $n^9+2$.
-More precisely, we show the following.
-\begin{claim}\label{claim:2}
-    Let $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ be the vertices of a connector gadget with sets $A$ and $B$. Then we have that 
-    %\begin{itemize}
-        %\item 
-        $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$,  $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$,
-        %\item 
-        $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$, $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$, and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$. 
-        %\item For all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\}), \lambda(\{\hat{v}_2,v\})\le n^9+2$.
-        %\item For all $v\in A\setminus B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-        %\item For all $v\in B$ we have $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9$.
-        %\item 
-        Furthermore, for all $v\in V^\star$ we have $n^9\le \lambda(\{\hat{v}_1,v\})\le n^9+2$ and $n^9\le \lambda(\{\hat{v}_2,v\}) \le n^9+2$.
-    %\end{itemize}
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the vertex of the alignment gadget that is neighbor of $w^\star$ and $\hat{v}_0$.
-We have $d(w^\star,\hat{v}_0)=n^9$.
-It follows that $\lambda(\{w,\hat{v}_0\})=n^9$.
-Since $d(\hat{v}_1,w)=\infty$ and $d(w,\hat{v}_1)=\infty$, we have that $\lambda(\{\hat{v}_0,\hat{v}_1\})=n^9$.
-    Note that $\hat{v}_1$ is the only common neighbor of $\hat{v}_0$ and $\hat{v}_2$ and the only common neighbor of $\hat{v}_0$ and $\hat{v}_0'$.
-Since $d(\hat{v}_0,\hat{v}_2)=2$ and $d(\hat{v}_0,\hat{v}_0')=3$ we have that $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$ and $\lambda(\{\hat{v}_0',\hat{v}_1\})=n^9+2$.
-Similarly, we have that $\hat{v}_2$ is the only common neighbor of $\hat{v}_3$ and $\hat{v}_1$ and the only common neighbor of $\hat{v}_3$ and $\hat{v}_3'$.
-Since $d(\hat{v}_3,\hat{v}_1)=2$ and $d(\hat{v}_3,\hat{v}_3')=3$ we have that $\lambda(\{\hat{v}_2,\hat{v}_3\})=n^9$ and $\lambda(\{\hat{v}_2,\hat{v}_3'\})=n^9+2$.
-
-%    
-Let $v\in V^\star$.
-Note that $d(v,\hat{v}_0)=\infty$ and $d(v,\hat{v}_3)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\ge n^9$ and $\lambda(\{\hat{v}_2,v\})\ge n^9$.
-Otherwise, there would be a temporal path from $v$ to $\hat{v}_0$ via $\hat{v}_1$ or a temporal path from $v$ to $\hat{v}_3$ via $\hat{v}_2$, a contradiction.
-Furthermore, note that $d(\hat{v}_0',v)=\infty$ and $d(\hat{v}_3',v)=\infty$.
-It follows that $\lambda(\{\hat{v}_1,v\})\le n^9+2$ and $\lambda(\{\hat{v}_2,v\})\le n^9+2$.
-Otherwise, there would be a temporal path from $\hat{v}_0'$ to $v$ via $\hat{v}_1$ or a temporal path from $\hat{v}_3$ to $v$ via $\hat{v}_2$, a contradiction.
-%Furthermore, if $v\in B$ then we also have $d(\hat{v}_0,v)=\infty$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9$.
-%If $v\notin B$ then we have $d(\hat{v}_0,v)=3$ and it follows that $\lambda(\{\hat{v}_1,v\})=n^9+2$ or $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-\end{claimproof}
-
-Now we take a closer look at the edge selection gadgets. We make a number of observations that will allow us to define a set of vertices in $H$ that we claim to be a multicolored clique.
-
-\begin{claim}\label{claim:3}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})\le n^9+2$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    Consider the first connector gadget of the edge selection gadget for $i,j$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_{i,j}^{\star\star}\in B$ and hence we have that $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-Furthermore, we have that $u^\ell_{4n}\notin B$ and hence $d(\hat{v}_0,u^\ell_{4n})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $u^\ell_{4n}$ arrives at $u^\ell_{4n}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_{i,j}^{\star\star}$ via $u^\ell_{4n}$, a contradiction to $d(\hat{v}_0,v_{i,j}^{\star\star})=\infty$.
-\end{claimproof}
-
-\begin{claim}\label{claim:4}
-    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-\end{claim}
-\begin{claimproof}
-    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$.
-Note that $x_1$ is connected to the alignment gadget.
-Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$.
-Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.
-
-    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$.
-Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$.
-However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
-    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$.
-Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$.
-However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
-    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$.
-Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$.
-This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue.
-    From this assumption and \cref{claim:2} it follows, that the first edge of the temporal path has a label with value at least $n^9$.
-However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label with value at most $n^9+2$.
-It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.
-
-    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$.
-Now let $1<\ell\le m$.
-We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$.
-Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$.
-Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$.
-Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue.
-By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$.
-Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$.
-It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$.
-Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$.
-In both cases we have a contradiction.
-    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$.
-Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$.
-Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction.
-\end{claimproof}
-
-\begin{claim}\label{claim:5}
-    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.
-
-    Furthermore, a fastest temporal path from $x_\ell$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell'}_{4n}$ with $\sigma_{i,j}(\ell')=\ell$ (of the edge selection gadget for $i,j$) as its second last vertex.
-\end{claim}
-\begin{claimproof}
-    For every $\ell\in[m]$ we have that $d(x_\ell,v_{i,j}^{\star\star})=8n+5$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
-From \cref{claim:2,claim:4} follows that all edges incident with $x_\ell$ have a label of at least $n^9$ except the one to $v_{i,j}^\star$ and, if $\ell=1$, the edge connecting $x_1$ to the alignment gadget.
-In the latter case, no temporal path from $x_1$ from $v_{i,j}^{\star\star}$ can continue to the neighbor of $x_1$ in the alignment gadget, since it cannot continue from there.
-
-    Now consider $v_{i,j}^{\star\star}$.
-By \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$.
-It follows that a fastest temporal path $P$ from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ after $x_\ell$, since otherwise we have $d(x_\ell,v_{i,j}^{\star\star})\le 2$, a contradiction.
-
-    Furthermore, we have by \cref{claim:2} that all edges incident with $v_{i,j}^{\star\star}$ have a label of at least $n^9$ except the ones incident to $u_{\ell'}^{2n}$ for $\ell'\in[m]$.
-By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\le 4n^6$.
-    It follows that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Otherwise, we have $d(x_\ell,v_{i,j}^{\star\star})> 8n+5$ (for sufficiently large $n$), a contradiction.
-
-    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex.
-Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one).
-Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
-    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$.
-It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$.
-We set $\sigma_{i,j}(\ell')=\ell$.
-
-    Finally, we show that $\sigma_{i,j}$ is a permutation on $[m]$.
-Assume for contradiction that there are $\ell,\ell'\in[m]$ with $\ell\neq \ell'$ such that $\sigma_{i,j}(\ell)=\sigma_{i,j}(\ell')$.
-Then we have that $\lambda(\{u^{\ell}_{4n},v_{i,j}^{\star\star}\})=\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})$.
-However, by \cref{claim:4} we have that all edges from $v_{i,j}^\star$ to a vertex in $X_{i,j}$ have distinct labels.
-Furthermore, we argued above that every fastest path from a vertex in $X_{i,j}$ to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex and a vertex from the set $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ as its second last vertex.
-Since for all $x_{\ell''}$ with $\ell''\in[m]$ we have that $d(x_{\ell''},v_{i,j}^{\star\star})=8n+5$, we must have that all edges from vertices in $\{u^{\ell''}_{4n} :  \ell''\in[m]\}$ to $v_{i,j}^{\star\star}$ must have distinct labels.
-Hence, we have a contradiction and can conclude that $\sigma_{i,j}$ is indeed a permutation.
-\end{claimproof}
-
-For all $1\le i<j\le k$, let $\sigma_{i,j}$ be the permutation on $[m]$ as defined in \cref{claim:5}. We call $\sigma_{i,j}$ the \emph{permutation of color combination $i,j$}. 
-Now we have enough information to define a set of vertices of $H$ that form a multicolored clique.
-To this end, consider the following set $X$ of edges from $H$.
-\[
-X=\{e_\ell^{i,j}\in F_{i,j} :  \sigma_{i,j}(\ell)=1\}
-\]
-We claim that $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-From now on, denote $\{e_{i,j}\}=X\cap F_{i,j}$.
-We show that for all $i\in [k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$, that is, for every color~$i$, all edges of a color combination involving $i$ have the same vertex of color $i$ as endpoint.
-This implies that $\bigcup_{e\in X}e$ is a multicolored clique in $H$.
-
-Before we proceed, we show some further properties of $\lambda$. First, let us focus on the labels on edges of the edge selection gadgets.
-
-\begin{claim}\label{claim:6}
-    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i<j\le k$ and $\ell\in[m]$.
-    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex.
-    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$.
-It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$.
-Hence, the temporal path $P$ has duration at most $8n+3$.
-
-    We investigate the temporal path $P$ from its destination $u^\ell_{4n}$ back to its start vertex $v_{i,j}^\star$.
-Consider the neighbors of $u^\ell_{4n}$ that are different from $v_{i,j}^{\star\star}$.
-By \cref{claim:2} we have that all edges from $u^\ell_{4n}$ to neighbors of $u^\ell_{4n}$ that are vertices of connector gadgets have a label of at least $n^9$.
-Hence, $P$ does not visit any of those neighbors.
-Next, consider neighbors of $u^\ell_{4n}$ in verification gadgets.
-Assume $u^\ell_{4n}$ has a neighbor in the verification gadget of color $i'$ for some $i'\in[k]$.
-Then this neighbor is vertex $b^{i',j,\ell}_{5n}$.
-Note that if $P$ visits $b^{i',j,\ell}_{5n}$, then it also visits all of $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$, since all these vertices have degree two.
-   Now consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are contained in $A$ and are not contained in $B$.
-Hence, we have that all non-adjacent pairs of vertices in $\{b^{i',j,\ell}_{\ell'} :  \ell'\in[5n]\}$ are on duration $3$ apart, according to $D$, and that $|\lambda(\{b^{i',j,\ell}_{\ell'},b^{i',j,\ell}_{\ell'+1}\})-\lambda(\{b^{i',j,\ell}_{\ell'+1},b^{i',j,\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$.
-    It follows that $P$ would have a duration larger than $8n+3$. We can conclude that $P$ does not visit $b^{i',j,\ell}_{5n}$. It follows that $P$ visits $u^\ell_{4n-1}$.
-    Here, we can make an analogous investigation.
-Additionally, we have to consider the case that $P$ visits a neighbor of $u^\ell_{4n-1}$ in verification gadget of color $i'$ for some $i'\in[k]$ that is vertex $a^{i',j,\ell}_{5n}$.
-However, we can exclude this by a similar argument as above.
-
-    By repeating the above arguments, we can conclude that $P$ visits (exactly) all vertices in $\{u^\ell_{\ell'} :  0\le \ell'\le 4n\}$ and $v_{i,j}^\star$.
-    Consider the second connector gadget of the edge selection gadget of $i,j$ with set $A$ and $B$.
-Note that all vertices visited by $P$ are contained in $A\setminus B$.
-It follows that all pairs of non-adjacent vertices visited by $P$ are on duration $3$ apart, according to $D$.
-In particular, we have $d(u^\ell_{\ell'-1},u^\ell_{\ell'+1})=3$ for all $\ell'\in[4n-1]$ and $d(v_{i,j}^\star,u^\ell_{1})=3$.
-If follows that for every $\ell'\in[4n-1]$ we have that $\lambda(\{u^\ell_{\ell'},u^\ell_{\ell'+1}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})\ge 2$ and $\lambda(\{u^\ell_{1},u^\ell_{2}\})-\lambda(\{v_{i,j}^\star,u^\ell_{1}\})\ge 2$.
-
-    By investigating the sets $A,B$ of the first connector gadget of the edge selection gadget of $i,j$, we get that $d(x_{\sigma_{i,j}(\ell)},u^\ell_{1})=3$ and hence $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})\ge 2$.
-Furthermore, we get that $d(u^\ell_{4n-1},v_{i,j}^{\star\star})=3$ and hence $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})\ge 2$.
-Considering that $P$ visits $4n+2$ vertices, we have that all mentioned inequalities of differences of labels have to be equalities, otherwise $P$ has a duration larger than $8n+3$ or we have that $\lambda(\{v_{i,j}^\star,u^\ell_{1}\})-\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})< 2$ or $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})-\lambda(\{u^\ell_{4n-1},u^\ell_{4n}\})< 2$.
-Since by \cref{claim:4,claim:5} the labels $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^\star\})$ and $\lambda(\{v_{i,j}^{\star\star},u^\ell_{4n}\})$ are determined, then also all labels of edges traversed by $P$ are determined and the claim follows.
-    \end{claimproof}
-
-Next, we investigate the labels of the verification gadgets.
-
-\begin{claim}\label{claim:7}
-    For all $i\in[k]$ we have that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claim}
-\begin{claimproof}
-    Let $w\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Note that we have $d(w^\star,y^i)=n^8-1$.
-It follows that $\lambda(\{w,y^i\})=n^8-1$.
-Furthermore, we have that $d(w,v_0^i)=2$ and note that $y^i$ has degree 2.
-It follows that $\lambda(\{y^i,v_0^i\})=n^8$.
-\end{claimproof}
-
-\begin{claim}\label{claim:8}
-    %Let $i\in[k]$ %and $i<j\le k$ (resp.\ $1\le j< i$) 
-    %and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $1,i$ (or $1,2$ if $i=1$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_0^i$ (of the verification gadget for color $i$).
-    For all $1<i\le k$ and all $\ell\in[m]$ we have that $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\le n^8$ or $\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})\ge n^9+2$.
-    For $i=1$ we have that $\lambda(\{v_0^i,\hat{u}^i_1\})\le n^8$ or $\lambda(\{v_0^i,\hat{u}^i_1\})\ge n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1<i\le k$ and $\ell\in[m]$.
-Assume that $n^8<\lambda(\{v_0^i,a^{i,1,\ell}_{1}\})< n^9+2$.
-Then, since by \cref{claim:7} we have $\lambda(\{y^i,v_0^i\})=n^8$, there is a temporal path from $w^\star$ to $a^{i,1,\ell}_{1}$ via $v_0^i$ that arrives at $a^{i,1,\ell}_{1}$ strictly earlier than $n^9+2$.
-However, we have $d(w^\star,a^{i,1,\ell}_{1})=n^9+2$, a contradiction.
-The argument for case where $i=1$ is analogous.
-\end{claimproof}
-
-\begin{claim}\label{claim:9}
-    For all $1\le i< k$ and all $\ell\in[m]$ we have that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})\le n^9+2$.
-    For $i=k$ we have that $\lambda(\{v_{k}^i,\hat{u}^i_{13n+1}\})\le n^9+2$.
-%
-    %Let $i\in[k]$ and $i<j\le k$ (resp.\ $1\le j< i$) and let $u^\ell_{\ell'}$ be a vertex of the edge selection gadget of color combination $i,j$ (resp.\ $j,i$) for some $\ell\in[m]$ and $0\le\ell'\le 2n$ that is adjacent to vertex $v_k^i$ (of the verification gadget for color $i$).
-Then we have that $\lambda(\{v_k^i,u^\ell_{\ell'}\})\le n^9+2$.
-\end{claim}
-\begin{claimproof}
-    Let $1\le i< k$ and $\ell\in[m]$.
-    Consider the first connector gadget of verification gadget for color $i$ with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and sets $A,B$.
-Recall that $v_k^i\in B$ and hence we have that $d(\hat{v}_0,v_k^i)=\infty$.
-Furthermore, we have that $b^{i,k,\ell}_{1}\notin B$ and hence $d(\hat{v}_0,b^{i,k,\ell}_{1})=3$.
-By \cref{claim:2} and the fact that $d(w^\star,\hat{v}_0)=n^9$ we have that both edges incident with $\hat{v}_0$ have label $n^9$.
-It follows that a fastest temporal path from $\hat{v}_0$ to $b^{i,k,\ell}_{1}$ arrives at $b^{i,k,\ell}_{1}$ at time $n^9+2$.
-Now assume for contradiction that $\lambda(\{v_k^i,b^{i,k,\ell}_{1}\})> n^9+2$.
-Then there exists a temporal walk from $\hat{v}_0$ to $v_k^i$ via $b^{i,k,\ell}_{1}$, a contradiction to $d(\hat{v}_0,v_k^i)=\infty$.
-    The argument for case where $i=k$ is analogous.
-\end{claimproof}
-
-Now we are ready to prove for all $i\in [k]$ that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$.
-Assume for contradiction that for some color $i\in[k]$ we have that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|\neq 1$.
-Consider the verification gadget for color $i$. Recall that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-We first argue that $P$ cannot visit any vertex of a connector gadget or the alignment gadget.
-
-\begin{claim}\label{claim:10}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of a connector gadget.
-\end{claim}
-\begin{claimproof}
-Assume for contradiction that $P$ visits a vertex of a connector gadget.
-Then by \cref{claim:2} we have that the arrival time of $P$ is at least $n^9$.
-By \cref{claim:2} and \cref{claim:9} we have that the arrival time of $P$ is at most $n^9+2$.
-This means that the second vertex visited by $P$ cannot be a vertex from a connector gadget, because by \cref{claim:2} this would imply $d(v_0^i,v_k^i)\le 2$.
-Now we can deduce with \cref{claim:8} that $P$ must have a starting time of at most $n^8$.
-It follows that the arrival time of $P$ must be smaller than $n^9$, a contradiction to the assumption that $P$ visits a vertex of a connector gadget.
-\end{claimproof}
-
-\begin{claim}\label{claim:11}
-Let $i\in[k]$. Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$. Then $P$ does not visit any vertex of the alignment gadget.
-\end{claim}
-\begin{claimproof}
-    Note that $P$ starts outside the alignment gadget.
-This means that if $P$ visits a vertex of the alignment gadget, then the first vertex of the alignment gadget visited by $P$ is a neighbor of $w^\star$.
-However, these vertices have degree two and the edge to $w^\star$ has label one.
-It follows that $P$ cannot continue from the vertex of the alignment gadget, a contradiction.
-\end{claimproof}
-
-It follows that the second vertex visited by $P$ is a vertex $a^{i,1,\ell}_{1}$ for some $\ell\in[m]$ or vertex $\hat{u}_1^i$ if $i=1$.
-In the former case, $P$ has to follow the path segment consisting of vertices in $\{a^{i,1,\ell}_{\ell'} :  \ell'\in[5n]\}$ until it reaches the edge selection gadget of color combination $1,i$.
-From there it can reach vertex $v_1^i$ by traversing some path segment consisting of vertices $\{b^{i,1,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-Alternatively, it can reach vertex $v^1_{i-1}$ or $v^1_{i}$ by traversing some path segment consisting of vertices $\{a^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$ or $\{b^{1,i,\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$, respectively.
-In the latter case ($i=1$), the temporal path $P$ has to follow the path segment consisting of vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ until it reaches $v^i_1$.
-More generally, we can make the following observation.
-\begin{claim}\label{claim:12}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path starting at $v^i_j$ and visiting at most $13n+1$ vertices and no vertex of a connector gadget or the alignment gadget.
-Then $P$ cannot visit vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$.
-\end{claim}
-\begin{claimproof}
-    Consider the edge selection gadget of color combination $i',j'$ for some $i',j'\in[k]$ and let $u^\ell_{\ell'}$ be a vertex of that gadget.
-Disregarding connections via connector gadgets and the alignment gadget, we have that $u^\ell_{\ell'}$ is (potentially) connected to the verification gadget for color $i'$ and the verification gadget of color $j'$.
-    More specifically, by construction of $G$, we have that $u^\ell_{\ell'}$ is potentially connected to 
-    \begin{itemize}
-        \item vertex $v^{i'}_{j'-1}$ by a path along vertices $\{a^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$,
-        \item vertex $v^{i'}_{j'}$ by a path along vertices $\{b^{i',j',\ell}_{\ell''} :  \ell''\in[5n]\}$, 
-        \item vertex $v^{j'}_{i'-1}$ by a path along vertices $\{a^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$, and
-        \item vertex $v^{j'}_{i'}$ by a path along vertices $\{b^{j',i',\ell}_{\ell''} :  \ell''\in[5n]\}$.
-    \end{itemize}
-    Furthermore, by construction of $G$, we have that the duration of a fastest path from $u^\ell_{\ell'}$ to any $v^{i''}_{j''}$ with $i'',j''\in\{0,1,\ldots,k\}$ not mentioned above is at least $10n$ (disregarding edges incident with connector gadgets or the alignment gadget).
-
-    Now consider $v^i_j$ and assume $i<j$ ($i>j$).
-This vertex is (if $j\neq i-1$ and $j\neq k$) connected to some vertex $u^\ell_{\ell'}$ in the edge selection gadget for color combination $i,j+1$ ($j+1,i$) via a path along vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$.
-Furthermore, $v^i_j$ is (if $j\neq 0$ and $j\neq i$) connected to some vertex $u^{\ell'}_{\ell'''}$ in the edge selection gadget for color combination $i,j$ ($j,i$) via a path along vertices $\{b^{i,j,\ell'}_{\ell''} :  \ell''\in[5n]\}$.
-
-    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$.
-From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$.
-Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
-
-    Lastly, consider the case that $j=i-1$ or $j=i$.
-Then we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-The claim follows.
-\end{claimproof}
-Furthermore, we can make the following observation on the duration of the temporal paths characterized in \cref{claim:12}.
-\begin{claim}\label{claim:13}
-    Let $i,j\in\{0,1,\ldots,k\}$.
-Let $P$ be a temporal path from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ and visiting no vertex of a connector gadget or the alignment gadget.
-Then $P$ has duration at least $20n$.
-\end{claim}
-\begin{claimproof}
-    As argued in the proof of \cref{claim:12}, a temporal path $P$ from $v^i_j$ to a vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ or a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-We analyse the former case first.
-
-    Consider the second connector gadget of a verification gadget $i'$ with sets $A,B$, we have that all vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are contained in $A$ and are not contained in $B$.
-It follows that all non-adjacent pairs of vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}\cup\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n],j'\in[k]\setminus\{i'\}\}$ are on duration $3$ apart, according to $D$.
-It follows that $|\lambda(\{a^{i',j',\ell}_{\ell'},a^{i',j',\ell}_{\ell'+1}\})-\lambda(\{a^{i',j',\ell}_{\ell'+1},a^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-Analogously, we have that $|\lambda(\{b^{i',j',\ell}_{\ell'},b^{i',j',\ell}_{\ell'+1}\})-\lambda(\{b^{i',j',\ell}_{\ell'+1},b^{i',j',\ell}_{\ell'+2}\})|\ge 2$ for all $\ell'\in[5n-2]$ and $j'\in[k]\setminus\{i'\}$.
-It follows that two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$ traversed by $P$ both have duration $10n$ and hence $P$ has duration at least $20n$.
-
-    In the latter case, where $P$ traverses a segment of the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$, we can make an analogous argument, since all vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ are contained in the set $A$ of the second connector gadget of the verification gadget of color $i$ but not in the set $B$ of that connector gadget.
-\end{claimproof}
-
-Recall that $P$ denotes a fastest temporal path from $v_0^i$ to $v_k^i$ and that $d(v_0^i,v_k^i)=k(20n+6)+6n-1$.
-By \cref{claim:10,claim:11,claim:12} he have that $P$ needs to visit at least one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^i_0,v^i_k\}$.
-Next, we analyse which vertices in this set are visited by $P$.
-
-\begin{claim}\label{claim:14}
-Let $i\in[k]$.
-Let $P$ be a fastest temporal path from $v_0^i$ to $v_k^i$.
-Then $P$ visits all vertices in $\{v^j_i :  0\le j\le k\}$ and no vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}\setminus\{v^j_i :  0\le j\le k\}$.
-Furthermore, $P$ visits the vertices in order $v^i_0, v^i_1, v^i_2, \ldots, v^i_{k-1},v^i_k$.
-\end{claim}
-\begin{claimproof}
-Let $X\subseteq \{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ denote the set of vertices in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that are visited by $P$.
-By \cref{claim:12,claim:13} we have that $|X|\le k+1$, since otherwise the duration of $P$ would be at least $20n(k+1)>k(20n+6)+6n-1$, a contradiction.
-
-    To prove the claim, we use the notion of a \emph{potential $p^i$ with respect to $i$} of a vertex $v^{i'}_j$.
-    %and a \emph{second potential $p^i_2$ with respect to $i$} of a vertex $v^{i'}_j$. 
-    We say that the first potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i(v^{i'}_j)=i'+j-i$.
-    %We say that the second potential of vertex $v^{i'}_j$ with respect to $i$ is $p^i_2(v^{i'}_j)=j-|i'-i|$. 
-    The temporal path $P$ starts at vertex $v^i_0$ with $p^i(v^i_0)=0$, and ends at vertex $v^i_k$ with $p^i(v^i_k)=k$.
-
-    %Consider the first potential. 
-    Assume the path $P$ is at some vertex $v^{i'}_j$ with $p^i_1(v^{i'}_j)=i'+j-i$.
-    By \cref{claim:12} we have that the next vertex in  $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is some $v^{i''}_{j'}\in \{v^{i'}_{j-1},v^{i'}_j,v^{i'}_{j+1},v^j_{i'-1},v^j_i,v^{j+1}_{i'-1},v^{j+1}_{i'}\}$.
-We can observe that $|p^i(v^{i'}_j)-p^i(v^{i''}_{j'})|\le 1$, that is, the first potential changes at most by one when $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    Since $|X|\le k+1$ we and $p^i(v^i_k)-p^i(v^i_0)=k$ have that the  potential has to increase by exactly one every time $P$ goes from one vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ to the next one.
-    We can conclude that $|X|=k+1$.
-    Furthermore, we have that if the path $P$ is at some vertex $v^{i'}_j$, the next vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ visited by $P$ is either $v^{i'}_{j+1}$ or $v^{j+1}_{i'}$.
-
-    By \cref{claim:13} we have that the temporal path segments from $v^{i'}_j$ to $v^{i'}_{j+1}$ and $v^{j+1}_{i'}$, respectively, have duration at least $20n$.
-However, for the temporal path from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) we can obtain a larger lower bound.
-As argued in the proof of \cref{claim:11}, a temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ has to either traverse two segments of $5n$ vertices in $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in\{i-1,i,j,j+1\}$.
-More precisely, the temporal path segment has to traverse part of the edge selection gadget of color combination $i',j+1$.
-To this end, it traverses the $5n$ vertices in $\{a^{i',j+1,\ell}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell\in[m]$.
-Then it traverses some vertices in the edge selection gadget, and then it traverses the $5n$ vertices in $\{b^{j+1,i',\ell'}_{\ell''} :  \ell''\in[5n]\}$ for some $\ell'\in[m]$.
-
-By construction of $G$, the first vertex of the edge selection gadget visited by the path segment (after traversing vertices in $\{a^{i',j+1,\ell}_{\ell'} :  \ell''\in[5n]\}$) is some vertex $u^\ell_{\ell''}$ with $\ell''\in\{0,1,\ldots,4n\}$.
-The last vertex of the edge selection gadget visited by the path segment is (before traversing the vertices in $\{b^{j+1,i',\ell'}_{\ell''''} :  \ell''''\in[5n]\}$) some vertex $u^{\ell'}_{\ell'''}$ with $\ell'''\in\{0,1,\ldots,4n\}$.
-By construction of $G$, the duration of a fastest path between $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ (in $G$) is at least $3n$.
-Investigating the second connector gadget of the edge selection gadget for $i',j+1$ we can see that a temporal path from $u^\ell_{\ell''}$ and $u^{\ell'}_{\ell'''}$ has duration at least $6n$.
-
-It follows that the temporal path segment from $v^{i'}_j$ to $v^{j+1}_{i'}$ (with $j\neq i'-1$) has duration at least $26n$.
-Furthermore, recall that $P$ starts at $v^i_0$ and ends at $v^i_k$.
-We have that if $P$ contains a path segment from some $v^{i'}_j$ to $v^{j+1}_{i'}$ some (with $j\neq i'-1$), then $P$ visits a vertex $v^{i''}_{j'}$ with $i''\neq i$.
-Hence, it needs to contain at least one additional path segment from some $v^{i'}_j$ to some $v^{j+1}_{i'}$ (with $j\neq i-1$).
-However, then we have that the duration of $P$ is at least $20kn+12n>k(20n+6)+6n-1$, a contradiction.
-
-We can conclude that $P$ only contains temporal path segments from $v^{i}_{j-1}$ to $v^i_{j}$ for $j\in[k]$ and the claim follows.
-%
-   %By \cref{claim:12} and the observations above we have that the second vertex in $\{v^{i'}_{j'} :  i',j'\in \{0,1,\ldots,k\}\}$ that is visited by $P$ has to be one in $\{v^i_1, v^1_{i}\}$. 
-    %
-    \end{claimproof}
-
-Now we have by \cref{claim:12,claim:14} that we can divide $P$ into $k$ segments, the subpaths from $v^i_{j-1}$ to $v^i_j$ for $j\in [k]$.
-We show that all subpaths except the one from $v_{i-1}^i$ to $v_i^i$ have duration $20n+5$.
-The subpath from $v_{i-1}^i$ to $v_i^i$ has duration $26n+5$.
-
-\begin{claim}\label{claim:15}
-    Let $i\in[k]$ and $j\in[k]\setminus\{i\}$.
-Let $P$ be a temporal path from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-If $P$ has duration at most $20n+5$, then it visits exactly two vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$ (or $j,i$).
-\end{claim}
-\begin{claimproof}
-    By the construction of $G$ (and as also argued in the proofs of \cref{claim:12,claim:13}), a temporal path $P$ with duration at most $20n+5$ that does not visit vertices from connector gadgets and the alignment gadget from $v_{j-1}^i$ to $v_j^i$ has to first traverse a segment of $5n$ vertices in $\{a^{i,j-1,\ell}_{\ell'} :  \ell'\in[5n]\}$ and then a segment of $5n$ vertices $\{b^{i,j,\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$.
-By construction of $G$, the two vertices visited in the edge selection gadget for color combination $i,j$ (or $j,i$) are $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ for some $\ell'\in[4n]$.
-By inspecting the connector gadgets in an analogous way as in the proof of \cref{claim:13} we can deduce that all consecutive edges traversed by $P$ must have labels that differ by at least 2.
-If follows that if all consecutive edges have labels that differ by exactly two, then $P$ has duration $20n+5$.
-\end{claimproof}
-
-\begin{claim}\label{claim:16}
-    Let $i\in[k]$. Let $P$ be a temporal path from $v_{i-1}^i$ to $v_i^i$ that does not visit vertices from connector gadgets and the alignment gadget. Then $P$ has duration at least $26n+5$.
-\end{claim}
-\begin{claimproof}
-    By construction of $G$ we have that $v^i_{i-1}$ and $v^i_i$ are connected via a path inside the verification gadget for color $i$, visiting the $13n+1$ vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$.
-Assume $P$ follows this path.
-By inspecting the connector gadgets of the verification gadget of color $i$, we can see that all consecutive edges traversed by $P$ must have labels that differ by at least two.
-It follows that $P$ has duration at least $26n+5$.
-By construction of $G$ we have that if $P$ does not follow the vertices in $\{\hat{u}^i_\ell :  \ell\in[13n+1]\}$ it has to visit at least three different edge selection gadgets: The one of color combination $i-1,i$, then one of $i-1,i+1$, and then the one of $i,i+1$.
-If follows that $P$ needs to visit at least four segments of length $5n$ composed of vertices $\{a^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ or $\{b^{i',j',\ell}_{\ell'} :  \ell'\in[5n]\}$ for some $\ell\in[m]$ and $i',j'\in[k]$.
-By inspecting the connector gadgets of the verification gadgets we know that it takes at least $10n$ time steps to traverse such a segment.
-Hence, the duration of $P$ is at least $40n$.
-\end{claimproof}
-
-Furthermore, we need the following observation which is relevant when we try to connect the above mentioned segments to a temporal path.
-
-\begin{claim}\label{claim:17}
-Let $i\in[k]$ and $0\le j\le k$. The absolute difference of labels of any two different edges incident with $v^i_j$ is at least two.
-\end{claim}
-\begin{claimproof}
-    This follows by inspecting the connector gadgets of the verification gadget of color $i$.
-\end{claimproof}
-
-From \cref{claim:10,claim:11,claim:14,claim:15,claim:16,claim:17} we get that a fastest temporal path $P$ from $v^i_0$ to $v^i_k$ has the following properties.
-\begin{enumerate}
-    \item The path $P$ can be segmented into temporal path segments $P_j$ from $v^i_{j-1}$ to $v^i_j$ for $j\in[k]\setminus\{i\}$ such that $P_j$ is a temporal path from $v^i_{j-1}$ to $v^i_j$ that does not visit vertices from connector gadgets and the alignment gadget and has duration $20n+5$.
-    \item The segment of $P$ from $v^i_{i-1}$ to $v^i_i$ has duration $26n+5$.
-    \item The path $P$ dwells at each vertex $v^i_j$ with $j\in[k-1]$ for exactly two time steps, that is, the absolute difference of the labels on the edges incident with $v^i_j$ that are traversed by $P$ is exactly two.
-\end{enumerate}
-If any of the properties does not hold, then we can observe that $d(v^i_0,v^i_k)>8n+5$ would follow.
-
-Now assume $i\in[k]$ and $j\in[k]\setminus\{i\}$ and consider a fastest temporal path $P_j$ from $v_{j-1}^i$ to $v_j^i$ that does not visit vertices from connector gadgets and the alignment gadget and a fastest temporal path $P_{j+1}$ from $v_{j}^i$ to $v_{j+1}^i$ that does not visit vertices from connector gadgets and the alignment gadget.
-By \cref{claim:15} we know that $P_j$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\ell\in[m]$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i,j$. 
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $\sigma_{i,j}$ is the permutation of color combination $i,j$ (or $j,i$).
-Analogously, we have by \cref{claim:15} that $P_{j+1}$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\ell''\in[m]$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,j+1$.
-%By construction of $G$ we have that $\ell'\in[n]$.
-By \cref{claim:6} we have that $\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})=(i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2$, where $\sigma_{i,j+1}$ is the permutation of color combination $i,j+1$ (or $j+1,i$).
-We have that
-\begin{align*}
-%\[
-& \lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = \\
-%\]
-%\[
-& (i+j+1)\cdot (2n\cdot (\sigma_{i,j+1}(\ell''))^2 +18n+6)+2\ell'''+2\\
-& -((i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2) = \\
-%\]
-%\[
-& (i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') + 18n + 6
-%\]
-\end{align*}
-By the arguments made before we also have that if $P_j$ and $P_{j+1}$ are both path segments of $P$, then 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 20n+6.
-\]
-It follows that 
-\[
-(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2 + 2(\ell'''-\ell') = 2n.
-\]
-Assume that $\sigma_{i,j}(\ell)\neq \sigma_{i,j+1}(\ell'')$, then we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2<6n$ or $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2>10n$, since $|(\sigma_{i,j}(\ell''))^2-(\sigma_{i,j}(\ell))^2|\ge 3$ and $(i+j)\ge 3$.
-However, we have that $\ell',\ell'''\in[4n]$ and hence $|2(\ell'''-\ell')|< 8n$.
-We can conclude that $\sigma_{i,j}(\ell)= \sigma_{i,j+1}(\ell'')$.
-In this case we have that $(i+j+1)\cdot 2n\cdot (\sigma_{i,j+1}(\ell''))^2 - (i+j)\cdot 2n\cdot (\sigma_{i,j}(\ell))^2= 2n\cdot (\sigma_{i,j}(\ell'))^2$.
-It follows that $2n(\sigma_{i,j}(\ell))^2-2(\ell'''-\ell')=2n$. Again, since $|2(\ell'''-\ell')|< 8n$, we have that $\sigma_{i,j}(\ell)=1$ and in turn this implies that $\ell'=\ell'''$.
-
-Note that if $i=1$ or $i=k$ we can already conclude that $|(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})|=1$. 
-By construction of $G$ we have that for all $j\in[k]\setminus\{i\}$ that $v^i_{j-1}$ and $v^i_j$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,j$ (or $j,i$), respectively, via paths using vertices $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ and $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ (for $i=k$, or vertex $w^i_{\ell'-3n}\in W_i$ for $i=1$) is incident with edge $e^{i,j}_\ell\in F_{i,j}$.
-Note that since $\sigma_{i,j}(\ell)=1$ we have that $e^{i,j}_\ell\in X$.
-Since $\ell'$ is independent from $\ell$ and $j$, it follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$ for $i=k$ and $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'-3n}\}$ for $i=1$.
-
-Assume now that $1\neq i\neq k$.
-By \cref{claim:16} we know that the duration of the path segment $P_i$ from $v^i_{i-1}$ to $v^i_i$ is $26n+5$.
-Consider the path segment $P^\star$ from $v^i_{i-2}$ to $v^i_{i+1}$.
-By the arguments above we know that $P^\star$ visits vertices $u^\ell_{\ell'-1},u^\ell_{\ell'}$ with $\sigma_{i-1,i}(\ell)=1$, and $\ell'\in[4n]$ of the edge selection gadget for color combination $i-1,i$ and afterwards $P^\star$ visits vertices $u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}$ with $\sigma_{i,i+1}(\ell'')=1$, and $\ell'''\in[4n]$ of the edge selection gadget for color combination $i,i+1$.
-By analogous arguments as above and the fact that the duration of $P_i$ is $26n+5$ we get that 
-\[
-\lambda(\{u^{\ell''}_{\ell'''-1},u^{\ell''}_{\ell'''}\})-\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\}) = 46n+6.
-\]
-It follows that 
-\[
-(2i+1)\cdot (20n+6)+2\ell'''+2 -((2i-1)\cdot (20n+6)+2\ell'+2) = 46n+6,
-\]
-and hence $\ell'''-\ell'=3n$.
-By construction of $G$ we have that $v^i_{i-2}$ and $v^i_{i-1}$ are connected to $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i-1,i$, respectively, via paths using vertices $\{a^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i-1,\ell}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i-1,i}_\ell\in F_{i-1,i}$.
-Furthermore, we have that $v^i_{i}$ and $v^i_{i+1}$ are connected to $u^{\ell''}_{3n+\ell'-1}$ and $u^{\ell''}_{3n+\ell'}$ of the edge selection gadget of color combination $i,i+1$, respectively, via paths using vertices $\{a^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$ and $\{b^{i,i+1,\ell''}_{\ell''''} :  \ell''''\in[5n]\}$, respectively, if the vertex $w^i_{\ell'}\in W_i$ is incident with edge $e^{i,i+1}_{\ell''}\in F_{i,i+1}$.
-
-Note that since $\sigma_{i-1,i}(\ell)=\sigma_{i,i+1}(\ell'')=1$ we have that $e^{i-1,i}_\ell\in X$ and $e^{i,i+1}_{\ell''}\in X$.
-Since, again, $\ell'$ is independent from $\ell$ and $j$, it follows that $e^{i-1,i}_\ell\cap e^{i,i+1}_{\ell''} =\{w^i_{\ell'}\}$.
-By arguments analogous to the ones above we can also deduce that $\bigcap_{1\le j<i} e_{j,i}=\{w^i_{\ell'}\}$ and $\bigcap_{i<j\le k} e_{i,j}=\{w^i_{\ell'}\}$.
-It follows that $(\bigcap_{1\le j<i} e_{j,i}) \cap (\bigcap_{i<j\le k} e_{i,j})=\{w^i_{\ell'}\}$.
-
-We can conclude that indeed $\bigcup_{e\in X}e$ forms a multicolored clique in $H$.
-
-\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution.
-We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.
-
-We start with the labels for edges from the alignment gadget. 
-\begin{itemize}
-    \item For every $w\in\hat{W}$ we set $\lambda(\{w^\star,w\})=1$.
-    \item Let $\hat{v}_0$ belong to some connector gadget and let $w\in\hat{W}$ be neighbor of $\hat{v}_0$. Then we set $\lambda(\{w,\hat{v}_0\})=n^9$.
-    \item Let $y^i$ belong to the verification gadget of color $i$ and let $w\in\hat{W}$ be neighbor of $y^i$. Then we set $\lambda(\{w,y^i\})=n^8-1$. Furthermore, we set $\lambda(\{y_i,v^i_0\})=n^8$.
-    \item Let $x_1$ belong to the edge selection gadget for color combination $i,j$ and let $w\in\hat{W}$ be neighbor of $x_1$. Then we set $\lambda(\{w,x_1\})=(i+j)(20n+6)$.
-\end{itemize}
-
-Next, consider a connector gadget with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and set $A,B$.
-\begin{itemize}
-    \item We set $\lambda(\{\hat{v}_0,\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3\})=n^9$.
-    \item We set $\lambda(\{\hat{v}_0',\hat{v}_1\})=\lambda(\{\hat{v}_,\hat{v}_3'\})=n^9+2$.
-    \item We set $\lambda(\{\hat{v}_1,\hat{v}_2\})=n^9+1$.
-    \item For all vertices $v\in A\setminus B$ we set $\lambda(\{\hat{v}_1,v\})=n^9$ and $\lambda(\{\hat{v}_2,v\})=n^9+2$.
-    \item For all vertices $v\in B$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9$.
-    \item For all vertices $v\in V^\star\setminus A$ we set $\lambda(\{\hat{v}_1,v\})=\lambda(\{\hat{v}_2,v\})=n^9+2$.
-(Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets).
-\end{itemize}
-
-Recall that the following duration requirements were specified in the construction of the instance.
-It is straightforward to verify that durations requirements we recall in the following are all met, assuming no faster connections are introduced.
-\begin{itemize}
-    \item We have set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we have set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we have set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we have set $d(v,v')=3$.
-\end{itemize}
-For two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$, we have set the following durations.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we have set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we have set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we have set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
- For the alignment gadget the following requirements were specified.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We have set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we have set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We have set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We have set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we have set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. We have set $d(w^\star,\hat{v}_1)=n^9$.
-
-We will make sure that no faster connections are introduced by only using even numbers as labels and labels that are strictly smaller than $n^8-1$.
-Furthermore, we can already see that no vertex except the ones in $\hat{W}$ can reach $w^\star$ and no two vertices $w,w'\in\hat{W}$ can reach each other, as required.
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-To describe the labels, we define a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ as follows.
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$.
-Then, since $X$ is a clique in $H$, we have that $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-We set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$.
-For all $\ell'''\in[m]$ with $1\neq\ell'''\neq\ell$ we set $\sigma_{i,j}(\ell''')=\ell'''$.
-
-Let $x_1, x_2, \ldots, x_m$ belong to the edge selection gadget for color combination $i,j$.
-\begin{itemize}
-    \item For all $\ell'''\in[m]$ we set $\lambda(\{x_{\ell'''},v_{i,j}^{\star}\})=(i+j)\cdot (2n({\ell'''})^2 +18n+6)$.
-\end{itemize}
-Note that using these labels, we obey the following duration constraints.
-\begin{itemize}
-    \item For all $1\le \ell'''<\ell''''\le m$ we have set $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$.
-\end{itemize}
-Furthermore, we set the following labels.
-\begin{itemize}
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{0},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2$, where $u^{\ell'''}_{0}$ belongs to the edge selection gadget for $i,j$.
-    \item For all $\ell'''\in[m]$ and $\ell''''\in[4n]$ we set $\lambda(\{u^{\ell'''}_{\ell''''-1},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+2\ell''''+2$, where $u^{\ell'''}_{\ell''''-1}$ and $u^{\ell'''}_{\ell''''}$ belong to the edge selection gadget for $i,j$.
-    \item  For all $\ell'''\in[m]$ we set $\lambda(\{u^{\ell'''}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell'''))^2 +18n+6)+8n+4$, where $u^{\ell'''}_{4n}$ belongs to the edge selection gadget for $i,j$.
-\end{itemize}
-
-It is straightforward to verify that with these labels we get for all $\ell'''\in[m]$ that $d(x_{\ell'''},v_{i,j}^{\star\star})=8n+5$, as required.
-Furthermore, we get that for all $\ell'''\in[m]$ that $d(v_{i,j}^{\star\star},x_{\ell'''})=\infty$.
-To see this, consider the following.
-Vertex $v_{i,j}^{\star\star}$ is not temporally connected to vertices $x_{\ell'''}$ with $\ell'''\in[m]$ via any of the connector gadgets, since for all connector gadgets where $v_{i,j}^{\star\star}\in A$ we have that all vertices $x_{\ell'''}$ with $\ell'''\in[m]$ are either contained in $B$ or they are not contained in $A$.
-By the construction of the labels of the connector gadgets, it follows that $v_{i,j}^{\star\star}$ cannot reach any vertex $x_{\ell'''}$ with $\ell'''\in[m]$ via the connector gadgets.
-We can observe that in all other connections in the underlying graph from $v_{i,j}^{\star\star}$ to a vertex $x_{\ell'''}$ with $\ell'''\in[m]$ are paths which have non-increasing labels, hence they also do not provide a temporal connection.
-
- Furthermore, we get that for all $1\le \ell'''\le\ell''''\le m$ we get that $d(x_{\ell'''},x_{\ell''''})=2n\cdot (i+j)\cdot((\ell'''')^2-(\ell''')^2)+1$, through a temporal path via $v_{i,j}^\star$.
-By similar observations as in the previous paragraph, we also have that $d(x_{\ell''''},x_{\ell'''})=\infty$.
-
-Finally, consider the validation gadget for color $i$. 
-%For all $j\in[k]\setminus\{i\}$. Assume $j<i$, the case of $j>i$ is analogous. 
-Let $1\le j<i$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{j,i}_\ell\in F_{j,i}$. 
-Recall that we set $\sigma_{j,i}(\ell)=1$ and $\sigma_{j,i}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{j,i}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{\ell'-1},u^{\ell}_{\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+2$, where $u^{\ell}_{\ell'-1}$ and $u^{\ell}_{\ell'}$ belong to the edge selection gadget for $j,i$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-10n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+10n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+10n-2\ell''+4$.
-\end{itemize}
-For all $\ell''\in[13n]$ we set the following.
-\begin{itemize}
-    \item $\lambda(\{\hat{u}^i_{\ell''},\hat{u}^i_{\ell''+1}\})=2i\cdot (20n+6)+2\ell'-10n+2\ell''-2$.
-    \item $\lambda(\{v^i_{i-1},\hat{u}^i_{1}\})=2i\cdot (20n+6)+2\ell'-10n-2$.
-    \item $\lambda(\{v^i_i,\hat{u}^i_{13n+1}\})=2i\cdot (20n+6)+2\ell'+16n+4$.
-\end{itemize}
-Let $i<j\le k$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$. 
-Recall that we set $\sigma_{i,j}(\ell)=1$ and $\sigma_{i,j}(1)=\ell$. For all $\ell''\in[m]$ with $1\neq\ell''\neq\ell$ we set $\sigma_{i,j}(\ell'')=\ell''$.
-Recall that we set $\lambda(\{u^{\ell}_{3n+\ell'-1},u^{\ell}_{3n+\ell'}\})=(i+j)\cdot (20n+6)+2\ell'+6n+2$, where $u^{\ell}_{3n+\ell'-1}$ and $u^{\ell}_{3n+\ell'}$ belong to the edge selection gadget for $i,j$.
-Now we set for all $\ell''\in[5n-1]$ and all $\ell'''\in[m]$ the following.
-\begin{itemize}
-    \item $\lambda(\{a^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{a^{i,j,\ell'''}_{1},v^i_{j-1}\})=(i+j)\cdot (20n+6)+2\ell'-4n-2$.
-    \item $\lambda(\{a^{i,j,\ell'''}_{\ell''},a^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'-4n+2\ell''$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{5n},u^{\ell'''}_{\ell''''}\})=(i+j)\cdot (20n+6)+2\ell'+6n+4$ for all $\ell''''$ such that this edge exists.
-    \item $\lambda(\{b^{i,j,\ell'''}_{1},v^i_{j}\})=(i+j)\cdot (20n+6)+2\ell'+16n+6$.
-    \item $\lambda(\{b^{i,j,\ell'''}_{\ell''},b^{i,j,\ell'''}_{\ell''+1}\})=(i+j)\cdot (20n+6)+2\ell'+16n-2\ell''+4$.
-\end{itemize}
-
-Now we verify that we meet the duration requirements.
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-To see that this holds, we analyse the fastest paths from vertices $v^i_{j-1}$ to vertices $v^i_j$ for $j\in[k]\setminus\{i\}$. 
-Let $\{w^i_{\ell'}\}=X\cap W_i$ and $\{w^j_{\ell''}\}=X\cap W_j$ and $\{w^i_{\ell'},w^j_{\ell''}\}=e^{i,j}_\ell\in F_{i,j}$.
-Then, starting at $v^i_{j-1}$, we follow the vertices in $\{a^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $u^{\ell}_{\ell'-1}$.
-From there we move to $u^{\ell}_{\ell'}$ and from there we continue along the vertices in $\{b^{i,j,\ell}_{\ell''} :  \ell''\in[5n]\}$ to arrive at $v^i_j$.
-By construction this describes a fastest temporal path from $v^i_{j-1}$ to $v_j$ with duration $20n+5$.
-To get from $v^i_j$ to $v^i_{j'}$ for $0\le j<j'<i$ we move from $v^i_j$ to $v^i_{j+1}$ in the above described fashion and from there to $v^i_{j+1}$ and so on until we arrive at $v^i_{j'}$.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)-1$, as required.
-The case where $i\le j<j'\le k$ is analogous.
-
-For all $0\le j<i$ and all $i\le j'\le k$ we have set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-Here we move from $v^i_j$ to $v^i_{i-1}$ in the above described fashion.
-Then we move from $v^i_{i-1}$ to $v^i_i$ along vertices $\{\hat{u}^i_{\ell''} :  \ell''\in[13+1]\}$ and then we move from $v^i_i$ to $v^i_{j'}$ again in the above described fashion.
-By construction this yields a fastest temporal path from $v^i_j$ to $v^i_{j'}$ with duration $(20n+6)(j'-j)+6n-1$, as required.
-
-By similar observations as in the analysis for the edge selection gadgets, we also get that for all $1\le j<j'\le k$ that $d(v^i_{j'},v^i_j)=\infty$.
-
-This finishes the proof.
-
-\subparagraph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-\end{proof}
-
-\section{Algorithms for \deltaExact}\label{sec:algos}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-
-We first show in \cref{sec:treealgo} that in the case when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, then we can determine desired $\Delta$-periodic labeling $\lambda$ of $G$ in polynomial time.
-In \cref{sec:FPT} we generalize this result.
-We show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-Finally, in \cref{sec:cyclealgo} we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-We first start with defining certain notions, that will be of use when solving the problem.
-
-    \begin{definition}[Travel delays]
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-    More specifically:
-    \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-    \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-    \end{definition}
-    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-    From the above definition and the definition of the duration of the temporal path $P$ we get the following two observations.
-    \begin{observation}\label{obs:durationPwithWaitingTimes}
-        Let $P = (v_0, v_1, \dots, v_p)$ be the underlying path of the temporal path
-        $(P, \lambda)$ from $v_0$ to $v_p$.
-        Then $d(P,\lambda) = \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1 $.
-    \end{observation}
-    \begin{proof}
-        For the simplicity of the proof denote $t_i = \lambda(v_{i-1}v_i)$, and suppose that $t_i \leq t_{i+1}$, for all $i \in \{1,2,3,\dots,p\}$.
-        Then
-        \begin{align*}
-        \sum_{i = 1}^{p-1} \tau_{v_i}^{v_{i-1}v_i} + 1  
-        &= \sum _{i = 1}^{p-1} (t_{i+1} - t_i) + 1 \\
-        & = (t_2 - t_1) + (t_3  t_2) + \cdots + (t_p - t_{p-1}) + 1  \\
-        & = t_{p-1} - t_1 + 1\\
-        & = d(P)
-        \end{align*}
-        Now in the case when $t_i > t_{i+1}$ we get that $\tau_{v_i}^{v_{i-1}v_{i+1}} = \Delta + t_{i+1} - t_i$.
-        At the end this still results in the correct duration as the last time we traverse the path $P$ is not exactly $t_p$ but $k \lambda + t_p$, for some $k$.
-    \end{proof}
-    We also get the following.
-    \begin{observation}\label{obs:travel-delays-both-directions}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact.
-    For any two incident edges $e_1 = uv$ and $e_2 = vz$ on vertices $u,v,z \in V$, with $e_1 \cap e_2 = v$, we have $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{observation}
-
-    \begin{proof}
-        Let $e_1 = uv$ and $e_2 = vz$ be two edges in $G$ for which $e_1 \cap e_2 = v$. 
-        By the definition $\tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta$ and $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-        Summing now both equations we get $\tau_v^{uz} + \tau_v^{zu} \equiv \lambda(e_2) - \lambda(e_1) + \lambda (e_1) - \lambda(e_2) \pmod \Delta$, and therefore $\tau_v^{uz} + \tau_v^{zu} \equiv 0 \pmod \Delta$, which is equivalent as saying $\tau_v^{uz} \equiv - \tau_v^{zu} \pmod \Delta$ or $\tau_v^{zu} = \Delta - \tau_v^{uz} \pmod \Delta$.
-    \end{proof}
-
-\begin{lemma} \label{lemma:unique-fastest-path-allDelays}
-    Let $(G, \lambda)$ be a temporal graph satisfying conditions of problem \deltaExact,
-    and let $(P,\lambda)=(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-    Suppose that for any $v_i$ in $P$ it follows that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-    Then we can determine travel delays on vertices of $P$ using the following equation
-    \begin{equation}\label{eq:trav-delays-paths}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-    \end{equation}
-    for all $i \in \{2,3, \dots, k-1\}$.
-\end{lemma}
-
-\begin{proof}
-    Let $(P,\lambda)$ be a fastest temporal path from $v_1$ to $v_k$ with the properties from the claim, and let $v_i$ be an arbitrary vertex in $P \setminus \{v_1,v_k\}$.
-    Using the properties of fastest paths and the definition of duration, we can rewrite \cref{eq:trav-delays-paths} as follows
-    \begin{align*}
-        \tau_{v_i}^{v_{i-1},v_{i+1}} & = D_{1,i+1} - D_{1,i} =  d(P_{1,i+1}) - d(P_{1,i}) \\
-        & \equiv 
-        \left(\lambda(v_{i}v_{i+1}) - \lambda(v_1v_2) + 1\right) -  
-        \left(\lambda(v_{i-1}v_{i}) - \lambda(v_1v_2) + 1\right) \pmod \Delta \\
-        & \equiv \lambda(v_{i}v_{i+1}) - \lambda(v_{i-1}v_{i}) \pmod \Delta,
-        \end{align*}
-    which is exactly the definition of $\tau_{v_i}^{v_{i-1},v_{i+1}}$.
-\end{proof}
-
-\subsection{Polynomial-time algorithm for trees}\label{sec:treealgo}
-%All of the above is used in the design of the following polynomial-time algorithms.
-We are now ready to provide a polynomial-time algorithm for \deltaExact\ when the underlying graph is a tree.
-Let $D$ be a matrix from \deltaExact\ and let the underlying graph $G$ of $D$ be a tree on $n$ vertices $\{v_1, v_2, \dots, v_n\}$.
-Let $v_i,v_j$ be two arbitrary vertices in $G$. Then we know that there exists a unique (static) path $P$ among them.
-Consequently, it follows that the temporal paths $(P_{i,j},\lambda)$ from $v_i$ to $v_j$ and $(P_{j,i},\lambda)$ from $v_j$ to $v_i$ are also unique, up to modulo of the period $\Delta$ of the labeling $\lambda$,
-and therefore are the fastest.
-Then $D$ is of the following form:
-\begin{equation*}
-    D_{i,j} =
-    \begin{cases}
-    0 & \text{if $i = j$}, \\
-    1 & \text{if $v_i$ and $v_j$ are neighbours in G}\\
-    d(P_{i,j},\lambda) & \text{else}
-    \end{cases},
-\end{equation*}
-where $d(P_{i,j},\lambda)$ is the duration of the (unique) temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$.
-
-\begin{observation}\label{obs:travel-delays-in-trees}
-    Let $v_i,v_j$  be arbitrary two vertices in a tree $G$. 
-    Since there is a unique temporal path $(P_{i,j},\lambda)$ from $v_i$ to $v_j$, it is also the fastest one, therefore $d(P_{i,j},\lambda) = D_{i,j}$. 
-    Note, all other vertices $v' \in P_{i,j} \setminus \{v_i,v_j\}$ are reached form $v_i$ using a part of the path $(P_{i,j},\lambda)$.
-    Now using \cref{lemma:unique-fastest-path-allDelays}, we can determine the waiting times for all \emph{inner} vertices of the path $P_{i,j}$.
-\end{observation}
-
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial time on trees.
-\end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check if it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-
-    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-    We now take the unique path $P_{i,j}$ in $G$, 
-    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-    When we have exhausted the $i$-th row of $D$,
-    \ie vertex $v_i$ now reaches every vertex of $G$,
-    we continue and repeat the procedure for all other vertices.
-    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-    \begin{claim}\label{lemma:matrixT-travelDelays-tree}
-        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-    \end{claim}
-    \begin{claimproof}
-        Note, by the definition of travel delays, a vertex of degree $1$ cannot have a travel delay.
-        Suppose now that there is a vertex $v_i \in V(G)$ of degree at least $2$, for which our algorithm did not calculate its travel delay.
-        Let $v_a, v_b$ be two arbitrary neighbors of $v_i$, \ie $v_a v_i, v_i v_b \in E(G)$.
-        Since $G$ is a tree, the unique (and fastest) temporal path from $v_a$ to $v_b$ passes through $v_i$.
-        When our algorithm was inspecting the row of $D$ corresponding to vertex $v_a$, it had to consider the temporal path from $v_a$ to $v_b$. 
-        At this point, it calculated $\tau_{v_i}^{v_a,v_b}$. 
-        Since this is true for any two $v_a, v_b \in N(v_i)$, it cannot happen that some travel delay at $v_i$ is not calculated.
-        Since $v_i$ was an arbitrary vertex in $G$ of degree at least $2$, the claim holds.
-    \end{claimproof}
-
-    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
-
-\subsection{FPT-algorithm for feedback edge number}\label{sec:FPT}
-
-In this section we show how to generalize the result presented in \cref{sec:treealgo}.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.
-
-\begin{theorem}\label{thm:FPTwrtFES}
-    \deltaExactLong\ is in FPT when parameterized by the feedback edge number of the underlying graph.
-\end{theorem}
-
-We first give an informal and very high-level description of the main ideas of the algorithm.
-It is well-known that the number of paths between two vertices in a static graph can be upper-bounded by a function of the feedback edge number of the graph.
-Intuitively, this would allow us to ``guess'' paths between a small number of vertex pairs in $G$ (the underlying graph of our instance \deltaExact).
-These paths would then be used to create (representatives of) fastest temporal paths among vertex pairs in $(G,\lambda)$.
-We would then try to use the polynomial algorithm for trees (which includes paths) to figure out the labeling $\lambda$ of the edges used by these path.
-An idea like this has been used for several other temporal graph problems related to the connectivity between two vertices~\cite{casteigts2021finding,FMNR22a,EMM22}.
-
-In our case, however, it is not enough to consider fastest temporal paths among some subset of vertices, but we have to determine the fastest temporal paths between all pairs of vertices.
-This means that we have to somehow extend the labeling $\lambda$ of the edges used by guessed paths to all other edges of $G$.
-Besides that we also need to make sure that all temporal paths that do not follow our guessed paths are not too fast.
-
-	A further difficulty arises from the somewhat unintuitive characteristic of fastest paths in temporal graphs.
- When considering the problem of finding shortest paths among vertices in static graphs, we have the nice property that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
-	then the subpath of $P$ from $u$ to $w$ is a shortest path from $u$ to $w$. This can help tremendously when developing algorithms.
-	However, one can see that this property does not carry over to fastest paths in temporal graphs, for an example see~\cref{fig:ftpExample}.
- For us this means that even if we guess a fastest path between two vertices, we cannot simply determine all labels of the edges used by the fastest path.
-	%This makes all the standard intuition and work with these kind of paths, much harder.
-    %This also explains why our FPT algorithm, w.r.t the feedback edge number, is so complex. 
-    %Usually, the feedback edge number parameter (denote it $k$) provides an easy algorithm, 
-    %where one first determines $O(k)$ special vertices,
-    %guesses desired structures among them (\ie iterates through all possibilities) and then simply extends the solution to the rest of the graph.
-    %An example with this approach, on temporal graphs, can be observed in \cite{casteigts2021finding} where the authors provide an FPT algorithm that determines all temporal paths, under certain constraints.
-    %In our case the similar approach cannot work, as we cannot at any point calculate some partial labeling $\lambda$ of a delta periodic graph $(G,\lambda)$,
-    %that could at the end be extended to the whole $G$.
-
-	\begin{figure}[t]
-    \centering
-	\begin{tikzpicture}[xscale=2]
-	%%%S_uv
-	\node[vert,label=below:$u$] (v1) at (1,0) {};
-	\node[vert] (v2) at (2,0) {};
-	\node[vert,label=below:$w$] (v3) at (3,0) {};
-	\node[vert] (v4) at (4,0) {};
-	\node[vert,label=below:$v$] (v5) at (5,0) {};
-	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
-	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);
-
-	\draw[transform canvas={yshift=-1.5mm}, blue]
-	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;
-
-	\draw[red]
-	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
-\end{tikzpicture}
-	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
-		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
-		\label{fig:ftpExample}}
-	\end{figure}
-
-To overcome the above mentioned difficulties, we propose the following high-level strategy.
-\begin{itemize}
-    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
-    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
-    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
-    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
-    \item We compute a solution to the ILP and construct a labeling from that solution.
-Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
-\end{itemize}
-
-For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
-the matrix of the fastest temporal paths among $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
-With $F$ we denote a minimum feedback edge set of $G$, and with $k$ the feedback edge number of $G$.
-We are now ready to present our FPT algorithm. For an easier readability we split the description and analysis of the algorithm in five subsections.
-We start with a preprocessing procedure for graph $G$, where we define a set of interesting vertices which then allows us to guess the desired structures.
-Next we introduce some extra properties of our problem, that we then use to create ILP instances and their constraints.
-At the end we present how to solve all instances and produce the desired labeling $\lambda$ of $G$, if possible.
-
-\begin{comment}
-
-\todo[inline]{HM: not sure if the discussion below is necessary.
-i think guessing is a pretty established term in algorithm design.
-also, i think the name comes from the idea of using non-determinism.}
-Throughout the proof, whenever we say \emph{guess} the path/subpath/vertex, etc., we mean that we enumerate all possibilities, and assume we are in a branch of the algorithm where we consider one that leads to a solution (if one exists).
-For example, let $u$ and $v$ be two vertices in a graph $G$. 
-We say that we \emph{guess} that $P$ is the underlying path of a fastest temporal path $(P, \lambda)$ from $u$ to $v$ in $(G, \lambda)$.
-This means that we iterate over all possible possible $u,v$-paths $P_1, P_2, \dots $ in $G$, 
-and form multiple cases, 
-one in which $(P_1, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$,
-one when $(P_2, \lambda)$ is a fastest temporal path from $u$ to $v$ in $(G,\lambda)$, etc.
-To correctly determine if the problem has a valid solution, we must check all cases.
-In each case we perform required calculations, 
-and we either come to the contradiction (meaning that the current guess was wrong) 
-or our assumption holds (meaning that the guessed path is really a fastest path from $u$ to $v$ in $(G, \lambda)$).
-
-%%%%% HM: the two sentences below seem trivial to me.
-%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
-%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
-We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
-We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
-If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
-Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
-If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
-Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
-Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
-\end{comment}
-%
-
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
-iteratively removing vertices of degree one from $G$,
-and denote with 
-\[
-Z = V(G) \setminus V(G').
-\]
-Then we determine a minimum feedback edge set $F$ of $G'$.
-%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
-Note that $F$ is also a minimum feedback edge set of $G$.
-Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
-Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
-Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
-and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
-Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
-and $|V_3| \leq |V_1|$ by the properties of trees.
-We denote with 
-\[U = V_1 \cup V_2 \cup V_3\]
-the set of vertices of interest. It follows that $|U| \leq 4k$.
-We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
-\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
-Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, therefore $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
-Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
-
-%Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
-%, and no other temporal path from $v_i$ to $v_j$ is faster.
-In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
-where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
-and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
-which results in one equality constraint for the labels on the path $P$. 
-For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $poly(n,m)$ constraints. 
-Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
-%We have to guarantee only that the number of guesses of fastest temporal paths is exponential in $k$ and not in $n$.
-
-For an easier understanding and the analysis of the algorithm we give the following definition.
-\begin{definition}
-    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
-    Note $S_{u,v} \neq S_{v,u}$.
-\end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
-\begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
-\end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
-%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
-
-\subsubsection{Guessing necessary structures \label{sec:FPT-guessing}}
-Once the sets $U, U^*$ and $Z^*$ are determined, we are ready to start guessing  the necessary structures.
-Note that whenever we say that we guess the fastest temporal path between two vertices, we mean that we guess the underlying path of a representative fastest temporal path between those two vertices.
-In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
-Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique fastest path) among two vertices, we denote it by $\rightarrow$,
-if the fastest path among two vertices is not uniquely determined, we denote it by $\leadsto$.
-We guess the following structures.
-\begin{enumerate}[G-1.]
-    \item \label{FPT-guessFTPamongU}
-    The fastest temporal paths among all pairs of vertices of $U$.
-    For a pair $u,v$ of vertices in $U$, there are $k!$ possible paths in $G'$ between them. 
-    Therefore, we have to try all $O(k^k)$ possible paths, where at least one of them will be a fastest temporal path from $u$ to $v$, respecting the values from $D$.
-    %If this does not happen we conclude that $D$ is a \textsc{No} instance of \deltaExact.
-    Repeating this procedure for all pairs of vertices $u,v \in U$ we get $O((k^k)^{k^2})=O(k^{k^3})$ different variations of the fastest temporal paths among all vertices in $U$.
-    \item \label{FPT-guessFTPamongZstar}
-    The fastest temporal paths among all vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstar}
-    The fastest temporal paths among all vertices in $U^*$.
-    This gives us $O(k^{k^6})$ guesses.
-    \item \label{FPT-guessFTPamongUandUstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $U^*$,
-    and vice versa, the fastest temporal paths from vertices in $U^*$ to vertices in $U$.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongUandZstar}
-    The fastest temporal paths from vertices of $U$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^3})$ guesses.
-    \item \label{FPT-guessFTPamongUstarandZstar}
-    The fastest temporal paths from vertices of $U^*$ to vertices in $Z^*$,
-    and vice versa.
-    This gives us $O(k^{k^4})$ guesses.
-    \item \label{FPT-guessFTPamongv2z2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments,
-    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
-    We want to guess the following fastest temporal path
-    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 
-    We repeat this procedure for all pairs of segments.
-    Since there are $O(k^2)$ segments in $G'$,
-    there are $O(k^{k^5})$ possible paths of this form. \\
-    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$.
-Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint.
-Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths:
-    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
-    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
-    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
-    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.
-    %
-    For an example see~\cref{fig:FPT-guessG4}.
-    \item \label{FPT:guess-uToSegmentz2}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
-    and let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest.
-    We want to
-    guess the following fastest temporal paths
-    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_2$,
-    and
-    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v_3 \rightarrow \cdots v \leadsto w$.
-    \\
-    For a fixed segment $S_{u,v}$ and a fixed vertex $w \in U \cup Z^*$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
-    %
-    For an example see~\cref{fig:FPT-guessG5}.
-    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
-    \item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
-    Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
-    fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    In the case when $S_{u,v}$ is of length $4$, the fixed vertex $v_i$ is the middle vertex (\ie vertex that is on distance two from $u$ and $v$ in $S_{u,v}$).
-    If $S_{u,v}$ is not of length~$4$, we fix an arbitrary vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
-    Let 
-    $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be another segment in $G'$.
-    Note that all inner vertices of $S_{w,z}$ (\ie vertices in $S_{w,z} \setminus \{w,z\}$)
-    can be reached from $v_i$ by some path that has to go through $w$ or $z$.
-    Therefore, the values of the duration of the fastest path from $v_i$ to vertices on 
-    the segment
-    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
-    We split the analysis into two cases.
-    \begin{enumerate}
-        \item 
-    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
-    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 
-    $D_{v_i,z_{r-1}} < D_{v_i,z_{r-2}} < \dots < D_{v_i,z_j}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j-1}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    We now want to guess which vertex $w$ or $z$ is on a fastest temporal path from $v_i$ to $z_j$.
-    Similarly,
-    all fastest temporal paths starting at $v_i$ have to go either through $u$ or through $v$,
-    which also gives us two extra guesses for the fastest temporal path from $v_i$ to $z_j$.
-    Therefore, all together we have $4$ possibilities on how the fastest temporal path from $v_i$ to $z_j$ starts and ends.
-    Besides that we want to guess also how the fastest temporal paths from $v_i$ to $z_{j-1}, z_{j+1}$ start and end.
-    Note that one of these is the subpath of the fastest temporal path from $v_i$ to $z_j$, and the ending part is uniquely determined for both of them,
-    \ie to reach $z_{j-1}$ the fastest temporal path travels through $w$, and to reach $z_{j+1}$ the fastest temporal path travels through $z$.
-    Therefore we have to determine only how the path starts, namely if it travels through $u$ or $v$.
-    This introduces two extra guesses.
-    For a fixed $S_{u,v}, v_i$ and $S_{w,z}$ we find the vertex $z_j$ in polynomial time, 
-    or determine that $z_j$ does not exist.
-    We then make four guesses where we determine how the fastest temporal path from $v_i$ to $z_j$ passes through vertices $u,v$ and $w,z$ and 
-    for each of them two extra guesses to determine the fastest temporal path from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$.
-    We repeat this procedure for all pairs of segments,
-    which results in producing $O(k^{k^6})$ new guesses.
-    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
-    \item 
-    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
-    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
-    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{r-1}}$.
-    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
-    and 
-    the fastest temporal paths from $v_i$ to $z_{r-1}, z_{r-2}, \dots, z_{j+1}$ go through $z$.
-    In this case we only need to guess the following two fastest temporal paths 
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$.
-    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-    Note that in this case we do not introduce any new guesses, as we have aready guessed 
-    the fastest paths of form
-    $u \leadsto w \rightarrow z_2$
-    and $u \leadsto z \rightarrow z_{r-1}$
-    (see guess~G-\ref{FPT:guess-uToSegmentz2}).
-    \end{enumerate}
-    Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-    \ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-    %
-    For an example see~\cref{fig:FPT-guessG6}.
-    \item \label{FPT:guess-splitFromUtoAnotherSegment}
-    Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
-    Similarly as above, in guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-    We again have two cases,
-    first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-    and the
-    second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $O(k^{k^2})$ new guesses.
-    %
-    For an example see~\cref{fig:FPT-guessG7}.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-%
-\begin{figure}[t]
-    \centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-		\begin{tikzpicture}
-			%%%S_uv
-			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-			\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-			%%%% S_wz
-			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-			\draw (z1) -- (z2) -- (zr1) -- (zr);
-
-			\draw [violet] (v2) edge[diredge2] (v1);
-
-			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-			(v1) edge[dirwave] [out=250,in=120] (z1) 
-			(z1) edge[diredge2] (z2);
-
-			\draw [red] %[transform canvas={yshift=-0.5mm}] 
-			(v1) edge[dirwave] [out=300,in=90] (zr) 
-			(zr) edge[diredge2] (zr1);
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-	\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
-
-			\begin{tikzpicture}
-				%%%S_uv
-				\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-				\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-				\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-				\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-				\draw (v1) -- (v2) -- (vp1) -- (vp);
-
-				%%%% node w
-				\node[vert,label=below:$w$] (w) at (4,-3) {};
-
-				\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=160,in=285] (v1) 
-				(v1) edge[diredge2] (v2);
-
-				\draw [red]%[transform canvas={yshift=0.5mm},thick] 
-				(w) edge[dirwave] [out=20,in=255] (vp) 
-				(vp) edge[diredge2] (vp1);
-
-			\end{tikzpicture}}
-		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-			\centering
-			\resizebox{1.2\linewidth}{!}{
-				%
-				\begin{tikzpicture}[scale=1]
-					%%%S_uv
-					\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-					\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-					\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-					\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-					\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-					\draw (v1) -- (v2) -- (vi) -- (vp1) -- (vp);
-
-					%%%% S_wz
-					\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
-					\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
-					\node[vert,label=below:$z_{j-1}$] (zj-1) at (3.2,-3) {};
-					\node[vert,label=below:$z_{j}$] (zj) at (4,-3) {};
-					\node[vert,label=below:$z_{j+1}$] (zj+1) at (4.8,-3) {};
-					\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
-					\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
-					\draw (z1) -- (z2) -- (zj-1) -- (zj) -- (zj+1) -- (zr1) -- (zr);
-
-					\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
-					(vi) -- (v2) edge[diredge2] (v1) 
-					(v1) edge[dirwave] [out=40,in=55,distance=5.2cm] (zr) 
-					(zr) --(zr1) -- (zj+1)
-					(zj+1) edge[diredge2] (zj);
-
-					\draw [red]
-					(vi) -- (vp1) edge[diredge2] (vp) 
-					(vp) edge[dirwave] [out=250,in=60] (z1) 
-					(z1) --(z2)
-					(z2) edge[diredge2] (zj-1);
-
-			\end{tikzpicture}}
-			\caption{Example of a guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}, where, for fixed a vertex $v_i \in S_{u,v}$,
-				we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-				and guessed the fastest paths of form
-				$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-				and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-				\label{fig:FPT-guessG6}}
-		\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{\linewidth}{!}{
 	\begin{tikzpicture}
@@
 
-		\end{tikzpicture}}
-	\caption{Example of a guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}, where, for a vertex of interest $w$, 
-		we
-		calculated its corresponding split vertex $v_i \in S_{u,v}$,
-		and guessed the fastest paths of form
-		$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-		and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-		\label{fig:FPT-guessG7}}
-	\end{subfigure}
-\caption{An example of guesses G-\ref{FPT-guessFTPamongv2z2}, G-\ref{FPT:guess-uToSegmentz2}, G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths} and G-\ref{FPT:guess-splitFromUtoAnotherSegment}.}
-\end{figure}
-%
-We create all of the guesses independently.
-We start with the first one, that results in $O(k^{k^3})$ different possibilities, then we split each one of these guesses into $O(k^{k^3})$ new ones, that respond to the guessing in the second step, etc.
-After creating all of the guesses we end up with $f(k)$ different cases (where $f$ is a double exponential).
-We now create one ILP instance for each case.
-From now on we assume that we know exactly the structure of all paths we have guessed.
-
-\subsubsection{Properties of \deltaExact}
-
-In this section we study the properties of our problem, that then help us creating constraints of our ILP instances.
-Recall that with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
-We start with an empty labeling of edges and try to specify each one of them.
-Note, that this does not necessarily mean that we assign numbers to the labels, but we might specify labels as variables or functions of other labels.
-We say that the label of an edge $f$ is \emph{determined with respect to} the label of the edge edge $e$, if we have determined $\lambda(f)$ as a function of $\lambda(e)$.
-
-In our analysis we exploit the following greatly, that is why we state is as an observation.
-
-\begin{observation}\label{obs:FirstLabelAndDuration}
-    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
-    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
-\end{observation}
-The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}.
-This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
-where the label of last edge is considered with some delta periods,
-\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
-Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
-Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.
-
-In the following we prove that knowing the structure (the underlying path) of a fastest temporal path $P$ from a vertex of interest $u$ to a vertex of interest $v$,
-results in determining the labeling of each edge in the fastest temporal path from $u$ to $v$ 
-(with the exception of some constant number of edges), with respect to the label of the first edge.
-More precisely, if path $P$ from $u$ to $v$ is a segment, then we can determine labels of all edges as a function of the label of the first edge.
-If $P$ consists of $\ell$ segments, then we can determine the labels of all but $\ell -1$ edges as a function of the label of the first edge.
-For the exact formulation and proofs see \cref{lemma:FPT-uv-Labelalledges,lemma:FPT-uv-LabelAlmostalledges}.
-
-\begin{lemma}\label{lemma:FPT-uv-Labelalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1,v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Moreover suppose also that $P$ is a segment.
-    %Suppose also that no other vertex from $P$ is a vertex of interest, \ie $P \setminus \{u,v\} \cap U = \emptyset$.
-    We can determine the labeling $\lambda$ of every edge in $P$ with respect to the label $\lambda(uv_2)$ of the first edge.
-    %such that the labeling $\lambda$ respects $D'$.
-\end{lemma}
-
-\begin{proof}
-We claim that $u$ reaches all of the vertices in $P$ the fastest, when traveling along $P$ (\ie by using a subpath of $P$).
-To prove this suppose for the contradiction that there is a vertex $v_i \in P \setminus \{u,v\}$, that is reached from $v$ on a path different than $P_i = (u, v_2, v_3, \dots, v_i)$ faster than through $P_i$.
-Since the only vertices of interest of $P$ are $u$ and $v$, it follows that all other vertices on $P$ are of degree $2$. 
-Then the only way to reach $v_i$ from $u$, that differs from $P$, would be to go from $u$ to $v$ using a different path $P_2$,
-and then go from $v$ to $v_{p-1}, v_{p-2}, \dots, v_i$.
-But since $P$ is the fastest temporal path from $u$ to $v$, we get that $d(P_2) \geq d(P)$ and $d(P_2 \cup (v,v_{p-1}, \dots, v_i)) > d(P) > d(P_i)$.
-
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-uv-LabelAlmostalledges}
-    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
-    is a path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
-    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = |\{P \setminus \{u,v \} \} \cap U |$.
-    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
-    such that the labeling $\lambda$ respects the values from $D$.
-%    Moreover, for the labels of edges that cannot be determined precisely, we introduce some extra restrictions.
-\end{lemma}
-
-For the proof of the above lemma, we first prove a weaker statement,
-for which we need to introduce some extra definitions and fix some notations.
-%
-In the following
-we only consider \emph{wasteless} temporal paths. 
-We call 
-a temporal path $P=((e_{1},t_{1}),\ldots ,(e_{k},t_{k}))$ a \emph{wasteless} temporal path, 
-if for every $i=1,2,\ldots ,k-1$, we have that $t_{i+1}$ is the first time after $t_{i}$ that the edge $e_{i+1}$ appears.
-
-Let $u,v\in V$, and let $t\in \mathbb{N}$. 
-Given that a temporal path starts within the period $[t,t+\Delta -1]$,
-we denote with $A_{t}(u,v)$
-the \emph{arrival} of the fastest path in $(G,\lambda )$ from $u$ to $v$, and
-with $A_{t}(u,v,P)$,
-the \emph{arrival} along path $P$ in $(G,\lambda )$ from $u$ to $v$.
-%
-Whenever $t=1$, we may omit the index $t$, i.e. we may write 
-$A(u,v,P)=A_{1}(u,v,P)$ and $A(u,v)=A_{1}(u,v)$.
-
-Suppose now that 
-we know the underlying path $P_{u,v} = (u=v_1, v_2, \dots, v_p = v)$ of the fastest temporal path among vertices of interest $u$ and $v$ in $G'$.
-Let $v_i\in U$ with $u\neq v_i \neq v$ be a vertex of interest on the path $P_{u,v}$.
-Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
-(for details see~\cref{fig:FPT-uv-Labelalledges}).
-
-From the above we get the following assumptions:
-	\begin{enumerate}
-		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
-		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
-	\end{enumerate}
-In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
-%%%%%% HM: the following is never used..
-%It follows that:
-%	\begin{itemize}
-%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
-%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
-%		u$ to $v$.
-%	\end{itemize}
-%
- Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
-	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
-	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
-    From Assumption~\ref{assumption1-FPT} we get
-	\begin{equation*}
-		\delta
-		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
-	\end{equation*}%
-	and thus%
-	\begin{equation}
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
-		\label{basic-eq-1}
-	\end{equation}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=.85]
-		%%%S_uv
-		\node[vert,label=below:$u{=} v_1$] (v1) at (1,0) {};
-		\node[vert, label=below:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=below:$v_3$] (v3) at (3,0) {};
-		\node[vert,label=below:$v_{i-1}$] (vi-1) at (6,0) {};
-		\node[vert,label=below:$v_i$] (vi) at (7,0) {};
-		\node[vert,label=below:$v_{i+1}$] (vi+1) at (8,0) {};
-		\node[vert,label=below:$v_{p} {=} v$] (v) at (10,0) {};
-
-		\draw (v1) -- node[label={above:$t_{v_2}$},yshift=-5] {} (v2) -- (v3) -- (vi-1) -- node[label={above:$e$},yshift=-5] {} (vi) -- node[label={above:$f$},yshift=-5] {} (vi+1) -- (v);
-
-		\draw (v1) to [out=80,in=100,distance=3cm]
-		node[pos=0.1,label={left:$t_{u_2}$}] {}
-		node[vert,pos=0.15,label=above:$u_2$] {}
-		node[vert,pos=0.3,label=above:$u_3$] {}
-		node[vert,pos=0.85,label=above:$u_{j-1}$] {}
-		node[pos=0.9,label={right:$g$}] {} (vi);
-
-		%\draw[transform canvas={yshift=0mm}, blue]
-		%(v1) -- (v2) -- (v3) -- node[pos=0.3,yshift=-2,label=above:$P_{u,v}$] {} (vi-1) -- (vi) ;
-
-		%\draw[red]
-		%(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
 	\end{tikzpicture}
-	\caption{An example of the situation in \cref{lemma:FPT-uv-LabelAlmostalledges},
-		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
-		\label{fig:FPT-uv-Labelalledges}}
-\end{figure}
-
-We use all of the above discussion, to prove the following lemma.
- 	\begin{lemma}
-		\label{lem-1}If $t_{u_{2}}\neq t_{v_2}$, then $\delta _{0}\leq \Delta -2$
-		and $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{lemma}
-
-	\begin{proof}
-		First assume that $\delta _{0}\geq \Delta -1$. Then, it follows by \cref%
-		{basic-eq-1} that $%
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq
-		t_{u_{2}}-t_{v_2}-\Delta +1\leq 0$, and thus $A_{t_{v_2}}(u,v_{i},P)%
-		\leq A_{t_{v_2}}(u,v_{i},Q)$. Therefore, since we can traverse path $P$
-		from $u$ to $v_{i}$ by departing at time $t_{u_{2}}\geq t_{v_2}+1$ and
-		by arriving no later than traversing path $Q$, we have that $d(u,v_p,P\cup Q)<d(u,v_p,Q\cup R)$, which is a contradiction to the
-		second initial assumption. Therefore $\delta _{0}\leq \Delta -2$.
-
-		Now assume that $t_{v_2}+1\leq t_{u_{2}}\leq t_{v_2}+\delta _{0}$. Then,
-		it follows by \cref{basic-eq-1} that $A_{t_{v_2}}(u,v_{i},P)\leq
-		A_{t_{v_2}}(u,v_{i},Q)$ which is, similarly to the previous case, a
-		contradiction. Therefore $t_{u_{2}}\geq t_{v_2}+\delta _{0}+1$.
-	\end{proof}
-
- The next corollary follows immediately from \cref{lem-1}.
-
-	\begin{corollary}
-		\label{cor-1}If $t_{u_{2}}\neq t_{v_2}$, then $1\leq
-		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)\leq \Delta
-		-1-\delta _{0}$.
-	\end{corollary}
-
-We are now ready to prove the following result.
-
-	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
-		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
-		\{v_{i}v_{i-1}\})$.
-	\end{lemma}
-	\begin{proof}
-		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
-		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
-
-		\emph{Case 1: }$t_{u_{2}}\neq t_{v_2}$. Then \cref{cor-1}
-		implies that $e+1\leq g\leq e+(\Delta -1-\delta _{0})$. Assume that $g<f$.
-		Then, we can traverse path $P$ from $u$ to $v_{i}$ by departing at time $%
-		t_{u_{2}}\geq t_{v_2}+1$ and by arriving at most at time $x\Delta +f-1$,
-		and thus $d(u,v_p,P\cup R)<d(u,v_p,Q\cup R)$, which is a
-		contradiction to the second initial assumption. Therefore $g\geq f$. That is,%
-		\begin{equation*}
-			e+1\leq f\leq g\leq e+(\Delta -1-\delta _{0}).  %\label{basic-eq-2} %%HM: is never referenced.
-		\end{equation*}
-
-		Consider the path $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$. Assume that we start
-		traversing $P^{\ast }$ at time $t_{u_{2}}$. Then we arrive at $v_{i}$ at
-		time $x\Delta +g$, and we continue by traversing edge $v_{i}v_{i-1}$ at time 
-		$(x+1)\Delta +e$. That is, $d(u,v_{i-1},P^{\ast })=(x+1)\Delta
-		+e-t_{u_{2}}+1$.
-
-		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
-		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
-		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, i.e. $%
-		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
-		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
-		\end{eqnarray*}%
-		which proves the statement of the lemma.
-
-		\emph{Case 2: }$t_{u_{2}}=t_{v_2}$. Then, it follows by Equation~(\ref%
-		{basic-eq-1}) that $%
-		A_{t_{v_2}}(u,v_{i},P)=A_{t_{v_2}}(u,v_{i},Q)-\delta _{0}\leq
-		A_{t_{v_2}}(u,v_{i},Q)$. Therefore $g\leq e$. Similarly to Case 1
-		above, consider the paths $P^{\ast }=P\cup \{v_{i}v_{i-1}\}$ and $Q^{\ast
-		}=Q\setminus \{v_{i}v_{i-1}\}$. Assume that we start traversing $P^{\ast }$
-		at time $t_{u_{2}}=t_{v_2}$. Then we arrive at $v_{i}$ at time $x\Delta +g$%
-		, and we continue by traversing edge $v_{i}v_{i-1}$, either at time $%
-		(x+1)\Delta +e$ (in the case where $g=e$) or at time $x\Delta +e$ (in the
-		case where $g\neq e$). That is, $d(u,v_{i-1},P^{\ast })\geq x\Delta
-		+e-t_{v_2}+1$.
-
-		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
-		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
-		x\Delta +e-h$, i.e. $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
-		Summarizing, we have:%
-		\begin{equation*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
-		\end{equation*}%
-		which proves the statement of the lemma.
-	\end{proof}
-
- From the above it follows that if $P$ is a fastest path from $u$ to $v$,
- then all vertices of $P$, with the exception of vertices of interest $v_i \in P\setminus \{u,v\}$,
- are reached using the same path $P$.
- We use this fact in the following proof.
-
-\begin{proof}[Proof of \cref{lemma:FPT-uv-LabelAlmostalledges}]
-For every vertex of interest $v_i \in U \cap (P \setminus \{u,v\})$
-we have two options.
-First, when the fastest temporal path $P'$ from $u$ to $v_i$ is
-a subpath of $P$.
-In this case we determine the labeling of $P'$ using \cref{lemma:FPT-uv-Labelalledges}.
-Second, when the fastest temporal path $P'$ from $u$ to $v_i$ is 
-not a subpath of $P$. 
-In this case we know exactly how to label all of the edges of $P$,
-with the exception of edges of from $v_{i-1}v_i$, that are incident to $v_i$ in $P$.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
-    Suppose that
-    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
-    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
-    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
-    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
-    travels through the same two vertices $u$ and $w$.
-    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or~$z,v$.
-\end{lemma}
-\begin{proof}
-    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
-    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
-    Denote with $P_{v_i,z_j}^\ell$
-    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
-    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
-    Let us observe the following possibilities.
-
-    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
-    Denote this path as $P^1_{v_i,z_\ell}$.
-    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
-    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-
-    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
-    Denote this path as $P^2_{v_i,z_\ell}$.
-    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
-    Therefore since
-    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
-    and since there is unique way to
-    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
-    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
-    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
-    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
-    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
-
-    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
-    Denote this path as $P^3_{v_i,z_\ell}$.
-    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
-\end{proof}
-
-\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, among vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
-\end{lemma}
-
-\begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
-
-    Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
-    Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
-    Suppose for the contradiction, that none of the fastest temporal paths among vertices of $S_{u,v}$ traverses the edge $f$.
-
-    \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths among $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
-    \begin{itemize}
-        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
-    is of the following form 
-    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
-    and
-        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
-    is of the following form 
-    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
-    \end{itemize}
-    It follows that 
-    $
-    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
-    $
-    and
-    $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
-    $.
-    Let 
-    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
-    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
-    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
-    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
-    Summing now both of the above equations we get
-    \begin{equation}
-    \begin{split} \label{eq:FPT-prf-fUnlabeled}
-        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
-        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
-        %
-        2 + 
-        1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
-        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
-        &\leq 
-        1 + (t_2 - t_1)_\Delta + 
-        1 + (t_1 - t_2)_\Delta\\
-        %
-        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
-        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
-    \end{split}
-    \end{equation}
-    Note that if $t_i \neq t_j$ we get that 
-    the sum
-    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
-    and if $t_i = t_j$ the sum equals $2\Delta$.
-    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
-    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
-    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
-    for any relation of labels $t_1,t_2, \dots, t_5$,
-    which is a contradiction.
-
-    \emph{Case 2: }$f = v_3v_4$.
-    Here we consider the fastest paths among vertices $v_{2}$ and $v_{4}$.
-    By similar arguments as above we get
-    \begin{align*}
-        (t_5 - t_1)_\Delta + (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta + (t_1 - t_5)_\Delta + 2 \leq (t_3 - t_2)_\Delta + (t_2 - t_3)_\Delta,
-    \end{align*}
-    which is impossible.
-
-    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, among vertices in $S{_u,v}$, avoid an edge $f$.
-
-    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
-    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
-    Suppose that the fastest temporal paths among $v_1$ and $v_3$ do not use the edge $f$.
-    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
-    which is of form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
-    and similarly 
-    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
-    of form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
-    Again we get the following.
-    \begin{equation*}
-    \begin{split}
-        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
-        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
-        %
-        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
-        &\leq 
-        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
-    \end{split}
-    \end{equation*}
-    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
-    Repeating the analysis for the fastest paths among $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
-\end{proof}
-
-\subsubsection{Adding constraints and variables to the ILP}
-We start by analyzing the case where we want to determine the labels on fastest temporal paths among vertices of interest.
-We proceed in the following way.
-Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
-If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
-In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
-We call these $\ell - 1$ edges, \emph{partially determined} edges.
-After repeating this step for all pairs of vertices in $U$,
-the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
-or are partially determined.
-If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
-All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
-are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
-
-Now we want to relate the not yet determined segments with the determined ones.
-Let $S_{u,v}$ and $S_{w,z}$ be two segments.
-At the beginning we have guessed the fastest path from $v_i$ to all vertices in $S_{w,z}$ (see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}).
-We did this by determining which vertices $z_j, z_{j+1}$ in $S_{w,z}$ are furthest away from $v_i$
-(remember we can have the case when $z_j = z_{j+1}$),
-and then we guessed how the path from $v_i$ leaves the segment $S_{u,v}$ (\ie either through the vertex $u$ or $v$),
-and then how it reaches $z_j$ (in the case when $z_j \neq z_{j+1}$ there is a unique way,
-when $z_j = z_{j+1}$ we determined which of the vertices $w$ or $z$ is on the fastest path).
-W.l.o.g.\ assume that we have guessed that the fastest path from $v_i$ to $z_j$
-passes through $w$ and $z_{j-1}$.
-Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
-And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
-use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
-Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
-with the exception of the edge $z_j z_{j+1}$.
-Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
-Since we repeat that procedure for all pairs of segments,
-we get that for a fixed segment $S_{w,z}$ we end up with a not yet determined edge $z_j z_{j+1}$
-if and only if this is a not yet determined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.
-%
-We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined, 
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
-and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
-We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths among vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-We proceed as follows.
-\begin{enumerate}[G-1.]
-    \setcounter{enumi}{\value{guesscounter}}
-    \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    For every segment $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$,
-    we guess which of the following fastest temporal paths pass through the edge $f$,
-    one of the fastest paths between $v_{i-1}$ and $v_{i+1}$ (either from $v_{i-1}$ to $v_{i+1}$, or vice versa), 
-    and 
-    one of the fastest paths between $v_{i}$ and $v_{i+2}$.
-    We create $4$ guesses for each such segments, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
-    % counter for guesses continues
-    \setcounter{guesscounter}{\value{enumi}}
-\end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
-that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
-or it depends on no other label.
-We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
-At the end we create our final guess.
-\begin{enumerate}[G-1.]
-% counter for guesses continues
-\setcounter{enumi}{\value{guesscounter}}
-%%
-    \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2 !) = O(k^{2k^2}) = O(k^{k^3})$ guesses
-and consequently
-each of the ILP instances we created up to now is further split into $O(k^{k^3})$ new ones.
-\end{enumerate}
-We have now finished creating all ILP instances.
-From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
-We proceed with adding constraints to each of our ILP instances.
-First we add all constraints for the labels of edges that we have determined up to now.
-We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths among them.
-
-We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
-Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
-and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
-Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
-Using \cref{obs:durationPwithWaitingTimes}
-we create an \emph{equality constraint} for $P$
-of the form 
-\begin{equation}\label{eq:FPT-equalityConstraint}
-    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
-\end{equation}
-and an \emph{inequality constraint} for $Q$ 
-\begin{equation}\label{eq:FPT-inequalityConstraint}
-    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
-\end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference among them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess G-~\ref{FPT:guessallPermutations}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
-
-We iterate through all pairs of vertices $x,y$ and make sure that the fastest temporal path from $x$ to $y$ produces the equality constrain \cref{eq:FPT-equalityConstraint},
-and all other temporal paths from $x$ to $y$ produce the inequality constraint \cref{eq:FPT-inequalityConstraint}.
-For each pair we argue how we determine these paths.
-
-\subparagraph{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$.}
-First we consider the case when $u,v$ are two vertices of interest.
-This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
-We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
-We then continue 
-through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
-There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.
-
-\subparagraph{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$.}
-Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
-From the guesses G-\ref{FPT:guess-uToSegmentz2} and G-\ref{FPT:guess-splitFromUtoAnotherSegment} it follows that we know the fastest temporal paths from $u$ to all vertices in a segment $S_{w,v}$.
-In this case we create the equality constraint for the fastest path and
-iterate through all other paths, for which we introduce the inequality constraints.
-There are $O(k^k)$ possible paths of $u \leadsto w$ (resp.~$u \leadsto v$),
-and a unique way how to extend those paths from $w$ (resp.~$v$) to reach $x$ in $S_{w,v}$.
-Therefore we add $O(k^k)$ inequality constraints.
-
-%%%%%%
-%%%%%% below was done before we had the Guess 7, now we see this case follows easily from it.
-\begin{comment}
-
-We have three possibilities:
-\begin{enumerate}[(i)]
-    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_{p-1},v_p = v)$. 
-    If $x$ is on a fastest path from $u$ to some other vertex $w \in U$, then we know that the fastest path from $u$ to $x$ is a subpath of the segment $S_{u,v}$.
-    We introduce the equality constraint for it.
-    We iterate through all possible paths of form $u \leadsto v \rightarrow v_{p-1} \rightarrow \dots \rightarrow x$ and introduce inequaity constraints for them.
-    Since there are $O(k^k)$ possible paths from $u$ to $v$, we create $O(k^k)$ inequality constraints.
-
-    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex $w \in U$.
-    Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (which we know from guess~G-\ref{FPT-guessFTPamongv2z2}).
-    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
-    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
-    Then we know that the fastest temporal paths from $u$ to $v_1, v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
-    and the fastest temporal paths from $u$ to $v_{p-1}, v_{p-2}, \dots, v_{i+1} $ travel along $Q$.
-    Therefore we can uniquely determine the fastest temporal path from $u$ to $x$.
-    We introduce the equality constraint for these fastest temporal paths, and iterate through all other paths,
-    for which we introduce the inequality constraints.
-    Note that to find all other paths we need to find all $u \leadsto v$ paths, that we then uniquely extend to $x$.
-    Therefore we introduce $O(k^k)$ inequality constraints.
-    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$, 
-    but it does not lie on the segment $S_{u,v}$.
-    Suppose that $x$ lies on a segment $S_{w,z}$.
-    Then by \cref{lemma:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$.
-    This results in adding the equality constraint for this fastest temporal path.
-    We now have to iterate through all others temporal paths from $u$ to $x$ and add the inequality constraints.
-    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
-    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
-    Therefore we add $O(k^k)$ inequality constraints for all these paths.
-
-    \item \label{item:FPT-uToxcase2}
-    Vertex $x$ is not on a fastest temporal path from $u$ to any $v \in U$.
-    Suppose that $x$ lies on a segment $S_{w,z} = (w=z_1,z_3, \dots, z_r = z)$.
-    Since we the fastest paths $Q^+$ of form $u \leadsto w \rightarrow z_2$ and 
-    $Q^-$ of form $u \leadsto z \rightarrow z_{r-1}$ Denote with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_{p-1}$ (see guess~G-\ref{FPT-guessFTPamongv2z2}),
-    we have to only determine how we reach vertex $x$ from the segment (\ie will the fastest path go through $w$ or through $z$).
-    This is done,
-    by checking the distances from $u$ to $z_i$, for $z_i \in S_{w,z} \setminus \{w,z\}$,
-    and determining the split vertex $z_j$ from $u$ on the segment $S_{w,z}$ (\ie vertex $z_i$ in $S_{w,z}$ that has biggest value $D_{u,z_i}$).
-    For all vertices $z_i \neq z_j$, we know which part of the segment is used to reach it.
-    Namely, if $z_i$ is closer to $w$ than $z_j$ in $S_{w,z}$ we first use the path $Q^+$, that is then uniquely extended to reach $z_i$,
-    and similarly 
-    if $z_i$ is closer to $z$ than $z_j$ in $S_{w,z}$
-    we first use the path $Q^+$, that is then uniquely extended to reach $z_i$.
-    We set this path as the fastest temporal path, that must satisfy the equalities and for all other temporal paths
-    (\ie paths of form $u \leadsto z \rightarrow z_{r-1} \rightarrow \cdots \rightarrow x$, and paths of form $u \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow x$),
-    we add the inequalities constraints.
-    If $x = w^*$, we have two possibilities,
-
-    we check the values of each one and set the minimum of them, to equal the $D_{u,x}$, 
-    if this is even possible, if one is too small we immediately reject.
-    Note, we know the durations of fastest temporal paths from $u$ to $z_2$ and $z_{r-1}$. We also know all the labels of the edges of $S_{w,z}$, with respect to each other,
-    with the exception of at most one inner edge.
-    Therefore we can completely calculate the duration from $u$ to $x=w^*$ coming from one side (\ie either from $w$ or $z$).
-    Suppose that the value of the duration of the fastest path from $u$ to $w^*$, through $w$ is
-    smaller than $D_{u,x}$, then we reject and stop the calculation.
-    If the value equals $D_{u,x}$ we have determined the fastest temporal path and we use it to create equality constraints, while we use the other path, through $z$, to create an inequality constraint.
-    If the value is bigger than $D_{u,x}$, we create an inequality constraint for this path and create an equality constraint for the path through $z$.
-    We calculate also all other possible paths from $u$ to $x$ and create inequalities for all of them.
-    These paths are exactly all the paths from $u$ to $w$ (resp.~$z$), from where we uniquely continue to $x$ through $S_{w,z}$.
-    There are $O(k^{k})$ different paths from $u$ to $w$ (resp.~$z$), therefore we add
-    $O(k^k)$ inequality constraints for all these paths, for a fixed $u$ and $x$.   
-\end{enumerate} 
-\end{comment}
-
-Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
-%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
-Let $x$ a vertex in the segment $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$.
-If $S_{w,z}$ is of length $3$ or less, then we already know the fastest temporal path from every vertex in the segment to $u$ 
-(since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess G-\ref{FPT-guessFTPamongUandUstar}).
-Therefore assume that $S_{w,z}$ is of length at least $4$.
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~G-\ref{FPT:guess-uToSegmentz2}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
-and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
-$(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
-We distinguish the following two options.
-\begin{enumerate}[(i)]
-    \item \label{FPT:equality-fromUtoX-twosplit}
-    $z_i \neq z_{i+1}$.
-    Then the fastest temporal path from $z_i$ to $u$ is 
-    $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    and 
-    the fastest temporal path from $z_{i+1}$ to $u$ is 
-    $(z_{i+1} \rightarrow z_{i+2} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-    \item \label{FPT:equality-fromUtoX-onesplit}
-    $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
-    Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
-    If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
-    if $c = D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$,
-    if $c > D_{z_{i},u}$ then the fastest temporal path from $z_i$ to $u$ is of form $(z_i \rightarrow z_{i+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-\end{enumerate}
-Once the fastest temporal paths are determined and we introduce the equality constraints for them.
-For all other $O(k^k)$ paths (which correspond to all paths of form $w \leadsto u$ and $z \leadsto u$, together with the unique subpath on $S_{w,z}$),
-we introduce the inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$.}
-Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
-We have two options.
-\begin{enumerate}[(i)]
-    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path among vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-    \item Vertices $x$ and $y$ are in different segments. 
-Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
-By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
-we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
-Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
-This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
-Now we determine the vertex $v_j \in S_{u,v} \setminus \{u,v\}$,
-for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
-Again, if there are two such vertices $v_{j}$ and $v_{j+1}$ we know exactly how the fastest temporal paths, starting in these two vertices,
-leave the segment $S_{u,v}$. 
-We use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-Knowing the vertex $v_j$
-implies that the fastest temporal paths from the vertices $v_2, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_{p-1}$) to the vertex $y$ passes through $u$ (resp.~$v$).
-Since we know the following fastest temporal paths (see guess~G-\ref{FPT-guessFTPamongv2z2}) 
-$z_2 \rightarrow w \leadsto u \rightarrow v_2$,
-$z_2 \rightarrow w \leadsto v \rightarrow v_{p-1}$,
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$ and
-$z_{r-1} \rightarrow z \leadsto v \rightarrow v_{p-1}$,
-we can uniquely determine all fastest temporal paths from $x \neq v_j$ to any $y \in S_{u,v} \setminus \{z_i\}$.
-
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from $v_j$ to $z_i$,
-using 
-similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
-we can again uniquely determine the fastest path from $v_j$ to $z_i$, using the same approach, 
-and the knowledge of fastest paths to (or from) all vertices of the segment of length $3$
-(as we guessed them in guess~G-\ref{FPT-guessFTPamongv2z2}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses G-\ref{FPT-guessFTPamongv2z2} and G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}.
-\end{enumerate}
-Once the fastest paths are uniquely determined we introduce the equality constraints for them
-and iterate through all other paths, that produce inequalities.
-To find all non-fastest temporal paths we have to consider all possible paths $u \leadsto w$ among vertices of interest, that are the endpoints of observed segments,
-once the segment is reached there is a unique path how to traverse it.
-Therefore we introduce $O(k^k)$ inequality constraints for each pair of vertices $x,y$.
-
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path among them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
-\end{lemma}
-\begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
-Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths among $z,u$ where $z \in Z$ and $u \in U$.}
-Let us start with the case when we want to determine the fastest temporal path from a representative vertex $r_i$ in some tree $T_i$ to a vertex of interest $u \in U$.
-We distinguish the following two cases.
-\begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~G-\ref{FPT:guess-uToSegmentz2} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $O(k^k)$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subset R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other paths we add the inequality constraints. 
-       There are $O(k^k)$ of paths like this.
-    \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess G-\ref{FPT:guess-uToSegmentz2}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $O(k^k)$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $O(k^k)$ inequality constraints. .
-\end{enumerate}
-
-In the case when we want to determine the fastest path from a vertex of interest $u \in U$ to a representative vertex $r_i$ in $T_i$, we 
-again have to split the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess G-\ref{FPT:guess-uToSegmentz2}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,y$ where $z \in Z$ and $y \in V(G') \setminus U$.}
-The next two cases are the ones where we want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest,
-and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess G-\ref{FPT:guess-splitFromUtoAnotherSegment}.\\
-%
-Since $y \in S_{u,v}$ there are $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $O(k^{k})$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-In the case when we want to determine the fastest path from a vertex $y \in V(G')$, that is not a vertex of interest,
-to a representative vertex $r_i$ in $T_i$, 
-we 
-again have to split the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess G-\ref{FPT:guess-uToSegmentz2}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths among $z,z'$ where $z \in Z$ and $z' \in Z$.}
-The last case to consider is when we want to determine the fastest temporal paths among two vertices from $Z$.
-Let $r_i, r_j$ be representative vertices of trees $T_i$ and $T_j$ and let $w_i, w_j$ be their clip vertices, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths among them (see guess G-\ref{FPT:guess-uToSegmentz2}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths among 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $O(k^k)$ inequality constraints.
-
-\subsubsection{Solving ILP instances}
-All of the above finishes our construction of ILP instances.
-We have created $f(k)$ instances (where $f$ is a double exponential function), 
-each with $O(k^2)$ variables and $n^2 g(k)$ constraints (again, $g$ is a double exponential function).
-We now solve each ILP instance $I$, using results from Lenstra \cite{Lenstra1983Integer},
-in the FPT time, with respect to $k$.
-%
-If none of the ILP instances gives a positive solution, then there exists no labeling $\lambda$ of $G$ that would realize the matrix $D$ (\ie for any pair of vertices $u,v \in V(G)$ the duration of a fastest temporal path from $u$ to $v$ has to be $D_{u,v}$).
-If there is at least one $I$ that has a valid solution, 
-we use this solution and produce our labeling $\lambda$, for which $(G,\lambda)$ realizes the matrix $D$.
-We have proven in the previous subsections that this is true since each ILP instance corresponds to a specific configuration of fastest temporal paths in the graph (\ie considering all ILP instances is equivalent to exhaustively searching through all possible temporal paths among vertices).
-Besides that, in each ILP instance we add also the constraints for durations of all temporal paths among each pair of vertices.
-This results in setting the duration of a fastest path from a vertex $u \in V(G)$ to a vertex $v \in V(G)$ as $D_{u,v}$,
-and the duration of all other temporal paths from $u$ to $v$, to be greater or equal to $D_{u,v}$,
-for all pairs of vertices $u,v$.
-Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
-
-To create the labeling $\lambda$ from a solution $X$, of a positive ILP instance,
-we use the following procedure.
-First we
-label each edge $e$, that corresponds to the variable $x_e$
-by assigning the value $\lambda(e) = x_e$.
-We then continue to set the labels of all other edges. 
-We know that the labels of all of the remaining edges depend on the label of (at least one) of the edges that were determined in previous step. 
-Therefore, we easily calculate the desired labels for all remaining edges.
-
-\subsection{Polynomial-time algorithm for cycles}\label{sec:cyclealgo}
-In this section, we present a polynomial-time algorithm for \deltaExact\ when the underlying graph is a cycle.
-Note that \cref{thm:FPTwrtFES} already implies that \deltaExact\ on cycles is polynomial time solvable, however, for this particular case we can give a much simpler algorithm.
-
-Let us observe some properties of the matrix $D$ from \deltaExact, when the underlying graph $G$ of $D$ is a cycle $C_n = \{v_1, v_2, \dots, v_n\}$  on $n$ vertices.
-By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
-therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
-This results in the upper and lower diagonal of $D$ having all $1$'s, together with $D_{1,n} = D_{n,1} = 1$.
-The matrix $D$ is of the following form
-\begin{equation} \label{eq:D-matrixForCycles}
-  D = 
-  \begin{bmatrix}
-    0 & 1 &  &  &  & 1\\
-    1 & 0 & 1 &  &  & \\
-    & 1 & 0 & 1 & & \\
-    & & \ddots & \ddots & \ddots &   \\
-    &   & &1 &  0 & 1\\ 
-    1 &  &  &  &1 &  0 
-  \end{bmatrix},
-\end{equation}
-where the empty entries consists of positive integers different than $1$.
-
-Given a matrix in the input of \deltaExact\ we can check in $O(n^2)$ time if it is of correct form, by traversing it once.
-If it is not of correct form, our algorithm stops and returns the negative answer.
-From now on, we assume, that the input matrix has the same form as $D$ from \cref{eq:D-matrixForCycles}.
-
-Let $v_i$ be an arbitrary vertex in the cycle $C_n =\{v_1, v_2, \dots, v_n\}$.
-Vertex $v_i$ can reach an arbitrary vertex $v_k \in C_n$ using a positive side of the cycle (\ie going from $v_i$ to $v_{i+1},  v_{i+2}$, etc.), 
-and using the negative side of the cycle (\ie going from $v_i$ to $v_{i-1}, v_{i-2}$, etc.).
-Let us denote with the $d^+(i,k)$ the duration of the temporal path from $v_i$ to $v_k$ using the positive side of the cycle,
-and with $d^-(i,k)$, the duration of the temporal path from $v_i$ to $v_k$ using the negative side of the cycle.
-Since these two are the only possible paths from $v_i$ to $v_k$ in $C_n$ we know that $D_{i,k} = min \{d^+(i,k), d^-(i,k)\}$.
-
-\begin{lemma} \label{lemma:poly-delta-cycle-monotonicity}
-    If vertex $v_i$ reaches vertex $v_j$ the fastest, using the positive (resp.~negative) side of the cycle, \ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$),
-    then $v_i$ reaches all other vertices $v_k$, where $k \in \{i+1, i+2, \dots, j-1\}$ (resp.~ $k \in \{i-1, i-2, \dots, j+1\}$)
-    using the same, positive (resp.~negative) side of the cycle,
-    where the indices are taken modulo $n$.
-\end{lemma}
-\begin{proof}
-    Let $v_i, v_j$ be two arbitrary vertices in $C_n$ and suppose that $D_{i,j} = d^+(i,j)$,
-    but there exists a vertex $v_k$ from $C_n$, where $k \in \{i+1, i+2, \dots, j-1\}$,
-    for which $D_{i,k} \neq d^+(i,k)$.
-    Then $d^-(i,k)$ passes through vertex $v_j$, and we can split the path from $v_i$ to $v_k$ into two pieces, 
-    first from $v_i$ to $v_j$ and the second one from $v_k$ to $v_j$.
-    So 
-    \begin{equation} \label{eq:poly-delta-cycle-monotonicity}
-        d^-(i,k) = d^-(i,j) + d^-(j,k)^*,
-    \end{equation} where $d^-(j,k)^*$ is the duration of the path from $v_j$ to $v_k$, using the negative side of the cycle, with consideration that we come to vertex $v_j$ at time $d^-(i,j)$ and we potentially have to wait there for some positive amount of time, before we continue to $v_j$
-    (\ie $d^-(j,k)^* \geq d^-(i,j) \geq D_{j,k}$ includes some waiting time at vertex $v_j$).
-    By the assumption we know that $d^+(i,j) \leq d^-(i,j)$, so we can rewrite \cref{eq:poly-delta-cycle-monotonicity} as
-    $d^-(i,k) \leq d^+(i,j) + d^-(j,k)^*$.
-This means that we can reach $v_k$ from $v_j$ by going from $v_i$ to $v_j$ using the positive side of the cycle, wait some time at $v_j$, before we continue back to $v_j$.
-    In the above construction vertex $v_k$ is visited twice.
-By the definition, the fastest temporal path from $v_i$ to $v_k$ visits $v_k$ exactly once.
-Therefore we can stop at $v_k$ already when traveling from $v_i$ to $v_j$ the first time, using the positive side of the cycle.
-    It follows that $D_{i,j} = d^+(i,j) \leq d^-(i,j)$, which contradicts with our assumption.
-\end{proof}
-
-Let $v_i$ and $v_j$ be two arbitrary vertices in the cycle $C_n$, for which $v_i v_j \notin E(C_n)$.
-Suppose that $P^+_{i,j}$ (resp.~$P^-_{i,j})$ is the underlying path of the fastest temporal path from $v_i$ to $v_j$, 
-using positive (resp.~negative) side of the cycle, 
-\ie $v_i, v_{i+1}, \dots, v_{j-1}, v_j$ (resp. $v_i, v_{i-1}, \dots, v_{j+1}, v_j$).
-Then by \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays},
-we get that we can determine all travel delays at vertices of $P^+_{i,j} \setminus \{v_i, v_j\}$ (resp.~$P^-_{i,j} \setminus \{v_i, v_j\}$).
-
-Let $v_i$ be an arbitrary vertex of $C_n$. Let us look at the row $i$ of the matrix $D$, which corresponds to the durations of fastest temporal paths from $v_i$ to all other vertices $v_j \in C_n$.
-Using \cref{lemma:poly-delta-cycle-monotonicity} we know that $v_i$ will reach some consecutive vertices $v_{i+1}, v_{i+2}, \dots, v_j$ the fastest, using the positive side of the cycle 
-and $v_{i-1}, v_{i-2}, \dots, v_{j+1}$ the fastest, using the negative side of the cycle.
-Suppose $v_j \in C_n$ is the last vertex $v_i$ reaches using the positive side of the cycle, and $v_{j+1}$ the last vertex that is reached using the negative side of the cycle.
-Then we know that $D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}$.
-Note that it can happen that $v_j = v_{j+1}$, \ie to reach vertex $v_j$ from $v_i$ the fastest, we can use either positive or negative side of the cycle.
-Using the above observations, every row $i$ ($i \in [n]$) of matrix $D$ has two (or one) maximum elements, one at position $j$ and the other at position $j+1$, where $j, j+1 \in [n]$ and the indices are considered modulo $n$.
-Let us denote these two values as $m_i^1$ and $m_i^2$.
-The row $i$ of $D$ is of the following form, it has a $0$ at the entry $i$, it has $1$ at entries $i-1, i+1$,
-the values increase on the positions $i+1, i+2, i+3, \dots, j-1, j$ for some $j$ with value $m_i^1$, 
-and on the other side, values increase on the positions $i-1, i-2, i-3, \dots, j+2, j+1$ for some $j+1$ with value $m_i^2$,
-where indices are taken modulo $n$.
-
-Knowing this, we can split the vertices $v_j \in V(C_n) \setminus \{v_i\}$ into two parts, ones that are reached from $v_i$ the fastest using the positive side of the cycle and ones that are reached using the negative side of the cycle.
-To determine these two sets we do the following.
-We fix a vertex $v_i \in C_n$ and check its corresponding row in the matrix $D$. 
-We determine two max values $m_i^1$ and $m_i^2$ at positions $j$ and $j+1$ (modulo $n$), respectively,
-for which it has to hold that
-$D_{i,i+1} < D_{i,i+2} < \cdots< D_{i,j-1} < D_{i,j}=m_i^1$ and 
-$D_{i,i-1} < D_{i,i-2} < \cdots < D_{i,j+2} < D_{i,j+1}=m_i^2$.
-Note, it can also happen that $m_i^1 = m_i^2$. 
-Now denote the path that uses the positive side of the cycle, from $v_i$ to $v_j$, as $P^+_i$ and
-the path that uses the negative side of the cycle, from $v_i$ to $v_{j+1}$, as $P^-_i$.
-By \cref{lemma:poly-delta-cycle-monotonicity} and \cref{lemma:unique-fastest-path-allDelays} we can calculate travel delays at every vertex $v_k \in C_n \setminus \{v_i, v_j, v_{j+1}\}$,
-which we store in a list $T$ of length $n$,
-where the entry at the position $k$ corresponds to the travel delay at vertex $v_k$ when traveling from $v_{k-1}$ to $v_{k+1}$.
-Note, from \cref{obs:travel-delays-both-directions} it follows, that it is enough to store the value of the travel delay in one direction (\ie knowing $\tau_v^{u,w}$ we know also $\tau_v^{w,u}$).
-We repeat the above procedure for all rows in the matrix $D$, \ie for all vertices $v_i \in C_n$.
-Calculation in one row is performed in $O(n)$ time, repeating it for all rows we need $O(n^2)$ time.
-
-To determine the labeling $\lambda$ satisfying the matrix $D$, we have to make sure that we have calculated travel delays for all vertices.
-
-\begin{lemma}
-List $T$ of travel delays has non-empty values at all positions, \ie we have successfully calculated travel delays for all vertices.
-\end{lemma}
-\begin{proof}
-    Throughout the proof we
-    denote with $d^+(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the positive side of the cycle $C_n$,
-    and similarly with $d^-(i,j)$ the duration of the temporal path that starts at $v_i$ and finishes at $v_j$, that uses the negative side of the cycle $C_n$,
-    where indices are taken modulo $n$.
-
-    Suppose for the contradiction that the statement of the claim does not hold. Then there exists a vertex $v_i \in C_n$, for which we did not calculate its travel delay.
-    Let $v_j \in C_n \setminus \{v_i\}$ be an arbitrary vertex. 
-    Note that the only time we cannot calculate the travel delay at vertex $v_i$, when considering vertex $v_j$, is in this case when $v_i$ is one of the maximum elements in $D_j$, \ie $v_i$ is a vertex that is on a maximum duration from $v_j$.
-    This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
-    We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
-    Since $v_i$ has to be on the maximum duration from both of them 
-    (\ie is one of the two maximum values $m^1_{i-1}, m^2_{i-1}$ for vertex $v_{i-1}$ and one of the two maximum values $m^1_{i+1}, m^2_{i+1}$ for vertex $v_{i+1}$),
-    we know that 
-    \begin{align}\label{eq:cycle-travel-delays-all}
-        & d^+(i+1,i-1) < d^-(i+1,i-1) & \text{and}\\
-        & d^-(i-1,i+1) < d^+(i-1,i+1).
-    \end{align}
-    If this would not hold, the fastest path would go through $v_i$ and we would be able to calculate the travel delay at $v_i$.
-
-    Denote the labels $\lambda(v_{i-1}v_i) = a, \lambda(v_{i}v_{i+1})=a'$, and $\lambda(v_{i-2}v_{i-1}) = b, \lambda (v_{i+1}v_{i+2})=b'$, where $a,a',b,b' \in [\Delta]$.
-    W.l.o.g. we can suppose that $a \geq a'$.
-    Therefore, using the definition for the duration of temporal paths, we get that
-    $d^+(i+1,i-1) = (k \Delta + b) - b' + 1$, where $k$ is some non-negative integer, and $d^-(i+1,i-1) = a - a' + 1$.
-    Using the first inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k \Delta + b) - b' +1 < a - a' + 1$ which is equivalent to $(k \Delta + b) - b' < a - a'$, which can be true only when $k = 0$, but because the duration is positive we get that $b > b'$ and
-    $b - b' < a - a'$.
-    Now again using the definition of the duration, we get
-    $d^+(i-1,i+1)= (k\Delta + a') - a + 1$, where $k$ is some non-negative integer, but since $v_{i-1}v_i$ and $v_iv_{i+1}$ are incident edges, we know also that $k=1$, therefore $d^+(i-1,i+1)= \Delta + a - a + 1$.
-    Again by the definition, $d^-(i-1,i+1) = (k' \Delta + b') -b + 1$, for some non-negative integer $k'$.
-    Using the second inequality from \cref{eq:cycle-travel-delays-all} we get that 
-    $(k' \Delta + b') -b + 1 < \Delta + a - a + 1$.
-    Which is equivalent to  $(k' \Delta + b') -b < \Delta + a' - a $.
-This can hold only when $k' = 1$, in that case we get $ \Delta + b' -b < \Delta + a' - a $ which is equivalent to $b' -b < a' - a$.
-    This is in the contradiction with the inequality  $b - b' < a - a'$ as this is equivalent to $b'-b > a'-a$.
-
-    Therefore it cannot happen that there is a vertex $v_i$ for which we cannot calculate its travel delay in $C_n$.
-\end{proof}
-
-All of the above observations imply the following result.
-\begin{theorem}
-    \deltaExact\ can be solved in polynomial time on cycles.
-\end{theorem}
-
-\begin{proof}
-As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
-Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
-We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
-Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-\end{proof}
-
-\begin{comment}
-We have the following two cases.
-\begin{enumerate}[(i)]
-    \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    Similarly as above, we determine two cases.
-    \begin{itemize}
-    \item $S_{w,z}$ has no not yet determined edge $p$ in the middle, or $p \cap \{x \} = \emptyset$.
-    Then we can determine the waiting time at vertex $x$, when traversing from $r_i$ to $z_{i-1}$ (resp.~$z_{i+1}$).
-    Let $P$ be the underlying path of a fastest temporal path from $x$ to $y$ (we determined it in one of the previous steps, when we were considering vertices $x$ and $y$).
-    W.l.o.g. suppose that $P$ passes through vertex $z_{i-1}$. 
-    Then we set $P^-$ as $P^- = \{r_i, x\} \cup P^-$ and check the value of $d(P^-)$.
-    If $d(P^-) < D_{r_i,y}$ we stop with calculations and determine that the ILP instance hos no valid solution.
-    If $d(P^-) = D_{r_i,y}$ we determine that $P^-$ is the underlying path of the fastest temporal path from $r_i$ to $y$. 
-    If $d(P^-) > D_{r_i,y}$ we determine that the fastest temporal path from $r_i$ to $y$ goes through the vertex $z_{i+1}$.
-    We determine $P^+$ as the union of the unique path from $x$ to $z_p$, and the underlying path of the fastest temporal path $P'$ of form $z_p \rightarrow z \leadsto y$, \ie $P^+ = (r_i, x, z_{i+1}, \dots, z_p) \cup P'$.
-    We know how to determine $P'$, since
-    we did it in one of the previous steps, when we were considering fastest path from $z_p$ through $z$ to $y$.
-    Note, if the fastest temporal path from $z_p$ to $y$ does not pass through $z$, then we would be in previous case, where the fastest temporal path from $r_i$ to $y$ would be $P^-$.
-
-    \item The segment $S_{w,z}$ has an extra not yet determined edge $p$. Suppose that $p = x z_{i+1}$.
-
-    \end{itemize}
-
-    In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-    For all other paths we add the inequality constraints. 
-    Since the path from $r_i$ to $z_1$ (resp.~$z_p$) is unique, the number of non-fastest paths temporal paths from $r_i$ to $y$ depends on the number of non-fastest temporal paths from $z_1$ (resp.~$z_p$) to $y$.
-    There are $O(k^{k^6})$ such paths.
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-
-\end{enumerate}
-\end{comment}
-
-\section{Conclusion}\label{sec:conclusion}
-We have introduced a natural and canonical temporal version of the graph realization problem with respect to distance requirements, called \deltaExactLong. 
-We have shown that the problem is NP-hard in general and polynomial-time solvable if the underlying graph is a tree.
-Building upon those results, we have investigated its parameterized computational complexity with respect to structural parameters of the underlying graph that measure ``tree-likeness''.
-For those parameters, we essentially gave a tight classification between parameters that allow for tractability (in the FPT sense) and parameters that presumably do not.
-We showed that our problem is W[1]-hard when parameterized by the feedback vertex number of the underlying graph, and that it is in FPT when parameterized by the feedback edge number of the underlying graph.
-Note that most other common parameters that measure tree-likeness (such as the treewidth) are smaller than the vertex cover number.
-
-We believe that our work spawns several interesting future research directions and builds a base upon which further temporal graph realization problems can be investigated.
-
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
-\begin{itemize}
-    \item The \emph{vertex cover number} measures the distance to an independent set, on which we trivially only have no-instances of our problem.
-We believe this is a promising parameter to obtain tractability.
-    \item The \emph{tree-depth} measures ``star-likeness'' of a graph and is incomparable to both the feedback vertex number and the feedback edge number.
-We leave the parameterized complexity of our problem with respect to this parameter open.
-    \item Parameters that measure ``path-likeness'' such as the \emph{pathwidth} or the \emph{vertex deletion distance to disjoint paths} are also natural candidates to investigate.
-\end{itemize}
-Furthermore, we can consider combining a structural parameter with $\Delta$.
-Our NP-hardness reduction (\cref{thm:NPhardness}) produces instances with constant $\Delta$, so as a single parameter $\Delta$ cannot yield fixed-parameter tractability.
-However, in our parameterized hardness reduction (\cref{thm:W1wrtFVS}) the value for $\Delta$ in the produced instance is large.
-This implies that our result does not rule out e.g.\ fixed-parameter tractability for the combination of the treewidth and $\Delta$ as a parameter.
-We believe that investigating such parameter combinations is a promising future research direction.
-
-\subparagraph{Further problem variants.}
-There are many natural variants of our problem that are well-motivated and warrant consideration.
-In the following, we give two specific examples.
-We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
-
-\bibliography{bibliography}
-
-\clearpage
-
-\appendix
 

### 2023-12-20 SAND2024/SAND24-longversion.tex
SAND

--- 2023-10-05 STACS2023/STACS23-longversion.tex
@@
 For the remainder of this section, we fix the following notation. 
-Let $D$ be the input matrix of \deltaExact\ \ie
+Let $D$ be the input matrix of \deltaExact, \ie
 the matrix of the fastest temporal paths between all pairs of $n$ vertices, and let $G$ be its underlying graph, on $n$ vertices and $m$ edges.
@@
 It follows that $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
+
+From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $Z$ consists of disjoint trees. 
+Each of these trees has a unique neighbor $u_i$ in $G'$.
+Denote by $T_i$ the tree that is obtained by such a vertex $u_i$ of $G'$ and all the trees of $Z$ that are incident to $u_i$.
+Then  we call $u_i$ the \emph{clip vertex} of the tree $T_i$.
+For each of these trees~$T_{i}$, we select an arbitrary vertex $r_i \in Z$ that is a neighbor of the clip vertex $u_i$ in $T_i$,
+and call it the \emph{representative vertex} of the tree $T_{u_i}$. 
+We now define by $Z^*$ the set of all representatives $r_i$ of the trees $T_i$,
+where the clip vertex $u_i$ of $T_i$ is a vertex of interest, \ie
 \[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
+Z^* = \{ r_i  :  r_i \in Z \text{ is a neighbor of the clip vertex $u_i$ in the tree $T_i$, and $u_i \in U$}\}.
 \]
@@
 \subparagraph{\boldmath Considering the paths for vertices from $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
-Remember that removed vertices form disjoint trees in $G$.
-Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
-Since there is a unique (static) path between any two vertices $z_1, z_2$ in a tree $T_i$,
-it follows that there is also a unique (therefore also the fastest) temporal path between them.
-Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
-Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
-Recall that for every tree $T_i$ there is a representative vertex $v_i$ of $T_i$,
-and a clip vertex $u_i \in V(G')$, such that $v_i \in N_G(u_i)$.
+All of the above is enough to determine the labeling $\lambda$ of $G'$.
+Now we have to make sure that the labeling considers also the vertices of~$Z= V(G) \setminus V(G')$ that we initially removed from $G$.
+Recall that $Z$ consists of disjoint trees, and that each of these trees has a unique neighbor $u_i$ in $G'$. 
+Furthermore recall that $T_i$ denotes the tree that is obtained by such a vertex $u_i$ of $G'$ and all the trees of $Z$ that are incident to $u_i$; then $u_i$ is the \emph{clip vertex} of the tree $T_i$.
+Moreover, for each of these trees~$T_{i}$ we have selected an arbitrary vertex $r_i \in Z$ that is a neighbor of the clip vertex $u_i$ in $T_i$, 
+and $r_i$ is called the \emph{representative vertex} of the tree $T_{u_i}$. 
+Let us now describe now how to determine the labels on the edges of any such tree $T_i$.
 To determine the correct label of all edges of $T_i$ we use the following property.
 \begin{lemma}
-Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a representative of $T_i$.
-Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
-Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
+Let $T_i$ be a tree having $u_i$ as its clip vertex, and let $e_i = (u_i,r_i)$. 
+Among all neighbors of $u_i$ in $G'$, let $v \in N_{G'}(u_i)$ be the one that is closest vertex to $r_i$ (with respect to the values of $D$), \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u_i)$.
+Then the path $P^*=(r_i,u_i,v)$ is the fastest temporal path from $r_i$ to $v$.
 \end{lemma}
@@
     The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighboring vertices of $x$, 
     where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
@@
 By the definition, each vertex is on distance $0$ from itself, and therefore also the duration $0$. This corresponds with all diagonal entries of $D$ being $0$.
-Now, let us observe that each vertex $v_i$ has exactly two neighbours in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
+Now, let us observe that each vertex $v_i$ has exactly two neighbors in $C_n$, namely $v_{i-1}$ and $v_{i+1}$,
 therefore for all $i\in [n]$ we set $D_{i,i-1} = D_{i, i+1} = 1$, where indices are taken modulo $n$.
@@
     This has to hold for all vertices $v_j$, therefore $v_i$ has to be on the maximum duration from every vertex $v_j \in C_n \setminus \{v_i\}$.
-    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbours of $v_i$.
+    It then also has to hold for vertices $v_{i-1}, v_{i+1}$, that are neighbors of $v_i$.
     We know that in this case $d^+(i-1,i) = 1, d^-(i+1,i) = 1$.
@@
     \item The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighbouring vertices of $x$, 
+    Let $x$ be a part of a segment $S_{w,z} = (w, z_1, z_2, \dots, z_r, z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighboring vertices of $x$, 
     where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 

### 2024-01-11 SAND2024/SAND24-longversion.tex
changes 10th jan - small changes to full version Nina

@@
 Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$.
-If this check succeeds for all vertex pairs, output the labelling $\lambda$, otherwise abort.
+If this check succeeds for all vertex pairs, output the labeling $\lambda$, otherwise abort.
 
@@
 	\textbf{Inner segment guess II}.
-	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$,
 	and let $w \in U \cup Z^*$. %be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest.
@@
 	\textbf{Split vertex guess I}.
-	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$, and let us
 	fix a vertex $v_i \in S_{u,v} \setminus \{u,v\}$.
@@
 Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
-    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.
+    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$.
     Similarly as above, in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
@@
     Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
-    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
+    Symmetrically, knowing $\lambda(e_p)$ and $d(P,\lambda)$, we can uniquely determine $\lambda(e_1)$.
 \end{observation}
@@
 
-Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
-therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
-where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
-we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
-This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
+Now, to determine the labeling $\lambda$ of the path $P$ we use the property that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$. 
+We set the label of the first edge of $P$ to be a constant $c\in [\Delta]$
+and
+use \cref{obs:FirstLabelAndDuration} to label all remaining edges,
+where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$.
+This gives us a unique labeling $\lambda$ of $P$ where the label of each edge of $P$ is a function of $c$.
 \end{proof}
@@
 \begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
-\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
-is not a part of any fastest temporal path, of length at least $2$, between vertices in $S_{u,v}$,
-\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
-In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
+Let $S_{u,v}$ be a segment in $G$ of length at least $5$, denoted as $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
+It is impossible for an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$ (where $f$ is an edge that is not incident to a vertex from $U$)
+to not be a part of any fastest temporal path, of length at least $2$ between vertices in $S_{u,v}$.
+In other words, there must exist a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through $f$.
+In the case where $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it, while the label of the last remaining edge is a function of $\lambda(f)$.
 \end{lemma}
@@
     $. 
-    Let 
     Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
@@
     In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
-    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, between vertices in $S{_u,v}$, avoid an edge $f$.
+    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, between vertices in $S_{u,v}$, avoid edge $f$.
 
@@
     The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
-    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
-
+    as in this case the left hand side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
+    %
     Repeating the analysis for the fastest paths between $v_2$ and $v_4$,
-    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
-    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
+    we conclude that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
+    %
+    Altogether, we get that $f$ is not a part of any fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
+    %
+    Note now that the fastest temporal path from $v_2$ to $v_4$ must first use the edge $u v_2$ and finish with the edge $v_4 v_5$, and it has to be of duration $D_{v_2, v_4}$.
+Using \cref{lemma:FPT-uv-Labelalledges} we determine the label of the edge $v_4v_5$ as a function of $\lambda(f)$.
 \end{proof}
@@
 are called the \emph{not yet determined} edges.
-Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.
+Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path between any two vertices in $U$.
 
@@
 with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We will now relate also these edges.
+We now relate also some of these edges.
 More precisely,
@@
     For the fastest temporal paths from $v_{i-1}$ to $v_{i+1}$, from $v_{i+1}$ to $v_{i-1}$, from $v_{i}$ and $v_{i+2}$, and $v_{i+2}$ and $v_{i}$, we guess whether it passes through the edge $f$. 
-    Thus we create $4$ guesses for every such segment $S_{u,v}$, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
+    Thus we create $4$ guesses for every such segment $S_{u,v}$, and $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
     % counter for guesses continues
@@
 In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
-which results in a segment with two not yet determined edges.
+But in this case we know that three edges have the same label, denote it $c$, while the label of the last one is a function of $c$.
 In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
 therefore these segments remain with three, two or one not yet determined edges, respectively.
-From now on we refer to segments of length less than $4$.
-
-At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
+%From now on we refer to segments of length less than $4$.
+
+At this point $G'$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
 that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,

### 2024-01-12 SAND2024/SAND24-longversion.tex
before new changes

@@
 
-From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $Z$ consists of disjoint trees. 
+From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (graph induced in $G$ by $Z$) consists of disjoint trees. 
 Each of these trees has a unique neighbor $u_i$ in $G'$.
-Denote by $T_i$ the tree that is obtained by such a vertex $u_i$ of $G'$ and all the trees of $Z$ that are incident to $u_i$.
+Denote by $T_i$ the tree that is obtained by such a vertex $u_i$ and all the trees from $G[Z]$ that are incident to $u_i$.
 Then  we call $u_i$ the \emph{clip vertex} of the tree $T_i$.
@@
 Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case we know that three edges have the same label, denote it $c$, while the label of the last one is a function of $c$.
-In the case when the segment $S_{u,v}$ has just three, two or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two or one not yet determined edges, respectively.
+In the case when a segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
+But in this case, we know that three edges have the same label, denote it $c$, while the label of the last one is a function of $c$.
+In the case when the segment $S_{u,v}$ has just three, two, or one edge, this procedure does not improve anything,
+therefore these segments remain with three, two, or one not yet determined edges, respectively.
 %From now on we refer to segments of length less than $4$.
@@
 We now describe how we create variables and start building our ILP instances. 
-For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
-Besides that we create one variable for each edge that is still not yet determined on a segment.
+For every edge $e$ in $G'$ that is incident to a vertex of interest, we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
+Besides that, we create one variable for each edge that is still not yet determined on a segment.
 Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
@@
 together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
+Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check the labels of all of its neighbors,
 which are determined by some other label,
@@
 Recall that $Z$ consists of disjoint trees, and that each of these trees has a unique neighbor $u_i$ in $G'$. 
-Furthermore recall that $T_i$ denotes the tree that is obtained by such a vertex $u_i$ of $G'$ and all the trees of $Z$ that are incident to $u_i$; then $u_i$ is the \emph{clip vertex} of the tree $T_i$.
+Furthermore, recall that $T_i$ denotes the tree that is obtained by such a vertex $u_i$ of $G'$ and all the trees of $Z$ that are incident to $u_i$; then $u_i$ is the \emph{clip vertex} of the tree $T_i$.
 Moreover, for each of these trees~$T_{i}$ we have selected an arbitrary vertex $r_i \in Z$ that is a neighbor of the clip vertex $u_i$ in $T_i$, 
@@
 there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find fastest temporal paths from and to the 
+we present the study for cases when we find the fastest temporal paths from and to the 
 representative vertex $r_i$ of tree $T_i$.
-Each of these paths are then uniquely extended to all vertices in $T_i$.
+Each of these paths is then uniquely extended to all vertices in $T_i$.
 

### 2024-01-13 SAND2024/SAND24-longversion.tex
Fixed proof for tree vertices of the FPT algorithm

@@
 
-From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (graph induced in $G$ by $Z$) consists of disjoint trees. 
+%From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by $Z$) consists of disjoint trees.
 Each of these trees has a unique neighbor $u_i$ in $G'$.
-Denote by $T_i$ the tree that is obtained by such a vertex $u_i$ and all the trees from $G[Z]$ that are incident to $u_i$.
-Then  we call $u_i$ the \emph{clip vertex} of the tree $T_i$.
-For each of these trees~$T_{i}$, we select an arbitrary vertex $r_i \in Z$ that is a neighbor of the clip vertex $u_i$ in $T_i$,
-and call it the \emph{representative vertex} of the tree $T_{u_i}$. 
-We now define by $Z^*$ the set of all representatives $r_i$ of the trees $T_i$,
-where the clip vertex $u_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in Z \text{ is a neighbor of the clip vertex $u_i$ in the tree $T_i$, and $u_i \in U$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
+Denote by $T_i$ the tree obtained by considering such a vertex $u_i$ and all the trees from $G[Z]$ that are incident to $u_i$.
+We then refer to $u_i$ as the \emph{clip vertex} of the tree $T_i$.
+
 Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
-For an illustration see \cref{fig:labelingVertices}. Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.
+For an illustration see \cref{fig:labelingVertices}. Note that determining sets $U$ and $U^*$ takes linear time.
 
@@
 In order to find a labeling that satisfies this property we split our analysis in nine cases.
-We consider fastest temporal paths 
+We consider the fastest temporal paths 
 where the starting vertex is in one of the sets $U,V(G') \setminus U, Z$,
 and similarly the destination vertex is in one of the sets $U,V(G') \setminus U, Z$.
-In each of these cases we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
+In each of these cases, we guess the underlying path $P$ that at least one fastest temporal path from the vertex $v_i$ to $v_j$ follows, 
 which results in one equality constraint for the labels on the path $P$. 
@@
 
-For an easier understanding and the analysis of the algorithm we give the following definition.
+For an easier understanding and analysis of the algorithm, we give the following definition.
 \begin{definition}\label{def:segments}
@@
 \end{definition}
-%From the definition it follows, that there are $O(k^2)$ segments in $G'$. \todo{True but does not follow directly just from the definition}
-Note from \cref{def:segments} we get that $S_{u,v} \neq S_{v,u}$, since we consider paths to be directed.
-Observe that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
-Furthermore, since we have at most $4k$ interesting vertices in $G'$, we can deduce the following important result.
+%TODO: We can have two segments among a pair of vertices in U !!!
+%Among a fixed pair of vertices $u,v \in U$ there can be at most two different segments.
+If there are two, then one has to be of length $1$, just a single edge, and the second one of length at least $2$.
+Note from \cref{def:segments} that $S_{u,v} \neq S_{v,u}$ since we consider paths to be directed. It's also worth emphasizing that $S_{v,u}$ is essentially the reversed path of $S_{u,v}$.
+Furthermore, it's important to observe that a temporal path in $G'$ between two vertices of interest is either a segment or consists of a sequence of segments.
+Moreover, any inner vertex $v_i$ in the segment $S_{u,v}$ ($v_i \in S_{u,v} \setminus \{u,v\}$) is part of precisely two segments: $S_{u,v}$ and $S_{v,u}$.
+Given that we have at most $4k$ interesting vertices in $G'$, we can deduce the following crucial result.
 \begin{corollary}\label{obs:FPT-k2segments}
@@
 \end{corollary}
-%In the analysis of the algorithm we rely heavily on the fact that there are $O(k^2)$ segments in $G'$.
-%, which we prove later on (see~\cref{obs:FPT-k2segments}).
+%TODO: one reviewer asked how we get this number? (number of paths)
 %For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.
@@
 
+\begin{comment}
+%we never refer to this lemma
 \begin{lemma}\label{lemma:FPT-unlabeldPaths-01}
@@
 \end{proof}
+\end{comment}
 
 \begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
-Let $S_{u,v}$ be a segment in $G$ of length at least $5$, denoted as $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
-It is impossible for an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$ (where $f$ is an edge that is not incident to a vertex from $U$)
+Let $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G$.
+If $S_{u,v}$ is of length at least $5$ ($p > 5$) 
+then it is impossible for an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$ (where $f$ is an edge that is not incident to a vertex from $U$)
 to not be a part of any fastest temporal path, of length at least $2$ between vertices in $S_{u,v}$.
 In other words, there must exist a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through $f$.
-In the case where $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it, while the label of the last remaining edge is a function of $\lambda(f)$.
+If $S_{u,v}$ is of length $4$ then all temporal paths of length $2$ avoid the inner edge $f$ if and only if $f$ has the same label as both of the edges incident to it, while the label of the last remaining edge is determined with respect to $\lambda(f)$.
 \end{lemma}
@@
 \begin{proof}
-    For an easier understanding and better readability we present the proof for $S_{u,v}$ of fixed length $5$.
-    The case where $S_{u,v}$ is longer easily follows from presented results.
+    For an easier understanding and better readability, we present the proof for $S_{u,v}$ of fixed length $5$.
+    The case where $S_{u,v}$ is longer easily follows from the presented results.
 
@@
     \emph{Case 1: }$f = v_2v_3$.
-    Let us observe the case of fastest temporal paths between $v_{1}$ and $v_{3}$.
+    Let us observe the case of the fastest temporal paths between $v_{1}$ and $v_{3}$.
     Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
-    From our proposition it follows that
+    From our proposition, it follows that
     \begin{itemize}
@@
     Note now that the fastest temporal path from $v_2$ to $v_4$ must first use the edge $u v_2$ and finish with the edge $v_4 v_5$, and it has to be of duration $D_{v_2, v_4}$.
-Using \cref{lemma:FPT-uv-Labelalledges} we determine the label of the edge $v_4v_5$ as a function of $\lambda(f)$.
+Using \cref{lemma:FPT-uv-Labelalledges} we determine the label of the edge $v_4v_5$ with respect to $\lambda(f)$.
 \end{proof}
@@
 We repeat this procedure for all pairs of segments.
-Each specific calculation takes linear time, since there are $O(k^2)$ segments, this calculation takes $O(k^4)$ time.
+Each specific calculation takes linear time. Since there are $O(k^2)$ segments, the whole calculation takes $O(k^4)$ time.
 At this point
-the edges of every segment are fully determined, 
+the edges of every segment are fully determined
 with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
@@
 We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this we use the fact that at least one of the temporal paths between vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ has at least $5$ edges (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
+For this, we use the fact that at least one of the temporal paths between vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ is of length at least $5$ or if it is of length $4$ there is a unique labeling that allows no such path to traverse $f$ (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
+%
 We proceed as follows.
@@
     For the fastest temporal paths from $v_{i-1}$ to $v_{i+1}$, from $v_{i+1}$ to $v_{i-1}$, from $v_{i}$ and $v_{i+2}$, and $v_{i+2}$ and $v_{i}$, we guess whether it passes through the edge $f$. 
-    Thus we create $4$ guesses for every such segment $S_{u,v}$, and $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
+    Thus we create $O(1)$ guesses for every such segment $S_{u,v}$, and $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
     % counter for guesses continues
@@
 \end{enumerate}
-Once we know which two fastest temporal paths pass through $f$, 
+Once we know which temporal paths pass through $f$, 
 we can determine the label of edge $f$ 
@@
 Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments with at least $5$ edges.
-In the case when a segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$.
-But in this case, we know that three edges have the same label, denote it $c$, while the label of the last one is a function of $c$.
+Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments of length at least $4$.
 In the case when the segment $S_{u,v}$ has just three, two, or one edge, this procedure does not improve anything,
@@
 Besides that, we create one variable for each edge that is still not yet determined on a segment.
-Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
+Since each vertex of interest is incident to at most $k$ edges in $G'$, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
 At the end we create our final guess.
@@
     \item \label{FPT:guessallPermutations}
-We guess the permutation of all $O(k^2)$ variables,
-together with the relation of each variable to the labels of edges incident to these not yet determined edges.
-Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check the labels of all of its neighbors,
-which are determined by some other label,
-and variables of the not yet determined neighbors,
-and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
-So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
-and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
-$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
+We guess the permutation of all $O(k^2)$ variables.
+%together with the relation of each variable to the labels of edges incident to these not yet determined edges.
+%Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check the labels of all of its neighbors, which are determined by some other label, and variables of the not yet determined neighbors, and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
+So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$.
+%and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or $x_e = \lambda(g)$, or $x_e > \lambda(g)$.
 This results in $O(k^2)! = k^{O(k^2)}$ guesses
@@
 In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
-Note that we know if the difference of two consecutive labels is positive or negative. 
-In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference between them is easy to determine,
-if one or both consecutive labels are not yet determined 
-then we have guessed in what kind of relation they are (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guessallPermutations}}}}).
-Therefore we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
+Note that we can determine if the difference of two consecutive labels is positive or negative. 
+In the case when two consecutive labels are determined with respect to the same label $\lambda(e)$ the difference between them is easy to determine.
+If consecutive labels are not determined with respect to the same label, both labels are considered undetermined and are assigned a variable for which we know in what kind of relation they are (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guessallPermutations}}}}).
+Therefore, we know when $\Delta$ has to be added, which implies that \cref{eq:FPT-equalityConstraint,eq:FPT-inequalityConstraint} are calculated correctly for all paths.
 
@@
 All of the above is enough to determine the labeling $\lambda$ of $G'$.
-Now we have to make sure that the labeling considers also the vertices of~$Z= V(G) \setminus V(G')$ that we initially removed from $G$.
-Recall that $Z$ consists of disjoint trees, and that each of these trees has a unique neighbor $u_i$ in $G'$. 
-Furthermore, recall that $T_i$ denotes the tree that is obtained by such a vertex $u_i$ of $G'$ and all the trees of $Z$ that are incident to $u_i$; then $u_i$ is the \emph{clip vertex} of the tree $T_i$.
-Moreover, for each of these trees~$T_{i}$ we have selected an arbitrary vertex $r_i \in Z$ that is a neighbor of the clip vertex $u_i$ in $T_i$, 
-and $r_i$ is called the \emph{representative vertex} of the tree $T_{u_i}$. 
-Let us now describe now how to determine the labels on the edges of any such tree $T_i$.
-To determine the correct label of all edges of $T_i$ we use the following property.
-\begin{lemma}
-Let $T_i$ be a tree having $u_i$ as its clip vertex, and let $e_i = (u_i,r_i)$. 
-Among all neighbors of $u_i$ in $G'$, let $v \in N_{G'}(u_i)$ be the one that is closest vertex to $r_i$ (with respect to the values of $D$), \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u_i)$.
-Then the path $P^*=(r_i,u_i,v)$ is the fastest temporal path from $r_i$ to $v$.
+Now we have to extend the labeling to consider also the vertices of~$Z= V(G) \setminus V(G')$ that we initially removed from $G$.
+From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by $Z$) consists of disjoint trees. 
+Each of these trees has a unique neighbor $u_i$ in $G'$. 
+Denote by $T_i$ the tree obtained by considering such a vertex $u_i$ and all the trees from $G[Z]$ that are incident to $u_i$. 
+We then refer to $u_i$ as the \emph{clip vertex} of the tree $T_i$.
+Recall that $G[Z]$ consists of disjoint trees and that each of these trees has a unique neighbor $u_i$ in $G'$.
+
+Before we describe how to determine the fastest temporal paths between any vertex from $Z$ and any other vertex in $G$,
+we prove the following.
+
+\begin{lemma}\label{lemma:ftp-tree-neighbor}
+Let $T_i$ be a tree with $u_i$ as its clip vertex and let $r_i \in V(T_i) \cap N_{T_i}(u_i)$ be an arbitrary vertex of $T_i$ that is a neighbor of $u_i$. 
+Now, among all neighbors of $u_i$ in $G'$ we chose the one that is the closest to $r_i$ with respect to the values of $D$. 
+In other words, we find $v \in N_{G'}(u_i)$ for which $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u_i)$.
+Then we have that the path $P^*=(r_i,u_i,v)$ is the fastest temporal path from $r_i$ to $v$.
 \end{lemma}
 \begin{proof}
-Suppose that this is not true.
-Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$,
-and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
-Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
+Suppose for the contradiction that there exists a path $P^*_2$ from $r_i$ to $v$ that is faster than $P^*=(r_i,u_i,v)$. 
+By the structure of $G$ it follows that $P^*_2$ passes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$ in $G'$), through a vertex $w \in N_{G'}(u_i) \setminus \{v \}$, 
+and through some other vertices $u_1, u_2, \dots, u_j$ in $G$ ($j \geq 0$), before it finishes in $v$.
+Therefore, $P^*_2= (r_i,u_i,w,u_1,u_2,\dots,u_j,v)$, and $d(P^*_2) \leq d(P^*)$.
 Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
@@
 \end{proof}
+Observe that determining a vertex $v$ closest to $r_i$ (with respect to the values of $D$) is a straightforward process.
+We only need to check the values in the $r_i$-th row of the matrix $D$.
+Therefore, this process takes linear time.
+%
 Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from the representative $r_i$ of $T_i$ to the vertex $v$ in the neighborhood of the clip vertex $v_i$ of $T_i$.
+$(r_i,u_i,v)$ is the fastest temporal path from $r_i$ in $T_i$ to the vertex $v$.
 Then
-we can determine the label of edge $r_i u_i$ as 
-$\lambda (r_i u_i) \equiv \lambda(u_i v) + 1 - D_{r_i,v} \pmod \Delta$.
-Now, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$.
-We repeat this procedure for all trees in $Z$.
-What remains, is to add the equality (resp.~inequality) constraints for the fastest (resp. non-fastest) temporal paths from vertices of $Z$ to all other vertices in $G'$ and vice versa.
-Note that since 
-there is a unique path between vertices of tree $T_i$, and since all edges of tree $T_i$ are determined with respect to the same label,
-we present the study for cases when we find the fastest temporal paths from and to the 
-representative vertex $r_i$ of tree $T_i$.
-Each of these paths is then uniquely extended to all vertices in $T_i$.
-
-\subparagraph{\boldmath Fastest paths from $z \in Z$ to $u \in U$.}
-Let $u\in U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
+we can determine the label of the edge $r_i u_i$ with respect to $\lambda(u_i v)$ (see \cref{obs:FirstLabelAndDuration}).\label{lemma:ftp-tree-neighbor}
+Furthermore, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$ with respect to the same label.
+Using the properties from the trees and similar arguing as in \cref{lemma:ftp-tree-neighbor} we get the following.
+\begin{observation}\label{obs:tree-only-neighbors}
+Let $T_i$ be a tree described as above, with $u_i$ being its clip vertex.
+Let $r_i, r_j$ be two vertices in $T_i$ where $r_i$ is a neighbor of $u_i$ and $r_j$ is a neighbor of $r_i$, and let $x \in V(G)\setminus \{r_i,r_j\}$ be an arbitrary vertex in $G$.
+Denote with
+$P_i$ and $P_j$ the underlying paths of the fastest temporal paths from $r_i$ and $r_j$ to $x$, respectively.
+Then $P_i$ and $P_j$ differ only in the edge $r_ir_j$, more specifically $P_j = \{r_ir_j\} \cup P_i$ or $P_i = \{r_i r_j \} \cup P_j$.
+\end{observation}
+Because of \cref{obs:tree-only-neighbors} in the upcoming analysis we focus only on the vertices of each tree $T_i$ that are neighbors of their corresponding clip vertex $u_i$. 
+All fastest temporal paths to and from all other tree vertices are then uniquely extended.
+From this point onward, whenever we refer to a vertex $r$ in the tree $T_i$ we actually mean the vertex $r$ that is a neighbor of the clip vertex of the tree $T_i$.
+
+We split our analysis into two cases.
+First, when the clip vertex of tree $T_i$ is not a vertex of interest
+and second when the clip vertex is also a vertex of interest in $G'$.
+During the process of determining the fastest paths from and to the vertices in $Z$, we use the fact that we have already identified the fastest paths among all vertices in $G'$.
+It's worth noting that finding the fastest path between two vertices from the same tree $T_i$ is trivial, so we exclude this case from our analysis.
+
+To efficiently determine the fastest temporal paths to and from the vertices from $Z$ we still need to show some extra properties.
+We start with a property for the case when the clip vertex of the tree $T_i$ is not a vertex of interest.
+\begin{lemma} \label{lemma:treeLabels-notInteresting}
+    Let $z \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{z\}]$, where $z \notin U$. 
+    Let $v_1$ and $v_2$ be the two neighbors of $z$ in $G'$.
+    Then the labels of the tree $T_i$ can be determined with respect to $\lambda(v_1 z)$ and $\lambda(z v_2)$.
+\end{lemma}
+%
+\begin{proof}
+    First observe that since $z$ is not a vertex of interest it must be a part of some segment $S_{u,w}$, where $u,v \in U$ and $z \neq u \neq v$. Therefore, $z$ is of degree $2$ in $G'$.
+    Let $r \in V(T_i)$ be a neighbor of $z$.
+    We observe the values $D_{r,v_1}, D_{r,v_2}$ and distinguish the following cases.
+
+    First, $D_{r,v_1} = D_{r,v_2}$
+    Then, using \cref{lemma:ftp-tree-neighbor} we get that the fastest paths from $r$ to $v_1$ and from $r$ to $v_2$ are of length two.
+    Moreover, we know that these two paths consist of the edge $rz$ and one of the edges $zv_1,zv_2$.
+    This allows us to determine the label of the edge $rz$ (and consequently all other edges of $T_i$) with respect to $\lambda(zv_1)$ (see \cref{obs:FirstLabelAndDuration}).
+
+    Second, $D_{r,v_1} \neq D_{r,v_2}$. 
+    Let us denote with $t_1 = \lambda(z v_1), t_2 = \lambda(z v_2)$ and $t_3 = \lambda(rz)$.
+    W.l.o.g. suppose $D_{r,v_1} > D_{r,v_2}$, which implies that $t_1 > t_2$ (the other case is analogous), and suppose that $t_1, t_2 > t_3$.
+    Now we claim that $D_{v_1,r} < D_{v_2,r}$.
+    Suppose for the contradiction that this is not true.
+Then $D_{v_2,r} < D_{v_1,r} \leq (\Delta + t_3 - t_1)$.
+This implies that the fastest temporal path from $v_2$ to $r$ cannot use the path $(v_1,z,r)$, and is therefore of form $(v_2,z,r)$.
+    By the definition, the duration of this path is then $D_{v_2,r} = \Delta + t_3 - t_2 + 1$.
+    But since $t_1 > t_2$ it follows that $(\Delta + t_3 - t_2) + 1 > (\Delta + t_3 - t_1) + 1$ and by the definition $D_{v_1,r} \leq > (\Delta + t_3 - t_1) + 1$. 
+    Therefore we get $D_{v_2,r} > D_{v_1,r} $, a contradiction.
+    All together, from $D_{r,v_1} > D_{r,v_2}$ we determine the label of edge $rz$ with respect to $\lambda(z v_2)$,
+    and from $D_{v_1,r} < D_{v_2,r}$ we determine the label of edge $rz$ with respect to $\lambda(z v_1)$.
+    %
+\end{proof}
+%
+In the case when the clip vertex of the tree $T_i$ is a vertex of interest we cannot determine the labeling of the tree with respect to the labels of all edges incident to the clip vertex.
+Therefore, to efficiently determine the fastest temporal paths from and to vertices of $T_i$ in this case we proceed as follows.
+We split the vertices of $T_i$ in a small number of equivalence classes (bounded in $k$) and guess the fastest temporal paths among a vertex in each equivalence class and all the vertices from $U \cup U^*$.
+With this, we can determine the fastest temporal between vertices in $Z$ and all other vertices in $G$.
+Let us start with describing how to create equivalence classes.
+
+Let $u \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{u\}]$, where $u \in U$. 
+We split the vertices of $T_i$ into (at most) $|N_{G'}(u)|$ equivalence classes using the following procedure.
+For a vertex $r_i \in V(T_i)$ we determine the vertex $w \in N_{G'}(u)$ that is on the smallest duration from $r_i$.
+In other words, we find the vertex $w$ such that for any other $w' \in N_{G'}(u)$ it holds $D_{r_1,w} \leq D_{r_1,w'}$.
+We then create an equivalence class $C_w$ and set $r_i \in C_w$.
+If there is another $w'' \in N_{G'}(u)$ for which $D_{r_1,w} = D_{r_1,w''}$ then $C_w = C_{w''}$.
+We repeat the above procedure for all trees $T_i$ and all their vertices.
+In the set $Z^*$ we collect a representative vertex from each of the equivalence classes.
+There are $O(k)$ vertices of interest, each with at most $k$ neighbors, therefore we create at most $O(k^2)$ equivalence classes, which implies $|Z^*| \in O(k^2)$.
+Note that creating all equivalence classes takes linear time, since for any tree vertex we check the values in the matrix $D$ for the corresponding vertices exactly once.
+
+Let us now show the following important property of equivalence classes.
+\begin{lemma}\label{lemma:treeEquivClass-intVertices}
+    Let $u \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{u\}]$, where $u \in U$,
+    and let $r_i,r_2 \in V(T_i)$ be in the same equivalence class.
+    Then, the fastest temporal paths from $r_1$ and $r_2$ to any other vertex in $G$ coincide on the vertices of $V(G) \setminus V(T_i)$.
+    Similarly, it holds for the fastest temporal paths from any other vertex in $G$ to $r_1$ and $r_2$.
+\end{lemma}
+%
+\begin{proof}
+    Let $y \neq u$ be a vertex in $V(G')$.
+    %
+    Denote with $P_1$ the underlying path of the fastest temporal path from $r_1$ to $y$, which consists of the edge $r_1 u$ and the path $P$ from $u$ to $y$.
+    Similarly, let $Q_2$ be the underlying path of the fastest temporal path from $r_2$ to $y$, consisting of the edge $r_2u$ together with the path $Q$ from $u$ to $y$.
+    Define $P_2$ as the second path from $r_2$ to $y$ that first uses the edge $r_1u$ and then the path $P$.
+    Similarly, $Q_1$ represents the second path from $r_1$ to $y$ that first uses the edge $r_2u$ and then the path $Q$.
+    Our objective is to demonstrate that either $P = Q$ or that $d(P_1, \lambda) = d(Q_1, \lambda)$ (and $d(P_2, \lambda) = d(Q_2, \lambda)$).
+    This implies that $r_1$ and $r_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_i)$ to reach $y$.
+
+    Let us set the label of the edge $r_1u$ to $t_1$, the label of $r_2u$ to $t_2$, the label of the last edge of the path $P$ as $t_p$ and the label of the last edge of the path $Q$ as $t_q$.
+    By the definition, since $P_1$ represents the fastest temporal paths form $r_1$ to $y$ we get that
+        $D_{r_1,y} = t_p - t_1 + c_p \Delta$, where $c_p \in \mathbb{N}$.
+    Similarly, for the path $Q_2$ it holds that $D_{r_2,y} = t_q - t_2 + c_q \Delta$ with $c_q \in \mathbb{N}$.
+    Note that since $r_1$ and $r_2$ are in the same equivalence class, it holds that the first label of $P$ and the first label of $Q$ have to be bigger than $t_1,t_2$.
+Meaning that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
+    or the difference (with at least one $t_1,t_2$) is $\Delta$ if and only if the first label of $P$ and the first label of $Q$ are the same. 
+    This observation is crucial in our arguing below.
+
+    We want to first show that $c_p = c_q$.
+    Let us assume, for the sake of contradiction, that this is not the case, and suppose that $c_p > c_q$ (the case with $c_q > c_p$ is analogous).
+    Then $c_p \leq c_q + 1$.
+    Now, since $r_1$ and $r_2$ are in the same equivalence class and by the definition of the duration of a temporal path we get that $d(P_2, \lambda) = t_p - t_2 + c_p \Delta \leq t_p - t_2 + (c_q - 1)\Delta$.
+    Because $Q_2$ is the fastest path from $r_2$ to $y$ we have also that $d(P_2, \lambda) \geq D_{r_2,y}$, which gives us $t_p - t_2 + (c_q - 1) \Delta \geq t_q - t_2 + c_q \Delta$.
+    This is equivalent to $t_p \geq t_q + \Delta$, but since $t_p, t_q \in \Delta$ this cannot happen.
+    Therefore, we conclude that $c_p = c_q$.
+
+    Now, we want to show also, that $t_p = t_q$.
+    Let us assume, for the sake of contradiction, that this is not the case, and suppose that $t_p > t_q$ (the case with $t_q > t_p$ is analogous).
+    Then the duration of the path $Q_1$ is $d(Q_1,\lambda) = t_q - t_1 + c_q \Delta$ since $c_q = c_p$.
+    Above we proved that $c_p = c_q$.
+We also know that $d(Q_1,\lambda) \geq d(P_1,\lambda)$ as $P_1$ is the fastest path from $r_1$ to $y$.
+All of this results in $t_q - t_1 + c_p \Delta \geq t_p - t_1 + c_p \Delta$ implying $t_q \geq t_p$, a contradiction.
+    Therefore, $t_p = t_q$.
+
+    We proved that either $P$ and $Q$ are the same, or if they are different then $P_1$ and $Q_1$ are of the same duration and are both fastest paths from $r_1$ to $y$ (the same holds for $r_2$).
+
+    Proof for the fastest temporal paths in the other direction, namely starting at $y$ and reaching $r_1$ and $r_2$, is done analogously.
+\end{proof}
+From the above lemma we conclude that determining the fastest temporal path from any vertex within an equivalence class $C_w$ of $T_i$ to a given vertex $y \in V(G)$ requires only knowledge of the fastest temporal path $P^w_y$ from any vertex $r \in C_w$ to $y$.
+For all other vertices in $C_w$ to $y$, the fastest temporal paths share identical vertices and edges as $P^w_y$ outside the tree $T_i$.
+Within the tree $T_i$, there is a unique way in which the path is extended from these vertices.
+The same holds for the temporal paths from $y$ to vertices in $C_w$.
+We are now ready to describe our last guess.
+\begin{enumerate}[G-1.]
+\setcounter{enumi}{\value{guesscounter}}
+
+\item \label{FPT-guessFTPtreesEquivalence}
+    We guess the fastest temporal paths between all pairs of vertices of $Z^*$ and $U,U^*,Z^*$.
+    Since $Z^*$ is of size $O(k^2)$ and $U \cup U^* \cup Z^*$ is of size $O(k^2)$ 
+    we introduce $k^{O(k^5)}$ guesses.
+\end{enumerate}
+%
+Now we are ready to explain how we determine the fastest temporal paths for all the vertices in $Z$
+
+\subparagraph{\boldmath Fastest paths from $z \in Z$ to $y \in U \cup U^*$.}
+Let $x \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{x\}]$ with $z \in V(T_i)$.
 We distinguish the following two cases.
 \begin{enumerate}[(i)]
-    \item \label{FPT:z-u-clipnotU}
-    The clip vertex $x$ of the tree $T_i$ is not a vertex of interest.
-    Let $x = z_i$ be a part of a segment $S_{w,z} = (w = z_1, z_2, \dots, z_r = z)$, and denote with $z_{i-1}$ and $z_{i+1}$ the neighboring vertices of $x$, 
-    where $z_{i-1}$ is closer to $w$ in $S_{w,z}$ and 
-    $z_{i+1}$ is closer to $z$ in $S_{w,z}$.
-    From guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}} we know the following fastest paths $z_{2} \rightarrow w \leadsto u$ and %%%TBD
-    $z_{r-1} \rightarrow z \leadsto u$.
-    Denote thew with $Q_1$ and $Q_r$ respectively.
-    There are two options.
-    \begin{enumerate}[(a)]
-        \item The segment $S_{w,z}$ is of length at least $5$ and has no not yet determined edges, with the exception of the first/last one.
-        Which results in knowing all the waiting times at vertices of $S_{w,z}$ when traversing the segment.
-        Then we also know that the labels of tree $T_i$ edges are determined with respect to that same edge label.
-        This results in knowing the value of waiting time
-        $\tau_x^{r_i,z_{i-1}}$ at vertex $x$ when traversing it from $r_i$ to $z_{i-1}$ and 
-        the value of waiting time $\tau_x^{r_i,z_{i+1}}$ at vertex $x$
-        when traversing it from $r_i$ to $z_{i+1}$.
-        We also know the value $D_{x,u}$ and the underlying path of the fastest temporal path from $x$ to $u$ (which we determined in previous steps).
-        W.l.o.g. suppose that the fastest path from $x$ to $u$ goes through $z_{i-1}$ and uses the path $Q_1$.
-        Denote with $P^{-} = (r_i, x, z_{i-1}, z_2) \cup Q_1$
-        and with $P^{+} = (r_i, x, z_{i+1}, z_{r-1}) \cup Q_r$.
-        Then we calculate the duration $d(P^{-})$ as $d(P^{-}) = D_{x,u} + \tau_x^{r_i,z_i-1}$
-        and compare it to $D_{r_i,u}$.
-        If $d(P^{-}) < D_{r_i,u} $ then we stop with the calculation and determine that our input graph has no solution.
-        If $d(P^{-}) = D_{r_i,u} $ then we know that $P^{-}$ is the underlying path of the fastest temporal path from $r_i$ to $u$. 
-        If $d(P^{-}) > D_{r_i,u} $ then the fastest temporal path from $r_i$ to $u$ has to be $P^{+}$.
-        For the fastest temporal path we introduce the equality constraint, 
-        for all other paths we introduce the inequality constraints.
-        By similar arguing as in cases above, we introduce $k^{O(k)}$ inequality constraints.
-        \item The segment $S_{w,z}$ is of length $4$ or less
-        and has an extra not yet determined edge $p$. 
-        If $p \cap \{x\} = \emptyset$, 
-        we can proceed with the same approach as above.
-        So suppose now that $p = x z_{i+1}$.  
-        Then, from knowing that $p$ is a not yet determined edge we conclude that
-        all fastest temporal paths from $x$ to any vertex of interest $u'$ go through the edge $z_{i-1}x$, not trough $p$ 
-        (this is true as if a fastest temporal path from $x$ to some vertex of interest $w'$ went through $p$, then $p$ would be determined).
-        Now, if the edges of tree are determined with respect to the label of the edge $z_{i-1}x$ (not $p$),
-        we use the same approach as above to determine the fastest temporal path from $r_i$ to $u$.
-        Therefore, suppose that the edges of the tree $T_i$ are determined with respect to the label of the edge $p$.
-        Which means that $D_{r_i, z_{i+1}} < D_{r_i, z_{i-1}}$.
-        We want to now determine if the fastest temporal path from $r_i$ to $u$ is of the form 
-        $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$ or
-        $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.
-        We do the following.
-        Denote with $c$ the value $c = D_{r_i z_{i-1}} + D_{x u} + 1$.
-        We now claim the following, note that we do not know what is the fastest temporal path from $r_i$ to $x_{i-1}$. 
-        It can be of the form $P^- = (r_i,x,z_{i-1})$,
-        or of the form $P^+ = (r_i,x, z_{i+1}, z_{i+2}, \dots, z) \cup Q \cup (w, z_2, \dots, z_{i-1})$, where $Q$ is some path from $z$ to $w$.
-        Denote with $R^x$ the underlying path of the fastest temporal path from $x$ to $u$,
-        and with $R^{i-1}$ the underlying path of a fastest temporal path from $z_{i-1}$ to $u$.
-        Note $R^{i-1} \subseteq R^x$.
-        Similarly,
-        denote with $R^{i+1}$ the underlying path of the fastest temporal path from $z_{i+1}$ to $u$, 
-        for which we know it goes through the vertex $z$.
-        \begin{itemize}
-            \item  If $c < D_{r_i,u}$, then we have a contradiction and we stop with the calculation.\\
-            This is true since we have found a temporal path from $r_i$ to $u$, with faster duration than the fastest temporal path from $r_i$ to $u$,
-            which cannot happen.
-            \item  If $c = D_{r_i,u}$, then 
-            the fastest temporal path is of the form $r_i \rightarrow x \rightarrow z_{i-1} \rightarrow \dots \rightarrow w \leadsto u$.\\
-            We have two options, first when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we have determined that $P^- \cup R^{i-1}$ is the fastest temporal path from $r_i$ to $u$.
-            In the second case we suppose that the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^+$.
-            But then the duration of the path $P^+ \cup R^{i-1}$ from $r_i$ to $u$ equals the duration of the fastest path from $r_i$ to $u$.
-But note that $P^+ \cup R^{i-1}$ is actually not a path but a walk, since there is repetition of edges between $w$ and $z_{i-1}$,
-            therefore it includes a path from $r_i$ to $u$, which is even faster,
-            a contradiction.
-            Therefore we get that in this case $P^-$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-            And the fastest path from $r_i$ to $z_{i-1}$ is $P^- \cup R^{i-1}$.
-            \item If $c > D_{r_i,u}$, then 
-            the fastest temporal path is of the form $r_i \rightarrow x \rightarrow z_{i+1} \rightarrow \dots \rightarrow z \leadsto u$.\\
-            We again have two options.
-            First when the fastest temporal path from $r_i$ to $z_{i-1}$ is $P^-$.
-            In this case we easily deduce that $P^- \cup R^{i-1}$ is not the underlying path of the fastest temporal path from $r_i$ to $u$.
-            And therefore it follows that the the underlying path of the fastest temporal path from $r_i$ to $u$ is  $(r_i, x, z_{i+1}) \cup R^{i+1}$.
-            In the second case, suppose that $P^+$ is the underlying path of the fastest temporal path from $x_i$ to $z_{i-1}$.
-            We want to now prove that the fastest temporal path from $r_i$ to $u$ travels through vertices $z_{i+1}, z_{i+2}, \dots z$.
-            Suppose for the contradiction that this is not true. 
-            Then $S = (r_i, x, z_{i-1}) \cup R^{i-1}$ is the underlying path of the fastest temporal path from $r_i$ to $u$.
-            Then we get that the duration $d(S)$ of $S$ equals to $D_{r_i,u}$.
-            Let $D(r_i,z_{i-1},S)$ be the duration of the temporal path from $r_i$ to $z_{i-1}$ along the path $S$.
-            By the definition we get that $d(S) = D(r_i,z_{i-1},S) + D_{x,u} - 1$.
-            From this it follows that $D(r_i,z_{i-1},S) = D_{r_i, z_{i-1}}$, which is in contradiction with our assumption.
-            Therefore we get that in this case 
-            $(r_i, x, z_{i+1}) \cup R^{i+1}$ is always the underlying path of the fastest path from $r_i$ to $z_{i-1}$.
-        \end{itemize}
-       In all of the cases, we have uniquely determined the underlying path of the fastest temporal path from $r_i$ to $u$,
-       which gives us an equality constraint.
-       For all other $k^{O(k)}$ paths we add the inequality constraints. 
+    \item \label{FPT:clipInU-1}
+    The clip vertex $x =u \in U$ is a vertex of interest.
+    From guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPtreesEquivalence}}}} we determine the fastest temporal path from $z$ to $y$.
+    \item \label{FPT:clipNotInU-1}
+    The clip vertex $x \in U$ is not a vertex of interest. Then $x = v_j$ is a part of some segment $S_{u,v} = \{u=v_1, v_2, \dots, v_p = v)$, where $j \neq 1 \neq p$.
+    Then all the labels of the tree $T_i$ are determined with respect to the label $\lambda(v_{j-1}v_j)$ and with respect to the label $\lambda(v_{j}v_{j+1})$ (see~\cref{lemma:treeLabels-notInteresting}).
+    From the calculations above and the performed guesses we know the exact structure (\ie the sequence of vertices and edges) of the following paths:
+    \begin{itemize}
+        \item path $P_{xy}^*$ which is the fastest temporal path from the vertex $x$ to the vertex $y$,
+        \item path $P_{xy}^u$ which is the fastest temporal path from the vertex $x$ to the vertex $y$, that passes through the vertex $u$,
+        \item path $P_{xy}^v$ which is the fastest temporal path from the vertex $x$ to the vertex $y$, that passes through the vertex $v$.
+    \end{itemize}
+    Note that $P_{xy}^*$ is either equal to the path $P_{xy}^u$ or to the path $P_{xy}^v$.
+    To be precise, from the guesses performed we know the structure of the fastest path from $v_2$ through $u$ to any other vertex of interest, and any other neighbor of the vertex of interest, which can be easily (uniquely) extended to start from $x=v_i$
+    (see~guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}} and
+    \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
+
+    Before we proceed note also that since the labels of the tree are determined with respect to the label of the edge $v_{i-1}v_i$ and $v_{i}v_{i+1}$ we can determine the difference 
+    $|\lambda(v_{i-1} x) - \lambda (z x)|$ and $|\lambda(xv_{i+1}) - \lambda (z x)|$.
+    %
+    Suppose now that $P_{xy}^* = P_{xy}^u$.
+    We calculate the value $c = D_{x,y} + |\lambda(v_{i-1} x) - \lambda (z x)|$ and compare it to $D_{z,y}$.
+    There are three options.
+    First $c = D_{z,y}$, in this case the fastest temporal path from $z$ to $y$ uses first the edge $zx$ and then continues to $y$ using the edges and vertices of $P_{xy}^*$.
+    Second $c > D_{z,y}$, in this case the fastest temporal path from $z$ to $y$ uses first the edge $zx$ and then continues to $y$ using the vertices and edges of $P_{xy}^v$.
+    Third $c < D_{z,y}$, in this case we stop the calculation and return an empty solution, as it cannot happen that a temporal path has a smaller duration than the corresponding value in the matrix $D$.
+%
 \end{enumerate}
-
-    \item The clip vertex $w$ of the tree $T_i$ is a vertex of interest.
-    In this case we know exactly the fastest path from a representative vertex $r_i$ to $u$
-    (we determined it in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
-    We create an equality constraint for this path,
-    and create inequality constraints for all other paths.
-    Since there are $k^{O(k)}$ possible paths from $w$ to $u$, and there is a unique path (edge) from $r_i$ to $w$,
-    we create $k^{O(k)}$ inequality constraints.
-\end{enumerate}
-
-\subparagraph{\boldmath Fastest path from $u \in U$ to $z \in Z$.}
-Let $u\in U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
-In this case we split again the analysis in two cases.
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-    In this case
-we know the fastest paths from $u$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $u$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$).
-\item The clip vertex of $T_i$ is a vertex of interest.
-    In this case
-we know exactly what is the fastest path (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.
-
-\subparagraph{\boldmath Fastest path from $z \in Z$ to $y \in V(G') \setminus U$.}
-Let $y \in V(G') \setminus U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
-%%%We now want to determine the fastest temporal path from a representative vertex $r_i$ in $T_i$, to some vertex $y \in V(G') \setminus U$ that is not a vertex of interest, and vice versa.
-Since $y$ is not a vertex of interest it holds that $y \in S_{u,v}=(u = v_1, v_2, \dots, v_p = v)$. %Let $y = v_j \in S_{u,v} \setminus\{u,v\}$.
-We use the similar approach as in the above case, when we were determining paths between vertices in $Z$ and $U$, 
-to determine the fastest temporal path from $r_i$ to $y$. 
-The difference in this case is that 
-we know the fastest temporal path from the clip vertex of $T_i$ to $y$
-(when the clip vertex is not a vertex of interest),
-or we know the exact fastest path from the representative $r_i$ of $T_i$ to $y$
-(when the clip vertex is a vertex of interest).
-The latter follows from the guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.\\
-%
-Since $y \in S_{u,v}$ there are $k^{O(k)}$ paths from the clip vertex to $y$, when the clip vertex is not a vertex of interest,
-and $k^{O(k)}$ paths from the clip vertex to $y$, when the clip vertex is a vertex of interest.
-In all of the cases, we can uniquely determine the underlying path of the fastest temporal path from $r_i$ to $y$, which gives us an equality constraint.
-For all other paths we add the inequality constraints.
-
-\subparagraph{\boldmath Fastest path from $y \in V(G') \setminus U$ to $z \in Z$.}
-Let $y \in V(G') \setminus U$ and $z\in Z$. Then $z$ belongs to a tree $T_i$, and let $r_i$ be the representative of $T_i$. 
-In this case we split again the analysis in two cases. 
-\begin{itemize}
-    \item The clip vertex $x \in S_{w,z}$ of $T_i$ is not a vertex of interest.
-In this case we
-know the fastest paths from $y$ to $x$, and to both of its neighbors $x_{i}$ and $x_{j}$, on the segment $S_{w,z}$,
-which is enough to determine the exact fastest path from $x$ to $r_i$ 
-(we use the same procedure as in the case~\ref{FPT:z-u-clipnotU} when determining the fastest paths from $x$ to $u$). 
-    \item The clip vertex $u_i$ of $T_i$ is a vertex of interest.
-Let $y \in S_{u,v} = (u = v_1,v_2, \dots, v_p = v)$.
-In this case we know the fastest paths from $v_2$ and $v_{p-1}$ to $r_i$ (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
-Since the path from $y$ to $v_2$ (resp.~$v_{p-1}$) is uniquely extended, 
-we use the same procedure as in the 
-case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-to determine which is the fastest path from $y$ to $r_i$.
-\end{itemize}
-The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.
-
-\subparagraph{\boldmath Fastest paths between $z,z'$ where $z \in Z$ and $z' \in Z$.}
-Let $z,z'\in Z$, and let $z$ (resp.~$z'$) belong to the tree $T_i$ (resp.~$T_j$).
-Let $r_i, r_j$ be representative vertices and let $w_i, w_j$ be the clip vertices of the trees $T_i$ and $T_j$, respectively.
-We distinguish following cases.
-\begin{itemize}
-    \item  Both clip vertices $w_i,w_j$ are vertices of interest.
-    In this case $r_i, r_j \in Z^*$
-    and therefore we know the fastest paths between them (see guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
-    \item One clip vertex is a vertex of interest and the other is not.
-    Let $w_i \in U$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$.
-    We know the fastest paths from the representative $r_i$ of tree $T_i$,
-    to vertices $w_{j-1},w_j,w_{j+1}$ 
-    (we determined them in the above case 
-    when we were determining the fastest paths from $z \in Z$ to $y \in V(G')\setminus U$).
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-    \item None of the clip vertices $w_i, w_j$ is a vertex of interest.
-    Let $w_i \in S_{w,z}$ and $w_j \in S_{u,v} \setminus \{u,v\}$.
-    Denote with $w_{j-1}$ and $w_{j+1}$ the two neighbors of $w_j \in S_{u,v}$,
-    and 
-    similarly with 
-    $w_{i-1}$ and $w_{i+1}$ the two neighbors of $w_i \in S_{w,z}$.
-    We know all the fastest paths from
-    $r_i$ to $w_{j-1},w_j,w_{j+1}$,
-    and similarly all fastest paths 
-    from $r_j$ to $w_{i-1},w_i,w_{i+1}$,
-    together with all the fastest paths between 
-    each pair of the following vertices
-    $w_{j-1},w_j,w_{j+1} w_{i-1},w_i,w_{i+1}$.
-
-    Now we use the same procedure as in
-    the case~\ref{FPT:z-u-clipnotU}, when determining the fastest paths from $x$ to $u$,
-    to determine the exact fastest path from $r_i$ to $r_j$.
-\end{itemize}
+In both cases, we introduce the equality constraint for the determined fastest temporal path and inequality constraint for all the other $k^{O(k)}$ paths.
+
+\subparagraph{\boldmath Fastest paths from $z \in Z$ to $y \in V(G) \setminus (U \cup U^*)$.}
+The proof in this case is similar to the one above.
+We still split the analysis into two parts, one where the clip vertex $x$ of a tree $T_i$ that includes $z$ is in $U$ and one where it is not in $U$.
+The difference is that in some cases we need to also extend the ending part of the path (which can be done uniquely, using the same arguments as in the previous case).
+
+Once we determine the fastest temporal path from $z$ to $y$ we introduce an equality constraint for it, and for all other $k^{O(k)}$ paths we introduce the inequality constraints.
+
 The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.

### 2024-01-14 SAND2024/SAND24-longversion.tex
working on proof changes

@@
 
-%From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by $Z$) consists of disjoint trees.
-Each of these trees has a unique neighbor $u_i$ in $G'$.
-Denote by $T_i$ the tree obtained by considering such a vertex $u_i$ and all the trees from $G[Z]$ that are incident to $u_i$.
-We then refer to $u_i$ as the \emph{clip vertex} of the tree $T_i$.
+From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by $Z$) consists of disjoint trees. 
+Each of these trees has a unique neighbor $v$ in $G'$. 
+Denote by $T_v$ the tree obtained by considering such a vertex $v$ and all the trees from $G[Z]$ that are incident to $v$ in $G$. 
+We then refer to $v$ as the \emph{clip vertex} of the tree $T_v$.
+In the case $v$ is a vertex of interest we define also the set $Z^*_v$ of \emph{representative vertices} of $T_v$, as follows.
+
+\noindent
+We first create an empty set $C_w$ for every vertex $w$ that is a neighbor of $u$ in $G'$.
+We then iterate through every vertex $r$ that is in the first layer of the tree $T_v$ (\ie vertex that is a direct child from the root $v$), we check the matrix $D$ and find the vertex $w \in N_{G'}(v)$ that is on the shortest duration from $r$.
+In other words, for a $r \in N_{T_v}(v)$ we find $w \in N_{G'}(v)$ such that $D_{r,w} \leq D_{r,w'}$ for all $w' \in  N_{G'}(v)$.
+%
+We add vertex $r$ to $C_w$.
+In the case when there exist another $w'' \in  N_{G'}(v) $ for which $D_{r,w''} = D_{r,w}$, we add $r$ also to the set $C_{w''}$. In fact, in this case $C_{w''} = C_w$.
+At the end we create $|N_{G'}(v)|$ sets $C_w$, containing all vertices of the first layer of $T_v$.
+We call these sets \emph{equivalence classes} of the tree $T_v$.
+Now, from each equivalence class $C_w$ we chose an arbitrary vertex $r_w$ and put it into the set $Z^*_v$.
+%
+We repeat the above procedure for all trees $T_u$ with the clip vertex $u$ from $U$, and define $Z^*$ as 
+$$Z^* = \bigcup\limits_{u \in U} Z^*_u.$$
+%
+Since $|U| \in O(k)$ and for each $u$ it holds $|N(u)| \in O(k)$, we get that $|Z^*| \in O(k^2)$. 
+%For every vertex in the first layer of the tree $T_u$, where $u \in U$, we check the corresponding values in the matrix $D$ exactly once. Therefore, $Z^*$ is determined in linear time.
 
 Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
-For an illustration see \cref{fig:labelingVertices}. Note that determining sets $U$ and $U^*$ takes linear time.
+For an illustration see \cref{fig:labelingVertices}. Note that determining sets $U, U^*$ and $Z^*$ takes linear time.
 
@@
 
-For every pair of important vertices $u,v \in U \cup U^{\ast} \cup Z^{\ast}$, we guess the sequence of edges in the fastest temporal path from $u$ to $v$.
+%For every pair of important vertices $u,v \in U \cup U^{\ast} \cup Z^{\ast}$, we guess the sequence of edges in the fastest temporal path from $u$ to $v$.
 Since $U \cup U^{\ast} \cup Z^{\ast}\in O(k^2)$ and there are $k^{O(k)}$ possibilities for a sequence of edges between a fixed vertex pair, we have $k^{O(k^5)}$ overall possible guesses.
+We start by guessing the following.
 \begin{enumerate}[G-1.]
@@
     The fastest temporal paths between all pairs of vertices in $Z^*$, 
-    which by similar arguing as for vertices in $U$, gives us $k^{O(k^3)}$ guesses.
+    which by similar arguing as for vertices in $U$, gives us $k^{O(k^5)}$ guesses.
     \item \label{FPT-guessFTPamongUstar}
@@
     and vice versa.
-    This gives us $k^{O(k^3)}$ guesses.
+    This gives us $k^{O(k^4)}$ guesses.
     \item \label{FPT-guessFTPamongUstarandZstar}
@@
     and vice versa.
-    This gives us $k^{O(k^4)}$ guesses.
+    This gives us $k^{O(k^5)}$ guesses.
 	\setcounter{guesscounter}{\value{enumi}}
@@
 \begin{proof}
-    For an easier understanding and better readability, we present the proof for $S_{u,v}$ of fixed length $5$.
+    For an easier understanding and better readability, we present the proof for $S_{u,v}$ of length $5$.
     The case where $S_{u,v}$ is longer easily follows from the presented results.
@@
     Let $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5, v_6=v)$.
-    We distinguish two cases, first that $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
-    and the second that  $f = v_3v_4$.
+    We distinguish two cases, first when $f = v_2v_3$ (note that the case with $f = v_4v_5$ is symmetrical),
+    and the second when  $f = v_3v_4$.
     Throughout the proof we denote with $t_i$ the label of edge $v_i v_{i+1}$.
@@
 \end{proof}
+
+We now present some properties that involve the vertices from $Z$, that form the trees in $G[Z]$.
+\begin{lemma}\label{lemma:ftp-tree-neighbor}
+Let $v \in V(G')$ be a clip vertex of the tree $T_v$ in $G[Z \cup \{v\}]$, and let $r_i \in N_{T_v}(v)$ be an arbitrary vertex of $T_v$ that is a neighbor (child) of $v$. 
+Among all neighbors of $v$ in $G'$ let $w$ be the one that is on the smallest duration away from $r_i$ with respect to the values of $D$. 
+In other words, $w \in N_{G'}(v)$ such that $D_{r_i,w} \leq D_{r_i,w'}$ for all $w' \in N_{G'}(v)$.
+Then, the path $P^*=(r_i,v,w)$ represents the fastest temporal path from $r_i$ to $w$.
+%
+Moreover, all labels of the tree $T_v$ are determined with respect to the label $\lambda(vw)$.
+\end{lemma}
+\begin{proof}
+Suppose for contradiction that there exists a path $P^*_2$ from $r_i$ to $w$ that is faster than $P^*=(r_i,v,w)$. 
+By the structure of $G$, it follows that $P^*_2$ passes through the clip vertex $v$ of $T_v$ (as this is the only neighbor of $r_i$ in $G'$), continues through a vertex $w' \in N_{G'}(v) \setminus \{w \}$,
+and through some other vertices $u_1, u_2, \dots, u_j$ in $G$ ($j \geq 0$) before finishing in $w$.
+Therefore, $P^*_2= (r_i,v,w',u_1,u_2,\dots,u_j,w)$, and $d(P^*_2,\lambda) \leq d(P^*,\lambda)$.
+Now, since $D_{r_i,w} \leq D_{r_i,w'}$ for all $ w' \in N_{G'}(v)$ the first part of path $P^*_2$ from $r_i$ to $w'$ takes at least $D_{r_i,w}$ time.
+Since $w \neq w'$, we need at least one more time-step (one more edge) to traverse from $w'$ to reach $w$. 
+Therefore, $d(P^*_2, \lambda) \geq D_{r_i,w} + 1$ which implies that $P^*$ is a faster temporal path than $P^*_2$.
+
+For the second part, knowing that the duration of $P^*$ is $D_{r_i,w}$ we can determine the label of the edge $r_i v$ with respect to the label $\lambda(vw)$ (see \cref{obs:FirstLabelAndDuration}).
+Furthermore, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we can now determine labels on all edges of $T_v$ with respect to the same label $\lambda(v w)$.
+\end{proof}
+
+\begin{lemma} \label{lemma:treeLabels-notInteresting}
+    Let $z \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{z\}]$, where $z \notin U$. 
+    Let $v_1$ and $v_2$ be the two neighbors of $z$ in $G'$.
+    Then the labels of the tree $T_i$ can be determined with respect to $\lambda(v_1 z)$ and $\lambda(z v_2)$.
+\end{lemma}
+%
+\begin{proof}
+    First observe that since $z$ is not a vertex of interest it must be a part of some segment $S_{u,w}$, where $u,v \in U$ and $z \neq u \neq v$. Therefore, $z$ is of degree $2$ in $G'$.
+    Let $r \in V(T_i)$ be a neighbor of $z$.
+    We observe the values $D_{r,v_1}, D_{r,v_2}$ and distinguish the following cases.
+
+    First, $D_{r,v_1} = D_{r,v_2}$
+    Then, using \cref{lemma:ftp-tree-neighbor} we get that the fastest paths from $r$ to $v_1$ and from $r$ to $v_2$ are of length two.
+    Moreover, we know that these two paths consist of the edge $rz$ and one of the edges $zv_1,zv_2$.
+    This allows us to determine the label of the edge $rz$ (and consequently all other edges of $T_i$) with respect to $\lambda(zv_1)$ (see \cref{obs:FirstLabelAndDuration}).
+
+    Second, $D_{r,v_1} \neq D_{r,v_2}$. 
+    Let us denote with $t_1 = \lambda(z v_1), t_2 = \lambda(z v_2)$ and $t_3 = \lambda(rz)$.
+    W.l.o.g. suppose $D_{r,v_1} > D_{r,v_2}$, which implies that $t_1 > t_2$ (the other case is analogous), and suppose that $t_1, t_2 > t_3$.
+    Now we claim that $D_{v_1,r} < D_{v_2,r}$.
+    Suppose for the contradiction that this is not true.
+Then $D_{v_2,r} < D_{v_1,r} \leq (\Delta + t_3 - t_1)$.
+This implies that the fastest temporal path from $v_2$ to $r$ cannot use the path $(v_1,z,r)$, and is therefore of form $(v_2,z,r)$.
+    By the definition, the duration of this path is then $D_{v_2,r} = \Delta + t_3 - t_2 + 1$.
+    But since $t_1 > t_2$ it follows that $(\Delta + t_3 - t_2) + 1 > (\Delta + t_3 - t_1) + 1$ and by the definition $D_{v_1,r} \leq > (\Delta + t_3 - t_1) + 1$. 
+    Therefore we get $D_{v_2,r} > D_{v_1,r} $, a contradiction.
+    All together, from $D_{r,v_1} > D_{r,v_2}$ we determine the label of edge $rz$ with respect to $\lambda(z v_2)$,
+    and from $D_{v_1,r} < D_{v_2,r}$ we determine the label of edge $rz$ with respect to $\lambda(z v_1)$.
+    %
+\end{proof}
+
+%%%% TODO NKL some description of equivalence classes
+Let us now show the following important property of equivalence classes.
+\begin{lemma}\label{lemma:treeEquivClass-intVertices}
+    Let $u \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{u\}]$, where $u \in U$,
+    and let $r_i,r_2 \in V(T_i)$ be in the same equivalence class of the tree $T_i$.
+    Then, the fastest temporal paths from $r_1$ and $r_2$ to any other vertex in $G$ coincide on the vertices of $V(G) \setminus V(T_i)$.
+    Similarly, it holds for the fastest temporal paths from any other vertex in $G$ to $r_1$ and $r_2$.
+\end{lemma}
+%
+\begin{proof}
+    Let $y \neq u$ be a vertex in $V(G')$.
+    %
+    Denote with $P_1$ the underlying path of the fastest temporal path from $r_1$ to $y$, which consists of the edge $r_1 u$ and the path $P$ from $u$ to $y$.
+    Similarly, let $Q_2$ be the underlying path of the fastest temporal path from $r_2$ to $y$, consisting of the edge $r_2u$ together with the path $Q$ from $u$ to $y$.
+    Define $P_2$ as the second path from $r_2$ to $y$ that first uses the edge $r_1u$ and then the path $P$.
+    Similarly, $Q_1$ represents the second path from $r_1$ to $y$ that first uses the edge $r_2u$ and then the path $Q$.
+    Our objective is to demonstrate that either $P = Q$ or that $d(P_1, \lambda) = d(Q_1, \lambda)$ (and $d(P_2, \lambda) = d(Q_2, \lambda)$).
+    This implies that $r_1$ and $r_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_i)$ to reach $y$.
+
+    Let us set the label of the edge $r_1u$ to $t_1$, the label of $r_2u$ to $t_2$, the label of the last edge of the path $P$ as $t_p$ and the label of the last edge of the path $Q$ as $t_q$.
+    By the definition, since $P_1$ represents the fastest temporal paths form $r_1$ to $y$ we get that
+        $D_{r_1,y} = t_p - t_1 + c_p \Delta$, where $c_p \in \mathbb{N}$.
+    Similarly, for the path $Q_2$ it holds that $D_{r_2,y} = t_q - t_2 + c_q \Delta$ with $c_q \in \mathbb{N}$.
+    Note that since $r_1$ and $r_2$ are in the same equivalence class, it holds that the first label of $P$ and the first label of $Q$ have to be bigger than $t_1,t_2$.
+Meaning that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
+    or the difference (with at least one $t_1,t_2$) is $\Delta$ if and only if the first label of $P$ and the first label of $Q$ are the same. 
+    This observation is crucial in our arguing below.
+
+    We want to first show that $c_p = c_q$.
+    Let us assume, for the sake of contradiction, that this is not the case, and suppose that $c_p > c_q$ (the case with $c_q > c_p$ is analogous).
+    Then $c_p \leq c_q + 1$.
+    Now, since $r_1$ and $r_2$ are in the same equivalence class and by the definition of the duration of a temporal path we get that $d(P_2, \lambda) = t_p - t_2 + c_p \Delta \leq t_p - t_2 + (c_q - 1)\Delta$.
+    Because $Q_2$ is the fastest path from $r_2$ to $y$ we have also that $d(P_2, \lambda) \geq D_{r_2,y}$, which gives us $t_p - t_2 + (c_q - 1) \Delta \geq t_q - t_2 + c_q \Delta$.
+    This is equivalent to $t_p \geq t_q + \Delta$, but since $t_p, t_q \in \Delta$ this cannot happen.
+    Therefore, we conclude that $c_p = c_q$.
+
+    Now, we want to show also, that $t_p = t_q$.
+    Let us assume, for the sake of contradiction, that this is not the case, and suppose that $t_p > t_q$ (the case with $t_q > t_p$ is analogous).
+    Then the duration of the path $Q_1$ is $d(Q_1,\lambda) = t_q - t_1 + c_q \Delta$ since $c_q = c_p$.
+    Above we proved that $c_p = c_q$.
+We also know that $d(Q_1,\lambda) \geq d(P_1,\lambda)$ as $P_1$ is the fastest path from $r_1$ to $y$.
+All of this results in $t_q - t_1 + c_p \Delta \geq t_p - t_1 + c_p \Delta$ implying $t_q \geq t_p$, a contradiction.
+    Therefore, $t_p = t_q$.
+
+    We proved that either $P$ and $Q$ are the same, or if they are different then $P_1$ and $Q_1$ are of the same duration and are both fastest paths from $r_1$ to $y$ (the same holds for $r_2$).
+
+    Proof for the fastest temporal paths in the other direction, namely starting at $y$ and reaching $r_1$ and $r_2$, is done analogously.
+\end{proof}
+
+\begin{observation}\label{obs:tree-only-neighbors}
+Let $v \in V(G')$ be a clip vertex of the tree $T_v$ in $G[Z \cup \{v\}]$,
+$r_i \in N_{T_v}(v)$ be a child of $v$ in the tree $T_v$, and let $r_j$ be a descendant of $r_i$ in the tree $T_v$.
+In other words, $r_i$ is a vertex on the first level of the tree $T_v$, while $r_j$ is a vertex in a subtree of $T_v$, that is rooted at $r_i$.
+Define $Q$ as the (unique) path between $r_i$ and $r_j$ in $T_v$.
+Let $x \in V(G)\setminus V(T_v)$ be an arbitrary vertex in $G$.
+Denote with
+$P_i$ and $P_j$ the underlying paths of the fastest temporal paths from $r_i$ and $r_j$ to $x$, respectively.
+Then $P_i$ and $P_j$ differ only in the edges and vertices of $Q$.
+\end{observation}
+The correctness from the above observation is a consequence of \cref{lemma:treeEquivClass-intVertices} and the fact that $P_i$ and $P_j$ leave the tree $T_i$ using the same edge $r_ix$.
+
+%%%
+%%%
 
@@
 Now we have to extend the labeling to consider also the vertices of~$Z= V(G) \setminus V(G')$ that we initially removed from $G$.
-From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by $Z$) consists of disjoint trees. 
-Each of these trees has a unique neighbor $u_i$ in $G'$. 
-Denote by $T_i$ the tree obtained by considering such a vertex $u_i$ and all the trees from $G[Z]$ that are incident to $u_i$. 
-We then refer to $u_i$ as the \emph{clip vertex} of the tree $T_i$.
-Recall that $G[Z]$ consists of disjoint trees and that each of these trees has a unique neighbor $u_i$ in $G'$.
-
-Before we describe how to determine the fastest temporal paths between any vertex from $Z$ and any other vertex in $G$,
-we prove the following.
-
-\begin{lemma}\label{lemma:ftp-tree-neighbor}
-Let $T_i$ be a tree with $u_i$ as its clip vertex and let $r_i \in V(T_i) \cap N_{T_i}(u_i)$ be an arbitrary vertex of $T_i$ that is a neighbor of $u_i$. 
-Now, among all neighbors of $u_i$ in $G'$ we chose the one that is the closest to $r_i$ with respect to the values of $D$. 
-In other words, we find $v \in N_{G'}(u_i)$ for which $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u_i)$.
-Then we have that the path $P^*=(r_i,u_i,v)$ is the fastest temporal path from $r_i$ to $v$.
-\end{lemma}
-\begin{proof}
-Suppose for the contradiction that there exists a path $P^*_2$ from $r_i$ to $v$ that is faster than $P^*=(r_i,u_i,v)$. 
-By the structure of $G$ it follows that $P^*_2$ passes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$ in $G'$), through a vertex $w \in N_{G'}(u_i) \setminus \{v \}$, 
-and through some other vertices $u_1, u_2, \dots, u_j$ in $G$ ($j \geq 0$), before it finishes in $v$.
-Therefore, $P^*_2= (r_i,u_i,w,u_1,u_2,\dots,u_j,v)$, and $d(P^*_2) \leq d(P^*)$.
-Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
-Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
-So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
-\end{proof}
-Observe that determining a vertex $v$ closest to $r_i$ (with respect to the values of $D$) is a straightforward process.
-We only need to check the values in the $r_i$-th row of the matrix $D$.
-Therefore, this process takes linear time.
-%
-Suppose now that we know that 
-$(r_i,u_i,v)$ is the fastest temporal path from $r_i$ in $T_i$ to the vertex $v$.
-Then
-we can determine the label of the edge $r_i u_i$ with respect to $\lambda(u_i v)$ (see \cref{obs:FirstLabelAndDuration}).\label{lemma:ftp-tree-neighbor}
-Furthermore, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we determine labels on all edges of $T_i$ with respect to the same label.
-Using the properties from the trees and similar arguing as in \cref{lemma:ftp-tree-neighbor} we get the following.
-\begin{observation}\label{obs:tree-only-neighbors}
-Let $T_i$ be a tree described as above, with $u_i$ being its clip vertex.
-Let $r_i, r_j$ be two vertices in $T_i$ where $r_i$ is a neighbor of $u_i$ and $r_j$ is a neighbor of $r_i$, and let $x \in V(G)\setminus \{r_i,r_j\}$ be an arbitrary vertex in $G$.
-Denote with
-$P_i$ and $P_j$ the underlying paths of the fastest temporal paths from $r_i$ and $r_j$ to $x$, respectively.
-Then $P_i$ and $P_j$ differ only in the edge $r_ir_j$, more specifically $P_j = \{r_ir_j\} \cup P_i$ or $P_i = \{r_i r_j \} \cup P_j$.
-\end{observation}
+%
+Recall that $G[Z]$ consists of disjoint trees and that each of these trees has a unique neighbor (clip vertex) $v$ in $G'$. 
+%
+Now we are ready to explain how we determine the fastest temporal paths for all the vertices in $Z$
+
+%%% TODO NKL
 Because of \cref{obs:tree-only-neighbors} in the upcoming analysis we focus only on the vertices of each tree $T_i$ that are neighbors of their corresponding clip vertex $u_i$. 
@@
 We start with a property for the case when the clip vertex of the tree $T_i$ is not a vertex of interest.
-\begin{lemma} \label{lemma:treeLabels-notInteresting}
-    Let $z \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{z\}]$, where $z \notin U$. 
-    Let $v_1$ and $v_2$ be the two neighbors of $z$ in $G'$.
-    Then the labels of the tree $T_i$ can be determined with respect to $\lambda(v_1 z)$ and $\lambda(z v_2)$.
-\end{lemma}
-%
-\begin{proof}
-    First observe that since $z$ is not a vertex of interest it must be a part of some segment $S_{u,w}$, where $u,v \in U$ and $z \neq u \neq v$. Therefore, $z$ is of degree $2$ in $G'$.
-    Let $r \in V(T_i)$ be a neighbor of $z$.
-    We observe the values $D_{r,v_1}, D_{r,v_2}$ and distinguish the following cases.
-
-    First, $D_{r,v_1} = D_{r,v_2}$
-    Then, using \cref{lemma:ftp-tree-neighbor} we get that the fastest paths from $r$ to $v_1$ and from $r$ to $v_2$ are of length two.
-    Moreover, we know that these two paths consist of the edge $rz$ and one of the edges $zv_1,zv_2$.
-    This allows us to determine the label of the edge $rz$ (and consequently all other edges of $T_i$) with respect to $\lambda(zv_1)$ (see \cref{obs:FirstLabelAndDuration}).
-
-    Second, $D_{r,v_1} \neq D_{r,v_2}$. 
-    Let us denote with $t_1 = \lambda(z v_1), t_2 = \lambda(z v_2)$ and $t_3 = \lambda(rz)$.
-    W.l.o.g. suppose $D_{r,v_1} > D_{r,v_2}$, which implies that $t_1 > t_2$ (the other case is analogous), and suppose that $t_1, t_2 > t_3$.
-    Now we claim that $D_{v_1,r} < D_{v_2,r}$.
-    Suppose for the contradiction that this is not true.
-Then $D_{v_2,r} < D_{v_1,r} \leq (\Delta + t_3 - t_1)$.
-This implies that the fastest temporal path from $v_2$ to $r$ cannot use the path $(v_1,z,r)$, and is therefore of form $(v_2,z,r)$.
-    By the definition, the duration of this path is then $D_{v_2,r} = \Delta + t_3 - t_2 + 1$.
-    But since $t_1 > t_2$ it follows that $(\Delta + t_3 - t_2) + 1 > (\Delta + t_3 - t_1) + 1$ and by the definition $D_{v_1,r} \leq > (\Delta + t_3 - t_1) + 1$. 
-    Therefore we get $D_{v_2,r} > D_{v_1,r} $, a contradiction.
-    All together, from $D_{r,v_1} > D_{r,v_2}$ we determine the label of edge $rz$ with respect to $\lambda(z v_2)$,
-    and from $D_{v_1,r} < D_{v_2,r}$ we determine the label of edge $rz$ with respect to $\lambda(z v_1)$.
-    %
-\end{proof}
-%
+
 In the case when the clip vertex of the tree $T_i$ is a vertex of interest we cannot determine the labeling of the tree with respect to the labels of all edges incident to the clip vertex.
@@
 
-Let $u \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{u\}]$, where $u \in U$. 
-We split the vertices of $T_i$ into (at most) $|N_{G'}(u)|$ equivalence classes using the following procedure.
-For a vertex $r_i \in V(T_i)$ we determine the vertex $w \in N_{G'}(u)$ that is on the smallest duration from $r_i$.
-In other words, we find the vertex $w$ such that for any other $w' \in N_{G'}(u)$ it holds $D_{r_1,w} \leq D_{r_1,w'}$.
-We then create an equivalence class $C_w$ and set $r_i \in C_w$.
-If there is another $w'' \in N_{G'}(u)$ for which $D_{r_1,w} = D_{r_1,w''}$ then $C_w = C_{w''}$.
-We repeat the above procedure for all trees $T_i$ and all their vertices.
-In the set $Z^*$ we collect a representative vertex from each of the equivalence classes.
-There are $O(k)$ vertices of interest, each with at most $k$ neighbors, therefore we create at most $O(k^2)$ equivalence classes, which implies $|Z^*| \in O(k^2)$.
-Note that creating all equivalence classes takes linear time, since for any tree vertex we check the values in the matrix $D$ for the corresponding vertices exactly once.
-
-Let us now show the following important property of equivalence classes.
-\begin{lemma}\label{lemma:treeEquivClass-intVertices}
-    Let $u \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{u\}]$, where $u \in U$,
-    and let $r_i,r_2 \in V(T_i)$ be in the same equivalence class.
-    Then, the fastest temporal paths from $r_1$ and $r_2$ to any other vertex in $G$ coincide on the vertices of $V(G) \setminus V(T_i)$.
-    Similarly, it holds for the fastest temporal paths from any other vertex in $G$ to $r_1$ and $r_2$.
-\end{lemma}
-%
-\begin{proof}
-    Let $y \neq u$ be a vertex in $V(G')$.
-    %
-    Denote with $P_1$ the underlying path of the fastest temporal path from $r_1$ to $y$, which consists of the edge $r_1 u$ and the path $P$ from $u$ to $y$.
-    Similarly, let $Q_2$ be the underlying path of the fastest temporal path from $r_2$ to $y$, consisting of the edge $r_2u$ together with the path $Q$ from $u$ to $y$.
-    Define $P_2$ as the second path from $r_2$ to $y$ that first uses the edge $r_1u$ and then the path $P$.
-    Similarly, $Q_1$ represents the second path from $r_1$ to $y$ that first uses the edge $r_2u$ and then the path $Q$.
-    Our objective is to demonstrate that either $P = Q$ or that $d(P_1, \lambda) = d(Q_1, \lambda)$ (and $d(P_2, \lambda) = d(Q_2, \lambda)$).
-    This implies that $r_1$ and $r_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_i)$ to reach $y$.
-
-    Let us set the label of the edge $r_1u$ to $t_1$, the label of $r_2u$ to $t_2$, the label of the last edge of the path $P$ as $t_p$ and the label of the last edge of the path $Q$ as $t_q$.
-    By the definition, since $P_1$ represents the fastest temporal paths form $r_1$ to $y$ we get that
-        $D_{r_1,y} = t_p - t_1 + c_p \Delta$, where $c_p \in \mathbb{N}$.
-    Similarly, for the path $Q_2$ it holds that $D_{r_2,y} = t_q - t_2 + c_q \Delta$ with $c_q \in \mathbb{N}$.
-    Note that since $r_1$ and $r_2$ are in the same equivalence class, it holds that the first label of $P$ and the first label of $Q$ have to be bigger than $t_1,t_2$.
-Meaning that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
-    or the difference (with at least one $t_1,t_2$) is $\Delta$ if and only if the first label of $P$ and the first label of $Q$ are the same. 
-    This observation is crucial in our arguing below.
-
-    We want to first show that $c_p = c_q$.
-    Let us assume, for the sake of contradiction, that this is not the case, and suppose that $c_p > c_q$ (the case with $c_q > c_p$ is analogous).
-    Then $c_p \leq c_q + 1$.
-    Now, since $r_1$ and $r_2$ are in the same equivalence class and by the definition of the duration of a temporal path we get that $d(P_2, \lambda) = t_p - t_2 + c_p \Delta \leq t_p - t_2 + (c_q - 1)\Delta$.
-    Because $Q_2$ is the fastest path from $r_2$ to $y$ we have also that $d(P_2, \lambda) \geq D_{r_2,y}$, which gives us $t_p - t_2 + (c_q - 1) \Delta \geq t_q - t_2 + c_q \Delta$.
-    This is equivalent to $t_p \geq t_q + \Delta$, but since $t_p, t_q \in \Delta$ this cannot happen.
-    Therefore, we conclude that $c_p = c_q$.
-
-    Now, we want to show also, that $t_p = t_q$.
-    Let us assume, for the sake of contradiction, that this is not the case, and suppose that $t_p > t_q$ (the case with $t_q > t_p$ is analogous).
-    Then the duration of the path $Q_1$ is $d(Q_1,\lambda) = t_q - t_1 + c_q \Delta$ since $c_q = c_p$.
-    Above we proved that $c_p = c_q$.
-We also know that $d(Q_1,\lambda) \geq d(P_1,\lambda)$ as $P_1$ is the fastest path from $r_1$ to $y$.
-All of this results in $t_q - t_1 + c_p \Delta \geq t_p - t_1 + c_p \Delta$ implying $t_q \geq t_p$, a contradiction.
-    Therefore, $t_p = t_q$.
-
-    We proved that either $P$ and $Q$ are the same, or if they are different then $P_1$ and $Q_1$ are of the same duration and are both fastest paths from $r_1$ to $y$ (the same holds for $r_2$).
-
-    Proof for the fastest temporal paths in the other direction, namely starting at $y$ and reaching $r_1$ and $r_2$, is done analogously.
-\end{proof}
-From the above lemma we conclude that determining the fastest temporal path from any vertex within an equivalence class $C_w$ of $T_i$ to a given vertex $y \in V(G)$ requires only knowledge of the fastest temporal path $P^w_y$ from any vertex $r \in C_w$ to $y$.
+From \cref{lemma:treeEquivClass-intVertices}, we conclude that determining the fastest temporal path from any vertex within an equivalence class $C_w$ of $T_i$ to a given vertex $y \in V(G)$ requires only knowledge of the fastest temporal path $P^w_y$ from any vertex $r \in C_w$ to $y$.
 For all other vertices in $C_w$ to $y$, the fastest temporal paths share identical vertices and edges as $P^w_y$ outside the tree $T_i$.
@@
 The same holds for the temporal paths from $y$ to vertices in $C_w$.
-We are now ready to describe our last guess.
-\begin{enumerate}[G-1.]
-\setcounter{enumi}{\value{guesscounter}}
-
-\item \label{FPT-guessFTPtreesEquivalence}
-    We guess the fastest temporal paths between all pairs of vertices of $Z^*$ and $U,U^*,Z^*$.
-    Since $Z^*$ is of size $O(k^2)$ and $U \cup U^* \cup Z^*$ is of size $O(k^2)$ 
-    we introduce $k^{O(k^5)}$ guesses.
-\end{enumerate}
-%
-Now we are ready to explain how we determine the fastest temporal paths for all the vertices in $Z$
+
+%%% TODO NKL
 
@@
 Therefore, if there is an instance with a positive solution, then this instance gives rise to the desired labeling, as it satisfies all of the constraints.
-For the other direction we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
-Since we consider all configurations, one of the produced ILP instances will correspond the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
+For the other direction, we can observe that if there is a labeling $\lambda$ meeting all duration requirements specified by $D$, then this labeling produces a specific configuration of fastest temporal paths.
+Since we consider all configurations, one of the produced ILP instances will correspond to the configuration implicitly defined by $\lambda$, and hence our algorithm finds a solution.
 

### 2024-01-17 SAND2024/SAND24-longversion.tex
changing how we guess fastest temporal paths (added observation that all segments are determined if they are of length at least 4)

@@
 In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of~$G$; see \cref{fig:periodic-example} for an illustration. 
-When it is clear from the context, we drop $\Delta$ form the notation and 
+When it is clear from the context, we drop $\Delta$ from the notation and 
 we denote the ($\Delta$-periodic) temporal graph by $(G,\lambda)$.
@@
     \item between any pair of vertices $v_i$ and $v_j$ in the tree $T$, there is a \emph{unique} path $P$ in $T$ from $v_i$ to $v_j$, and 
-    \item in any periodic temporal graph $(T,\lambda,\Delta)$ and any fastest temporal path $P=((e_1,t_1),\ldots,(e_i,t_i),\ldots,(e_j,t_j),\ldots,(e_\ell,t_\ell))$ from $v_1$ to $v_{\ell}$ we have that the sub-path $P'=((e_i,t_i),\ldots,(e_j,t_j))$ is also a fastest temporal path from $v_i$ to $v_j$.
+    \item in any periodic temporal graph $(T,\lambda,\Delta)$ and any fastest temporal path $P=((e_1,t_1),\ldots,(e_i,t_i),\ldots,(e_j,t_j),\ldots,(e_{\ell-1},t_{\ell-1}))$ from $v_1$ to $v_{\ell}$ we have that the sub-path $P'=((e_i,t_i),\ldots,(e_{j-1},t_{j-1}))$ is also a fastest temporal path from $v_i$ to $v_j$.
 \end{itemize}
@@
 We then refer to $v$ as the \emph{clip vertex} of the tree $T_v$.
-In the case $v$ is a vertex of interest we define also the set $Z^*_v$ of \emph{representative vertices} of $T_v$, as follows.
+In the case where $v$ is a vertex of interest we define also the set $Z^*_v$ of \emph{representative vertices} of $T_v$, as follows.
 
@@
 We first create an empty set $C_w$ for every vertex $w$ that is a neighbor of $u$ in $G'$.
-We then iterate through every vertex $r$ that is in the first layer of the tree $T_v$ (\ie vertex that is a direct child from the root $v$), we check the matrix $D$ and find the vertex $w \in N_{G'}(v)$ that is on the shortest duration from $r$.
-In other words, for a $r \in N_{T_v}(v)$ we find $w \in N_{G'}(v)$ such that $D_{r,w} \leq D_{r,w'}$ for all $w' \in  N_{G'}(v)$.
+We then iterate through every vertex $r$ that is in the first layer of the tree $T_v$ (\ie vertex that is a child of the root $v$ in the tree $T_v$), check the matrix $D$ and find the vertex $w \in N_{G'}(v)$ that is on the smallest duration from $r$.
+In other words, for an $r \in N_{T_v}(v)$ we find $w \in N_{G'}(v)$ such that $D_{r,w} \leq D_{r,w'}$ for all $w' \in  N_{G'}(v)$.
 %
 We add vertex $r$ to $C_w$.
-In the case when there exist another $w'' \in  N_{G'}(v) $ for which $D_{r,w''} = D_{r,w}$, we add $r$ also to the set $C_{w''}$. In fact, in this case $C_{w''} = C_w$.
-At the end we create $|N_{G'}(v)|$ sets $C_w$, containing all vertices of the first layer of $T_v$.
-We call these sets \emph{equivalence classes} of the tree $T_v$.
-Now, from each equivalence class $C_w$ we chose an arbitrary vertex $r_w$ and put it into the set $Z^*_v$.
+In the case when there exists also another vertex $w' \in  N_{G'}(v) $ for which $D_{r,w'} = D_{r,w}$, we add $r$ also to the set $C_{w'}$. In fact, in this case $C_{w'} = C_w$.
+At the end we create $|N_{G'}(v)|=O(k)$ sets $C_w$, whose union contains all children of $v$ in $T_v$. 
+For every two sets $C_w$ and $C_{w'}$, where $w,w'\in N_{G'}(v)$, we have that either $C_w = C_{w'}$, or $C_w \cap C_{w'} = \emptyset$. 
+We call each of these sets $\{C_w : w \in N_{G'}(v)\}$ an \emph{equivalence class} of the tree $T_v$. 
+Now, from each equivalence class $C_w$ we choose an arbitrary vertex $r_w$ and put it into the set $Z^*_v$.
 %
 We repeat the above procedure for all trees $T_u$ with the clip vertex $u$ from $U$, and define $Z^*$ as 
-$$Z^* = \bigcup\limits_{u \in U} Z^*_u.$$
-%
-Since $|U| \in O(k)$ and for each $u$ it holds $|N(u)| \in O(k)$, we get that $|Z^*| \in O(k^2)$. 
+\begin{equation}
+    Z^* = \bigcup\limits_{v \in U} Z^*_v.
+\end{equation}
+%
+Since $|U| \in O(k)$ and for each $u \in U$ it holds $|N_{G'}(u)| = O(k)$, we get that $|Z^*| \in O(k^2)$. 
 %For every vertex in the first layer of the tree $T_u$, where $u \in U$, we check the corresponding values in the matrix $D$ exactly once. Therefore, $Z^*$ is determined in linear time. 
-
 Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
@@
 %Let us remember the following basic property of the problem \deltaExact.
-Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$.
+Recall that a labeling $\lambda$ of $G$ satisfies $D$ if the duration of a fastest temporal path from each vertex $v_i$ to each other vertex $v_j$ equals $D_{v_i, v_j}$.
 %, and no other temporal path from $v_i$ to $v_j$ is faster.
@@
     Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
-    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
+    A path $P = (u=v_1,v_2, \dots, v_p = v)$  with at least two edges in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
+    is called a \emph{segment} from $u$ to $v$, which we denote as $S_{u,v}$.
 \end{definition}
@@
 If there are two, then one has to be of length $1$, just a single edge, and the second one of length at least $2$.
-Note from \cref{def:segments} that $S_{u,v} \neq S_{v,u}$ since we consider paths to be directed. It's also worth emphasizing that $S_{v,u}$ is essentially the reversed path of $S_{u,v}$.
+Note from \cref{def:segments} that $S_{u,v} \neq S_{v,u}$ since we consider paths to be directed. It is also worth emphasizing that $S_{v,u}$ is essentially the reverse path of $S_{u,v}$.
 Furthermore, it's important to observe that a temporal path in $G'$ between two vertices of interest is either a segment or consists of a sequence of segments.
@@
 Let $u,v,x$ be three vertices in $G'$.
-We write $u \leadsto x \rightarrow v$ to denote a temporal path from $u$ to $v$ that passes through $x$, and then goes directly to $v$ (via one edge).
-If there is an edge (\ie a unique fastest path) between two vertices, we denote it by $\rightarrow$,
-if the fastest path between two vertices is not uniquely determined, we denote it by $\leadsto$.
-
+We write $u \leadsto x \rightarrow v$ to denote a temporal path from $u$ to $v$ that passes through $x$, and then goes directly to $v$ (via one edge or a unique path in $G'$).
+In other words, if the fastest path between two vertices is not uniquely determined we denote it by $\leadsto$, while if it is unique we denote it by $\rightarrow$.
+%
 %For every pair of important vertices $u,v \in U \cup U^{\ast} \cup Z^{\ast}$, we guess the sequence of edges in the fastest temporal path from $u$ to $v$.
 Since $U \cup U^{\ast} \cup Z^{\ast}\in O(k^2)$ and there are $k^{O(k)}$ possibilities for a sequence of edges between a fixed vertex pair, we have $k^{O(k^5)}$ overall possible guesses.
-We start by guessing the following.
+We guess the following paths.
 \begin{enumerate}[G-1.]
@@
 With the information provided by the described guesses we are still not able to determine all fastest paths. For example consider the case depicted in \cref{fig:guesses-advanced}. 
-Therefore we introduce additional guesses that provide us with sufficient information to determine all fastest paths.
+Therefore, we introduce additional guesses that provide us with sufficient information to determine all fastest paths.
 We guess the following structures.
@@
 
-We now present some properties that involve the vertices from $Z$, that form the trees in $G[Z]$.
+We now present some properties involving the vertices from $Z$, that form the trees in~$G[Z]$.
 \begin{lemma}\label{lemma:ftp-tree-neighbor}
-Let $v \in V(G')$ be a clip vertex of the tree $T_v$ in $G[Z \cup \{v\}]$, and let $r_i \in N_{T_v}(v)$ be an arbitrary vertex of $T_v$ that is a neighbor (child) of $v$. 
-Among all neighbors of $v$ in $G'$ let $w$ be the one that is on the smallest duration away from $r_i$ with respect to the values of $D$. 
-In other words, $w \in N_{G'}(v)$ such that $D_{r_i,w} \leq D_{r_i,w'}$ for all $w' \in N_{G'}(v)$.
-Then, the path $P^*=(r_i,v,w)$ represents the fastest temporal path from $r_i$ to $w$.
-%
-Moreover, all labels of the tree $T_v$ are determined with respect to the label $\lambda(vw)$.
+Let $v \in V(G')$ be a clip vertex of the tree $T_v$ in $G[Z \cup \{v\}]$, and let $z \in N_{T_v}(v)$ be an arbitrary child of $v$ in $T_v$. 
+Among all neighbors of $v$ in $G'$, let $w$ be the one that is on the smallest duration away from $z$ with respect to the values of $D$. 
+In other words, $w \in N_{G'}(v)$ such that $D_{z,w} \leq D_{z,w'}$ for all $w' \in N_{G'}(v)$.
+Then, the path $P^*=(z,v,w)$ represents the unique fastest temporal path from $z$ to $w$.
+%
+Moreover, we can determine all labels of the tree $T_v$ with respect to the label $\lambda(vw)$.
 \end{lemma}
 \begin{proof}
-Suppose for contradiction that there exists a path $P^*_2$ from $r_i$ to $w$ that is faster than $P^*=(r_i,v,w)$. 
-By the structure of $G$, it follows that $P^*_2$ passes through the clip vertex $v$ of $T_v$ (as this is the only neighbor of $r_i$ in $G'$), continues through a vertex $w' \in N_{G'}(v) \setminus \{w \}$,
+Suppose for contradiction that there exists a path $P^{**} \neq P^*$ from $z$ to $w$ such that $d(P^{**},\lambda) \leq d(P^*,\lambda)$. 
+By the structure of $G$, it follows that $P^{**}$ passes through the clip vertex $v$ of $T_v$ (as this is the only neighbor of $z$ in $G'$), continues through a vertex $w' \in N_{G'}(v) \setminus \{w \}$,
 and through some other vertices $u_1, u_2, \dots, u_j$ in $G$ ($j \geq 0$) before finishing in $w$.
-Therefore, $P^*_2= (r_i,v,w',u_1,u_2,\dots,u_j,w)$, and $d(P^*_2,\lambda) \leq d(P^*,\lambda)$.
-Now, since $D_{r_i,w} \leq D_{r_i,w'}$ for all $ w' \in N_{G'}(v)$ the first part of path $P^*_2$ from $r_i$ to $w'$ takes at least $D_{r_i,w}$ time.
+Therefore, $P^{**}= (z,v,w',u_1,u_2,\dots,u_j,w)$.
+Now, since $D_{z,w} \leq D_{z,w'}$ by assumption, the first part of $P^{**}$ from $z$ to $w'$ takes at least $D_{z,w'}$ time, and thus it takes at least $D_{z,w}$ time.
 Since $w \neq w'$, we need at least one more time-step (one more edge) to traverse from $w'$ to reach $w$. 
-Therefore, $d(P^*_2, \lambda) \geq D_{r_i,w} + 1$ which implies that $P^*$ is a faster temporal path than $P^*_2$.
-
-For the second part, knowing that the duration of $P^*$ is $D_{r_i,w}$ we can determine the label of the edge $r_i v$ with respect to the label $\lambda(vw)$ (see \cref{obs:FirstLabelAndDuration}).
-Furthermore, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we can now determine labels on all edges of $T_v$ with respect to the same label $\lambda(v w)$.
+Therefore, $d(P^{**}, \lambda) \geq D_{z,w} + 1$ 
+which implies that $P^{**}$ is not the fastest temporal path from $z$ to $w$. Therefore, the only fastest temporal path from $z$ to $w$ is $P^*=(z,v,w)$.
+
+For the second part, knowing that the duration of $P^*$ is $D_{z,w}$, we can determine the label of the edge $z v$ with respect to the label $\lambda(vw)$ (see \cref{obs:FirstLabelAndDuration}).
+Furthermore, using the algorithm for trees (see \cref{thm:deltaExact-PolyTimeTrees}), we can now determine all the labels on the edges of $T_v$ with respect to the same label $\lambda(v w)$.
 \end{proof}
@@
 \begin{lemma} \label{lemma:treeLabels-notInteresting}
-    Let $z \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{z\}]$, where $z \notin U$. 
-    Let $v_1$ and $v_2$ be the two neighbors of $z$ in $G'$.
-    Then the labels of the tree $T_i$ can be determined with respect to $\lambda(v_1 z)$ and $\lambda(z v_2)$.
+    Let $x \in V(G')$ be a clip vertex of the tree $T_x$ in $G[Z \cup \{x\}]$, where $x \notin U$. 
+    Let $v_1$ and $v_2$ be the two neighbors of $x$ in $G'$.
+    Then the labels of the tree $T_x$ can be determined with respect to $\lambda(v_1 x)$ and $\lambda(x v_2)$.
 \end{lemma}
@@
 \begin{proof}
-    First observe that since $z$ is not a vertex of interest it must be a part of some segment $S_{u,w}$, where $u,v \in U$ and $z \neq u \neq v$. Therefore, $z$ is of degree $2$ in $G'$.
-    Let $r \in V(T_i)$ be a neighbor of $z$.
-    We observe the values $D_{r,v_1}, D_{r,v_2}$ and distinguish the following cases.
-
-    First, $D_{r,v_1} = D_{r,v_2}$
-    Then, using \cref{lemma:ftp-tree-neighbor} we get that the fastest paths from $r$ to $v_1$ and from $r$ to $v_2$ are of length two.
-    Moreover, we know that these two paths consist of the edge $rz$ and one of the edges $zv_1,zv_2$.
-    This allows us to determine the label of the edge $rz$ (and consequently all other edges of $T_i$) with respect to $\lambda(zv_1)$ (see \cref{obs:FirstLabelAndDuration}).
-
-    Second, $D_{r,v_1} \neq D_{r,v_2}$. 
-    Let us denote with $t_1 = \lambda(z v_1), t_2 = \lambda(z v_2)$ and $t_3 = \lambda(rz)$.
-    W.l.o.g. suppose $D_{r,v_1} > D_{r,v_2}$, which implies that $t_1 > t_2$ (the other case is analogous), and suppose that $t_1, t_2 > t_3$.
-    Now we claim that $D_{v_1,r} < D_{v_2,r}$.
-    Suppose for the contradiction that this is not true.
-Then $D_{v_2,r} < D_{v_1,r} \leq (\Delta + t_3 - t_1)$.
-This implies that the fastest temporal path from $v_2$ to $r$ cannot use the path $(v_1,z,r)$, and is therefore of form $(v_2,z,r)$.
-    By the definition, the duration of this path is then $D_{v_2,r} = \Delta + t_3 - t_2 + 1$.
-    But since $t_1 > t_2$ it follows that $(\Delta + t_3 - t_2) + 1 > (\Delta + t_3 - t_1) + 1$ and by the definition $D_{v_1,r} \leq > (\Delta + t_3 - t_1) + 1$. 
-    Therefore we get $D_{v_2,r} > D_{v_1,r} $, a contradiction.
-    All together, from $D_{r,v_1} > D_{r,v_2}$ we determine the label of edge $rz$ with respect to $\lambda(z v_2)$,
-    and from $D_{v_1,r} < D_{v_2,r}$ we determine the label of edge $rz$ with respect to $\lambda(z v_1)$.
+    First observe that since $x$ is not a vertex of interest it must be a part of some segment $S_{u,w}$, where $u,v \in U$ and $x \neq u \neq v$. Therefore, $x$ is of degree $2$ in $G'$.
+    Let $z \in V(T_x)$ be a child of $x$ in $T_x$, \ie a vertex in the first layer of the tree $T_x$.
+    We observe the values $D_{z,v_1}, D_{z,v_2}$ and distinguish the following cases.
+
+    First, $D_{z,v_1} = D_{z,v_2}$
+    Then, using \cref{lemma:ftp-tree-neighbor} we conclude that the fastest temporal paths from $z$ to $v_1$ and from $z$ to $v_2$ are of length two.
+    We know that these two paths consist of the edge $zx$ and $xv_1,xv_2$, respectively.
+    This allows us to determine the label of the edge $zx$ (and consequently all other edges of $T_x$) with respect to $\lambda(xv_1)$ and $\lambda(xv_2)$.
+
+    Second, $D_{z,v_1} \neq D_{z,v_2}$. 
+    Let us denote with $t_1 = \lambda(x v_1), t_2 = \lambda(x v_2)$ and $t_3 = \lambda(zx)$.
+    W.l.o.g. suppose that $\min \{t_1,t_2,t_3\} = t_3$, and that $D_{z,v_1} > D_{z,v_2}$ (the other case is analogous). It follows that $t_1 > t_2$.
+    We want to now prove that the inequality $D_{v_1,z} < D_{v_2,z}$ holds.
+    Suppose for the contradiction that the inequality is false.
+Then $D_{v_2,z} < D_{v_1,z} \leq (\Delta + t_3 - t_1)$.
+This implies that the fastest temporal path from $v_2$ to $z$ cannot use the path $(v_1,x,z)$, and is therefore of form $(v_2,x,z)$.
+    By the definition, the duration of this path is $D_{v_2,z} = \Delta + t_3 - t_2 + 1$.
+    But since $t_1 > t_2$ it follows that $(\Delta + t_3 - t_2) + 1 > (\Delta + t_3 - t_1) + 1$.  We also know that $D_{v_1,z} \leq  (\Delta + t_3 - t_1) + 1$. 
+    This implies that $D_{v_2,z} > D_{v_1,z} $, a contradiction.\\
+    Knowing $D_{z,v_1} > D_{z,v_2}$ we can determine the label of edge $zx$ (and consequently all other edges of $T_x$) with respect to $\lambda(x v_2)$,
+    and similarly knowing $D_{v_1,z} < D_{v_2,z}$ we determine the label of edge $zx$ (and all other edges of $T_x$) with respect to $\lambda(x v_1)$.
     %
@@
 
-%%%% TODO NKL some description of equivalence classes
-Let us now show the following important property of equivalence classes.
+Remember, in the case where the clip vertex $u$ of the tree $T_u$ in $G[Z \cup \{u\}]$ is a vertex of interest, we split the vertices in the first layer of $T_u$ into at most $|N_{G'}(u)|$ equivalence classes.
+Let us now show the following important property of these equivalence classes.
 \begin{lemma}\label{lemma:treeEquivClass-intVertices}
-    Let $u \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{u\}]$, where $u \in U$,
-    and let $r_i,r_2 \in V(T_i)$ be in the same equivalence class of the tree $T_i$.
-    Then, the fastest temporal paths from $r_1$ and $r_2$ to any other vertex in $G$ coincide on the vertices of $V(G) \setminus V(T_i)$.
-    Similarly, it holds for the fastest temporal paths from any other vertex in $G$ to $r_1$ and $r_2$.
+    Let $u \in V(G')$ be a clip vertex of the tree $T_u$ in $G[Z \cup \{u\}]$, where $u \in U$,
+    and let $z_1,z_2 \in V(T_v)$ be in the same equivalence class of the tree $T_u$.
+    Then, the fastest temporal paths from $z_1$ and from $z_2$ to any other vertex in $G'$ coincide on the edges of $G'$.
+    Similarly, the fastest temporal paths from any other vertex in $G'$ to $z_1$ and to $z_2$ coincide on the edges of $G'$.
 \end{lemma}
@@
     %
-    Denote with $P_1$ the underlying path of the fastest temporal path from $r_1$ to $y$, which consists of the edge $r_1 u$ and the path $P$ from $u$ to $y$.
-    Similarly, let $Q_2$ be the underlying path of the fastest temporal path from $r_2$ to $y$, consisting of the edge $r_2u$ together with the path $Q$ from $u$ to $y$.
-    Define $P_2$ as the second path from $r_2$ to $y$ that first uses the edge $r_1u$ and then the path $P$.
-    Similarly, $Q_1$ represents the second path from $r_1$ to $y$ that first uses the edge $r_2u$ and then the path $Q$.
+    Denote with $P_1$ the underlying path of the fastest temporal path from $z_1$ to $y$, which consists of the edge $z_1 u$ and the path $P$ from $u$ to $y$.
+    Similarly, let $Q_2$ be the underlying path of the fastest temporal path from $z_2$ to $y$, consisting of the edge $z_2u$ together with the path $Q$ from $u$ to $y$.
+    Define $P_2$ as the second path from $z_2$ to $y$ that first uses the edge $z_1u$ and then the path $P$.
+    Similarly, $Q_1$ represents the second path from $z_1$ to $y$ that first uses the edge $z_2u$ and then the path $Q$.
     Our objective is to demonstrate that either $P = Q$ or that $d(P_1, \lambda) = d(Q_1, \lambda)$ (and $d(P_2, \lambda) = d(Q_2, \lambda)$).
-    This implies that $r_1$ and $r_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_i)$ to reach $y$.
-
-    Let us set the label of the edge $r_1u$ to $t_1$, the label of $r_2u$ to $t_2$, the label of the last edge of the path $P$ as $t_p$ and the label of the last edge of the path $Q$ as $t_q$.
-    By the definition, since $P_1$ represents the fastest temporal paths form $r_1$ to $y$ we get that
-        $D_{r_1,y} = t_p - t_1 + c_p \Delta$, where $c_p \in \mathbb{N}$.
-    Similarly, for the path $Q_2$ it holds that $D_{r_2,y} = t_q - t_2 + c_q \Delta$ with $c_q \in \mathbb{N}$.
-    Note that since $r_1$ and $r_2$ are in the same equivalence class, it holds that the first label of $P$ and the first label of $Q$ have to be bigger than $t_1,t_2$.
-Meaning that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
+    This implies that $z_1$ and $z_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_u)$ to reach $y$.
+
+    Let us set the label of the edge $z_1u$ to $t_1$, the label of $z_2u$ to $t_2$, the label of the last edge of the path $P$ as $t_p$ and the label of the last edge of the path $Q$ as $t_q$.
+    By the definition, since $P_1$ represents the fastest temporal path form $z_1$ to $y$ we get that
+        $D_{z_1,y} = t_p - t_1 + c_p \Delta$, where $c_p \in \mathbb{N}$.
+    Similarly, for the path $Q_2$ it holds that $D_{z_2,y} = t_q - t_2 + c_q \Delta$ with $c_q \in \mathbb{N}$.
+    Note that since $z_1$ and $z_2$ are in the same equivalence class, it holds that the first label of $P$ and the first label of $Q$ have to be bigger than $t_1,t_2$.
+Meaning, that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
     or the difference (with at least one $t_1,t_2$) is $\Delta$ if and only if the first label of $P$ and the first label of $Q$ are the same. 
@@
     Then $c_p \leq c_q + 1$.
-    Now, since $r_1$ and $r_2$ are in the same equivalence class and by the definition of the duration of a temporal path we get that $d(P_2, \lambda) = t_p - t_2 + c_p \Delta \leq t_p - t_2 + (c_q - 1)\Delta$.
-    Because $Q_2$ is the fastest path from $r_2$ to $y$ we have also that $d(P_2, \lambda) \geq D_{r_2,y}$, which gives us $t_p - t_2 + (c_q - 1) \Delta \geq t_q - t_2 + c_q \Delta$.
+    Now, since $z_1$ and $z_2$ are in the same equivalence class and by the definition of the duration of a temporal path we get that $d(P_2, \lambda) = t_p - t_2 + c_p \Delta \leq t_p - t_2 + (c_q - 1)\Delta$.
+    Because $Q_2$ is the fastest path from $z_2$ to $y$ we have also that $d(P_2, \lambda) \geq D_{z_2,y}$, which gives us $t_p - t_2 + (c_q - 1) \Delta \geq t_q - t_2 + c_q \Delta$.
     This is equivalent to $t_p \geq t_q + \Delta$, but since $t_p, t_q \in \Delta$ this cannot happen.
@@
     Above we proved that $c_p = c_q$.
-We also know that $d(Q_1,\lambda) \geq d(P_1,\lambda)$ as $P_1$ is the fastest path from $r_1$ to $y$.
+We also know that $d(Q_1,\lambda) \geq d(P_1,\lambda)$ as $P_1$ is the fastest path from $z_1$ to $y$.
 All of this results in $t_q - t_1 + c_p \Delta \geq t_p - t_1 + c_p \Delta$ implying $t_q \geq t_p$, a contradiction.
@@
 
-    We proved that either $P$ and $Q$ are the same, or if they are different then $P_1$ and $Q_1$ are of the same duration and are both fastest paths from $r_1$ to $y$ (the same holds for $r_2$).
-
-    Proof for the fastest temporal paths in the other direction, namely starting at $y$ and reaching $r_1$ and $r_2$, is done analogously.
+    We proved that either $P$ and $Q$ are the same, or if they are different then $P_1$ and $Q_1$ are of the same duration and are both fastest paths from $z_1$ to $y$ (the same holds for $z_2$).
+
+    Proof for the fastest temporal paths in the other direction, namely starting at $y$ and reaching $z_1$ and $z_2$, is done analogously.
 \end{proof}
@@
 Let $v \in V(G')$ be a clip vertex of the tree $T_v$ in $G[Z \cup \{v\}]$,
-$r_i \in N_{T_v}(v)$ be a child of $v$ in the tree $T_v$, and let $r_j$ be a descendant of $r_i$ in the tree $T_v$.
-In other words, $r_i$ is a vertex on the first level of the tree $T_v$, while $r_j$ is a vertex in a subtree of $T_v$, that is rooted at $r_i$.
-Define $Q$ as the (unique) path between $r_i$ and $r_j$ in $T_v$.
-Let $x \in V(G)\setminus V(T_v)$ be an arbitrary vertex in $G$.
-Denote with
-$P_i$ and $P_j$ the underlying paths of the fastest temporal paths from $r_i$ and $r_j$ to $x$, respectively.
-Then $P_i$ and $P_j$ differ only in the edges and vertices of $Q$.
+$z \in N_{T_v}(v)$ be a child of $v$ in $T_v$, and let $z'$ be a descendant of $z$ in $T_v$.
+%In other words, $r_i$ is a vertex on the first level of the tree $T_v$, while $r_j$ is a vertex in a subtree of $T_v$, that is rooted at $r_i$.
+Let $x \in V(G)\setminus V(T_v)$ be an arbitrary vertex. 
+Denote by $P_z$ and $P_{z'}$ the underlying paths of the fastest temporal paths from $z$ and from $z'$ to $x$, respectively,
+and denote by $Q$ the (unique) path between $z$ and $z'$ in $T_v$.
+Then $P_z$ and $P_{z'}$ differ only in the edges of $Q$.
 \end{observation}
-The correctness from the above observation is a consequence of \cref{lemma:treeEquivClass-intVertices} and the fact that $P_i$ and $P_j$ leave the tree $T_i$ using the same edge $r_ix$.
+The correctness of the above observation is a consequence of \cref{lemma:treeEquivClass-intVertices} and of the fact that $P_z$ and $P_{z'}$ leave the tree $T_v$ using the same edge $zv$.
 
@@
 Each specific calculation takes linear time. Since there are $O(k^2)$ segments, the whole calculation takes $O(k^4)$ time.
-At this point
-the edges of every segment are fully determined
-with the exception of at most three edges per segment (the first and last edge and potentially one extra somewhere in the segment).
-We now relate also some of these edges.
-More precisely,
-let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$ be a segment with three not yet determined edges,
-and let $e_i =v_iv_{i+1}$ denote an edge of $S_{u,v}$.
-From the above procedure (when we were determining labels of edges of segments with each other) 
-we conclude that all of the edges $e_i$ of $S_{u,v}$ are in the following relation.
-There are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$,
-we have an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
+
+From the above procedure (where we were determining labels of edges of segments with each other) 
+we conclude that all of the edges $e_i=v_i v_{i+1}$ of a segment $S_{u,v}=(u=v_1, v_2, \dots, v_p=v)$ are in one of the following relations.
+First, where all of the edges are determined with respect to each other.
+Second, where
+there are some edges $e_1, e_2, \dots e_{i-1}$, whose label is determined with respect to the label $\lambda(e_1)$, there is an edge $f = e_i = v_i v_{i+1}$ which is not yet determined,
 and then there follow the edges
-$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to the $\lambda(e_{p-1})$.
+$e_{i+1}, e_{i+2}, \dots, e_{p-1}$, whose labels are determined with respect to $\lambda(e_{p-1})$.
+Third, where the first $e_1, \dots, e_{i-1}$ edges are determined with respect to the $\lambda(e_1)$ and all of the remaining edges $e_i, e_{i+1} \dots, e_{p-1}$ are determined with respect to the $\lambda(e_{p-1})$.
+%
 We want to now determine all of the edges in such segment $S_{u,v}$ with respect to just one edge (either the first or the last one).
-For this, we use the fact that at least one of the temporal paths between vertices in $S_{u,v}$ has to pass through $f$, when $S_{u,v}$ is of length at least $5$ or if it is of length $4$ there is a unique labeling that allows no such path to traverse $f$ (see~\cref{lemma:FPT-noUndeterminedEdgeInSegment}).
-%
-We proceed as follows.
+In the second case, we use the fact that at least one of the temporal paths between $v_{i-1}$ and $v_{i+1}$ has to pass through $f$, to determine $\lambda(f)$ with respect to $\lambda(e_{i-1})$ (and consequently $\lambda(e_1)$),
+and similarly, one of the temporal paths between $v_{i}$ and $v_{i+2}$ has to pass through $f$, which determines $\lambda(f)$ with respect to $\lambda(e_{i+1})$ (and consequently $\lambda(e_{p-1})$).
+In the third case, knowing the temporal paths between $v_{i-1}$ to $v_{i+1}$ results in determining the label of $\lambda(e_{i-1}$ with $\lambda(e_i)$, which consequently relates labels of all of the edges of the segment against each other.
+%
+To determine the desired paths we proceed as follows.
 \begin{enumerate}[G-1.]
@@
     \item \label{FPT-guessFTPinSegmentTgroughEdge}
-    Let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  be a segment with a not yet determined edge $v_i v_{i+1} = f \in S_{u,v}$. 
-    For the fastest temporal paths from $v_{i-1}$ to $v_{i+1}$, from $v_{i+1}$ to $v_{i-1}$, from $v_{i}$ and $v_{i+2}$, and $v_{i+2}$ and $v_{i}$, we guess whether it passes through the edge $f$. 
-    Thus we create $O(1)$ guesses for every such segment $S_{u,v}$, and $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
+    Let $S_{u,v} = (u=v_1, v_2, \dots, v_p=v)$  be a segment of length at least $4$.
+    If there is a not yet determined edge $v_i v_{i+1} = f$ in $S_{u,v}$ then
+    we guess which of the fastest temporal paths: from $v_{i-1}$ to $v_{i+1}$, from $v_{i+1}$ to $v_{i-1}$, from $v_{i}$ to $v_{i+2}$, from $v_{i+2}$ to $v_{i}$ pass through the edge $f$. 
+    If there are two incident edges $e = v_{i-1} v_{i}$ and $f = v_i v_{i+1} $ in $S_{u,v}$, that are determined with respect to $\lambda(v_1 v_2)$ and $\lambda (v_{p-1} v_p)$, respectively then we guess which of the fastest temporal paths: from $v_{i-1}$ to $v_{i+1}$, from $v_{i+1}$ to $v_{i-1}$ pass through the edges $e,f$.
+\\
+    %
+    We create $O(1)$ guesses for every such segment $S_{u,v}$, and $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.
     % counter for guesses continues
@@
 \end{enumerate}
-Once we know which temporal paths pass through $f$, 
-we can determine the label of edge $f$ 
-with respect to the first edge of the segment (when considering the fastest temporal path between $v_{i-1}$ and $v_{i+1}$),
-and with respect to the last edge of the segment (when considering the fastest temporal path between $v_{i}$ and $v_{i+2}$).
-Both these steps together determine all of the labels of $S_{u,v}$ with respect to just one label.
-Note, from \cref{lemma:FPT-noUndeterminedEdgeInSegment} it follows that the above procedure holds only for segments of length at least $4$.
-In the case when the segment $S_{u,v}$ has just three, two, or one edge, this procedure does not improve anything,
-therefore these segments remain with three, two, or one not yet determined edges, respectively.
-%From now on we refer to segments of length less than $4$.
-
+%
+Note that the condition for segment length at least four comes from~\cref{lemma:FPT-noUndeterminedEdgeInSegment}.
+We now conclude the following.
+\begin{observation}\label{obs:FPT-4determined}
+    Let $S_{u,v}$ be an arbitrary segment in $G'$.
+    If $S_{u,v}$ is of length at least $4$ then the labels of all the edges are determined with respect to its first edge.
+    If $S_{u,v}$ is of length $3$ or $2$ then it has at most $3$ or $2$ not yet determined edges, respectively.
+\end{observation}
+
+%\paragraph*{Creating variables}
 At this point $G'$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
@@
 \end{enumerate}
+
+%\paragraph*{Creating constraints}
 We have now finished creating all ILP instances.
@@
 We then iterate over all other paths from $u$ to $v$ (resp.~from $v$ to $u$) in $G'$, and for each one we introduce an inequality constraint.
-There are $O(k^2)$ pairs of vertices $u,v\in U$, and there are $k^{O(k)}$ possible paths from $u$ to $v$ (resp.~from $v$ to $u$) in $G'$, therefore in this step we introduce $k^{O(k^3)}$ constraints in total.
+There are $k^{O(k)}$ possible paths from $u$ to $v$ in $G'$. Therefore we add $k^{O(k)}$ inequality constraints for the pair $u,v$.
 
@@
 Assume that $S_{w,z}$ is of length at least $4$.
+
 This implies that there are at most two not yet determined edges in it.
@@
 
-\subparagraph{\boldmath Considering the paths for vertices from $Z$.}
+\subparagraph{\boldmath Fastest paths for vertices in $Z$.}
 All of the above is enough to determine the labeling $\lambda$ of $G'$.
@@
 %
+Now we are ready to explain how we determine the fastest temporal paths for all the vertices in $Z$
+
+%%% TODO NKL
 Recall that $G[Z]$ consists of disjoint trees and that each of these trees has a unique neighbor (clip vertex) $v$ in $G'$.
-%
-Now we are ready to explain how we determine the fastest temporal paths for all the vertices in $Z$
-
-%%% TODO NKL
-Because of \cref{obs:tree-only-neighbors} in the upcoming analysis we focus only on the vertices of each tree $T_i$ that are neighbors of their corresponding clip vertex $u_i$. 
-All fastest temporal paths to and from all other tree vertices are then uniquely extended.
-From this point onward, whenever we refer to a vertex $r$ in the tree $T_i$ we actually mean the vertex $r$ that is a neighbor of the clip vertex of the tree $T_i$.
+We then define the tree $T_v$ in $G[Z \cup \{v\}]$ as the collection of trees from $G[Z]$ with a clip vertex $v$, together with the root $v$.
+Determining the fastest temporal paths between any two vertices in the same tree is a straightforward process (see~\ref{thm:deltaExact-PolyTimeTrees}), so we exclude this case from our upcoming analysis.
+From \cref{obs:tree-only-neighbors} it follows that knowing temporal paths between any $y  \in V(G') \setminus (T_v)$ and all vertices in the first layer of the tree $T_v$ (\ie children of the root $v$),
+it is enough to determine the fastest temporal paths between $y$ and all other vertices in $T_v$.
+Therefore,
+in the upcoming analysis, we focus only on the vertices in the first layer of each tree $T_v$.
+During the process of determining the fastest paths from and to the vertices in $Z$, we use the fact that we have already identified the fastest paths among all vertices in $G'$.
 
 We split our analysis into two cases.
-First, when the clip vertex of tree $T_i$ is not a vertex of interest
+First, when the clip vertex $v$ of tree $T_v$ is not a vertex of interest,
 and second when the clip vertex is also a vertex of interest in $G'$.
-During the process of determining the fastest paths from and to the vertices in $Z$, we use the fact that we have already identified the fastest paths among all vertices in $G'$.
-It's worth noting that finding the fastest path between two vertices from the same tree $T_i$ is trivial, so we exclude this case from our analysis.
-
-To efficiently determine the fastest temporal paths to and from the vertices from $Z$ we still need to show some extra properties.
-We start with a property for the case when the clip vertex of the tree $T_i$ is not a vertex of interest.
-
-In the case when the clip vertex of the tree $T_i$ is a vertex of interest we cannot determine the labeling of the tree with respect to the labels of all edges incident to the clip vertex.
-Therefore, to efficiently determine the fastest temporal paths from and to vertices of $T_i$ in this case we proceed as follows.
-We split the vertices of $T_i$ in a small number of equivalence classes (bounded in $k$) and guess the fastest temporal paths among a vertex in each equivalence class and all the vertices from $U \cup U^*$.
-With this, we can determine the fastest temporal between vertices in $Z$ and all other vertices in $G$.
-Let us start with describing how to create equivalence classes.
-
-From \cref{lemma:treeEquivClass-intVertices}, we conclude that determining the fastest temporal path from any vertex within an equivalence class $C_w$ of $T_i$ to a given vertex $y \in V(G)$ requires only knowledge of the fastest temporal path $P^w_y$ from any vertex $r \in C_w$ to $y$.
-For all other vertices in $C_w$ to $y$, the fastest temporal paths share identical vertices and edges as $P^w_y$ outside the tree $T_i$.
-Within the tree $T_i$, there is a unique way in which the path is extended from these vertices.
-The same holds for the temporal paths from $y$ to vertices in $C_w$.
-
-%%% TODO NKL
-
-\subparagraph{\boldmath Fastest paths from $z \in Z$ to $y \in U \cup U^*$.}
-Let $x \in V(G')$ be a clip vertex of the tree $T_i$ in $G[Z \cup \{x\}]$ with $z \in V(T_i)$.
+%
+In the first case we use the fact that $v$ has only two edges $e,f$ incident to it in $G'$, and that we can determine all the labels of the tree edges with respect to $\lambda(e),\lambda(f)$ (see~\cref{lemma:treeLabels-notInteresting}).
+This results to be enough for us to determine the fastest temporal paths among any vertex $r$ in the first layer of the tree $T_v$ and an arbitrary vertex in $V(G)\setminus V(T_v)$.
+%
+In the second case we cannot determine the labeling of the tree with respect to the labels of all edges incident to the clip vertex.
+Therefore, we split the vertices in the first layer of $T_v$ into equivalence classes, and use the fact that the fastest temporal paths between two vertices in the same equivalence class coincide on the edges outside of $T_v$.
+
+\subparagraph{\boldmath Fastest paths from $r \in Z$ to $y \in U \cup U^*$.}
+Let $x \in V(G')$ be a clip vertex of the tree $T_x$ in $G[Z \cup \{x\}]$ with $r \in V(T_i)$ be a vertex in the first layer of $T_x$.
 We distinguish the following two cases.
@@
     The clip vertex $x =u \in U$ is a vertex of interest.
-    From guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPtreesEquivalence}}}} we determine the fastest temporal path from $z$ to $y$.
+    In this case we can w.l.o.g. assume that $r$ is a representative vertex in its equivalence class among the first layer vertices of $T_u$.
+    From the guesses~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongUandZstar}}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongUstarandZstar}}}}
+    we know the fastest temporal path from $r$ to $y$.
     \item \label{FPT:clipNotInU-1}
     The clip vertex $x \in U$ is not a vertex of interest. Then $x = v_j$ is a part of some segment $S_{u,v} = \{u=v_1, v_2, \dots, v_p = v)$, where $j \neq 1 \neq p$.
-    Then all the labels of the tree $T_i$ are determined with respect to the label $\lambda(v_{j-1}v_j)$ and with respect to the label $\lambda(v_{j}v_{j+1})$ (see~\cref{lemma:treeLabels-notInteresting}).
+    Then all the labels of the tree $T_x$ are determined with respect to the label $\lambda(v_{j-1}v_j)$ and with respect to the label $\lambda(v_{j}v_{j+1})$ (see~\cref{lemma:treeLabels-notInteresting}).
     From the calculations above and the performed guesses we know the exact structure (\ie the sequence of vertices and edges) of the following paths:
@@
     Note that $P_{xy}^*$ is either equal to the path $P_{xy}^u$ or to the path $P_{xy}^v$.
-    To be precise, from the guesses performed we know the structure of the fastest path from $v_2$ through $u$ to any other vertex of interest, and any other neighbor of the vertex of interest, which can be easily (uniquely) extended to start from $x=v_i$
-    (see~guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}} and
+    More precisely, from the guesses performed we know the structure of the fastest path from $v_2$ through $u$, that then continues to any other vertex of interest, and any other neighbor of the vertex of interest (see~guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}} and
     \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
-
-    Before we proceed note also that since the labels of the tree are determined with respect to the label of the edge $v_{i-1}v_i$ and $v_{i}v_{i+1}$ we can determine the difference 
-    $|\lambda(v_{i-1} x) - \lambda (z x)|$ and $|\lambda(xv_{i+1}) - \lambda (z x)|$.
+    This path can then be easily (uniquely) extended to start from $x=v_i$, as there is a unique (temporal) path starting at $x$ and finishing in $u$ or $v$.
+
+    Before we proceed note also that the labels of the tree are determined with respect to the label of the edge $v_{i-1}v_i$ and $v_{i}v_{i+1}$ (see~\cref{lemma:treeLabels-notInteresting}), therefore we can determine the difference
+    $|\lambda(v_{i-1} x) - \lambda (r x)|$ and $|\lambda(x v_{i+1}) - \lambda (r x)|$.
     %
     Suppose now that $P_{xy}^* = P_{xy}^u$.
-    We calculate the value $c = D_{x,y} + |\lambda(v_{i-1} x) - \lambda (z x)|$ and compare it to $D_{z,y}$.
+    We calculate the value $c = D_{x,y} + |\lambda(v_{i-1} x) - \lambda (r x)|$ and compare it to $D_{r,y}$.
     There are three options.
-    First $c = D_{z,y}$, in this case the fastest temporal path from $z$ to $y$ uses first the edge $zx$ and then continues to $y$ using the edges and vertices of $P_{xy}^*$.
-    Second $c > D_{z,y}$, in this case the fastest temporal path from $z$ to $y$ uses first the edge $zx$ and then continues to $y$ using the vertices and edges of $P_{xy}^v$.
-    Third $c < D_{z,y}$, in this case we stop the calculation and return an empty solution, as it cannot happen that a temporal path has a smaller duration than the corresponding value in the matrix $D$.
+    First $c = D_{r,y}$, in this case the fastest temporal path from $r$ to $y$ uses first the edge $rx$ and then continues to $y$ using the edges and vertices of $P_{xy}^*$.
+    Second $c > D_{r,y}$, in this case the fastest temporal path from $r$ to $y$ uses first the edge $rx$ and then continues to $y$ using the vertices and edges of $P_{xy}^v$.
+    Third $c < D_{r,y}$, in this case we stop the calculation and return false, as it cannot happen that a temporal path has a smaller duration than the corresponding value in the matrix $D$.
 %
@@
 
-\subparagraph{\boldmath Fastest paths from $z \in Z$ to $y \in V(G) \setminus (U \cup U^*)$.}
+\subparagraph{\boldmath Fastest paths from $r \in Z$ to $y \in V(G) \setminus (U \cup U^*)$.}
 The proof in this case is similar to the one above.
-We still split the analysis into two parts, one where the clip vertex $x$ of a tree $T_i$ that includes $z$ is in $U$ and one where it is not in $U$.
+We still split the analysis into two parts, one where the clip vertex $x$ of a tree $T_x$ that includes $r$ is in $U$ and one where it is not in $U$.
 The difference is that in some cases we need to also extend the ending part of the path (which can be done uniquely, using the same arguments as in the previous case).
 
-Once we determine the fastest temporal path from $z$ to $y$ we introduce an equality constraint for it, and for all other $k^{O(k)}$ paths we introduce the inequality constraints.
+Once we determine the fastest temporal path from $r$ to $y$ we introduce an equality constraint for it, and for all other $k^{O(k)}$ paths we introduce the inequality constraints.
 
 The procedure produces one equality constraint (for the fastest path) and $k^{O(k)}$ inequality constraints.
+
+\subparagraph{\boldmath Fastest paths from $y \in V(G)$ to $r \in Z$.}
+The process of determining fastest temporal paths from any vertex in the graph $G$ to a vertex $r$ that is a vertex in the first layer of a tree $T_x \in G[Z \cup \{x\}]$, where $x \in V(G')$,
+is similar to the one above, but performed in the opposite direction.
 

### 2024-01-17 SAND2024/SAND24-longversion.tex
Finished with the changes for the FPT proof.

@@
 
-    \begin{definition}[Travel delays]
+    \begin{definition}[Travel delays] \label{def:travel-delay}
     Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
@@
 If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
-%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
 In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
@@
 We now conclude the following.
-\begin{observation}\label{obs:FPT-4determined}
+\begin{corollary}\label{cor:FPT-4determined}
     Let $S_{u,v}$ be an arbitrary segment in $G'$.
-    If $S_{u,v}$ is of length at least $4$ then the labels of all the edges are determined with respect to its first edge.
     If $S_{u,v}$ is of length $3$ or $2$ then it has at most $3$ or $2$ not yet determined edges, respectively.
-\end{observation}
+    If $S_{u,v}$ is of length at least $4$ then the labels of all its edges are determined with respect to the first edge. 
+\end{corollary}
 
@@
 (since $S_{w,z}$ has at most $2$ inner vertices, we determined the fastest temporal paths from them to $u$ in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongUandUstar}}}}).
-Assume that $S_{w,z}$ is of length at least $4$.
-
-This implies that there are at most two not yet determined edges in it.
-We can easily compute the vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
-Denote with $P^+$ the fastest temporal path of the form $z_2 \rightarrow z \leadsto u$,
-and with $P^-$ the fastest temporal path of the form $z_{r-1} \rightarrow w \leadsto u$.
-Note that we know these paths from guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}.
-Then we know that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ on the 
-following fastest temporal path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$ 
+
+Assume that $S_{w,z}$ is of length at least $4$. From \cref{cor:FPT-4determined} we know that the labels of all the edges in $S_{w,z}$ are determined with respect to the label of the first edge.
+Moreover, this gives us the knowledge of the exact differences among two consecutive edge labels, which is enough to uniquely determine travel delays at all of the inner vertices $z_i \in S_{w,z}$ (see~\cref{def:travel-delay}).
+
+From the matrix $D$ we can easily determine the two vertices $z_i, z_{i+1} \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
+Let us denote with $P^+$ the fastest temporal path of the form $z_2 \rightarrow z \leadsto u$,
+and with $P^-$ the fastest temporal path of the form $z_{r-1} \rightarrow w \leadsto u$ 
+(we know these paths from guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
+%
+It follows that all vertices $z_j$ in $S_{w,z} \setminus\{z_i,z_{i+1}\}$ that are closer to $w$ than $z_i,z_{i+1}$ reach $u$ the fastest using the path $(z_j \rightarrow z_{j-1} \rightarrow \cdots \rightarrow z_2) \cup P^+$
 and
-all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ on the 
-following fastest temporal path
+all the vertices $z_j$ in $S_{w,z}\setminus\{z_i,z_{i+1}\}$ that are closer to $z$ than $z_i, z_{i+1}$ reach $u$ the fastest using the path
 $(z_j \rightarrow z_{j+1} \rightarrow \cdots \rightarrow z_{r-1}) \cup P^-$.
-Since the first part of fastest paths is unique, and we know the second part is the fastest, the above paths are the fastest temporal paths.
-We still have to determine the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
+Since the first part of the above path is unique, and we know that the second part is the fastest, it follows that these paths indeed represent the fastest temporal paths to $u$.
+%
+What remains to determine is the fastest temporal paths from $z_i,z_{i+1}$ to $u$.
 We distinguish the following two options.
@@
     $z_i = z_{i+1}$, \ie let $z_i$ be the unique vertex, that is furthest away from $u$ in $S_{w,z}$.
-    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, goes first through vertex $z_{i-1}$ (and then through $w$),
-    or it goes first through $z_{i+1}$ (and then through $z$).
+    In this case we have to determine if the fastest temporal path from $z_i$ to $u$, travels first through vertex $z_{i-1}$ (and then through $w$),
+    or it travels first through $z_{i+1}$ (and then through $z$).
     Since we know the values $D_{z_{i-1},u}, D_{z_{i+1},u}$,
-    and since there are at most two not yet determined labels in $S_{w,z}$,
-    we can uniquely determine one of the following
-    waiting times:
-    the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$,
-    or
-    the waiting time $\tau_{v_{i+1}} ^{v_{i}, v_{i+2}}$ at vertex $v_{i+1}$ when traveling from $v_i$ to $v_{i+2}$.
-    Suppose we know the former (for the latter case, analysis follows similarly).
-    Then we set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$.
-    We now compare $c$ and the value $D_{z_{i},u}$.
+    and we know the value of the waiting time $\tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$ at vertex $v_{i-1}$ when traveling from $v_i$ to $v_{i-2}$, 
+    we can uniquely determine the desired path.
+    We set $c = D_{z_{i-1},u} +  \tau_{v_{i-1}} ^{v_{i}, v_{i-2}}$
+    and compare $c$ to the value $D_{z_{i},u}$.
     If $c < D_{z_{i},u}$ we conclude that our ILP has no solution and we stop with calculations,
@@
 Let $x,y \in V(G') \setminus U$.
-We have two options.
+There are two options.
 \begin{enumerate}[(i)]
     \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. 
-    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path between vertices.
-    Suppose now that $S_{u,v}$ is of length at least $5$. Then there are at most two not yet determined edges in $S_{u,v}$.
-
-    W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
-    Denote with $x = v_i$.
-    Let $v_k \in S_{u,v}$ be a vertex for which the duration from $v_i$ is the biggest 
-    (note that in the case when we have two such vertices, $v_k$ and $v_{k+1}$ we know exactly what are the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    by similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
-    Therefore we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
-    with the exception of the fastest path from $x$ to $v_k$.
-    Since there is at most one undetermined edge in $S_{u,v}$,
-    and since we know the exact durations $D_{x,v_{k-1}}$ and $D_{x,v_{k+1}}$,
-    we can determine either
-    $c = D_{x,v_{k-1}} + \tau _ {v_k-1}^{v_k,v_{k-2}}$ or 
-    $c' = D_{x,v_{k+1}} + \tau _ {v_k+1}^{v_k,v_{k+2}}$.
-    We then compare (one of) these values to $D_{x,v_k}$ which then 
-    uniquely determines the fastest temporal path from $x$ to $v_k$
-    (for details see case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')\setminus U$ to $u \in U$).
+    If the length of $S_{u,v}$ is less than $4$ then we know what is the fastest path between vertices, as $x,y \in U^*$.
+    Suppose now that $S_{u,v}$ is of length at least $4$ and assume that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
+    Then we have two options; either the path from $x$ to $y$ travels only through the edges of $S_{u,v}$, denote such path as $P_{x,y}$,
+    or it is of the form $x \rightarrow v_1 \rightarrow u \leadsto v \rightarrow v_p \rightarrow y$, denote is as $P_{x,y}^*$.
+    Note that we can determined $P_{x,y}^*$ as it is a concatenation of a unique path from $x$ to $v_2$, together with the fastest path from $v_2$ to $v_{p}$, that travels through $u$ and $v$ (we know this path from \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}),
+    and the unique path from $v_p$ to $y$.
+    %
+    Because of \cref{cor:FPT-4determined} we can determine $c = d(P_{x,y}, \lambda)$.
+    If $c > D_{x,y}$ we set the fastest path to be $P_{x,y}^*$,
+    if $c = D_{x,y}$ then the fastest path is $P_{x,y}$, and if 
+    $c < D_{x,y}$ we conclude that our ILP has no solution and we stop with calculations.
+    %
     \item Vertices $x$ and $y$ are in different segments. 
 Let $x$ be a vertex in the segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w=z_1, z_2,z_3, \dots, z_r = z)$.
+%
 By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
@@
 Note that if there are two such vertices $z_i$ and $z_{i+1}$, we know exactly how all fastest temporal paths enter $S_{w,z}$ 
-(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$).
+(we use similar arguing as in case~(\ref{FPT:equality-fromUtoX-twosplit}) from above, where we were determining the fastest path from $x \in V(G')$ to $u \in U$).
 This implies that the fastest temporal paths from $x$ to all vertices $z_2, z_3, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_{r-1}$)  pass through $w$ (resp.~$z$).
@@
 
-We have to now consider the case when 
-$x = v_j$ and $y = z_i$.
-If at least one of the segments $S_{u,v}$ and $S_{w,z}$ is of length more than $5$,
-then this segment has no inner edges with not yet determined labels
-and
-we can uniquely determine the fastest path from~$v_j$ to $z_i$,
+In case when $x = v_j$ and $y = z_i$ and the segments are of length at least $4$, we can uniquely determine the fastest path from~$v_j$ to $z_i$,
 using 
 similar arguing as in case~(\ref{FPT:equality-fromUtoX-onesplit}) from above, when we were determining the fastest path from $x \in V(G')$ to $u \in U$.
-If at least one of them is of length $3$ or less,
+If at least one of the segments is of length $3$ or less,
 we can again uniquely determine the fastest path from~$v_j$ to~$z_i$, using the same approach, 
@@
 (as we guessed them in guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}).
-If both segments are of the length $4$, then we know how all vertices reach each other,
-as we guessed the fastest paths in guesses~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}} and~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}.
 \end{enumerate}
@@
 
-%%% TODO NKL
 Recall that $G[Z]$ consists of disjoint trees and that each of these trees has a unique neighbor (clip vertex) $v$ in $G'$.

### 2024-01-18 SAND2024/SAND24-longversion.tex
small changes to the long version

@@
 
-It is easy to see that the described algorithm runs in polynomial time. In the remainder, we proof that it is correct.
+It is easy to see that the described algorithm runs in polynomial time. In the remainder, we prove that it is correct.
 
@@
 Initially, our algorithm labels $e^\star$ with one, which equals $\lambda(e^\star)$.
-Now let $e$ be an edge popped off the queue by the algorithm in some iteration.
-Let $e'$ be the edge incident with $e$ that already obtained a label and is considered by the algorithm.
-Since $G$ is a tree, we have that $e'$ is closer to $e^\star$ than $e$.
+Now let $e$ be an edge popped off the queue by the algorithm in some iteration, that is on the distance $i$ from $e^\star$.
+Let $e'$ be the edge incident with $e$ that is on the distance $i-1$ from $e^\star$.
+Since $G$ is a tree $e'$ has already been considered by the algorithm and thus already has a label.
 By induction we have that the algorithm labeled $e'$ with $\lambda(e')$.
@@
 Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph.
-Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$. 
+This is true as any such path can traverse $0,1,2,\dots k$ feedback edges in different orders.
+Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$
+(by guess we mean enumerate and test all possibilities).
 However, 
@@
 \subparagraph{\boldmath Fastest paths for vertices in $Z$.}
-All of the above is enough to determine the labeling $\lambda$ of $G'$.
-Now we have to extend the labeling to consider also the vertices of~$Z= V(G) \setminus V(G')$ that we initially removed from $G$.
-%
-Now we are ready to explain how we determine the fastest temporal paths for all the vertices in $Z$
+All of the above is enough to determine the labeling $\lambda$ of $G'$. We have to extend the labeling to consider also the vertices of~$Z= V(G) \setminus V(G')$ that we initially removed from $G$.
 
@@
 We then define the tree $T_v$ in $G[Z \cup \{v\}]$ as the collection of trees from $G[Z]$ with a clip vertex $v$, together with the root $v$.
-Determining the fastest temporal paths between any two vertices in the same tree is a straightforward process (see~\ref{thm:deltaExact-PolyTimeTrees}), so we exclude this case from our upcoming analysis.
-From \cref{obs:tree-only-neighbors} it follows that knowing temporal paths between any $y  \in V(G') \setminus (T_v)$ and all vertices in the first layer of the tree $T_v$ (\ie children of the root $v$),
+Determining the fastest temporal paths between any two vertices in the same tree is a straightforward process (see~\cref{thm:deltaExact-PolyTimeTrees}), therefore we exclude this case from our upcoming analysis.
+From \cref{obs:tree-only-neighbors} it follows that knowing temporal paths between any $y  \in V(G')$ and all vertices in the first layer of the tree $T_v$ (\ie children of the root $v$),
 it is enough to determine the fastest temporal paths between $y$ and all other vertices in $T_v$.
@@
     The clip vertex $x \in U$ is not a vertex of interest. Then $x = v_j$ is a part of some segment $S_{u,v} = \{u=v_1, v_2, \dots, v_p = v)$, where $j \neq 1 \neq p$.
-    Then all the labels of the tree $T_x$ are determined with respect to the label $\lambda(v_{j-1}v_j)$ and with respect to the label $\lambda(v_{j}v_{j+1})$ (see~\cref{lemma:treeLabels-notInteresting}).
-    From the calculations above and the performed guesses we know the exact structure (\ie the sequence of vertices and edges) of the following paths:
+    Using \cref{lemma:treeLabels-notInteresting} we can determine all the edge labels of $T_x$ with respect to the label $\lambda(v_{j-1}v_j)$ and with respect to the label $\lambda(v_{j}v_{j+1})$.
+    Using the calculations of fastest temporal paths among vertices in $G'$ and the performed guesses we know the exact structure (\ie the sequence of vertices and edges) of the following paths:
     \begin{itemize}
@@
 
-    Before we proceed note also that the labels of the tree are determined with respect to the label of the edge $v_{i-1}v_i$ and $v_{i}v_{i+1}$ (see~\cref{lemma:treeLabels-notInteresting}), therefore we can determine the difference
-    $|\lambda(v_{i-1} x) - \lambda (r x)|$ and $|\lambda(x v_{i+1}) - \lambda (r x)|$.
-    %
     Suppose now that $P_{xy}^* = P_{xy}^u$.
-    We calculate the value $c = D_{x,y} + |\lambda(v_{i-1} x) - \lambda (r x)|$ and compare it to $D_{r,y}$.
-    There are three options.
+    Since the labels of $T_x$ are determined with respect to $\lambda(v_{i-1} x)$ we can calculate the value $c = D_{x,y} + |\lambda(v_{i-1} x) - \lambda (r x)|$.
+    We then compare $c$ to $D_{r,y}$ and get one of the following three options.
     First $c = D_{r,y}$, in this case the fastest temporal path from $r$ to $y$ uses first the edge $rx$ and then continues to $y$ using the edges and vertices of $P_{xy}^*$.
@@
 \end{enumerate}
-In both cases, we introduce the equality constraint for the determined fastest temporal path and inequality constraint for all the other $k^{O(k)}$ paths.
+In both cases, we introduce an equality constraint for the determined fastest temporal path and inequality constraints for all the other $k^{O(k)}$ paths.
 
@@
 We still split the analysis into two parts, one where the clip vertex $x$ of a tree $T_x$ that includes $r$ is in $U$ and one where it is not in $U$.
-The difference is that in some cases we need to also extend the ending part of the path (which can be done uniquely, using the same arguments as in the previous case).
-
-Once we determine the fastest temporal path from $r$ to $y$ we introduce an equality constraint for it, and for all other $k^{O(k)}$ paths we introduce the inequality constraints.
+The difference is that in some cases we need to also extend the ending part of the path (which can be done uniquely, using the same arguments as in the above analysis).
+
+Once we determine the fastest temporal path from $r$ to $y$ we introduce an equality constraint for it, and for all other $k^{O(k)}$ paths we introduce inequality constraints.
 

### 2024-01-19 SAND2024/SAND24-longversion.tex
Removed folder for figures from SAND
SAND submission - first version

@@
 
-\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords
+\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity, parameterized complexity.} %TODO mandatory; please add comma-separated list of keywords
 
@@
 We denote by $d(P,\lambda,\Delta)$, or simply by $d(P,\lambda)$ when $\Delta$ is clear from the context, the duration of any of the temporal paths $(P,\lambda,\Delta)$; note that they all have the same duration.
+Whenever we use the term \emph{label of an edge} $e$, we actually mean $\lambda(e) \in [\Delta]$.
+Note that for a given path $(P, \lambda, \Delta)$ that passes through the edge $e$, the label used by $P$ at that edge is $\lambda(e) + c \Delta$, for some $c \geq 0$.
 Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
@@
 which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
+
+We use standard terminology from parameterized complexity theory~\cite{DF13,FG06,Cyg+15}.
+Let~$\Sigma$ denote a
+finite alphabet.
+A parameterized problem~$L\subseteq \{(x,k)\in \Sigma^*\times \mathbb N_0\}$ is a subset of all instances~$(x,k)$ from~$\Sigma^*\times \mathbb N_0$,
+where~$k$ denotes the \emph{parameter}.
+A parameterized problem~$L$ is 
+FPT (\emph{fixed-parameter tractable}) if there is an algorithm that decides every instance~$(x,k)$ for~$L$ in~$f(k)\cdot |x|^{O(1)}$ time,
+where~$f$ is any computable function only depending on the parameter.
+If a parameterized problem $L$ is W[1]-hard, then it is presumably not
+fixed-parameter tractable.
 
@@
 If $w\in W_i$, then we say that $w$ has \emph{color} $i$.
-W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color.
+W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$.
     Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
@@
 
-We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, the sought temporal graph is not periodic) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
+We give a reduction to a variant of \deltaExact\ where the period $\Delta$ is infinite (that is, the sought temporal graph is not periodic and the labeling function $\lambda : E\rightarrow \mathbb{N}$ maps to the natural numbers) and we allow $D$ to have infinity entries, meaning that the two respective vertices are not temporally connected.
 Note that, given the matrix $D$, we can easily compute the underlying graph $G$, as follows.
@@
 It is straightforward to verify that the label of $e$ computed by the algorithm equals $\lambda(e)$.
-It follows that the algorithm computes $\lambda$.
+It follows that the algorithm computes~$\lambda$.
 \end{proof}
@@
 
-Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph.
-This is true as any such path can traverse $0,1,2,\dots k$ feedback edges in different orders.
+Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph~\cite{casteigts2021finding}.
+This is true as any such path can traverse $0,1,2,\dots k$ feedback edges in different order.
 Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$
@@
     %%%\item We perform a preprocessing step by iteratively removing all vertices of degree one.
-    \item We identify a small number $f(k)$ of ``important vertices''; these consist of the sets that we call $U, U^{\ast}, Z^{\ast}$.
+    \item We identify a small number $f(k)$ of ``important vertices''.%; these consist of the sets that we call $U, U^{\ast}, Z^{\ast}$.
     \item For each pair $u,v$ of important vertices, we guess the edges of the fastest temporal path from $u$ to $v$ (and from $v$ to $u$).
@@
     \item From these guesses we deduce fixed relationships between the labels of most of the edges of the graph. 
-    \item For all the edges, for which we do not have deduced a label yet, we introduce a \emph{variable}. Using all these variables, we build an Integer Linear Program (ILP). 
-    Among the constraints in this ILP we have that, for each of the $O(n^2)$ pairs of vertices $u,v$ in the graph, the duration of one specific temporal path from $u$ to $v$ (according to our guesses) is \emph{equal} to the desired duration $D_{u,v}$, while the duration of each of the other temporal paths from $u$ to $v$ is \emph{at least} $D_{u,v}$.
+    \item For all the edges, for which we have not deduced a label yet, we introduce a \emph{variable}. With all these variables, we build an Integer Linear Program (ILP). 
+    Among the constraints in this ILP we have that, for each of the $O(n^2)$ pairs of vertices $u,v$ in the graph, the duration of one specific temporal path from $u$ to $v$ (according to our guesses) is \emph{equal} to the desired duration $D_{u,v}$, while the duration of each of the other temporal path from $u$ to $v$ is \emph{at least} $D_{u,v}$.
     \item 
@@
 Furthermore, the set of feasible solutions for all constructed ILPs coincide with the set of all solutions to \deltaExact\ (\ie regardless of our guesses).
-    By making each of the above combinations of guesses, we essentially enumerate all possible ways that our instance of \deltaExact\ has a solution, and for each of these possible ways we create an ILP.
-That is, our instance of \deltaExact\ has a solution if and only if at least one of these ILPs has a feasible solution.
+    Each specific configuration of fastest temporal paths among all pairs of vertices corresponds to a specific ILP instance.
+By exhaustively trying all possible fastest temporal paths configurations it follows that our instance of \deltaExact\ has a solution if and only if at least one of these ILPs has a feasible solution.
     As each ILP can be solved in FPT time with respect to $k$ by Lenstra's Theorem~\cite{Lenstra1983Integer} (the number of variables is upper bounded by a function of $k$), we obtain our FPT algorithm for \deltaExact\ with respect to $k$.
@@
 
-\subsubsection{Preprocessing of the input}
-From the underlying graph $G$ of $D$ we first create a graph $G'$ by
+\subsubsection{Preprocessing of the input \label{sec:preprocessing-FPT}}
+From the underlying graph $G$ of $D$ we extract a (connected) graph $G'$ by
 iteratively removing vertices of degree one from $G$,
@@
 
-From the construction of $Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by $Z$) consists of disjoint trees. 
-Each of these trees has a unique neighbor $v$ in $G'$. 
+From the construction of~$Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by~$Z$) is a forest, \ie consists of disjoint trees. 
+Each of these trees has a unique neighbor $v$ in~$G'$. 
 Denote by $T_v$ the tree obtained by considering such a vertex $v$ and all the trees from $G[Z]$ that are incident to $v$ in $G$. 
 We then refer to $v$ as the \emph{clip vertex} of the tree $T_v$.
-In the case where $v$ is a vertex of interest we define also the set $Z^*_v$ of \emph{representative vertices} of $T_v$, as follows.
-
-\noindent
-We first create an empty set $C_w$ for every vertex $w$ that is a neighbor of $u$ in $G'$.
-We then iterate through every vertex $r$ that is in the first layer of the tree $T_v$ (\ie vertex that is a child of the root $v$ in the tree $T_v$), check the matrix $D$ and find the vertex $w \in N_{G'}(v)$ that is on the smallest duration from $r$.
+In the case where $v$ is a vertex of interest we define also the set $Z^*_v$ of \emph{representative vertices} of~$T_v$, as follows.
+%
+We first create an empty set~$C_w$ for every vertex $w$ that is a neighbor of $v$ in~$G'$.
+We then iterate through every vertex~$r$ that is in the first layer of the tree $T_v$ (\ie vertex that is a child of the root $v$ in the tree~$T_v$), check the matrix $D$ and find the vertex~$w \in N_{G'}(v)$ that is on the smallest duration from $r$.
 In other words, for an $r \in N_{T_v}(v)$ we find $w \in N_{G'}(v)$ such that $D_{r,w} \leq D_{r,w'}$ for all $w' \in  N_{G'}(v)$.
@@
 In the case when there exists also another vertex $w' \in  N_{G'}(v) $ for which $D_{r,w'} = D_{r,w}$, we add $r$ also to the set $C_{w'}$. In fact, in this case $C_{w'} = C_w$.
-At the end we create $|N_{G'}(v)|=O(k)$ sets $C_w$, whose union contains all children of $v$ in $T_v$. 
+At the end we create $|N_{G'}(v)| \in O(k)$ sets $C_w$, whose union contains all children of $v$ in $T_v$. 
 For every two sets $C_w$ and $C_{w'}$, where $w,w'\in N_{G'}(v)$, we have that either $C_w = C_{w'}$, or $C_w \cap C_{w'} = \emptyset$. 
-We call each of these sets $\{C_w : w \in N_{G'}(v)\}$ an \emph{equivalence class} of the tree $T_v$. 
-Now, from each equivalence class $C_w$ we choose an arbitrary vertex $r_w$ and put it into the set $Z^*_v$.
+We interpret each of these sets $\{C_w : w \in N_{G'}(v)\}$ as an \emph{equivalence class} of the neighbors of $v$ in the tree $T_v$. 
+Now, from each equivalence class~$C_w$ we choose an arbitrary vertex $r_w \in C_w$ and put it into the set $Z^*_v$.
 %
@@
 %
-Since $|U| \in O(k)$ and for each $u \in U$ it holds $|N_{G'}(u)| = O(k)$, we get that $|Z^*| \in O(k^2)$. 
+Since $|U| \in O(k)$ and for each $u \in U$ it holds $|N_{G'}(u)| \in O(k)$, we get that $|Z^*| \in O(k^2)$. 
 %For every vertex in the first layer of the tree $T_u$, where $u \in U$, we check the corresponding values in the matrix $D$ exactly once. Therefore, $Z^*$ is determined in linear time. 
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{fig-example-names-vertices}
+	\includegraphics[width=0.8\columnwidth]{fig-example-names-vertices_new}
 	\caption{An example of a graph with its important vertices: $U$ (in blue), $U^*$ (in green) and $Z^*$ (in orange).
@@
 \begin{corollary}\label{obs:FPT-k2segments}
-    There are at most $O(k^2)$ segments in $G'$.
+    There are $O(k^2)$ segments in $G'$.
 \end{corollary}
@@
 
-Remember, in the case where the clip vertex $u$ of the tree $T_u$ in $G[Z \cup \{u\}]$ is a vertex of interest, we split the vertices in the first layer of $T_u$ into at most $|N_{G'}(u)|$ equivalence classes.
+Remember, in the case where the clip vertex $u$ of the tree $T_u$ in $G[Z \cup \{u\}]$ is a vertex of interest, we split the vertices in the first layer of $T_u$ into at most $|N_{G'}(u)|$ equivalence classes (as explained in \cref{sec:preprocessing-FPT}).
 Let us now show the following important property of these equivalence classes.
@@
     and let $z_1,z_2 \in V(T_v)$ be in the same equivalence class of the tree $T_u$.
-    Then, the fastest temporal paths from $z_1$ and from $z_2$ to any other vertex in $G'$ coincide on the edges of $G'$.
-    Similarly, the fastest temporal paths from any other vertex in $G'$ to $z_1$ and to $z_2$ coincide on the edges of $G'$.
+    Then, the fastest temporal paths from $z_1$ and from $z_2$ to any other vertex in $G'$ coincide on the edges in $G'$.
+    Similarly, the fastest temporal paths from any other vertex in $G'$ to $z_1$ and to $z_2$ coincide on the edges in $G'$.
 \end{lemma}
@@
     Similarly, for the path $Q_2$ it holds that $D_{z_2,y} = t_q - t_2 + c_q \Delta$ with $c_q \in \mathbb{N}$.
-    Note that since $z_1$ and $z_2$ are in the same equivalence class, it holds that the first label of $P$ and the first label of $Q$ have to be bigger than $t_1,t_2$.
-Meaning, that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
+    Note that the difference between the first label of $P$ (resp.~$Q$) with $t_1$ and $t_2$ is smaller than $\Delta$,
     or the difference (with at least one $t_1,t_2$) is $\Delta$ if and only if the first label of $P$ and the first label of $Q$ are the same. 

### 2024-01-19 SAND2024/SAND24-shortversion.tex
Removed folder for figures from SAND
SAND submission - first version

--- 2024-01-17 SAND2024/SAND24-shortversion.tex
@@
 
-\clearpage
+%\clearpage
 
@@
 To this end, we first give a reduction from \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval} to a variant of \deltaExact\ where the period $\Delta$ is infinite, that is, when the labeling is non-periodic.
-We use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
+Then we use a special gadget (the ``infinity'' gadget) which allows us to transfer the result to a finite period $\Delta$.
 The latter construction is independent from the particular reduction we use, and can hence be treated as a reduction from the non-periodic to the periodic setting.
@@
 
-There are some problem settings that share similarities with ours, which we discuss now in more detail.
+%There are some problem settings that share similarities with ours, which we discuss now in more detail.
 
@@
 For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D(v,v')=1$) and then we provide the remaining entries of $D$.
-At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.
+In the Appendix, we show how to obtain the result for a finite $\Delta$ (by introducing a so-called ``infinity gadget'') and a matrix $D$ of durations of fastest paths which only has finite entries.
 
@@
 Every \emph{edge selection gadget} is associated with a color combination $i,j$ in the \textsc{Multicolored Clique} instance, and its main purpose is to ``select'' an edge connecting a vertex from color $i$ with a vertex from color $j$.
-Roughly speaking, the edge selection gadget consists of $m$ paths, one for every edge in $F_{i,j}$ (see \cref{fig:hardness1} for reference).
+Roughly speaking, the edge selection gadget consists of $m$ paths, one for every edge in $F_{i,j}$ (see Figure~3 in the Appendix for reference).
 The distance matrix $D$ will enforce that the labels on those paths effectively order them temporally, that is, in particular, the labels on one of the paths will be smaller than the labels on all other paths.
@@
  The verification gadget for color $i$ is connected to all edge selection gadgets that involve color $i$.
-More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see \cref{fig:hardness1} for reference).
+More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see Figure~3 in the Appendix for reference).
 Intuitively, the distances in the verification gadget are only realizable if the selected edges all have the same endpoint of color $i$.
@@
 
-\begin{comment}
-
-    \emph{Connector Gadget.} Next, we describe \emph{connector gadgets}.
-Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{Yes}-instances much easier.
-Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$.
-    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
-    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
-    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
-    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later.
-Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
-    We have the following edges. 
-    \begin{itemize}
-        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
-        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
-        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
-    \end{itemize}
-    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.
-
-    The \emph{first connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
-        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
-        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
-    \end{itemize}
-    The \emph{second connector gadget for the edge selection gadget of color combination $i,j$} with $i<j$ has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
-        %\item Set $A'$ contains all vertices in $X_{i,j}$.
-        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
-        \item Set $B$ is empty.
-    \end{itemize}
-    The \emph{first connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        %\item Set $A$ contains all vertices of the verification gadget. % and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
-        \item Sets $A$ and $B$ contain all vertices $v^i_\ell$ with $0\le \ell\le k$.
-    \end{itemize}
-The \emph{second connector gadget for the verification gadget of color $i$} has the following sets.
-    \begin{itemize}
-        \item Set $A$ contains all vertices of the verification gadget except vertices $v^i_\ell$ with $0\le \ell \le k$.
-        \item Set $B$ is empty.
-    \end{itemize}
-
-\emph{Alignment Gadget.} Lastly, we introduce an \emph{alignment gadget}.
-It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget, one vertex for each verification gadget, and one vertex for each connector gadget.
-Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
-The vertex $x_1$ of each edge selection gadget, the vertex $y^i$ of each verification gadget, and the vertex $\hat{v}_1$ of each connector gadget are each connected to  one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.
-
-\end{comment}
-
-\begin{figure}[t!]
-\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65, yscale=.7]
-\scriptsize
-\node (A) at (14,0) {};
-
-\draw[rounded corners, dashed, gray] (-13, 5.4) rectangle (10, 1.6) {};
-\node (A) at (-10.5,4.5) {alignment gadget};
-
-\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
-\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
-\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
-\node[rotate=90] (A) at (-14.5,-16) {connector gadget};
-
-\draw[rounded corners, dashed, gray] (-9.5, 1.4) rectangle (1.5, -26) {};
-\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};
-
-\draw[rounded corners, dashed, gray] (3.5, 1.4) rectangle (6.5, -26) {};
-\node[rotate=-90] (A) at (7,-21.5) {verification gadget for $j$};
-
-    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
-    \node[vert] (W1) at (-6.5,2) {};
-    \node[vert] (W2) at (-10,2) {};
-    \node[vert] (W3) at (-12,2) {};
-    \node[vert] (W4) at (7,2) {}; 
-    \node[vert] (W5) at (3.5,2) {};
-    \node[vert] (W6) at (9,2) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
-    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
-    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
-    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};
-
-    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
-    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
-    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
-    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
-    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
-    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};
-
-    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
-    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
-    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
-    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
-    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
-    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};
-
-    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
-    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
-    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
-    \node (A) at (-2,0) {$\ldots$};
-    \node[vert,label=above:$x_m$] (XM) at (0,0) {};
-
-    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};
-
-    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
-    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
-    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
-    \node (A) at (-2,-6) {$\ldots$};
-    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};
-
-    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
-    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
-    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
-    \node (A) at (-2,-8) {$\ldots$};
-    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};
-
-    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
-    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
-    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
-    \node (A) at (-2,-10) {$\ldots$};
-    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};
-
-    \node (A) at (-8,-11.5) {$\vdots$}; 
-    \node (A) at (-6,-11.5) {$\vdots$}; 
-    \node (A) at (-4,-11.5) {$\vdots$}; 
-    \node (A) at (0,-11.5) {$\vdots$};
-
-    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
-    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
-    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
-    \node (A) at (-2,-13) {$\ldots$};
-    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};
-
-    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
-    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
-    \node (A) at (-2,-17) {$\ldots$};
-    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};
-
-    \node (A) at (-8,-18.5) {$\vdots$}; 
-    \node (A) at (-6,-18.5) {$\vdots$}; 
-    \node (A) at (-4,-18.5) {$\vdots$}; 
-    \node (A) at (0,-18.5) {$\vdots$};
-
-    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
-    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
-    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
-    \node (A) at (-2,-20) {$\ldots$};
-    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};
-
-    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};
-
-    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
-    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
-    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
-    \node (A) at (5,-5.5) {$\vdots$};
-    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
-    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
-    \node (A) at (5,-12.5) {$\vdots$};
-    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
-    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
-    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
-    \node (A) at (5,-19.5) {$\vdots$};
-    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
-    \node (A) at (5,-22.5) {$\vdots$};
-    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};
-
-	\draw[edge] (X1) --node[] {} (VS);
-	\draw[edge] (X2) --node[] {} (VS);
-	\draw[edge] (X3) --node[] {} (VS);
-	\draw[edge] (XM) --node[] {} (VS);
-
-    \draw[edge] (Y1) --node[] {} (VS);
-	\draw[edge] (Y2) --node[] {} (VS);
-	\draw[edge] (Y3) --node[] {} (VS);
-	\draw[edge] (YM) --node[] {} (VS);
-
-    \draw[edge] (Y1) --node[] {} (U11);
-	\draw[edge] (Y2) --node[] {} (U12);
-	\draw[edge] (Y3) --node[] {} (U13);
-	\draw[edge] (YM) --node[] {} (U1M);
-
-    \draw[edge] (U21) --node[] {} (U11);
-	\draw[edge] (U22) --node[] {} (U12);
-	\draw[edge] (U23) --node[] {} (U13);
-	\draw[edge] (U2M) --node[] {} (U1M);
-
-    \draw[edge] (UN1) --node[] {} (UN11);
-	\draw[edge] (UN2) --node[] {} (UN12);
-	\draw[edge] (UN3) --node[] {} (UN13);
-	\draw[edge] (UNM) --node[] {} (UN1M);
-
-    \draw[edge] (U2N1) --node[] {} (VSS);
-	\draw[edge] (U2N2) --node[] {} (VSS);
-	\draw[edge] (U2N3) --node[] {} (VSS);
-	\draw[edge] (U2NM) --node[] {} (VSS);
-
-    \draw[edge] (VH11) --node[] {} (VH12);
-	\draw[edge] (VH12) --node[] {} (VH111);
-	\draw[edge] (VH12) --node[] {} (VH13);
-    \draw[edge] (VH13) --node[] {} (VH14);
-	\draw[edge] (VH13) --node[] {} (VH144);
-
-    \draw[edge] (VH21) --node[] {} (VH22);
-	\draw[edge] (VH22) --node[] {} (VH211);
-	\draw[edge] (VH22) --node[] {} (VH23);
-    \draw[edge] (VH23) --node[] {} (VH24);
-	\draw[edge] (VH23) --node[] {} (VH244);
-
-    \draw[edge] (VH31) --node[] {} (VH32);
-	\draw[edge] (VH32) --node[] {} (VH311);
-	\draw[edge] (VH32) --node[] {} (VH33);
-    \draw[edge] (VH33) --node[] {} (VH34);	
-    \draw[edge] (VH33) --node[] {} (VH344);
-
-    \draw[edge] (VH41) --node[] {} (VH42);
-	\draw[edge] (VH42) --node[] {} (VH411);
-	\draw[edge] (VH42) --node[] {} (VH43);
-    \draw[edge] (VH43) --node[] {} (VH44);	
-    \draw[edge] (VH43) --node[] {} (VH444);
-
-	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
-	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);
-
-    \draw[edge,double] (VIJ1) --node {} (U13);
-	\draw[edge,double] (VIJ) --node {} (U23);
-
-	\draw[edge] (W) --node[] {} (W1);
-	\draw[edge] (W) --node[] {} (W2);
-	\draw[edge] (W) --node[] {} (W3);
-	\draw[edge] (W) --node[] {} (W4);
-	\draw[edge] (W) --node[] {} (W5);
-	\draw[edge] (W) --node[] {} (W6);
-
-	\draw[edge] (X1) --node[] {} (W1);
-	\draw[edge] (VH11) --node[] {} (W2);
-	\draw[edge] (VH21) edge[bend left=50] node[] {} (W3);
-	\draw[edge] (VH31) --node[] {} (W4);
-	\draw[edge] (YI) --node[] {} (W5);
-	\draw[edge] (VH41) edge[bend right=50] node[] {} (W6);
-
-	\draw[edge] (YI) --node[] {} (VI0);
-
-	\draw[edge] (VII1) --node[] {} (UI1);
-	\draw[edge] (UI1) --node[] {} (UI2);
-\end{tikzpicture}
-    %\end{center}
-    }
-    \caption{Illustration of part of the underlying graph $G$. Edges incident with vertices $\hat{v}_1,\hat{v}_2$ of connector gadgets are omitted. Gray vertices form a feedback vertex set.
-    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
-    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
-    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
-    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
-    }\label{fig:hardness1}
-\end{figure}
-
 Furthermore, we use \emph{connector gadgets}, two for each edge selection gadget, and two for every verification gadget.
@@
 
-This finishes the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
+This finishes the description of the underlying graph $G$. For an illustration see Figure~3 in the Appendix. We can observe that the vertex set containing
 %\begin{itemize}
@@
 As mentioned before, due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
-
-\begin{comment}
-\emph{Duration Matrix $D$.} We proceed with describing the matrix $D$ of durations of fastest paths.
-For a more convenient presentation, we use the notation $d(v,v'):= D_{v,v'}$.
-For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.
-
-Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$.
-Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$.
-We set the following durations.
-Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
-\begin{itemize}
-    \item We set $d(\hat{v}_0,\hat{v}_2)=d(\hat{v}_3,\hat{v}_1)=d(\hat{v}_2,\hat{v}_0')=d(\hat{v}_1,\hat{v}_3')=2$, and $d(\hat{v}_0,\hat{v}_0')=d(\hat{v}_3,\hat{v}_3')=d(\hat{v}_0,\hat{v}_3')=d(\hat{v}_3,\hat{v}_0')=3$.
-    \item Let $v\in A$, then we set $d(v,\hat{v}_0')=3$ and $d(v,\hat{v}_3')=3$.
-    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$ and $d(\hat{v}_3,v)=3$.
-    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
-\end{itemize}
-Now consider two connector gadgets, one with vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$ and with sets $A$ and $B$, and one with vertices $\hat{v}_0',\hat{v}_0'',\hat{v}_1',\hat{v}_2',\hat{v}_3',\hat{v}_3''$ and with sets $A'$ and $B'$.
-\begin{itemize}
-    \item If there is a vertex $v\in A$ with $v\notin A'$, then we set $d(\hat{v}_1,\hat{v}_1')=3$.
-    \item If there is a vertex $v\in A$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_1,\hat{v}_2')=3$.
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\notin A'$, then we set $d(\hat{v}_2,\hat{v}_1')=3$.    
-    \item If there is a vertex $v\in V^\star\setminus (A\setminus B)$ with $v\in A'\setminus B'$, then we set $d(\hat{v}_2,\hat{v}_2')=3$.
-\end{itemize}
-
-Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
-\begin{itemize}
-    \item Let $1\le \ell<\ell'\le m$. We set $d(x_\ell,x_{\ell'})=2n\cdot (i+j)\cdot((\ell')^2-\ell^2)+1$.
-    \item For all $\ell\in[m]$ we set $d(x_\ell,v_{i,j}^{\star\star})=8n+5$.
-\end{itemize}
-
-Next, consider the validation gadget for color $i$. 
-%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
-%\begin{itemize}
-    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
-    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
-%\end{itemize}
-%
-For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
-\end{itemize}
-%The next cases are only relevant if $1\neq i \neq k$. 
-%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
-%\begin{itemize}
-%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
-%\end{itemize}
-%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
-%\end{itemize}
-For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
-\begin{itemize}
-    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
-\end{itemize}
-%For all 
-%$\ell\in[n+3]$ and 
-%$i<j\le k$ we set the following.
-%\begin{itemize}
-%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
-%\end{itemize}
-
-Finally, we consider the alignment gadget.
-Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$).
-\begin{itemize}
-    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
-\end{itemize}
-
-Let $y^i$ belong to the verification gadget of color $i$ and let $w'\in \hat{W}$ denote the neighbor of $y^i$ in the alignment gadget.
-Let $\hat{v}_1$ and $\hat{v}_2$ belong to the connector gadget of the verification gadget for color $i$.
-Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the one of the verification gadget for color $i$).
-Let $V_i$ denote the set of all vertices of the verification gadget of color $i$.
-\begin{itemize}
-    \item We set $d(w^\star,y^i)=n^8-1$, $d(w',v^i_0)=2$, and $d(w^\star,v^i_0)=n^8$.
-    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w^\star,\hat{v}_2)=n^9$, $d(w',\hat{v}_1)=n^9-n^8$, and $d(w',\hat{v}_2)=n^9-n^8$.
-    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus V_i$ we set $d(w^\star,v)=n^9+1$, $d(w,v)=n^9-n^8+2$, and $d(y^i,v)=n^9-n^8+2$.
-\end{itemize}
-Let $\hat{v}_1$ belong to some connector gadget. Then we set $d(w^\star,\hat{v}_1)=n^9$.
-
-All fastest path durations between non-adjacent vertex pairs that are not specified above are set to infinity.
-
-\end{comment}
-
-%This finishes the construction of \deltaExactLong\ instance $D$, which can clearly be computed in polynomial time.
-For an illustration see \cref{fig:hardness1}.
-As discussed earlier, we have that the vertex cover number of the underlying graph of the instance is in $O(k^2)$.
-
-%
-%\begin{comment}
-\emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
-To this end, we introduce the \emph{infinity gadget}.
-We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
-Let $V$ denote the set of all remaining vertices.
-We set the following durations.
-\begin{itemize}
-    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
-    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
-    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
-    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
-    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
-    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
-\end{itemize}
-Now we analyse which implications we get for the labels on the newly introduced edges.
-Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
-%\begin{itemize}
-    %\item 
-    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
-    %\item 
-    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
-    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
-    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
-%\end{itemize}
-For an illustration see \cref{fig:hardness2}.
-It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
-Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
-
-\begin{figure}[t]
-%\noindent\makebox[\textwidth]{
-\centering
-%\begin{center}
-\begin{tikzpicture}[line width=1pt, scale=.65,yscale=.7]
-\scriptsize
-
-\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
-\node (A) at (2,-7) {$V$};
-
-    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
-    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
-    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
-    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};
-
-    \node[vert,label=below:$v$] (V) at (-2,-7) {};
-    \node[vert,label=below:$v'$] (VV) at (6,-7) {};
-
-    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
-    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);
-
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
-    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
-    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
-\end{tikzpicture}
-    %\end{center}
-%    }
-    \caption{Illustration of the infinity gadget. Gray vertices are added to the feedback vertex set.}\label{fig:hardness2}
-\end{figure}
-
-Lastly, consider two vertices $v,v'\in V$.
-Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
-Furthermore, if $D$ is a \textsc{Yes}-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
-This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
-Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
-For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
-We can conclude that the originally constructed instance $D$ is a \textsc{Yes}-instance if and only if it remains a \textsc{Yes}-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
-%\end{comment}
 \end{proof}
@@
 
-\begin{theorem} \label{thm:deltaExact-PolyTimeTrees}
+\begin{theorem}[$\star$] \label{thm:deltaExact-PolyTimeTrees}
     \deltaExact\ can be solved in polynomial time on trees.
 \end{theorem}
-
-\begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
-    Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
-    This can be done in polynomial time as we need to loop through the matrix $D$ once and connect vertices $v_i, v_j$ for which $D_{i,j} = 1$.
-At the same time we also check if $D_{i,i} = 0$, for all $i \in [n]$.
-    When $G$ is constructed we run DFS algorithm on it and check that it has no cycles.
-    If at any step we encounter a problem, our algorithm stops and returns a negative answer.
-
-    Having computed $G$, our algorithm proceeds as follows.
-We pick an arbitrary edge $f$ and give it label one, that is, $\lambda(f)=1$.
-Now we push all edges incident with $f$ into a (initially empty) queue.
-Now we repeat the following as long as the queue is not empty:
-\begin{itemize}
-    \item Pop edge $e=\{u,v\}$ from the queue.
-Since $e$ was pushed into the queue, there is an edge $e'$ incident with $e$ that already obtained a label.
-Let w.l.o.g.\ $e'=\{v,w\}$.
-Then we set $\lambda(e)=(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
-    \item Push all edges incident with $e$ that have not received a label yet into the queue.
-\end{itemize}
-When the queue is empty, all edges have received a label.
-Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$.
-If this check succeeds for all vertex pairs, output the labelling $\lambda$, otherwise abort.
-
-It is easy to see that the described algorithm runs in polynomial time. In the remainder, we proof that it is correct.
-
-$(\Rightarrow)$: Since the algorithm checks at the end whether all durations specified in $D$ are realized by the corresponding fastest paths, we clearly face a yes-instance whenever the algorithm outputs a labeling.
-
-$(\Leftarrow)$: Assume we face a yes-instance, then there exists a labeling $\lambda^\star$ that realizes all durations specified in $D$.
-Let $e^\star$ denote the edge initially picked by the algorithm.
-For all edges $e$ let $\lambda(e)=(\lambda^\star(e)-\lambda^\star(e^\star)+1)\bmod \Delta$.
-Clearly, the labeling $\lambda$ also realizes all durations specified in $D$ since $\lambda$ is obtained by adding the constant $(1-\lambda^\star(e^\star))$ modulo $\Delta$ to all labels of $\lambda^\star$ which does not change the duration of any temporal path, that is all durations in $(G,\lambda^\star)$ are the same as their counterparts in $(G,\lambda)$.
-We claim that our algorithm computes and outputs $\lambda$.
-
-We prove that our algorithm computes $\lambda$ by induction on the distance of the labeled edges to $e^\star$, where the distance of two edges $e,e'$ is defined as the length of a shortest path that uses $e$ as its first edge and $e'$ as its last edge.
-
-Initially, our algorithm labels $e^\star$ with one, which equals $\lambda(e^\star)$.
-Now let $e$ be an edge popped off the queue by the algorithm in some iteration.
-Let $e'$ be the edge incident with $e$ that already obtained a label and is considered by the algorithm.
-Since $G$ is a tree, we have that $e'$ is closer to $e^\star$ than $e$.
-By induction we have that the algorithm labeled $e'$ with $\lambda(e')$.
-Assume that $e=\{u,v\}$ and $e'=\{v,w\}$.
-Since $G$ is a tree there is only one path from $u$ to $w$ in $G$ and it uses edges $e$ and $e'$.
-It follows that $\lambda(e')-\lambda(e)+1=D_{u,w}$ if $\lambda(e')>\lambda(e)$, and $\lambda(e')-\lambda(e)+\Delta+1=D_{u,w}$ otherwise.
-Our algorithm labels $e$ with $(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
-It is straightforward to verify that the label of $e$ computed by the algorithm equals $\lambda(e)$.
-It follows that the algorithm computes $\lambda$.
-%    From now on we can assume that we know that the underlying graph $G$ of $D$ is a tree and we know its structure.
-%    For the next part of the algorithm we use \cref{obs:travel-delays-in-trees}.
-%    
-%    We pick an arbitrary vertex $v_i \in V(G)$ and check which vertex $v_j \in V(G)$ is furthest away from it, \ie we find a maximum element in the $i$-th row of the matrix $D$.
-%    We now take the unique path $P_{i,j}$ in $G$, 
-%    which has to also be the underlying path of the fastest temporal path from $v_i$ to $v_j$, and using \cref{obs:travel-delays-in-trees} calculate waiting times at all inner vertices.
-%    We save those values in a matrix $T$, of size $n \times n \times n$, and mark vertices of the path  $P_{i,j}$ as visited.
-%    Matrix $T$ stores at the position $(k,j,\ell)$ the value corresponding to the travel delay at vertex $v_k$ when traveling from $v_{j}$ to $v_{\ell}$, 
-%    \ie it stores the value $\tau_{v_k}^{v_{j}, v_\ell}$, where $v_j,v_\ell \in N(v_k)$. All other values of $T$ are set to \textsc{Null}.
-%    Now we repeat procedure, from vertex $v_i$, for vertices that are not marked as visited yet, \ie vertices in $V \setminus P_{i,j}$.
-%    We find a vertex in $V \setminus P_{i,j}$ that is furthest away from $v_i$ and repeat the procedure.
-%    When we have exhausted the $i$-th row of $D$,
-%    \ie vertex $v_i$ now reaches every vertex of $G$,
-%    we continue and repeat the procedure for all other vertices.
-%    If at any point we get two different values for the same travel delay at a specific vertex, then we stop with the algorithm and return the negative answer.
-%    If the above procedure finishes successfully we get the matrix $T$ with travel delays for all vertices in $G$, of degree at least $2$.
-%    The above calculation is performed in polynomial time, as for every vertex $v_i$ we inspect the whole graph once.
-%    \begin{claim}[$\star$]\label{lemma:matrixT-travelDelays-tree}
-%        Matrix $T$ consists of travel delays for all vertices of degree at least $2$ in $G$.
-%    \end{claim}
-%
-%
-%    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
-%    We start by fixing the label of an arbitrary edge as $a$, where $a \in [\Delta]$.
-%    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
-%    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
-%    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
-%    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
-%    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
-%    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling.
-Therefore, all together the whole algorithm is performed in polynomial time.
-\end{proof}
 
@@
 
-Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph.
-Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$. 
+Before presenting the structure of our algorithm for \cref{thm:FPTwrtFES}, observe that, in a static graph, the number of paths between two vertices can be upper-bounded by a function $f(k)$ of the feedback edge number $k$ of the graph~\cite{casteigts2021finding}.
+Therefore, for any fixed pair of vertices $u$ and $v$, we can ``guess'' the edges of the fastest temporal path from $u$ to $v$ (by guess we mean enumerate and test all possibilities).
 However, 
@@
     %%%\item We perform a preprocessing step by iteratively removing all vertices of degree one.
-    \item We identify a small number $f(k)$ of ``important vertices''; these consist of the sets that we call $U, U^{\ast}, Z^{\ast}$.
+    \item We identify a small number $f(k)$ of ``important vertices''.
     \item For each pair $u,v$ of important vertices, we guess the edges of the fastest temporal path from $u$ to $v$ (and from $v$ to $u$).
@@
 A full description of the algorithm is deferred to the Appendix.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{fig-example-names-vertices_new}
+	\caption{An example of a graph with its important vertices: $U$ (in blue), $U^*$ (in green) and $Z^*$ (in orange).
+    Corresponding feedback edges are marked with a thick red line, while dashed edges represent the edges (and vertices) ``removed'' from $G'$ at the initial step.
+	\label{fig:labelingVertices}}
+\end{figure}
 
@@
 It follows that $|U^*| \in O(k^2)$.
-From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
-it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
-For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
-and call it a \emph{clip vertex of the tree $T_i$}.
-It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
-but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
-Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
-from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
-that are clipped at the same vertex $u_i \in V(G')$.
-For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
-and call it \emph{a representative vertex of the tree $T_{u_i}$}.
-We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
-where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
-\[
-Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
-\]
-Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
+From the construction of~$Z$ (\ie by exhaustively removing vertices of degree one from~$G$), it follows that $G[Z]$ (the graph induced in $G$ by~$Z$) is a forest, \ie consists of disjoint trees. 
+Each of these trees has a unique neighbor $v$ in~$G'$. 
+Denote by $T_v$ the tree obtained by considering such a vertex $v$ and all the trees from $G[Z]$ that are incident to $v$ in $G$. 
+We then refer to $v$ as the \emph{clip vertex} of the tree $T_v$.
+In the case where $v$ is a vertex of interest we define also the set $Z^*_v$ of \emph{representative vertices} of~$T_v$, as follows.
+%
+We first create an empty set $C_w$ for every vertex $w$ that is a neighbor of $v$ in~$G'$.
+We then iterate through every vertex $r$ that is in the first layer of the tree $T_v$ (\ie vertex that is a child of the root $v$ in the tree $T_v$), check the matrix $D$ and find the vertex~$w \in N_{G'}(v)$ that is on the smallest duration from $r$.
+In other words, for an $r \in N_{T_v}(v)$ we find $w \in N_{G'}(v)$ such that $D_{r,w} \leq D_{r,w'}$ for all $w' \in  N_{G'}(v)$.
+%
+We add vertex $r$ to $C_w$.
+In the case when there exists also another vertex $w' \in  N_{G'}(v) $ for which $D_{r,w'} = D_{r,w}$, we add $r$ also to the set $C_{w'}$. In fact, in this case $C_{w'} = C_w$.
+At the end we create $|N_{G'}(v)| \in O(k)$ sets $C_w$, whose union contains all children of $v$ in $T_v$. 
+For every two sets $C_w$ and $C_{w'}$, where $w,w'\in N_{G'}(v)$, we have that either $C_w = C_{w'}$, or $C_w \cap C_{w'} = \emptyset$. 
+We interpret each of these sets $\{C_w : w \in N_{G'}(v)\}$ as an \emph{equivalence class} of the neighbors of $v$ in the tree $T_v$. 
+Now, from each equivalence class~$C_w$ we choose an arbitrary vertex $r_w \in C_w$ and put it into the set $Z^*_v$.
+%
+We repeat the above procedure for all trees $T_u$ with the clip vertex $u$ from $U$, and define $Z^*$ as 
+\begin{equation}
+    Z^* = \bigcup\limits_{v \in U} Z^*_v.
+\end{equation}
+%
+Since $|U| \in O(k)$ and for each $u \in U$ it holds $|N_{G'}(u)| \in O(k)$, we get that $|Z^*| \in O(k^2)$. 
 Finally, the set of \emph{important vertices} is defined as the set $U \cup U^{\ast} \cup Z^{\ast}$.
 For an illustration see \cref{fig:labelingVertices}.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{fig-example-names-vertices}
-	\caption{An example of a graph with its important vertices: $U$ (in blue), $U^*$ (in green) and $Z^*$ (in orange).
-    Corresponding feedback edges are marked with a thick red line, while dashed edges represent the edges (and vertices) ``removed'' from $G'$ at the initial step.
-	\label{fig:labelingVertices}}
-\end{figure}
 
@@
 	Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
-	A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
+	A path $P = (u=v_1,v_2, \dots, v_p = v)$ of length at least $2$ in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for all $i \in \{ 2, 3, \dots, p-1\}$,
 	is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
@@
 \begin{corollary}\label{obs:FPT-k2segments}
-	There are at most $O(k^2)$ segments in $G'$.
+	There are $O(k^2)$ segments in $G'$.
 \end{corollary}
@@
 	%
-	For an example see~\cref{fig:FPT-guessG4}.
+	For an example see Figure~8a in the Appendix.
 	\item \label{FPT:guess-uToSegmentz2}
@@
 	%
-	For an example see~\cref{fig:FPT-guessG5}.
+	For an example see Figure~8b in the Appendix.
 	%All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
@@
 	%
-	For an example see~\cref{fig:FPT-guessG6}.
+	For an example see Figure~8c in the Appendix.
 	\item \label{FPT:guess-splitFromUtoAnotherSegment}
@@
 	%
-	For an example see~\cref{fig:FPT-guessG7}.
+	For an example see Figure~8d in the Appendix.
 	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
@@
 \end{enumerate}
-%
-\begin{figure}[t]
-	\centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{0.88\linewidth}{!}{
-			\includegraphics{fig-guess1}}
-		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
-			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
-			\label{fig:FPT-guessG4}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{0.88\linewidth}{!}{
-
-			\includegraphics{fig-guess2}}
-		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
-			\label{fig:FPT-guessG5}}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.48\textwidth}
-		\vspace{-0.4cm}
-        \centering
-		\resizebox{0.98\linewidth}{!}{
-			%
-			\includegraphics{fig-guess3}}
-		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
-			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
-			and guessed the fastest paths of the form
-			$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
-			and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
-			\label{fig:FPT-guessG6}}
-	\end{subfigure}
-	\quad
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\resizebox{0.88\linewidth}{!}{
-			\includegraphics{fig-guess4}}
-		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
-			we
-			calculated its corresponding split vertex $v_i \in S_{u,v}$,
-			and guessed the fastest paths of the form
-			$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
-			and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
-			\label{fig:FPT-guessG7}}
-	\end{subfigure}
-	\caption{Illustration of the guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
-\end{figure}
 %

### 2024-01-19 SAND2024/SAND24-longversion.tex
Submission typos corrected.

@@
 Note that, given the matrix $D$, we can easily compute the underlying graph $G$, as follows.
-Two vertices $v,v'$ are adjacent if $G$ if and only if $D_{v,v'}=1$, as having an edge between $v$ and $v'$ is the only way that there exists a temporal path from $v$ to $v'$ with duration 1.
-For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D(v,v')=1$) and then we provide the remaining entries of $D$.
+Two vertices $v,v'$ are adjacent in $G$ if and only if $D_{v,v'}=1$, as having an edge between $v$ and $v'$ is the only way that there exists a temporal path from $v$ to $v'$ with duration 1.
+For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D_{v,v'}=1$) and then we provide the remaining entries of $D$.
 At the end of the proof we show how to obtain the result for a finite $\Delta$ and a matrix $D$ of durations of fastest paths, that only has finite entries.

### 2024-01-19 SAND2024/SAND24-shortversion.tex
Submission typos corrected.

@@
 Note that, given the matrix $D$, we can easily compute the underlying graph $G$, as follows.
-Two vertices $v,v'$ are adjacent if $G$ if and only if $D_{v,v'}=1$, as having an edge between $v$ and $v'$ is the only way that there exists a temporal path from $v$ to $v'$ with duration 1.
-For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D(v,v')=1$) and then we provide the remaining entries of $D$.
+Two vertices $v,v'$ are adjacent in $G$ if and only if $D_{v,v'}=1$, as having an edge between $v$ and $v'$ is the only way that there exists a temporal path from $v$ to $v'$ with duration 1.
+For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D_{v,v'}=1$) and then we provide the remaining entries of $D$.
 In the Appendix, we show how to obtain the result for a finite $\Delta$ (by introducing a so-called ``infinity gadget'') and a matrix $D$ of durations of fastest paths which only has finite entries.

### 2024-01-19 SAND2024/SAND24-longversion.tex
changes to short submited version

@@
 	\textbf{Inner segment guess I}.
-	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments. %,
+	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ and $S_{w,z} = (w=z_1,z_2, \dots, z_r = z)$ be two segments in $G'$. %,
 	%first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.
@@
 	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$,
-	and let $w \in U \cup Z^*$. %be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a vertex of interest.
+	and let $w \in U \cup Z^*$.
 	We want to
@@
 	\\
-	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $k^{O(k)}$ different possible such paths, therefore we make $k^{O(k^4)}$ guesses for these paths.
+	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $k^{O(k)}$ different possible such paths, therefore we make $k^{O(k^5)}$ guesses for these paths.
 	%
 	For an example see~\cref{fig:FPT-guessG5}.
-	%All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
-	%Each of the previous partial ILP instances is therefore extended into $O(k^6)$ new ILP instances.
 	\item \label{FPT:guess-splitFromAnotherSegmentAndPaths}
@@
 		In this case we only need to guess the following two fastest temporal paths 
-		$u \leadsto w \rightarrow z_2$
-		and $u \leadsto z \rightarrow z_{r-1}$.
-		Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-		which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-		In this case we do not introduce any new guesses, as we have aready guessed 
-		the fastest paths of the form
-		$u \leadsto w \rightarrow z_2$
-		and $u \leadsto z \rightarrow z_{r-1}$
-		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
+		$v_i \leadsto w \rightarrow z_2$
+		and $v_i \leadsto z \rightarrow z_{r-1}$.
+		Each of these paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $z_j$, resp.~$z_{j+1}$,
+		which give us fastest temporal paths from $v_i$ to $z_j$ and from $v_i$ to $z_{j+1}$.
+		In this case we introduce only two more guesses.
+        We repeat this procedure for all pairs of segments. which results in creating $k^{O(k^5)}$ new guesses.
 	\end{enumerate}
-	Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-	\ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
-	%
 	For an example see~\cref{fig:FPT-guessG6}.
@@
 	\textbf{Split vertex guess II}.
-Let $w \in U \cup Z^*$ be either a vertex of interest or a representative vertex of a tree, whose clipped vertex is a  of interest,
+    Let $w \in U \cup Z^*$,
     and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$.
-    Similarly as above, in guess \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, we want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+    We want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
     We again have two cases,
@@
     second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-    In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-    travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-    Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-    we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-    or 
-    $v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-    Which produces two new guesses.
-    In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-    Therefore no new guesses are needed.
-    Note that the above guesses, together with the guesses from \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}},
-    uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-    (this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-
-    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-    We repeat this for all vertices of interest, and all segments,
-    which produces $k^{O(k^2)}$ new guesses.
+    All together we make two guesses for each pair $w, S_{u,v}$.
+	We repeat this for all vertices in $U \cup Z^*$, and all segments,
+	which produces $k^{O(k^5)}$ new guesses.
     %
     For an example see~\cref{fig:FPT-guessG7}.
- %
-%	Let $w \in U \cup Z^*$ 
-%	and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$.
-%	We want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
-%	We again have two cases,
-%	first one where $v_i$ is a unique vertex in $S_{u,v}$ that is furthest away from $w$,
-%	and the
-%	second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-	\begin{comment}
-	In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-	travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-	Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-	we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-	or 
-	$v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-	Which produces two new guesses.
-	In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-	Therefore no new guesses are needed.
-	Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-	uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-	(this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-	\end{comment}
-%	All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-%	We repeat this for all vertices of interest, and all segments,
-%	which produces $k^{O(k^2)}$ new guesses.
-	%
-%	For an example see~\cref{fig:FPT-guessG7}.
-%	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
 	% counter for guesses continues
@@
     Let $u \in V(G')$ be a clip vertex of the tree $T_u$ in $G[Z \cup \{u\}]$, where $u \in U$,
-    and let $z_1,z_2 \in V(T_v)$ be in the same equivalence class of the tree $T_u$.
+    and let $z_1,z_2 \in V(T_u)$ be in the same equivalence class of the tree $T_u$.
     Then, the fastest temporal paths from $z_1$ and from $z_2$ to any other vertex in $G'$ coincide on the edges in $G'$.

### 2024-01-19 SAND2024/SAND24-shortversion.tex
changes to short submited version

@@
 \section{Algorithms for \deltaExact}
+%%%%%
+%%%%% CHANGES BELOW - NKL
+In this section, to complement the discussed hardness aspects of \deltaExact, we present some algorithmic results.
+We start by restricting the underlying graph $G$ of the input matrix $D$ of \deltaExact\ to be a tree and get the following.
+\begin{theorem}[$\star$] \label{thm:deltaExact-PolyTimeTrees}
+    \deltaExact\ can be solved in polynomial time on trees.
+\end{theorem}
+The main reason, for which \deltaExact\ is straightforward to solve on trees, is twofold: 
+\begin{itemize}
+    \item between any pair of vertices $v_i$ and $v_j$ in the tree $T$, there is a \emph{unique} path $P$ in $T$ from $v_i$ to $v_j$, and 
+    \item in any periodic temporal graph $(T,\lambda,\Delta)$ and any fastest temporal path $P=((e_1,t_1),\ldots,(e_i,t_i),\ldots,(e_j,t_j),\ldots,(e_{\ell-1},t_{\ell-1}))$ from $v_1$ to $v_{\ell}$ we have that the sub-path $P'=((e_i,t_i),\ldots,(e_{j-1},t_{j-1}))$ is also a fastest temporal path from $v_i$ to $v_j$.
+\end{itemize}
+However, these two nice properties do not hold when the underlying graph is not a tree.
+For example, in~\cref{fig:ftpExample}, the fastest temporal path from $u$ to $v$ is $P_{u,v}$ (depicted in blue) goes through~$w$, however the sub-path of $P_{u,v}$ that stops at $w$ is not the fastest temporal path from $u$ to $w$.
+The fastest temporal path from $u$ to $w$ consists only of the single edge $uw$ (with label $9$ and duration $1$, depicted in red).
+%, while the fastest temporal path from $u$ to $v$ contains the four other edges (with labels 1, 3, 5, 7 and duration 7).
+
+Nevertheless, we prove that we can still solve \deltaExact\ efficiently if the underlying graph is similar to a tree; more specifically we show the following result, which turns out to be non-trivial.
+
+%%%%%%%
+%%%%%%% CHANGES ABOVE - NKL
 \begin{comment}
-In this section we provide several algorithms for \deltaExact.
-By \cref{thm:NPhardness} we have that \deltaExact\ is NP-hard in general, hence we start by identifying restricted cases where we can solve the problem in polynomial time.
-%
-The first case, when the underlying graph $G$ of an instance $(D, \Delta)$ of \deltaExact\ is a tree, we get the following result.
-
-\begin{theorem}[$\star$]\label{thm:deltaExact-PolyTimeTrees}
-    \deltaExact\ can be solved in polynomial-time on trees.
-\end{theorem}
-
-In the case when the underlying graph is unrestricted, we show that \deltaExact\ is fixed-parameter tractable when parameterized by the feedback edge number of the underlying graph.
-Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-In the Appendix we give also a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-\end{comment}
-
 In this section we provide several algorithms for \deltaExact.
@@
 Note that our parameterized hardness result (\cref{thm:W1wrtFVS}) implies that we presumably cannot replace the feedback edge number with the smaller parameter feedback vertex number, or any other parameter that is smaller than the feedback vertex number, such as e.g.\ the treewidth.
-%In the appendix we give a dedicated algorithm to solve \deltaExact\ in polynomial time if the underlying graph is a cycle.
-Note that this is already implied by our FPT result, however the direct algorithm we provide is much simpler for this case.
-
-%We first start with defining certain notions, that will be of use when solving the problem.
-
-%    \begin{definition}[Travel delays]
-%    Let $(G, \lambda)$ be a temporal graph satisfying conditions of \deltaExact.
-%    Let $e_1=uv$ and $e_2=vz$ be two incident edges in $G$ with $e_1 \cap e_2 = v$.
-%    We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-%    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
-%    More specifically:
-%    \begin{equation}\label{eq:def-VertexWaitingTime}
-%       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
-%    \end{equation}
-%    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
-%    \end{definition}
-%    Intuitively, the value of $\tau_v^{uz}$ represents how long a temporal path waits at vertex $v$ when first taking edge $e_1=uv$ and then edge $e_2 = vz$.
-
-%    We can make the following observation concerning subpaths of a fastest temporal path.
-
-%\begin{lemma}[$\star$]\label{lemma:unique-fastest-path-allDelays}
-%    Let $(G, \lambda)$ be a temporal graph satisfying conditions of the \deltaExact\ problem,
-%    and let $(P_{1,k},\lambda)$ be a fastest temporal path from $u=v_1$ to $v=v_k$ on $k$ vertices $v_1,v_2,\dots,v_k$.
-%    Let us denote with $(P_{1,i}, \lambda)$ the sub-path of temporal path $(P_{1,k},\lambda)$, that starts at $v_1$ and finishes at $v_i$.
-%    Suppose that, for any $v_i$ in $P$, we have that $(P_{1,i}, \lambda)$ is also the fastest temporal path from $u=v_1$ to $v_i$.
-%    Then we can determine travel delays on vertices of $P$ using the following equation
-%    \begin{equation}\label{eq:trav-delays-paths}
-%        \tau_{v_i}^{v_{i-1},v_{i+1}} = D_{1,i+1} - D_{1,i},
-%    \end{equation}
-%    for all $i \in \{2,3, \dots, k-1\}$.
-%\end{lemma}
 
@@
 Nevertheless, we prove in this section that we can still solve \deltaExact\ efficiently if the underlying graph is similar to a tree; more specifically we show the following result, which turns out to be non-trivial.
-
-% In this section we show how to generalize the polynomial-time algorithm for trees.
-Following the \emph{distance-from-triviality} parameterization paradigm~\cite{FJR13,GHN04}, we aim to obtain fixed-parameter tractability using a parameter that measures the distance from the underlying graph to a tree.
-\cref{thm:W1wrtFVS} tells us that we presumably cannot use the feedback vertex number (or any smaller measure such as the treewidth) as a parameter to obtain tractability.
-Hence, we choose the feedback edge number as a parameter and we present an FPT algorithm for \deltaExact\ parameterized by the feedback edge number of the underlying graph.
-
-% In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subseteq E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
-The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
-Determining $F$ can be done in linear time, by simply removing edges of a spanning tree (forest) from the given graph.
-%one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$.%, \ie $F = E(G) \setminus E(T)$.
-
+\end{comment}
 	\begin{figure}[t]
@@
 Let $u,v,x$ be three vertices in $G'$.
-We write $u \leadsto x \rightarrow v$ to denote a temporal path from $u$ to $v$ that passes through $x$, and then goes directly to $v$ (via one edge).
+We write $u \leadsto x \rightarrow v$ to denote a temporal path from $u$ to $v$ that passes through $x$, and then goes to $v$ (via one edge).
 %In the case when we want to guess the fastest path from $u$, that passes through vertex $x$ (not necessarily via one edge), and then goes directly to $v$ (via one edge), we write it as a fastest path of the form $u \leadsto x \rightarrow v$.
@@
 	\\
-	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $k^{O(k)}$ different possible such paths, therefore we make $k^{O(k^4)}$ guesses for these paths.
+	For fixed $S_{u,v}$ and $w \in U \cup Z^*$ we have $k^{O(k)}$ different possible such paths, therefore we make $k^{O(k^5)}$ guesses for these paths.
 	%
@@
 		In this case we only need to guess the following two fastest temporal paths 
-		$u \leadsto w \rightarrow z_2$
-		and $u \leadsto z \rightarrow z_{r-1}$.
-		Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
-		which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
-		In this case we do not introduce any new guesses, as we have aready guessed 
-		the fastest paths of the form
-		$u \leadsto w \rightarrow z_2$
-		and $u \leadsto z \rightarrow z_{r-1}$
-		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).
+		$v_i \leadsto w \rightarrow z_2$
+		and $v_i \leadsto z \rightarrow z_{r-1}$.
+		Each of these paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $z_j$, resp.~$z_{j+1}$,
+		which give us fastest temporal paths from $v_i$ to $z_j$ and from $v_i$ to $z_{j+1}$.
+		In this case we introduce only two more guesses.
+        We repeat this procedure for all pairs of segments. which results in creating $k^{O(k^5)}$ new guesses.
 	\end{enumerate}
-	Note that this case results also in knowing the fastest paths from the vertex $v_i \in S_{u,v}$ to $w,z \in S_{w,z}$ for all segments $S_{w,z}$, 
-	\ie we know the fastest paths from a fixed $v_i \in S_{u,v}$ to all vertices of interest in $U$.
 	%
@@
 	second one where $v_i, v_{i+1}$ are two incident vertices in $S_{u,v}$, that are furthest away from $w$.
-	\begin{comment}
-	In first case we know exactly how the fastest paths from $w$ to all vertices $v_j \in S_{u,v} \setminus \{v_i\}$
-	travel through the segment $S_{u,v}$ (\ie either through $u$ or $v$).
-	Therefore we have to guess how the fastest path from $w$ reaches vertex $v_i$,
-	we have two options, either it travels through $u \rightarrow v_2 \rightarrow \cdots \rightarrow v_{i-1} \rightarrow v_i$
-	or 
-	$v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1} \rightarrow v_i$.
-	Which produces two new guesses.
-	In the second case we know exactly how the fastest temporal path reaches $v_i$ and $v_{i+1}$, and consequently all the inner vertices.
-	Therefore no new guesses are needed.
-	Note that the above guesses, together with the guesses from G-\ref{FPT:guess-uToSegmentz2},
-	uniquely determine fastest temporal paths from $w$ to all vertices in $S_{u,v}$ 
-	(this also holds for the case when $w \in S_{u,v}$, \ie $w = u$ or $w = v$).
-	\end{comment}
-	All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
-	We repeat this for all vertices of interest, and all segments,
-	which produces $k^{O(k^2)}$ new guesses.
+	All together we make two guesses for each pair $w, S_{u,v}$.
+	We repeat this for all vertices in $U \cup Z^*$, and all segments,
+	which produces $k^{O(k^5)}$ new guesses.
 	%

### 2024-01-19 Figures/fig-fpt-equivClass.tex
added fig for proof of the equivalence classes

--- 2023-12-20 SAND2024/Figures/fig-guess4.tex
@@
 	\begin{tikzpicture}
-		%%%S_uv
-		\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
-		\node[vert,label=above:$v_2$] (v2) at (2,0) {};
-		\node[vert,label=above:$v_i$] (vi) at (3,0) {};
-		\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
-		\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
-		\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
-		\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);
 
-		%%%% node w
-		\node[vert,label=below:$w$] (w) at (4,-3) {};
+		\node [vert,label=below:$x$] (x) at (0, 0) {};
+		\node [vert,label=below:$z_2$] (z2) at (-1.5, 1) {};
+		\node [vert,label=above:$z_1$] (z1) at (-1.5, -1) {};
+		\node [vert,label=below:$y$] (y) at (7, 0) {};
 
+		\draw (z1) edge[] node[below, yshift=-1mm, text=black] {$t_1$}  (x);
+		\draw (z2) edge[] node[above, yshift= 1mm,  text=black] {$t_2$} (x);
+		\draw [red]
+		(x) edge[] [bend right] node[below, text=black] {$P$} 
+		node[vert, pos=0.87, color=black, fill=white] {}
+		node[pos=0.96,below, text=black] {$t_p$} (y) ;
 		\draw [blue]
-		(w) edge[dirwave] [out=160,in=285] (v1) 
-		(v1) -- (v2)
-		(v2) edge[diredge2] (vi);
-
-		\draw [red]
-		(w) edge[dirwave] [out=20,in=255] (vp) 
-		(vp) -- (vp1)
-		(vp1) edge[diredge2] (vi+1);
+		(x) edge[] [bend left] node[above, text=black] {$Q$} 
+		node[vert, pos=0.87, color=black, fill=white] {}
+		node[pos=0.96,above, text=black] {$t_q$}
+		(y) ;
 

### 2024-01-19 Figures/fig-fpt-equivClass.tex
small change to fig

@@
 
-		\draw (z1) edge[] node[below, yshift=-1mm, text=black] {$t_1$}  (x);
-		\draw (z2) edge[] node[above, yshift= 1mm,  text=black] {$t_2$} (x);
+		\draw (z1) edge[] node[below, pos=0.6, yshift=-1mm, text=black] {$t_1$}  (x);
+		\draw (z2) edge[] node[above, pos=0.6, yshift= 1mm,  text=black] {$t_2$} (x);
 		\draw [red]
-		(x) edge[] [bend right] node[below, text=black] {$P$} 
+		(x) edge[] [bend right] node[below] {$P$} 
 		node[vert, pos=0.87, color=black, fill=white] {}
@@
 		\draw [blue]
-		(x) edge[] [bend left] node[above, text=black] {$Q$} 
+		(x) edge[] [bend left] node[above] {$Q$} 
 		node[vert, pos=0.87, color=black, fill=white] {}

### 2024-01-19 SAND2024/SAND24-longversion.tex
Updates from Overleaf

@@
     Our objective is to demonstrate that either $P = Q$ or that $d(P_1, \lambda) = d(Q_1, \lambda)$ (and $d(P_2, \lambda) = d(Q_2, \lambda)$).
-    This implies that $z_1$ and $z_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_u)$ to reach $y$.
+    This implies that $z_1$ and $z_2$ use temporal paths that coincide on the vertices of $V(G) \setminus V(T_u)$ to reach $y$. For an illustration see \cref{fig:FPT-equivClass}.
+
+    \begin{figure}[t]
+	\centering
+	\includegraphics[width=0.6\columnwidth]{fig-fpt-equivClass}
+	\caption{An example of the situation in \cref{lemma:treeEquivClass-intVertices}.
+        We have two paths $Q$ (in blue) and $P$ (in red) from $x$ to $y$.
+        We assume that the fastest temporal path from $z_1$ to $y$ is $P_1 = \{z_1 u\} \cup P$,
+		and the fastest temporal path from $z_2$ to $y$ is $Q_2 = \{z_2 x\} \cup Q$.
+        %
+        We denote with $Q_1 = \{z_1 u\} \cup Q$ another temporal path from $z_1$ to $y$, 
+        with $P_2 = \{z_2 u\} \cup P$ another temporal path from $z_2$ to $y$.
+        The labels on the edges $z_1 x, z_2 x$ are $t_1,t_2$, respectively. Similar, the labels of the last edges of paths $P$ and $Q$ are  $t_p, t_q$, respectively.
+		\label{fig:FPT-equivClass}}
+\end{figure}
 

### 2024-03-26 SAND2024/SAND24-cameraReady.tex
SAND working on the camera ready version

--- 2024-01-19 SAND2024/SAND24-shortversion.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate, anonymous]{lipics-v2021}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
 %This is a template for producing LIPIcs articles. 
@@
 
-\vspace{0,2cm}
-\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
-	clearly marked Appendix to be read at the discretion of the Program Committee.}
+%\vspace{0,2cm}
+%\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a clearly marked Appendix to be read at the discretion of the Program Committee.}
 \end{abstract}
@@
 (resp.~the quickest communication delay between two moving satellites). 
-Furthermore, periodicity appears also in (the otherwise quite complex) social networks which describe the dynamics of people meeting~\cite{snapnets,sapiezynski2015tracking}, as every person individually follows mostly a daily routine~\cite{Arrighi2023Multi}.
-
-Although periodic temporal graphs have already been studied 
+Furthermore, periodicity appears also in (the otherwise quite complex) social networks which describe the dynamics of people meeting~\cite{snapnets,sapiezynski2015tracking}, as every person individually follows mostly a weekly routine.%~\cite{Arrighi2023Multi}.
+
+Expanding the work on periodic temporal graphs
 (see~\cite[Class 8]{casteigts2012time} and~\cite{Arrighi2023Multi,ErlebachS20,morawietz2021timecop,morawietz2020timecop}), 
-we make here the first attempt to understand the complexity of a graph realization problem in the context of temporal graphs. 
+our study represents the first attempt to understand the complexity of a graph realization problem in the context of temporal graphs. 
 Therefore, we focus in this paper on the most fundamental case, where all edges have the same period $\Delta$ 
@@
 To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.
-Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the Appendix.
+Due to space constraints, proofs of results marked with $\star$ are (partially) deferred to the full version on arXiv \cite{fullPaper}.
 
@@
 and therefore they are not necessarily known in advance~\cite{Kuhn2011Dynamic}.
+
+\subparagraph{Problem setting.}
+We would like to point out that the choice of our setting is not unique.
+There exist different variations of the problem, where each one gives interesting motivation to be considered.
+We now briefly mention a few of them, together with some of the potential obstacles one could encounter when studying them.
+As we already mentioned, the periodic temporal graphs can also be defined as temporal graphs where each edge $e$ admits a different period $\Delta_e$, or/and where each edge $e$ admits more than one time label per period $\Delta_e$.
+Because of simplicity, we focus only on a case with one label per edge and a common period $\Delta$.
+This should give us a good understanding of the problem and potential starting points for the research of the extended versions.
+In another setting, one could define the sought temporal paths differently.
+First of all, we could be looking for ``non-stric'' temporal paths. These are paths with non-decreasing consecutive labels (\ie a path can traverse more than a single edge in one time step).
+One of the potential drawbacks of this scenario is that the input matrix does not uniquely describe the underlying graph.
+In the next modification, one could also consider foremost or shortest temporal paths, instead of the fastest temporal paths.
+We believe that the complexity of the problem for these two variations does not differ significantly from the problem discussed in this paper.
+Some of our proof techniques and approaches can be easily adaptable to these modified settings and therefore certain results would carry over (for example, the NP-hardness).
+Lastly, the big question is why consider periodic temporal graphs and not simply just temporal graphs.
+One of the reasons is the fact that a periodic temporal graph is temporally connected whenever its underlying graph is connected, and therefore the input matrix $D$ consists of all finite values (which is also true in the case of realizing ``static'' graphs).
+Building upon this property, a periodic temporal graph with one label per edge is always temporally connected, while the same does not hold for a non-periodic temporal graph.
+Also for the case of non-periodic temporal graphs, some of our results and approaches carry over.
+For example, the NP-hardness and W[1]-hardness parameterized by the feedback vertex number of the underlying graph can be easily modified for the non-periodic temporal graph setting.
 
@@
 For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D_{v,v'}=1$) and then we provide the remaining entries of $D$.
-In the Appendix, we show how to obtain the result for a finite $\Delta$ (by introducing a so-called ``infinity gadget'') and a matrix $D$ of durations of fastest paths which only has finite entries.
+In the full paper \cite{fullPaper}, we show how to obtain the result for a finite $\Delta$ (by introducing a so-called ``infinity gadget'') and a matrix $D$ of durations of fastest paths which only has finite entries.
+
+\begin{figure}%[t]
+\noindent\makebox[\textwidth]{
+\centering
+\includegraphics{fig-W1-reduction}
+    }
+    \caption{Illustration of part of the underlying graph $G$ and a possible labeling.
+Edges incident with vertices $\hat{v}_1,\hat{v}_2$ of connector gadgets are omitted.
+Gray vertices form a feedback vertex set.
+    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
+    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
+    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
+    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
+    }\label{fig:hardness1}
+\end{figure}
 
@@
 Every \emph{edge selection gadget} is associated with a color combination $i,j$ in the \textsc{Multicolored Clique} instance, and its main purpose is to ``select'' an edge connecting a vertex from color $i$ with a vertex from color $j$.
-Roughly speaking, the edge selection gadget consists of $m$ paths, one for every edge in $F_{i,j}$ (see Figure~3 in the Appendix for reference).
+Roughly speaking, the edge selection gadget consists of $m$ paths, one for every edge in $F_{i,j}$ (see \cref{fig:hardness1} for reference).
 The distance matrix $D$ will enforce that the labels on those paths effectively order them temporally, that is, in particular, the labels on one of the paths will be smaller than the labels on all other paths.
@@
  The verification gadget for color $i$ is connected to all edge selection gadgets that involve color $i$.
-More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see Figure~3 in the Appendix for reference).
+More specifically, this is connected to every path corresponding to an edge at a position in the path that encodes the endpoint of color $i$ of that edge (again, see \cref{fig:hardness1} for reference).
 Intuitively, the distances in the verification gadget are only realizable if the selected edges all have the same endpoint of color $i$.
@@
 In the following, for every gadget, we give a formal description of the underlying graph of this gadget (\ie not the complete distance sub-matrix of the gadget).
-Due to space constraints, we defer the description of the distance matrix $D$ and the formal proof of correctness for the reduction to the Appendix.
+Due to space constraints, we defer the description of the distance matrix $D$ and the formal proof of correctness for the reduction to the full paper~\cite{fullPaper}.
 
@@
 Intuitively, this gadget is used to relate labels of different gadgets to each other.
-A formal description of these two gadgets is given in the Appendix.
-
-This finishes the description of the underlying graph $G$. For an illustration see Figure~3 in the Appendix. We can observe that the vertex set containing
+A formal description of these two gadgets is given in the full paper~\cite{fullPaper}.
+
+This finishes the description of the underlying graph $G$. For an illustration see \cref{fig:hardness1}. We can observe that the vertex set containing
 %\begin{itemize}
@@
 
-As mentioned before, due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the Appendix.
+As mentioned before, due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the full paper~\cite{fullPaper}.
 \end{proof}
@@
 In this section, to complement the discussed hardness aspects of \deltaExact, we present some algorithmic results.
-We start by restricting the underlying graph $G$ of the input matrix $D$ of \deltaExact\ to be a tree and get the following.
+We start by restricting the underlying graph $G$ of the input matrix~$D$ of \deltaExact\ to be a tree and get the following.
 \begin{theorem}[$\star$] \label{thm:deltaExact-PolyTimeTrees}
@@
 We now present the first part of our FPT algorithm, that is, identifying important vertices and guessing information about the fastest temporal paths.
-A full description of the algorithm is deferred to the Appendix.
+A full description of the algorithm is deferred to the full paper~\cite{fullPaper}.
 
@@
 Since $U \cup U^{\ast} \cup Z^{\ast}\in O(k^2)$ and there are $k^{O(k)}$ possibilities for a sequence of edges between a fixed vertex pair, we have $k^{O(k^5)}$ overall possible guesses.
-We  defer further details to the Appendix (see guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-6}}}).
+We  defer further details to the full paper~\cite{fullPaper} (see guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-6}}}).
 
@@
 	%
-	For an example see Figure~8a in the Appendix.
+	For an example see~\cref{fig:FPT-guessG4}.
 	\item \label{FPT:guess-uToSegmentz2}
@@
 	%
-	For an example see Figure~8b in the Appendix.
+	For an example see~\cref{fig:FPT-guessG5}.
 	%All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.
@@
 	%
-	For an example see Figure~8c in the Appendix.
+	For an example see~\cref{fig:FPT-guessG5}.
 	\item \label{FPT:guess-splitFromUtoAnotherSegment}
@@
 	%
-	For an example see Figure~8d in the Appendix.
-	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.
+	For an example see~\cref{fig:FPT-guessG6}.
+	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to the full paper~\cite{fullPaper}.
 	% counter for guesses continues
@@
 
-There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that are deferred to the Appendix. 
-We prove in the Appendix that, for all guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-12}}}, there are in total at most $f(k)$ possible choices, and for each one of them we create an ILP with at most $f(k)$ variables and at most $f(k)\cdot |D|^{O(1)}$ constraints.
+\begin{figure}[t]
+	\centering
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{0.88\linewidth}{!}{
+			\includegraphics{fig-guess1}}
+		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
+			and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
+			\label{fig:FPT-guessG4}}
+	\end{subfigure}
+	\quad
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{0.88\linewidth}{!}{
+
+			\includegraphics{fig-guess2}}
+		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+			\label{fig:FPT-guessG5}}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.48\textwidth}
+		\vspace{-0.4cm}
+        \centering
+		\resizebox{0.98\linewidth}{!}{
+			%
+			\includegraphics{fig-guess3}}
+		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
+			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
+			and guessed the fastest paths of the form
+			$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
+			and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
+			\label{fig:FPT-guessG6}}
+	\end{subfigure}
+	\quad
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\resizebox{0.88\linewidth}{!}{
+			\includegraphics{fig-guess4}}
+		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
+			we
+			calculated its corresponding split vertex $v_i \in S_{u,v}$,
+			and guessed the fastest paths of the form
+			$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
+			and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
+			\label{fig:FPT-guessG7}}
+	\end{subfigure}
+	\caption{Illustration of the guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
+\end{figure}
+
+There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that are deferred to the full paper~\cite{fullPaper}. 
+We prove in~\cite{fullPaper} that, for all guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-12}}}, there are in total at most $f(k)$ possible choices, and for each one of them we create an ILP with at most $f(k)$ variables and at most $f(k)\cdot |D|^{O(1)}$ constraints.
 Each of these ILPs can be solved in FPT time by Lenstra's Theorem~\cite{Lenstra1983Integer}.
@@
 %which ensures that each ILP is solved in an FPT-time.
-For detailed explanation and proofs of this part see Appendix.
+For detailed explanation and proofs of this part see~\cite{fullPaper}.
 
@@
 %\subparagraph{Further parameterizations.} 
-There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
+There are several structural parameters which can be considered to obtain tractability which are either larger than or incomparable to the feedback vertex number.
 We believe that the \emph{vertex cover number} or the \emph{tree depth} are promising candidates.
@@
 A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
-Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
+%Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
 

### 2024-03-26 SAND2024/SAND24-cameraReady.tex
Camera ready version SAND 24

@@
 
+\begin{comment}
 \subparagraph{Problem setting.}
@@
 For example, the NP-hardness and W[1]-hardness parameterized by the feedback vertex number of the underlying graph can be easily modified for the non-periodic temporal graph setting.
+\end{comment}
 
@@
 For simplicity of the presentation of the reduction, we describe the underlying graph $G$ (which directly implies the entries of $D$ where $D_{v,v'}=1$) and then we provide the remaining entries of $D$.
-In the full paper \cite{fullPaper}, we show how to obtain the result for a finite $\Delta$ (by introducing a so-called ``infinity gadget'') and a matrix $D$ of durations of fastest paths which only has finite entries.
+At the end of the proof, we show how to obtain the result for a finite $\Delta$ (by introducing a so-called ``infinity gadget'') and a matrix $D$ of durations of fastest paths which only has finite entries.
 
@@
 In the following, for every gadget, we give a formal description of the underlying graph of this gadget (\ie not the complete distance sub-matrix of the gadget).
-Due to space constraints, we defer the description of the distance matrix $D$ and the formal proof of correctness for the reduction to the full paper~\cite{fullPaper}.
+Due to space constraints, we defer the description of the distance matrix $D$ and the formal proof of correctness for the reduction to~\cite{fullPaper}.
 
@@
 Intuitively, this gadget is used to relate labels of different gadgets to each other.
-A formal description of these two gadgets is given in the full paper~\cite{fullPaper}.
+A formal description of these two gadgets is given in~\cite{fullPaper}.
 
@@
 
-As mentioned before, due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to the full paper~\cite{fullPaper}.
+As mentioned before, due to space constraints, we defer the description of the distance matrix $D$ and a formal correctness proof of the reduction to~\cite{fullPaper}.
+
+\emph{Infinity gadget.} Finally, we show how to get rid of the infinity entries in $D$ and how to allow a finite $\Delta$.
+To this end, we introduce the \emph{infinity gadget}.
+We add four vertices $z_1, z_2, z_3, z_4$ to the graph and we set $\Delta=n^{11}$.
+Let $V$ denote the set of all remaining vertices.
+We set the following durations.
+\begin{itemize}
+    \item For all $v\in V$ we set $d(z_1,v)=2$, $d(z_2,v)=d(v,z_2)=1$, $d(z_3,v)=d(v,z_3)=1$, and $d(z_4,v)=2$.
+    Furthermore, we set $d(v,z_1)=n^{11}$ and $d(v,z_4)=n^{10}-1$.
+    \item We set $d(z_1,z_2)=d(z_2,z_1)=1$, $d(z_2,z_3)=d(z_3,z_2)=1$, and $d(z_3,z_4)=d(z_4,z_3)=1$.
+    \item We set $d(z_1,z_3)=3$, $d(z_3,z_1)=n^{11}-1$, $d(z_2,z_4)=n^{10}-2$, and $d(z_4,z_2)=n^{11}-n^{10}+4$.
+    \item We set $d(z_1,z_4)=n^{10}$ and $d(z_4,z_1)=2n^{11}-n^{10}+2$.
+    \item For every pair of vertices $v,v'\in V$ where previously the duration of a fastest path from $v$ to $v'$ was specified to be infinite, we set $d(v,v')=n^{10}$.
+\end{itemize}
+Now we analyse which implications we get for the labels on the newly introduced edges.
+Assume $\lambda(\{z_1,z_2\})=t$, then we get the following.
+%\begin{itemize}
+    %\item 
+    For all $v\in V$ we have that $d(z_1,v)=2$ and hence we get that $\lambda(\{z_2,v\})=t+1$. 
+    %\item 
+    Since $d(z_1,z_4)=n^{10}$, we have that $\lambda(z_3,z_4)=t+n^{10}-1$.
+    From this follows that for all $v\in V$, since $d(z_4,v)=2$, that $\lambda(\{z_3,v\})=t+n^{10}$.
+    Finally, since $d(z_1,z_3)=3$, we have that $\lambda(\{z_2,z_3\})=t+2$.
+%\end{itemize}
+For an illustration see \cref{fig:hardness2}.
+It is easy to check that all duration requirements between vertex pairs in $\{z_1,z_2,z_3,z_4\}$ are met and that all duration requirements between each vertex $v\in V$ and each vertex in  $\{z_1,z_2,z_3,z_4\}$ are met.
+Furthermore, it is easy to check that the gadget increases the feedback vertex set by two ($z_2$ and $z_3$ need to be added).
+
+\begin{figure}[t]
+%\noindent\makebox[\textwidth]{
+\centering
+
+\includegraphics{fig-W1-infinity}
+    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
+\end{figure}
+
+Lastly, consider two vertices $v,v'\in V$.
+Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$.
+Furthermore, if $D$ is a \textsc{Yes}-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$.
+This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$.
+Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$.
+For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$.
+We can conclude that the originally constructed instance $D$ is a \textsc{Yes}-instance if and only if it remains a \textsc{Yes}-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
 \end{proof}
@@
 We now present the first part of our FPT algorithm, that is, identifying important vertices and guessing information about the fastest temporal paths.
-A full description of the algorithm is deferred to the full paper~\cite{fullPaper}.
+A full description of the algorithm is deferred to~\cite{fullPaper}.
 
@@
 Since $U \cup U^{\ast} \cup Z^{\ast}\in O(k^2)$ and there are $k^{O(k)}$ possibilities for a sequence of edges between a fixed vertex pair, we have $k^{O(k^5)}$ overall possible guesses.
-We  defer further details to the full paper~\cite{fullPaper} (see guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-6}}}).
+We  defer further details to~\cite{fullPaper} (see guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-6}}}).
 
@@
 	For an example see~\cref{fig:FPT-guessG6}.
-	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to the full paper~\cite{fullPaper}.
+	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to~\cite{fullPaper}.
 	% counter for guesses continues
@@
 
-There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that are deferred to the full paper~\cite{fullPaper}. 
+There are two more guesses \textcolor{lipicsGray}{\textsf{\textbf{G-11}}} and \textcolor{lipicsGray}{\textsf{\textbf{G-12}}} that are deferred to~\cite{fullPaper}. 
 We prove in~\cite{fullPaper} that, for all guesses \textcolor{lipicsGray}{\textsf{\textbf{G-1}}} to \textcolor{lipicsGray}{\textsf{\textbf{G-12}}}, there are in total at most $f(k)$ possible choices, and for each one of them we create an ILP with at most $f(k)$ variables and at most $f(k)\cdot |D|^{O(1)}$ constraints.

### 2024-03-29 SAND2024/SAND24-cameraReady.tex
Camera ready version for SAND

@@
 
-\author{Hendrik~Molter}{Department of Computer Science, Ben-Gurion~University~of~the~Negev, Beer-Sheva, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1456/18, and the ERC, grant number 949707.}
+\author{Hendrik~Molter}{Department of Computer Science, Ben-Gurion~University~of~the~Negev, Beer-Sheva, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant nr.~1456/18, and by the European Union's Horizon Europe research and innovation programme under grant agreement 949707.}
 
@@
 To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting.
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
+However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22,KMZ23}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
 
@@
 \centering
-\includegraphics{fig-W1-reduction}
+\includegraphics{fig-W1-reduction_nolabels}
     }

### 2024-03-29 SAND2024/SAND24-longversion.tex
Camera ready version for SAND

@@
 (resp.~the quickest communication delay between two moving satellites). 
-Furthermore, periodicity appears also in (the otherwise quite complex) social networks which describe the dynamics of people meeting~\cite{snapnets,sapiezynski2015tracking}, as every person individually follows mostly a daily routine~\cite{Arrighi2023Multi}.
-
-Although periodic temporal graphs have already been studied 
+Furthermore, periodicity appears also in (the otherwise quite complex) social networks which describe the dynamics of people meeting~\cite{snapnets,sapiezynski2015tracking}, as every person individually follows mostly a weekly routine.%~\cite{Arrighi2023Multi}.
+
+Expanding the work on periodic temporal graphs have already been studied 
 (see~\cite[Class 8]{casteigts2012time} and~\cite{Arrighi2023Multi,ErlebachS20,morawietz2021timecop,morawietz2020timecop}), 
-we make here the first attempt to understand the complexity of a graph realization problem in the context of temporal graphs. 
+our study represents the first attempt to understand the complexity of a graph realization problem in the context of temporal graphs. 
 Therefore, we focus in this paper on the most fundamental case, where all edges have the same period $\Delta$ 
@@
 
-\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger or incomparable to the feedback vertex number.
+\subparagraph{Further parameterizations.} There are several structural parameters which can be considered to obtain tractability which are either larger than or incomparable to the feedback vertex number.
 \begin{itemize}

### 2024-03-31 SAND2024/SAND24-cameraReady.tex
Camera ready SAND24 submitted
Final camera ready version

@@
 Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
+\relatedversiondetails{Full Version}{https://arxiv.org/abs/2302.08860}
 
@@
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
+\EventEditors{Arnaud Casteigts and Fabian Kuhn}
 \EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventLongTitle{3rd Symposium on Algorithmic Foundations of Dynamic Networks (SAND 2024)}
+\EventShortTitle{SAND 2024}
+\EventAcronym{SAND}
+\EventYear{2024}
+\EventDate{June 5-7, 2024}
+\EventLocation{Patras, Greece}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
+\SeriesVolume{292}
+\ArticleNo{3}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. 
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22,KMZ23}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
+Very recently, Erlebach et al.~\cite{ErlebachMW-SAND24} have built upon our results and, among others, studied the case where edges might appear more than once in each period. 
+Many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22,KMZ23}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
 
@@
 We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period.
-A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
+A well-motivated variant (especially from the network design perspective) of our problem is to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
+This problem variant has very recently been studied by Mertzios et al.~\cite{MMS24}.
 %Our work gives a starting point for many interesting future research directions such as the two mentioned examples.

### 2024-03-31 SAND2024/SAND24-longversion.tex
Final camera ready version

@@
 To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. 
-However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
+Very recently, Erlebach et al.~\cite{ErlebachMW-SAND24} have built upon our results and, among others, studied the case where edges might appear more than once in each period. 
+Many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.
 
@@
 A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations.
+This problem variant has very recently been studied by Mertzios et al.~\cite{MMS24}.
 %Our work gives a starting point for many interesting future research directions such as the two mentioned examples.

### 2024-03-31 Arxiv-31-3-24/arxiv.tex
added arxiv version

--- 2024-03-31 SAND2024/SAND24-longversion.tex
@@
 \usepackage{graphicx}
-\graphicspath{{../Figures/}}
+%\graphicspath{{Figures/}}
 
@@
 
-\bibliography{bibliography}
+\begin{thebibliography}{10}
+
+	\bibitem{akrida2017complexity}
+	Eleni~C Akrida, Leszek G{\k{a}}sieniec, George~B. Mertzios, and Paul~G
+	Spirakis.
+	\newblock The complexity of optimal design of temporally connected graphs.
+	\newblock {\em Theory of Computing Systems}, 61:907--944, 2017.
+
+	\bibitem{Akrida-explorer-21}
+	Eleni~C. Akrida, George~B. Mertzios, Paul~G. Spirakis, and Christoforos
+	Raptopoulos.
+	\newblock The temporal explorer who returns to the base.
+	\newblock {\em Journal of Computer and System Sciences}, 120:179--193, 2021.
+
+	\bibitem{Arrighi2023Multi}
+	Emmanuel Arrighi, Niels Gr{\"u}ttemeier, Nils Morawietz, Frank Sommer, and
+	Petra Wolf.
+	\newblock Multi-parameter analysis of finding minors and subgraphs
+	in edge-periodic temporal graphs.
+	\newblock In {\em Proceedings of the 48th International Conference on Current
+		Trends in Theory and Practice of Computer Science (SOFSEM)}, pages 283--297,
+	2023.
+
+	\bibitem{augustine2022distributed}
+	John Augustine, Keerti Choudhary, Avi Cohen, David Peleg, Sumathi
+	Sivasubramaniam, and Suman Sourav.
+	\newblock Distributed graph realizations.
+	\newblock {\em IEEE Transactions on Parallel and Distributed Systems},
+	33(6):1321--1337, 2022.
+
+	\bibitem{barNoy2020efficiently}
+	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
+	\newblock Efficiently realizing interval sequences.
+	\newblock {\em SIAM Journal on Discrete Mathematics}, 34(4):2318--2337, 2020.
+
+	\bibitem{Bar-NoyCPR20}
+	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
+	\newblock Graph realizations: Maximum degree in vertex neighborhoods.
+	\newblock In {\em Proceedings of the 17th Scandinavian Symposium and Workshops
+		on Algorithm Theory (SWAT)}, pages 10:1--10:17, 2020.
+
+	\bibitem{barNoy2021composed}
+	Amotz Bar{-}Noy, David Peleg, Mor Perry, and Dror Rawitz.
+	\newblock Composed degree-distance realizations of graphs.
+	\newblock In {\em Proceedings of the 32nd International Workshop on
+		Combinatorial Algorithms ({IWOCA})}, pages 63--77, 2021.
+
+	\bibitem{barNoy2022GraphRealization}
+	Amotz Bar-Noy, David Peleg, Mor Perry, and Dror Rawitz.
+	\newblock Graph realization of distance sets.
+	\newblock In {\em Proceedings of the 47th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 13:1--13:14,
+	2022.
+
+	\bibitem{behzad1976eccentric}
+	Mehdi Behzad and James~E Simpson.
+	\newblock Eccentric sequences and eccentric sets in graphs.
+	\newblock {\em Discrete Mathematics}, 16(3):187--193, 1976.
+
+	\bibitem{bixby1988almost}
+	Robert~E Bixby and Donald~K Wagner.
+	\newblock An almost linear-time algorithm for graph realization.
+	\newblock {\em Mathematics of Operations Research}, 13(1):99--123, 1988.
+
+	\bibitem{xuan_computing_2003}
+	Binh-Minh Bui-Xuan, Afonso Ferreira, and Aubin Jarry.
+	\newblock Computing shortest, fastest, and foremost journeys in dynamic
+	networks.
+	\newblock {\em International Journal of Foundations of Computer Science},
+	14(02):267--285, 2003.
+
+	\bibitem{CasteigtsCS22}
+	Arnaud Casteigts, Timoth{\'{e}}e Corsini, and Writika Sarkar.
+	\newblock Invited paper: Simple, strict, proper, happy: A study of reachability
+	in temporal graphs.
+	\newblock In {\em Proceedings of the 24th International Symposium on
+		Stabilization, Safety, and Security of Distributed Systems ({SSS})}, pages
+	3--18, 2022.
+
+	\bibitem{casteigts2012time}
+	Arnaud Casteigts, Paola Flocchini, Walter Quattrociocchi, and Nicola Santoro.
+	\newblock Time-varying graphs and dynamic networks.
+	\newblock {\em International Journal of Parallel, Emergent and Distributed
+		Systems}, 27(5):387--408, 2012.
+
+	\bibitem{casteigts2021finding}
+	Arnaud Casteigts, Anne-Sophie Himmel, Hendrik Molter, and Philipp Zschoche.
+	\newblock Finding temporal paths under waiting time constraints.
+	\newblock {\em Algorithmica}, 83(9):2754--2802, 2021.
+
+	\bibitem{chen1966realization}
+	Wai-Kai Chen.
+	\newblock On the realization of a $(p, s)$-digraph with prescribed degrees.
+	\newblock {\em Journal of the Franklin Institute}, 281(5):406--422, 1966.
+
+	\bibitem{chung2001distance}
+	Fan Chung, Mark Garrett, Ronald Graham, and David Shallcross.
+	\newblock Distance realization problems with applications to internet
+	tomography.
+	\newblock {\em Journal of Computer and System Sciences}, 63(3):432--448, 2001.
+
+	\bibitem{culberson1989fast}
+	Joseph~C. Culberson and Piotr Rudnicki.
+	\newblock A fast algorithm for constructing trees from distance matrices.
+	\newblock {\em Information Processing Letters}, 30(4):215--220, 1989.
+
+	\bibitem{Cyg+15}
+	Marek Cygan, Fedor~V. Fomin, {\L{}}ukasz Kowalik, Daniel Lokshtanov,
+	D{\'{a}}niel Marx, Marcin Pilipczuk, Micha\l{} Pilipczuk, and Saket Saurabh.
+	\newblock {\em Parameterized Algorithms}.
+	\newblock Springer, 2015.
+
+	\bibitem{deligkas2022optimizing}
+	Argyrios Deligkas and Igor Potapov.
+	\newblock Optimizing reachability sets in temporal graphs by delaying.
+	\newblock {\em Information and Computation}, 285:104890, 2022.
+
+	\bibitem{DF13}
+	Rodney~G. Downey and Michael~R. Fellows.
+	\newblock {\em Fundamentals of Parameterized Complexity}.
+	\newblock Texts in Computer Science. Springer, London, 2013.
+
+	\bibitem{enright2021deleting}
+	Jessica Enright, Kitty Meeks, George~B. Mertzios, and Viktor Zamaraev.
+	\newblock Deleting edges to restrict the size of an epidemic in temporal
+	networks.
+	\newblock {\em Journal of Computer and System Sciences}, 119:60--77, 2021.
+
+	\bibitem{enright2021assigning}
+	Jessica Enright, Kitty Meeks, and Fiona Skerman.
+	\newblock Assigning times to minimise reachability in temporal graphs.
+	\newblock {\em Journal of Computer and System Sciences}, 115:169--186, 2021.
+
+	\bibitem{EMM22}
+	Jessica~A. Enright, Kitty Meeks, and Hendrik Molter.
+	\newblock Counting temporal paths.
+	\newblock In {\em Proceedings of the 40th International Symposium on
+		Theoretical Aspects of Computer Science ({STACS})}, volume 254, pages
+	30:1--30:19, 2023.
+
+	\bibitem{erdos1960graphs}
+	Paul Erd{\H{o}}s and Tibor Gallai.
+	\newblock Graphs with prescribed degrees of vertices.
+	\newblock {\em Mat. Lapok}, 11:264--274, 1960.
+
+	\bibitem{erlebach2021temporal}
+	Thomas Erlebach, Michael Hoffmann, and Frank Kammer.
+	\newblock On temporal graph exploration.
+	\newblock {\em Journal of Computer and System Sciences}, 119:1--18, 2021.
+
+	\bibitem{ErlebachMW-SAND24}
+	Thomas Erlebach, Nils Morawietz, and Petra Wolf.
+	\newblock Parameterized algorithms for multi-label periodic temporal graph
+	realization.
+	\newblock In {\em Proceedings of the 3rd Symposium on Algorithmic Foundations
+		of Dynamic Networks ({SAND})}, pages 14:1--14:16, 2024.
+	\newblock \href {https://doi.org/10.4230/LIPIcs.SAND.2024.14}
+	{\path{doi:10.4230/LIPIcs.SAND.2024.14}}.
+
+	\bibitem{ErlebachS20}
+	Thomas Erlebach and Jakob~T. Spooner.
+	\newblock A game of cops and robbers on graphs with periodic edge-connectivity.
+	\newblock In {\em Proceedings of the 46th International Conference on Current
+		Trends in Theory and Practice of Informatics (SOFSEM)}, pages 64--75, 2020.
+
+	\bibitem{fellows2009multipleinterval}
+	Michael~R. Fellows, Danny Hermelin, Frances Rosamond, and St{\'e}phane
+	Vialette.
+	\newblock On the parameterized complexity of multiple-interval graph problems.
+	\newblock {\em Theoretical Computer Science}, 410(1):53--61, 2009.
+
+	\bibitem{FJR13}
+	Michael~R. Fellows, Bart M.~P. Jansen, and Frances~A. Rosamond.
+	\newblock Towards fully multivariate algorithmics: {P}arameter ecology and the
+	deconstruction of computational complexity.
+	\newblock {\em European Journal of Combinatorics}, 34(3):541--566, 2013.
+
+	\bibitem{FG06}
+	J{\"o}rg Flum and Martin Grohe.
+	\newblock {\em Parameterized Complexity Theory}, volume XIV of {\em Texts in
+		Theoretical Computer Science. An EATCS Series}.
+	\newblock Springer, 2006.
+
+	\bibitem{Flu+19a}
+	Till Fluschnik, Hendrik Molter, Rolf Niedermeier, Malte Renken, and Philipp
+	Zschoche.
+	\newblock Temporal graph classes: A view through temporal separators.
+	\newblock {\em Theoretical Computer Science}, 806:197--218, 2020.
+
+	\bibitem{frank1992augmenting}
+	Andr{\'a}s Frank.
+	\newblock Augmenting graphs to meet edge-connectivity requirements.
+	\newblock {\em SIAM Journal on Discrete Mathematics}, 5(1):25--53, 1992.
+
+	\bibitem{frank1994connectivity}
+	Andr{\'a}s Frank.
+	\newblock Connectivity augmentation problems in network design.
+	\newblock {\em Mathematical Programming: State of the Art 1994}, 1994.
+
+	\bibitem{frank1970connectivity}
+	H.~Frank and Wushow Chou.
+	\newblock Connectivity considerations in the design of survivable networks.
+	\newblock {\em IEEE Transactions on Circuit Theory}, 17(4):486--490, 1970.
+
+	\bibitem{FMNR22a}
+	Eugen F\"uchsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
+	\newblock Delay-robust routes in temporal graphs.
+	\newblock In {\em Proceedings of the 39th International Symposium on
+		Theoretical Aspects of Computer Science (STACS)}, pages 30:1--30:15, 2022.
+
+	\bibitem{FuchsleMNR22}
+	Eugen F{\"{u}}chsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
+	\newblock Temporal connectivity: Coping with foreseen and unforeseen delays.
+	\newblock In {\em Proceedings of the 1st Symposium on Algorithmic Foundations
+		of Dynamic Networks ({SAND})}, pages 17:1--17:17, 2022.
+
+	\bibitem{fulkerson1960zero}
+	D.R. Fulkerson.
+	\newblock Zero-one matrices with zero trace.
+	\newblock {\em Pacific Journal of Mathematics}, 10(3):831--836, 1960.
+
+	\bibitem{GolovachM17}
+	Petr~A. Golovach and George~B. Mertzios.
+	\newblock Graph editing to a given degree sequence.
+	\newblock {\em Theoretical Computer Science}, 665:1--12, 2017.
+
+	\bibitem{GolumbicTrenk04}
+	Martin~Charles Golumbic and Ann~N. Trenk.
+	\newblock {\em Tolerance Graphs}.
+	\newblock Cambridge Studies in Advanced Mathematics. Cambridge University
+	Press, 2004.
+
+	\bibitem{gomory1961multi}
+	Ralph~E Gomory and Tien~Chung Hu.
+	\newblock Multi-terminal network flows.
+	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
+	9(4):551--570, 1961.
+
+	\bibitem{grotschel1995design}
+	Martin Gr{\"o}tschel, Clyde~L Monma, and Mechthild Stoer.
+	\newblock Design of survivable networks.
+	\newblock {\em Handbooks in Operations Research and Management Science},
+	7:617--672, 1995.
+
+	\bibitem{GHN04}
+	Jiong Guo, Falk H{\"u}ffner, and Rolf Niedermeier.
+	\newblock A structural view on parameterizing problems: Distance from
+	triviality.
+	\newblock In {\em Proceedings of the 1st International Workshop on
+		Parameterized and Exact Computation (IWPEC)}, pages 162--173, 2004.
+
+	\bibitem{hakimi1962realizability}
+	S.~Louis Hakimi.
+	\newblock On realizability of a set of integers as degrees of the vertices of a
+	linear graph.~{I}.
+	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
+	10(3):496--506, 1962.
+
+	\bibitem{hakimi1965distance}
+	S.~Louis Hakimi and Stephen~S. Yau.
+	\newblock Distance matrix of a graph and its realizability.
+	\newblock {\em Quarterly of applied mathematics}, 22(4):305--317, 1965.
+
+	\bibitem{hell2009linear}
+	Pavol Hell and David Kirkpatrick.
+	\newblock Linear-time certifying algorithms for near-graphical sequences.
+	\newblock {\em Discrete Mathematics}, 309(18):5703--5713, 2009.
+
+	\bibitem{KKK00}
+	David Kempe, Jon~M. Kleinberg, and Amit Kumar.
+	\newblock Connectivity and inference problems for temporal networks.
+	\newblock {\em Journal of Computer and System Sciences}, 64(4):820--842, 2002.
+
+	\bibitem{klobas2023interference}
+	Nina Klobas, George~B. Mertzios, Hendrik Molter, Rolf Niedermeier, and Philipp
+	Zschoche.
+	\newblock Interference-free walks in time: Temporally disjoint paths.
+	\newblock {\em Autonomous Agents and Multi-Agent Systems}, 37(1):1, 2023.
+
+	\bibitem{KlobasMMS22}
+	Nina Klobas, George~B. Mertzios, Hendrik Molter, and Paul~G. Spirakis.
+	\newblock The complexity of computing optimum labelings for temporal
+	connectivity.
+	\newblock In {\em Proceedings of the 47th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 62:1--62:15,
+	2022.
+
+	\bibitem{Kuhn2011Dynamic}
+	Fabian Kuhn and Rotem Oshman.
+	\newblock Dynamic networks: Models and algorithms.
+	\newblock {\em SIGACT News}, 42(1):82–96, mar 2011.
+
+	\bibitem{Lenstra1983Integer}
+	Hendrik~W. Lenstra.
+	\newblock Integer programming with a fixed number of variables.
+	\newblock {\em Mathematics of Operations Research}, 8:538--548, 1983.
+
+	\bibitem{snapnets}
+	Jure Leskovec and Andrej Krevl.
+	\newblock {SNAP Datasets}: {Stanford} large network dataset collection.
+	\newblock \url{http://snap.stanford.edu/data}, June 2014.
+
+	\bibitem{lesniak1975eccentric}
+	Linda Lesniak.
+	\newblock Eccentric sequences in graphs.
+	\newblock {\em Periodica Mathematica Hungarica}, 6:287--293, 1975.
+
+	\bibitem{McConnellS02}
+	Ross~M. McConnell and Jeremy~P. Spinrad.
+	\newblock Construction of probe interval models.
+	\newblock In {\em Proceedings of the 13th Annual {ACM-SIAM} Symposium on
+		Discrete Algorithms (SODA)}, pages 866--875, 2002.
+
+	\bibitem{McMorris98}
+	F.R. McMorris, Chi Wang, and Peisen Zhang.
+	\newblock On probe interval graphs.
+	\newblock {\em Discrete Applied Mathematics}, 88(1):315--324, 1998.
+	\newblock Computational Molecular Biology DAM - CMB Series.
+
+	\bibitem{MertziosMS19}
+	George~B. Mertzios, Othon Michail, and Paul~G. Spirakis.
+	\newblock Temporal network optimization subject to connectivity constraints.
+	\newblock {\em Algorithmica}, 81(4):1416--1449, 2019.
+
+	\bibitem{Mertzios-transitivity21}
+	George~B. Mertzios, Hendrik Molter, Malte Renken, Paul~G. Spirakis, and Philipp
+	Zschoche.
+	\newblock The complexity of transitively orienting temporal graphs.
+	\newblock In {\em Proceedings of the 46th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 75:1--75:18,
+	2021.
+
+	\bibitem{MMS24}
+	George~B. Mertzios, Hendrik Molter, and Paul~G. Spirakis.
+	\newblock Realizing temporal transportation trees.
+	\newblock {\em CoRR}, abs/2403.18513, 2024.
+	\newblock URL: \url{https://doi.org/10.48550/arXiv.2403.18513}, \href
+	{http://arxiv.org/abs/2403.18513} {\path{arXiv:2403.18513}}.
+
+	\bibitem{MolterRZ21}
+	Hendrik Molter, Malte Renken, and Philipp Zschoche.
+	\newblock Temporal reachability minimization: Delaying vs. deleting.
+	\newblock In {\em Proceedings of the 46th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, pages 76:1--76:15,
+	2021.
+
+	\bibitem{morawietz2020timecop}
+	Nils Morawietz, Carolin Rehs, and Mathias Weller.
+	\newblock A timecop's work is harder than you think.
+	\newblock In {\em Proceedings of the 45th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, volume 170, pages
+	71--1, 2020.
+
+	\bibitem{morawietz2021timecop}
+	Nils Morawietz and Petra Wolf.
+	\newblock A timecop’s chase around the table.
+	\newblock In {\em Proceedings of the 46th International Symposium on
+		Mathematical Foundations of Computer Science (MFCS)}, 2021.
+
+	\bibitem{Patrinos-Hakimi-72}
+	A.N. Patrinos and S.~Louis Hakimi.
+	\newblock The distance matrix of a graph and its tree realization.
+	\newblock {\em Quarterly of Applied Mathematics}, 30:255--269, 1972.
+
+	\bibitem{Rubei16}
+	Elena Rubei.
+	\newblock Weighted graphs with distances in given ranges.
+	\newblock {\em Journal of Classification}, 33:282–--297, 2016.
+
+	\bibitem{sapiezynski2015tracking}
+	Piotr Sapiezynski, Arkadiusz Stopczynski, Radu Gatej, and Sune Lehmann.
+	\newblock Tracking human mobility using wifi signals.
+	\newblock {\em PloS one}, 10(7):e0130824, 2015.
+
+	\bibitem{Schaefer1978complexity}
+	Thomas~J. Schaefer.
+	\newblock The complexity of satisfiability problems.
+	\newblock In {\em Proceedings of the 10th Annual {ACM} Symposium on Theory of
+		Computing (STOC)}, pages 216--226, 1978.
+
+	\bibitem{Tamura93}
+	H.~Tamura, M.~Sengoku, S.~Shinoda, and T.~Abe.
+	\newblock Realization of a network from the upper and lower bounds of the
+	distances (or capacities) between vertices.
+	\newblock In {\em Proceedings of the 1993 IEEE International Symposium on
+		Circuits and Systems (ISCAS)}, pages 2545–--2548, 1993.
+
+	\bibitem{Wu2016Efficient}
+	Huanhuan Wu, James Cheng, Yiping Ke, Silu Huang, Yuzhen Huang, and Hejun Wu.
+	\newblock Efficient algorithms for temporal path computation.
+	\newblock {\em {IEEE} Transactions on Knowledge and Data Engineering},
+	28(11):2927--2942, 2016.
+
+	\bibitem{Zsc+19}
+	Philipp Zschoche, Till Fluschnik, Hendrik Molter, and Rolf Niedermeier.
+	\newblock The complexity of finding separators in temporal graphs.
+	\newblock {\em Journal of Computer and System Sciences}, 107:72--92, 2020.
+
+\end{thebibliography}
 

### 2024-05-01 Arxiv-30-4-24/arxiv-30-4-24.tex
Changes 1st May 2024

--- 2024-03-31 Arxiv-31-3-24/arxiv.tex
@@
 	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
-	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
+	\Delta $ and that 
+ \begin{equation}
+t_{v_{2}} \leq t_{u_{2}} \leq t_{v_{2}}+\Delta -1 \leq 2\Delta -1.
+\label{basic-ineq-0}
+\end{equation}
     From Assumption~\ref{assumption1-FPT} we get
@@
 		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
-		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
-		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
-		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.
+		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{2}}}(u,v_{i},Q)=x%
+		\Delta +e$. Then $A_{t_{v_{2}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
+		that $A_{t_{v_{2}}}(u,v_{i},P)=x\Delta +g$.
 
@@
 		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
-		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
+		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{2}}}(u,v_{i-1},Q^{\ast
 		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
@@
 		\begin{eqnarray*}
-			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
-			+h-(t_{u_{2}}-t_{v_2}) \\
-			&\geq &(\Delta -\delta _{0})+h>0,
+			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta +h-(t_{u_{2}}-t_{v_2}) \\
+			&\geq & \Delta +1-(\Delta-1)>0,
 		\end{eqnarray*}%
-		which proves the statement of the lemma.
+		where the last inequality follows by (\ref{basic-ineq-0}). This proves the statement of the lemma.
 
@@
 		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
-		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
+		A_{t_{v_{2}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
 		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%

### 2024-05-22 Arxiv-30-4-24/ARXIV+nina-corrections.tex
Added changes from Nina's PhD thesis comments

--- 2024-05-01 Arxiv-30-4-24/arxiv-30-4-24.tex
@@
 %that runs in polynomial-time.
-Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial-time  the matrix $D$
+Hence, given a $\Delta$-periodic temporal graph $(G,\lambda,\Delta)$, we can compute in polynomial time  the matrix $D$
 which consists of durations of fastest temporal paths among all pairs of vertices in $(G,\lambda,\Delta)$.
@@
 	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}.
-Here we are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
+We are given a formula $\phi$ that is a conjunction of so-called NAE (not-all-equal) clauses, where each clause contains exactly 3 literals (with three distinct variables).
     A NAE clause evaluates to \textsc{true} if and only if not all of its literals are equal, that is, at least one literal evaluates to \textsc{true} and at least one literal evaluates to \textsc{false}.
@@
     $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
-    If $x_i$ appears negated in $c$ we specify the following duratios:
+    If $x_i$ appears negated in $c$ we specify the following durations:
     $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
-    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
+    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following durations:
     $d(x_i,c)=2 \Delta$, $d(c,x_i)=\Delta + 2$
@@
     $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
-    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
+    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following durations:
     $d(x_i,x_j)=2\Delta +1$ and
     $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
-    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
+    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following durations:
     $d(c_i,c_j)= \Delta + 1$.
@@
 For an example of the constructed temporal graph see~\cref{fig:NP-example}.
-We now verify that all duratios are realized.
+We now verify that all durations are realized.
 \begin{itemize}
@@
     Therefore the temporal path from $c_i$ to $c_j$
-    uses the edges $\{x_k^T, c_i\}$, $\{x_\ell^T, c_j\}$, and $\{x_k^T, x_\ell ^T\}$, with labels $1$,~$2$, and $1$ (at times $1$,~$2$, and $\delta + 1$), respectively,
+    uses the edges $\{x_k^T, c_i\}$, $\{x_\ell^T, c_j\}$, and $\{x_k^T, x_\ell ^T\}$, with labels $1$,~$2$, and $1$ (at times $1$,~$2$, and $\Delta + 1$), respectively,
     which proves the desired equality.
@@
 \begin{proof}
-    Let $D$ be an input matrix for problem \deltaExact\ of dimension $n \times n$.
+    Let $D$ be an input matrix of \deltaExact\ of dimension $n \times n$.
     Let us fix the vertices of the corresponding graph $G$ of $D$ as $v_1, v_2, \dots, v_n$, where vertex $v_i$ corresponds to the row and column $i$ of matrix $D$.
@@
 Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$.
-If this check succeeds for all vertex pairs, output the labeling $\lambda$, otherwise abort.
+If this check succeeds for all vertex pairs, output yes, otherwise abort.
 
@@
 $(\Leftarrow)$: Assume we face a yes-instance, then there exists a labeling $\lambda^\star$ that realizes all durations specified in $D$.
-Let $e^\star$ denote the edge initially picked by the algorithm.
+Let $e^\star$ denote the edge initially picked by our algorithm.
 For all edges $e$ let $\lambda(e)=(\lambda^\star(e)-\lambda^\star(e^\star)+1)\bmod \Delta$.
@@
 
-Initially, our algorithm labels $e^\star$ with one, which equals $\lambda(e^\star)$.
+Initially, our algorithm labels $e^\star$ with $1$, which equals $\lambda(e^\star)$.
 Now let $e$ be an edge popped off the queue by the algorithm in some iteration, that is on the distance $i$ from $e^\star$.
@@
 For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
-This results in producing $f(k) \cdot |D| ^ {O(1)}$ constraints. 
+This results in producing $f(k) \cdot |D| ^ {O(1)}$ constraints, where $|D|= n^2$. 
 Note that we have to do this while keeping the total number of variables upper-bounded by some function in $k$.
@@
     and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$.
-    We want to guess a split vertex of $w$ in $S_{u,v}$, and the fastest temporal path that reaches it.
+    We want to determine the split vertex of $w$ in $S_{u,v}$, and guess the fastest temporal path that reaches it.
     We again have two cases,
@@
 			\includegraphics{fig-guess2}}
-		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red).
+		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow  v_{p-1} \rightarrow v_2$ (in red).
 			\label{fig:FPT-guessG5}}
@@
     We define the \emph{travel delay} from $u$ to $z$ at vertex $v$, denoted with $\tau_v^{uz}$,
-    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$.
+    as the difference of the labels of $e_2$ and $e_1$, where we subtract the value of the label of $e_1$ from the label of $e_2$,  modulo~$\Delta$, if the labels are different, or we set it to $\Delta$.
     More specifically:
+    \begin{itemize}
+        \item if $\lambda(e_1) \neq \lambda(e_2)$ we have
     \begin{equation}\label{eq:def-VertexWaitingTime}
-       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta.
+       \tau_v^{uz} \equiv \lambda (e_2) - \lambda(e_1) \pmod \Delta,
     \end{equation}
-    Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
+    \item if $\lambda(e_1) = \lambda(e_2)$ we have
+    \begin{equation*}
+    \tau_v^{uz} = \Delta.
+    \end{equation*}
+    \end{itemize}
+    %Similarly, $\tau_v^{zu} \equiv \lambda (e_1) - \lambda(e_2) \pmod \Delta$.
     \end{definition}
@@
 Suppose that $v_i$ is reached the fastest from $u$ by a path $P = (u = u_1, u_2, \dots, u_{j-1}, v_i)$.
-We split the path with $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
+We split the path $P_{u,v}$ into a path $ Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$
 (for details see~\cref{fig:FPT-uv-Labelalledges}).
@@
 		where we assume that the fastest temporal path from $u$ to $v$ is $P_{u,v} = (u=v_1, v_2, \dots v_p)$,
-		and the fastest temporal path from $u$ to $v_i$ in $P_{u,v}$ is $P = (u, u_2, u_3, \dots, v_i)$.
-		We denote with $Q = (u=v_1, v_2, \dots, v_i)$ and with $R = (v_i, v_{i+1}, \dots, v_p=v)$.
+		and the fastest temporal path from $u$ to $v_i$ is $P = (u, u_2, u_3, \dots, v_i)$.
+		We denote $Q = (u=v_1, v_2, \dots, v_i)$ and $R = (v_i, v_{i+1}, \dots, v_p=v)$.
 		\label{fig:FPT-uv-Labelalledges}}
@@
     Let us observe the case of the fastest temporal paths between $v_{1}$ and $v_{3}$.
-    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
+    Denote $Q = (v_{1}, v_2, v_3)$ and $P' = (v_3,v_4,v_5,v_6)$.
     From our proposition, it follows that
@@
     $
-    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
+    d(v_{3}, v_{1}, P^-) \leq d(v_{3}, v_{1}, Q)
     $. 
@@
     of the form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
-    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
+    We denote $R' = (v_3, v_4, v_5)$ and $S = (v_1,v_2,v_3)$.
     Again we get the following.
@@
     Similarly, let $Q_2$ be the underlying path of the fastest temporal path from $z_2$ to $y$, consisting of the edge $z_2u$ together with the path $Q$ from $u$ to $y$.
-    Define $P_2$ as the second path from $z_2$ to $y$ that first uses the edge $z_1u$ and then the path $P$.
-    Similarly, $Q_1$ represents the second path from $z_1$ to $y$ that first uses the edge $z_2u$ and then the path $Q$.
+    Define $P_2$ as the second path from $z_2$ to $y$ that first uses the edge $z_2u$ and then the path $P$.
+    Similarly, $Q_1$ represents the second path from $z_1$ to $y$ that first uses the edge $z_1u$ and then the path $Q$.
     Our objective is to demonstrate that either $P = Q$ or that $d(P_1, \lambda) = d(Q_1, \lambda)$ (and $d(P_2, \lambda) = d(Q_2, \lambda)$).
@@
 	\caption{An example of the situation in \cref{lemma:treeEquivClass-intVertices}.
-        We have two paths $Q$ (in blue) and $P$ (in red) from $x$ to $y$.
+        We have two paths $Q$ (in blue) and $P$ (in red) from $u$ to $y$.
         We assume that the fastest temporal path from $z_1$ to $y$ is $P_1 = \{z_1 u\} \cup P$,
-		and the fastest temporal path from $z_2$ to $y$ is $Q_2 = \{z_2 x\} \cup Q$.
+		and the fastest temporal path from $z_2$ to $y$ is $Q_2 = \{z_2 u\} \cup Q$.
         %
@@
         with $P_2 = \{z_2 u\} \cup P$ another temporal path from $z_2$ to $y$.
-        The labels on the edges $z_1 x, z_2 x$ are $t_1,t_2$, respectively. Similar, the labels of the last edges of paths $P$ and $Q$ are  $t_p, t_q$, respectively.
+        The labels on the edges $z_1 u, z_2 u$ are $t_1,t_2$, respectively. Similar, the labels of the last edges of paths $P$ and $Q$ are  $t_p, t_q$, respectively.
 		\label{fig:FPT-equivClass}}
@@
     Because $Q_2$ is the fastest path from $z_2$ to $y$ we have also that $d(P_2, \lambda) \geq D_{z_2,y}$, which gives us $t_p - t_2 + (c_q - 1) \Delta \geq t_q - t_2 + c_q \Delta$.
-    This is equivalent to $t_p \geq t_q + \Delta$, but since $t_p, t_q \in \Delta$ this cannot happen.
+    This is equivalent to $t_p \geq t_q + \Delta$, but since $t_p, t_q \in [\Delta]$ this cannot happen.
     Therefore, we conclude that $c_p = c_q$.
@@
 and similarly, one of the temporal paths between $v_{i}$ and $v_{i+2}$ has to pass through $f$, which determines $\lambda(f)$ with respect to $\lambda(e_{i+1})$ (and consequently $\lambda(e_{p-1})$).
-In the third case, knowing the temporal paths between $v_{i-1}$ to $v_{i+1}$ results in determining the label of $\lambda(e_{i-1}$ with $\lambda(e_i)$, which consequently relates labels of all of the edges of the segment against each other.
+In the third case, knowing the temporal paths between $v_{i-1}$ to $v_{i+1}$ results in determining the label of $\lambda(e_{i-1})$ with $\lambda(e_i)$, which consequently relates labels of all of the edges of the segment against each other.
 %
@@
 %and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or $x_e = \lambda(g)$, or $x_e > \lambda(g)$.
-This results in $O(k^2)! = k^{O(k^2)}$ guesses
+This results in $O(k^2!) = k^{O(k^2)}$ guesses
 and consequently
@@
 \end{equation}
-In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is negative, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
+In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is not positive, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
 Note that we can determine if the difference of two consecutive labels is positive or negative. 
@@
 \subparagraph{\boldmath Fastest paths from $r \in Z$ to $y \in U \cup U^*$.}
-Let $x \in V(G')$ be a clip vertex of the tree $T_x$ in $G[Z \cup \{x\}]$ with $r \in V(T_i)$ be a vertex in the first layer of $T_x$.
+Let $x \in V(G')$ be a clip vertex of the tree $T_x$ in $G[Z \cup \{x\}]$ with $r \in V(T_x)$ be a vertex in the first layer of $T_x$.
 We distinguish the following two cases.
